### 2025-01-27 manuscript_GNM.qmd
initial commit

---
title: "WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis"
authors:
  - name: Shreya Dimri
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
    corresponding: true
  - name: Tuba Rizvi
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
  - name: Júlio Segovia
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
  - name: Alfredo Sánchez-Tójar
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany

bibliography: references.bib
---

# Methods (\~2200 words)

@dimri2024

then methods and results (generally following one of my previous meta-analysis, e.g. the Gambusia one)

# Supplementary Materials

### 2025-01-27 code/00_search_stratergy_litsearchr_code.R

@@ -1,117 +1,0 @@
-#-------------------------- Installing required packages----------------------------------------
-# Remotes package is required to allow you to install litsearchr package
-# Since it is only available through Github and not CRAN
-# Skip this part if you have already installed litsearchr 
-
-
-install.packages("remotes")
-library(remotes)
-#to install litsearchr from Github
-install_github("elizagrames/litsearchr", ref="main")
-
-#-----------------------------------------------------------------------------------------------
-
-#Loading required packaged if they are already installed
-pacman::p_load(litsearchr,igraph,ggplot2)
-
-#---------------------------------- Naive search file import and deduplication---------------------------------------------
- 
-# Before using litsearchr to refine your search terms, we can perform a naive search on the topic on WOS
-# The references generated from this naive search can then be used to refine the search terms using litsearchr
-# In this case we used references that were present in our own library (through previous searches)
-
-# We can import .bib, .ris or .txt files using 
-# import_results function of litsearchr (which is from synthesizer package)
-# The function can also be used in case the searches were performed in more the one data base...
-# ...e.g.  =c("savedrecs.bib","scopus.bib"))
-
-
-# In our case we use .bib file "own_library_references.bib" from our own set of references
-search_directory="data/01_systematic_search/01_search_strategy/data_litsearchr"
-naiveimport<- litsearchr::import_results(directory=search_directory,
-                                         file = "own_library_references.bib")
-
-
-#remove_duplicates function can be used to deduplicate the list based on titles 
-# One can use different methods to deduplicate such as exact search or fuzzy search
-
-# In our case, we do not need to deduplicate since we have a short list of references 
-# of 15 papers that we have looked at manually already.. 
-# However we perform deduplication to show as an example with exact title comparision..
-deduplicated_naiveimport<- litsearchr::remove_duplicates(naiveimport, field= "title", method = "exact")
-
-#----------------------------to extract/search for keywords for the naive search------------------------------------------
-
-#extract_terms is used to extract the search string words from our data base
-#here we look for search string words in the title, abstract and keywords of the paper
-#we use the fakerake method which is the default method of litsearchr that is similar to rapid automatic keyword extraction
[…]

### 2025-01-27 code/01_systematic_search_deduplication.R

@@ -1,92 +1,0 @@
-##############################################################
-# Description of script and Instructions
-##############################################################
-
-# This script is to:
-# 1. import the .bib files from Web of Science (WOS) and Scopus
-# 2. combine the 2 .bib files to produce a full reference list (encoding errors may occur depending 
-# on the system and "UTF-16LE" was used in this case for writing and reading the full_reference_before_deduplication)
-# 3. deduplicate the full reference list and produce a unique list of 
-# papers
-
-# INPUT files: 
-# GNM_wos.bib
-# GNM_scopus.bib
-
-# OUTPUT files:
-# full_reference_before_deduplication.csv
-# unique_reference_list.csv
-# Packages used: dplyr , revtools
-
-
-# created on 12.09.22 for green nest material project 
-# Code written by: SD and revised by: NA
-
-##############################################################
-# Packages needed
-##############################################################
-
-# load pacakges
-# If pacman is not installed already use
-# install.packages("pacman")
-pacman::p_load(dplyr, revtools)
-
-# cleaning up
-rm(list=ls())
-
-
-################################
-
-# importing the .bib files from WEB OF SCIENCE and SCOPUS
-
-reference_data_wos <- read_bibliography("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
-reference_data_scopus <- read_bibliography("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
-
-# reducing fields to the minimum number of fields
-# so that all databases have the same columns. Also, these fields
-# are the important ones for the screening.
-reducing_fields <- c("label","title","author","journal",
-                         "volume","number","pages","year",
-                         "doi","abstract") 
-
-
-reference_data_wos_reduced <- reference_data_wos[,reducing_fields]
-reference_data_scopus_reduced <- reference_data_scopus[,reducing_fields]
-
-##############################################################
-# Full reference list without de-duplication
-##############################################################
-
-# building the full reference list before de-duplication
-full_reference_data <- rbind(reference_data_wos_reduced,
-                             reference_data_scopus_reduced)
-
-#write.csv(full_reference_data,"data/01_systematic_search/02_reference_data/full_reference_before_deduplication.csv",row.names=FALSE, fileEncoding = "UTF-16LE")
-#full_reference_data <- read.table("data/01_systematic_search/02_reference_data/full_reference_before_deduplication.csv",
-#                           header=T,sep=",",fileEncoding = "UTF-16LE")
-
-
[…]

### 2025-01-27 code/02_abstract_screening.R

@@ -1,92 +1,0 @@
-##############################################################
-# Description of script and Instructions
-##############################################################
-
-# This script is to:
-# 1. import the unique reference list after de-duplication
-# 2. Adding a unique identified (Paper_ID) for each article
-# 3. Creating subsets for title and abstract screening for the 
-# three screeners (SD, JS and TR) for preliminary and final phase of screening
-
-# Title and abstract screening was conducted using revtools package- screen_abstracts()
-
-# Packages used: dplyr , revtools , readr
-
-# created on 04.10.22 for green nest material project
-# Code written by: SD and revised by: 
-
-##############################################################
-# Packages needed
-##############################################################
-
-# load pacakges
-pacman::p_load(dplyr, revtools, readr)
-
-# cleaning up
-rm(list=ls())
-
-# set seed for reproducibility (for consistent random number generation)
-set.seed(1)
-
-############################################################
-# Importing data after de-duplication
-############################################################
-
-unique_reference_list <- read.table("data/01_systematic_search/02_reference_data/unique_reference_list.csv",
-                                    header=T,sep=",")
-
-# Giving individual paper ID for screening
-
-Paper_ID=sprintf("GNM_%03d", 1:nrow(unique_reference_list))
-unique_reference_list=cbind(Paper_ID,unique_reference_list)
-
-
-##################################################################
-# Abstract screening subsets for multiple screenings 
-##################################################################
-
-##############################################################
-# Multiple abstract screening (performed by SD, JS and TR) 
-# To randomly select 40 papers (~10%) in two sub-sets
-# Abstract screening performed using revtools package
-##############################################################
-
-random_ID1<-sample(1:nrow(unique_reference_list),40)
-prelim_screen_set1=unique_reference_list[random_ID1[1:20],]
-screen_abstracts(prelim_screen_set1)
-prelim_screen_set2=unique_reference_list[random_ID1[21:40],]
-screen_abstracts(prelim_screen_set2)
-
-##############################################################
-# Rest of the abstract screening performed by SD, JS and TR 
-# Each paper screened twice
-##############################################################
-
-# To create three sets with all the papers that have not been screened yet
-
-##############################################################
-
-#screened by SD and TR
[…]

### 2025-01-27 code/03_data_cleaning_after_abstract_screening.R

@@ -1,117 +1,0 @@
-##############################################################
-# Description of script and Instructions
-##############################################################
-
-# This script is to:
-# 1. import the files after title and abstract screening (after any resolving differences)
-# 2. Creating a final dataset_after_abstract_screening with only final decisions
-# 3. Creating a file with selected_abstract_screening for further steps
-
-# INPUT files required
-# 
-# differences_prelim_set1_2022_10_07
-# differences_prelim_set2_2022_10_14
-# differences_abstract_screening_set1
-# differences_abstract_screening_set2
-# differences_abstract_screening_set3
-
-# Packages used: dplyr, readr, tidyverse, stringr
-
-# created on 17.11.22 for green nest material project
-# Code written by: SD and revised by: NA
-
-
-##############################################################
-# Packages needed
-##############################################################
-
-
-pacman::p_load(dplyr, readr, tidyverse, stringr)
-
-# cleaning up
-rm(list=ls())
-
-# set seed for reproducibility (for random number generation)
-set.seed(1)
-
-
-##############################################################
-# To merge three sets of abstract screening after screening
-
-##############################################################
-
-## Load datasets after screening
-
-differences_prelim_set1_2022_10_07 <- read_delim("data/01_systematic_search/03_title_and_abstract_screening/differences_prelim_set1_2022_10_07.csv",delim = ";", escape_double = FALSE, trim_ws = TRUE)
-differences_prelim_set2_2022_10_14 <- read_delim("data/01_systematic_search/03_title_and_abstract_screening/differences_prelim_set2_2022_10_14.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
-differences_abstract_screening_set1 <- read_delim("data/01_systematic_search/03_title_and_abstract_screening/differences_abstract_screening_set1.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
-differences_abstract_screening_set2 <- read_delim("data/01_systematic_search/03_title_and_abstract_screening/differences_abstract_screening_set2.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
-differences_abstract_screening_set3 <- read_delim("data/01_systematic_search/03_title_and_abstract_screening/differences_abstract_screening_set3.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
-
-# To keep only the final decisions after the discussions between screeners 
-
[…]

### 2025-02-17 manuscript_GNM.qmd
Added supplementary material and a structure that should work in principle

@@
 
-@dimri2024
+### Registration and Reporting
 
-then methods and results (generally following one of my previous meta-analysis, e.g. the Gambusia one)
+We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024].
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1).
+All resources associated with this study, including data and code, are available at [https://github.com/shreyadimri/Green_Nest_Material](#0){.uri} (insert Zenodo citation later).
+
+### Systematic Review
+
+#### Literature search
+
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 @supptbl-2
+
+#### Eligibility criteria
+
+#### Study selection and eligibility criteria
+
+-   Keyword search: where and when..
+
+-   Justification for development of keyword search
+
+-   Findings/Results of search
+
+-   Exclusion criteria
+
+-   How many papers in final meta-analysis and how many effect sizes
+
+-   PRISMA Diagram link
+
+### Data Extraction
+
+-   What did we extract in priority order
+
+-   Wrote to authors for missing info, used methods to deal with missing info
+
+-   Figures extraction
+
+-   Moderators extracted
+
+### Effect size calculation
+
+### Meta-analysis and meta-regressions
+
+-   main effect model
+
+-   meta-regressions for testing hypothesis
+
+-   meta-regressions for exploratory analyses
+
+Senstivity analysis and Publication Bias Test
+
+### Deviations from registration
 
 # Supplementary Materials
+
+<details><summary> Supplementary materials </summary>
+{{< include supplementary_appendix.qmd >}}
+</details>

### 2025-02-17 docs/supplementary_appendix.qmd
Added supplementary material and a structure that should work in principle

---
title: "Supplementary Appendix"
---

::: {#supptbl-1}
## PRISMA Eco-Evo Checklist

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

Here is a Prisma list that we have filled according to
:::

::: {#supptbl-2}
## Search String

The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile. For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date. We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.

1.  **Web of Science Core Collection Database**

Databases used in the search:

-   Science Citation Index Expanded (SCI-EXPANDED) - 1900 - present

-   Social Sciences Citation Index (SSCI) -1900 - present

-   Arts & Humanities Citation Index (AHCI) - 1975 - present

-   Conference Proceedings Citation Index - Science (CPCI-S) -1991 - present

-   Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) -1991 - present

-   Emerging Sources Citation Index (ESCI) 2017- present

TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))

2.  **SCOPUS Database**

TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))
:::

### 2025-02-17 manuscript_GNM.qmd
Added supplementary material and a structure that should work in principle

@@
 We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1).
-All resources associated with this study, including data and code, are available at [https://github.com/shreyadimri/Green_Nest_Material](#0){.uri} (insert Zenodo citation later).
+All resources associated with this study, including data and code, are available at <https://github.com/shreyadimri/Green_Nest_Material> (insert Zenodo citation later).
 
@@
 
-#### Eligibility criteria
+#### ility criteria
 
@@
 
-# Supplementary Materials
+<details>
 
-<details><summary> Supplementary materials </summary>
+<summary>Supplementary Appendix</summary>
+
 {{< include supplementary_appendix.qmd >}}
+
 </details>

### 2025-02-18 docs/manuscript_GNM.qmd
supp should work now

--- 2025-02-17 manuscript_GNM.qmd
@@
 
+```{r Setup, include=FALSE, echo=FALSE}
+
+pacman::p_load(readr)
+
+```
+
 # Methods (\~2200 words)
 
-### Registration and Reporting
+Registration and Reporting
 
 We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024].
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1).
-All resources associated with this study, including data and code, are available at <https://github.com/shreyadimri/Green_Nest_Material> (insert Zenodo citation later).
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
 
-### Systematic Review
+## Systematic Review
+
+### Literature search
+
+```{r load search data, include=FALSE, echo=FALSE}
+
+unique_reference_list <- read_csv("data/unique_reference_list.csv")
+
+```
+
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024.
+The search query was designed in three blocks to included terms for predictor/treatment ("green*" OR "herb*" OR "aromatic*" AND "nest*"), population of interest ("bird*" OR "aves" OR "avian" OR "ornithol*" OR "passerine*" OR "passeriform*" OR "songbird*" OR list of all bird genera) and only experimental studies ("experiment*" OR "manipulat\*") (for complete search string details see @figsupp-string).
+We searched the title, abstract and keywords in English language only.
+Our search found `{r} nrow(unique_reference_list)`
 
@@
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 @supptbl-2
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022
 
-#### ility criteria
+Eligibility criteria
 
@@
 
+## Supplementary Appendix
+
 <details>
 
-<summary>Supplementary Appendix</summary>
+<summary>Supplementary materials</summary>
 

### 2025-02-18 docs/supplementary_appendix.qmd
supp should work now

@@
 title: "Supplementary Appendix"
+bibliography: references.bib
 ---
 
-::: {#supptbl-1}
-## PRISMA Eco-Evo Checklist
+::: {#figsupp-checklist}
+| Checklist Item | Sub-item Number | Sub-item | Reported by authors? | Notes |
+|----------------|-----------------|----------|----------------------|-------|
+|                |                 |          |                      |       |
+|                |                 |          |                      |       |
+|                |                 |          |                      |       |
 
-| Col1 | Col2 | Col3 |
-|------|------|------|
-|      |      |      |
-|      |      |      |
-|      |      |      |
-
-Here is a Prisma list that we have filled according to
+Prisma Eco-Evo Checklist @odea2021
 :::
 
-::: {#supptbl-2}
-## Search String
-
+::: {#figsupp-string}
 The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile.
@@
 We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.
-
-1.  **Web of Science Core Collection Database**
-
-Databases used in the search:
-
--   Science Citation Index Expanded (SCI-EXPANDED) - 1900 - present
-
--   Social Sciences Citation Index (SSCI) -1900 - present
-
--   Arts & Humanities Citation Index (AHCI) - 1975 - present
-
--   Conference Proceedings Citation Index - Science (CPCI-S) -1991 - present
-
--   Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) -1991 - present
-
--   Emerging Sources Citation Index (ESCI) 2017- present
-
-TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))
-
-2.  **SCOPUS Database**
-
-TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))
 :::

### 2025-02-18 supplementary_appendix.qmd
Added supplementary material and a structure that should work in principle
search string emmbed works, phew

--- 2025-02-17 docs/supplementary_appendix.qmd
@@
 
-1.  **Web of Science Core Collection Database**
-
-Databases used in the search:
-
--   Science Citation Index Expanded (SCI-EXPANDED) - 1900 - present
-
--   Social Sciences Citation Index (SSCI) -1900 - present
-
--   Arts & Humanities Citation Index (AHCI) - 1975 - present
-
--   Conference Proceedings Citation Index - Science (CPCI-S) -1991 - present
-
--   Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) -1991 - present
-
--   Emerging Sources Citation Index (ESCI) 2017- present
-
-TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))
-
-2.  **SCOPUS Database**
-
-TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))
+{{< include search_string.txt >}}
 :::

### 2025-02-18 supplementary_appendix.qmd
There is magic in this world, I do not understand it!

@@
 
-Prisma Eco-Evo Checklist @odea2021
+Prisma Eco-Evo Checklist according to @odea2021
 :::
@@
 The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile.
-For both the searches, we did not use any time limitation i.e.
-it included all the published literature till that given date.
-We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.
+For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date.
+We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.\
+\
+Search string for the Web of Science Core Collection\
+Databases used in the search included\
+-Science Citation Index Expanded (SCI-EXPANDED) \[1900-present\]\
+-Social Sciences Citation Index (SSCI) \[1900-present\]\
+-Arts & Humanities Citation Index (AHCI) \[1975 - present\]\
+-Conference Proceedings Citation Index - Science (CPCI-S) \[1991 - present\]\
+-Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) \[1991 - present\]\
+-Emerging Sources Citation Index (ESCI) \[2017- present\]\
+\
+We used advance search option and Title (TI), Abstract (AB) and Author Keywords (AK) to conduct our systematic search using the following string\
+\
+\<TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))\>\
+\
+The search was also conducted on SCOPUS using Advance Search Option and Title Abstract and Keyword (TITLE-ABS-KEY) on the same dates using the string\
+\
+\<TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))\>
 
-{{< include search_string.txt >}}
+Complete search string for the systematic search
 :::

### 2025-02-25 manuscript_GNM.qmd
Little more writing

@@
 
+```{r Setup, include=FALSE, echo=FALSE}
+
+pacman::p_load(readr)
+
+```
+
 # Methods (\~2200 words)
 
-### Registration and Reporting
+## Registration and Reporting
 
-We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024].
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1).
-All resources associated with this study, including data and code, are available at <https://github.com/shreyadimri/Green_Nest_Material> (insert Zenodo citation later).
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
+Unless stated otherwise, we adhered to the registered protocol.
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
 
-### Systematic Review
+## Systematic Review
 
-#### Literature search
+### Literature search
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 @supptbl-2
+```{r load search data, include=FALSE, echo=FALSE}
 
-#### ility criteria
+unique_reference_list <- read_csv("data/unique_reference_list.csv")
+full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
+selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
+```
+
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024.
+The search query was designed in three blocks to included terms for predictor/treatment (“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored for specific database see @figsupp-string).
+We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
+We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
+We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
+
+All title and abstract screening were screened independently by atleast two screeners (SD,TR,JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs) and measured any form of fitness proxy that can be used to address any of our hypothesis.
+`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening.
+
+Eligibility criteria
 

### 2025-02-25 manuscript_GNM.qmd

@@
 
-### Literature search
+### Study selection and eligibility crtieria
 
@@
 selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
+
+# For updated search
+unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
+full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
+selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")
 ```
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024.
-The search query was designed in three blocks to included terms for predictor/treatment (“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored for specific database see @figsupp-string).
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
+The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored for specific database see @figsupp-string).
 We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
@@
 
-All title and abstract screening were screened independently by atleast two screeners (SD,TR,JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
 We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs) and measured any form of fitness proxy that can be used to address any of our hypothesis.
-`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening.
+`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another.
+The three screeners collectively resolved the conflicting decisions (\~1% for title and abstract screening and 0% for fulltext screening) through discussion.
+
+We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` articles.
+After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
+We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
+In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search.
+These studies met our inclusion criteria and were added to our meta-analysis.
 
 Eligibility criteria
+
+Eligibility criteria
+
+Titles and abstracts were screened using **Rayyan QCRI** (Ouzzani et al.
+2016) by multiple reviewers, following a pre-defined decision tree (**Supplementary Figure S1**).
+A subset of studies (\~20%) was double-screened to ensure consistency, with conflicts (\~7% of cases) resolved through discussion.
+Following abstract screening, **\[X\] studies** proceeded to full-text review.
+Studies were included if they (1) involved free-living or captive birds, (2) experimentally tested the effects of green nest materials, and (3) reported fitness-related outcomes (e.g., survival, immune response, reproductive success).
+
+During full-text screening, **\[Y\] studies** were excluded due to missing quantitative data (e.g., mean, sample size, dispersion measures).
+When necessary, we contacted authors of studies published after **1995** to request missing data.
+For studies where authors did not respond, we imputed missing standard deviations when feasible but did not impute missing standard errors (**see Data Extraction and Effect Size Calculation**).
+
+The final dataset included **\[Z\] studies** (see PRISMA flowchart, **Figure 1**).
+All included studies, along with data, analysis code, and additional variables beyond our primary predictions, are available at **\[repository link\]** for transparency and reproducibility.Study selection and eligibility criteria
 

### 2025-02-26 docs/supplementary_appendix.qmd
Search and selection section done

@@
 The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile.
-For both the searches, we did not use any time limitation i.e.
-it included all the published literature till that given date.
-We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.
+For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date.
+We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.\
+\
+Search string for the Web of Science Core Collection\
+Databases used in the search included\
+-Science Citation Index Expanded (SCI-EXPANDED) \[1900-present\]\
+-Social Sciences Citation Index (SSCI) \[1900-present\]\
+-Arts & Humanities Citation Index (AHCI) \[1975 - present\]\
+-Conference Proceedings Citation Index - Science (CPCI-S) \[1991 - present\]\
+-Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) \[1991 - present\]\
+-Emerging Sources Citation Index (ESCI) \[2017- present\]\
+\
+We used advance search option and Title (TI), Abstract (AB) and Author Keywords (AK) to conduct our systematic search using the following string\
+\
+\<TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))\>\
+\
+The search was also conducted on SCOPUS using Advance Search Option and Title Abstract and Keyword (TITLE-ABS-KEY) on the same dates using the string\
+\
+\<TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))\>
+
+Complete search string for the systematic search
 :::
+
+::: {#figsupp-decision-tree}
+![](images/Decision_Tree_updated.png)
+:::
+
+::: {#figsupp-prisma-flowchart}
+This is the prisma flowchart
+:::

### 2025-02-26 manuscript_GNM.qmd
Search and selection section done

--- 2025-02-25 manuscript_GNM.qmd
@@
 
-### Literature search
+### Study selection and eligibility criteria
 
@@
 selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
+
+# For updated search
+unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
+full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
+selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")
+
+# For fulltext screening
+excluded_fulltext <- read_csv("data/excluded_fulltext.csv")
 ```
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024.
-The search query was designed in three blocks to included terms for predictor/treatment (“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored for specific database see @figsupp-string).
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
+The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string).
 We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
@@
 
-All title and abstract screening were screened independently by atleast two screeners (SD,TR,JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
-We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs) and measured any form of fitness proxy that can be used to address any of our hypothesis.
-`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening.
+All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
+`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another.
+We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
+`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
 
-Eligibility criteria
+We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
+After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
+We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
+In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search.
+These studies met our inclusion criteria and were added to our meta-analysis.
+The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart.
+We finally extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
+These were identified through our efforts to contact the authors of all included studies, and one dataset was provided by a co-author of this paper.
+<!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
 
-#### Study selection and eligibility criteria
-
--   Keyword search: where and when..
-
--   Justification for development of keyword search
-
--   Findings/Results of search
-
--   Exclusion criteria
+### Data Extraction
 
@@
 
--   PRISMA Diagram link
-
-### Data Extraction
+<!-- -->
 

### 2025-02-27 docs/supplementary_appendix.qmd
Data extraction section (almost complete)

@@
 ---
-title: "Supplementary Appendix"
 bibliography: references.bib
@@
 Prisma Eco-Evo Checklist according to @odea2021
+:::
+
+::: {#figsupp-variables}
+| variable name | description | values | Notes |
+|---------------|-------------|--------|-------|
+|               |             |        |       |
+|               |             |        |       |
+|               |             |        |       |
+
+This is the list of all the variables that were extracted for the purpose of this study
 :::

### 2025-02-27 manuscript_GNM.qmd
Data extraction section (almost complete)

@@
 
-## Systematic Review
-
-### Study selection and eligibility criteria
+## Study selection and eligibility criteria
 
@@
 The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart.
-We finally extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
-These were identified through our efforts to contact the authors of all included studies, and one dataset was provided by a co-author of this paper.
+
+## Data Extraction
+
+### Data collection process
+
+Data was extracted evenly by one of the three authors (\~33% each SD, TR and JMGS) and was checked by another to ensure correctness of the data.
+We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
+In cases where primary data was only available in figures (such as boxplots), we used 'metaDigitise' v.1.0.1 (@pick2018).
+If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
+In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
+
+To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
+We obtained one unpublished dataset ...
+\[calculate estimates here\]..
+Another unpublished dataset was provided by a co-author of this paper.
+We extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
+
 <!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
 
-### Data Extraction
+### Extracted variables
 
--   How many papers in final meta-analysis and how many effect sizes
+We extracted mean, variance and sample size for a control-treatment pairwise comparison.
+Controls included non-aromatic materials (e.g., grass, moss), lesser amounts of aromatic material, or no material.
+Treatments consisted of aromatic materials added by authors, birds, or both.
+In cases comparing non-aromatic material to a blank nest, the non-aromatic material was considered the treatment.
+We recorded the type of comparison being made as a moderator.
+Each pairwise comparison was given a unique Observation ID, a paper ID (for each article reporting this data), an experiment ID (for estimates coming from the same experimental setup), a group ID (for estimates from the same group of individual) and a repeated trait ID (for estimates that were measured repeatedly across time).
 
-<!-- -->
+For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, trait measured) and information about the extracted data (location or source of the data recorded).
+We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
+In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied ino arthropods or micro-organisms.
+For a complete list of variables extracted see @figsupp-variables .
 
--   What did we extract in priority order
+## Effect size calculation
 
--   Wrote to authors for missing info, used methods to deal with missing info
+Using the information we extracted from the articles, we calculated two effect sizes,along with their associated sampling variance, for each pairwise comparison-log response ratio (hereafter lnRR) and standardised mean difference with heteroscedasticity correction (hereafter SMDH).
 
--   Figures extraction
-
--   Moderators extracted
-
-### Effect size calculation
+-   How many papers in final meta-analysis and how many effect size.
 

### 2025-03-16 docs/manuscript_GNM.qmd
effect size text added

@@
 
-# Methods (\~2200 words)
+# Methods (\~2200-3800 words)
 
-Registration and Reporting
+## Registration and Reporting
 
-We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024].
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
+Unless stated otherwise, we adhered to the registered protocol.
 We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
@@
 
-## Systematic Review
-
-### Literature search
+## Study selection and eligibility criteria
 
@@
 unique_reference_list <- read_csv("data/unique_reference_list.csv")
+full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
+selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
 
+# For updated search
+unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
+full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
+selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")
+
+# For fulltext screening
+excluded_fulltext <- read_csv("data/excluded_fulltext.csv")
 ```
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024.
-The search query was designed in three blocks to included terms for predictor/treatment ("green*" OR "herb*" OR "aromatic*" AND "nest*"), population of interest ("bird*" OR "aves" OR "avian" OR "ornithol*" OR "passerine*" OR "passeriform*" OR "songbird*" OR list of all bird genera) and only experimental studies ("experiment*" OR "manipulat\*") (for complete search string details see @figsupp-string).
-We searched the title, abstract and keywords in English language only.
-Our search found `{r} nrow(unique_reference_list)`
+We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
+The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string).
+We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
+We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
+We validated our search using an initial library of 15 relevant articles (\@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 
-#### Literature search
+All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
+`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another.
+We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
+`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022
+We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
+After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
+We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
+In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search.
+These studies met our inclusion criteria and were added to our meta-analysis.
+The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart.
 
-Eligibility criteria
+## Data Extraction
 
-#### Study selection and eligibility criteria
+### Data collection process
 
--   Keyword search: where and when..
+Data was extracted evenly by one of the three authors (\~33% each SD, TR and JMGS) and was checked by another to ensure correctness of the data.
+We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
+In cases where primary data was only available in figures (such as boxplots), we used 'metaDigitise' v.1.0.1 (@pick2018).
+If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
+In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
 
--   Justification for development of keyword search
+To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
+We obtained one unpublished dataset ...
+\[calculate estimates here\]..
+Another unpublished dataset was provided by a co-author of this paper.
+We extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
 
--   Findings/Results of search
+<!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
 
--   Exclusion criteria
+### Extracted variables
 
--   How many papers in final meta-analysis and how many effect sizes
+We extracted mean, variance and sample size for a control-treatment pairwise comparison.
+Controls included non-aromatic materials (e.g., grass, moss), lesser amounts of aromatic material, or no material.
+Treatments consisted of aromatic materials added by authors, birds, or both.
+In cases comparing non-aromatic material to a blank nest, the non-aromatic material was considered the treatment.
+We recorded the type of comparison being made as a moderator.
+Each pairwise comparison was given a unique Observation ID, a paper ID (for each article reporting this data), an experiment ID (for estimates coming from the same experimental setup), a group ID (for estimates from the same group of individual) and a repeated trait ID (for estimates that were measured repeatedly across time).
 
--   PRISMA Diagram link
+For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, trait measured) and information about the extracted data (location or source of the data recorded).
+We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
+In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied into arthropods or micro-organisms.
+For a complete list of variables extracted see @figsupp-variables .
 
-### Data Extraction
+## Effect size calculation
 
--   What did we extract in priority order
+We calculated two effect sizes for each pairwise comparision-log response ratio (lnRR) and standardised mean difference with heteroscedasticity correction (SMDH), using escalc function (measure= ROM and SMDH respectively, vtype= "LS") in metafor package (@metafor).
+We specified treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the sign was inverted to ensure comparability across all fitness proxies.
+In all cases, the effect size were coded such that the fitness proxies were positively correlated with the overall fitness.
 
--   Wrote to authors for missing info, used methods to deal with missing info
+For studies reporting only inferential statistics (e.g., t-tests, ANCOVA, or contingency tables), we estimated SMD values using the equations provided by @thehand2019.
+lnRR cannot be computed from inferential statistics, and only SMD under the assumption of homoskedasticity was derived from such data.
+Since lnRR can only be used for ratio scale data, we excluded all effect sizes with a negative value (n=?) when calculating lnRR.
 
--   Figures extraction
-
--   Moderators extracted
-
-### Effect size calculation
+The sample sizes used was the number of nests in each group, and not the number of individuals, whenever possible.
+In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
+For the cases where the authors reported no significant difference between the two groups (k=2, n=16) but did not provide the values, we used zero as the effect size.
+To impute the SD for these cases, we used the missing case approach following @nakagawa2022.
 
@@
 
+## Stuff that needs to go somewhere
+
+**Methods**
+
+**Effect Size Calculation**
+
+To quantify the effect of green nest material on bird fitness, we computed effect sizes using two primary metrics: log response ratio (lnRR) and standardized mean difference with heteroscedasticity correction (SMDH).
+lnRR was calculated following Hedges et al.
+(1999) using the `escalc()` function in the R package `metafor` (Viechtbauer, 2010), with `measure=ROM` and `vtype=LS`, the latter ensuring large sample approximation for sampling variance estimation (Bonett, 2008).
+SMDH was computed similarly using `measure=SMDH`, incorporating bias correction for heteroscedasticity (Bonett, 2009).
+For studies reporting inferential statistics (e.g., t-values, F-values) but not primary data, we derived SMD estimates using equations from Lajeunesse (2013) and Nakagawa & Cuthill (2007).
+Effect sizes were adjusted to ensure that positive values corresponded to increased fitness in experimental groups relative to controls.
+To account for repeated use of control or treatment groups across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group appeared in comparisons.
+
+**Meta-Analysis and Meta-Regression**
+
+We conducted two separate multilevel meta-analyses (intercept-only models) to estimate the overall effect size using both lnRR and SMDH as dependent variables.
+Sampling variances were modeled as variance--covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study (Noble et al., 2017).
+Robust variance estimation was applied using the `robust()` function from `metafor`, employing the CR2 correction from the `clubSandwich` package (Pustejovsky, 2024) for small-sample adjustments.
+Sensitivity analyses were conducted with correlation values of 0.3 and 0.7, with results reported in supplementary materials.
+
+For moderator analyses, we implemented unimoderator multilevel meta-regressions to investigate heterogeneity sources.
+These models included key moderators such as parasite type, experimental design, bird species, and trait type.
+Categorical moderators required a minimum of five data points per level; otherwise, levels were merged or excluded from analyses.
+To assess heterogeneity, we calculated four metrics (I², τ², CV, and M) following Yang et al.
+(2023).
+The proportion of heterogeneity explained by moderators was quantified using R² marginal (Nakagawa & Schielzeth, 2013).
+
+**Publication Bias and Heterogeneity**
+
+Publication bias was assessed through multilevel meta-regressions maintaining the same random-effects structure as above. Following Nakagawa et al. (2022), we executed the following steps:
+
+1.  A uni-moderator meta-regression to detect small-study effects for both lnRR and SMDH, using the square root of the inverse effective sample size as the moderator.
+
+2.  A subsequent uni-moderator meta-regression using the inverse effective sample size to provide a less biased adjusted overall effect.
+
+3.  A time-lag bias analysis using publication year (mean-centered) as the moderator.
+
+4.  A full meta-regression model incorporating small-study effects, time-lag bias, and all other moderators to assess combined heterogeneity sources.
+
+Heterogeneity was further explored using variance decomposition and random-effects modeling, including species and phylogeny if additional effect sizes warranted phylogenetic non-independence correction (Cinar et al., 2022).
+
+**Sensitivity Analyses**
+
+To ensure robustness, we conducted additional sensitivity analyses:
+
+1.  Repeating meta-analyses and meta-regressions using only effect sizes derived from means, SDs, and sample sizes, excluding those based on inferential statistics.
+
+2.  Implementing a bivariate multilevel meta-analytic model (Yang et al., 2024) incorporating both lnRR and SMDH as response variables.
+
+3.  Re-running intercept-only meta-analyses with different sampling variance correlations (ρ = 0.3 and 0.7) and extending these sensitivity analyses to meta-regressions if necessary.
+
+Non-pre-registered sensitivity analyses that emerged during data processing were reported in supplementary materials.
+
+**Data Management and Software**
+
+All data extraction and cleaning were conducted in R.
+The dataset and analysis scripts are publicly available on GitHub (https://github.com/shreyadimri/Green_Nest_Material).
+Effect size calculations and meta-analyses were performed using the `metafor` package (Viechtbauer, 2010), and additional robust variance estimation was conducted with the `clubSandwich` package (Pustejovsky, 2024).
+
+# Results
+
+How many papers in final meta-analysis and how many effect size.
+
 ## Supplementary Appendix

### 2025-03-16 manuscript_GNM.qmd
effect size text added

@@
 
-# Methods (\~2200 words)
+# Methods (\~2200-3800 words)
 
@@
 We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
-We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved.
+We validated our search using an initial library of 15 relevant articles (\@figsupp-own-library), ensuring all were retrieved.
 Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
@@
 We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
-In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied ino arthropods or micro-organisms.
+In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied into arthropods or micro-organisms.
 For a complete list of variables extracted see @figsupp-variables .
@@
 
-Using the information we extracted from the articles, we calculated two effect sizes,along with their associated sampling variance, for each pairwise comparison-log response ratio (hereafter lnRR) and standardised mean difference with heteroscedasticity correction (hereafter SMDH).
+We calculated two effect sizes for each pairwise comparision-log response ratio (lnRR) and standardised mean difference with heteroscedasticity correction (SMDH), using escalc function (measure= ROM and SMDH respectively, vtype= "LS") in metafor package (@metafor).
+We specified treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the sign was inverted to ensure comparability across all fitness proxies.
+In all cases, the effect size were coded such that the fitness proxies were positively correlated with the overall fitness.
 
--   How many papers in final meta-analysis and how many effect size.
+For studies reporting only inferential statistics (e.g., t-tests, ANCOVA, or contingency tables), we estimated SMD values using the equations provided by @thehand2019.
+lnRR cannot be computed from inferential statistics, and only SMD under the assumption of homoskedasticity was derived from such data.
+Since lnRR can only be used for ratio scale data, we excluded all effect sizes with a negative value (n=?) when calculating lnRR.
+
+The sample sizes used was the number of nests in each group, and not the number of individuals, whenever possible.
+In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
+For the cases where the authors reported no significant difference between the two groups (k=2, n=16) but did not provide the values, we used zero as the effect size.
+To impute the SD for these cases, we used the missing case approach following @nakagawa2022.
 
 ### Meta-analysis and meta-regressions
+
+To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical using lnRR or SMDH as dependent variables.
+
+Sampling variances were modeled as variance--covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study (Noble et al., 2017).
+Robust variance estimation was applied using the `robust()` function from `metafor`, employing the CR2 correction from the `clubSandwich` package (Pustejovsky, 2024) for small-sample adjustments.
+Sensitivity analyses were conducted with correlation values of 0.3 and 0.7, with results reported in supplementary materials.
+
+For moderator analyses, we implemented unimoderator multilevel meta-regressions to investigate heterogeneity sources.
+These models included key moderators such as parasite type, experimental design, bird species, and trait type.
+Categorical moderators required a minimum of five data points per level; otherwise, levels were merged or excluded from analyses.
+To assess heterogeneity, we calculated four metrics (I², τ², CV, and M) following Yang et al.
+(2023).
+The proportion of heterogeneity explained by moderators was quantified using R² marginal (Nakagawa & Schielzeth, 2013).
 
@@
 
+## Stuff that needs to go somewhere
+
+**Methods**
+
+**Effect Size Calculation**
+
+To quantify the effect of green nest material on bird fitness, we computed effect sizes using two primary metrics: log response ratio (lnRR) and standardized mean difference with heteroscedasticity correction (SMDH).
+lnRR was calculated following Hedges et al.
+(1999) using the `escalc()` function in the R package `metafor` (Viechtbauer, 2010), with `measure=ROM` and `vtype=LS`, the latter ensuring large sample approximation for sampling variance estimation (Bonett, 2008).
+SMDH was computed similarly using `measure=SMDH`, incorporating bias correction for heteroscedasticity (Bonett, 2009).
+For studies reporting inferential statistics (e.g., t-values, F-values) but not primary data, we derived SMD estimates using equations from Lajeunesse (2013) and Nakagawa & Cuthill (2007).
+Effect sizes were adjusted to ensure that positive values corresponded to increased fitness in experimental groups relative to controls.
+To account for repeated use of control or treatment groups across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group appeared in comparisons.
+
+**Meta-Analysis and Meta-Regression**
+
+**Publication Bias and Heterogeneity**
+
+Publication bias was assessed through multilevel meta-regressions maintaining the same random-effects structure as above. Following Nakagawa et al. (2022), we executed the following steps:
+
+1.  A uni-moderator meta-regression to detect small-study effects for both lnRR and SMDH, using the square root of the inverse effective sample size as the moderator.
+
+2.  A subsequent uni-moderator meta-regression using the inverse effective sample size to provide a less biased adjusted overall effect.
+
+3.  A time-lag bias analysis using publication year (mean-centered) as the moderator.
+
+4.  A full meta-regression model incorporating small-study effects, time-lag bias, and all other moderators to assess combined heterogeneity sources.
+
+Heterogeneity was further explored using variance decomposition and random-effects modeling, including species and phylogeny if additional effect sizes warranted phylogenetic non-independence correction (Cinar et al., 2022).
+
+**Sensitivity Analyses**
+
+To ensure robustness, we conducted additional sensitivity analyses:
+
+1.  Repeating meta-analyses and meta-regressions using only effect sizes derived from means, SDs, and sample sizes, excluding those based on inferential statistics.
+
+2.  Implementing a bivariate multilevel meta-analytic model (Yang et al., 2024) incorporating both lnRR and SMDH as response variables.
+
+3.  Re-running intercept-only meta-analyses with different sampling variance correlations (ρ = 0.3 and 0.7) and extending these sensitivity analyses to meta-regressions if necessary.
+
+Non-pre-registered sensitivity analyses that emerged during data processing were reported in supplementary materials.
+
+**Data Management and Software**
+
+All data extraction and cleaning were conducted in R.
+The dataset and analysis scripts are publicly available on GitHub (https://github.com/shreyadimri/Green_Nest_Material).
+Effect size calculations and meta-analyses were performed using the `metafor` package (Viechtbauer, 2010), and additional robust variance estimation was conducted with the `clubSandwich` package (Pustejovsky, 2024).
+
+# Results
+
+How many papers in final meta-analysis and how many effect size.
+
 ## Supplementary Appendix

### 2025-03-17 docs/manuscript_GNM.qmd
Added a little more to methods

@@
 
-pacman::p_load(readr)
+pacman::p_load(readr,tidyverse)
 
@@
 
+```{r load data extraction, include=FALSE, echo=FALSE}
+
+merged_data_extraction <- read_csv("data/03_data_cleaning/merged_data_extraction.csv")
+
+dataset_after_cleaning <- merged_data_extraction %>% filter(fulltext_screening!="excluded")
+included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
+```
+
 ### Data collection process
@@
 Another unpublished dataset was provided by a co-author of this paper.
-We extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
-
-<!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
+We extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
 
@@
 
-We calculated two effect sizes for each pairwise comparision-log response ratio (lnRR) and standardised mean difference with heteroscedasticity correction (SMDH), using escalc function (measure= ROM and SMDH respectively, vtype= "LS") in metafor package (@metafor).
+```{r load effect size, include=FALSE, echo=FALSE}
+
+inferential_stats<-dataset_after_cleaning%>%filter(statistics_type=="t-test"|statistics_type=="ANCOVA")
+
+contingency_table<-dataset_after_cleaning%>%filter(proxy_decision=="contingency table")
+
+no_ES<-dataset_after_cleaning%>%filter(proxy_comment == "use 0 as ES")
+
+negative_lnRR<-dataset_after_cleaning%>%
+  filter(measure_central_tendency_experiment<=0 | measure_central_tendency_control<=0)
+
+```
+
+We calculated two effect sizes for each pairwise comparision-log response ratio (lnRR) and standardised mean difference with heteroscedasticity correction (SMDH), using `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in `metafor` package (@metafor).
 We specified treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
@@
 
-For studies reporting only inferential statistics (e.g., t-tests, ANCOVA, or contingency tables), we estimated SMD values using the equations provided by @thehand2019.
-lnRR cannot be computed from inferential statistics, and only SMD under the assumption of homoskedasticity was derived from such data.
-Since lnRR can only be used for ratio scale data, we excluded all effect sizes with a negative value (n=?) when calculating lnRR.
+For studies reporting only inferential statistics (e.g., t-tests, ANCOVA), we estimated SMD values (n=`{r} nrow(inferential_stats)`, k=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019 .
+In cases of dichotomous variables (e.g., successful nests, n=`{r} nrow(contingency_table)`, k=`{r} length(unique(contingency_table$paper_ID))`) we used the data to calculate log odds ratio using `escalc` function (`measure=OR`) and convert it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics or dichotomous variables, only SMD under the assumption of homoskedasticity was derived from such data.
+We excluded these effect sizes along with any zero or negative values (n=`{r} nrow(negative_lnRR)`, k=`{r} length(unique(negative_lnRR$paper_ID))`) when calculating lnRR.
 
@@
 In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
-For the cases where the authors reported no significant difference between the two groups (k=2, n=16) but did not provide the values, we used zero as the effect size.
+For the cases where the authors reported no significant difference between the two groups (n=`{r} nrow(no_ES)`, k=`{r} length(unique(no_ES$paper_ID))`) but did not provide the values, we used zero as the effect size.
 To impute the SD for these cases, we used the missing case approach following @nakagawa2022.
 
-### Meta-analysis and meta-regressions
+## Meta-analysis
 
--   main effect model
+We used rma.mv function from metafor pacjage using 'REML' method to fit all the models.
+To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical using lnRR or SMDH as dependent variables.
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017].
 
--   meta-regressions for testing hypothesis
+*To understand the sources of variation, we calculated Q and total heterogeneity (𝜎2), its source (or relative heterogeneity; I2) and two different metrics to understand its magnitude – a mean-standardized metric (CV) and a variance-mean-standardized metric (M; more in* @yang2025*).*
 
--   meta-regressions for exploratory analyses
+*To understand the sources of variation or heterogeneity, for the intercept-only models, we will use the pluralistic approach recently suggested by which consists of calculating four metrics of heterogeneity (σ2, I2, CV, M) to comprehensively understand both total and random-effect specific heterogeneity.
+For the meta-regressions, we will calculate Rmarginal2 to quantify the heterogeneity explained by the moderator(s) in proportion to the total variation (Nakagawa & Schielzeth, 2013).*
 
-Senstivity analysis and Publication Bias Test
+## Meta-regression for testing hypothesis
 
-### Deviations from registration
+For understanding the effect of green nest material on reproductive success (courtship hypothesis) and on protective effects and health benefits for the nestling (Parental care hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
 
-## Stuff that needs to go somewhere
+*For meta-regression models, we estimated the percentage of heterogeneity explained by the moderators using R2marginal (Nakagawa & Schielzeth 2013).
+We graphically presented the results as orchard plots using the R package “orchaRd” v.2.0 (Nakagawa et al.
+2023).*
 
-**Methods**
+## Meta-regression for exploratory analyses
 
-**Effect Size Calculation**
-
-To quantify the effect of green nest material on bird fitness, we computed effect sizes using two primary metrics: log response ratio (lnRR) and standardized mean difference with heteroscedasticity correction (SMDH).
-lnRR was calculated following Hedges et al.
-(1999) using the `escalc()` function in the R package `metafor` (Viechtbauer, 2010), with `measure=ROM` and `vtype=LS`, the latter ensuring large sample approximation for sampling variance estimation (Bonett, 2008).
-SMDH was computed similarly using `measure=SMDH`, incorporating bias correction for heteroscedasticity (Bonett, 2009).
-For studies reporting inferential statistics (e.g., t-values, F-values) but not primary data, we derived SMD estimates using equations from Lajeunesse (2013) and Nakagawa & Cuthill (2007).
-Effect sizes were adjusted to ensure that positive values corresponded to increased fitness in experimental groups relative to controls.
-To account for repeated use of control or treatment groups across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group appeared in comparisons.
-
-**Meta-Analysis and Meta-Regression**
-
-We conducted two separate multilevel meta-analyses (intercept-only models) to estimate the overall effect size using both lnRR and SMDH as dependent variables.
-Sampling variances were modeled as variance--covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study (Noble et al., 2017).
-Robust variance estimation was applied using the `robust()` function from `metafor`, employing the CR2 correction from the `clubSandwich` package (Pustejovsky, 2024) for small-sample adjustments.
-Sensitivity analyses were conducted with correlation values of 0.3 and 0.7, with results reported in supplementary materials.
-
-For moderator analyses, we implemented unimoderator multilevel meta-regressions to investigate heterogeneity sources.
-These models included key moderators such as parasite type, experimental design, bird species, and trait type.
-Categorical moderators required a minimum of five data points per level; otherwise, levels were merged or excluded from analyses.
-To assess heterogeneity, we calculated four metrics (I², τ², CV, and M) following Yang et al.
-(2023).
-The proportion of heterogeneity explained by moderators was quantified using R² marginal (Nakagawa & Schielzeth, 2013).
-
-**Publication Bias and Heterogeneity**
+## Publication Bias Test
 
@@
 
+## Deviations from registration
+
 **Sensitivity Analyses**
@@
 
-**Data Management and Software**
-
-All data extraction and cleaning were conducted in R.
-The dataset and analysis scripts are publicly available on GitHub (https://github.com/shreyadimri/Green_Nest_Material).
-Effect size calculations and meta-analyses were performed using the `metafor` package (Viechtbauer, 2010), and additional robust variance estimation was conducted with the `clubSandwich` package (Pustejovsky, 2024).
+## Stuff that needs to go somewhere
 
@@
 
-How many papers in final meta-analysis and how many effect size.
+We obtained X effect sizes from k studies including How many papers in final meta-analysis and how many effect size.
 

### 2025-03-17 code/00_search_stratergy_litsearchr_code.R

@@ -1,0 +1,119 @@
+#-------------------------- Installing required packages----------------------------------------
+# Remotes package is required to allow you to install litsearchr package
+# Since it is only available through Github and not CRAN
+# Skip this part if you have already installed litsearchr 
+
+
+install.packages("remotes")
+library(remotes)
+#to install litsearchr from Github
+install_github("elizagrames/litsearchr", ref="main")
+
+#-----------------------------------------------------------------------------------------------
+
+#Loading required packaged if they are already installed
+pacman::p_load(litsearchr,igraph,ggplot2,tidyverse)
+
+#---------------------------------- Naive search file import and deduplication---------------------------------------------
+ 
+# Before using litsearchr to refine your search terms, we can perform a naive search on the topic on WOS
+# The references generated from this naive search can then be used to refine the search terms using litsearchr
+# In this case we used references that were present in our own library (through previous searches)
+
+# We can import .bib, .ris or .txt files using 
+# import_results function of litsearchr (which is from synthesizer package)
+# The function can also be used in case the searches were performed in more the one data base...
+# ...e.g.  =c("savedrecs.bib","scopus.bib"))
+
+
+# In our case we use .bib file "own_library_references.bib" from our own set of references
+search_directory="data/01_systematic_search/01_search_strategy/data_litsearchr"
+naiveimport<- litsearchr::import_results(directory=search_directory,
+                                         file = "own_library_references.bib")
+
+
+#remove_duplicates function can be used to deduplicate the list based on titles 
+# One can use different methods to deduplicate such as exact search or fuzzy search
+
+# In our case, we do not need to deduplicate since we have a short list of references 
+# of 15 papers that we have looked at manually already.. 
+# However we perform deduplication to show as an example with exact title comparision..
+deduplicated_naiveimport<- litsearchr::remove_duplicates(naiveimport, field= "title", method = "exact")
+
+#----------------------------to extract/search for keywords for the naive search------------------------------------------
+
+#extract_terms is used to extract the search string words from our data base
+#here we look for search string words in the title, abstract and keywords of the paper
+#we use the fakerake method which is the default method of litsearchr that is similar to rapid automatic keyword extraction
[…]

### 2025-03-27 docs/manuscript_GNM.qmd
First-ish draft of methods

@@
 
-# Methods (\~2200-3800 words)
+```{r load search data, include=FALSE, echo=FALSE, message= FALSE}
 
-## Registration and Reporting
+# Own reference list
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv")
 
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
-Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
-All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
-
-## Study selection and eligibility criteria
-
-```{r load search data, include=FALSE, echo=FALSE}
-
+# Systematic search and abstract screening
 unique_reference_list <- read_csv("data/unique_reference_list.csv")
@@
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
-The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string).
+# Methods
+
+## Registration and Reporting
+
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
+Unless stated otherwise, we adhered to the registered protocol.
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
+
+## Information source and search
+
+We conducted a systematic search on the Web of science Core Collection and Scopus citation database on 07.09.2022.
+The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for a complete search string tailored to specific database see @figsupp-string).
 We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
 We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
-We validated our search using an initial library of 15 relevant articles (\@figsupp-own-library), ensuring all were retrieved.
+We validated our search using an initial library of `{r} nrow(own_library)` relevant articles (@figsupp-own-library), ensuring all were retrieved.
 Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 
-All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+## Eligibility criteria
+
+All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in `revtools`.
 We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
@@
 We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
-`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
+`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decisions (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
 
 We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
-After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
+After de-duplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
 We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
@@
 These studies met our inclusion criteria and were added to our meta-analysis.
-The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart.
+The exact number of screened and included studies along with reasons of exclusion are shown in @figsupp-prisma-flowchart.
 
@@
 
-merged_data_extraction <- read_csv("data/03_data_cleaning/merged_data_extraction.csv")
+merged_data_extraction <- read_csv("data/03_data_cleaning/merged_data_extraction.csv", show_col_types = F)
 
@@
 included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
+
+# Numbers for extraction ID
+data_extractors <- merged_data_extraction %>%
+     distinct(paper_ID, .keep_all = TRUE) %>%
+     select(paper_ID, extractor_ID) %>%
+     mutate(extractor_ID = case_when(
+    extractor_ID == "JS/SD/TR" ~ "TR/JMGS/SD",
+    TRUE ~ extractor_ID)) %>%
+     group_by(extractor_ID) %>%
+     summarise(total_papers = n(), .groups = "drop")
+
+excluded_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="exclude")
+SAonly_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="senstivity-analysis" | proxy_decision=="sensitivity-analysis")
 ```
-
-### Data collection process
 
@@
 We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
-In cases where primary data was only available in figures (such as boxplots), we used 'metaDigitise' v.1.0.1 (@pick2018).
+In cases where primary data was only available in figures (such as boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
 If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
 In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
+When data was presented in different sources, we prioritized the source having the maximum resolution.
 
 To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
-We obtained one unpublished dataset ...
-\[calculate estimates here\]..
-Another unpublished dataset was provided by a co-author of this paper.
+We contacted 4 authors for missing data, while the rest were asked for any potential unpublished data.
+All four authors responded to our email- 2 provided the data as requested, one did not have the data any more and one did not give a conclusive response.
+One author provided unpublished data.
+Another unpublished data was provided by the author of this study (MO).
 We extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
-
-### Extracted variables
 
@@
 We recorded the type of comparison being made as a moderator.
-Each pairwise comparison was given a unique Observation ID, a paper ID (for each article reporting this data), an experiment ID (for estimates coming from the same experimental setup), a group ID (for estimates from the same group of individual) and a repeated trait ID (for estimates that were measured repeatedly across time).
 
@@
 For a complete list of variables extracted see @figsupp-variables .
+We excluded some traits (n=`{r} nrow(excluded_proxies)` , k=`{r} length(unique(excluded_proxies$paper_ID))`) measured from all our analysis because it was unclear how they related to fitness (see @figsupp-excluded-proxies for the list and reason of exclusion).
+We also had to exclude some fitness proxies (n=?, k=?) because of the low sample size per group (less than x).
 
@@
 
-We calculated two effect sizes for each pairwise comparision-log response ratio (lnRR) and standardised mean difference with heteroscedasticity correction (SMDH), using `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in `metafor` package (@metafor).
+We calculated two effect sizes for each pairwise comparison-log response ratio (lnRR) and standardised mean difference with heteroskedasticity correction (SMDH), using `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in `metafor` package (@metafor).
 We specified treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
 In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the sign was inverted to ensure comparability across all fitness proxies.
-In all cases, the effect size were coded such that the fitness proxies were positively correlated with the overall fitness.
+In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
 
@@
 In cases of dichotomous variables (e.g., successful nests, n=`{r} nrow(contingency_table)`, k=`{r} length(unique(contingency_table$paper_ID))`) we used the data to calculate log odds ratio using `escalc` function (`measure=OR`) and convert it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics or dichotomous variables, only SMD under the assumption of homoskedasticity was derived from such data.
+Since lnRR cannot be calculated from inferential statistics or dichotomous variables, only SMD under the assumption of homoscedasticity was derived from such data.
 We excluded these effect sizes along with any zero or negative values (n=`{r} nrow(negative_lnRR)`, k=`{r} length(unique(negative_lnRR$paper_ID))`) when calculating lnRR.
 
-The sample sizes used was the number of nests in each group, and not the number of individuals, whenever possible.
+The sample sizes used were the number of nests in each group, and not the number of individuals, whenever possible.
 In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
 For the cases where the authors reported no significant difference between the two groups (n=`{r} nrow(no_ES)`, k=`{r} length(unique(no_ES$paper_ID))`) but did not provide the values, we used zero as the effect size.
-To impute the SD for these cases, we used the missing case approach following @nakagawa2022.
+To impute the SD for these cases, we used the missing-case approach following @nakagawa2022.
 
-## Meta-analysis
+## Data Analysis
 
-We used rma.mv function from metafor pacjage using 'REML' method to fit all the models.
-To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical using lnRR or SMDH as dependent variables.
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017].
+We performed analysis in R version 4.3.0 (@positteam2023).
+All multilevel meta-analytical models and meta-regressions were fit using `metafor v.4.8-0` (@metafor).
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using `vcalc` function.
+(See Supplementary Appendix @figsupp-correlation for sensitivity analysis using different values of correlation (ρ)).
 
-*To understand the sources of variation, we calculated Q and total heterogeneity (𝜎2), its source (or relative heterogeneity; I2) and two different metrics to understand its magnitude – a mean-standardized metric (CV) and a variance-mean-standardized metric (M; more in* @yang2025*).*
+Our data had various sources of non-independence which we accounted for using random effects.
+We considered the following level of non-independence- (a) multiple effect sizes were collected from same study (Paper ID), (b) some bird species (species ID) and (c) some geographical locations (population ID) were studied multiple times, (d) some sub-populations (Experiment ID e.g.
+birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID, eg.
+males and females in a population, first clutch and second clutch) were represented in our data several times and (f) repeated traits collected on the same group of animals (repeated trait ID e.g.
+chick mass on day 7, 14 and 21).
 
-*To understand the sources of variation or heterogeneity, for the intercept-only models, we will use the pluralistic approach recently suggested by which consists of calculating four metrics of heterogeneity (σ2, I2, CV, M) to comprehensively understand both total and random-effect specific heterogeneity.
-For the meta-regressions, we will calculate Rmarginal2 to quantify the heterogeneity explained by the moderator(s) in proportion to the total variation (Nakagawa & Schielzeth, 2013).*
+We fitted the following random effects in all our models unless stated otherwise- Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
+Initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
+Experiment ID and group ID were almost indistinguishable, as such we decided to leave out the one with lesser resolution i.e.
+Experiment ID.
+Additionally, we observed that not many effect sizes were measured repeatedly, making the repeated trait ID very similar to the observation ID.
+After exploring the overlap (@figsupp-random-effect), we decided to only keep observation ID.
+We added population ID, which accounts for many effect sizes from different studies coming from the same geographical location.
 
-## Meta-regression for testing hypothesis
+### Meta-analytical models for biological predictions
 
-For understanding the effect of green nest material on reproductive success (courtship hypothesis) and on protective effects and health benefits for the nestling (Parental care hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical models using lnRR or SMDH as dependent variables.
+We used `rma.mv` function from `metafor` package using the 'REML' method.
+Test statistics and confidence intervals for the fixed effects were computed using t distribution.
+We used the entire dataset for this analysis except some traits (n=`{r} nrow(SAonly_proxies)` , k=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies for details) that we decided to exclude from all our analysis due to lack of evidence supporting their relationship with fitness.
+However, we also conducted a sensitivity analysis (@figsupp-MLMA-excluded) including these proxies to ensure robustness of our results.
+In the model using SMDH, We estimated total amount of heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) (@yang2025).
 
-*For meta-regression models, we estimated the percentage of heterogeneity explained by the moderators using R2marginal (Nakagawa & Schielzeth 2013).
-We graphically presented the results as orchard plots using the R package “orchaRd” v.2.0 (Nakagawa et al.
-2023).*
+To test the effect of green nest material on reproductive success (courtship hypothesis) and on protective effects and health benefits for the nestling (Parental care hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+using the entire dataset.
+For this and all meta-regressions, we estimated $R_{marginal}^2$, the percentage of heterogeneity explained by the moderators (@nakagawa2012) using the entire dataset.
 
-## Meta-regression for exploratory analyses
+### Meta-regressions for exploratory analysis
 
-## Publication Bias Test
+We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
+To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (n=?, k=?).
+We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
+We also ran a meta-regression with with the entire dataset set using bird species as a moderator (levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris, Parus major, Passer cinnamomeus, Buteo buteo) to understand if the effect of green nest material on fitness depended on the system being studied.
+To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
+We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We explored the impact of methodological differences on the relationship between green nest material and fitness.
+To understand the effect of type of experimental design (i.e.
+whether the authors compared - non-aromatic vs.
+aromatic, no added material vs.
+aromatic, no added material vs.
+non-aromatic), we ran a meta-regression with type of experimental design as the moderator.
 
-Publication bias was assessed through multilevel meta-regressions maintaining the same random-effects structure as above. Following Nakagawa et al. (2022), we executed the following steps:
+### Publication Bias Test
 
-1.  A uni-moderator meta-regression to detect small-study effects for both lnRR and SMDH, using the square root of the inverse effective sample size as the moderator.
-
-2.  A subsequent uni-moderator meta-regression using the inverse effective sample size to provide a less biased adjusted overall effect.
-
-3.  A time-lag bias analysis using publication year (mean-centered) as the moderator.
-
-4.  A full meta-regression model incorporating small-study effects, time-lag bias, and all other moderators to assess combined heterogeneity sources.
-
-Heterogeneity was further explored using variance decomposition and random-effects modeling, including species and phylogeny if additional effect sizes warranted phylogenetic non-independence correction (Cinar et al., 2022).
-
-## Deviations from registration
-
-**Sensitivity Analyses**
-
-To ensure robustness, we conducted additional sensitivity analyses:
-
-1.  Repeating meta-analyses and meta-regressions using only effect sizes derived from means, SDs, and sample sizes, excluding those based on inferential statistics.
-
-2.  Implementing a bivariate multilevel meta-analytic model (Yang et al., 2024) incorporating both lnRR and SMDH as response variables.
-
-3.  Re-running intercept-only meta-analyses with different sampling variance correlations (ρ = 0.3 and 0.7) and extending these sensitivity analyses to meta-regressions if necessary.
-
-Non-pre-registered sensitivity analyses that emerged during data processing were reported in supplementary materials.
-
-## Stuff that needs to go somewhere
+Publication bias is the higher likelihood of a subset of research findings, such as statistically significant results, being published as compared to the rest.
+We tested for evidence of publication bias (following @nakagawa2021) for both lnRR and SMDH separately.
+To test for small study effects, we ran meta-regression , using the inverse of effective sample size as a moderator.
+To understand the decline effect (also known as time-lag bias) we ran another meta-regression with a mean-centered publication year as a moderator.
 

### 2025-03-27 supplementary_appendix.qmd
First-ish draft of methods

@@
 ---
-title: "Supplementary Appendix"
 bibliography: references.bib
+code-fold: true
 ---
@@
 Prisma Eco-Evo Checklist according to @odea2021
+:::
+
+::: {#figsupp-variables}
+| variable name | description | values | Notes |
+|---------------|-------------|--------|-------|
+|               |             |        |       |
+|               |             |        |       |
+|               |             |        |       |
+
+This is the list of all the variables that were extracted for the purpose of this study
+:::
+
+::: {#figsupp-own-library}
+```{r}
+pacman::p_load(readr,knitr, dplyr)
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv", 
+                        show_col_types = F)
+own_library%>% 
+  select(c(title,author,doi, journal, year, issn))%>% 
+  kable(col.names=(c("Article Title","Authors","DOI", "Journal", "Year of Publication", "ISSN" )),
+        caption = "Articles from our own library used for validating search strategy")
+```
+:::
+
+::: {#figsupp-random-effect}
+```{r}
+pacman::p_load(readr, dplyr, tidyverse)
+install.packages("devtools", repos = "https://cloud.r-project.org/")
+devtools::install_github("davidsjoberg/ggsankey")
+library(ggsankey)
+analysis_dataset <- read_csv("data/03_data_cleaning/dataset_analysis.csv", 
+                        show_col_types = F)
+
+sankey_data <- analysis_dataset %>%
+  select(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)%>%
+  mutate(across(c(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded), as.character)) %>%
+  make_long(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)
+
+ggplot(sankey_data, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
+  geom_alluvial(flow.alpha = .6) +
+  scale_fill_viridis_d(drop = FALSE) +
+  theme_alluvial(base_size = 18) +
+  labs(x = NULL) +
+  theme(legend.position = "none",
+        plot.title = element_text(hjust = .5))
+
+sankey_data_birds <- analysis_dataset %>%
+  select(paper_ID, bird_species, population_ID)%>%
+  mutate(across(c(paper_ID, bird_species, population_ID), as.character)) %>%
+  make_long(paper_ID, bird_species, population_ID)
+
+ggplot(sankey_data_birds, aes(x = x, 
+               next_x = next_x, 
+               node = node, 
+               next_node = next_node,
+               fill = factor(node))) +
+  geom_sankey() +
+  scale_fill_discrete(drop=FALSE) +
+  theme(legend.position = "none")
+
+```
 :::
@@
 :::
+
+::: {#figsupp-decision-tree}
+![](images/Decision_Tree_updated.png)
+:::
+
+::: {#figsupp-prisma-flowchart}
+This is the prisma flowchart
+:::
+
+::: {#figsupp-correlation}
+Table for different values of correlation
+:::
+
+::: {#figsupp-MLMA-excluded}
+Model output and plot including proxies that were excluded
+:::

### 2025-04-22 docs/supplementary_appendix.qmd
Results: Intercept only model - overall effect

@@
 bibliography: references.bib
+code-fold: true
 ---
@@
 This is the list of all the variables that were extracted for the purpose of this study
+:::
+
+::: {#figsupp-own-library}
+```{r}
+pacman::p_load(readr,knitr, dplyr)
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv", 
+                        show_col_types = F)
+own_library%>% 
+  select(c(title,author,doi, journal, year, issn))%>% 
+  kable(col.names=(c("Article Title","Authors","DOI", "Journal", "Year of Publication", "ISSN" )),
+        caption = "Articles from our own library used for validating search strategy")
+```
+:::
+
+::: {#figsupp-random-effect}
+```{r}
+# pacman::p_load(readr, dplyr, tidyverse)
+# install.packages("devtools", repos = "https://cloud.r-project.org/")
+# devtools::install_github("davidsjoberg/ggsankey")
+# library(ggsankey)
+# analysis_dataset <- read_csv("data/03_data_cleaning/dataset_analysis.csv", 
+#                         show_col_types = F)
+# 
+# sankey_data <- analysis_dataset %>%
+#   select(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)%>%
+#   mutate(across(c(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded), as.character)) %>%
+#   make_long(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)
+# 
+# ggplot(sankey_data, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
+#   geom_alluvial(flow.alpha = .6) +
+#   scale_fill_viridis_d(drop = FALSE) +
+#   theme_alluvial(base_size = 18) +
+#   labs(x = NULL) +
+#   theme(legend.position = "none",
+#         plot.title = element_text(hjust = .5))
+# 
+# sankey_data_birds <- analysis_dataset %>%
+#   select(paper_ID, bird_species, population_ID)%>%
+#   mutate(across(c(paper_ID, bird_species, population_ID), as.character)) %>%
+#   make_long(paper_ID, bird_species, population_ID)
+# 
+# 
+# ggplot(sankey_data_birds, aes(x = x, 
+#                next_x = next_x, 
+#                node = node, 
+#                next_node = next_node,
+#                fill = factor(node))) +
+#   geom_sankey() +
+#   scale_fill_discrete(drop=FALSE) +
+#   theme(legend.position = "none")
+
+```
 :::
@@
 :::
+
+::: {#figsupp-correlation}
+Table for different values of correlation
+:::
+
+::: {#figsupp-MLMA-excluded}
+Model output and plot including proxies that were excluded
+:::

### 2025-04-22 manuscript_GNM.qmd
Results: Intercept only model - overall effect

--- 2025-02-27 manuscript_GNM.qmd
@@
 ```{r Setup, include=FALSE, echo=FALSE}
-
-pacman::p_load(readr)
+devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
+pacman::p_load(readr,tidyverse,metafor,orchaRd)
 
@@
 
-# Methods (\~2200 words)
+```{r load search data, include=FALSE, echo=FALSE, message= FALSE}
 
-## Registration and Reporting
+# Own reference list
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv")
 
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
-Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
-All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
-
-## Study selection and eligibility criteria
-
-```{r load search data, include=FALSE, echo=FALSE}
-
+# Systematic search and abstract screening
 unique_reference_list <- read_csv("data/unique_reference_list.csv")
@@
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
-The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string).
-We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
+# Methods
+
+## Registration and Reporting
+
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details the study's objectives, a priori hypotheses and predictions, methods and planned data analyses.
+Unless stated otherwise, we adhered to the registered protocol.
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
+
+## Information source and search
+
+We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022.
+The keyword search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for a complete search string tailored to specific database see @figsupp-string).
+We searched the title, abstract and keywords in English-language only, with no restrictions on publication date or study type.
 We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
-We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved.
+We validated our search using an initial library of `{r} nrow(own_library)` relevant articles (@figsupp-own-library), ensuring all were retrieved.
 Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 
-All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
+## Eligibility criteria
+
+All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in `revtools`.
 We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
@@
 We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
-`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
+`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decisions (\~1% disagreement for title and abstract screening and none for fulltext screening) were resolved through discussion.
 
 We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
-After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
+After de-duplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
 We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
@@
 
-### Data collection process
+```{r load data extraction, include=FALSE, echo=FALSE}
+
+merged_data_extraction <- read_csv("data/03_data_cleaning/merged_data_extraction.csv", show_col_types = F)
+
+dataset_after_cleaning <- merged_data_extraction %>% filter(fulltext_screening!="excluded")
+included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
+
+# Numbers for extraction ID
+data_extractors <- merged_data_extraction %>%
+     distinct(paper_ID, .keep_all = TRUE) %>%
+     select(paper_ID, extractor_ID) %>%
+     mutate(extractor_ID = case_when(
+    extractor_ID == "JS/SD/TR" ~ "TR/JMGS/SD",
+    TRUE ~ extractor_ID)) %>%
+     group_by(extractor_ID) %>%
+     summarise(total_papers = n(), .groups = "drop")
+
+excluded_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="exclude")
+SAonly_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="senstivity-analysis" | proxy_decision=="sensitivity-analysis")
+```
 
@@
 We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
-In cases where primary data was only available in figures (such as boxplots), we used 'metaDigitise' v.1.0.1 (@pick2018).
+In cases where primary data was only available in figures (such as boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
 If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
 In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
+When data was presented in different sources, we prioritized the source having the maximum resolution.
 
 To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
-We obtained one unpublished dataset ...
-\[calculate estimates here\]..
-Another unpublished dataset was provided by a co-author of this paper.
-We extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
-
-<!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
-
-### Extracted variables
+We contacted 4 authors for missing data, while the rest were asked for any potential unpublished data.
+All four authors responded to our email- 2 provided the data as requested, one did not have the data any more and one did not give a conclusive response.
+One author provided unpublished data.
+Another unpublished data was provided by the author of this study (MO).
+We extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
 
@@
 We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
-In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied ino arthropods or micro-organisms.
+In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied into arthropods or micro-organisms.
 For a complete list of variables extracted see @figsupp-variables .
+We excluded some traits (k=`{r} nrow(excluded_proxies)` , n=`{r} length(unique(excluded_proxies$paper_ID))`) measured from all our analysis because it was unclear how they related to fitness (see @figsupp-excluded-proxies for the list and reason of exclusion).
+We also had to exclude some fitness proxies (n=?, k=?) because of the low sample size per group (less than x).
 
@@
 
-Using the information we extracted from the articles, we calculated two effect sizes,along with their associated sampling variance, for each pairwise comparison-log response ratio (hereafter lnRR) and standardised mean difference with heteroscedasticity correction (hereafter SMDH).
+```{r load effect size, include=FALSE, echo=FALSE}
 
--   How many papers in final meta-analysis and how many effect size.
+inferential_stats<-dataset_after_cleaning%>%filter(statistics_type=="t-test"|statistics_type=="ANCOVA")
 
-### Meta-analysis and meta-regressions
+contingency_table<-dataset_after_cleaning%>%filter(proxy_decision=="contingency table")
 
--   main effect model
+no_ES<-dataset_after_cleaning%>%filter(proxy_comment == "use 0 as ES")
 
--   meta-regressions for testing hypothesis
+negative_lnRR<-dataset_after_cleaning%>%
+  filter(measure_central_tendency_experiment<=0 | measure_central_tendency_control<=0)
 
--   meta-regressions for exploratory analyses
+```
 
-Senstivity analysis and Publication Bias Test
+We calculated two effect sizes for each pairwise comparison-log response ratio (lnRR) and standardised mean difference with heteroskedasticity correction (SMDH), using `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in `metafor` package (@metafor).
+We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the sign was inverted to ensure comparability across all fitness proxies.
+In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
 
-### Deviations from registration
+For studies reporting only inferential statistics (e.g., t-tests, ANCOVA), we estimated SMD values (k=`{r} nrow(inferential_stats)`, n=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019 .
+In cases of dichotomous variables (e.g., successful nests, k=`{r} nrow(contingency_table)`, n=`{r} length(unique(contingency_table$paper_ID))`) we used the data to calculate log odds ratio using `escalc` function (`measure=OR`) and convert it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics or dichotomous variables, only SMD under the assumption of homoscedasticity was derived from such data.
+We excluded these effect sizes along with any zero or negative values (k=`{r} nrow(negative_lnRR)`, n=`{r} length(unique(negative_lnRR$paper_ID))`) when calculating lnRR.
+
+The sample sizes used were the number of nests in each group, and not the number of individuals, whenever possible.
+In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
+For the cases where the authors reported no significant difference between the two groups (n=`{r} nrow(no_ES)`, k=`{r} length(unique(no_ES$paper_ID))`) but did not provide the values, we used zero as the effect size.
+To impute the SD for these cases, we used the missing-case approach following @nakagawa2022.
+
+## Data Analysis
+
+We performed analysis in R version 4.3.0 (@positteam2023).
+All multilevel meta-analytical models and meta-regressions were fit using `metafor v.4.8-0` (@metafor).
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using `vcalc` function.
+(See Supplementary Appendix @figsupp-correlation for sensitivity analysis using different values of correlation (ρ)).
+
+Our data had various sources of non-independence which we accounted for using random effects.
+We considered the following level of non-independence- (a) multiple effect sizes were collected from same study (Paper ID), (b) some bird species (species ID) and (c) some geographical locations (population ID) were studied multiple times, (d) some sub-populations (Experiment ID e.g.
+birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID, eg.
+males and females in a population, first clutch and second clutch) were represented in our data several times and (f) repeated traits collected on the same group of animals (repeated trait ID e.g.
+chick mass on day 7, 14 and 21).
+
+We fitted the following random effects in all our models unless stated otherwise- Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
+Initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
+Experiment ID and group ID were almost indistinguishable, as such we decided to leave out the one with lesser resolution i.e.
+Experiment ID.
+Additionally, we observed that not many effect sizes were measured repeatedly, making the repeated trait ID very similar to the observation ID.
+After exploring the overlap (@figsupp-random-effect), we decided to only keep observation ID.
+We added population ID, which accounts for many effect sizes from different studies coming from the same geographical location.
+
+### Meta-analytical models for biological predictions
+
+To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical models using lnRR or SMDH as dependent variables.
+We used the `rma.mv` function from the `metafor` package using the 'REML' method.
+Test statistics and confidence intervals for the fixed effects were computed using t distribution.
+We used the entire dataset for this analysis except some traits (k=`{r} nrow(SAonly_proxies)` , n=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies for details) that we decided to exclude from all our analysis due to lack of evidence supporting their relationship with fitness.
+However, we also conducted a sensitivity analysis (@figsupp-MLMA-excluded) including these proxies to ensure robustness of our results.
+In the model using SMDH, We estimated total amount of heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) (@yang2025).
+
+To test the effect of green nest material on reproductive success (courtship hypothesis) and on protective effects and health benefits for the nestling (Parental care hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+using the entire dataset.
+For this and all meta-regressions, we estimated $R_{marginal}^2$, the percentage of heterogeneity explained by the moderators (@nakagawa2012) using the entire dataset.
+
+### Meta-regressions for exploratory analysis
+
+We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
+To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (n=?, k=?).
+We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
+We also ran a meta-regression with with the entire dataset set using bird species as a moderator (levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris, Parus major, Passer cinnamomeus, Buteo buteo) to understand if the effect of green nest material on fitness depended on the system being studied.
+To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
+We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We explored the impact of methodological differences on the relationship between green nest material and fitness.
+To understand the effect of type of experimental design (i.e.
+whether the authors compared - non-aromatic vs.
+aromatic, no added material vs.
+aromatic, no added material vs.
+non-aromatic), we ran a meta-regression with type of experimental design as the moderator.
+
+### Publication Bias Test
+
+Publication bias is the higher likelihood of a subset of research findings, such as statistically significant results, being published as compared to the rest.
+We tested for evidence of publication bias (following @nakagawa2021) for both lnRR and SMDH separately.
+To test for small study effects, we ran meta-regression , using the inverse of effective sample size as a moderator.
+To understand the decline effect (also known as time-lag bias) we ran another meta-regression with a mean-centered publication year as a moderator.
+
+# Results
+
+```{r}
+dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")
+
+ES_per_study<-dataset_analysis%>%group_by(paper_ID)%>%count(paper_ID)
+
+birds_info<-dataset_analysis%>%group_by(bird_species)%>%count(bird_species)
+birds_info$perc<-(birds_info$n/nrow(dataset_analysis))*100
+```
+
+We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies, published between `{r} min((dataset_analysis$year_publication),na.rm = T)`-`{r} max((dataset_analysis$year_publication),na.rm = T)`.
+The mean (±SD) number of effect sizes per study was `{r} as.numeric(format(mean(ES_per_study$n), digit=3))` ± `{r} as.numeric(format(sd(ES_per_study$n), digit=3))`, with a range of `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)` effect sizes per study.
+Median and mean sample sizes per effect size were `{r} median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))` and `{r} as.numeric(format(mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)), digit=3))` respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`-- `{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size less than 2 in each group).
+The studies were conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` locations.
+About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes come from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
+
+**Does addition of green nest material have an adaptive function?**
+
+```{r}
+intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
+intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
+```
+
+The intercept only meta-analytic model using the log response ratio (lnRR) estimated a `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% increase in fitness in nests with green nest material across bird species \[Figure ; lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))`, `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))`, `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 2, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\].
+The total heterogeneity (𝜎2) was estimated at `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),3)`, p \< 0.001).
+Measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity (mean-standardized: CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_lnRR)[1]),2)` and variance-mean-standardized: M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
+Using standardized mean difference (SMDH) as an alternate effect size, the intercept only meta-analytic model estimated a small positive but statistically significant effect of green nest material on fitness \[Figure ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))`, `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))`, `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\].
+Total heterogeneity was higher in case of SMDH (𝜎^2^= `{r} round(sum(intercept_SMDH$sigma2), 3)` Q = `{r} round(sum(intercept_SMDH$QE),3)`, p \< 0.001).
+and the relative heterogeneity was substantially reduced (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%).
+The standardized heterogeneity (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) remained high.
+While lnRR and SMDH differ in their scale, both effect sizes suggest a small but positive effect of green nest material on fitness.
+These differences in overall effect can stem from the different underlying biological and statistical assumptions.
+lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (see @yang2024 for more details).
+
+```{r}
+orchaRd::caterpillars(intercept_lnRR, mod = "1", group="paper_ID",xlab = "Effect size (Log Response Ratio - lnRR)")
+
+orchaRd::caterpillars(intercept_SMDH, mod = "1", group="paper_ID",xlab = "Effect size (Standardized Mean Difference - SMDH)")
+
+intercept_lnRR_plot <- orchard_plot(intercept_lnRR,
+                                         mod = "1",
+                                         group = "paper_ID",
+                                         trunk.size = 1,
+                                         branch.size = 2,
+                                         alpha = 0.3,
+                                         twig.size = 1,
+                                         xlab = "Effect size (Log Response Ratio - lnRR)",
+                                         colour = "#218833",
+                                         fill = T) +
+  scale_fill_manual(values = "#218833") +
+  scale_colour_manual(values = "#218833") +  
+  theme(legend.direction="horizontal", legend.title = element_text(size =8),
+        legend.text = element_text(size = 10), 
+        axis.title = element_text(size = 15),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_blank()) +
+  labs(x = "Intercept")
+
+print(intercept_lnRR_plot)
+
+intercept_SMDH_plot <- orchard_plot(intercept_SMDH,
+                                         mod = "1",
+                                         group = "paper_ID",
+                                         trunk.size = 1,
+                                         branch.size = 2,
+                                         alpha = 0.3,
+                                         twig.size = 1,
+                                         xlab = "Effect size (Standardized Mean Difference - SMDH)",
+                                         colour = "#895129",
+                                         fill = T) +
+  scale_fill_manual(values = "#895129") +
+  scale_colour_manual(values = "#895129") +  
+  theme(legend.direction="horizontal", legend.title = element_text(size =8),
+        legend.text = element_text(size = 10), 
+        axis.title = element_text(size = 15),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_blank()) +
+  labs(x = "Intercept")
+
+print(intercept_SMDH_plot)
+```
+
+\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--
 

### 2025-04-22 notebook/data_analysis.qmd
Results: Intercept only model - overall effect

---
title: "Green Nest Material Meta-Analysis"
subtitle: "The adaptive value of green nest material across birds: A systematic review and meta-analysis"
author: "Shreya Dimri"
date: last-modified

format:
  html:
   toc: true 
   toc-title: "Table of Contents" 
   toc-depth: 2 
   toc-expand: 3 
   toc-location: left 
   mainfont: Verdana 
   monofont: Jetbrains Mono 
   fontsize: 12pt 
   code-fold: show
   df-print: paged 
   highlight-style: github 
   pdf: default
editor: visual
---

```{r setup, warning=FALSE, message=FALSE, echo=F}

# Setting up workspace

# For plotting trees, and although not strictly necessary, we may need the `ggtree` R package, which you should be able to install by running:
# if (!require("BiocManager", quietly = TRUE))
# install.packages("BiocManager")
# BiocManager::install("ggtree")

#devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
pacman::p_load(here, tidyverse, metafor,ggpubr,orchaRd,ggpubfigs) #Packages needed
rm(list=ls()) ## cleaning up
set.seed(430) #set seed for reproducibility (for random number generation)
# Loading cleaned dataset
dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))

# Functions needed

# function to estimate typical sampling error variance obtained from 
# https://github.com/Yefeng0920/heterogeneity_ecoevo/tree/main/function
sigma2_v <- function(mod){
  sigma2_v <- sum(1 / mod$vi) * (mod$k - 1) /
    (sum(1 / mod$vi)^2 - sum((1 / mod$vi)^2))
  return(sigma2_v)
}
```

### Creating Phylogeny for the plot

```{r}
# install.packages("pacman")
# load packages
pacman::p_load(rotl,
               ape,
               ggtree)
# Doesn't matter if I take dataset_lnRR or dataset_SMDH
bird_species <- unique(dataset_analysis$bird_species)

# extracting taxonomic information
taxa <- rotl::tnrs_match_names(names = bird_species)
taxa
# check approximate matches
taxa[taxa$approximate_match==TRUE & !(is.na(taxa$approximate_match)),]
# phylogenetic information for our species from the Open Tree of Life
tree <- rotl::tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")
ape::is.binary(tree)
# here are the species included in the tree
sort(tree$tip.label)

# removing the underscore "_" from the tree tip.label
tree$tip.label <- gsub("_"," ", tree$tip.label)
sort(tree$tip.label)

# compute branch lengths of tree
phylo_branch <- compute.brlen(tree, method = "Grafen", power = 1)

# check tree is ultrametric
is.ultrametric(phylo_branch) # TRUE

# matrix to be included in the models
bird_phylo <- vcv(phylo_branch, cor = T)
bird_phylo

plot(tree) #check: https://www.rdocumentation.org/packages/ape/versions/5.3/topics/plot.phylo
```

### Visualizing random effects structure

```{r}
# install.packages("devtools")
#devtools::install_github("davidsjoberg/ggsankey")
library(ggsankey)

sankey_data <- dataset_analysis %>%
  select(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded)%>%
  mutate(across(c(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded), as.character)) %>%
  make_long(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded)

sankey_data <- dataset_analysis %>%
  select(paper_ID, bird_species, population_ID)%>%
  mutate(across(c(paper_ID, bird_species, population_ID), as.character)) %>%
  make_long(paper_ID, bird_species, population_ID)

ggplot(sankey_data, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node))) +
  geom_sankey() +
  scale_fill_discrete(drop=FALSE) +
  theme(legend.position = "none")

ggplot(sankey_data, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
  geom_alluvial(flow.alpha = .6) +
  scale_fill_viridis_d(drop = FALSE) +
  theme_alluvial(base_size = 18) +
  labs(x = NULL) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5))

```

# lnRR Multilevel meta-analysis

```{r}
# selecting dataset which are not flagged
dataset_lnRR<-dataset_analysis%>%
   filter(lnRR_sign != "NA" | lnRR_variance != "NA")%>%
  filter(proxy_decision == "include")

# selecting dataset which are flagged
lnRR_con_flagged<-dataset_analysis%>%
   filter(lnRR_sign != "NA" | lnRR_variance != "NA")%>%
  filter(proxy_decision != "SMDH only" | proxy_decision != "contingency table" )

# selecting dataset without those using 0 as ES because authors reported no effect

lnRR_sin_missingES <- dataset_lnRR %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))

lnRR_flagged_no_missingES<- lnRR_con_flagged %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))

```

## Intercept only models

*"Does adding green material to the nest have an adaptive function across the bird species that perform this behaviour?"*

```{r}

VCV_lnRR<- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

```

The MLMA using lnRR as the effect size measure incorporate the imputed sampling variance-covariance:

```{r intercept-only-model-lnRR}

intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR)

# saving the model
 saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))

summary(intercept_lnRR)
predict(intercept_lnRR)

```

Now looking at the intercept only model

```{r}

# Then also:
# # Typical sampling variance (which captures the statistical noise of the data, 
# # but is rarely reported in the current meta-analytic practice):
sigma2_v(intercept_lnRR)

# To calculate heterogeneity, these are the functions from orchaRd:
# # I2, CV and M
sigma2_main_model_vector <- sum(intercept_lnRR$sigma2)
I2_main_model_vector <- orchaRd::i2_ml(intercept_lnRR)
CV_main_model_vector <- orchaRd::cvh1_ml(intercept_lnRR)
M_main_model_vector <- orchaRd::m2_ml(intercept_lnRR)

# # # Total unstandardized raw variance (i.e. total heterogeneity)
round(sum(intercept_lnRR$sigma2), 3)

```

### Senstivity Analysis with flagged proxies

```{r}

# Preparing new variance-covariance matrix

VCV_lnRR_flagged <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = lnRR_con_flagged,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_lnRR_VCV_flagged<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_flagged, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = lnRR_con_flagged)

# What is the effect now?

summary(MLMA_lnRR_VCV_flagged)
predict(MLMA_lnRR_VCV_flagged)

```

### Sensitivity Analysis without 0 ES

```{r}

# Preparing new variance-covariance matrix

VCV_lnRR_no_missingES <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = lnRR_sin_missingES,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_lnRR_VCV_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_no_missingES, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = lnRR_sin_missingES)

# What is the effect now?

summary(MLMA_lnRR_VCV_no_missingES)
predict(MLMA_lnRR_VCV_no_missingES)

```

### Sensitivity Analysis with flagged proxies and no missing ES

```{r}

# Preparing new variance-covariance matrix

VCV_flagged_no_missingES <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = lnRR_flagged_no_missingES,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_lnRR_flagged_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = lnRR_flagged_no_missingES)

# What is the effect now?

summary(MLMA_lnRR_flagged_no_missingES)
predict(MLMA_lnRR_flagged_no_missingES)
```

[**Robust variance estimation to guard against arbitary value of sampling correlation**]{.underline} - 'robust()' function from R package 'metafor' (Viechtbauer 2010) using 'CR2' (bias reduced linearization correction) from the R package 'clubSandwich' (Pustejovsky 2024) for small-sample size adjustment.

At the moment, this is not working..

```{r}
#MLMA_lnRR_RVE<- robust(MLMA_lnRR_VCV,
#                        cluster = paper_ID,
#                        clubSandwich = TRUE,
#                        verbose=T)

# # summary(MLMA_lnRR_RVE)
# I2_CI <- i2_ml(MLMA_lnRR_RVE) # Relative heterogeneity
# round(I2_CI,2) # absolute heterogeneity is reported in the summary of the model
```

::: callout-important
Sensitivity Analysis

We will also perform a sensitivity analysis using 0.3 and 0.7 correlation between the sampling variances from the same paper_ID and report it in the supplementary materials. If this sensitivity analysis shows large differences in conclusions for the intercept-only model, we will proceed to perform such sensitivity analysis for the meta-regressions.
:::

First, set a series of ρs (i.e., 0.3, 0.5, 0.7) (we assume these values arbitrarily):

```{r lnRR rho sensitivity analysis}
# rho_range <- c(0.3, 0.5, 0.7)
# 
# MLMAlnRR_VCV_range <- list() # repeatedly run the specified model with varying rho
# for (i in 1:length(rho_range))
# {VCV_range <- vcalc(vi = lnRR_variance,
#                   cluster = paper_ID,
#                   subgroup = group_ID,
#                   obs = Observation_ID,
#                   data = dataset_lnRR,
#                    rho = rho_range[i],
#                     ) # impute sampling variance covariance matrix with varying rho
# 
# MLMAlnRR_VCV_range[[i]] <- rma.mv(yi = lnRR_sign,
#                                   V = VCV_range, # sampling variance covariance matrix with varying values of rho.
#                                  random = list(~ 1 | paper_ID,
#                                   ~ 1 | Observation_ID,
#                                   ~ 1 | experiment_ID,
#                                   ~ 1 | group_ID,
#                                   ~ 1 | repeated_trait_ID),
#                                   method = "REML",
#                                   data = dataset_lnRR # run the model with varying rho
# )
# }
# 
# save(VCV_range, file = here::here("GNM/figures/VCV_range.Rdata"))
# save(MLMAlnRR_VCV_range, file = here::here("GNM/figures/MLMAlnRR_VCV_range.Rdata"))

```

```{r Table for lnRR rho sensitivity analysis}

# t4 <- data.frame(rho  = rho_range,
#                  "overall effect"  = sapply(MLMAlnRR_VCV_range, function(x) coef(x)),
#                  "standard error" = sapply(MLMAlnRR_VCV_range, function(x) x$se),
#                  "p-value" = sapply(MLMAlnRR_VCV_range, function(x) x$pval),
#                  "Lower CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.lb),
#                  "Upper CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.ub),
#                  "Log-likehood" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[1,1]),
#                  "AIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[3,1]),
#                  "BIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[4,1]),
#                  "AICc" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[5,1]))
# 
# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
# 
# t4 %>% dfround(4) %>% DT::datatable()
```

### Plot

```{r caterpillar plot lnRR}

orchaRd::caterpillars(intercept_lnRR, mod = "1", group="paper_ID",xlab = "Effect size (Log response ratio - lnRR)")
```

```{r intercept only plot}

lnRR_intercept_only_plot <- orchard_plot(intercept_lnRR,
                                         mod = "1",
                                         group = "paper_ID",
                                         trunk.size = 1,
                                         branch.size = 2,
                                         alpha = 0.3,
                                         twig.size = 1,
                                         xlab = "Effect size (Log response ratio - lnRR)",
                                         colour = "#218833",
                                         fill = T) +
  scale_fill_manual(values = "black") +
  scale_colour_manual(values = "#218833") +  
  theme(legend.direction="horizontal", legend.title = element_text(size =8),
        legend.text = element_text(size = 10), 
        axis.title = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_blank()) +
  labs(x = "Intercept")

print(lnRR_intercept_only_plot)
```

```{# intercept_only_plot<- ggarrange(MLMA_lnRR_intercept_only_plot,}
#                                       MLMA_lnRR_VCV_intercept_only_plot,
#                                       ncol = 2,  nrow = 1)

# intercept_only_plot
# ggsave("intercept_only_plot.pdf", plot = intercept_only_plot, height = 250, width = 500, units = "mm", dpi = 600)

```

## Uni-moderator multilevel meta-regressions

#### Hypothesis

To address our secondary questions "Does the addition of green nest material by birds increase their reproductive success? (Courtship hypothesis)" and "Does the addition of green nest material have protective effects and health benefits for the nestlings? (Parental care hypothesis)", we will make use of the unimoderator multilevel meta-regressions hypothesis type (levels: CH, PCH, Both) as the moderator.

```{r}
MR_lnRR_hypothesis <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance;
                    mods = ~ - 1 + Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# save(MR_lnRR_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
```

```{r Plot lnRR meta-regression on hypothesis}

 MR_lnRR_hypothesis_plot <-
  orchard_plot(
    mod_results(
       MR_lnRR_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID",
      data = dataset_lnRR
    ), xlab ="") +
  scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "lnRR")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Different Hypothesis")

  MR_lnRR_hypothesis_plot
```

#### Exploratory Analysis

For our exploratory analyses (see section Exploratory Analyses), we will run unimoderator multilevel meta-regressions using the following moderators:

#### Type of parasites

(levels: arthropods, micro-organisms)

```{r Types of parasite}
# This analysis only includes dataset that has a proxy relating to parasite or pathogen
dataset_lnRR_parasite <- dataset_lnRR%>%
  filter(trait_type == "Parasitic_and_pathogenic")
VCV_lnRR_parasite <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_parasite,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

 MR_lnRR_parasite <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_parasite,# specify lnRR's sampling variance;
                    mods = ~ - 1 + parasite_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                   test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_parasite)

 # Warning: 4 rows with NAs omitted from model fitting.
 # Check what rows are these..

 # save( MR_lnRR_parasite, file = here::here("GNM/figures/ MR_lnRR_parasite.Rdata"))
```

```{r}
 MR_lnRR_parasite_plot <-
  orchard_plot(
    mod_results(
        MR_lnRR_parasite,
      mod = "parasite_type",
      group = "paper_ID",
      data = dataset_lnRR_parasite
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "lnRR")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Parasite_type")

   MR_lnRR_parasite_plot
```

2\. Time of addition of green nest material (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).

#### Type of experimental design

(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).

```{r}
# This analysis only includes dataset that has a proxy relating to comaparision type
dataset_lnRR_design <- dataset_lnRR %>%
  filter(!is.na(comparision_type))%>%
  mutate(comparision_type= as.factor(comparision_type))

VCV_lnRR_design <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_design,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
MR_lnRR_design <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_design ,# specify lnRR's sampling variance;
                    mods = ~ comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_design )

# save(MR_lnRR_design, file = here::here("GNM/figures/MR_lnRR_trait.Rdata"))
```

```{r}

MR_lnRR_design_plot <-
  orchard_plot(
    mod_results(
        MR_lnRR_design,
      mod = "comparision_type",
      group = "paper_ID",
      data = dataset_lnRR_design
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "lnRR")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Experimental Design")

   MR_lnRR_design_plot

```

#### Bird species

(levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)

```{r}
MR_lnRR_birds <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR,# specify lnRR's sampling variance;
                    mods = ~ - 1 + bird_species,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# save(MR_lnRR_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
```

```{r Plot lnRR meta-regression on birds}

MR_lnRR_birds_plot <-
  orchard_plot(
    mod_results(
       MR_lnRR_birds,
      mod = "bird_species",
      group = "paper_ID",
      data = dataset_lnRR
    ), xlab ="") +
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
  labs(x = "",
       y = "lnRR")+
  theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
  ggtitle("Bird Species")

 MR_lnRR_birds_plot
```

#### Type of trait studied

(levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology)

```{r}
MR_lnRR_trait <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = lnRR_variance,# specify lnRR's sampling variance;
                    mods = ~ - 1 + trait_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR)

# save(MR_lnRR_trait, file = here::here("GNM/figures/MR_lnRR_trait.Rdata"))
```

```{r}
MR_lnRR_trait_plot <-
  orchard_plot(
    mod_results(
        MR_lnRR_trait,
      mod = "trait_type",
      group = "paper_ID",
      data = dataset_lnRR
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
  labs(x = "",
       y = "lnRR")+
   theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
  ggtitle("Type of trait studied")

   MR_lnRR_trait_plot
```

# SMDH Multilevel meta-analysis

```{r}
# selecting dataset which are not flagged
dataset_SMDH<-dataset_analysis%>%
   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")

# selecting dataset which are flagged
SMDH_con_flagged<-dataset_analysis%>%
   filter(SMDH_sign != "NA")

# selecting dataset without those using 0 as ES because authors reported no effect

SMDH_sin_missingES <- dataset_SMDH %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))

SMDH_flagged_no_missingES<- SMDH_con_flagged %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))
```

### Intercept only model

We are only running these analysis for the fitness proxy labelled "included". Some proxies have been flagged and we will run them in a sensitivity analysis only.

their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).

their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).

```{r}

VCV_SMDH <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

```

The MLMA using SMDH as the effect size measure incorporate the imputed sampling variance

```{r}

intercept_SMDH<- rma.mv(yi = SMDH_sign, # specify SMDH as the effect size measure;
                    V = VCV_SMDH, # specify SMDH's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_SMDH)

# saving the model
# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))

```

Now looking at the intercept only model

```{r}
summary(intercept_SMDH)
predict(intercept_SMDH)

# Then also:
# # Typical sampling variance (which captures the statistical noise of the data, 
# # but is rarely reported in the current meta-analytic practice):
sigma2_v(intercept_SMDH)

# To calculate heterogeneity, these are the functions from orchaRd:
# # I2, CV and M
sigma2_main_model_vector <- sum(intercept_SMDH$sigma2)
I2_main_model_vector <- orchaRd::i2_ml(intercept_SMDH)
CV_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
M_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)

# # # Total unstandardized raw variance (i.e. total heterogeneity)
round(sum(intercept_SMDH$sigma2), 3)

```

### Senstivity Analysis with flagged proxies

```{r}

# Preparing new variance-covariance matrix

VCV_SMDH_flagged <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = SMDH_con_flagged,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_SMDH_VCV_flagged<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_flagged, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = SMDH_con_flagged)

# What is the effect now?

summary(MLMA_SMDH_VCV_flagged)
predict(MLMA_SMDH_VCV_flagged)

```

### Sensitivity Analysis without 0 ES

```{r}

# Preparing new variance-covariance matrix

VCV_SMDH_no_missingES <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = SMDH_sin_missingES,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_SMDH_VCV_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_no_missingES, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = SMDH_sin_missingES)

# What is the effect now?

summary(MLMA_SMDH_VCV_no_missingES)
predict(MLMA_SMDH_VCV_no_missingES)

```

### Sensitivity Analysis with flagged proxies and no missing ES

```{r}

# Preparing new variance-covariance matrix

VCV_SMDH_flagged_no_missingES <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = SMDH_flagged_no_missingES,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

## Running intercept only model

MLMA_SMDH_flagged_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = SMDH_flagged_no_missingES)

# What is the effect now?

summary(MLMA_SMDH_flagged_no_missingES)
predict(MLMA_SMDH_flagged_no_missingES)
```

[**Robust variance estimation to guard against arbitary value of sampling correlation**]{.underline} - 'robust()' function from R package 'metafor' (Viechtbauer 2010) using 'CR2' (bias reduced linearization correction) from the R package 'clubSandwich' (Pustejovsky 2024) for small-sample size adjustment.

At the moment, this is not working..

```{r}
# MLMA_SMDH_RVE<- robust(MLMA_SMDH_VCV,
#                        cluster = paper_ID,
#                        clubSandwich = TRUE)

# summary(MLMA_SMDH_RVE)
# I2_CI <- i2_ml(MLMA_SMDH_RVE) # Relative heterogeneity
# round(I2_CI,2) # absolute heterogeneity is reported in the summary of the model
```

### Plot

```{r}
# MLMA_SMDH

MLMA_SMDH_intercept_only_plot <-
  orchard_plot(
    mod_results(
      intercept_SMDH,
      mod = "1",
      group = "paper_ID",
      data = dataset_lnRR
    ),
    xlab = "Effect Size SMDH") +
  scale_fill_manual(values="darkgreen") +
  scale_colour_manual(values="darkgreen")+
  theme(legend.direction="horizontal", legend.title = element_text(size =8),
        legend.text = element_text(size = 10), 
        axis.title = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_blank()) +
  labs(
    x = "",
    y = "SMDH"
  )+
  ggtitle("Main effect of GNM on fitness using VCV Matrix")

MLMA_SMDH_intercept_only_plot

```

## Unimoderator multilevel meta-regressions

#### Hypothesis

To address our secondary questions "Does the addition of green nest material by birds increase their reproductive success? (Courtship hypothesis)" and "Does the addition of green nest material have protective effects and health benefits for the nestlings? (Parental care hypothesis)", we will make use of the unimoderator multilevel meta-regressions hypothesis type (levels: CH, PCH, Both) as the moderator.

```{r}
MR_SMDH_hypothesis <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance;
                    mods = ~ - 1 + Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# save(MR_SMDH_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
```

```{r Plot meta-regression on hypothesis SMDH}

 MR_SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
       MR_SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID",
      data = dataset_SMDH
    ), xlab ="") +
  scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "SMDH")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Different Hypothesis")

  MR_SMDH_hypothesis_plot
```

#### Exploratory Analysis

For our exploratory analyses (see section Exploratory Analyses), we will run unimoderator multilevel meta-regressions using the following moderators:

#### Type of parasites

(levels: arthropods, micro-organisms)

```{r Types of parasite SMDH}
# This analysis only includes dataset that has a proxy relating to parasite or pathogen
dataset_SMDH_parasite <- dataset_SMDH%>%
  filter(trait_type == "Parasitic_and_pathogenic")
VCV_SMDH_parasite <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_parasite,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

 MR_SMDH_parasite <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
                    mods = ~ - 1 + parasite_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                   test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_parasite)

 # Warning: 4 rows with NAs omitted from model fitting.
 # Check what rows are these..

 # save( MR_lnRR_parasite, file = here::here("GNM/figures/ MR_lnRR_parasite.Rdata"))
```

```{r}
 MR_SMDH_parasite_plot <-
  orchard_plot(
    mod_results(
        MR_SMDH_parasite,
      mod = "parasite_type",
      group = "paper_ID",
      data = dataset_SMDH_parasite
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "SMDH")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Parasite_type")

   MR_SMDH_parasite_plot
```

2\. Time of addition of green nest material (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).

#### Type of experimental design

(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).

```{r}
# This analysis only includes dataset that has a proxy relating to comaparision type
dataset_SMDH_design <- dataset_SMDH %>%
  filter(!is.na(comparision_type))%>%
  mutate(comparision_type= as.factor(comparision_type))

VCV_SMDH_design <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_design,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
MR_SMDH_design <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_design ,# specify lnRR's sampling variance;
                    mods = ~ - 1 + comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_design )

# save(MR_SMDH_design, file = here::here("GNM/figures/MR_SMDH_trait.Rdata"))
```

```{r}
 MR_SMDH_design_plot <-
  orchard_plot(
    mod_results(
        MR_SMDH_design,
      mod = "comparision_type",
      group = "paper_ID",
      data = dataset_SMDH_design
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
  labs(x = "",
       y = "SMDH")+
  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  ggtitle("Experimental Design")

    MR_SMDH_design_plot
```

#### Bird species

(levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)

```{r}
MR_SMDH_birds <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH,# specify lnRR's sampling variance;
                    mods = ~ - 1 + bird_species,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# save(MR_SMDH_birds, file = here::here("GNM/figures/MR_SMDH_birds.Rdata"))
```

```{r Plot SMDH meta-regression on birds}

MR_SMDH_birds_plot <-
  orchard_plot(
    mod_results(
       MR_SMDH_birds,
      mod = "bird_species",
      group = "paper_ID",
      data = dataset_SMDH
    ), xlab ="") +
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
  labs(x = "",
       y = "SMDH")+
  theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
  ggtitle("Bird Species")

 MR_SMDH_birds_plot
```

#### Type of trait studied

(levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology)

```{r}
MR_SMDH_trait <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = SMDH_variance,# specify lnRR's sampling variance;
                    mods = ~ - 1 + trait_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

# save(MR_SMDH_trait, file = here::here("GNM/figures/MR_SMDH_trait.Rdata"))
```

```{r}
MR_SMDH_trait_plot <-
  orchard_plot(
    mod_results(
        MR_SMDH_trait,
      mod = "trait_type",
      group = "paper_ID",
      data = dataset_SMDH
    ),
    xlab = "")+
     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
  labs(x = "",
       y = "SMDH")+
   theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
  ggtitle("Type of trait studied")

   MR_SMDH_trait_plot
```

# **Sensitivity analyses / robustness checks**

We will run several sensitivity analyses using the same random effect structure as described above aimed at ensuring the robustness of our results.

1.  We will re-run all our meta-analyses and meta-regressions only using effect sizes calculated from means, SDs, and ns (i.e., excluding any effect sizes calculated from inferential statistics)

2.  For the overall effect size (i.e., the meta-analytical mean), we will run the bivariate multilevel meta-analytic model suggested by Yang et al. (2024), which models both lnRR and SMD(H) simultaneously (i.e., including them both as response variables and estimating their correlation; random).

```{r}
dataset_bivariate <- data.frame(paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
                      Observation_ID = c(dataset_lnRR$Observation_ID, dataset_SMDH$Observation_ID),
                      ES = c(dataset_lnRR$lnRR_sign, dataset_SMDH$SMDH_sign),
                      V_ES = c(dataset_lnRR$lnRR_variance, dataset_SMDH$SMDH_variance),
                      ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMD", nrow(dataset_SMDH)))
                      )

VCV <- vcalc(vi = V_ES, # sampling variances of lnRR and SMD that are correlated within the same study;
             cluster = paper_ID, # study identity;
             type = ES_measure, # different types of effect size measures underlying the observed effect sizes;
             data = dataset_bivariate, # the long format data frame;
             rho = 0.5, # assuming that the effect sizes within the same study are correlated with rho = 0.5.
             nearpd = TRUE # specify whether impose the non positive definite VCV matrix (not invertible) to the nearest positive semi-definite matrix 
             )

BMLMA <- rma.mv(yi = ES, # specify the effect size estimate (the variable ES in our case);
                V = VCV, # specify the imputed variance-covariance matrix;
                mods = ~ ES_measure - 1, # specify the variable "ES_measure" indicating the types of effect size measures;
                random = list(~ ES_measure | paper_ID, 
                              ~ ES_measure | Observation_ID), # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
                struct = "UN", # impose an unstructured variance-covariance of the study-specific random effects;
                test = "t", # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
                method = "REML", # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
                data = dataset_bivariate, # the long format dataset
                sparse = T
               )

```

3.  We will re-run our intercept-only multivariate meta-analysis (with both lnRR and SMDH as effect sizes) using 0.3 and 0.7 correlation (ρs) between sampling variances from the same paper_ID. If we find large differences in conclusions depending on ρs, we will run the corresponding sensitivity analyses for all our meta-regressions as well.

4.  If during our analyses we notice the need to run additional sensitivity analyses to ensure the robustness of our results, we will label those analyses as non-pre-registered and report them in the supplementary materials of the eventual manuscript.

### Risk of Bias

6\. Blinding: (Levels: yes, no(

7\. Random Assignment: (Levels: yes, no)

8\. Missing Data: (Levels: yes, no)

Note that the specific subset of data for each meta-regression may differ based on the data availability (e.g., information about the type of parasites is only available for effect sizes based on parasite/pathogen related fitness proxy). We will conduct meta-regression on suitable subsets of data for each analysis, provided we have sufficient effect sizes per moderator level (i.e., at least 5 effect sizes per moderator level).

::: callout-important
## Phylogenetic Effects

Note also that if we obtain additional effect sizes for other bird species after we update our search and/or contact authors, our models may need to account for phylogenetic nonindependence via the inclusion of two additional random effects: "species" and "phylogeny" following Cinar et al. (2022).
:::

## Other Analysis

### Risk of Bias Assessment

-   RoB - The outcome will be presented in the form of a [**summary table**]{.underline}. We will conduct uni-moderator meta-regressions using these variables.

## Heterogeneity

To understand the sources of variation or heterogeneity,

### For the intercept-only models

we will use the pluralistic approach recently suggested by Yang et al. (2023),

which consists of calculating four metrics of heterogeneity (σ2, I2, CV, M) to comprehensively understand both total and random-effect specific heterogeneity.

### For the meta-regressions,

we will calculate Rmarginal2 to quantify the heterogeneity explained by the moderator(s) in proportion to the total variation (Nakagawa & Schielzeth, 2013).

## Publication Bias

To explore evidence of publication bias, we will run multilevel meta-regressions with the same random effects structure as described above. We will follow the approach recommended in section 4.3 from Nakagawa et al. (2022) for both lnRR and SMDH, which consists of the following steps:

First, run a uni-moderator meta-regression to test for evidence of small-study effects for both lnRR and SMDH separately, where the moderator is the square root of the inverse of the 'effective sample size' (see equation 27 in Nakagawa et al. 2022). The slope of this meta-regression provides information about whether funnel plot asymmetry exists, and the intercept corresponds to the overall effect size adjusted by small-study effects. However, if this intercept is statistically significantly different from zero,

```{r}
dataset_SMDH<-dataset_SMDH%>%
  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))

MR_SMDH_small_study <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = SMDH_variance,# specify lnRR's sampling variance;
                    mods = ~sqrt_effective_n_inv,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

summary(MR_SMDH_small_study)

SMDH_small_study_bubble<-orchaRd::mod_results(MR_SMDH_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop")
orchaRd::bubble_plot(SMDH_small_study_bubble,
                      mod="sqrt_effective_n_inv",
                     group="paper_ID")

round(r2_ml(MR_SMDH_small_study)*100,2)
```

Then, run the following uni-moderator meta-regression for both lnRR and SMDH separately which provides a less biased adjusted overall effect. The moderator here is simply the inverse of the 'effective sample size' (see equation 28 in Nakagawa et al. 2022). The slope of this meta-regression provides information about whether funnel plot asymmetry exists and the intercept corresponds to a less biased overall effect size adjusted by small-study effects.

Next, run a uni-moderator meta-regression to test for evidence of decline effects (also known as time-lag bias) which includes year of publication (mean-centered) as the only moderator, and whose slope would provide information about whether the overall effect size has changed (decline) over time (Nakagawa et al. 2022; Sánchez-Tójar et al. 2018).

```{r}
dataset_SMDH<-dataset_SMDH%>%
  filter(year_publication!="Unpublished")%>%
  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])

MR_SMDH_decline_eff <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = SMDH_variance,# specify lnRR's sampling variance;
                    mods = ~ year_MeanCenter,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH)

summary(MR_SMDH_decline_eff)

round(r2_ml(MR_SMDH_decline_eff)*100,2)

MR_SMDH_decline_effect_bubble<-orchaRd::mod_results(MR_SMDH_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop")
orchaRd::bubble_plot(MR_SMDH_decline_effect_bubble,
                      mod="year_MeanCenter",
                     group="paper_ID")
```

Last, run an all-in meta-regression including both the (square root of the) inverse of the 'effective sample size' and the mean-centered year of publication as well as all the other moderators tested in our study to estimate how much heterogeneity is explained by all moderators combined as well as to explore whether evidence remains similar after accounting for all the other moderators (see equation 29 in Nakagawa et al. 2022 for more information about this approach).

### 2025-05-08 docs/manuscript_GNM.qmd
Incorporated changes for methods

@@
 ```{r Setup, include=FALSE, echo=FALSE}
-
-pacman::p_load(readr,tidyverse)
+devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
+pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
 
@@
 We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
+The pre-registration details the study's objectives, a priori hypotheses and predictions, methods and planned data analyses.
 Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist).
 All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
@@
 
-We conducted a systematic search on the Web of science Core Collection and Scopus citation database on 07.09.2022.
-The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for a complete search string tailored to specific database see @figsupp-string).
-We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
+We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022.
+The keyword search query was designed as a three-block query to included terms related to the predictor/treatment (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), our population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit it to only experimental studies only ("experiment\*" OR "manipulat\*").
+The complete search strings tailored to each specific platform are provided in @figsupp-string.
+We searched through titles, abstracts and keywords in English-language only with no restrictions on publication date or study type.
+We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used the R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
-We validated our search using an initial library of `{r} nrow(own_library)` relevant articles (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 
@@
 
-All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in `revtools`.
-We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
-`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another.
-We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
-`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decisions (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
+All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree (@figsupp-decision-tree).
+We included all studies on birds that experimentally manipulated the green nest material (both aromatics or herbs).
+`{r} nrow(selected_abstract_screening)` articles passed the title-and-abstract screening and were further evaluated during the full-text screening.
+Each article was screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
+We used the same criteria as above (see @figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
+`{r} nrow(excluded_fulltext)` articles were excluded.
+All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
 
-We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
-After de-duplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
-We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
-In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search.
-These studies met our inclusion criteria and were added to our meta-analysis.
-The exact number of screened and included studies along with reasons of exclusion are shown in @figsupp-prisma-flowchart.
+To update our systematic lietrature search, we repeated our search on 12.08.2024.
+This updated search found `{r} nrow(unique_reference_list_repeat)` unique articles after removing ``` {r} nrow(full_reference_before_deduplication_repeat)-``nrow(unique_reference_list_repeat) ``` duplicates.
+Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article.
+Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles.
+In all, X <!--# Fill the no.
+of articles that are included --> articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
 
@@
 
-Data was extracted evenly by one of the three authors (\~33% each SD, TR and JMGS) and was checked by another to ensure correctness of the data.
-We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
-In cases where primary data was only available in figures (such as boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
-If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
-In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
-When data was presented in different sources, we prioritized the source having the maximum resolution.
+The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
+We extracted the primary data (i.e., measures of central tendency, variance and sample size) from text whenever possible.
+In cases where primary data was only available in figures (e.g., boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
+If primary data was not available, we extracted any inferential statistics (t value, F value) that could be transformed into an effect size.
+In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the provided raw data.
+When data was presented in different sources (e.g.
+in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).
 
-To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
-We contacted 4 authors for missing data, while the rest were asked for any potential unpublished data.
-All four authors responded to our email- 2 provided the data as requested, one did not have the data any more and one did not give a conclusive response.
-One author provided unpublished data.
-Another unpublished data was provided by the author of this study (MO).
-We extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
+To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
+unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
+We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
+All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
+In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
+In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
 
-We extracted mean, variance and sample size for a control-treatment pairwise comparison.
-Controls included non-aromatic materials (e.g., grass, moss), lesser amounts of aromatic material, or no material.
+We extracted the means, variances and sample size for each control-treatment pairwise comparison.
+Controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material, or no material at all.
 Treatments consisted of aromatic materials added by authors, birds, or both.
@@
 
-For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, trait measured) and information about the extracted data (location or source of the data recorded).
-We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
-In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied into arthropods or micro-organisms.
+For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and information about the extracted data (location or source of the data recorded).
+We categorized the fitness proxy measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load and phenology.
+For parasites or pathogens, we categorised them into arthropods or micro-organisms.
 For a complete list of variables extracted see @figsupp-variables .
-We excluded some traits (n=`{r} nrow(excluded_proxies)` , k=`{r} length(unique(excluded_proxies$paper_ID))`) measured from all our analysis because it was unclear how they related to fitness (see @figsupp-excluded-proxies for the list and reason of exclusion).
-We also had to exclude some fitness proxies (n=?, k=?) because of the low sample size per group (less than x).
+We did not include some traits in all our analyses becaause it was unclear how they related to fitness (k=`{r} nrow(excluded_proxies)` , n=`{r} length(unique(excluded_proxies$paper_ID))`;see @figsupp-excluded-proxies for the list and reason of exclusion).
+We also had to exclude some effect sizes (n=?, k=?) because of the low sample size per group (less than x).
 
@@
 
-We calculated two effect sizes for each pairwise comparison-log response ratio (lnRR) and standardised mean difference with heteroskedasticity correction (SMDH), using `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in `metafor` package (@metafor).
-We specified treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that the positive values indicate the trait value increased in the treatment group.
-In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the sign was inverted to ensure comparability across all fitness proxies.
+We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` (@metafor).
+We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that positive values indicate the 'fitness' value increased in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the effect size sign was inverted to ensure comparability across all fitness proxies.
 In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
 
-For studies reporting only inferential statistics (e.g., t-tests, ANCOVA), we estimated SMD values (n=`{r} nrow(inferential_stats)`, k=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019 .
-In cases of dichotomous variables (e.g., successful nests, n=`{r} nrow(contingency_table)`, k=`{r} length(unique(contingency_table$paper_ID))`) we used the data to calculate log odds ratio using `escalc` function (`measure=OR`) and convert it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics or dichotomous variables, only SMD under the assumption of homoscedasticity was derived from such data.
-We excluded these effect sizes along with any zero or negative values (n=`{r} nrow(negative_lnRR)`, k=`{r} length(unique(negative_lnRR$paper_ID))`) when calculating lnRR.
+For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k=`{r} nrow(inferential_stats)`, n=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019.
+For dichotomous variables (e.g., number of successful nests, k= `{r} nrow(contingency_table)`, n= `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k=`{r} nrow(negative_lnRR)`, n=`{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k=?, n=?) subset is smaller than that of SMDH (k=?,n=?).
 
-The sample sizes used were the number of nests in each group, and not the number of individuals, whenever possible.
-In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in the comparison, to account for shared group non-independence.
-For the cases where the authors reported no significant difference between the two groups (n=`{r} nrow(no_ES)`, k=`{r} length(unique(no_ES$paper_ID))`) but did not provide the values, we used zero as the effect size.
-To impute the SD for these cases, we used the missing-case approach following @nakagawa2022.
+When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size, whenever possible to reduce the effect of genetic relatedness non-independence.
+In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
+For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k=`{r} nrow(no_ES)`, n=`{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparision and imputed its SD using the missing-case approach described in @nakagawa2022.
 
@@
 
-We performed analysis in R version 4.3.0 (@positteam2023).
+We performed all analyses in R version 4.3.0 (@positteam2023).
 All multilevel meta-analytical models and meta-regressions were fit using `metafor v.4.8-0` (@metafor).
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using `vcalc` function.
-(See Supplementary Appendix @figsupp-correlation for sensitivity analysis using different values of correlation (ρ)).
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the `vcalc` function from `metafor`.
+(See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
-Our data had various sources of non-independence which we accounted for using random effects.
-We considered the following level of non-independence- (a) multiple effect sizes were collected from same study (Paper ID), (b) some bird species (species ID) and (c) some geographical locations (population ID) were studied multiple times, (d) some sub-populations (Experiment ID e.g.
-birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID, eg.
-males and females in a population, first clutch and second clutch) were represented in our data several times and (f) repeated traits collected on the same group of animals (repeated trait ID e.g.
+We considered the following levels of non-independence for our analyses: (a) multiple effect sizes collected from same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) some sub-populations (Experiment ID; e.g.
+birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID; eg.
+males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) some traits were collected on the same group of animals repeatedly (Repeated trait ID; e.g.
 chick mass on day 7, 14 and 21).
 
-We fitted the following random effects in all our models unless stated otherwise- Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
-Initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
-Experiment ID and group ID were almost indistinguishable, as such we decided to leave out the one with lesser resolution i.e.
+Unless stated otherwise, we fitted the following random effects in all our models to account for non-independence: Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
+Our random effect structure deviated from our pre-registration since, initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
+However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution i.e.
 Experiment ID.
-Additionally, we observed that not many effect sizes were measured repeatedly, making the repeated trait ID very similar to the observation ID.
-After exploring the overlap (@figsupp-random-effect), we decided to only keep observation ID.
-We added population ID, which accounts for many effect sizes from different studies coming from the same geographical location.
+Additionally, few effect sizes were measured repeatedly, making the Repeated trait ID almost identical to the observation-level random effect (Observation ID), so we excluded it (@figsupp-random-effect).
+Last, we decided to add Population ID, since we noticed that several studies were performed in the same geographical locations.
 
-### Meta-analytical models for biological predictions
+### Meta-analytic models: biological predictions
 
-To estimate the overall effect of green nest material addition to the nest on fitness across bird species that perform this behaviour, we fitted two separate multilevel intercept-only meta-analytical models using lnRR or SMDH as dependent variables.
-We used `rma.mv` function from `metafor` package using the 'REML' method.
-Test statistics and confidence intervals for the fixed effects were computed using t distribution.
-We used the entire dataset for this analysis except some traits (n=`{r} nrow(SAonly_proxies)` , k=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies for details) that we decided to exclude from all our analysis due to lack of evidence supporting their relationship with fitness.
-However, we also conducted a sensitivity analysis (@figsupp-MLMA-excluded) including these proxies to ensure robustness of our results.
-In the model using SMDH, We estimated total amount of heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) (@yang2025).
+To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMDH.
+Thus, throughout, we fitted two separate sets of model for each effect size.
+First, we fitted multilevel intercept-only meta-analytical model to test the overall effect, its uncertainty and heterogeneity.
+We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k=`{r} nrow(SAonly_proxies)` , n=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies).
+For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
 
-To test the effect of green nest material on reproductive success (courtship hypothesis) and on protective effects and health benefits for the nestling (Parental care hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
-using the entire dataset.
-For this and all meta-regressions, we estimated $R_{marginal}^2$, the percentage of heterogeneity explained by the moderators (@nakagawa2012) using the entire dataset.
+<!--# You have to correct the numbers for contingency table. It does not include the one data point from unpublished results -->
 
-### Meta-regressions for exploratory analysis
+<!--# Check what is MLMA-excluded and figsupp-SAonly-proxies for figures and decide which one makes more sense to include/exclude?? -->
+
+To test the relative importance of the two main hypotheses suggested for green nest material: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators (@nakagawa2012).
+
+### Meta-analytic models: exploratory analyses
 
@@
 aromatic, no added material vs.
-non-aromatic), we ran a meta-regression with type of experimental design as the moderator.
+non-aromatic), we ran a meta-regression with the type of experimental design as a moderator.
 
@@
 
-Publication bias is the higher likelihood of a subset of research findings, such as statistically significant results, being published as compared to the rest.
-We tested for evidence of publication bias (following @nakagawa2021) for both lnRR and SMDH separately.
-To test for small study effects, we ran meta-regression , using the inverse of effective sample size as a moderator.
-To understand the decline effect (also known as time-lag bias) we ran another meta-regression with a mean-centered publication year as a moderator.
+Publication bias occurs when a subset of research findings, most often statistically non-significant ones, are less likely to be published or being published as compared to the rest.
+We tested for evidence of publication bias, both small-study and decline effects following @nakagawa2021.
+Publication bias tests were performed for both lnRR and SMDH separately, and using the same random effect structure as reported above.
+To test for small-study effects, we ran a multilevel meta-regression, using the inverse of the effective sample size as a moderator.
+To test for decline effects (also known as time-lag bias; @sanchez-tojar2018), we ran multilevel meta-regression year of publication (mean-centered) as a moderator.
 
@@
 
-We obtained X effect sizes from k studies including How many papers in final meta-analysis and how many effect size.
+```{r}
+dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")
+
+ES_per_study<-dataset_analysis%>%group_by(paper_ID)%>%count(paper_ID)
+
+birds_info<-dataset_analysis%>%group_by(bird_species)%>%count(bird_species)
+birds_info$perc<-(birds_info$n/nrow(dataset_analysis))*100
+```
+
+We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations.
+About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
+Our dataset included two unpublished studies (k=XX effect sizes), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
+The mean (±SD) number of effect sizes per study was `{r} as.numeric(format(mean(ES_per_study$n), digit=3))` ± `{r} as.numeric(format(sd(ES_per_study$n), digit=2))`(range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean sample size per effect size were `{r} median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))` and `{r} as.numeric(format(mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)), digit=3))` respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
+
+**Overall effect of green nest material on fitness proxies**
+
+```{r}
+intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
+intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
+bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
+```
+
+Both lnRR and SMDH intercept-only multilevel meta-analyses showed an increase in fitness in the nests with an increase in green nest material compared to control nests; however, the overall effect was only statistically significant for SMDH.
+
+The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
+Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH1~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_lnRR)[1]),2)` and M1~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
+The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high.
+Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2023; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
+
+While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
+While neither intercept was statistically significant, the results strengthens the interpretation that any effect of green nest material on fitness outcomes in likely to be very small at best \[lnRR = `{r} as.double(formatC(coef(bivariate_model)[1], digit = 3, format="f"))`, p-value = `{r} as.double(formatC(bivariate_model$pval[1], digits = 3, format = "f"))` and SMDH = `{r} as.double(formatC(coef(bivariate_model)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(bivariate_model$pval[2], digits = 3, format = "f"))`\].
+
+![Overall effect of green nest material on fitness: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardized mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect width="1059"}
+
+**Mechanisms behind green nest material effects**
+
+```{r}
+lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
+SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))
+```
+
+Using the multilevel meta-regressions with hypothesis type as a moderator, we found no clear support for either of the proposed mechanism [@fig-hypothesis].
+There was a small positive but non-significant effect of green nest material on reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[2], digits = 3, format = "f"))` and SMDH~courtship~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[2], digits = 3, format = "f"))`\].
+We found even smaller, non-significant effect of green nest material on protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[3], digits = 3, format = "f"))` and SMDH~parental_care~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[3], digits = 3, format = "f"))`\].
+In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either mechanisms, we found a small positive effect \[lnRR~both~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[1], digits = 3, format = "f"))` and SMDH~both~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[1], digits = 3, format = "f"))`\].
+The moderator explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+
+![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests.
+Orchard plot of the multilevel meta-regression for A.
+log response ratio (lnRR) and B.
+Standardised mean difference (SMDH).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}
+
+## Pre-registered exploratory analyses
+
+```{r}
+# Loading models for experimental design
+lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
+
+# Loading models for parasite type
+lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
+SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
+
+# Loading models for time of green nest material addition
+lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
+SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
+
+# Loading models for the type of trait studied
+lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
+
+# Loading models for the bird species studied
+lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+
+```
+
+There was no evidence that the effect of green nest material on parasite or pathogen load differed between arthropods and micro-organisms \[[@supp-fig-MR-non-sig]A-B; lnRR~arthropods~ = `{r} as.double(formatC(coef(lnRR_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[1], digits = 3, format = "f"))` and SMDH~arthropods~ = `{r} as.double(formatC(coef(SMDH_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[1], digits = 3, format = "f"))`; lnRR~micro-organisms~ = `{r} as.double(formatC(coef(lnRR_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[2], digits = 3, format = "f"))` and SMDH~micro-organisms~ = `{r} as.double(formatC(coef(SMDH_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[2], digits = 3, format = "f"))`\].
+The type of parasite or pathogen explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+
+The meta-regression using bird species as a moderator showed no significantly different effect of green nest material on fitness depending on the bird being studied \[[@supp-fig-MR-non-sig]C-D\]; .
+However, it explained some heterogeneity in the effect sizes ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+
+We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+
+To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
+
+We explored the impact of methodological differences on the relationship between green nest material and fitness.
+To understand the effect of type of experimental design (i.e.
+whether the authors compared - non-aromatic vs.
+aromatic, no added material vs.
+aromatic, no added material vs.
+non-aromatic), we ran a meta-regression with type of experimental design as the moderator.
+
+\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--
 
 ## Supplementary Appendix
+
+```{r results='asis'}
+cat(readLines("tables/SA_intercept_only.html"), sep ="\n")
+```
+
+![](figures/Figure_parasite_birds_trait.png){#supp-fig-MR-non-sig}
 

### 2025-05-08 docs/notebook/data_analysis.qmd
Incorporated changes for methods

--- 2025-04-22 notebook/data_analysis.qmd
@@
 
-# lnRR Multilevel meta-analysis
-
-```{r}
+# Preparing datasets
+
+```{r seperating datasets for analysis}
+
+## For lnRR
 # selecting dataset which are not flagged
@@
 # selecting dataset without those using 0 as ES because authors reported no effect
-
 lnRR_sin_missingES <- dataset_lnRR %>% 
@@
 
-```
-
-## Intercept only models
+## For SMDH
+# selecting dataset which are not flagged
+dataset_SMDH<-dataset_analysis%>%
+   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
+
+# selecting dataset which are flagged
+SMDH_con_flagged<-dataset_analysis%>%
+   filter(SMDH_sign != "NA")
+
+# selecting dataset without those using 0 as ES because authors reported no effect
+
+SMDH_sin_missingES <- dataset_SMDH %>% 
+   filter(!proxy_comment %in% c("use 0 as ES"))
+
+SMDH_flagged_no_missingES<- SMDH_con_flagged %>% 
+   filter(!proxy_comment %in% c("use 0 as ES"))
+
+# selecting dataset which are not flagged but without the SMDH calculated from inferential statistics
+
+SMDH_no_inferential<-dataset_analysis%>%
+  filter(proxy_decision == "include")%>% filter(SMDH_sign != "NA")
+```
+
+# Overall effect : Intercept-only meta-analytic model
 
@@
 
-```{r}
-
+## using lnRR
+
+```{r intercept-only-model-lnRR}
 VCV_lnRR<- vcalc(vi = lnRR_variance,
@@
                   )
-
-```
-
-The MLMA using lnRR as the effect size measure incorporate the imputed sampling variance-covariance:
-
-```{r intercept-only-model-lnRR}
 
@@
                     data = dataset_lnRR)
-
 # saving the model
@@
 
-summary(intercept_lnRR)
-predict(intercept_lnRR)
-
-```
-
-Now looking at the intercept only model
+```
+
+Exploring heterogeneity in intercept only model
+
+This is the function from Yefeng's Github for interpretting heterogeneity.
+I have to download the data used for this function to be able to use it.
+For now I am using the values from the table directly so I should just delete it later before finishing the code.
+
+```{r function-interpret-heterogeneity}
+# ## Function is from the Pluralistic approach to heterogeneity from Yefeng's Pre-print repository from GitHub
+# 
+# #-----------------------heterogeneity interpretation-----------------------#
+# het_interpret <- function(observed_value, het_type, es_type, data) {
+#   
+#   if (!het_type %in% c("I2", "CVH", "M", "sigma2", "V_bar")) {
+#     stop("Invalid heterogeneity type. Choose from 'I2', 'CVH', 'M', 'sigma2', or 'V_bar'.")
+#   }
+#   
+#   if (!es_type %in% unique(data$es.type)) {
+#     stop("Invalid effect size type. Check the levels of 'es.type'.")
+#   }
+#   
+#   filtered_data <- data %>% filter(es.type == es_type)
+#   
+#   if (nrow(filtered_data) == 0) {
+#     stop("No data available for the selected effect size type.")
+#   }
+#   
+#   het_values <- filtered_data[[het_type]]
+#   
+#   percentiles <- quantile(het_values, probs = seq(0, 1, by = 0.05), na.rm = TRUE)
+#   
+#   lower_bound <- max(percentiles[percentiles <= observed_value], na.rm = TRUE)
+#   upper_bound <- min(percentiles[percentiles >= observed_value], na.rm = TRUE)
+#   lower_percentile <- names(percentiles)[percentiles == lower_bound]
+#   upper_percentile <- names(percentiles)[percentiles == upper_bound]
+#   
+#   percentile_range <- paste0(lower_percentile, "-", upper_percentile, "th percentile")
+#   
+#   # return the results
+#   return(tibble::tibble(
+#     observed_value = observed_value,
+#     het_type = het_type,
+#     es_type = es_type,
+#     percentile_range = percentile_range
+#   ))
+# }
+# x<-het_interpret(observed_value= I2_main_model_vector[1], 
+#                  het_type = "I2", 
+#                  es_type = "lnRR_sign", 
+#                  data= intercept_lnRR)
+
+```
+
+## lnRR-heterogeneity
+
+Let us look at the heterogeneity in lnRR intercept-only model
 
@@
 sigma2_main_model_vector <- sum(intercept_lnRR$sigma2)
+# 0.11, 0.27, and 0.57 for lnRR
 I2_main_model_vector <- orchaRd::i2_ml(intercept_lnRR)
+# 0.88, 0.95, and 0.99 for lnRR
 CV_main_model_vector <- orchaRd::cvh1_ml(intercept_lnRR)
-M_main_model_vector <- orchaRd::m2_ml(intercept_lnRR)
+# CVH2 (CVH1) - 1.36 (1.16), 3.76 (1.94), and 12.1 (3.48) for lnRR
+M_main_model_vector <- orchaRd::m1_ml(intercept_lnRR)
+# M2(M1) - 0.58 (0.54), 0.79 (0.66), and 0.78 for lnRR;
 
@@
 
-### Senstivity Analysis with flagged proxies
+## using SMDH
+
+We are only running these analysis for the fitness proxy labelled "included". Some proxies have been flagged and we will run them in a sensitivity analysis only
+
+their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
+
+The MLMA using SMDH as the effect size measure incorporate the imputed sampling variance
+
+```{r intercept-only-model-SMDH}
+
+VCV_SMDH <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+intercept_SMDH<- rma.mv(yi = SMDH_sign, # specify SMDH as the effect size measure;
+                    V = VCV_SMDH, # specify SMDH's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH)
+
+# saving the model
+# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+```
+
+## SMDH-heterogeneity
+
+Now looking at the intercept only model
+
+```{r}
+summary(intercept_SMDH)
+predict(intercept_SMDH)
+
+# Then also:
+# # Typical sampling variance (which captures the statistical noise of the data, 
+# # but is rarely reported in the current meta-analytic practice):
+sigma2_v(intercept_SMDH)
+
+# To calculate heterogeneity, these are the functions from orchaRd:
+# # I2, CV and M
+sigma2_main_model_vector <- sum(intercept_SMDH$sigma2)
+# 0.54, 1.25, and 3.03 for SMD;
+I2_main_model_vector <- orchaRd::i2_ml(intercept_SMDH)
+# 0.78, 0.89, and 0.96 for SMD
+# 0.88, 0.95, and 0.99 for lnRR
+CV_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
+# CVH2 (CVH1) - 1.36 (1.16), 3.76 (1.94), and 12.1 (3.48) for lnRR
+M_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)
+# M2 (M1) - 0.58 (0.54), 0.79 (0.66), and 0.78 for lnRR
+
+# # # Total unstandardized raw variance (i.e. total heterogeneity)
+round(sum(intercept_SMDH$sigma2), 3)
+
+```
+
+## Bivariate Meta-analytical model
+
+For the overall effect size (i.e., the meta-analytical mean), we will run the bivariate multilevel meta-analytic model suggested by Yang et al.
+(2024), which models both lnRR and SMD(H) simultaneously (i.e., including them both as response variables and estimating their correlation; random).
+
+```{r}
+dataset_bivariate <- data.frame(paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
+                      Observation_ID = c(dataset_lnRR$Observation_ID, dataset_SMDH$Observation_ID),
+                      group_ID_coded = c(dataset_lnRR$group_ID_coded, dataset_SMDH$group_ID_coded),
+                      population_ID = c(dataset_lnRR$population_ID, dataset_SMDH$population_ID),
+                      bird_species = c(dataset_lnRR$bird_species, dataset_SMDH$bird_species),
+                      ES = c(dataset_lnRR$lnRR_sign, dataset_SMDH$SMDH_sign),
+                      V_ES = c(dataset_lnRR$lnRR_variance, dataset_SMDH$SMDH_variance),
+                      ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMDH", nrow(dataset_SMDH)))
+                      )
+
+VCV_bivariate <- vcalc(vi = V_ES, # sampling variances of lnRR and SMD that are correlated within the same study;
+             cluster = paper_ID, # study identity;
+             type = ES_measure, # different types of effect size measures underlying the observed effect sizes;
+             data = dataset_bivariate, # the long format data frame;
+             rho = 0.2, # assuming that the effect sizes within the same study are correlated with rho = 0.5.
+             nearpd = TRUE # specify whether impose the non positive definite VCV matrix (not invertible) to the nearest positive semi-definite matrix 
+             )
+
+Bivariate_model <- rma.mv(yi = ES, # specify the effect size estimate (the variable ES in our case);
+                V = VCV_bivariate, # specify the imputed variance-covariance matrix;
+                mods = ~ ES_measure - 1, # specify the variable "ES_measure" indicating the types of effect size measures;
+                random = list(~ ES_measure | paper_ID, 
+                              ~ ES_measure | Observation_ID,
+                              ~ 1 | group_ID_coded,
+                              ~ 1 | population_ID,
+                              ~ 1 | bird_species
+                              ), # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
+                struct = "UN", # impose an unstructured variance-covariance of the study-specific random effects;
+                test = "t", # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
+                method = "REML", # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
+                data = dataset_bivariate, # the long format dataset
+                sparse = T
+               )
+
+saveRDS(Bivariate_model, file = here::here("sensitivity_analysis/bivariate_model.rds"))
+
+summary(Bivariate_model)
+```
+
+```{r WARNING = F}
+pacman::p_load(ellipse)
+ab.l <- matreg(y=2, x=1, R=Bivariate_model$G, cov=TRUE, means=coef(Bivariate_model), n=Bivariate_model$g.levels.comb.k) # fit regression model
+
+xy <- ellipse(Bivariate_model$G, centre=coef(Bivariate_model), level=0.95) # get 95% coverage region
+ellipse_df <- data.frame(x = xy[, 1], y = xy[, 2]) # convert it int dataframe so that we can use ggplot to make a figure
+
+pivot_wider(dataset_bivariate, names_from = ES_measure, values_from = c(ES, V_ES)) %>%
+  ggplot() + 
+  geom_point(aes(x = ES_lnRR, y = ES_SMDH, size = 1/sqrt(V_ES_lnRR)), color = "#1B9E77", alpha = 0.5) + 
+  geom_point(aes(x = coef(Bivariate_model)[1], y = coef(Bivariate_model)[2]), color = "red", size = 2) + 
+  geom_abline(intercept = ab.l$tab$beta[1], slope = ab.l$tab$beta[2]) +
+  geom_path(data = ellipse_df, aes(x = x, y = y), color = "gray50") +
+  #scale_x_continuous(limits = c(-2.5, 2.5)) + 
+  #scale_y_continuous(limits = c(-2.5, 2.5)) + 
+  guides(size = "none") + 
+  labs(x = "lnRR", y = "SMD") + 
+  theme_bw()
+```
+
+There is a very high negative correlation between the two effect sizes.
+This probably is an artifact of the data and not a true correlation.
+If you look at the model summary, the $tau^2$ for lnRR, it is extremely small 0.0008, i.e., there is very little variance.
+This could also be stemming from the fact that the log values in the dataset could be causing this.
+For SMDH on the other hand, the $tau^2$ is 0.1681 that is much larger.
+This difference in the variance estimate itself could be causing this artifact of the model.
+I will only go ahead to present this model as a senstivity analysis because I am not completely convinced by it's robustness.
+
+# Sensitivity Analysis
+
+### Sensitivity Analysis with flagged proxies
 
@@
 
-MLMA_lnRR_VCV_flagged<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_flagged<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                     V = VCV_lnRR_flagged, # specify lnRR's sampling variance-covariance matrix;
@@
 
+# saving the model
+saveRDS(SA_lnRR_flagged, file = here::here("sensitivity_analysis/SA_lnRR_flagged.rds"))
+
 # What is the effect now?
 
-summary(MLMA_lnRR_VCV_flagged)
-predict(MLMA_lnRR_VCV_flagged)
+summary(SA_lnRR_flagged)
+predict(SA_lnRR_flagged)
+
+## Now for SMDH
+
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_flagged <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = SMDH_con_flagged,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_flagged<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_flagged, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = SMDH_con_flagged)
+
+# saving the model
+saveRDS(SA_SMDH_flagged, file = here::here("sensitivity_analysis/SA_SMDH_flagged.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_flagged)
+predict(SA_SMDH_flagged)
 
@@
 
-MLMA_lnRR_VCV_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                     V = VCV_lnRR_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
 
+# saving the model
+saveRDS(SA_lnRR_no_missingES, file = here::here("sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+
 # What is the effect now?
 
-summary(MLMA_lnRR_VCV_no_missingES)
-predict(MLMA_lnRR_VCV_no_missingES)
+summary(SA_lnRR_no_missingES)
+predict(SA_lnRR_no_missingES)
+
+## Now we do this for SMDH
+
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_no_missingES <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = SMDH_sin_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_missingES, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = SMDH_sin_missingES)
+
+# saving the model
+saveRDS(SA_SMDH_no_missingES, file = here::here("sensitivity_analysis/SA_SMDH_no_missingES.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_no_missingES)
+predict(SA_SMDH_no_missingES)
 
@@
 
-MLMA_lnRR_flagged_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_flagged_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                     V = VCV_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
 
+# saving the model
+saveRDS(SA_lnRR_flagged_no_missingES, file = here::here("sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
+
 # What is the effect now?
 
-summary(MLMA_lnRR_flagged_no_missingES)
-predict(MLMA_lnRR_flagged_no_missingES)
-```
+summary(SA_lnRR_flagged_no_missingES)
+predict(SA_lnRR_flagged_no_missingES)
+
+## with SMDH
+
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_flagged_no_missingES <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = SMDH_flagged_no_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_flagged_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = SMDH_flagged_no_missingES)
+
+# saving the model
+saveRDS(SA_SMDH_flagged_no_missingES, file = here::here("sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_flagged_no_missingES)
+predict(SA_SMDH_flagged_no_missingES)
+```
+
+### Sensitivity analysis only using effect sizes calculated from means, SDs, and ns
+
+(i.e., excluding any effect sizes calculated from inferential statistics)
+
+```{r}
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_no_inferential <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = SMDH_no_inferential,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_no_inferential<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_inferential, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = SMDH_no_inferential)
+
+# saving the model
+saveRDS(SA_SMDH_no_inferential, file = here::here("sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_no_inferential)
+predict(SA_SMDH_no_inferential)
+```
+
+### Different values of sampling variance correlation
 
@@
 
-### Plot
-
-```{r caterpillar plot lnRR}
-
-orchaRd::caterpillars(intercept_lnRR, mod = "1", group="paper_ID",xlab = "Effect size (Log response ratio - lnRR)")
-```
-
-```{r intercept only plot}
-
-lnRR_intercept_only_plot <- orchard_plot(intercept_lnRR,
-                                         mod = "1",
-                                         group = "paper_ID",
-                                         trunk.size = 1,
-                                         branch.size = 2,
-                                         alpha = 0.3,
-                                         twig.size = 1,
-                                         xlab = "Effect size (Log response ratio - lnRR)",
-                                         colour = "#218833",
-                                         fill = T) +
-  scale_fill_manual(values = "black") +
-  scale_colour_manual(values = "#218833") +  
-  theme(legend.direction="horizontal", legend.title = element_text(size =8),
-        legend.text = element_text(size = 10), 
-        axis.title = element_text(size = 15),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_blank()) +
-  labs(x = "Intercept")
-
-print(lnRR_intercept_only_plot)
-```
-
-```{# intercept_only_plot<- ggarrange(MLMA_lnRR_intercept_only_plot,}
-#                                       MLMA_lnRR_VCV_intercept_only_plot,
-#                                       ncol = 2,  nrow = 1)
-
-# intercept_only_plot
-# ggsave("intercept_only_plot.pdf", plot = intercept_only_plot, height = 250, width = 500, units = "mm", dpi = 600)
-
-```
-
-## Uni-moderator multilevel meta-regressions
-
-#### Hypothesis
+# Mechanistic Hypothesis
 
@@
 ```{r}
-MR_lnRR_hypothesis <-
+lnRR_hypothesis <-
   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
@@
 
-# save(MR_lnRR_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
-```
-
-```{r Plot lnRR meta-regression on hypothesis}
-
- MR_lnRR_hypothesis_plot <-
-  orchard_plot(
-    mod_results(
-       MR_lnRR_hypothesis,
-      mod = "Hypothesis",
-      group = "paper_ID",
-      data = dataset_lnRR
-    ), xlab ="") +
-  scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "lnRR")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Different Hypothesis")
-
-  MR_lnRR_hypothesis_plot
-```
-
-#### Exploratory Analysis
+saveRDS(lnRR_hypothesis, file = here::here("model/lnRR_hypothesis.rds"))
+
+lnRR_hypothesis_R2 <- r2_ml(lnRR_hypothesis)
+round(lnRR_hypothesis_R2 * 100, 1)
+
+SMDH_hypothesis <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+saveRDS(SMDH_hypothesis, file = here::here("model/SMDH_hypothesis.rds"))
+```
+
+# Exploratory Analysis
 
@@
 dataset_lnRR_parasite <- dataset_lnRR%>%
-  filter(trait_type == "Parasitic_and_pathogenic")
+  filter(!is.na(parasite_type))
+
 VCV_lnRR_parasite <- vcalc(vi = lnRR_variance,
@@
 
- MR_lnRR_parasite <-
+lnRR_parasite <-
   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
@@
 
- # Warning: 4 rows with NAs omitted from model fitting.
- # Check what rows are these..
-
- # save( MR_lnRR_parasite, file = here::here("GNM/figures/ MR_lnRR_parasite.Rdata"))
-```
-
-```{r}
- MR_lnRR_parasite_plot <-
-  orchard_plot(
-    mod_results(
-        MR_lnRR_parasite,
-      mod = "parasite_type",
-      group = "paper_ID",
-      data = dataset_lnRR_parasite
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "lnRR")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Parasite_type")
-
-   MR_lnRR_parasite_plot
-```
-
-2\. Time of addition of green nest material (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).
+saveRDS( lnRR_parasite, file = here::here("model/lnRR_parasite.rds"))
+
+### Similiarly for SMDH as well selecting the dataset with parasite type
+# This analysis only includes dataset that has a proxy relating to parasite or pathogen
+dataset_SMDH_parasite <- dataset_SMDH%>%
+  filter(!is.na(parasite_type))
+VCV_SMDH_parasite <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_parasite,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_parasite <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + parasite_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                   test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_parasite)
+
+saveRDS(SMDH_parasite, file = here::here("model/SMDH_parasite.rds"))
+```
+
+#### Time of addition of green nest material
+
+(levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).
+
+```{r}
+## We use the complete dataset in this case
+lnRR_time_gnm_addition <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ - 1 + time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+saveRDS(lnRR_time_gnm_addition, file = here::here("model/lnRR_time_gnm_addition.rds"))
+
+## Now similarly for the SMDH effect size using the complete dataset
+SMDH_time_gnm_addition <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ - 1 + time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+saveRDS(SMDH_time_gnm_addition, file = here::here("model/SMDH_time_gnm_addition.rds"))
+```
 
@@
                   )
-MR_lnRR_design <-
+lnRR_design <-
   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                     V = VCV_lnRR_design ,# specify lnRR's sampling variance;
-                    mods = ~ comparision_type,
+                    mods = ~ - 1 + comparision_type,
                     random = list(~ 1 | paper_ID,
@@
 
-# save(MR_lnRR_design, file = here::here("GNM/figures/MR_lnRR_trait.Rdata"))
-```
-
-```{r}
-
-MR_lnRR_design_plot <-
-  orchard_plot(
-    mod_results(
-        MR_lnRR_design,
-      mod = "comparision_type",
-      group = "paper_ID",
-      data = dataset_lnRR_design
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "lnRR")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Experimental Design")
-
-   MR_lnRR_design_plot
-
-```
-
-#### Bird species
-
-(levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)
-
-```{r}
-MR_lnRR_birds <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + bird_species,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_lnRR)
-
-# save(MR_lnRR_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
-```
-
-```{r Plot lnRR meta-regression on birds}
-
-MR_lnRR_birds_plot <-
-  orchard_plot(
-    mod_results(
-       MR_lnRR_birds,
-      mod = "bird_species",
-      group = "paper_ID",
-      data = dataset_lnRR
-    ), xlab ="") +
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
-  labs(x = "",
-       y = "lnRR")+
-  theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
-  ggtitle("Bird Species")
-
- MR_lnRR_birds_plot
-```
-
-#### Type of trait studied
-
-(levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology)
-
-```{r}
-MR_lnRR_trait <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = lnRR_variance,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + trait_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_lnRR)
-
-# save(MR_lnRR_trait, file = here::here("GNM/figures/MR_lnRR_trait.Rdata"))
-```
-
-```{r}
-MR_lnRR_trait_plot <-
-  orchard_plot(
-    mod_results(
-        MR_lnRR_trait,
-      mod = "trait_type",
-      group = "paper_ID",
-      data = dataset_lnRR
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
-  labs(x = "",
-       y = "lnRR")+
-   theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
-  ggtitle("Type of trait studied")
-
-   MR_lnRR_trait_plot
-```
-
-# SMDH Multilevel meta-analysis
-
-```{r}
-# selecting dataset which are not flagged
-dataset_SMDH<-dataset_analysis%>%
-   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
-
-# selecting dataset which are flagged
-SMDH_con_flagged<-dataset_analysis%>%
-   filter(SMDH_sign != "NA")
-
-# selecting dataset without those using 0 as ES because authors reported no effect
-
-SMDH_sin_missingES <- dataset_SMDH %>% 
-   filter(!proxy_comment %in% c("use 0 as ES"))
-
-SMDH_flagged_no_missingES<- SMDH_con_flagged %>% 
-   filter(!proxy_comment %in% c("use 0 as ES"))
-```
-
-### Intercept only model
-
-We are only running these analysis for the fitness proxy labelled "included". Some proxies have been flagged and we will run them in a sensitivity analysis only.
-
-their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
-
-their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
-
-```{r}
-
-VCV_SMDH <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-```
-
-The MLMA using SMDH as the effect size measure incorporate the imputed sampling variance
-
-```{r}
-
-intercept_SMDH<- rma.mv(yi = SMDH_sign, # specify SMDH as the effect size measure;
-                    V = VCV_SMDH, # specify SMDH's sampling variance-covariance matrix;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = dataset_SMDH)
-
-# saving the model
-# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
-
-```
-
-Now looking at the intercept only model
-
-```{r}
-summary(intercept_SMDH)
-predict(intercept_SMDH)
-
-# Then also:
-# # Typical sampling variance (which captures the statistical noise of the data, 
-# # but is rarely reported in the current meta-analytic practice):
-sigma2_v(intercept_SMDH)
-
-# To calculate heterogeneity, these are the functions from orchaRd:
-# # I2, CV and M
-sigma2_main_model_vector <- sum(intercept_SMDH$sigma2)
-I2_main_model_vector <- orchaRd::i2_ml(intercept_SMDH)
-CV_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
-M_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)
-
-# # # Total unstandardized raw variance (i.e. total heterogeneity)
-round(sum(intercept_SMDH$sigma2), 3)
-
-```
-
-### Senstivity Analysis with flagged proxies
-
-```{r}
-
-# Preparing new variance-covariance matrix
-
-VCV_SMDH_flagged <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = SMDH_con_flagged,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-## Running intercept only model
-
-MLMA_SMDH_VCV_flagged<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_flagged, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = SMDH_con_flagged)
-
-# What is the effect now?
-
-summary(MLMA_SMDH_VCV_flagged)
-predict(MLMA_SMDH_VCV_flagged)
-
-```
-
-### Sensitivity Analysis without 0 ES
-
-```{r}
-
-# Preparing new variance-covariance matrix
-
-VCV_SMDH_no_missingES <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = SMDH_sin_missingES,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-## Running intercept only model
-
-MLMA_SMDH_VCV_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_no_missingES, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = SMDH_sin_missingES)
-
-# What is the effect now?
-
-summary(MLMA_SMDH_VCV_no_missingES)
-predict(MLMA_SMDH_VCV_no_missingES)
-
-```
-
-### Sensitivity Analysis with flagged proxies and no missing ES
-
-```{r}
-
-# Preparing new variance-covariance matrix
-
-VCV_SMDH_flagged_no_missingES <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = SMDH_flagged_no_missingES,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-## Running intercept only model
-
-MLMA_SMDH_flagged_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = SMDH_flagged_no_missingES)
-
-# What is the effect now?
-
-summary(MLMA_SMDH_flagged_no_missingES)
-predict(MLMA_SMDH_flagged_no_missingES)
-```
-
-[**Robust variance estimation to guard against arbitary value of sampling correlation**]{.underline} - 'robust()' function from R package 'metafor' (Viechtbauer 2010) using 'CR2' (bias reduced linearization correction) from the R package 'clubSandwich' (Pustejovsky 2024) for small-sample size adjustment.
-
-At the moment, this is not working..
-
-```{r}
-# MLMA_SMDH_RVE<- robust(MLMA_SMDH_VCV,
-#                        cluster = paper_ID,
-#                        clubSandwich = TRUE)
-
-# summary(MLMA_SMDH_RVE)
-# I2_CI <- i2_ml(MLMA_SMDH_RVE) # Relative heterogeneity
-# round(I2_CI,2) # absolute heterogeneity is reported in the summary of the model
-```
-
-### Plot
-
-```{r}
-# MLMA_SMDH
-
-MLMA_SMDH_intercept_only_plot <-
-  orchard_plot(
-    mod_results(
-      intercept_SMDH,
-      mod = "1",
-      group = "paper_ID",
-      data = dataset_lnRR
-    ),
-    xlab = "Effect Size SMDH") +
-  scale_fill_manual(values="darkgreen") +
-  scale_colour_manual(values="darkgreen")+
-  theme(legend.direction="horizontal", legend.title = element_text(size =8),
-        legend.text = element_text(size = 10), 
-        axis.title = element_text(size = 15),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_blank()) +
-  labs(
-    x = "",
-    y = "SMDH"
-  )+
-  ggtitle("Main effect of GNM on fitness using VCV Matrix")
-
-MLMA_SMDH_intercept_only_plot
-
-```
-
-## Unimoderator multilevel meta-regressions
-
-#### Hypothesis
-
-To address our secondary questions "Does the addition of green nest material by birds increase their reproductive success?
-(Courtship hypothesis)" and "Does the addition of green nest material have protective effects and health benefits for the nestlings?
-(Parental care hypothesis)", we will make use of the unimoderator multilevel meta-regressions hypothesis type (levels: CH, PCH, Both) as the moderator.
-
-```{r}
-MR_SMDH_hypothesis <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + Hypothesis,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_SMDH)
-
-# save(MR_SMDH_hypothesis, file = here::here("GNM/figures/MR_lnRR_hypothesis.Rdata"))
-```
-
-```{r Plot meta-regression on hypothesis SMDH}
-
- MR_SMDH_hypothesis_plot <-
-  orchard_plot(
-    mod_results(
-       MR_SMDH_hypothesis,
-      mod = "Hypothesis",
-      group = "paper_ID",
-      data = dataset_SMDH
-    ), xlab ="") +
-  scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "SMDH")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Different Hypothesis")
-
-  MR_SMDH_hypothesis_plot
-```
-
-#### Exploratory Analysis
-
-For our exploratory analyses (see section Exploratory Analyses), we will run unimoderator multilevel meta-regressions using the following moderators:
-
-#### Type of parasites
-
-(levels: arthropods, micro-organisms)
-
-```{r Types of parasite SMDH}
-# This analysis only includes dataset that has a proxy relating to parasite or pathogen
-dataset_SMDH_parasite <- dataset_SMDH%>%
-  filter(trait_type == "Parasitic_and_pathogenic")
-VCV_SMDH_parasite <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH_parasite,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
- MR_SMDH_parasite <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + parasite_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                   test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_SMDH_parasite)
-
- # Warning: 4 rows with NAs omitted from model fitting.
- # Check what rows are these..
-
- # save( MR_lnRR_parasite, file = here::here("GNM/figures/ MR_lnRR_parasite.Rdata"))
-```
-
-```{r}
- MR_SMDH_parasite_plot <-
-  orchard_plot(
-    mod_results(
-        MR_SMDH_parasite,
-      mod = "parasite_type",
-      group = "paper_ID",
-      data = dataset_SMDH_parasite
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "SMDH")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Parasite_type")
-
-   MR_SMDH_parasite_plot
-```
-
-2\. Time of addition of green nest material (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).
-
-#### Type of experimental design
-
-(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).
-
-```{r}
+saveRDS(lnRR_design, file = here::here("model/lnRR_design.rds"))
+
 # This analysis only includes dataset that has a proxy relating to comaparision type
@@
                   )
-MR_SMDH_design <-
+SMDH_design <-
   metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
@@
 
-# save(MR_SMDH_design, file = here::here("GNM/figures/MR_SMDH_trait.Rdata"))
-```
-
-```{r}
- MR_SMDH_design_plot <-
-  orchard_plot(
-    mod_results(
-        MR_SMDH_design,
-      mod = "comparision_type",
-      group = "paper_ID",
-      data = dataset_SMDH_design
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3")) +
-  labs(x = "",
-       y = "SMDH")+
-  theme(axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1))+
-  ggtitle("Experimental Design")
-
-    MR_SMDH_design_plot
-```
+saveRDS(SMDH_design, file = here::here("model/SMDH_design.rds"))
+```
+
+Let me try to do a sensitivity analysis to see what happens when I remove the control condition of 3 in the overall model since that is expected to not have an effect according to the authors as well..
+i.e.
+it is a double control..
+
+```{r}
+dataset_lnRR_remove3<-dataset_lnRR%>%filter(is.na(comparision_type) | comparision_type!="3")
+
+VCV_lnRR_remove3 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_remove3,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_remove3 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_remove3 ,# specify lnRR's sampling variance;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_remove3 )
+
+## Now for SMDH
+
+dataset_SMDH_remove3<-dataset_SMDH%>%filter(is.na(comparision_type) | comparision_type!="3")
+
+VCV_SMDH_remove3 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_remove3,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_remove3 <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_remove3 ,# specify lnRR's sampling variance;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_remove3 )
+
+summary(SMDH_remove3)
+```
+
+Results remain practically the same irrespective..
 
@@
 ```{r}
-MR_SMDH_birds <-
+lnRR_birds <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + bird_species,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+saveRDS(lnRR_birds, file = here::here("model/lnRR_birds.rds"))
+
+## Now doing this for SMDH
+
+SMDH_birds <-
   metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
@@
 
-# save(MR_SMDH_birds, file = here::here("GNM/figures/MR_SMDH_birds.Rdata"))
-```
-
-```{r Plot SMDH meta-regression on birds}
-
-MR_SMDH_birds_plot <-
-  orchard_plot(
-    mod_results(
-       MR_SMDH_birds,
-      mod = "bird_species",
-      group = "paper_ID",
-      data = dataset_SMDH
-    ), xlab ="") +
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral","grey5")) +
-  labs(x = "",
-       y = "SMDH")+
-  theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
-  ggtitle("Bird Species")
-
- MR_SMDH_birds_plot
+saveRDS(SMDH_birds, file = here::here("model/SMDH_birds.rds"))
 ```
@@
 ```{r}
-MR_SMDH_trait <-
+lnRR_trait <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+saveRDS(lnRR_trait, file = here::here("model/lnRR_trait.rds"))
+
+## Now similarly for SMDH
+
+SMDH_trait <-
   metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = SMDH_variance,# specify lnRR's sampling variance;
+                    V = VCV_SMDH,# specify lnRR's sampling variance;
                     mods = ~ - 1 + trait_type,
@@
 
-# save(MR_SMDH_trait, file = here::here("GNM/figures/MR_SMDH_trait.Rdata"))
-```
-
-```{r}
-MR_SMDH_trait_plot <-
-  orchard_plot(
-    mod_results(
-        MR_SMDH_trait,
-      mod = "trait_type",
-      group = "paper_ID",
-      data = dataset_SMDH
-    ),
-    xlab = "")+
-     scale_colour_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
-  scale_fill_manual(values = c("darkorange", "lightgoldenrod3", "mediumpurple4", "palegreen3","brown4","lightcoral")) +
-  labs(x = "",
-       y = "SMDH")+
-   theme(axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+
-  ggtitle("Type of trait studied")
-
-   MR_SMDH_trait_plot
+saveRDS(SMDH_trait, file = here::here("model/SMDH_trait.rds"))
 ```
@@
 We will run several sensitivity analyses using the same random effect structure as described above aimed at ensuring the robustness of our results.
-
-1.  We will re-run all our meta-analyses and meta-regressions only using effect sizes calculated from means, SDs, and ns (i.e., excluding any effect sizes calculated from inferential statistics)
-
-2.
-For the overall effect size (i.e., the meta-analytical mean), we will run the bivariate multilevel meta-analytic model suggested by Yang et al.
-(2024), which models both lnRR and SMD(H) simultaneously (i.e., including them both as response variables and estimating their correlation; random).
-
-```{r}
-dataset_bivariate <- data.frame(paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
-                      Observation_ID = c(dataset_lnRR$Observation_ID, dataset_SMDH$Observation_ID),
-                      ES = c(dataset_lnRR$lnRR_sign, dataset_SMDH$SMDH_sign),
-                      V_ES = c(dataset_lnRR$lnRR_variance, dataset_SMDH$SMDH_variance),
-                      ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMD", nrow(dataset_SMDH)))
-                      )
-
-VCV <- vcalc(vi = V_ES, # sampling variances of lnRR and SMD that are correlated within the same study;
-             cluster = paper_ID, # study identity;
-             type = ES_measure, # different types of effect size measures underlying the observed effect sizes;
-             data = dataset_bivariate, # the long format data frame;
-             rho = 0.5, # assuming that the effect sizes within the same study are correlated with rho = 0.5.
-             nearpd = TRUE # specify whether impose the non positive definite VCV matrix (not invertible) to the nearest positive semi-definite matrix 
-             )
-
-BMLMA <- rma.mv(yi = ES, # specify the effect size estimate (the variable ES in our case);
-                V = VCV, # specify the imputed variance-covariance matrix;
-                mods = ~ ES_measure - 1, # specify the variable "ES_measure" indicating the types of effect size measures;
-                random = list(~ ES_measure | paper_ID, 
-                              ~ ES_measure | Observation_ID), # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
-                struct = "UN", # impose an unstructured variance-covariance of the study-specific random effects;
-                test = "t", # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
-                method = "REML", # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
-                data = dataset_bivariate, # the long format dataset
-                sparse = T
-               )
-
-```
 

### 2025-05-08 docs/notebook/tables.qmd
Incorporated changes for methods

---
title: ""
---

## Table: Sensitivity analysis for intercept only model

```{r}
#| label: SA_intercept_only_table

pacman::p_load(gt,dplyr,metafor)

# Loading the models including flagged proxies
SA_lnRR_flagged<-readRDS(here::here("sensitivity_analysis/SA_lnRR_flagged.rds"))
SA_SMDH_flagged<-readRDS(here::here("sensitivity_analysis/SA_SMDH_flagged.rds"))

# Loading the models without data for those using 0 as ES because authors reported no effect
SA_lnRR_no_missingES<-readRDS(here::here("sensitivity_analysis/SA_lnRR_no_missingES.rds"))
SA_SMDH_no_missingES<-readRDS(here::here("sensitivity_analysis/SA_SMDH_no_missingES.rds"))

# Loading the models without data for those using 0 as ES because authors reported no effect and including flagged proxies
SA_lnRR_flagged_no_missingES<-readRDS(here::here("sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
SA_SMDH_flagged_no_missingES<-readRDS(here::here("sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))

# Loading the model for SMDH without inferential statistics. There is none for lnRR because we can only uses means and deviation to estimate lnRR
SA_SMDH_no_inferential<-readRDS(here::here("sensitivity_analysis/SA_SMDH_no_inferential.rds"))

# Now let's build the table

SA_intercept_only <- tibble::tibble(
  effect_size = c("lnRR","lnRR","lnRR","SMDH","SMDH","SMDH","SMDH"),
  data_used = c("Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),

  Estimate = c(SA_lnRR_flagged$b[1],
               SA_lnRR_no_missingES$b[1],
               SA_lnRR_flagged_no_missingES$b[1],
               SA_SMDH_flagged$b[1],
               SA_SMDH_no_missingES$b[1],
               SA_SMDH_flagged_no_missingES$b[1],
               SA_SMDH_no_inferential$b[1]),

  CI_Lower = c(SA_lnRR_flagged$ci.lb,
               SA_lnRR_no_missingES$ci.lb,
               SA_lnRR_flagged_no_missingES$ci.lb,
               SA_SMDH_flagged$ci.lb,
               SA_SMDH_no_missingES$ci.lb,
               SA_SMDH_flagged_no_missingES$ci.lb,
               SA_SMDH_no_inferential$ci.lb),

  CI_Upper = c(SA_lnRR_flagged$ci.ub,
               SA_lnRR_no_missingES$ci.ub,
               SA_lnRR_flagged_no_missingES$ci.ub,
               SA_SMDH_flagged$ci.ub,
               SA_SMDH_no_missingES$ci.ub,
               SA_SMDH_flagged_no_missingES$ci.ub,
               SA_SMDH_no_inferential$ci.ub),

  PI_Lower = c(predict(SA_lnRR_flagged)$pi.lb,
               predict(SA_lnRR_no_missingES)$pi.lb,
               predict(SA_lnRR_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged)$pi.lb,
               predict(SA_SMDH_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_no_inferential)$pi.lb),

  PI_Upper = c(predict(SA_lnRR_flagged)$pi.ub,
               predict(SA_lnRR_no_missingES)$pi.ub,
               predict(SA_lnRR_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged)$pi.ub,
               predict(SA_SMDH_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_no_inferential)$pi.ub),

  P_value = c(SA_lnRR_flagged$pval,
              SA_lnRR_no_missingES$pval,
              SA_lnRR_flagged_no_missingES$pval,
              SA_SMDH_flagged$pval,
              SA_SMDH_no_missingES$pval,
              SA_SMDH_flagged_no_missingES$pval,
              SA_SMDH_no_inferential$pval),

  Q_value = c(SA_lnRR_flagged$QE,
              SA_lnRR_no_missingES$QE,
              SA_lnRR_flagged_no_missingES$QE,
              SA_SMDH_flagged$QE,
              SA_SMDH_no_missingES$QE,
              SA_SMDH_flagged_no_missingES$QE,
              SA_SMDH_no_inferential$QE),

  k_effect_sizes = c(SA_lnRR_flagged$k,
        SA_lnRR_no_missingES$k,
        SA_lnRR_flagged_no_missingES$k,
        SA_SMDH_flagged$k,
        SA_SMDH_no_missingES$k,
        SA_SMDH_flagged_no_missingES$k,
        SA_SMDH_no_inferential$k),

  n_studies = c(length(SA_lnRR_flagged$s.levels.f[[1]]),
                      length(SA_lnRR_no_missingES$s.levels.f[[1]]),
                      length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged$s.levels.f[[1]]),
                      length(SA_SMDH_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_no_inferential$s.levels.f[[1]])
))

# Combine CI and PI into a single column each for compactness
SA_intercept_only <- SA_intercept_only %>%
  mutate(
    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
    P_value = scales::pvalue(P_value),
    Q_value = sprintf("%.2f", Q_value)
  ) %>%
  select(
    effect_size,
    data_used,
    Estimate,
    CI,
    PI,
    P_value,
    Q_value,
    k_effect_sizes,
    n_studies
  )

# Let's make this table pretty
SA_intercept_only<-SA_intercept_only%>%
  gt()%>%
  tab_options(
    table.font.size = px(12),
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    heading.title.font.size = px(14),
    heading.subtitle.font.size = px(12),
    column_labels.font.weight = "bold"
  ) %>%
  tab_header(
    title = md("**Summary of Sensitivity Analyses for lnRR and SMDH Intercept-only models**")
  ) %>%
  cols_label(
    effect_size = "Effect Size",
    data_used = "Data used in model",
    Estimate = "Estimate",
    CI = "95% CI",
    PI = "95% PI",
    P_value = "P-value",
    Q_value = "Q value",
    k_effect_sizes = "k (No. of Effect Sizes)",
    n_studies = "n (No. of Studies)"
  ) %>%
  fmt_number(
    columns = c(Estimate),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 14,
    table.border.top.width = px(2),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  opt_table_outline()

#saving as a docx file
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
```

## Table: Output from meta-regressions

```{r}

pacman::p_load(gt, dplyr, broom, metafor, purrr, stringr)

# Loading models for experimental design
lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

# Loading models for parasite type
lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

# Loading models for time of green nest material addition
lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))

# Loading models for the type of trait studied
lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))

# Loading models for the bird species studied
lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))

```

### 2025-05-08 notebook/figures.qmd
Incorporated changes for methods

---
title: "Figures and Plots"
---

# Intercept only model

Orchard plot for overall effect of green nest material on fitness using lnRR and SMDH

```{r orchard plot for intercept only models}
devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
pacman::p_load(here,tidyverse,metafor,orchaRd,patchwork,cowplot)

# Loading models for SMDH and lnRR

intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))

# Plot for lnRR
intercept_lnRR_plot <- orchard_plot(intercept_lnRR,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.5,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.3,
                                    xlab = "Effect size (Log Response Ratio- lnRR)",
                                    colour = "#218833",
                                    fill = TRUE) +
  scale_fill_manual(values = "#218833") +
  scale_colour_manual(values = "#218833") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.5,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.3,
                                    xlab = "Effect size (Standardized Mean Difference- SMDH)",
                                    colour = "#895129",
                                    fill = TRUE) +
  scale_fill_manual(values = "#895129") +
  scale_colour_manual(values = "#895129") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept <- intercept_lnRR_plot / intercept_SMDH_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 250, width = 400, units = "mm", dpi = 600)
```

# Hypothesis meta-regression

```{r orchard plot hypothesis meta-regression}

# Loading models for SMDH and lnRR

lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))

# Plot lnRR meta-regression on hypothesis

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(
      lnRR_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("#895129", "mediumpurple4", "#218833")) +
  scale_fill_manual(values = c("#895129", "mediumpurple4", "#218833")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1)
  )

# Plot SMDH meta-regression on hypothesis

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("#895129", "mediumpurple4", "#218833")) +
  scale_fill_manual(values = c("#895129", "mediumpurple4", "#218833")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 90, vjust = 0.5, hjust = 1)
  )

# Combine using patchwork
Figure_hypothesis <- lnRR_hypothesis_plot + SMDH_hypothesis_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 150, width = 400, units = "mm", dpi = 600)
```

# Exploratory Analysis

## Parasite Type

```{r orchard plot parasite type meta-regression}

# Loading models for SMDH and lnRR

lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

lnRR_parasite_plot <-
  orchard_plot(mod_results(
      lnRR_parasite,
      mod = "parasite_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("#895129", "#218833")) +
  scale_fill_manual(values = c("#895129",  "#218833")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    # legend.title = element_text(size = 7),
    # legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_parasite_plot <-
  orchard_plot(mod_results(
      SMDH_parasite,
      mod = "parasite_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("#895129", "#218833")) +
  scale_fill_manual(values = c("#895129",  "#218833")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    # legend.title = element_text(size = 7),
    # legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

## Bird Species

```{r orchard plot bird species meta-regression}

# Loading models for SMDH and lnRR

lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))

lnRR_birds_plot <-
  orchard_plot(mod_results(
      lnRR_birds,
      mod = "bird_species",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  scale_fill_manual(values = c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    # legend.title = element_text(size = 7),
    # legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_birds_plot <-
  orchard_plot(mod_results(
      SMDH_birds,
      mod = "bird_species",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values =  c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  scale_fill_manual(values =  c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    # legend.title = element_text(size = 7),
    # legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle =0, vjust = 0.5, hjust = 1)
  )

```

## Trait studied

```{r orchard plot trait-studied meta-regression}

# Loading models for SMDH and lnRR

lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))

lnRR_trait_plot <-
  orchard_plot(mod_results(
      lnRR_trait,
      mod = "trait_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  scale_fill_manual(values = c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_trait_plot <-
  orchard_plot(mod_results(
      SMDH_trait,
      mod = "trait_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values =  c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  scale_fill_manual(values =  c("darkorange2", "lightgoldenrod3", "mediumpurple4", "#218833","#895129","lightcoral","grey5")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

### Combined plot

```{r combining meta-regression plots, no effect}

## I am going to remove the y ticks from the SMDH plots to make it smaller..
SMDH_parasite_plot <- SMDH_parasite_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_birds_plot <- SMDH_birds_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_trait_plot <- SMDH_trait_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_parasite_birds_trait <- ((lnRR_parasite_plot + SMDH_parasite_plot) / 
                                  (lnRR_birds_plot + SMDH_birds_plot) / 
                                  (lnRR_trait_plot + SMDH_trait_plot)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_parasite_birds_trait.png"), plot = Figure_parasite_birds_trait, height = 250, width = 400, units = "mm", dpi = 600)

```

## Time of green nest material addition

```{r orchard plot time of gnm addition meta-regression}

# Loading models for SMDH and lnRR

lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))

lnRR_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      lnRR_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg laying", "Before egg laying", "Continous addition"))

SMDH_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      SMDH_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

## Experimental Design

```{r orchard plot experimental design meta-regression}

# Loading models for SMDH and lnRR

lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","Aromatic Vs. Blank", "Non-Aromatic Vs. Blank"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ), xlab ="") +
  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
  labs(x = "",
       y = "SMDH")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

### Combined plot

```{r combining meta-regression plots, effect}

## I am going to remove the y ticks from the SMDH plots to make it smaller..
SMDH_design_plot <- SMDH_design_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 300, width = 400, units = "mm", dpi = 600)

```

##

### 2025-05-11 docs/manuscript_GNM.qmd
Results for meta-regressions completed

@@
 pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
-
+source(here::here("functions/extractor_metareg.R"))
 ```
@@
 
-```{r}
+```{r review-results}
 dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")
@@
 
-**Overall effect of green nest material on fitness proxies**
+## **Overall effect of green nest material on fitness proxies**
 
-```{r}
+```{r overall-results}
 intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
@@
 The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH1~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_lnRR)[1]),2)` and M1~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
+Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH2~total~ = `{r} round(as.double(orchaRd::cvh2_ml(intercept_lnRR)[1]),2)` and M2~total =~ `{r} round(as.double(orchaRd::m2_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
 The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high.
-Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2023; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
+Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2024a; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
 
@@
 
-**Mechanisms behind green nest material effects**
+## **Hypotheses explaining the effect of green nest material**
 
-```{r}
+```{r hypotheses-results}
 lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
 SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))
+
+summary_lnRR_hypothesis<-extractor_metareg(lnRR_hypothesis,"Hypothesis")
+summary_SMDH_hypothesis<-extractor_metareg(SMDH_hypothesis,"Hypothesis")
 ```
 
-Using the multilevel meta-regressions with hypothesis type as a moderator, we found no clear support for either of the proposed mechanism [@fig-hypothesis].
-There was a small positive but non-significant effect of green nest material on reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[2], digits = 3, format = "f"))` and SMDH~courtship~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[2], digits = 3, format = "f"))`\].
-We found even smaller, non-significant effect of green nest material on protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[3], digits = 3, format = "f"))` and SMDH~parental_care~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[3], digits = 3, format = "f"))`\].
-In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either mechanisms, we found a small positive effect \[lnRR~both~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[1], digits = 3, format = "f"))` and SMDH~both~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[1], digits = 3, format = "f"))`\].
-The moderator explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+Using the multilevel meta-regressions, we found no clear support for the proposed hypotheses in the literature ([@fig-hypothesis]).
+There is a small positive but non-significant effect of green nest material on fitness related to reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMDH~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
+We found even smaller, non-significant effect of green nest material on fitness related to protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ =`{r} summary_lnRR_hypothesis$estimate[3]`, CI: `{r} summary_lnRR_hypothesis$CI[3]`, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMDH~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
+In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either hypotheses, we found a small positive effect which was significant only in the case of SMDH \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMDH~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
+The moderator explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
 
@@
 log response ratio (lnRR) and B.
-Standardised mean difference (SMDH).
+Standardized mean difference (SMDH).
 Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
@@
 ```{r}
-# Loading models for experimental design
-lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
-SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
-
 # Loading models for parasite type
@@
 SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
+
+summary_lnRR_parasite<-extractor_metareg(lnRR_parasite,"parasite_type")
+summary_SMDH_parasite<-extractor_metareg(SMDH_parasite,"parasite_type")
+
+# Loading models for the bird species studied
+lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+
+summary_lnRR_birds<-extractor_metareg(lnRR_birds,"bird_species")
+summary_SMDH_birds<-extractor_metareg(SMDH_birds,"bird_species")
+
+# Loading models for the type of trait studied
+lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
+
+summary_lnRR_trait<-extractor_metareg(lnRR_trait,"trait_type")
+summary_SMDH_trait<-extractor_metareg(SMDH_trait,"trait_type")
 
@@
 
-# Loading models for the type of trait studied
-lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
-SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
+summary_lnRR_time_gnm_addition<- extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition")
+summary_SMDH_time_gnm_addition<- extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition")
 
-# Loading models for the bird species studied
-lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
-SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+# Loading models for experimental design
+lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
 
+summary_lnRR_design<- extractor_metareg(lnRR_design,"comparision_type")
+summary_SMDH_design<- extractor_metareg(SMDH_design,"comparision_type")
 ```
 
-There was no evidence that the effect of green nest material on parasite or pathogen load differed between arthropods and micro-organisms \[[@supp-fig-MR-non-sig]A-B; lnRR~arthropods~ = `{r} as.double(formatC(coef(lnRR_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[1], digits = 3, format = "f"))` and SMDH~arthropods~ = `{r} as.double(formatC(coef(SMDH_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[1], digits = 3, format = "f"))`; lnRR~micro-organisms~ = `{r} as.double(formatC(coef(lnRR_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[2], digits = 3, format = "f"))` and SMDH~micro-organisms~ = `{r} as.double(formatC(coef(SMDH_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[2], digits = 3, format = "f"))`\].
-The type of parasite or pathogen explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+The effect of green nest material on fitness varied largely by the experimental design.
+The experimental design comparison between no added material and aromatic material showed a positive and statistically significant effect on fitness \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\].
+The experimental design comparison between no added material and non-aromatic material showed a negative effect on fitness, which was significant in lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value = `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
+Contrary to our expectation, the non-aromatic and aromatic green nest material comparison showed small negative non-significant effect on fitness \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMDH~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
+Experimental design comparison type also explained a large proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
 
-The meta-regression using bird species as a moderator showed no significantly different effect of green nest material on fitness depending on the bird being studied \[[@supp-fig-MR-non-sig]C-D\]; .
-However, it explained some heterogeneity in the effect sizes ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+When green nest material was added continuously throughout the nesting phase, the effect of it on fitness was positive and statistically significant in the case of SMDH \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMDH~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
+Addition after egg hatching showed a positive but non-significant effect on fitness and before egg hatching had a near zero non-significant effect [\@fig-MR](C-D); Table X\].
+Timing of addition of green nest material explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
 
-We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+![](figures/Figure_design_time_gnm_addition.png){#fig-MR}
 
-To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
+There is positive non-significant effect of increased green nest material on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
+\[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
+The type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
 
-We explored the impact of methodological differences on the relationship between green nest material and fitness.
-To understand the effect of type of experimental design (i.e.
-whether the authors compared - non-aromatic vs.
-aromatic, no added material vs.
-aromatic, no added material vs.
-non-aromatic), we ran a meta-regression with type of experimental design as the moderator.
+Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
+All confidence and prediction intervals overlapped zero.
+However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+
+Among different types of fitness trait, only morphological trait showed positive effect of green nest material on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
+Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
+All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
+Trait type accounted for a small amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+
+## **Publication Bias**
 
@@
 
-![](figures/Figure_parasite_birds_trait.png){#supp-fig-MR-non-sig}
+```{r results='asis'}
+cat(readLines("tables/EA_MLMR_table.html"), sep ="\n")
+```
+
+![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
 

### 2025-05-11 manuscript_GNM.qmd
Results for meta-regressions completed

--- 2025-02-27 manuscript_GNM.qmd
@@
 ```{r Setup, include=FALSE, echo=FALSE}
-
-pacman::p_load(readr)
-
+devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
+pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
+source(here::here("functions/extractor_metareg.R"))
 ```
 
-# Methods (\~2200 words)
+```{r load search data, include=FALSE, echo=FALSE, message= FALSE}
 
-## Registration and Reporting
+# Own reference list
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv")
 
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details study objective, a priori hypothesis and predictions, methods and planned data analysis.
-Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist).
-All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
-
-## Study selection and eligibility criteria
-
-```{r load search data, include=FALSE, echo=FALSE}
-
+# Systematic search and abstract screening
 unique_reference_list <- read_csv("data/unique_reference_list.csv")
@@
 
-We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022.
-The search query was designed in three blocks to included terms for predictor/treatment ("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and only experimental studies ("experiment\*" OR "manipulat\*") (for complete search string tailored to specific database see @figsupp-string).
-We searched the title, abstract and keywords in English-language only with no restrictions on publication date or study type.
+# Methods
+
+## Registration and Reporting
+
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details the study's objectives, a priori hypotheses and predictions, methods and planned data analyses.
+Unless stated otherwise, we adhered to the registered protocol.
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
+
+## Information source and search
+
+We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022.
+The keyword search query was designed as a three-block query to included terms related to the predictor/treatment (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), our population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit it to only experimental studies only ("experiment\*" OR "manipulat\*").
+The complete search strings tailored to each specific platform are provided in @figsupp-string.
+We searched through titles, abstracts and keywords in English-language only with no restrictions on publication date or study type.
+We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used the R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
-We validated our search using an initial library of 15 key articles (\@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
 
-All title and abstract screening were screened independently by atleast two screeners (\~66% each by SD, TR, JMGS) following a pre-designed decision tree (@figsupp-decision-tree) in revtools.
-We included all studies on birds that experimentally manipulated the green nest material (including aromatics or herbs).
-`{r} nrow(selected_abstract_screening)` articles passed title and abstract screening and further evaluated in a fulltext screening by a single screener (\~33% each by SD, TR, JMGS) and double checked by another.
-We used the same criteria as above with an additional evaluation of whether the variable of interest in the article was a fitness proxy.
-`{r} nrow(excluded_fulltext)` articles were excluded and all conflicts in screening decision (\~1% for title and abstract screening and none for fulltext screening) were resolved through discussion.
+## Eligibility criteria
 
-We repeated our search using the same search string on 12.08.2024 and found `{r} nrow(full_reference_before_deduplication_repeat)` additional articles.
-After deduplicating, SD screened the title and abstract for the `{r} nrow(unique_reference_list_repeat)` unique articles using the same decision tree.
-We found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` article by updating our search.
-In addition, we identified `{r}  nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` articles through other sources that were not a part of our search.
-These studies met our inclusion criteria and were added to our meta-analysis.
-The exact number of screened and included studies along with reason of exclusion are shown in @figsupp-prisma-flowchart.
+All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree (@figsupp-decision-tree).
+We included all studies on birds that experimentally manipulated the green nest material (both aromatics or herbs).
+`{r} nrow(selected_abstract_screening)` articles passed the title-and-abstract screening and were further evaluated during the full-text screening.
+Each article was screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
+We used the same criteria as above (see @figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
+`{r} nrow(excluded_fulltext)` articles were excluded.
+All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
+
+To update our systematic lietrature search, we repeated our search on 12.08.2024.
+This updated search found `{r} nrow(unique_reference_list_repeat)` unique articles after removing ``` {r} nrow(full_reference_before_deduplication_repeat)-``nrow(unique_reference_list_repeat) ``` duplicates.
+Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article.
+Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles.
+In all, X <!--# Fill the no.
+of articles that are included --> articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
 
@@
 
-### Data collection process
+```{r load data extraction, include=FALSE, echo=FALSE}
 
-Data was extracted evenly by one of the three authors (\~33% each SD, TR and JMGS) and was checked by another to ensure correctness of the data.
-We extracted the primary data (i.e., measures of central tendency and variance) from text whenever possible.
-In cases where primary data was only available in figures (such as boxplots), we used 'metaDigitise' v.1.0.1 (@pick2018).
-If primary data was not available, we extracted any inferential statistics (t-test, F-statistics) that could be used to calculate an effect size.
-In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the raw data.
+merged_data_extraction <- read_csv("data/03_data_cleaning/merged_data_extraction.csv", show_col_types = F)
 
-To obtain any missing data and to locate any grey literature, we wrote to the corresponding author of the articles that passed fulltext screening using a standardized email template (\@figsupp-email).
-We obtained one unpublished dataset ...
-\[calculate estimates here\]..
-Another unpublished dataset was provided by a co-author of this paper.
-We extracted data for `{r}  nrow(selected_abstract_screening_repeat) + (nrow(selected_abstract_screening)-nrow(excluded_fulltext))` articles and 2 unpublished studies.
+dataset_after_cleaning <- merged_data_extraction %>% filter(fulltext_screening!="excluded")
+included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
 
-<!--# Fix the code for generating this number later by using the data file directly to calculate the number of article -->
+# Numbers for extraction ID
+data_extractors <- merged_data_extraction %>%
+     distinct(paper_ID, .keep_all = TRUE) %>%
+     select(paper_ID, extractor_ID) %>%
+     mutate(extractor_ID = case_when(
+    extractor_ID == "JS/SD/TR" ~ "TR/JMGS/SD",
+    TRUE ~ extractor_ID)) %>%
+     group_by(extractor_ID) %>%
+     summarise(total_papers = n(), .groups = "drop")
 
-### Extracted variables
+excluded_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="exclude")
+SAonly_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="senstivity-analysis" | proxy_decision=="sensitivity-analysis")
+```
 
-We extracted mean, variance and sample size for a control-treatment pairwise comparison.
-Controls included non-aromatic materials (e.g., grass, moss), lesser amounts of aromatic material, or no material.
+The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
+We extracted the primary data (i.e., measures of central tendency, variance and sample size) from text whenever possible.
+In cases where primary data was only available in figures (e.g., boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
+If primary data was not available, we extracted any inferential statistics (t value, F value) that could be transformed into an effect size.
+In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the provided raw data.
+When data was presented in different sources (e.g.
+in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).
+
+To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
+unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
+We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
+All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
+In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
+In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
+
+We extracted the means, variances and sample size for each control-treatment pairwise comparison.
+Controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material, or no material at all.
 Treatments consisted of aromatic materials added by authors, birds, or both.
@@
 We recorded the type of comparison being made as a moderator.
-Each pairwise comparison was given a unique Observation ID, a paper ID (for each article reporting this data), an experiment ID (for estimates coming from the same experimental setup), a group ID (for estimates from the same group of individual) and a repeated trait ID (for estimates that were measured repeatedly across time).
 
-For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, trait measured) and information about the extracted data (location or source of the data recorded).
-We categorized the trait measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology.
-In cases where the trait measured was a type of parasite or pathogen, we categorised the parasite studied ino arthropods or micro-organisms.
+For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and information about the extracted data (location or source of the data recorded).
+We categorized the fitness proxy measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load and phenology.
+For parasites or pathogens, we categorised them into arthropods or micro-organisms.
 For a complete list of variables extracted see @figsupp-variables .
+We did not include some traits in all our analyses becaause it was unclear how they related to fitness (k=`{r} nrow(excluded_proxies)` , n=`{r} length(unique(excluded_proxies$paper_ID))`;see @figsupp-excluded-proxies for the list and reason of exclusion).
+We also had to exclude some effect sizes (n=?, k=?) because of the low sample size per group (less than x).
 
@@
 
-Using the information we extracted from the articles, we calculated two effect sizes,along with their associated sampling variance, for each pairwise comparison-log response ratio (hereafter lnRR) and standardised mean difference with heteroscedasticity correction (hereafter SMDH).
+```{r load effect size, include=FALSE, echo=FALSE}
 
--   How many papers in final meta-analysis and how many effect size.
+inferential_stats<-dataset_after_cleaning%>%filter(statistics_type=="t-test"|statistics_type=="ANCOVA")
 
-### Meta-analysis and meta-regressions
+contingency_table<-dataset_after_cleaning%>%filter(proxy_decision=="contingency table")
 
--   main effect model
+no_ES<-dataset_after_cleaning%>%filter(proxy_comment == "use 0 as ES")
 
--   meta-regressions for testing hypothesis
+negative_lnRR<-dataset_after_cleaning%>%
+  filter(measure_central_tendency_experiment<=0 | measure_central_tendency_control<=0)
 
--   meta-regressions for exploratory analyses
+```
 
-Senstivity analysis and Publication Bias Test
+We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` (@metafor).
+We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that positive values indicate the 'fitness' value increased in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the effect size sign was inverted to ensure comparability across all fitness proxies.
+In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
 
-### Deviations from registration
+For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k=`{r} nrow(inferential_stats)`, n=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019.
+For dichotomous variables (e.g., number of successful nests, k= `{r} nrow(contingency_table)`, n= `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k=`{r} nrow(negative_lnRR)`, n=`{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k=?, n=?) subset is smaller than that of SMDH (k=?,n=?).
+
+When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size, whenever possible to reduce the effect of genetic relatedness non-independence.
+In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
+For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k=`{r} nrow(no_ES)`, n=`{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparision and imputed its SD using the missing-case approach described in @nakagawa2022.
+
+## Data Analysis
+
+We performed all analyses in R version 4.3.0 (@positteam2023).
+All multilevel meta-analytical models and meta-regressions were fit using `metafor v.4.8-0` (@metafor).
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the `vcalc` function from `metafor`.
+(See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
+
+We considered the following levels of non-independence for our analyses: (a) multiple effect sizes collected from same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) some sub-populations (Experiment ID; e.g.
+birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID; eg.
+males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) some traits were collected on the same group of animals repeatedly (Repeated trait ID; e.g.
+chick mass on day 7, 14 and 21).
+
+Unless stated otherwise, we fitted the following random effects in all our models to account for non-independence: Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
+Our random effect structure deviated from our pre-registration since, initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
+However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution i.e.
+Experiment ID.
+Additionally, few effect sizes were measured repeatedly, making the Repeated trait ID almost identical to the observation-level random effect (Observation ID), so we excluded it (@figsupp-random-effect).
+Last, we decided to add Population ID, since we noticed that several studies were performed in the same geographical locations.
+
+### Meta-analytic models: biological predictions
+
+To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMDH.
+Thus, throughout, we fitted two separate sets of model for each effect size.
+First, we fitted multilevel intercept-only meta-analytical model to test the overall effect, its uncertainty and heterogeneity.
+We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k=`{r} nrow(SAonly_proxies)` , n=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies).
+For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
+
+<!--# You have to correct the numbers for contingency table. It does not include the one data point from unpublished results -->
+
+<!--# Check what is MLMA-excluded and figsupp-SAonly-proxies for figures and decide which one makes more sense to include/exclude?? -->
+
+To test the relative importance of the two main hypotheses suggested for green nest material: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators (@nakagawa2012).
+
+### Meta-analytic models: exploratory analyses
+
+We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
+To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (n=?, k=?).
+We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
+We also ran a meta-regression with with the entire dataset set using bird species as a moderator (levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris, Parus major, Passer cinnamomeus, Buteo buteo) to understand if the effect of green nest material on fitness depended on the system being studied.
+To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
+We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We explored the impact of methodological differences on the relationship between green nest material and fitness.
+To understand the effect of type of experimental design (i.e.
+whether the authors compared - non-aromatic vs.
+aromatic, no added material vs.
+aromatic, no added material vs.
+non-aromatic), we ran a meta-regression with the type of experimental design as a moderator.
+
+### Publication Bias Test
+
+Publication bias occurs when a subset of research findings, most often statistically non-significant ones, are less likely to be published or being published as compared to the rest.
+We tested for evidence of publication bias, both small-study and decline effects following @nakagawa2021.
+Publication bias tests were performed for both lnRR and SMDH separately, and using the same random effect structure as reported above.
+To test for small-study effects, we ran a multilevel meta-regression, using the inverse of the effective sample size as a moderator.
+To test for decline effects (also known as time-lag bias; @sanchez-tojar2018), we ran multilevel meta-regression year of publication (mean-centered) as a moderator.
+
+# Results
+
+```{r review-results}
+dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")
+
+ES_per_study<-dataset_analysis%>%group_by(paper_ID)%>%count(paper_ID)
+
+birds_info<-dataset_analysis%>%group_by(bird_species)%>%count(bird_species)
+birds_info$perc<-(birds_info$n/nrow(dataset_analysis))*100
+```
+
+We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations.
+About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
+Our dataset included two unpublished studies (k=XX effect sizes), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
+The mean (±SD) number of effect sizes per study was `{r} as.numeric(format(mean(ES_per_study$n), digit=3))` ± `{r} as.numeric(format(sd(ES_per_study$n), digit=2))`(range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean sample size per effect size were `{r} median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))` and `{r} as.numeric(format(mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)), digit=3))` respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
+
+## **Overall effect of green nest material on fitness proxies**
+
+```{r overall-results}
+intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
+intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
+bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
+```
+
+Both lnRR and SMDH intercept-only multilevel meta-analyses showed an increase in fitness in the nests with an increase in green nest material compared to control nests; however, the overall effect was only statistically significant for SMDH.
+
+The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
+Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH2~total~ = `{r} round(as.double(orchaRd::cvh2_ml(intercept_lnRR)[1]),2)` and M2~total =~ `{r} round(as.double(orchaRd::m2_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
+The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high.
+Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2024a; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
+
+While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
+While neither intercept was statistically significant, the results strengthens the interpretation that any effect of green nest material on fitness outcomes in likely to be very small at best \[lnRR = `{r} as.double(formatC(coef(bivariate_model)[1], digit = 3, format="f"))`, p-value = `{r} as.double(formatC(bivariate_model$pval[1], digits = 3, format = "f"))` and SMDH = `{r} as.double(formatC(coef(bivariate_model)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(bivariate_model$pval[2], digits = 3, format = "f"))`\].
+
+![Overall effect of green nest material on fitness: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardized mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect width="1059"}
+
+## **Hypotheses explaining the effect of green nest material**
+
+```{r hypotheses-results}
+lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
+SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))
+
+summary_lnRR_hypothesis<-extractor_metareg(lnRR_hypothesis,"Hypothesis")
+summary_SMDH_hypothesis<-extractor_metareg(SMDH_hypothesis,"Hypothesis")
+```
+
+Using the multilevel meta-regressions, we found no clear support for the proposed hypotheses in the literature ([@fig-hypothesis]).
+There is a small positive but non-significant effect of green nest material on fitness related to reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMDH~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
+We found even smaller, non-significant effect of green nest material on fitness related to protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ =`{r} summary_lnRR_hypothesis$estimate[3]`, CI: `{r} summary_lnRR_hypothesis$CI[3]`, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMDH~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
+In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either hypotheses, we found a small positive effect which was significant only in the case of SMDH \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMDH~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
+The moderator explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+
+![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests.
+Orchard plot of the multilevel meta-regression for A.
+log response ratio (lnRR) and B.
+Standardized mean difference (SMDH).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}
+
+## Pre-registered exploratory analyses
+
+```{r}
+# Loading models for parasite type
+lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
+SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
+
+summary_lnRR_parasite<-extractor_metareg(lnRR_parasite,"parasite_type")
+summary_SMDH_parasite<-extractor_metareg(SMDH_parasite,"parasite_type")
+
+# Loading models for the bird species studied
+lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+
+summary_lnRR_birds<-extractor_metareg(lnRR_birds,"bird_species")
+summary_SMDH_birds<-extractor_metareg(SMDH_birds,"bird_species")
+
+# Loading models for the type of trait studied
+lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
+
+summary_lnRR_trait<-extractor_metareg(lnRR_trait,"trait_type")
+summary_SMDH_trait<-extractor_metareg(SMDH_trait,"trait_type")
+
+# Loading models for time of green nest material addition
+lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
+SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
+
+summary_lnRR_time_gnm_addition<- extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition")
+summary_SMDH_time_gnm_addition<- extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition")
+
+# Loading models for experimental design
+lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
+
+summary_lnRR_design<- extractor_metareg(lnRR_design,"comparision_type")
+summary_SMDH_design<- extractor_metareg(SMDH_design,"comparision_type")
+```
+
+The effect of green nest material on fitness varied largely by the experimental design.
+The experimental design comparison between no added material and aromatic material showed a positive and statistically significant effect on fitness \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\].
+The experimental design comparison between no added material and non-aromatic material showed a negative effect on fitness, which was significant in lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value = `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
+Contrary to our expectation, the non-aromatic and aromatic green nest material comparison showed small negative non-significant effect on fitness \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMDH~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
+Experimental design comparison type also explained a large proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
+
+When green nest material was added continuously throughout the nesting phase, the effect of it on fitness was positive and statistically significant in the case of SMDH \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMDH~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
+Addition after egg hatching showed a positive but non-significant effect on fitness and before egg hatching had a near zero non-significant effect [\@fig-MR](C-D); Table X\].
+Timing of addition of green nest material explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
+
+![](figures/Figure_design_time_gnm_addition.png){#fig-MR}
+
+There is positive non-significant effect of increased green nest material on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
+\[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
+The type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+
+Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
+However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+
+Among different types of fitness trait, only morphological trait showed positive effect of green nest material on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
+Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
+All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
+Trait type accounted for a small amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+
+## **Publication Bias**
+
+\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--
 
 ## Supplementary Appendix
+
+```{r results='asis'}
+cat(readLines("tables/SA_intercept_only.html"), sep ="\n")
+```
+
+```{r results='asis'}
+cat(readLines("tables/EA_MLMR_table.html"), sep ="\n")
+```
+
+![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
 

### 2025-05-11 notebook/data_analysis.qmd
Results for meta-regressions completed

@@
 
+## Loading Data for analysis
+
 ```{r setup, warning=FALSE, message=FALSE, echo=F}
@@
 
+# selecting only published dataset
+dataset_lnRR_published<-dataset_lnRR%>%
+  filter(!is.na(year_publication))
+
 # selecting dataset which are flagged
@@
 
-```
-
-## Intercept only models
+## For SMDH
+# selecting dataset which are not flagged
+dataset_SMDH<-dataset_analysis%>%
+   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
+
+# selecting only published dataset
+dataset_SMDH_published<-dataset_SMDH%>%
+  filter(!is.na(year_publication))
+
+# selecting dataset which are flagged
+SMDH_con_flagged<-dataset_analysis%>%
+   filter(SMDH_sign != "NA")
+
+# selecting dataset without those using 0 as ES because authors reported no effect
+
+SMDH_sin_missingES <- dataset_SMDH %>% 
+   filter(!proxy_comment %in% c("use 0 as ES"))
+
+SMDH_flagged_no_missingES<- SMDH_con_flagged %>% 
+   filter(!proxy_comment %in% c("use 0 as ES"))
+
+# selecting dataset which are not flagged but without the SMDH calculated from inferential statistics
+
+SMDH_no_inferential<-dataset_analysis%>%
+  filter(proxy_decision == "include")%>% filter(SMDH_sign != "NA")
+```
+
+# Overall effect : Intercept-only meta-analytic model
 
@@
 
-### Senstivity Analysis with flagged proxies
+## using SMDH
+
+We are only running these analysis for the fitness proxy labelled "included". Some proxies have been flagged and we will run them in a sensitivity analysis only
+
+their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
+
+The MLMA using SMDH as the effect size measure incorporate the imputed sampling variance
+
+```{r intercept-only-model-SMDH}
+
+VCV_SMDH <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+intercept_SMDH<- rma.mv(yi = SMDH_sign, # specify SMDH as the effect size measure;
+                    V = VCV_SMDH, # specify SMDH's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH)
+
+# saving the model
+# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+```
+
+## SMDH-heterogeneity
+
+Now looking at the intercept only model
+
+```{r}
+summary(intercept_SMDH)
+predict(intercept_SMDH)
+
+# Then also:
+# # Typical sampling variance (which captures the statistical noise of the data, 
+# # but is rarely reported in the current meta-analytic practice):
+sigma2_v(intercept_SMDH)
+
+# To calculate heterogeneity, these are the functions from orchaRd:
+# # I2, CV and M
+sigma2_main_model_vector <- sum(intercept_SMDH$sigma2)
+# 0.54, 1.25, and 3.03 for SMD;
+I2_main_model_vector <- orchaRd::i2_ml(intercept_SMDH)
+# 0.78, 0.89, and 0.96 for SMD
+# 0.88, 0.95, and 0.99 for lnRR
+CV_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
+# CVH2 (CVH1) - 1.36 (1.16), 3.76 (1.94), and 12.1 (3.48) for lnRR
+M_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)
+# M2 (M1) - 0.58 (0.54), 0.79 (0.66), and 0.78 for lnRR
+
+# # # Total unstandardized raw variance (i.e. total heterogeneity)
+round(sum(intercept_SMDH$sigma2), 3)
+
+```
+
+## Bivariate Meta-analytical model
+
+For the overall effect size (i.e., the meta-analytical mean), we will run the bivariate multilevel meta-analytic model suggested by Yang et al.
+(2024), which models both lnRR and SMD(H) simultaneously (i.e., including them both as response variables and estimating their correlation; random).
+
+```{r}
+dataset_bivariate <- data.frame(paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
+                      Observation_ID = c(dataset_lnRR$Observation_ID, dataset_SMDH$Observation_ID),
+                      group_ID_coded = c(dataset_lnRR$group_ID_coded, dataset_SMDH$group_ID_coded),
+                      population_ID = c(dataset_lnRR$population_ID, dataset_SMDH$population_ID),
+                      bird_species = c(dataset_lnRR$bird_species, dataset_SMDH$bird_species),
+                      ES = c(dataset_lnRR$lnRR_sign, dataset_SMDH$SMDH_sign),
+                      V_ES = c(dataset_lnRR$lnRR_variance, dataset_SMDH$SMDH_variance),
+                      ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMDH", nrow(dataset_SMDH)))
+                      )
+
+VCV_bivariate <- vcalc(vi = V_ES, # sampling variances of lnRR and SMD that are correlated within the same study;
+             cluster = paper_ID, # study identity;
+             type = ES_measure, # different types of effect size measures underlying the observed effect sizes;
+             data = dataset_bivariate, # the long format data frame;
+             rho = 0.2, # assuming that the effect sizes within the same study are correlated with rho = 0.5.
+             nearpd = TRUE # specify whether impose the non positive definite VCV matrix (not invertible) to the nearest positive semi-definite matrix 
+             )
+
+Bivariate_model <- rma.mv(yi = ES, # specify the effect size estimate (the variable ES in our case);
+                V = VCV_bivariate, # specify the imputed variance-covariance matrix;
+                mods = ~ ES_measure - 1, # specify the variable "ES_measure" indicating the types of effect size measures;
+                random = list(~ ES_measure | paper_ID, 
+                              ~ ES_measure | Observation_ID,
+                              ~ 1 | group_ID_coded,
+                              ~ 1 | population_ID,
+                              ~ 1 | bird_species
+                              ), # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
+                struct = "UN", # impose an unstructured variance-covariance of the study-specific random effects;
+                test = "t", # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
+                method = "REML", # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
+                data = dataset_bivariate, # the long format dataset
+                sparse = T
+               )
+
+saveRDS(Bivariate_model, file = here::here("sensitivity_analysis/bivariate_model.rds"))
+
+summary(Bivariate_model)
+```
+
+```{r WARNING = F}
+pacman::p_load(ellipse)
+ab.l <- matreg(y=2, x=1, R=Bivariate_model$G, cov=TRUE, means=coef(Bivariate_model), n=Bivariate_model$g.levels.comb.k) # fit regression model
+
+xy <- ellipse(Bivariate_model$G, centre=coef(Bivariate_model), level=0.95) # get 95% coverage region
+ellipse_df <- data.frame(x = xy[, 1], y = xy[, 2]) # convert it int dataframe so that we can use ggplot to make a figure
+
+pivot_wider(dataset_bivariate, names_from = ES_measure, values_from = c(ES, V_ES)) %>%
+  ggplot() + 
+  geom_point(aes(x = ES_lnRR, y = ES_SMDH, size = 1/sqrt(V_ES_lnRR)), color = "#1B9E77", alpha = 0.5) + 
+  geom_point(aes(x = coef(Bivariate_model)[1], y = coef(Bivariate_model)[2]), color = "red", size = 2) + 
+  geom_abline(intercept = ab.l$tab$beta[1], slope = ab.l$tab$beta[2]) +
+  geom_path(data = ellipse_df, aes(x = x, y = y), color = "gray50") +
+  #scale_x_continuous(limits = c(-2.5, 2.5)) + 
+  #scale_y_continuous(limits = c(-2.5, 2.5)) + 
+  guides(size = "none") + 
+  labs(x = "lnRR", y = "SMD") + 
+  theme_bw()
+```
+
+There is a very high negative correlation between the two effect sizes.
+This probably is an artifact of the data and not a true correlation.
+If you look at the model summary, the $tau^2$ for lnRR, it is extremely small 0.0008, i.e., there is very little variance.
+This could also be stemming from the fact that the log values in the dataset could be causing this.
+For SMDH on the other hand, the $tau^2$ is 0.1681 that is much larger.
+This difference in the variance estimate itself could be causing this artifact of the model.
+I will only go ahead to present this model as a senstivity analysis because I am not completely convinced by it's robustness.
+
+# Sensitivity Analysis
+
+### Sensitivity Analysis with published data only
 
@@
 
+VCV_lnRR_published <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_lnRR_published<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_published)
+
+# saving the model
+saveRDS(SA_lnRR_published, file = here::here("sensitivity_analysis/SA_lnRR_published.rds"))
+
+# What is the effect now?
+
+summary(SA_lnRR_published)
+predict(SA_lnRR_published)
+
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_published <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_published<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_published)
+
+# saving the model
+saveRDS(SA_SMDH_published, file = here::here("sensitivity_analysis/SA_SMDH_published.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_published)
+predict(SA_SMDH_published)
+
+```
+
+### Sensitivity Analysis with flagged proxies
+
+```{r}
+
+# Preparing new variance-covariance matrix
+
 VCV_lnRR_flagged <- vcalc(vi = lnRR_variance,
@@
 dataset_lnRR_parasite <- dataset_lnRR%>%
-  filter(trait_type == "Parasitic_and_pathogenic")
+  filter(!is.na(parasite_type))%>%
+  mutate(parasite_type=as.factor(parasite_type),
+         paper_ID=as.factor(paper_ID),
+         Observation_ID=as.factor(Observation_ID),
+         group_ID_coded=as.factor(group_ID_coded),
+         bird_species=as.factor(bird_species))
+
 VCV_lnRR_parasite <- vcalc(vi = lnRR_variance,
@@
 
-## Heterogeneity
-
-To understand the sources of variation or heterogeneity,
-
-### For the intercept-only models
-
-we will use the pluralistic approach recently suggested by Yang et al. (2023),
-
-which consists of calculating four metrics of heterogeneity (σ2, I2, CV, M) to comprehensively understand both total and random-effect specific heterogeneity.
-
-### For the meta-regressions,
-
-we will calculate Rmarginal2 to quantify the heterogeneity explained by the moderator(s) in proportion to the total variation (Nakagawa & Schielzeth, 2013).
-
 ## Publication Bias
 
-To explore evidence of publication bias, we will run multilevel meta-regressions with the same random effects structure as described above.
-We will follow the approach recommended in section 4.3 from Nakagawa et al.
-(2022) for both lnRR and SMDH, which consists of the following steps:
-
-First, run a uni-moderator meta-regression to test for evidence of small-study effects for both lnRR and SMDH separately, where the moderator is the square root of the inverse of the 'effective sample size' (see equation 27 in Nakagawa et al.
-2022).
-The slope of this meta-regression provides information about whether funnel plot asymmetry exists, and the intercept corresponds to the overall effect size adjusted by small-study effects.
-However, if this intercept is statistically significantly different from zero,
-
-```{r}
-dataset_SMDH<-dataset_SMDH%>%
+Small study effects:
+
+```{r}
+
+dataset_lnRR_published<-dataset_lnRR_published%>%
   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
@@
 
-MR_SMDH_small_study <-
+lnRR_small_study <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_published,# specify lnRR's sampling variance;
+                    mods = ~sqrt_effective_n_inv,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_published)
+
+# saving the model
+saveRDS(lnRR_small_study, file = here::here("model/lnRR_small_study.rds"))
+
+summary(lnRR_small_study)
+
+round(r2_ml(lnRR_small_study)*100,2)
+
+## Now for SMDH model
+
+dataset_SMDH_published<-dataset_SMDH_published%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))
+
+SMDH_small_study <-
   metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = SMDH_variance,# specify lnRR's sampling variance;
+                    V = VCV_SMDH_published,# specify lnRR's sampling variance;
                     mods = ~sqrt_effective_n_inv,
@@
                   control = list(optimizer="optim"),
-                  data = dataset_SMDH)
-
-summary(MR_SMDH_small_study)
-
-SMDH_small_study_bubble<-orchaRd::mod_results(MR_SMDH_small_study,
-                     mod="sqrt_effective_n_inv",
-                     group="paper_ID",
-                     weights="prop")
-orchaRd::bubble_plot(SMDH_small_study_bubble,
-                      mod="sqrt_effective_n_inv",
-                     group="paper_ID")
-
-round(r2_ml(MR_SMDH_small_study)*100,2)
-```
-
-Then, run the following uni-moderator meta-regression for both lnRR and SMDH separately which provides a less biased adjusted overall effect.
-The moderator here is simply the inverse of the 'effective sample size' (see equation 28 in Nakagawa et al.
-2022).
-The slope of this meta-regression provides information about whether funnel plot asymmetry exists and the intercept corresponds to a less biased overall effect size adjusted by small-study effects.
+                  data = dataset_SMDH_published)
+
+# saving the model
+saveRDS(SMDH_small_study, file = here::here("model/SMDH_small_study.rds"))
+
+summary(SMDH_small_study)
+
+round(r2_ml(SMDH_small_study)*100,2)
+
+```
+
+Decline effects (Time lag bias)
 
@@
 ```{r}
-dataset_SMDH<-dataset_SMDH%>%
-  filter(year_publication!="Unpublished")%>%
+dataset_lnRR_published<-dataset_lnRR_published%>%
   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])
 
-MR_SMDH_decline_eff <-
+lnRR_decline_eff <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_published,# specify lnRR's sampling variance;
+                    mods = ~ year_MeanCenter,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_published)
+
+# saving the model
+saveRDS(lnRR_decline_eff, file = here::here("model/lnRR_decline_eff.rds"))
+
+summary(lnRR_decline_eff)
+
+round(r2_ml(lnRR_decline_eff)*100,2)
+
+## --- Now for SMDH -----
+dataset_SMDH_published<-dataset_SMDH_published%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])
+
+SMDH_decline_eff <-
   metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = SMDH_variance,# specify lnRR's sampling variance;
+                    V = VCV_SMDH_published,# specify lnRR's sampling variance;
                     mods = ~ year_MeanCenter,
@@
                   control = list(optimizer="optim"),
-                  data = dataset_SMDH)
-
-summary(MR_SMDH_decline_eff)
-
-round(r2_ml(MR_SMDH_decline_eff)*100,2)
-
-MR_SMDH_decline_effect_bubble<-orchaRd::mod_results(MR_SMDH_decline_eff,
-                     mod="year_MeanCenter",
-                     group="paper_ID",
-                     weights="prop")
-orchaRd::bubble_plot(MR_SMDH_decline_effect_bubble,
-                      mod="year_MeanCenter",
-                     group="paper_ID")
+                  data = dataset_SMDH_published)
+# saving the model
+saveRDS(SMDH_decline_eff, file = here::here("model/SMDH_decline_eff.rds"))
+
+summary(SMDH_decline_eff)
+
+round(r2_ml(SMDH_decline_eff)*100,2)
+
 ```

### 2025-05-11 notebook/figures.qmd
Results for meta-regressions completed

@@
 
-##
+# Publication Bias Tests
+
+```{r}
+
+###---Small study Effects ----###
+
+lnRR_small_study<-readRDS(here::here("model/lnRR_small_study.rds"))
+SMDH_small_study<-readRDS(here::here("model/SMDH_small_study.rds"))
+
+lnRR_small_study_bubble<-orchaRd::bubble_plot(mod_results(lnRR_small_study,
+                     mod="sqrt_effective_n_inv",
+                     group="paper_ID",
+                     weights="prop"),
+                     group="paper_ID") +
+  scale_colour_manual(values ="mediumpurple4") +
+  scale_fill_manual(values = "mediumpurple4") +
+  labs(y = "Effect size (lnRR)",
+       x = expression(sqrt(1 / N[effective])))+
+    theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title = element_text(size = 14),
+    axis.text.x = element_text(size = 14),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))
+
+SMDH_small_study_bubble<-orchaRd::bubble_plot(mod_results(SMDH_small_study,
+                     mod="sqrt_effective_n_inv",
+                     group="paper_ID",
+                     weights="prop"),
+                     group="paper_ID") +
+  scale_colour_manual(values ="mediumpurple4") +
+  scale_fill_manual(values = "mediumpurple4") +
+  labs(y = "Effect size (SMDH)",
+       x = expression(sqrt(1 / N[effective])))+
+    theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title = element_text(size = 14),
+    axis.text.x = element_text(size = 14),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))
+
+###---Decline Effects ----###
+
+lnRR_decline_eff<-readRDS(here::here("model/lnRR_decline_eff.rds"))
+SMDH_decline_eff<-readRDS(here::here("model/SMDH_decline_eff.rds"))
+
+lnRR_decline_eff_bubble<-orchaRd::bubble_plot(mod_results(lnRR_decline_eff,
+                     mod="year_MeanCenter",
+                     group="paper_ID",
+                     weights="prop"),
+                     group="paper_ID")+
+  scale_colour_manual(values ="#218833") +
+  scale_fill_manual(values = "#218833") +
+  labs(y = "Effect size (lnRR)",
+       x = "Publication Year (Mean Cenetered)")+
+    theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title = element_text(size = 14),
+    axis.text.x = element_text(size = 14),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))
+
+SMDH_decline_effect_bubble<-orchaRd::bubble_plot(mod_results(SMDH_decline_eff,
+                     mod="year_MeanCenter",
+                     group="paper_ID",
+                     weights="prop"),
+                     group="paper_ID")+
+  scale_colour_manual(values ="#218833") +
+  scale_fill_manual(values = "#218833") +
+  labs(y = "Effect size (SMDH)",
+       x = "Publication Year (Mean Cenetered)")+
+    theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.title = element_text(size = 10),
+    legend.text = element_text(size = 10),
+    axis.title = element_text(size = 14),
+    axis.text.x = element_text(size = 14),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))
+
+# Combine using patchwork
+Figure_publication_bias <- ((lnRR_small_study_bubble + SMDH_small_study_bubble) /
+                               (lnRR_decline_eff_bubble + SMDH_decline_effect_bubble)) +
+  plot_annotation(tag_levels = "A")
+
+ggsave(here::here("figures/Figure_publication_bias.png"), plot = Figure_publication_bias, height = 300, width = 400, units = "mm", dpi = 600)
+```

### 2025-05-11 notebook/tables.qmd
Results for meta-regressions completed

--- 2025-05-08 docs/notebook/tables.qmd
@@
 
-pacman::p_load(gt, dplyr, broom, metafor, purrr, stringr)
+pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
 
@@
 SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+```
 
+```{r}
+
+# Let's source our custom function to extract values from the meta-regressions
+source(here::here("functions/extractor_metareg.R"))
+
+## For lnRR Values
+lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type")%>%
+  bind_rows(extractor_metareg(lnRR_birds,"bird_species"))%>%
+  bind_rows(extractor_metareg(lnRR_trait,"trait_type"))%>%
+  bind_rows(extractor_metareg(lnRR_design,"comparision_type"))%>%
+  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition"))%>%
+  mutate(effect_size = "lnRR")
+
+## For SMDH Values
+SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type")%>%
+  bind_rows(extractor_metareg(SMDH_birds,"bird_species"))%>%
+  bind_rows(extractor_metareg(SMDH_trait,"trait_type"))%>%
+  bind_rows(extractor_metareg(SMDH_design,"comparision_type"))%>%
+  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition"))%>%
+  mutate(effect_size = "SMDH")
+
+## Now let's write the table for publication:
+# Combine both results
+combined_results <- bind_rows(lnRR_results, SMDH_results)%>%
+  pivot_wider(
+    id_cols = c(moderator, level),
+    names_from = effect_size,
+    values_from = c(estimate, p_value, CI, PI, k, n),
+    names_glue = "{.value}_{effect_size}"
+  )%>% # Prepare row labels to mimic grouping
+  arrange(moderator, level)%>%
+  mutate(row_type = "level")
+
+# Create moderator header rows for heterogeneity metrics
+  moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
+  select(moderator, effect_size, Q, Q_pval, R2_marginal) %>%
+    distinct()%>%
+    pivot_wider(
+      names_from = effect_size,
+      values_from = c(Q, Q_pval, R2_marginal),
+      names_glue = "{.value}_{effect_size}"
+    )%>%
+  mutate(level = "Heterogeneity ",
+         row_type = "moderator")
+
+# Final combined table with headers and levels
+combined_results <- bind_rows(moderator_header, combined_results) %>%
+  arrange(moderator, row_type)%>% select(-row_type)%>%
+  relocate(level, .after = moderator)%>%
+  mutate(moderator=case_when(moderator=="parasite_type"~"Parasite Type",
+                             moderator=="bird_species"~"Bird Species",
+                             moderator=="trait_type"~"Trait Type Category",
+                             moderator=="comparision_type"~"Experimental Design",
+                             moderator=="time_of_gnm_addition"~"Time of Green Nest Material Addition"))%>%
+  mutate(level = case_when(level==1 ~ "Non-aromatic vs. Aromatic",
+                           level==2 ~ "No added material vs. Aromatic",
+                           level==3 ~ "No added material vs. Non-aromatic",
+                           level=="a" ~ "After egg hatching",
+                           level=="b" ~ "Before egg hatching",
+                           level=="c" ~ "Continously through nesting phase",
+                           level=="Parasitic_and_pathogenic"~"Parasitic and Pathogen Related", .default=level))
+
+# Optional: clean up or reorder columns for display
+# Select and order columns for clarity
+MLMR_table <- combined_results %>%
+  gt(groupname_col = "moderator") %>%
+  tab_header(title = md("**Multilevel Meta-analytic Models for Exploratory Analyses**")) %>%
+  cols_label(
+    Q_lnRR = "Q",
+    Q_pval_lnRR = "Q p-val",
+    R2_marginal_lnRR = "R²_mar",
+    Q_SMDH = "Q",
+    Q_pval_SMDH = "Q p-val",
+    R2_marginal_SMDH = "R²_mar",
+    level = "Level",
+    estimate_lnRR = "Estimate",
+    CI_lnRR = "95% CI",
+    PI_lnRR = "95% PI",
+    p_value_lnRR = "P-val",
+    k_lnRR = "k",
+    n_lnRR = "n",
+    estimate_SMDH = "Estimate",
+    CI_SMDH = "95% CI",
+    PI_SMDH = "95% PI",
+    p_value_SMDH = "P-val",
+    k_SMDH = "k",
+    n_SMDH = "n"
+  ) %>%
+   sub_missing(
+    columns = everything(),
+    missing_text = ""
+  ) %>%
+  opt_table_outline() %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 12,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "medium",
+    row_group.font.weight = "bold"
+  )   %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)
+    ),
+    locations = cells_body()
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      rows = level == "Heterogeneity"
+    ))%>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_lnRR),
+      rows = p_value_lnRR < 0.05
+    )
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_SMDH),
+      rows = p_value_SMDH < 0.05
+    )
+  )%>%
+  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))
+
+#saving as a docx file
+gtsave(MLMR_table,here::here("tables/EA_MLMR_table.docx"))
+gtsave(MLMR_table,here::here("tables/EA_MLMR_table.html"))
 ```

### 2025-05-11 functions/extractor_metareg.R

@@ -1,0 +1,125 @@
+# Let's write a function for extracting values from a meta-regression
+
+extractor_metareg <- function(model, moderator_name) {
+  
+  mod.summ <- summary(model)
+  # Extract levels of moderator (from rownames)
+  mod.levels <- rownames(mod.summ$beta)
+  mod.levels <- gsub(paste0(moderator_name),"", mod.levels)
+  
+  # Need to pass the complete data from the model to be able to calculate k and n for each level of moderator
+  mod.data <- model$data
+  
+  summ.k_n <-  mod.data %>%
+    group_by(level= as.character(mod.data[[moderator_name]])) %>%
+    summarise(
+      k = n(),  # effect sizes
+      n = n_distinct(paper_ID),  # unique papers
+      .groups = "drop"
+    )
+  
+  # Now we need a small function to extract the prediction interval per level of the moderator
+  # Get prediction intervals for each level
+  get_predicted<-function(model,mod.levels)
+  {
+    # Identity matrix for dummy-coded levels - categorical variables need dummy coding in metafor
+    newmods_mat <- diag(length(mod.levels))
+    predict.data<- data.frame(predict(model,newmods = newmods_mat))
+    predict.data<- predict.data%>%bind_cols(level=mod.levels)%>%select(pi.lb,pi.ub,level)
+    return(predict.data)
+  }
+  
+  prediction_interval<-get_predicted(model,mod.levels)
+  
+  ## Let's get all the heterogeneity metrics too
+  ## I am copying the r2_ml and R2_calc function code from orchaRd package
+  r2_ml <- function(model, data, boot = NULL) {
+    
+    if(all(class(model) %in% c("robust.rma", "rma.mv", "rma", "rma.uni")) == FALSE) {stop("Sorry, you need to fit a metafor model of class robust.rma, rma.mv, rma, rma.uni")}
+    
+    if(any(model$tau2 > 0)) { stop("Sorry. At the moment r2_ml cannot take models with heterogeneous variance.")}
+    
+    R2 <- R2_calc(model)
+    
+    if(!is.null(boot)){
+      
+      if(any(class(model) %in% c("robust.rma")) == TRUE){stop("Sorry, bootstrapping currently doesn't work for robust.rma objects. Please use rma.mv instead.")}
+      # Simulate the vector of effect sizes
[…]

### 2025-06-17 docs/manuscript_GNM.qmd
Some sensitivity analysis added

@@
 ---
+
+# Introduction
+
+Nest construction is a fundamental aspect of the bird breeding cycle, providing structural support and protection for eggs, parents, and nestlings against predators and environmental pressures, and in some species, even playing a role in sexual display during mating [@mainwaring2014; @hansell2000].
+Nest building behaviour is increasingly recognized as an expression of extended phenotype, demonstrating interspecific and intraspecific trait variation [@moreno2012; @perez2023].
+While most birds use organic plant materials- twigs, branches, grass, and moss- some incorporate inorganic items such as stones, feathers, snake skin and even anthropogenic materials [@sheard2024].
+These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+
+An intriguing nesting behaviour observed in some birds is the use of fresh green plant material (green nest material or GNM).
+This includes leaves, sprigs, herbs and branches added during or even after primary nest construction has completed.
+Importantly, these green nest materials differ from the structural components, being selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], often characterized by high levels of aromatic volatile compounds (commonly used by Passerines, [@mennerat2009]) and secondary metabolites such as oils and resins (preferred by raptors, [@ontiveros2007]).
+The costs associated with gathering these materials beyond the territory and maintaining fresh greenery through the breeding season imply adaptive significance of the GNM.
+
+Several hypotheses have been proposed to explain the adaptive function of green nest material (GNM).
+The courtship hypothesis suggests that males use aromatic plants as olfactory signals to attract mates or advertise nest site occupancy, particularly in cavity-nesting species where visual cues are limited.
+This idea traces back to the early natural history observations, beginning with @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to nests while singing and displaying to females.
+Subsequent studies in European and Spotless Starlings (*Sturnus unicolor*) support this view: unpaired males conspicuously deliver greenery during courtship but stop after egg-laying begins [@brouwer2004; @veiga2006], and they increase this behaviour in the presence of potential mates \[[@eens1993]\].
+Females often prefer nests with fresh herbs, suggesting that GNM may serve as a sexually selected signal of male quality and potentially increase fitness benefits for females.
+The courtship hypothesis has been also extended to species like Blue Tits (*Cyanistes caeruleus*), where it has been proposed that GNM might serve as a signal from females to the males [@tomás2013].
+However, in both starlings and blue tits, the link between plant-bringing material in males and the fitness benefits for females still remain unclear.
+
+Another hypothesis to explain the adaptive benefit of GNM is the widely tested nest protection hypothesis (NPH), which proposes that volatile compounds in green material reduce parasite abundance or pathogen loads, indirectly enhancing offspring survival.
+In an influential early comparitive study in raptors (Falconiformes), @wimberger1984 found indirect evidence for the reduction of ectoparasites in the nests with green nest material.
+@clark1988 later provided experimental support in European Starlings, showing that preferred herbs contained insect-repellent and antimicrobial volatile.
+They also outlined key criteria for evaluation of the NPH, including selective plant use, bioactive chemical properties and demonstrable adaptive benefits.
+Field observation and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM improved nestling condition without reducing parasite abundance [@gwinner2000].
+These findings led to the development of drug hypothesis, which suggests that the aromatic GNM directly enhance nestling development or immune function, independent of the parasite control [@gwinner2000; @mennerat2009a].
+Thus, while both hypotheses posit adaptive benefits of GNM, the drug hypothesis emphasizes a pharmacological mechanism, and the two are not mutually exclusive.
+Several other adaptive functions of GNM have also been proposed.
+These functions do not refer to the aromatic properties of GM, but could still provide some benefits such as enhance the crypticity of the nest [@skutch1957], provide insulation for eggs and nestling [@mertens1977], provide protection from sun, signal nest occupancy or simply fill the gaps between nesting materials [@lyons1987].
+These alternative functional roles have received little support or attention.
+
+Despite several observational and experimental studies and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], a comprehensive quantitative synthesis across studies and hypotheses has been lacking.
+This has limited our understanding of the generality and magnitude of GNM effects on fitness benefits.
+To address this gap, we conducted a systematic review and meta-analysis to assess the overall effect of GNM on various fitness proxies.
+We explicitly evaluate the evidence for the courtship and parental-care- the latter combining the nest protection and drug hypotheses due to their non-exclusivity.
+The drug hypothesis can only be supported by improved nestling health while ensuring that GNM has no protective effect against any parasite or pathogen.
+
+In addition to testing these primary hypotheses, we further explore the context-dependency in the research field and examine the potential sources of variation in the results (heterogeneity) in the GNM effects.
+Specifically, we explored whether the effect of GNM varied depending on the type of parasite (arthropods vs.
+microorganisms), the timing of GNM addition (e.g., before hatching, after hatching, or continuously), the experimental design (e.g., aromatic vs.
+non-aromatic vs.
+no added material), the focal species, and the type of fitness trait measured (e.g., physiology, morphology, reproduction).
+These exploratory moderators could allow us to assess context dependence and identify ecological or methodological patterns that may explain inconsistencies in previous findings.
+Together, our evidence synthesis approach provides the first quantitative test of the adaptive value of green nest material across bird species and research contexts.
 
@@
 We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details the study's objectives, a priori hypotheses and predictions, methods and planned data analyses.
+The pre-registration details our objectives, a priori hypotheses and predictions, methods and planned data analyses.
 Unless stated otherwise, we adhered to the registered protocol.
@@
 
-To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
-unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
-We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
-All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
-In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
-In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
-
 We extracted the means, variances and sample size for each control-treatment pairwise comparison.
@@
 We also had to exclude some effect sizes (n=?, k=?) because of the low sample size per group (less than x).
+
+To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
+unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
+We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
+All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
+In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
+In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
 
@@
 
-While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
-These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
-The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
 As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
@@
 Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
-All confidence and prediction intervals overlapped zero.
 However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
@@
 ## **Publication Bias**
+
+# Discussion
+
+Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased green nest material, though the strength of these effects depended on the effect size metric used.
+SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of green nest material---whether through sexual signaling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+
+The While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
 

### 2025-06-17 docs/notebook/data_analysis.qmd
Some sensitivity analysis added

@@
    filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
+
+# selecting only published dataset
+dataset_SMDH_published<-dataset_SMDH%>%
+  filter(!is.na(year_publication))
 
@@
 
+### Sensitivity Analysis with published data only
+
+```{r}
+
+# Preparing new variance-covariance matrix
+
+VCV_lnRR_published <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_lnRR_published<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_published)
+
+# saving the model
+saveRDS(SA_lnRR_published, file = here::here("sensitivity_analysis/SA_lnRR_published.rds"))
+
+# What is the effect now?
+
+summary(SA_lnRR_published)
+predict(SA_lnRR_published)
+
+# Preparing new variance-covariance matrix
+
+VCV_SMDH_published <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+## Running intercept only model
+
+SA_SMDH_published<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_published)
+
+# saving the model
+saveRDS(SA_SMDH_published, file = here::here("sensitivity_analysis/SA_SMDH_published.rds"))
+
+# What is the effect now?
+
+summary(SA_SMDH_published)
+predict(SA_SMDH_published)
+
+```
+
 ### Sensitivity Analysis with flagged proxies
@@
 dataset_lnRR_parasite <- dataset_lnRR%>%
-  filter(!is.na(parasite_type))
+  filter(!is.na(parasite_type))%>%
+  mutate(parasite_type=as.factor(parasite_type),
+         paper_ID=as.factor(paper_ID),
+         Observation_ID=as.factor(Observation_ID),
+         group_ID_coded=as.factor(group_ID_coded),
+         bird_species=as.factor(bird_species))
 
@@
 2022 for more information about this approach).
+
+## All-in Model for heterogeneity
+
+```{r}
+## For lnRR complete dataset
+VCV_lnRR_published<- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+all_in_lnRR <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ - 1 + time_of_gnm_addition + 
+                      year_MeanCenter + 
+                      sqrt_effective_n_inv + 
+                      comparision_type + 
+                      bird_species + 
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_published)
+
+## For SMDH complete published dataset
+VCV_SMDH_published<- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_published,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+all_in_SMDH<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ - 1 + time_of_gnm_addition + 
+                      year_MeanCenter + 
+                      sqrt_effective_n_inv + 
+                      comparision_type + 
+                      bird_species + 
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_published)
+```

### 2025-06-17 docs/notebook/figures.qmd
Some sensitivity analysis added

--- 2025-05-11 notebook/figures.qmd
@@
 ---
+
+# Visualising location and bird species
+
+I am using the figure code from here and adapting it for my needs..
+
+Mentesana, L., Hau, M., D'Amelio, P.B., Adreani, N.M.
+and Sánchez-Tójar, A.
+(2025), Do Egg Hormones Have Fitness Consequences in Wild Birds?
+A Systematic Review and Meta-Analysis.
+Ecology Letters, 28: e70100.
+<https://doi.org/10.1111/ele.70100> \[[Code](https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R)\]
+
+```{r}
+devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
+pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot)
+
+# Loading cleaned dataset
+dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
+
+# To split population_ID into location and country
+dataset_analysis[c('Location','Country')] <- str_split_fixed(dataset_analysis$population_ID, ',', 2)
+
+### For the purpose of this map, I am adding the the longitude and latitude of the study area manually.
+They exist in the dataset_analysis$population_location as they were extracted from the paper.
+I have also added some by just searching the general location since the coordinates were not provided for these..
+
+data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
+                             Lat_Location=c(51.50,38.41,40.45,40.75,45.40,52.39,37.18,
+                                             40.53,54,39.05,
+                                             51.57,48,42.54,39.95,
+                                             40.13,47.96,28.10,52.06,60.39),
+                             Long_Location=c(19.29,-9.02,-3.50,-3.78,-64.10,6.05,-3.11,
+                                              -4.0,-124,-76.81,
+                                              -2.26,11,8.91,-75.16,
+                                              -8.27,11.18,107.10,8.25,5.32))
+
+## Let's now merge the datasets by the location names
+
+dataset_analysis <- dataset_analysis %>%
+  left_join(data_coordinates, by = "Location")
+
+## Count how many times each Location appears in the full dataset
+location_counts <- dataset_analysis %>%
+  group_by(Location) %>%
+  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')
+
+# I will subset the data base so that I get one row per Location AND bird_species.
+# Like this, I get one point per location independently of the number of effect sizes 
+# we have per place.
+dataset_analysis_unique_rows <- dataset_analysis %>%
+  distinct(Location, bird_species, .keep_all = TRUE)
+
+# Merge the counts into the unique rows dataset
+dataset_analysis_unique_rows <- dataset_analysis_unique_rows %>%
+  left_join(location_counts, by = "Location")
+
+# create data for world coordinates using  
+# map_data() function 
+world_coordinates <- map_data("world")
+
+# create world map using ggplot() function 
+# geom_map() function takes world coordinates as input to plot world map 
+fig_map <- ggplot() + 
+  geom_map(data = world_coordinates, map = world_coordinates, 
+    aes(long, lat, map_id = region), 
+    color = "white", fill= "#D9EAF7") + 
+  geom_point(data = dataset_analysis_unique_rows, 
+             aes(x = Long_Location, y = Lat_Location,
+                 size = size.freq, colour=bird_species), alpha = 0.6) +
+scale_size(range = c(3, 10)) +
+  scale_fill_manual(values = c("#11a3d9","#f6c800",  "#fb5158", 
+                               "#ea60e9", "#40ad28","#ef8c27","#a083e2")) +
+
+  scale_colour_manual(values = c("#11a3d9","#f6c800",  "#fb5158", 
+                               "#ea60e9", "#40ad28","#ef8c27","#a083e2")) +
+  guides(size = "none", alpha = "none") +
+  labs(x = "Longitude",
+       y = "Latitude")+
+  theme_classic() +
+  theme(legend.position = c(0.88, 0.10),
+        legend.justification = c("right", "bottom"),
+        legend.background = element_rect(fill = "white", color = "black"),
+        axis.title = element_text(size = 12),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_blank())
+
+# To add the zoomed in map.. to show the points more clearly
+zoom_map <- ggplot() + 
+  geom_map(data = world_coordinates, map = world_coordinates,
+           aes(long, lat, map_id = region),
+           color = "white", fill = "lightgrey") +
+  geom_point(data = dataset_analysis_unique_rows,
+             aes(x = Long_Location, y = Lat_Location,
+                 size = size.freq, colour = bird_species),
+             alpha = 0.6) +
+  scale_size(range = c(3, 10)) +
+  scale_colour_manual(values = c("#11a3d9","#f6c800","#fb5158",
+                                 "#ea60e9","#40ad28","#ef8c27","#a083e2")) +
+  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
+  theme_void() +
+  theme(
+    legend.position = "none",
+    plot.background = element_rect(color = "white", fill="white"),
+    panel.border = element_rect(colour = "black", fill = NA, size = 1)
+  )
+
+geographic_distribution <- ggdraw() +
+  draw_plot(fig_map) +
+  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.62, height = 0.22)
+
+ggsave(here::here("figures/Figure_Distribution.png"), plot = geographic_distribution, height = 250, width = 400, units = "mm", dpi = 600)
+```
+
+# Visualizing author network
+
+```{r}
+# # Loading cleaned dataset
+# dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
+# 
+# library(tidyverse)
+# library(tidyr)
+# library(igraph)
+# installed.packages("ggraph")
+# library(ggraph)
+# 
+# clean_author <- function(name) {
+#   name %>%
+#     str_replace_all(",", "") %>%   # remove commas
+#     str_squish() %>%              # remove excess whitespace
+#     str_to_title()                # standardize case (optional, if needed)
+# }
+# 
+# # Apply cleaning to first and last author fields
+# author_roles <- dataset_analysis %>%
+#   distinct(paper_ID, .keep_all = TRUE) %>%
+#   select(paper_ID, authors, bird_species) %>%
+#   mutate(
+#     author_list = str_split(authors, ";\\s*"),
+#     first_author = map_chr(author_list, 1),
+#     last_author = map_chr(author_list, ~ tail(.x, 1))
+#   )%>%
+#   mutate(
+#     first_author=case_when(
+#       first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
+#       first_author == "Soler J J" ~ "Soler J. J.",
+#       first_author == "Glądalski, M" ~ "Gladalski M.",
+#       first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
+#       TRUE ~ as.character(first_author)
+#     ))%>%
+#   mutate(
+#     last_author=case_when(
+#       last_author == "Veiga J P" ~ "Veiga J. P.",
+#       TRUE ~ as.character(last_author)
+#     )
+#   )
+# 
+# # 2. Create Core Author Pairs (First → Last)
+# author_pairs_core <- author_roles %>%
+#   select(paper_ID, first_author, last_author) %>%
+#   rename(from = first_author, to = last_author) %>%
+#   filter(from != to) %>%
+#   count(from, to, name = "weight")
+# 
+# # 3. Build Author Graph
+# author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)
+# 
+# # 4. Assign Dominant Bird Species to PIs (last authors)
+# author_species <- author_roles %>%
+#   select(last_author, bird_species) %>%
+#   group_by(last_author, bird_species) %>%
+#   count() %>%
+#   slice_max(n, n = 1) %>%
+#   distinct(last_author, .keep_all = TRUE)
+# 
+# # Add species as vertex attribute
+# V(author_graph)$bird_species <- author_species$bird_species[
+#   match(V(author_graph)$name, author_species$last_author)
+# ]
+# 
+# # 5. Optional: Scale node size by number of papers per author
+# author_paper_counts <- author_roles %>%
+#   pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
+#   count(author, name = "paper_count")
+# 
+# # Add paper count attribute
+# V(author_graph)$paper_count <- author_paper_counts$paper_count[
+#   match(V(author_graph)$name, author_paper_counts$author)
+# ]
+# 
+# # Replace NAs with small size for isolated authors
+# V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1
+# 
+# # 6. Plot with ggraph
+# ggraph(author_graph, layout = "fr") +
+#   geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
+#   geom_node_point(aes(color = bird_species, size = paper_count)) +
+#   geom_node_text(aes(label = name), repel = TRUE, size = 3) +
+#   scale_edge_width(range = c(0.3, 2)) +
+#   scale_size(range = c(3, 10)) +
+#   theme_void() +
+#   labs(title = "Author Collaboration Network by Bird Species",
+#        size = "Paper Count") +
+#   theme(legend.position = "right")
+#
+
+```
+
+#
 
@@
 ```{r orchard plot for intercept only models}
-devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
 pacman::p_load(here,tidyverse,metafor,orchaRd,patchwork,cowplot)
@@
 # Plot for lnRR
-intercept_lnRR_plot <- orchard_plot(intercept_lnRR,
+intercept_lnRR_plot <- orchaRd::orchard_plot(intercept_lnRR,
                                     mod = "1",
@@
                                     xlab = "Effect size (Log Response Ratio- lnRR)",
-                                    colour = "#218833",
-                                    fill = TRUE) +
+                                    fill = T) +
    scale_fill_manual(values = "#218833") +
-  scale_colour_manual(values = "#218833") +
+   scale_colour_manual(values = "#218833" ) +
   theme_minimal(base_size = 14) +
@@
 # Plot for SMDH
-intercept_SMDH_plot <- orchard_plot(intercept_SMDH,
+intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                     mod = "1",
@@
                                     xlab = "Effect size (Standardized Mean Difference- SMDH)",
-                                    colour = "#895129",
                                     fill = TRUE) +

### 2025-06-17 manuscript_GNM.qmd
Some sensitivity analysis added

@@
 ---
+
+# Introduction
+
+Nest construction is a fundamental aspect of the bird breeding cycle, providing structural support and protection for eggs, parents, and nestlings against predators and environmental pressures, and in some species, even playing a role in sexual display during mating [@mainwaring2014; @hansell2000].
+Nest building behaviour is increasingly recognized as an expression of extended phenotype, demonstrating interspecific and intraspecific trait variation [@moreno2012; @perez2023].
+While most birds use organic plant materials- twigs, branches, grass, and moss- some incorporate inorganic items such as stones, feathers, snake skin and even anthropogenic materials [@sergio2011; @sheard2024].
+These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+
+An intriguing nesting behaviour observed in some birds is the use of fresh green plant material (green nest material or GNM).
+This includes leaves, sprigs, herbs and branches added during or even after primary nest construction has completed.
+Importantly, these green nest materials differ from the structural components, being selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], often characterized by high levels of aromatic volatile compounds (commonly used by Passerines, [@mennerat2009]) and secondary metabolites such as oils and resins (preferred by raptors, [@ontiveros2007]).
+The costs associated with gathering these materials beyond the territory and maintaining fresh greenery through the breeding season imply adaptive significance of the GNM.
+
+Several hypotheses have been proposed to explain the adaptive function of green nest material (GNM).
+The courtship hypothesis suggests that males use aromatic plants as olfactory signals to attract mates or advertise nest site occupancy, particularly in cavity-nesting species where visual cues are limited.
+This idea traces back to the early natural history observations, beginning with @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to nests while singing and displaying to females.
+Subsequent studies in European and Spotless Starlings (*Sturnus unicolor*) support this view: unpaired males conspicuously deliver greenery during courtship but stop after egg-laying begins [@brouwer2004; @veiga2006], and they increase this behaviour in the presence of potential mates \[[@eens1993]\].
+Females often prefer nests with fresh herbs, suggesting that GNM may serve as a sexually selected signal of male quality and potentially increase fitness benefits for females.
+The courtship hypothesis has been also extended to species like Blue Tits (*Cyanistes caeruleus*), where it has been proposed that GNM might serve as a signal from females to the males [@tomás2013].
+However, in both starlings and blue tits, the link between plant-bringing material in males and the fitness benefits for females still remain unclear.
+
+Another hypothesis to explain the adaptive benefit of GNM is the widely tested nest protection hypothesis (NPH), which proposes that volatile compounds in green material reduce parasite abundance or pathogen loads, indirectly enhancing offspring survival.
+In an influential early comparitive study in raptors (Falconiformes), @wimberger1984 found indirect evidence for the reduction of ectoparasites in the nests with green nest material.
+@clark1988 later provided experimental support in European Starlings, showing that preferred herbs contained insect-repellent and antimicrobial volatile.
+They also outlined key criteria for evaluation of the NPH, including selective plant use, bioactive chemical properties and demonstrable adaptive benefits.
+Field observation and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM improved nestling condition without reducing parasite abundance [@gwinner2000].
+These findings led to the development of drug hypothesis, which suggests that the aromatic GNM directly enhance nestling development or immune function, independent of the parasite control [@gwinner2000; @mennerat2009a].
+Thus, while both hypotheses posit adaptive benefits of GNM, the drug hypothesis emphasizes a pharmacological mechanism, and the two are not mutually exclusive.
+Several other adaptive functions of GNM have also been proposed.
+These functions do not refer to the aromatic properties of GM, but could still provide some benefits such as enhance the crypticity of the nest [@skutch1957], provide insulation for eggs and nestling [@mertens1977], provide protection from sun, signal nest occupancy or simply fill the gaps between nesting materials [@lyons1987].
+These alternative functional roles have received little support or attention.
+
+Despite several observational and experimental studies and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], a comprehensive quantitative synthesis across studies and hypotheses has been lacking.
+This has limited our understanding of the generality and magnitude of GNM effects on fitness benefits.
+To address this gap, we conducted a systematic review and meta-analysis to assess the overall effect of GNM on various fitness proxies.
+We explicitly evaluate the evidence for the courtship and parental-care- the latter combining the nest protection and drug hypotheses due to their non-exclusivity.
+The drug hypothesis can only be supported by improved nestling health while ensuring that GNM has no protective effect against any parasite or pathogen.
+
+In addition to testing these primary hypotheses, we further explore the context-dependency in the research field and examine the potential sources of variation in the results (heterogeneity) in the GNM effects.
+Specifically, we explored whether the effect of GNM varied depending on the type of parasite (arthropods vs.
+microorganisms), the timing of GNM addition (e.g., before hatching, after hatching, or continuously), the experimental design (e.g., aromatic vs.
+non-aromatic vs.
+no added material), the focal species, and the type of fitness trait measured (e.g., physiology, morphology, reproduction).
+These exploratory moderators could allow us to assess context dependence and identify ecological or methodological patterns that may explain inconsistencies in previous findings.
+Together, our evidence synthesis approach provides the first quantitative test of the adaptive value of green nest material across bird species and research contexts.
 
@@
 
+# Discussion
+
+Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased green nest material, though the strength of these effects depended on the effect size metric used.
+SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of green nest material---whether through sexual signaling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+
+The While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+
 \-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--

### 2025-06-17 notebook/data_analysis.qmd
Some sensitivity analysis added

@@
 
+### Sensitivity Analysis excluding the parasite and pathogen load fitness proxies
+
+```{r}
+
+## For the lnRR effect size...
+dataset_lnRR_no_PCH<-dataset_lnRR%>%filter(Hypothesis!="PCH")
+
+## The dataset is reduced to almost half
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_PCH)
+
+VCV_lnRR_no_PCH <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_PCH,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_PCH<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_PCH, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_PCH)
+
+## For the SMDH effect size..
+
+dataset_SMDH_no_PCH<-dataset_SMDH%>%filter(Hypothesis!="PCH")
+
+## The dataset is reduced to almost half
+nrow(dataset_SMDH)-nrow(dataset_SMDH_no_PCH)
+
+VCV_SMDH_no_PCH <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_no_PCH,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_SMDH_no_PCH<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_PCH, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_no_PCH)
+```
+
+### Sensitivity Analysis for excluding non-aromatic and blank (the two control group comparison)
+
+```{r}
+
+## For the lnRR effect size...
+dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3)
+## Only some rows are removed... 
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp3)
+
+VCV_lnRR_no_comp3 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_comp3,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_PCH<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_PCH, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_PCH)
+```
+
 ### Different values of sampling variance correlation
@@
 dataset_lnRR_design <- dataset_lnRR %>%
-  filter(!is.na(comparision_type))%>%
-  mutate(comparision_type= as.factor(comparision_type))
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
 
@@
                     V = VCV_lnRR_design ,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + comparision_type,
+                    mods = ~ - 1 + as.factor(comparision_type),
                     random = list(~ 1 | paper_ID,
@@
 dataset_SMDH_design <- dataset_SMDH %>%
-  filter(!is.na(comparision_type))%>%
-  mutate(comparision_type= as.factor(comparision_type))
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
 
@@
                     V = VCV_SMDH_design ,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + comparision_type,
+                    mods = ~ - 1 + as.factor(comparision_type),
                     random = list(~ 1 | paper_ID,
@@
 2022 for more information about this approach).
+
+## All-in Model for heterogeneity
+
+```{r}
+## For lnRR complete dataset
+
+## I am changing the year of unpublished studies to 2025 which is to now, assuming that if they were to be published now, what would be the effect.
+I will keep in mind that in this model if I do find an evidence of publication bias over years, I should keep in mind it is non-independent of the unpublished studies
+
+dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+
+VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition + 
+                      year_MeanCenter + 
+                      sqrt_effective_n_inv + 
+                      as.factor(comparision_type) + 
+                      bird_species + 
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_all_in)
+
+## For SMDH complete published dataset
+
+dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+
+VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition + 
+                      year_MeanCenter + 
+                      sqrt_effective_n_inv + 
+                      as.factor(comparision_type) + 
+                      bird_species + 
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_all_in)
+```

### 2025-06-17 notebook/figures.qmd
Some sensitivity analysis added

@@
     axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","Aromatic Vs. Blank", "Non-Aromatic Vs. Blank"))
+  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","Blank Vs. Aromatic", "Blank Vs. Non-Aromatic"))
 

### 2025-06-18 manuscript_GNM.qmd
Revising Introduction.. not rendered, just qmd file from one machine to another

@@
 
-Another hypothesis to explain the adaptive benefit of GNM is the widely tested nest protection hypothesis (NPH), which proposes that volatile compounds in green material reduce parasite abundance or pathogen loads, indirectly enhancing offspring survival.
-In an influential early comparitive study in raptors (Falconiformes), @wimberger1984 found indirect evidence for the reduction of ectoparasites in the nests with green nest material.
-@clark1988 later provided experimental support in European Starlings, showing that preferred herbs contained insect-repellent and antimicrobial volatile.
-They also outlined key criteria for evaluation of the NPH, including selective plant use, bioactive chemical properties and demonstrable adaptive benefits.
-Field observation and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM improved nestling condition without reducing parasite abundance [@gwinner2000].
-These findings led to the development of drug hypothesis, which suggests that the aromatic GNM directly enhance nestling development or immune function, independent of the parasite control [@gwinner2000; @mennerat2009a].
-Thus, while both hypotheses posit adaptive benefits of GNM, the drug hypothesis emphasizes a pharmacological mechanism, and the two are not mutually exclusive.
-Several other adaptive functions of GNM have also been proposed.
-These functions do not refer to the aromatic properties of GM, but could still provide some benefits such as enhance the crypticity of the nest [@skutch1957], provide insulation for eggs and nestling [@mertens1977], provide protection from sun, signal nest occupancy or simply fill the gaps between nesting materials [@lyons1987].
-These alternative functional roles have received little support or attention.
+Second and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites or pathogens in the nest, which could enhance offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and indirectly tested it by comparing the nest reuse, diet composition and the green nest material presence \[@wimberger1984\].
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatile was experimentally confirmed in European Starlings, therefore confirming two of the key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
+Observational and experimental studies on raptors \[@ontiveros2007; @dykstra2009\] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of drug hypothesis.
+The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring development or immune function, independent of the parasite control [@gwinner2000; @mennerat2009a].
+Thus, while both hypotheses suggest adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Importantly, these two hypothese are not mutually exclusive unless the improve in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
 
-Despite several observational and experimental studies and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], a comprehensive quantitative synthesis across studies and hypotheses has been lacking.
-This has limited our understanding of the generality and magnitude of GNM effects on fitness benefits.
-To address this gap, we conducted a systematic review and meta-analysis to assess the overall effect of GNM on various fitness proxies.
-We explicitly evaluate the evidence for the courtship and parental-care- the latter combining the nest protection and drug hypotheses due to their non-exclusivity.
-The drug hypothesis can only be supported by improved nestling health while ensuring that GNM has no protective effect against any parasite or pathogen.
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic properties have been proposed.
+These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], signal nest occupancy or simply fulfilling a structural function [@lyons1987].
+However, these alternative functional roles have received little support or attention.
+In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
+Given the importance of nests and nest building across the tree of life, and their increasing recognition as an expression of the extended phenotype, it is of paramount importance to qualitatively synthesise this field.
 
-In addition to testing these primary hypotheses, we further explore the context-dependency in the research field and examine the potential sources of variation in the results (heterogeneity) in the GNM effects.
-Specifically, we explored whether the effect of GNM varied depending on the type of parasite (arthropods vs.
-microorganisms), the timing of GNM addition (e.g., before hatching, after hatching, or continuously), the experimental design (e.g., aromatic vs.
+To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as to assess the relative importance of the main suggested hypothesis: the courtship hypotheses and the parental care hypothesis i.e.
+combining both the nest protection and drug hypotheses due to their non-exclusivity.
+In addition, we explore the observed context-dependency (i.e., high heterogeneity among effect sizes) via meta-regressions.
+Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
+microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design (aromatic vs.
 non-aromatic vs.
-no added material), the focal species, and the type of fitness trait measured (e.g., physiology, morphology, reproduction).
+no added material), the focal species, and the type of fitness proxy investigated (physiology, morphology, reproduction).
+Our meta-analysis of experimental studies corresponds to the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
+
 These exploratory moderators could allow us to assess context dependence and identify ecological or methodological patterns that may explain inconsistencies in previous findings.

### 2025-06-26 manuscript_GNM.qmd
Introduction update.. continued.. no built

--- 2025-05-11 manuscript_GNM.qmd
@@
 ---
+
+# Introduction
+
+Nest construction is a fundamental aspect of the bird breeding cycle,
+
+Nests provide structural support and protection for eggs, parents, and offspring against predators and environmental pressures, and are thus key to reproductive success and survival [@mainwaring2014; @hansell2000].
+While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items such as stones, feathers, snake skin and even anthropogenic materials [@sergio2011; @sheard2024].
+These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+Indeed, nests can play a key role in sexual display, with some features such as size acting as sexually selected signals of parental quality in many bird species (XX), and even being used interspecifically by brood parasites (XX).
+Nest building behaviour is increasingly recognized as an expression of extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
+Yet, despite hundreds of scientific articles studying nests and nesting behaviour in birds being published each year, much remains unknown.
+
+An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
+This green nest material (*GNM*) includes leaves, sprigs, herbs and branches often added from the onset of nest building to the start of egg laying, but in some species, such as the Blue Tits, also after primary nest building is completed.
+during or even after primary nest construction has completed.
+Importantly, contrary to the structural nest materials or components, this GNM are thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], often characterized by high levels of aromatic volatile compounds (commonly used by Passerines: @mennerat2009) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+The costs associated with gathering these materials beyond the territory and maintaining fresh greenery through the breeding season imply adaptive significance of the GNM.
+<!--# This information is important, but it’s not entirely clear why this behaviour is considered costly.
+Also, we haven’t yet mentioned that birds maintain this material fresh throughout the nesting period, which is key to arguing that it requires extra effort.
+We need to explain this point more clearly and provide evidence for the associated costs.
+Are there any studies that directly assess these costs?
+For instance, does this paper—https://journals.sagepub.com/doi/10.3184/175815512X13528994072997—address it?
+Please add this information, and I’ll be happy to help revise the text further.
+-->
+
+Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
+First, the courtship hypothesis suggests that mostly males use GNM signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
+This hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
+Subsequent studies in borh European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
+The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected of female quality [@tomás2013].
+
+Second and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites or pathogens in the nests, enhancing offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence \[@wimberger1984\].
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatile was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
+Observational and experimental studies on raptors \[@ontiveros2007; @dykstra2009\] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of drug hypothesis.
+The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
+Thus, while both hypotheses suggest adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
+
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic properties have been proposed.
+These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], or simply fulfilling a structural function [@lyons1987].
+However, these alternative functional roles have received little support or attention.
+In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
+Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and potentially far-reaching in its implications.
+
+To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as to assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and the parental care hypothesis (i.e.
+combining both the nest protection and drug hypotheses due to their non-exclusivity).
+In addition, we explore the observed context-dependency (i.e., high heterogeneity among effect sizes) via meta-regressions.
+Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
+microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design (aromatic vs.
+non-aromatic vs.
+no added material), the focal species, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
+Our meta-analysis of experimental studies is the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
 

### 2025-06-27 manuscript_GNM.qmd
Introducted updated again.. no build

@@
 
-Nest construction is a fundamental aspect of the bird breeding cycle,
-
-Nests provide structural support and protection for eggs, parents, and offspring against predators and environmental pressures, and are thus key to reproductive success and survival [@mainwaring2014; @hansell2000].
-While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items such as stones, feathers, snake skin and even anthropogenic materials [@sergio2011; @sheard2024].
+Nest and nest-building are fundamental across a diverse range of animals, including insects (e.g., termites, spiders), mammals (e.g., platypus, rodents), and perhaps more famously, birds.
+Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@mainwaring2014; @deeming2023; @hansell2000].
+While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@suárez-rodríguez2013; @sergio2011; @sheard2024].
 These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
-Indeed, nests can play a key role in sexual display, with some features such as size acting as sexually selected signals of parental quality in many bird species (XX), and even being used interspecifically by brood parasites (XX).
-Nest building behaviour is increasingly recognized as an expression of extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
+Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in many bird species [@moreno1994; @hoi1996], even across species [@soler1995].
+Nest-building behaviour is increasingly recognized as an expression of the extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
 Yet, despite hundreds of scientific articles studying nests and nesting behaviour in birds being published each year, much remains unknown.
@@
 An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
-This green nest material (*GNM*) includes leaves, sprigs, herbs and branches often added from the onset of nest building to the start of egg laying, but in some species, such as the Blue Tits, also after primary nest building is completed.
-during or even after primary nest construction has completed.
-Importantly, contrary to the structural nest materials or components, this GNM are thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], often characterized by high levels of aromatic volatile compounds (commonly used by Passerines: @mennerat2009) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-The costs associated with gathering these materials beyond the territory and maintaining fresh greenery through the breeding season imply adaptive significance of the GNM.
-<!--# This information is important, but it’s not entirely clear why this behaviour is considered costly.
-Also, we haven’t yet mentioned that birds maintain this material fresh throughout the nesting period, which is key to arguing that it requires extra effort.
-We need to explain this point more clearly and provide evidence for the associated costs.
-Are there any studies that directly assess these costs?
-For instance, does this paper—https://journals.sagepub.com/doi/10.3184/175815512X13528994072997—address it?
-Please add this information, and I’ll be happy to help revise the text further.
--->
+This green nest material (GNM) ---leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species keep adding it even after the nest is finished.
+Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+Collecting and constantly replenishing GNM requires extra foraging flights, sometimes even outside the territory [@mennerat2009].
+The costs associated with nest building [@mainwaring2013], and these additional efforts suggest that GNM is unlikely to be gathered opportunistically and suggests a possible adaptive significance.
 
 Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
-First, the courtship hypothesis suggests that mostly males use GNM signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
+First, the courtship hypothesis suggests that mostly males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
 This hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in borh European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
-The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected of female quality [@tomás2013].
+Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
+The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
-Second and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites or pathogens in the nests, enhancing offspring survival.
-This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence \[@wimberger1984\].
-Soon after, a preference for GNM containing insect-repellent and antimicrobial volatile was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
-Observational and experimental studies on raptors \[@ontiveros2007; @dykstra2009\] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of drug hypothesis.
+Second, and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence [@wimberger1984].
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
+Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
 The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
-Thus, while both hypotheses suggest adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Thus, while both hypotheses suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
 Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
@@
 To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
-Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as to assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and the parental care hypothesis (i.e.
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e.
 combining both the nest protection and drug hypotheses due to their non-exclusivity).

### 2025-07-05 docs/code/05_data_cleaning.Rmd
Updated Introduction/Methods completed Added all the codes and data files to the folder. Can publish directly from here for later..

---
title: "Data cleaning"
author: "Shreya D."
date: '`r Sys.Date()`'
output: html_document
license: CC-BY-4.0
email: shreya.dimri@uni-bielefeld.de
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
```

# Data Cleaning

This is the step conducted once all the data from different sources was extracted.

-   We had **40 papers after abstract and title screening**

-   We found **1** **paper** from from repeating the search on 12th August 2024

-   We found **1 paper** from other source (from Meinolf's poster)

-   We found **1 paper** that was sent over by Antje

-   We got access to **2 Unpublished datasets (**One was provided by Meinolf on buzzards and another was a Master Thesis project from Adele Menerate's students)

#### What do we do here?

1.  We import the dataset that we produced after data extraction (3 files for initial data-extraction, 3 for repeat search and additional article, 2 unpublished data sets). We merge these datasets.
2.  We exclude studies that did not meet our inclusion criteria.
3.  This script was used to clean the names of the fitness proxies (since we extracted them as they were mentioned in the publication, often with the time of data collection eg. chick mass (day 8). These needed to be standardized into similar names.
4.  We clean all the names of the moderators and standardise any typos in the dataset.

#### **Importing files after data extraction**

You can find all the data that is needed for this analysis.. in folder **data/02_data_extraction**. In short, we need the following files to run the data cleaning:

-   data_extraction_setJMGS_checkedSD.xlsx

-   data_extraction_setSD_checkedTR.xlsx

-   data_extraction_setTR_checkedJS_checkedSD.xlsx

-   data_extraction_repeat_search_JMGS.xlsx

-   data_extraction_repeat_search_SD.xlsx

-   data_extraction_repeat_search_TR.xlsx

-   data_extraction_MO_checkedSD.xlsx

-   data_extraction_UnpublishedThesis.xlsx

#### Setting up the space

```{r load_packages, message=FALSE, warning=FALSE}

pacman::p_load(here, dplyr, readxl, purrr, stringr, knitr, tidyverse)

rm(list=ls()) ## clearing up any previously present variable
```

```{r import, warning=FALSE, message=FALSE}

## We use column_types to make the loading variable datatype of all the datafiles same.

column_types = c(
  "text", "text", "text", "text", "text", "numeric", 
  "text", "text", "text", "text", "text", "text", 
  "text", "text", "text", "text", "numeric", "text", 
  "numeric", "text", "numeric", "numeric", "text", "numeric", 
  "text", "numeric", "text", "text", "text", "text", 
  "numeric", "text", "text", "numeric", "numeric", "numeric", 
  "numeric", "numeric", "text", "text", "text", "text", 
  "text", "text", "text", "text", "text", "text", 
  "numeric", "numeric"
)

# Data extracted from the selected papers after abstract screening

set_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx"),col_types =column_types)
set_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx"),col_types =column_types)
set_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx"),col_types =column_types)

# Data extracted from repeated search on 12.Aug.2024

set2_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx"),col_types =column_types)
set2_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_SD.xlsx"),col_types =column_types)
set2_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_TR.xlsx"),col_types =column_types)

# Unpublished dataset
set_unpublished1 <- read_excel(here::here("data/02_data_extraction/data_extraction_MO_checkedSD.xlsx"),col_types =column_types)
set_unpublished2 <-read_excel(here::here("data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx"),col_types =column_types)

# Merge all datasets
merged_data_extraction<-full_join(set_JMGS,set_SD)%>%full_join(set_TR)%>%full_join(set2_JMGS)%>%full_join(set2_SD)%>%full_join(set2_TR)%>%full_join(set_unpublished1)%>%full_join(set_unpublished2)

# write.csv(merged_data_extraction,here::here("data/03_data_cleaning/merged_data_extraction.csv"),row.names=FALSE)
```

### Full-text Screening

#### **Excluded articles**

These were the articles extracted during full-text screening according to the decision tree, for the following reasons given below..

```{r excluded data}
#| echo: false
#| output: asis

excluded_fulltext <- merged_data_extraction %>% filter(fulltext_screening=="excluded")
excluded_papers_no<-length(unique(excluded_fulltext$paper_ID))

# write.csv(excluded_fulltext,here::here("data/03_data_cleaning/excluded_fulltext.csv"),row.names=FALSE)
```

**Number of studies that were excluded from out data extraction process: `r excluded_papers_no`** .

```{r}
#| echo: false

kable(as.data.frame(summary(as.factor(excluded_fulltext$fulltext_notes))),
      col.names=("Number of studies excluded"),
      caption = "Reasons for exclusion")
```

#### **Included articles**

```{r}
#| echo: false
#| output: asis

dataset_after_cleaning <- merged_data_extraction %>%
  filter(fulltext_screening == "included" | is.na(fulltext_screening) | fulltext_screening == "NA")
included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))

```

**Number of studies that are included in our meta-analysis so far: `r included_papers_no`**

## Proxies of fitness

We extracted the names of the variables that the authors measured as it is, often along with the location/year when they were measured. We will now clean them a bit, making sure they are all named correctly. We are cleaning some of the names of the fitness proxy and storing them in the new variable called *fitness_proxy_cleaned*

```{r}
#| echo: false
#| output: asis

# print(dataset_after_cleaning %>% count(fitness_proxy), n = Inf)

# Renaming fitness proxies to standardise everything
dataset_after_cleaning$fitness_proxy_cleaned<-dataset_after_cleaning$fitness_proxy
```

We will try to list down all the decisions that we made along the way about the numerous proxies.. how we categorized what hypothesis they could be considered an evidence for (information on this is contained in a 1(TRUE) and 0(FALSE) format in the variables PCH and CH, ones that are 1 are considered as giving evidence to "Both" of the hypothesis i.e. in some cases, we simply could not clearly associate a fitness proxy with the suggested mechanistic hypothesis (e.g. fledgling survival, nestling mass etc.)

### Courtship Hypothesis only:

**1. Male and female proportion of visit:**

We will exclude female proportion of visit and female provisioning rate from all our analysis. In the study females add the GNM as noted by the authors (Study ID-GNM_018 in our meta-analysis), it is the male that would/should adjust their investment. One can argue female investment will be an indirect reflection of the male's investment. However, this is very indirect and the direction of this proxy in relation to the GNM addition can be argued both ways. That is, if females use GNM as an honest signal to increase male investment, their own investment would not be directly related to fitness or they would increase investment to compensate for the lack of male investment. Or it would be negatively related to fitness because they invested in bringing in the GNM as well as in higher provisioning.

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "male_visit",
   str_detect(fitness_proxy, regex("female proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "female_visit",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

**2. Male and female provisioning**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
     str_detect(fitness_proxy, regex("female provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "female_provisioning_rate",
   str_detect(fitness_proxy, regex("male provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning_rate",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

**3.** **Male food provisioning**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male food provisioning*" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**4.** **Male incubation attendance**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male incubation attendance*" , 
                                   ignore_case = TRUE)) ~ 
     "male_incubation_attendance",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

**5.** **Male Risk Taking**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male risk*" , 
                                   ignore_case = TRUE)) ~ 
     "male_risk_taking",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**6.** **Sex Ratio**

We will be excluding sex ratio as a fitness proxy from our main analysis (@krackow2002). However, we will test this with other similarly marked proxies in a sensitivity analysis.

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("Sex ratio offspring*", ignore_case = TRUE))
    ~ "sex_ratio",    
   str_detect(fitness_proxy, regex("proportion of males per breeding attempt", 
                                   ignore_case = TRUE))
    ~ "sex_ratio",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

**7.** **Female Testosterone**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("females' testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
   str_detect(fitness_proxy, regex("testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**8.** **Yolk Hormones**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Yolk Log T (testosterone)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    str_detect(fitness_proxy, regex("Yolk Log A4(androstenedione)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**9.** **Courtship Time**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("courtship time*" , 
                                   ignore_case = TRUE)) ~ 
     "courtship_time",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

### Both Hypothesis :

**1.** **Laying Date**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("laying date", ignore_case = TRUE))
    ~ "laying_date",    
    str_detect(fitness_proxy, regex("clutch initiation date", ignore_case = TRUE)) 
    ~ "laying_date",
      str_detect(fitness_proxy, regex("Onset of Laying", ignore_case = TRUE)) 
    ~ "laying_date",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

```

**2.** **Hatching Date**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("hatching date", ignore_case = TRUE))
    ~ "hatching_date",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

```

**3.** **Clutch size**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("clutch size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("clutch-size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
     str_detect(fitness_proxy, regex("eggslaid", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("Number of eggs", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**4. Number of nestlings (different age)**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of nestling", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("Number of hatchlings", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("broodsize", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",  
    str_detect(fitness_proxy, regex("brood size", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("number of eggs hatched", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("maxchicks*", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))

```

**5. Number of fledglings**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    str_detect(fitness_proxy, regex("number fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**6. Nestling survival rate**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("nestling survival rate", 
                                    ignore_case = TRUE)) ~ "survival_rate_nestling",

    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))

```

**7. Recruitment probability**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("probability of local recruitment" , 
                                   ignore_case = TRUE)) ~ "local_recruitment_probability",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

8\. **Hatching success**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("hatching success*" , 
                                   ignore_case = TRUE)) ~ "hatching_success",
   str_detect(fitness_proxy, regex("hatch success*" , 
                                   ignore_case = TRUE)) ~ "hatching_success",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**9.** **Fledgling success**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("fledging success*" , 
                                   ignore_case = TRUE)) ~ "fledgling_success",
   str_detect(fitness_proxy, regex("fledge success*" , 
                                   ignore_case = TRUE)) ~ "fledgling_success",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**10.** **Reproductive success**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("reproductive success" , 
                                   ignore_case = TRUE)) ~ "reproductive_success",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

11\. **Nest mortality**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Nest mortality" , 
                                   ignore_case = TRUE)) ~ "nest_mortality",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

**12. Mouth colouration**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("brightness" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
   str_detect(fitness_proxy, regex("hue" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
      str_detect(fitness_proxy, regex("saturation" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

```

**13. Male and female dispersal distance**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("dispersal distance (meters) males*", ignore_case = TRUE))
    ~ "dispersal_distance_males",    
    str_detect(fitness_proxy, regex("dispersal distance (meters) females*", ignore_case = TRUE)) 
    ~ "dispersal_distance_females",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

**14. Egg Size**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("egg size*" , 
                                   ignore_case = TRUE)) ~ 
     "egg_size",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**15. Chick mass, nestling mass and fledgling mass**

```{r}
# Checked paper GNM_069 and GNM_349 and the word body mass is used to describe nestlings of 14 days and 17 days respectlively
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("chick mass*", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("chick body mass", ignore_case = TRUE)) ~ "chick_mass",
     str_detect(fitness_proxy, regex("chickmass", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("fledgling mass", ignore_case = TRUE)) ~ "fledgeling_mass",
    str_detect(fitness_proxy, regex("fledgling body mass", ignore_case = TRUE)) ~ "fledgeling_mass",str_detect(fitness_proxy, regex("nestling mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestlings mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestling weight", ignore_case = TRUE)) ~ "nestling_mass",    str_detect(fitness_proxy, regex("body mass", ignore_case = TRUE)) ~ "nestling_mass",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**16. Nestling Size**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling size*" , ignore_case = TRUE)) 
   ~ "nestling_size",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**17. Nestling Tarsus Length**

```{r}

#checked paper GNM_069 word tarsus length is used to describe nestlings of 14 days

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling tarsus length" , ignore_case = TRUE)) ~ "nestling_tarsus_length",
      str_detect(fitness_proxy,"tarsal length") ~ "nestling_tarsus_length",
   str_detect(fitness_proxy,"Tarsus Length*") ~ "nestling_tarsus_length",

    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**18. Nestling Wing Length**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling wing*" , ignore_case = TRUE)) 
   ~ "nestling_wing_length",
   str_detect(fitness_proxy, regex("length of primary flight feather length of nestlings at day 12" , 
                                   ignore_case = TRUE)) 
   ~ "nestling_wing_length",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**19. Male and female body size**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("female body size", ignore_case = TRUE)) 
    ~ "female_bodysize",
    str_detect(fitness_proxy, regex("male body size", ignore_case = TRUE))
    ~ "male_bodysize",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

```

**20.** **Male and female mass**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
      str_detect(fitness_proxy, regex("female mass", ignore_case = TRUE)) 
    ~ "female_mass",
    str_detect(fitness_proxy, regex("male mass", ignore_case = TRUE))
    ~ "male_mass",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

```

**21.** **Male and female wing length**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
      str_detect(fitness_proxy, regex("female wing length", ignore_case = TRUE)) 
    ~ "female_winglength",
    str_detect(fitness_proxy, regex("male wing length", ignore_case = TRUE))
    ~ "male_winglength",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

**21.** **Male and female tarsus length**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
  str_detect(fitness_proxy, regex("female tarsus length", ignore_case = TRUE)) 
    ~ "female_tarsus_length",
    str_detect(fitness_proxy, regex("male tarsus length", ignore_case = TRUE))
    ~ "male_tarsus_length",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

**22. Female body condition (Tarsus/wing)**

Here the authors have studied the effect of parasite on he adult female (yearlings) measured at two time point to understand how the parasite load effects the adults in the nest (GNM_101)

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("female body condition*" , ignore_case = TRUE)) 
   ~ "female_body_condition",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

### For variables that fit Parental care hypothesis:

1\. **Number of mites**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("\\bmite(s)?\\b", ignore_case = TRUE)) ~ "mites",
    str_detect(fitness_proxy, regex("mite load*", ignore_case = TRUE)) 
    ~ "mites",
    str_detect(fitness_proxy, regex("mites_score", ignore_case = TRUE)) 
    ~ "mites",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**3.** **Number of fleas**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of fleas*", ignore_case = TRUE)) 
    ~ "fleas_number",
    str_detect(fitness_proxy, regex("fleas*", ignore_case = TRUE)) 
    ~ "fleas_number",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**4.** **Ticks Load**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("tick load in the nest*", ignore_case = TRUE)) 
    ~ "tick_load",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 5. **Number of blowfly**

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("\\bblowfl(ies|y)\\b", ignore_case = TRUE)) ~ "blowflies_number",
    str_detect(fitness_proxy, regex("Protocalliphora*", ignore_case = TRUE)) ~ "blowflies_number",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 6. **Number of blowflies parasitoids**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("blowfly parasitoid*", ignore_case = TRUE)) 
    ~ "blowfly_parasitoids_number",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 7. **Number of Midges**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of biting midges*", ignore_case = TRUE)) 
    ~ "midges_number",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 8. **Number of Blackflies**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of blackfl*", ignore_case = TRUE)) 
    ~ "blackflies_number",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 9. **Carnus flies load**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("Log Carnus flies*", ignore_case = TRUE)) 
    ~ "carnusflies_load",
    str_detect(fitness_proxy, regex("carnus*", ignore_case = TRUE)) 
    ~ "carnusflies_load",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 10. **Bacterial Load**

There are several different kinds of bacterial that authors have measures like enterococcus/enterobacteria or mesophilic bacterial. In some cases authors do not give description of what bacteria they measure the load for.

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("total bacterial load*", ignore_case = TRUE)) 
    ~ "bacterial_load",
    str_detect(fitness_proxy, regex("bacteria load*", ignore_case = TRUE)) 
    ~ "bacterial_load",
     str_detect(fitness_proxy, regex("load of enterobacteria*", ignore_case = TRUE)) 
    ~ "bacterial_load",
     str_detect(fitness_proxy, regex("log mesophilic bacteria*", ignore_case = TRUE)) 
    ~ "bacterial_load",
     str_detect(fitness_proxy, regex("log enterococcus*", ignore_case = TRUE)) 
    ~ "bacterial_load",
      str_detect(fitness_proxy, regex("mesophilic bacterial density (log)*", 
                                      ignore_case = TRUE)) 
    ~ "bacterial_load",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 11. **Bacterial Richness**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("bacterial_richness*", ignore_case = TRUE)) 
    ~ "bacterial_richness",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 12. **Bacterial Increase**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("bacterial increase*", ignore_case = TRUE)) 
    ~ "bacterial_increase",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 13. **Scab Score**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("\\bscab(s)?\\b", ignore_case = TRUE)) ~ "scab_score",   
    str_detect(fitness_proxy, regex("scab_score", ignore_case = TRUE)) ~ "scab_score",   
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

#### 1. **Haemoglobin Measure**

Hematocrit level is combined here with haemoglobin concentration as "hemoglobin_measure". Hematocrit is measured as a percentage as compared to Haemoglobin which is a w/V concentration.

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("hemoglobin concentration*", ignore_case = TRUE)) 
    ~ "hemoglobin_measure",
    str_detect(fitness_proxy, regex("blood haemoglobin*", ignore_case = TRUE)) 
    ~ "hemoglobin_measure",
     str_detect(fitness_proxy, regex("heamatocrit percent*", ignore_case = TRUE)) 
    ~ "hemoglobin_measure",
    str_detect(fitness_proxy, regex("hematocrit level*", ignore_case = TRUE)) 
    ~ "hemoglobin_measure",
    str_detect(fitness_proxy, regex("haematocrit", ignore_case = TRUE)) 
    ~ "hemoglobin_measure",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### **2. Glucose Measure**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("glucose concentration*", ignore_case = TRUE)) 
    ~ "glucose_measure",
     TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### **5. Nestling Immunity**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling PHA*" , ignore_case = TRUE)) 
   # PHA is phytohaemagglutinin and single-wing phytohaemagglutinin is used as a measure of immunity in avian biology: 
   # Smits, J.E., Bortolotti, G.R. and Tella, J.L. (1999), Simplifying the phytohaemagglutinin skin-testing technique in studies of avian immunocompetence. Functional Ecology, 13: 567-572. https://doi.org/10.1046/j.1365-2435.1999.00338.x
   ~ "nestling_immunity",
   str_detect(fitness_proxy, regex("Phytohaemagglutinin*" , ignore_case = TRUE)) 
   ~ "nestling_immunity",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### **7. Nestling Leukocytes**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling leukocyte*" , ignore_case = TRUE)) 
   ~ "nestling_leukocytes",
   str_detect(fitness_proxy, regex("WBC measure of nestlings" , ignore_case = TRUE)) 
   ~ "nestling_leukocytes",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### **8. Chick Feather Development**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("chick feather development*" , ignore_case = TRUE)) 
   ~ "chick_feather_development",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### **9. Development Score**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("meandevoscore*" , ignore_case = TRUE)) 
   ~ "clutch_development_score",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### **11. Telomere measure**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Rank telomere length*" , 
                                   ignore_case = TRUE)) 
   ~ "telomere_measure",
   str_detect(fitness_proxy, regex("Rank difference in Telomere length*" , 
                                   ignore_case = TRUE))
   ~ "telomere_measure",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### **12. Fat Score**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("fat score*" , ignore_case = TRUE)) 
   ~ "fat_score",
   TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

```{r}
#| echo: false

# # kable(as.data.frame(summary(as.factor
#                             (na.omit(
#                               dataset_after_cleaning$fitness_proxy_cleaned)))),
#       col.names=("Number of effect sizes"),
#       caption = "Proxies of fitness")

# The variable variable_notes contains additional information about the variable like if it is a mean value, log value or a score/PCA etc.
```

## We excluded some proxies from our dataset

```{r excluded proxies, echo=F}

unique(dataset_after_cleaning$proxy_decision)

excluded_proxies <- dataset_after_cleaning %>% filter(proxy_decision=="exclude" | proxy_decision=="exclude_NA" | proxy_decision=="excluded_NA" )

excluded_proxies%>%
  select(c(paper_ID,fitness_proxy,proxy_comment))%>%
  kable(col.names=(c("Paper ID","Fitness Trait","Reason for exclusion" )),caption = "Excluded proxies")

dataset_after_cleaning <- dataset_after_cleaning %>% 
  filter(!proxy_decision %in% c("exclude", "exclude_NA", "excluded_NA"))

 unique(dataset_after_cleaning$proxy_decision) 
```

### Adding Observation ID column

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(Observation_ID=row_number(), .before = experiment_ID)

```

### Adding Hypothesis column

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(Hypothesis= case_when(
      CH == 1 & PCH == 0 ~ "CH",   
      CH == 0 & PCH == 1 ~ "PCH",  
      CH == 1 & PCH == 1 ~ "both") 
    ,.after = PCH)

#checked, has no NAs
```

#### Cleaning Type of trait studied

(levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology)

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(trait_type = case_when(
    str_detect(trait_type, regex("physiology", ignore_case = TRUE)) ~ "Physiology",
    str_detect(trait_type, regex("reproduction", ignore_case = TRUE)) ~ "Reproduction",
    str_detect(trait_type, regex("morphology", ignore_case = TRUE)) ~ "Morphology",
    str_detect(trait_type, regex("parasite.*pathogenic|parasitic.*pathogenic", ignore_case = TRUE)) ~ "Parasitic_and_pathogenic",
    str_detect(trait_type, regex("behaviour", ignore_case = TRUE)) ~ "Behaviour",
    str_detect(trait_type, regex("phenology", ignore_case = TRUE)) ~ "Phenology",
    TRUE ~ as.character(trait_type)
  ))
```

### Adding Type of parasites

(levels: arthropods, micro-organisms)

```{r}

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(parasite_type= case_when(
    str_detect(parasite_type, regex("arthropod", ignore_case = TRUE)) ~ "Arthropod",
    str_detect(parasite_type, regex("micro[- ]?organism|microoragnism", ignore_case = TRUE)) ~ "Micro-organism",
    is.na(parasite_type) ~ NA_character_,  # Keep NA as it is
    TRUE ~ as.character(parasite_type)    # Retain other values (optional, if needed)
  ))
```

### Time of addition of green nest material

(levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).

### Type of experimental design

(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).

### Bird species

(levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(bird_species= case_when(
    str_detect(bird_species, regex("Cyanistes caeruleus, Parus major", ignore_case = TRUE)) ~ "Cyanistes caeruleus",
    str_detect(bird_species, regex("Cyanistes caeruleus|Cyanistes_caeruleus", ignore_case = TRUE)) ~ "Cyanistes caeruleus",
    str_detect(bird_species, regex("Sturnus unicolor|Sturnus_unicolor", ignore_case = TRUE)) ~ "Sturnus unicolor",
        str_detect(bird_species, regex("Sturnus vulgaris|Sturnus_vulgaris", ignore_case = TRUE)) ~ "Sturnus vulgaris",
    TRUE ~ as.character(bird_species)
  ))
```

Whichever between Cyanistes caeruleus and Parus major is higher.. assign that..

## Some quick checks to make sure all names are clean

```{r}
unique(dataset_after_cleaning$proxy_decision)

## found a typo, let's fix:

dataset_after_cleaning <- dataset_after_cleaning %>%
  mutate(proxy_decision = case_when(
    proxy_decision == "senstivity-analysis" ~ "sensitivity-analysis",
    TRUE ~ proxy_decision
  ))

## And now
unique(dataset_after_cleaning$proxy_decision)
```

### Saving dataset

```{r}
write.csv(dataset_after_cleaning,file=here::here("data/03_data_cleaning/dataset_after_cleaning.csv"),row.names = FALSE)
```

### 2025-07-05 docs/notebook/data_analysis.qmd
Updated Introduction/Methods completed Added all the codes and data files to the folder. Can publish directly from here for later..

@@
 # install.packages("devtools")
-#devtools::install_github("davidsjoberg/ggsankey")
+devtools::install_github("davidsjoberg/ggsankey")
 library(ggsankey)
@@
 ## For lnRR complete dataset
-VCV_lnRR_published<- vcalc(vi = lnRR_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_lnRR_published,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-all_in_lnRR <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ - 1 + time_of_gnm_addition + 
+
+## I am changing the year of unpublished studies to 2025 which is to now, assuming that if they were to be published now, what would be the effect.
+I will keep in mind that in this model if I do find an evidence of publication bias over years, I should keep in mind it is non-independent of the unpublished studies
+
+dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+
+VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition + 
                       year_MeanCenter + 
                       sqrt_effective_n_inv + 
-                      comparision_type + 
+                      as.factor(comparision_type) + 
                       bird_species + 
@@
                     test = "t",
-                    data = dataset_lnRR_published)
+                    data = dataset_lnRR_all_in)
 
 ## For SMDH complete published dataset
-VCV_SMDH_published<- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH_published,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-all_in_SMDH<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ - 1 + time_of_gnm_addition + 
+
+dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+
+VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition + 
                       year_MeanCenter + 
                       sqrt_effective_n_inv + 
-                      comparision_type + 
+                      as.factor(comparision_type) + 
                       bird_species + 
@@
                     test = "t",
-                    data = dataset_SMDH_published)
-```
+                    data = dataset_SMDH_all_in)
+```

### 2025-07-05 docs/notebook/figures.qmd
Updated Introduction/Methods completed Added all the codes and data files to the folder. Can publish directly from here for later..

@@
 devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
-pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot)
+pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot,maps)
 
@@
 
-lnRR_design_plot <-
-  orchard_plot(mod_results(
-      lnRR_design,
-      mod = "comparision_type",
-      group = "paper_ID"
-    ), xlab ="") +
-  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
-  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
-  labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 7),
-    legend.text = element_text(size = 7),
-    axis.title = element_text(size = 12),
-    axis.text.x = element_text(size = 12),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","Aromatic Vs. Blank", "Non-Aromatic Vs. Blank"))
-
-SMDH_design_plot <-
-  orchard_plot(mod_results(
-      SMDH_design,
-      mod = "comparision_type",
-      group = "paper_ID"
-    ), xlab ="") +
-  scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
-  scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
-  labs(x = "",
-       y = "SMDH")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 7),
-    legend.text = element_text(size = 7),
-    axis.title = element_text(size = 12),
-    axis.text.x = element_text(size = 12),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  )
+# lnRR_design_plot <-
+#   orchard_plot(mod_results(
+#       lnRR_design,
+#       mod = "comparision_type",
+#       group = "paper_ID"
+#     ), xlab ="") +
+#   scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
+#   scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
+#   labs(x = "",
+#        y = "lnRR")+
+#     theme(
+#     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+#     legend.position = "none",
+#     # legend.position.inside = c(0.98, 0.05),
+#     # legend.justification = c(1, 0), 
+#     # legend.direction = "horizontal",
+#     legend.title = element_text(size = 7),
+#     legend.text = element_text(size = 7),
+#     axis.title = element_text(size = 12),
+#     axis.text.x = element_text(size = 12),
+#     axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
+#   ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","Blank Vs. Aromatic", "Blank Vs. Non-Aromatic"))
+# 
+# SMDH_design_plot <-
+#   orchard_plot(mod_results(
+#       SMDH_design,
+#       mod = "comparision_type",
+#       group = "paper_ID"
+#     ), xlab ="") +
+#   scale_colour_manual(values = c( "#218833","mediumpurple4","#895129")) +
+#   scale_fill_manual(values = c( "#218833","mediumpurple4","#895129")) +
+#   labs(x = "",
+#        y = "SMDH")+
+#     theme(
+#     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+#     legend.position = "none",
+#     # legend.position.inside = c(0.98, 0.05),
+#     # legend.justification = c(1, 0), 
+#     # legend.direction = "horizontal",
+#     legend.title = element_text(size = 7),
+#     legend.text = element_text(size = 7),
+#     axis.title = element_text(size = 12),
+#     axis.text.x = element_text(size = 12),
+#     axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
+#   )
 
@@
 
-## I am going to remove the y ticks from the SMDH plots to make it smaller..
-SMDH_design_plot <- SMDH_design_plot +
-  theme(axis.text.y  = element_blank(),
-        axis.title.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
-  theme(axis.text.y  = element_blank(),
-        axis.title.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-# Combine using patchwork
-Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
-                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
-  plot_annotation(tag_levels = "A")
-
-ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 300, width = 400, units = "mm", dpi = 600)
-
+# ## I am going to remove the y ticks from the SMDH plots to make it smaller..
+# SMDH_design_plot <- SMDH_design_plot +
+#   theme(axis.text.y  = element_blank(),
+#         axis.title.y = element_blank(),
+#         axis.ticks.y = element_blank())
+# 
+# SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
+#   theme(axis.text.y  = element_blank(),
+#         axis.title.y = element_blank(),
+#         axis.ticks.y = element_blank())
+# 
+# # Combine using patchwork
+# Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
+#                                (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
+#   plot_annotation(tag_levels = "A")
+# 
+# ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 300, width = 400, units = "mm", dpi = 600)
+#        
 ```

### 2025-07-05 manuscript_GNM.qmd
Some info added to manuscript.. trying to fix supplementary material.
Updated Introduction/Methods completed Added all the codes and data files to the folder. Can publish directly from here for later..

@@
 ---
+
+# Abstract
+
+According to PRISMA Checklist.. I must:
+
+-   Summarise the aims and scope of the review
+
+-   Describe the data set
+
+-   State the results of the primary outcome
+
+-   State conclusions
+
+-   State limitations
 
@@
 devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
-pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
+pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork,english)
 source(here::here("functions/extractor_metareg.R"))
-```
-
-```{r load search data, include=FALSE, echo=FALSE, message= FALSE}
-
-# Own reference list
-own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv")
-
-# Systematic search and abstract screening
-unique_reference_list <- read_csv("data/unique_reference_list.csv")
-full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
-selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
-
-# For updated search
-unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
-full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
-selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")
-
-# For fulltext screening
-excluded_fulltext <- read_csv("data/excluded_fulltext.csv")
 ```
@@
 Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist).
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist and @figsupp-prisma-flow).
 All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
@@
 
-We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022.
-The keyword search query was designed as a three-block query to included terms related to the predictor/treatment (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), our population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit it to only experimental studies only ("experiment\*" OR "manipulat\*").
+```{r load search data, include=FALSE, echo=FALSE, message= FALSE}
+
+# Own reference list
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv")
+
+# Systematic search and abstract screening
+unique_reference_list <- read_csv("data/01_systematic_search/02_reference_data/unique_reference_list.csv")
+full_reference_before_deduplication<-read_csv("data/01_systematic_search/02_reference_data/full_reference_before_deduplication.csv")
+selected_abstract_screening<-read_csv("data/01_systematic_search/03_title_and_abstract_screening/selected_abstract_screening.csv")
+
+# For updated search
+unique_reference_list_repeat <- read_csv("data/01_systematic_search/04_search_repeat_12082024/unique_reference_repeat_12082024.csv")
+full_reference_before_deduplication_repeat<-read_csv("data/01_systematic_search/04_search_repeat_12082024/full_reference_repeat_12082024.csv")
+selected_abstract_screening_repeat<-read_csv("data/01_systematic_search/04_search_repeat_12082024/selected_abstract_screening_repeat.csv")
+
+# For fulltext screening
+excluded_fulltext <- read_csv("data/01_systematic_search/03_title_and_abstract_screening/excluded_fulltext.csv")
+```
+
+We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022 (see update below).
+The keyword search query was designed as a three-block query to include terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
@@
 We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package 'litsearchr' v1.0.0 (@grames2019) to confirm our keyword selection, which did not yield any new relevant terms.
-We found `{r} nrow(unique_reference_list)` unique articles after removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 (@westgate2019).
+Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, to confirm our keyword selection.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 [@westgate2019], we found `{r} nrow(unique_reference_list)` unique records.
 
@@
 
-All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree (@figsupp-decision-tree).
+All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
 We included all studies on birds that experimentally manipulated the green nest material (both aromatics or herbs).
-`{r} nrow(selected_abstract_screening)` articles passed the title-and-abstract screening and were further evaluated during the full-text screening.
-Each article was screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
-We used the same criteria as above (see @figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
-`{r} nrow(excluded_fulltext)` articles were excluded.
+`{r} tools::toTitleCase(as.character(english::english(nrow(selected_abstract_screening))))` articles passed the title-and-abstract screening and were further evaluated during the full-text screening, where each article was independently screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
+We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
+`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` passed the full-text screening and were, thus, eligible for our meta-analysis.
 All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
 
-To update our systematic lietrature search, we repeated our search on 12.08.2024.
-This updated search found `{r} nrow(unique_reference_list_repeat)` unique articles after removing ``` {r} nrow(full_reference_before_deduplication_repeat)-``nrow(unique_reference_list_repeat) ``` duplicates.
-Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article.
-Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles.
-In all, X <!--# Fill the no.
-of articles that are included --> articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
+We updated our systematic literature search by repeating our search on 12.08.2024.
+We found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
+Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before (@figsupp-decision-tree), and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article for our meta-analysis.
+Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles through other sources (i.e., identified through a poster by a collaborator and through an independent recommendation by a colleague).
+In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
 
@@
 
-dataset_after_cleaning <- merged_data_extraction %>% filter(fulltext_screening!="excluded")
+dataset_after_cleaning <- read_csv("data/03_data_cleaning/dataset_after_cleaning.csv", show_col_types = F)
 included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
@@
 
-excluded_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="exclude")
-SAonly_proxies<- dataset_after_cleaning %>% filter(proxy_decision=="senstivity-analysis" | proxy_decision=="sensitivity-analysis")
+excluded_proxies<- merged_data_extraction %>%
+  filter(fulltext_screening == "included" |
+         is.na(fulltext_screening) |
+         fulltext_screening == "NA") %>%
+  filter(proxy_decision== "exclude")
+
+dataset_analysis <- read_csv("data/04_data_analysis/dataset_analysis.csv", show_col_types = F)
+
+SAonly_proxies<- dataset_analysis %>% filter(proxy_decision=="sensitivity-analysis")
+
+inferential_only<- dataset_analysis%>%filter(statistics_type=="t-test"|statistics_type=="ANCOVA")
+
+contingency_table<-dataset_analysis%>%filter(proxy_decision=="contingency table")
+
+raw_data<-c("GNM_001_rep_table3","GNM_010","GNM_069","GNM_237") 
+#GNM_018 also provides open data but we ended up not needing it
+
+published_studies <- dataset_analysis %>%
+  filter(!str_detect(paper_ID, "Unpublished"))
+
+unpublished_studies <- dataset_analysis %>%
+  filter(str_detect(paper_ID, "Unpublished"))
+
 ```
@@
 The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
-We extracted the primary data (i.e., measures of central tendency, variance and sample size) from text whenever possible.
-In cases where primary data was only available in figures (e.g., boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
-If primary data was not available, we extracted any inferential statistics (t value, F value) that could be transformed into an effect size.
-In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the provided raw data.
-When data was presented in different sources (e.g.
-in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).
+We prioritised extracting the primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package `metaDigitise` v.1.0.1 (@pick2018).
+If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), that could be transformed into an effect size.
+Last, if the previous steps failed but the article has openly shared datasets (n = `{r} length(raw_data)`), we calculated the means, SD and sample sizes from them.
+**When data was presented in different sources (e.g.
+in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).**
 
@@
 Treatments consisted of aromatic materials added by authors, birds, or both.
-In cases comparing non-aromatic material to a blank nest, the non-aromatic material was considered the treatment.
+For cases that compared non-aromatic material to where authors did not add any additional nest material and any material added by the birds was removed, the non-aromatic material was considered the treatment.
 We recorded the type of comparison being made as a moderator.
+For each study, we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, or supplementary materials).
+We categorised the fitness proxies measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
+For studies testing whether green nest material affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
+For a complete list of variables extracted see @figsupp-variables .
+We did not include some traits in all our analyses because it was unclear how they related to fitness (k = `{r} nrow(excluded_proxies)` , n = `{r} length(unique(excluded_proxies$paper_ID))`; see @figsupp-excluded-proxies for the list and reasons of exclusion).
 
-For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and information about the extracted data (location or source of the data recorded).
-We categorized the fitness proxy measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load and phenology.
-For parasites or pathogens, we categorised them into arthropods or micro-organisms.
-For a complete list of variables extracted see @figsupp-variables .
-We did not include some traits in all our analyses becaause it was unclear how they related to fitness (k=`{r} nrow(excluded_proxies)` , n=`{r} length(unique(excluded_proxies$paper_ID))`;see @figsupp-excluded-proxies for the list and reason of exclusion).
-We also had to exclude some effect sizes (n=?, k=?) because of the low sample size per group (less than x).
-
-To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
-unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
-We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
-All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
-In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
+To obtain missing data (e.g., non-reported results, missing sample sizes, etc.), we contacted four authors.
+All four authors responded to our email, but only two provided the data as requested; one did not have the data any more, and one did not give a conclusive response.
+Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))`) to ask for any potential unpublished data that could be included in our meta-analysis.
+One corresponding author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO), provided data for another unpublished study.
 In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
+Author correspondance was performed using a standardised email template (@figsupp-email).
+In all, we extracted data for `{r} length(unique(published_studies$paper_ID))` published articles (k = `{r} nrow(published_studies)`) and `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`).
 
@@
 
-inferential_stats<-dataset_after_cleaning%>%filter(statistics_type=="t-test"|statistics_type=="ANCOVA")
+no_ES<-dataset_analysis%>%filter(proxy_comment == "use 0 as ES")
 
-contingency_table<-dataset_after_cleaning%>%filter(proxy_decision=="contingency table")
-
-no_ES<-dataset_after_cleaning%>%filter(proxy_comment == "use 0 as ES")
-
-negative_lnRR<-dataset_after_cleaning%>%
+negative_lnRR<-dataset_analysis%>%
   filter(measure_central_tendency_experiment<=0 | measure_central_tendency_control<=0)
 
+low_sample<-dataset_analysis%>%filter(is.na(SMDH_sign))
+
+dataset_lnRR <- read_csv("data/04_data_analysis/dataset_lnRR.csv", show_col_types = F)
+
+dataset_SMDH <- read_csv("data/04_data_analysis/dataset_SMDH.csv", show_col_types = F)
 ```
 
-We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` (@metafor).
+We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` [@metafor].
 We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that positive values indicate the 'fitness' value increased in the treatment group.
@@
 In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
+SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance— specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1 (excluded k = `{r} nrow(low_sample)`, n = `{r} length(unique(low_sample$paper_ID))`)
 
-For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k=`{r} nrow(inferential_stats)`, n=`{r} length(unique(inferential_stats$paper_ID))`) using the equations provided by @thehand2019.
-For dichotomous variables (e.g., number of successful nests, k= `{r} nrow(contingency_table)`, n= `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k=`{r} nrow(negative_lnRR)`, n=`{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k=?, n=?) subset is smaller than that of SMDH (k=?,n=?).
+For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) using the equations provided by @thehand2019.
+For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`, n = `{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
 
@@
 In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
-For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k=`{r} nrow(no_ES)`, n=`{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparision and imputed its SD using the missing-case approach described in @nakagawa2022.
+For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k = `{r} nrow(no_ES)`, n = `{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparison and imputed its sampling variance using the missing-case approach described in @nakagawa2022 for lnRR and using $\frac{n_1+n_2}{n_1×n_2}$ for SMD [@lajeunesse2013].
 
@@
 
-We performed all analyses in R version 4.3.0 (@positteam2023).
-All multilevel meta-analytical models and meta-regressions were fit using `metafor v.4.8-0` (@metafor).
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the `vcalc` function from `metafor`.
+We performed all analyses in R version 4.5.1 [@R-version].
+All multilevel meta-analytical models and meta-regressions were fit using metafor v.4.8-0 [@metafor].
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the vcalc function from metafor.
 (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
-We considered the following levels of non-independence for our analyses: (a) multiple effect sizes collected from same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) some sub-populations (Experiment ID; e.g.
-birds studied at the same location for multiple years or birds studied at the same location separated by distance) and (e) group of individuals (Group ID; eg.
-males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) some traits were collected on the same group of animals repeatedly (Repeated trait ID; e.g.
+We considered the following levels of non-independence for our analyses: multiple effect sizes collected from (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g.
+birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; eg.
+males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g.
 chick mass on day 7, 14 and 21).
@@
 
-To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMDH.
+To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
 Thus, throughout, we fitted two separate sets of model for each effect size.
@@
 We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k=`{r} nrow(SAonly_proxies)` , n=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies).
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
 For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
-
-<!--# You have to correct the numbers for contingency table. It does not include the one data point from unpublished results -->
 
@@
 To test the relative importance of the two main hypotheses suggested for green nest material: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
-For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators (@nakagawa2012).
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
 
@@
 
+```{r}
+parasite_pathogen<-dataset_after_cleaning%>%filter(trait_type=="Parasitic_and_pathogenic")
+```
+
 We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
-To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (n=?, k=?).
+To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`).
 We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
-We also ran a meta-regression with with the entire dataset set using bird species as a moderator (levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris, Parus major, Passer cinnamomeus, Buteo buteo) to understand if the effect of green nest material on fitness depended on the system being studied.
-To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
-We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We also ran a meta-regression with the entire dataset set using bird species as a moderator (levels: *Buteo buteo*, *Cyanistes caeruleus*, *Passer cinnamomeus*, *Parus major*, *Sturnus unicolor*, *Sturnus vulgaris*, *Tachycineta bicolor*) to understand if the effect of green nest material on fitness depended on the system being studied.
+To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with Time of addition of green nest material as the moderator.
+We explored the effect of green nest material on fitness depending on the type of trait studies (levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
 We explored the impact of methodological differences on the relationship between green nest material and fitness.
@@
 ```{r review-results}
-dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")
 
@@
 About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
-Our dataset included two unpublished studies (k=XX effect sizes), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean (±SD) number of effect sizes per study was `{r} as.numeric(format(mean(ES_per_study$n), digit=3))` ± `{r} as.numeric(format(sd(ES_per_study$n), digit=2))`(range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean sample size per effect size were `{r} median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))` and `{r} as.numeric(format(mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)), digit=3))` respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
+Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
+The mean (±SD) number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean effective sample size (i.e.
+after accounting for shared-group non-independence) were `{r} sprintf("%.1f", median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))` and `{r} sprintf("%.1f",mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))`, respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
 
@@
 
+Summary of the results.. wrap up with a few points
+
+Second paragraph
+
+-   Discussing your results.. effect sizes
+
+-   Difference between the hypothesis, whether you can do it or not
+
+-   Experimental design difference.. importance of aromatic vs. Non-aromatic (are the same that aroma per say) and time of addition
+
+    Third paragraph :
+
+How much heterogeneity is explained..
+
+Limitations and issues about the data.. mechanism, publication bias.. species are few tested, few labs..
+
+Proxies that are closer..
+
+If study ID is
+
 Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased green nest material, though the strength of these effects depended on the effect size metric used.
 SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
-Importantly, our results reveal that the commonly studied mechanistic hypotheses of green nest material---whether through sexual signaling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of green nest material---whether through sexual signalling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
 
@@
 
-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--
+------------------------------------------------------------------------
 
-## Supplementary Appendix
+# Supplementary Appendix
 
@@
 
-<details>
+### PRISMA Checklist
 
-<summary>Supplementary materials</summary>
+Check with the online prisma list at <https://arc.net/l/quote/zhrgrlso>
 
-{{< include supplementary_appendix.qmd >}}
+Some items might be missing in the list, confirm as you fill...
 
-</details>
+::: {#figsupp-checklist .table}
+|  |  |  |  |  |  |
+|------------|------------|------------|------------|------------|------------|
+| **Checklist item** | I**tem score** | **Sub-item number** | **Sub-item** | **Reported by authors?** | **Notes** |
+| **Title and abstract** | **100%** | 1.1 | Identify the review as a systematic review, meta-analysis, or both | Yes | Identified in title and in abstract as both a systematic review and a meta-analysis |
+|  |  | 1.2 | Summarise the aims and scope of the review | Yes | In the abstract |
+| 1.3 | Describe the data set | Yes | In the abstract |  |  |
+| 1.4 | State the results of the primary outcome | Yes | In the abstract |  |  |
+|  |  | 1.5 | State conclusions | Yes | In the abstract |
+|  |  | 1.6 | State limitations | Yes | In the abstract |
+| **Aims and questions** | **100%** | 2.1 | Provide a rationale for the review | Yes | Rationale explained in the Introduction in detail |
+|  |  | 2.2 | Reference any previous reviews or meta-analyses on the topic | Yes | Clearly stated twice in the introduction |
+|  |  | 2.3 | State the aims and scope of the review (including its generality) | Yes | Scope (only birds and experimental studies) explained in the aims in the last paragraph of Introduction |
+|  |  | 2.4 | State the primary questions the review addresses (e.g.
+which moderators were tested) | Yes | Moderators tested are clearly stated in the last paragraph of the introduction and the methods in data analysis section.
+|
+|  |  | 2.5 | Describe whether effect sizes were derived from experimental and/or observational comparisons | Yes | Only experimental studies were selected, described in the last paragraph of introduction as well as the methods |
+| **Review registration** | **100%** | 3.1 | Register review aims, hypotheses (if applicable), and methods in a time-stamped and publicly accessible archive and provide a link to the registration in the methods section of the manuscript.
+Ideally registration occurs before the search, but it can be done at any stage before data analysis.
+| Yes | <https://doi.org/10.17605/OSF.IO/S7J6Z> |
+|  |  | 3.2 | Describe deviations from the registered aims and methods | Yes | Described in methods wherever applicable |
+|  |  | 3.3 | Justify deviations from the registered aims and methods | Yes | When applicable, described in the methods |
+| **Eligibility criteria** | **0%** | 4.1 | Report the specific criteria used for including or excluding studies when screening titles and/or abstracts, and full texts, according to the aims of the systematic review (e.g.
+study design, taxa, data availability) | No |  |
+|  |  | 4.2 | Justify criteria, if necessary (i.e. not obvious from aims and scope. | No |  |
+| **Finding studies** | **0%** | 5.1 | Define the type of search (e.g. comprehensive search, representative sample) | No |  |
+|  |  | 5.2 | State what sources of information were sought (e.g. published and unpublished studies, personal communications) | No |  |
+|  |  | 5.3 | Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators | No |  |
+|  |  | 5.4 | Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates) | No |  |
+| **Study selection** | **0%** | 6.1 | Describe how studies were selected for inclusion at each stage of the screening process (e.g. use of decision trees, screening software) | No |  |
+|  |  | 6.2 | Report the number of people involved and how they contributed (e.g. independent parallel screening) | No |  |
+| **Data collection process** | **0%** | 7.1 | Describe where in the reports data were collected from (e.g. text or figures) | No |  |
+|  |  | 7.2 | Describe how data were collected (e.g. software used to digitize figures, external data sources) | No |  |
+| 7.3 | Describe moderator variables that were constructed from collected data (e.g. number of generations calculated from years and average generation time) | No |  |  |  |
+| 7.4 | Report how missing or ambiguous information was dealt with during data collection (e.g.
+authors of original studies were contacted for missing descriptive statistics, and/or effect sizes were calculated from test statistics) | No |  |  |  |
+|  |  | 7.5 | Report who collected data | No |  |
+| **Data items** | 0% | 8.1 | Describe the key data sought from each study | No |  |
+|  |  | 8.2 | Describe items that do not appear in the main results, or which could not be extracted due to insufficient information | No |  |
+| 8.3 | Describe main assumptions or simplifications that were made (e.g. categorising both 'length' and 'mass' as 'morphology') | No |  |  |  |
+|  |  | 8.4 | Describe the type of replication unit (e.g. individuals, broods, study sites) | No |  |
+| **Assessment of individual study quality** | **0%** | 9.1 | Describe whether the quality of studies included in the systematic review or meta-analysis was assessed (e.g.
+blinded data collection, reporting quality, experimental versus observational) | No |  |
+|  |  | 9.2 | Describe how information about study quality was incorporated into analyses (e.g. meta-regression and/or sensitivity analysis) | No |  |
+| **Effect size measures** | **0%** | 10.1 | Describe effect size(s) used | No |  |
+|  |  |  |  |  |  |
+|  |  | 10.2 | Provide a reference to the equation of each calculated effect size (e.g. standardised mean difference, log response ratio) and (if applicable) its sampling variance | No |  |
+| **Missing data** | **0%** | 11.1 | Describe any steps taken to deal with missing data during analysis (e.g. imputation, complete case, subset analysis) | No |  |
+|  |  | 11.2 | Justify the decisions made to deal with missing data | No |  |
+| **Meta-analytic model description** | **0%** | 12.1 | Describe the models used for synthesis of effect sizes | No |  |
+|  |  |  |  |  |  |
+|  |  | 12.2 | The most common approach in ecology and evolution will be a random-effects model, often with a hierarchical/multilevel structure.
+If other types of models are chosen (e.g.
+common/fixed effects model, unweighted model), provide justification for this choice | No |  |
+| **Software** | **0%** | 13.1 | Describe the statistical platform used for inference (e.g. R) | No |  |
+|  |  | 13.2 | Describe the packages used to run models | No |  |
+| Describe the functions used to run models | No |  |  |  |  |
+| 13.4 | Describe any arguments that differed from the default settings | No |  |  |  |
+|  |  | 13.5 | Describe the version numbers of all software used | No |  |
+| **Non-independence** | **0%** | 14.1 | Describe the types of non-independence encountered (e.g. phylogenetic, spatial, multiple measurements over time) | No |  |
+|  |  |  |  |  |  |
+|  |  | 14.2 | Describe how non-independence has been handled | No |  |
+|  |  |  |  |  |  |
+| 14.3 | Justify decisions made | No |  |  |  |
+|  |  |  |  |  |  |
+| **Meta-regression and model selection** | **0%** | 15.1 | Provide a rationale for the inclusion of moderators (covariates) that were evaluated in meta-regression models | No |  |
+|  |  |  |  |  |  |
+|  |  | 15.2 | Justify the number of parameters estimated in models, in relation to the number of effect sizes and studies (e.g.
+interaction terms were not included due to insufficient sample sizes) | No |  |
+|  |  |  |  |  |  |
+| 15.3 | Describe any process of model selection | No |  |  |  |
+|  |  |  |  |  |  |
+| **Publication bias and sensitivity analysis** | **0%** | 16.1 | Describe assessments of the risk of bias due to missing results (e.g. publication, time-lag, and taxonomic biases) | No |  |
+|  |  |  |  |  |  |
+|  |  | 16.2 | Describe any steps taken to investigate the effects of such biases (if present) | No |  |
+|  |  |  |  |  |  |
+| 16.3 | Describe any other analyses of robustness of the results, e.g.
+due to effect size choice, weighting or analytical model assumptions, inclusion or exclusion of subsets of the data, or the inclusion of alternative moderator variables in meta-regressions | No |  |  |  |
+|  |  |  |  |  |  |
+| **Clarification of post hoc analyses** | **0%** | 17.1 | When hypotheses were formulated after data analysis, this should be acknowledged. | No |  |
+|  |  |  |  |  |  |
+| **Metadata, data, and code** | 18.1 | Share metadata (i.e. data descriptions) | No |  |  |
+|  |  |  |  |  |  |
+|  |  | 18.2 | Share data required to reproduce the results presented in the manuscript | No |  |
+|  |  |  |  |  |  |
+| Share additional data, including information that was not presented in the manuscript (e.g.
+raw data used to calculate effect sizes, descriptions of where data were located in papers) | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 18.4 | Share analysis scripts (or, if a software package with graphical user interface (GUI) was used, then describe full model specification and fully specify choices) | No |  |  |  |
+|  |  |  |  |  |  |
+| **Results of study selection process** | **0%** | 19.1 | Report the number of studies screened | No |  |
+|  |  |  |  |  |  |
+|  |  | 19.2 | Report the number of studies excluded at each stage of screening | No |  |
+|  |  |  |  |  |  |
+| Report brief reasons for exclusion from the full text stage | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 19.4 | Present a Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)-like flowchart (www.prisma-statement.org). | No |  |  |  |
+|  |  |  |  |  |  |
+| **Sample sizes and study characteristics** | **0%** | 20.1 | Report the number of studies and effect sizes for data included in meta-analyses | No |  |
+|  |  |  |  |  |  |
+|  |  | 20.2 | Report the number of studies and effect sizes for subsets of data included in meta-regressions | No |  |
+|  |  |  |  |  |  |
+| Provide a summary of key characteristics for reported outcomes (either in text or figures; e.g. one quarter of effect sizes reported for vertebrates and the rest invertebrates) | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 20.4 | Provide a summary of limitations of included moderators (e.g. collinearity and overlap between moderators) | No |  |  |  |
+|  |  |  |  |  |  |
+| 20.5 | Provide a summary of characteristics related to individual study quality (risk of bias) | No |  |  |  |
+|  |  |  |  |  |  |
+| **Meta-analysis** | **0%** | 21.1 | Provide a quantitative synthesis of results across studies, including estimates for the mean effect size, with confidence/credible intervals | No |  |
+|  |  |  |  |  |  |
+| **Heterogeneity** |  |  |  |  |  |
+|  |  |  |  |  |  |
+| **Meta-regression** | 23.1 | Provide estimates of meta-regression slopes (i.e. regression coefficients) and confidence/credible intervals | No |  |  |
+|  |  |  |  |  |  |
+|  |  | 23.2 | Include estimates and confidence/credible intervals for all moderator variables that were assessed (i.e. complete reporting) | No |  |
+|  |  |  |  |  |  |
+| Report interactions, if they were included | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 23.4 | Describe outcomes from model selection, if done (e.g. R2 and AIC) | No |  |  |  |
+|  |  |  |  |  |  |
+| **Outcomes of publication bias and sensitivity analysis** | **0%** | 24.1 | Provide results for the assessments of the risks of bias (e.g. Egger's regression, funnel plots) | No |  |
+|  |  |  |  |  |  |
+|  |  | 24.2 | Provide results for the robustness of the review's results (e.g.
+subgroup analyses, meta-regression of study quality, results from alternative methods of analysis, and temporal trends) | No |  |
+|  |  |  |  |  |  |
+| **Discussion** | **0%** | 25.1 | Summarise the main findings in terms of the magnitude of effect | No |  |
+|  |  |  |  |  |  |
+|  |  | 25.2 | Summarise the main findings in terms of the precision of effects (e.g. size of confidence intervals, statistical significance) | No |  |
+|  |  |  |  |  |  |
+| Summarise the main findings in terms of their heterogeneity | No |  |  |  |  |
+|  |  |  |  |  |  |
+| Summarise the main findings in terms of their biological/practical relevance | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 25.5 | Compare results with previous reviews on the topic, if available | No |  |  |  |
+|  |  |  |  |  |  |
+| 25.6 | Consider limitations and their influence on the generality of conclusions, such as gaps in the available evidence (e.g. taxonomic and geographical research biases) | No |  |  |  |
+|  |  |  |  |  |  |
+| **Contributions and funding** | **0%** | 26.1 | Provide names, affiliations, and funding sources of all co-authors | No |  |
+|  |  |  |  |  |  |
+|  |  | 26.2 | List the contributions of each co-author | No |  |
+|  |  |  |  |  |  |
+| Provide contact details for the corresponding author | No |  |  |  |  |
+|  |  |  |  |  |  |
+| 26.4 | Disclose any conflicts of interest | No |  |  |  |
+|  |  |  |  |  |  |
+| **References** | **0%** | 27.1 | Provide a reference list of all studies included in the systematic review or meta-analysis | No |  |
+|  |  |  |  |  |  |
+|  |  | 27.2 | List included studies as referenced sources (e.g. rather than listing them in a table or supplement) | No |  |
+
+: Prisma Eco-Evo Checklist according to @odea2021
+:::
+
+![This is the placeholder for prisma flowchart which isnt ready at the moment](figures/Prisma_Flowchart.png){#figsupp-prisma-flow}
+
+::: {#figsupp-variables}
+| variable name | description | values | Notes |
+|---------------|-------------|--------|-------|
+|               |             |        |       |
+|               |             |        |       |
+|               |             |        |       |
+
+This is the list of all the variables that were extracted for the purpose of this study
+:::
+
+### own-library
+
+::: {#figsupp-own-library}
+```{r}
+pacman::p_load(readr,knitr, dplyr)
+own_library <- read_csv("data/01_systematic_search/01_search_strategy/own_library_references.csv", 
+                        show_col_types = F)
+own_library%>% 
+  select(c(title,author,doi, journal, year, issn))%>% 
+  kable(col.names=(c("Article Title","Authors","DOI", "Journal", "Year of Publication", "ISSN" )),
+        caption = "Articles from our own library used for validating search strategy")
+```
+:::
+
+### random effects
+
+::: {#figsupp-random-effect}
+```{r}
+# pacman::p_load(readr, dplyr, tidyverse)
+# install.packages("devtools", repos = "https://cloud.r-project.org/")
+# devtools::install_github("davidsjoberg/ggsankey")
+# library(ggsankey)
+# analysis_dataset <- read_csv("data/03_data_cleaning/dataset_analysis.csv", 
+#                         show_col_types = F)
+# 
+# sankey_data <- analysis_dataset %>%
+#   select(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)%>%
+#   mutate(across(c(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded), as.character)) %>%
+#   make_long(Observation_ID,paper_ID, experiment_ID_coded, group_ID_coded, repeated_trait_ID_coded)
+# 
+# ggplot(sankey_data, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
+#   geom_alluvial(flow.alpha = .6) +
+#   scale_fill_viridis_d(drop = FALSE) +
+#   theme_alluvial(base_size = 18) +
+#   labs(x = NULL) +
+#   theme(legend.position = "none",
+#         plot.title = element_text(hjust = .5))
+# 
+# sankey_data_birds <- analysis_dataset %>%
+#   select(paper_ID, bird_species, population_ID)%>%
+#   mutate(across(c(paper_ID, bird_species, population_ID), as.character)) %>%
+#   make_long(paper_ID, bird_species, population_ID)
+# 
+# 
+# ggplot(sankey_data_birds, aes(x = x, 
+#                next_x = next_x, 
+#                node = node, 
+#                next_node = next_node,
+#                fill = factor(node))) +
+#   geom_sankey() +
+#   scale_fill_discrete(drop=FALSE) +
+#   theme(legend.position = "none")
+
+```
+:::
+
+### Systematic Search Information
+
+Remember to make a text file to copy-paste more easily and put it in the repo maybe..
+
+::: {#figsupp-string}
+The search was conducted twice, the first time on 07.09.2022 and then repeated on 12.08.2024 to ensure it was the most up to date and did not miss any additional articles on the topic that were published meanwhile.
+For both the searches, we did not use any time limitation i.e. it included all the published literature till that given date.
+We used **Advance Search** option for both Web of Science Core Collection Database and Scopus Database using the search query given below.\
+\
+Search string for the Web of Science Core Collection\
+Databases used in the search included\
+-Science Citation Index Expanded (SCI-EXPANDED) \[1900-present\]\
+-Social Sciences Citation Index (SSCI) \[1900-present\]\
+-Arts & Humanities Citation Index (AHCI) \[1975 - present\]\
+-Conference Proceedings Citation Index - Science (CPCI-S) \[1991 - present\]\
+-Conference Proceedings Citation Index - Social Science & Humanities (CPCI-SSH) \[1991 - present\]\
+-Emerging Sources Citation Index (ESCI) \[2017- present\]\
+\
+We used advance search option and Title (TI), Abstract (AB) and Author Keywords (AK) to conduct our systematic search using the following string\
+\
+\<TI=((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR"Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AB= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") )) OR AK= ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*")))\>\
+\
+The search was also conducted on SCOPUS using Advance Search Option and Title Abstract and Keyword (TITLE-ABS-KEY) on the same dates using the string\
+\
+\<TITLE-ABS-KEY ((("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*" AND ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR "Accipiter" OR "Aegypius" OR "Aquila" OR "Aviceda" OR "Busarellus" OR "Butastur" OR "Buteo" OR "Buteogallus" OR "Chondrohierax" OR "Circaetus" OR "Circus" OR "Clanga" OR "Elanoides" OR "Elanus" OR "Gampsonyx" OR "Geranoaetus" OR "Geranospiza" OR "Gypaetus" OR "Gypohierax" OR "Gyps" OR "Haliaeetus" OR "Haliastur" OR "Harpagus" OR "Harpia" OR "Hieraaetus" OR "Ictinaetus" OR "Ictinia" OR "Kaupifalco" OR "Leptodon" OR "Leucopternis" OR "Lophotriorchis" OR "Milvus" OR "Morphnarchus" OR "Morphnus" OR "Necrosyrtes" OR "Neophron" OR "Nisaetus" OR "Parabuteo" OR "Pernis" OR "Pithecophaga" OR "Polemaetus" OR "Pseudastur" OR "Rostrhamus" OR "Rupornis" OR "Sarcogyps" OR "Spilornis" OR "Spizaetus" OR "Stephanoaetus" OR "Terathopius" OR "Torgos" OR "Trigonoceps" OR "Cathartes" OR "Coragyps" OR "Gymnogyps" OR "Sarcoramphus" OR "Vultur" OR "Pandion" OR "Sagittarius" OR "Aix" OR "Alopochen" OR "Amazonetta" OR "Anas" OR "Anser" OR "Asarcornis" OR "Aythya" OR "Branta" OR "Bucephala" OR "Cairina" OR "Callonetta" OR "Cereopsis" OR "Chen" OR "Chenonetta" OR "Chloephaga" OR "Clangula" OR "Coscoroba" OR "Cyanochen" OR "Cygnus" OR "Dendrocygna" OR "Heteronetta" OR "Histrionicus" OR "Hymenolaimus" OR "Lophodytes" OR "Lophonetta" OR "Malacorhynchus" OR "Mareca" OR "Marmaronetta" OR "Melanitta" OR "Merganetta" OR "Mergellus" OR "Mergus" OR "Neochen" OR "Netta" OR "Nettapus" OR "Nomonyx" OR "Oxyura" OR "Plectropterus" OR "Polysticta" OR "Pteronetta" OR "Sarkidiornis" OR "Sibirionetta" OR "Somateria" OR "Spatula" OR "Tachyeres" OR "Tadorna" OR "Thalassornis" OR "Anhima" OR "Chauna" OR "Anseranas" OR "Aegotheles" OR "Aerodramus" OR "Aeronautes" OR "Apus" OR "Chaetura" OR "Collocalia" OR "Cypseloides" OR "Cypsiurus" OR "Hirundapus" OR "Panyptila" OR "Streptoprocne" OR "Tachornis" OR "Tachymarptis" OR "Hemiprocne" OR "Abeillia" OR "Adelomyia" OR "Aglaeactis" OR "Aglaiocercus" OR "Amazilia" OR "Androdon" OR "Anopetia" OR "Anthocephala" OR "Anthracothorax" OR "Archilochus" OR "Atthis" OR "Augastes" OR "Avocettula" OR "Basilinna" OR "Boissonneaua" OR "Calliphlox" OR "Calypte" OR "Campylopterus" OR "Chaetocercus" OR "Chalcostigma" OR "Chalybura" OR "Chlorestes" OR "Chlorostilbon" OR "Chrysolampis" OR "Chrysuronia" OR "Clytolaema" OR "Coeligena" OR "Colibri" OR "Cyanophaia" OR "Cynanthus" OR "Discosura" OR "Doricha" OR "Doryfera" OR "Elvira" OR "Ensifera" OR "Eriocnemis" OR "Eugenes" OR "Eulampis" OR "Eulidia" OR "Eupetomena" OR "Eupherusa" OR "Eutoxeres" OR "Florisuga" OR "Glaucis" OR "Goethalsia" OR "Goldmania" OR "Haplophaedia" OR "Heliactin" OR "Heliangelus" OR "Heliodoxa" OR "Heliomaster" OR "Heliothryx" OR "Hylocharis" OR "Juliamyia" OR "Klais" OR "Lafresnaya" OR "Lampornis" OR "Lamprolaima" OR "Lepidopyga" OR "Lesbia" OR "Leucippus" OR "Leucochloris" OR "Lophornis" OR "Mellisuga" OR "Metallura" OR "Microchera" OR "Myrmia" OR "Myrtis" OR "Ocreatus" OR "Opisthoprora" OR "Oreonympha" OR "Oreotrochilus" OR "Orthorhyncus" OR "Oxypogon" OR "Panterpe" OR "Patagona" OR "Phaeochroa" OR "Phaethornis" OR "Phlogophilus" OR "Polyonymus" OR "Polytmus" OR "Pterophanes" OR "Ramphodon" OR "Ramphomicron" OR "Rhodopis" OR "Sappho" OR "Schistes" OR "Selasphorus" OR "Sephanoides" OR "Stephanoxis" OR "Sternoclyta" OR "Taphrospilus" OR "Thalurania" OR "Thaumastura" OR "Threnetes" OR "Topaza" OR "Trochilus" OR "Urochroa" OR "Urosticte" OR "Apteryx" OR "Anthracoceros" OR "Buceros" OR "Bycanistes" OR "Lophoceros" OR "Penelopides" OR "Rhabdotorrhinus" OR "Rhyticeros" OR "Tockus" OR "Bucorvus" OR "Phoeniculus" OR "Rhinopomastus" OR "Upupa" OR "Antrostomus" OR "Caprimulgus" OR "Chordeiles" OR "Eleothreptus" OR "Eurostopodus" OR "Hydropsalis" OR "Lurocalis" OR "Lyncornis" OR "Nyctidromus" OR "Nyctiphrynus" OR "Nyctipolus" OR "Nyctiprogne" OR "Phalaenoptilus" OR "Setopagis" OR "Systellura" OR "Uropsalis" OR "Nyctibius" OR "Batrachostomus" OR "Podargus" OR "Steatornis" OR "Cariama" OR "Casuarius" OR "Dromaius" OR "Aethia" OR "Alca" OR "Alle" OR "Brachyramphus" OR "Cepphus" OR "Cerorhinca" OR "Fratercula" OR "Pinguinus" OR "Ptychoramphus" OR "Synthliboramphus" OR "Uria" OR "Burhinus" OR "Anarhynchus" OR "Charadrius" OR "Elseyornis" OR "Erythrogonys" OR "Hoploxypterus" OR "Oreopholus" OR "Peltohyas" OR "Phegornis" OR "Pluvialis" OR "Thinornis" OR "Vanellus" OR "Chionis" OR "Dromas" OR "Cursorius" OR "Glareola" OR "Rhinoptilus" OR "Stiltia" OR "Haematopus" OR "Actophilornis" OR "Hydrophasianus" OR "Irediparra" OR "Jacana" OR "Metopidius" OR "Microparra" OR "Anous" OR "Chlidonias" OR "Chroicocephalus" OR "Creagrus" OR "Gelochelidon" OR "Gygis" OR "Hydrocoloeus" OR "Hydroprogne" OR "Ichthyaetus" OR "Larosterna" OR "Larus" OR "Leucophaeus" OR "Onychoprion" OR "Pagophila" OR "Phaetusa" OR "Rhodostethia" OR "Rissa" OR "Rynchops" OR "Sterna" OR "Sternula" OR "Thalasseus" OR "Xema" OR "Pedionomus" OR "Pluvianellus" OR "Pluvianus" OR "Himantopus" OR "Recurvirostra" OR "Nycticryphes" OR "Rostratula" OR "Actitis" OR "Arenaria" OR "Bartramia" OR "Calidris" OR "Coenocorypha" OR "Gallinago" OR "Limnodromus" OR "Limosa" OR "Lymnocryptes" OR "Numenius" OR "Phalaropus" OR "Scolopax" OR "Tringa" OR "Xenus" OR "Stercorarius" OR "Attagis" OR "Thinocorus" OR "Turnix" OR "Ciconia" OR "Ephippiorhynchus" OR "Jabiru" OR "Leptoptilos" OR "Mycteria" OR "Colius" OR "Urocolius" OR "Alectroenas" OR "Alopecoenas" OR "Caloenas" OR "Chalcophaps" OR "Claravis" OR "Columba" OR "Columbina" OR "Didunculus" OR "Drepanoptila" OR "Ducula" OR "Ectopistes" OR "Gallicolumba" OR "Geopelia" OR "Geophaps" OR "Geotrygon" OR "Goura" OR "Gymnophaps" OR "Hemiphaga" OR "Henicophaps" OR "Leptotila" OR "Leptotrygon" OR "Leucosarcia" OR "Lopholaimus" OR "Macropygia" OR "Metriopelia" OR "Ocyphaps" OR "Oena" OR "Otidiphaps" OR "Patagioenas" OR "Petrophassa" OR "Pezophaps" OR "Phapitreron" OR "Phaps" OR "Ptilinopus" OR "Raphus" OR "Reinwardtoena" OR "Spilopelia" OR "Streptopelia" OR "Treron" OR "Trugon" OR "Turacoena" OR "Turtur" OR "Uropelia" OR "Zenaida" OR "Zentrygon" OR "Actenoides" OR "Alcedo" OR "Caridonax" OR "Ceryle" OR "Ceyx" OR "Chloroceryle" OR "Cittura" OR "Corythornis" OR "Dacelo" OR "Halcyon" OR "Ispidina" OR "Lacedo" OR "Megaceryle" OR "Melidora" OR "Syma" OR "Tanysiptera" OR "Todiramphus" OR "Atelornis" OR "Brachypteracias" OR "Geobiastes" OR "Coracias" OR "Eurystomus" OR "Merops" OR "Nyctyornis" OR "Baryphthengus" OR "Electron" OR "Eumomota" OR "Hylomanes" OR "Momotus" OR "Todus" OR "Cacomantis" OR "Carpococcyx" OR "Centropus" OR "Cercococcyx" OR "Chrysococcyx" OR "Clamator" OR "Coccycua" OR "Coccyzus" OR "Coua" OR "Crotophaga" OR "Cuculus" OR "Dasylophus" OR "Dromococcyx" OR "Eudynamys" OR "Geococcyx" OR "Guira" OR "Hierococcyx" OR "Morococcyx" OR "Neomorphus" OR "Pachycoccyx" OR "Phaenicophaeus" OR "Piaya" OR "Rhinortha" OR "Scythrops" OR "Surniculus" OR "Tapera" OR "Urodynamis" OR "Zanclostomus" OR "Dinornis" OR "Anomalopteryx" OR "Emeus" OR "Euryapteryx" OR "Eurypyga" OR "Rhynochetos" OR "Caracara" OR "Daptrius" OR "Falco" OR "Herpetotheres" OR "Ibycter" OR "Micrastur" OR "Microhierax" OR "Milvago" OR "Phalcoboenus" OR "Polihierax" OR "Spiziapteryx" OR "Aburria" OR "Chamaepetes" OR "Crax" OR "Mitu" OR "Nothocrax" OR "Oreophasis" OR "Ortalis" OR "Pauxi" OR "Penelope" OR "Penelopina" OR "Pipile" OR "Alectura" OR "Megapodius" OR "Acryllium" OR "Guttera" OR "Numida" OR "Callipepla" OR "Colinus" OR "Cyrtonyx" OR "Dendrortyx" OR "Odontophorus" OR "Oreortyx" OR "Philortyx" OR "Ptilopachus" OR "Rhynchortyx" OR "Alectoris" OR "Ammoperdix" OR "Arborophila" OR "Argusianus" OR "Bambusicola" OR "Bonasa" OR "Caloperdix" OR "Centrocercus" OR "Chrysolophus" OR "Coturnix" OR "Crossoptilon" OR "Dendragapus" OR "Excalfactoria" OR "Falcipennis" OR "Francolinus" OR "Gallus" OR "Haematortyx" OR "Ithaginis" OR "Lagopus" OR "Lerwa" OR "Lophophorus" OR "Lophura" OR "Lyrurus" OR "Meleagris" OR "Pavo" OR "Peliperdix" OR "Perdix" OR "Phasianus" OR "Polyplectron" OR "Pternistis" OR "Pucrasia" OR "Rhizothera" OR "Rollulus" OR "Scleroptila" OR "Syrmaticus" OR "Tetrao" OR "Tetraogallus" OR "Tetraophasis" OR "Tragopan" OR "Tympanuchus" OR "Gavia" OR "Aramus" OR "Anthropoides" OR "Antigone" OR "Balearica" OR "Bugeranus" OR "Grus" OR "Leucogeranus" OR "Heliornis" OR "Psophia" OR "Aenigmatolimnas" OR "Amaurolimnas" OR "Amaurornis" OR "Anurolimnas" OR "Aramides" OR "Atlantisia" OR "Coturnicops" OR "Crex" OR "Dryolimnas" OR "Eulabeornis" OR "Fulica" OR "Gallicrex" OR "Gallinula" OR "Gallirallus" OR "Laterallus" OR "Lewinia" OR "Micropygia" OR "Neocrex" OR "Nesoclopeus" OR "Paragallinula" OR "Pardirallus" OR "Porphyrio" OR "Porphyriops" OR "Porzana" OR "Rallicula" OR "Rallina" OR "Rallus" OR "Tribonyx" OR "Canirallus" OR "Sarothrura" OR "Leptosomus" OR "Corythaeola" OR "Corythaixoides" OR "Crinifer" OR "Musophaga" OR "Tauraco" OR "Opisthocomus" OR "Afrotis" OR "Ardeotis" OR "Chlamydotis" OR "Neotis" OR "Otis" OR "Tetrax" OR "Acanthisitta" OR "Pachyplichas" OR "Traversia" OR "Xenicus" OR "Acanthiza" OR "Acanthornis" OR "Aethomyias" OR "Aphelocephala" OR "Calamanthus" OR "Gerygone" OR "Hylacola" OR "Neosericornis" OR "Oreoscopus" OR "Origma" OR "Pachycare" OR "Pycnoptilus" OR "Pyrrholaemus" OR "Sericornis" OR "Smicrornis" OR "Acrocephalus" OR "Arundinax" OR "Calamonastides" OR "Hippolais" OR "Iduna" OR "Nesillas" OR "Aegithalos" OR "Leptopoecile" OR "Psaltriparus" OR "Aegithina" OR "Alaemon" OR "Alauda" OR "Alaudala" OR "Ammomanes" OR "Calandrella" OR "Calendulauda" OR "Chersomanes" OR "Eremophila" OR "Eremopterix" OR "Galerida" OR "Lullula" OR "Melanocorypha" OR "Mirafra" OR "Pinarocorys" OR "Spizocorys" OR "Artamus" OR "Gymnorhina" OR "Melloria" OR "Bombycilla" OR "Buphagus" OR "Calcarius" OR "Plectrophenax" OR "Rhynchophanes" OR "Callaeas" OR "Heteralocha" OR "Philesturnus" OR "Calyptophilus" OR "Campephaga" OR "Ceblepyris" OR "Coracina" OR "Edolisoma" OR "Lalage" OR "Malindangia" OR "Pericrocotus" OR "Amaurospiza" OR "Cardinalis" OR "Caryothraustes" OR "Chlorothraupis" OR "Cyanocompsa" OR "Cyanoloxia" OR "Granatellus" OR "Habia" OR "Passerina" OR "Periporphyrus" OR "Pheucticus" OR "Piranga" OR "Spiza" OR "Certhia" OR "Salpornis" OR "Abroscopus" OR "Cettia" OR "Horornis" OR "Phyllergates" OR "Tesia" OR "Urosphena" OR "Chloropsis" OR "Cinclus" OR "Apalis" OR "Artisornis" OR "Camaroptera" OR "Cisticola" OR "Eremomela" OR "Heliolais" OR "Hypergerus" OR "Neomixis" OR "Oreolais" OR "Orthotomus" OR "Phragmacia" OR "Poliolais" OR "Prinia" OR "Schistolais" OR "Urolais" OR "Urorhipis" OR "Climacteris" OR "Cormobates" OR "Conopophaga" OR "Struthidea" OR "Aphelocoma" OR "Calocitta" OR "Cissa" OR "Coloeus" OR "Corvus" OR "Cyanocitta" OR "Cyanocorax" OR "Cyanolyca" OR "Cyanopica" OR "Dendrocitta" OR "Garrulus" OR "Gymnorhinus" OR "Nucifraga" OR "Perisoreus" OR "Pica" OR "Platylophus" OR "Podoces" OR "Psilorhinus" OR "Ptilostomus" OR "Pyrrhocorax" OR "Urocissa" OR "Ampelioides" OR "Ampelion" OR "Carpornis" OR "Cephalopterus" OR "Conioptilon" OR "Cotinga" OR "Doliornis" OR "Gymnoderus" OR "Haematoderus" OR "Lipaugus" OR "Perissocephalus" OR "Phoenicircus" OR "Phytotoma" OR "Pipreola" OR "Porphyrolaema" OR "Procnias" OR "Pyroderus" OR "Querula" OR "Rupicola" OR "Snowornis" OR "Xipholena" OR "Zaratornis" OR "Dasyornis" OR "Dicaeum" OR "Prionochilus" OR "Dicrurus" OR "Donacobius" OR "Dulus" OR "Emberiza" OR "Amadina" OR "Amandava" OR "Cryptospiza" OR "Erythrura" OR "Estrilda" OR "Euodice" OR "Euschistospiza" OR "Lagonosticta" OR "Lonchura" OR "Mandingoa" OR "Neochmia" OR "Nesocharis" OR "Nigrita" OR "Ortygospiza" OR "Parmoptila" OR "Pyrenestes" OR "Pytilia" OR "Spermophaga" OR "Stagonopleura" OR "Taeniopygia" OR "Uraeginthus" OR "Calyptomena" OR "Cymbirhynchus" OR "Eurylaimus" OR "Psarisomus" OR "Serilophus" OR "Smithornis" OR "Chamaeza" OR "Formicarius" OR "Acanthis" OR "Agraphospiza" OR "Akialoa" OR "Bucanetes" OR "Carduelis" OR "Carpodacus" OR "Chloris" OR "Chlorodrepanis" OR "Chlorophonia" OR "Chrysocorythus" OR "Coccothraustes" OR "Crithagra" OR "Drepanis" OR "Eophona" OR "Euphonia" OR "Fringilla" OR "Haemorhous" OR "Hemignathus" OR "Himatione" OR "Leucosticte" OR "Linaria" OR "Linurgus" OR "Loxia" OR "Loxioides" OR "Loxops" OR "Magumma" OR "Melamprosops" OR "Oreomystis" OR "Paroreomyza" OR "Pinicola" OR "Procarduelis" OR "Pseudonestor" OR "Psittirostra" OR "Pyrrhoplectes" OR "Pyrrhula" OR "Rhodopechys" OR "Rhodospiza" OR "Serinus" OR "Spinus" OR "Telespiza" OR "Anabacerthia" OR "Anabazenops" OR "Ancistrops" OR "Anumbius" OR "Aphrastura" OR "Asthenes" OR "Automolus" OR "Berlepschia" OR "Campylorhamphus" OR "Certhiasomus" OR "Certhiaxis" OR "Cinclodes" OR "Clibanornis" OR "Coryphistera" OR "Cranioleuca" OR "Deconychura" OR "Dendrexetastes" OR "Dendrocincla" OR "Dendrocolaptes" OR "Dendroplex" OR "Drymornis" OR "Drymotoxeres" OR "Furnarius" OR "Geocerthia" OR "Geositta" OR "Glyphorynchus" OR "Heliobletus" OR "Hellmayrea" OR "Hylexetastes" OR "Lepidocolaptes" OR "Leptasthenura" OR "Limnoctites" OR "Limnornis" OR "Lochmias" OR "Margarornis" OR "Mazaria" OR "Megaxenops" OR "Metopothrix" OR "Microxenops" OR "Nasica" OR "Ochetorhynchus" OR "Phacellodomus" OR "Philydor" OR "Phleocryptes" OR "Premnoplex" OR "Premnornis" OR "Pseudasthenes" OR "Pseudocolaptes" OR "Pseudoseisura" OR "Pygarrhichas" OR "Roraimia" OR "Schoeniophylax" OR "Sclerurus" OR "Sittasomus" OR "Spartonoica" OR "Sylviorthorhynchus" OR "Synallaxis" OR "Syndactyla" OR "Tarphonomus" OR "Thripadectes" OR "Thripophaga" OR "Upucerthia" OR "Xenerpestes" OR "Xenops" OR "Xiphocolaptes" OR "Xiphorhynchus" OR "Grallaria" OR "Grallaricula" OR "Hylopezus" OR "Myrmothera" OR "Alopochelidon" OR "Atticora" OR "Cecropis" OR "Delichon" OR "Haplochelidon" OR "Hirundo" OR "Neochelidon" OR "Notiochelidon" OR "Orochelidon" OR "Petrochelidon" OR "Phedina" OR "Progne" OR "Psalidoprocne" OR "Pseudhirundo" OR "Pseudochelidon" OR "Ptyonoprogne" OR "Riparia" OR "Stelgidopteryx" OR "Tachycineta" OR "Hyliota" OR "Hypocolius" OR "Agelaioides" OR "Agelaius" OR "Agelasticus" OR "Amblycercus" OR "Amblyramphus" OR "Anumara" OR "Cacicus" OR "Chrysomus" OR "Curaeus" OR "Dives" OR "Dolichonyx" OR "Euphagus" OR "Gnorimopsar" OR "Gymnomystax" OR "Hypopyrrhus" OR "Icterus" OR "Lampropsar" OR "Leistes" OR "Macroagelaius" OR "Molothrus" OR "Nesopsar" OR "Oreopsar" OR "Psarocolius" OR "Pseudoleistes" OR "Quiscalus" OR "Sturnella" OR "Xanthocephalus" OR "Xanthopsar" OR "Icteria" OR "Ifrita" OR "Irena" OR "Corvinella" OR "Eurocephalus" OR "Lanius" OR "Actinodura" OR "Argya" OR "Garrulax" OR "Grammatoptila" OR "Heterophasia" OR "Ianthocincla" OR "Laniellus" OR "Leiothrix" OR "Liocichla" OR "Minla" OR "Pterorhinus" OR "Trochalopteron" OR "Turdoides" OR "Bradypterus" OR "Cincloramphus" OR "Helopsaltes" OR "Locustella" OR "Megalurus" OR "Poodytes" OR "Machaerirhynchus" OR "Graueria" OR "Hylia" OR "Macrosphenus" OR "Melocichla" OR "Sylvietta" OR "Chlorophoneus" OR "Dryoscopus" OR "Laniarius" OR "Malaconotus" OR "Nilaus" OR "Rhodophoneus" OR "Tchagra" OR "Telophorus" OR "Amytornis" OR "Chenorhamphus" OR "Clytomyias" OR "Malurus" OR "Stipiturus" OR "Melampitta" OR "Melanocharis" OR "Oedistoma" OR "Toxorhamphus" OR "Melanopareia" OR "Acanthagenys" OR "Acanthorhynchus" OR "Anthochaera" OR "Anthornis" OR "Caligavis" OR "Entomyzon" OR "Epthianura" OR "Glycifohia" OR "Gymnomyza" OR "Lichmera" OR "Manorina" OR "Melidectes" OR "Melilestes" OR "Meliphaga" OR "Melipotes" OR "Melithreptus" OR "Myzomela" OR "Nesoptilotis" OR "Philemon" OR "Phylidonyris" OR "Prosthemadera" OR "Ptiloprora" OR "Ptilotula" OR "Pycnopygius" OR "Timeliopsis" OR "Xanthotis" OR "Menura" OR "Allenia" OR "Cinclocerthia" OR "Dumetella" OR "Margarops" OR "Melanoptila" OR "Melanotis" OR "Mimus" OR "Oreoscoptes" OR "Ramphocinclus" OR "Toxostoma" OR "Lamprospiza" OR "Mitrospingus" OR "Moho" OR "Mohoua" OR "Arses" OR "Carterornis" OR "Clytorhynchus" OR "Grallina" OR "Hypothymis" OR "Monarcha" OR "Myiagra" OR "Symposiachrus" OR "Terpsiphone" OR "Trochocercus" OR "Anthus" OR "Macronyx" OR "Motacilla" OR "Alethe" OR "Anthipes" OR "Brachypteryx" OR "Calliope" OR "Campicoloides" OR "Cercotrichas" OR "Chamaetylas" OR "Copsychus" OR "Cossypha" OR "Cyanoptila" OR "Cyornis" OR "Enicurus" OR "Erithacus" OR "Eumyias" OR "Ficedula" OR "Fraseria" OR "Irania" OR "Larvivora" OR "Leonardina" OR "Luscinia" OR "Melaenornis" OR "Monticola" OR "Muscicapa" OR "Myiomela" OR "Myioparus" OR "Myophonus" OR "Myrmecocichla" OR "Niltava" OR "Oenanthe" OR "Phoenicurus" OR "Pogonocichla" OR "Saxicola" OR "Sheppardia" OR "Sholicola" OR "Stiphrornis" OR "Tarsiger" OR "Thamnolaea" OR "Vauriella" OR "Aethopyga" OR "Anabathmis" OR "Anthreptes" OR "Arachnothera" OR "Chalcomitra" OR "Cinnyris" OR "Cyanomitra" OR "Deleornis" OR "Hedydipna" OR "Kurochkinegramma" OR "Leptocoma" OR "Nectarinia" OR "Daphoenositta" OR "Nesospingus" OR "Nicator" OR "Notiomystis" OR "Aleadryas" OR "Oriolus" OR "Pitohui" OR "Sphecotheres" OR "Turnagra" OR "Colluricincla" OR "Falcunculus" OR "Melanorectes" OR "Pachycephala" OR "Pseudorectes" OR "Panurus" OR "Cicinnurus" OR "Diphyllodes" OR "Manucodia" OR "Paradisaea" OR "Ptiloris" OR "Paramythia" OR "Pardalotus" OR "Baeolophus" OR "Cephalopyrus" OR "Cyanistes" OR "Lophophanes" OR "Machlolophus" OR "Melaniparus" OR "Melanochlora" OR "Pardaliparus" OR "Parus" OR "Periparus" OR "Poecile" OR "Pseudopodoces" OR "Sittiparus" OR "Sylviparus" OR "Basileuterus" OR "Cardellina" OR "Catharopeza" OR "Dendroica" OR "Geothlypis" OR "Helmitheros" OR "Leiothlypis" OR "Limnothlypis" OR "Mniotilta" OR "Myioborus" OR "Myiothlypis" OR "Oporornis" OR "Oreothlypis" OR "Parkesia" OR "Protonotaria" OR "Seiurus" OR "Setophaga" OR "Vermivora" OR "Aimophila" OR "Ammodramus" OR "Amphispiza" OR "Arremon" OR "Arremonops" OR "Artemisiospiza" OR "Atlapetes" OR "Calamospiza" OR "Chlorospingus" OR "Chondestes" OR "Junco" OR "Melospiza" OR "Melozone" OR "Oreothraupis" OR "Oriturus" OR "Passerculus" OR "Passerella" OR "Peucaea" OR "Pezopetes" OR "Pipilo" OR "Pooecetes" OR "Pselliophorus" OR "Rhynchospiza" OR "Spizella" OR "Spizelloides" OR "Xenospiza" OR "Zonotrichia" OR "Carpospiza" OR "Gymnoris" OR "Hypocryptadius" OR "Montifringilla" OR "Onychostruthus" OR "Passer" OR "Petronia" OR "Pyrgilauda" OR "Alcippe" OR "Gampsorhynchus" OR "Illadopsis" OR "Jabouilleia" OR "Kenopia" OR "Laticilla" OR "Malacocincla" OR "Malacopteron" OR "Napothera" OR "Pellorneum" OR "Rimator" OR "Trichastoma" OR "Amalocichla" OR "Drymodes" OR "Eopsaltria" OR "Eugerygone" OR "Heteromyias" OR "Melanodryas" OR "Microeca" OR "Monachella" OR "Pachycephalopsis" OR "Peneoenanthe" OR "Peneothello" OR "Petroica" OR "Poecilodryas" OR "Tregellasia" OR "Peucedramus" OR "Microligea" OR "Phaenicophilus" OR "Xenoligea" OR "Phylloscopus" OR "Picathartes" OR "Antilophia" OR "Ceratopipra" OR "Chiroxiphia" OR "Chloropipo" OR "Corapipo" OR "Cryptopipo" OR "Heterocercus" OR "Ilicura" OR "Lepidothrix" OR "Machaeropterus" OR "Manacus" OR "Masius" OR "Neopelma" OR "Pipra" OR "Pseudopipra" OR "Tyranneutes" OR "Xenopipo" OR "Erythropitta" OR "Hydrornis" OR "Pitta" OR "Batis" OR "Platysteira" OR "Anaplectes" OR "Bubalornis" OR "Euplectes" OR "Malimbus" OR "Plocepasser" OR "Ploceus" OR "Quelea" OR "Sporopipes" OR "Pnoepyga" OR "Microbates" OR "Polioptila" OR "Ramphocaenus" OR "Garritornis" OR "Prunella" OR "Cinclosoma" OR "Ptilorrhoa" OR "Phainopepla" OR "Phainoptila" OR "Ptiliogonys" OR "Ailuroedus" OR "Amblyornis" OR "Ptilonorhynchus" OR "Sericulus" OR "Alophoixus" OR "Andropadus" OR "Arizelocichla" OR "Atimastillas" OR "Baeopogon" OR "Bleda" OR "Chlorocichla" OR "Criniger" OR "Eurillas" OR "Hemixos" OR "Hypsipetes" OR "Iole" OR "Ixos" OR "Neolestes" OR "Phyllastrephus" OR "Pycnonotus" OR "Spizixos" OR "Stelgidillas" OR "Tricholestes" OR "Regulus" OR "Anthoscopus" OR "Auriparus" OR "Remiz" OR "Rhagologus" OR "Eleoscytalopus" OR "Liosceles" OR "Psilorhamphus" OR "Pteroptochos" OR "Scelorchilus" OR "Scytalopus" OR "Teledromas" OR "Rhipidura" OR "Rhodinocichla" OR "Sapayoa" OR "Sitta" OR "Spindalis" OR "Chelidorhynx" OR "Culicicapa" OR "Elminia" OR "Acridotheres" OR "Agropsar" OR "Ampeliceps" OR "Aplonis" OR "Basilornis" OR "Cinnyricinclus" OR "Creatophora" OR "Gracula" OR "Gracupica" OR "Hartlaubius" OR "Hylopsar" OR "Lamprotornis" OR "Leucopsar" OR "Mino" OR "Notopholia" OR "Onychognathus" OR "Pastor" OR "Poeoptera" OR "Rhabdornis" OR "Sarcops" OR "Scissirostrum" OR "Speculipastor" OR "Spodiopsar" OR "Streptocitta" OR "Sturnia" OR "Sturnus" OR "Chamaea" OR "Chleuasicus" OR "Chloropeta" OR "Chrysomma" OR "Conostoma" OR "Fulvetta" OR "Lioparus" OR "Paradoxornis" OR "Pseudoalcippe" OR "Psittiparus" OR "Rhopophilus" OR "Sinosuthora" OR "Suthora" OR "Sylvia" OR "Teretistris" OR "Akletos" OR "Ampelornis" OR "Aprositornis" OR "Batara" OR "Cercomacra" OR "Cercomacroides" OR "Cymbilaimus" OR "Dichrozona" OR "Drymophila" OR "Dysithamnus" OR "Epinecrophylla" OR "Euchrepomis" OR "Formicivora" OR "Frederickena" OR "Gymnocichla" OR "Gymnopithys" OR "Hafferia" OR "Herpsilochmus" OR "Hylophylax" OR "Hypocnemis" OR "Hypocnemoides" OR "Hypoedaleus" OR "Isleria" OR "Mackenziaena" OR "Megastictus" OR "Microrhopias" OR "Myrmeciza" OR "Myrmelastes" OR "Myrmoborus" OR "Myrmochanes" OR "Myrmoderus" OR "Myrmophylax" OR "Myrmorchilus" OR "Myrmornis" OR "Myrmotherula" OR "Neoctantes" OR "Oneillornis" OR "Percnostola" OR "Phaenostictus" OR "Phlegopsis" OR "Pithys" OR "Poliocrania" OR "Pygiptila" OR "Pyriglena" OR "Rhegmatorhina" OR "Rhopias" OR "Rhopornis" OR "Sakesphorus" OR "Sciaphylax" OR "Sclateria" OR "Sipia" OR "Taraba" OR "Thamnistes" OR "Thamnomanes" OR "Thamnophilus" OR "Willisornis" OR "Xenornis" OR "Anisognathus" OR "Bangsia" OR "Buthraupis" OR "Calochaetes" OR "Catamblyrhynchus" OR "Catamenia" OR "Charitospiza" OR "Chlorochrysa" OR "Chlorophanes" OR "Chlorornis" OR "Chrysothlypis" OR "Cissopis" OR "Cnemoscopus" OR "Coereba" OR "Compsospiza" OR "Compsothraupis" OR "Conirostrum" OR "Conothraupis" OR "Coryphospingus" OR "Creurgops" OR "Cyanerpes" OR "Cyanicterus" OR "Cypsnagra" OR "Dacnis" OR "Delothraupis" OR "Diglossa" OR "Diuca" OR "Dolospingus" OR "Donacospiza" OR "Dubusia" OR "Emberizoides" OR "Embernagra" OR "Eucometis" OR "Euneornis" OR "Geospiza" OR "Gubernatrix" OR "Haplospiza" OR "Hemispingus" OR "Hemithraupis" OR "Heterospingus" OR "Incaspiza" OR "Iridophanes" OR "Iridosornis" OR "Lanio" OR "Lophospingus" OR "Loxigilla" OR "Loxipasser" OR "Melanodera" OR "Melanospiza" OR "Melopyrrha" OR "Nemosia" OR "Nephelornis" OR "Oreomanes" OR "Oryzoborus" OR "Parkerthraustes" OR "Paroaria" OR "Phrygilus" OR "Piezorina" OR "Pipraeidea" OR "Poospiza" OR "Pyrrhocoma" OR "Ramphocelus" OR "Rhodospingus" OR "Saltator" OR "Saltatricula" OR "Schistochlamys" OR "Sericossypha" OR "Sicalis" OR "Sporophila" OR "Stephanophorus" OR "Tachyphonus" OR "Tangara" OR "Tersina" OR "Thlypopsis" OR "Thraupis" OR "Tiaris" OR "Trichothraupis" OR "Volatinia" OR "Wetmorethraupis" OR "Xenodacnis" OR "Xenospingus" OR "Tichodroma" OR "Macronus" OR "Pomatorhinus" OR "Spelaeornis" OR "Stachyridopsis" OR "Stachyris" OR "Iodopleura" OR "Laniisoma" OR "Laniocera" OR "Myiobius" OR "Onychorhynchus" OR "Oxyruncus" OR "Pachyramphus" OR "Schiffornis" OR "Terenotriccus" OR "Tityra" OR "Xenopsaris" OR "Campylorhynchus" OR "Cantorchilus" OR "Catherpes" OR "Cinnycerthia" OR "Cistothorus" OR "Cyphorhinus" OR "Henicorhina" OR "Microcerculus" OR "Odontorchilus" OR "Pheugopedius" OR "Salpinctes" OR "Thryomanes" OR "Thryophilus" OR "Thryothorus" OR "Troglodytes" OR "Uropsila" OR "Catharus" OR "Cichlopsis" OR "Entomodestes" OR "Geokichla" OR "Hylocichla" OR "Ixoreus" OR "Myadestes" OR "Neocossyphus" OR "Ridgwayia" OR "Sialia" OR "Stizorhina" OR "Turdus" OR "Zoothera" OR "Agriornis" OR "Alectrurus" OR "Anairetes" OR "Aphanotriccus" OR "Arundinicola" OR "Atalotriccus" OR "Attila" OR "Camptostoma" OR "Capsiempis" OR "Casiornis" OR "Cnemarchus" OR "Cnemotriccus" OR "Cnipodectes" OR "Colonia" OR "Colorhamphus" OR "Conopias" OR "Contopus" OR "Corythopis" OR "Culicivora" OR "Deltarhynchus" OR "Elaenia" OR "Empidonax" OR "Empidonomus" OR "Euscarthmus" OR "Fluvicola" OR "Griseotyrannus" OR "Gubernetes" OR "Hemitriccus" OR "Heteroxolmis" OR "Hirundinea" OR "Hymenops" OR "Inezia" OR "Knipolegus" OR "Lathrotriccus" OR "Legatus" OR "Leptopogon" OR "Lessonia" OR "Lophotriccus" OR "Machetornis" OR "Mecocerculus" OR "Megarynchus" OR "Mionectes" OR "Mitrephanes" OR "Muscigralla" OR "Muscisaxicola" OR "Myiarchus" OR "Myiodynastes" OR "Myiopagis" OR "Myiophobus" OR "Myiornis" OR "Myiotheretes" OR "Myiotriccus" OR "Myiozetetes" OR "Neopipo" OR "Neoxolmis" OR "Nephelomyias" OR "Ochthoeca" OR "Ochthornis" OR "Oncostoma" OR "Ornithion" OR "Phaeomyias" OR "Philohydor" OR "Phyllomyias" OR "Phylloscartes" OR "Piprites" OR "Pitangus" OR "Platyrinchus" OR "Poecilotriccus" OR "Pogonotriccus" OR "Polioxolmis" OR "Polystictus" OR "Pseudelaenia" OR "Pseudocolopteryx" OR "Pseudotriccus" OR "Pyrocephalus" OR "Pyrrhomyias" OR "Ramphotrigon" OR "Rhynchocyclus" OR "Rhytipterna" OR "Satrapa" OR "Sayornis" OR "Serpophaga" OR "Silvicultrix" OR "Sirystes" OR "Stigmatura" OR "Sublegatus" OR "Suiriri" OR "Tachuris" OR "Taeniotriccus" OR "Todirostrum" OR "Tolmomyias" OR "Tumbezia" OR "Tyrannopsis" OR "Tyrannulus" OR "Tyrannus" OR "Uromyias" OR "Xenotriccus" OR "Xolmis" OR "Zimmerius" OR "Urocynchramus" OR "Artamella" OR "Calicalicus" OR "Cyanolanius" OR "Euryceros" OR "Falculea" OR "Hypositta" OR "Leptopterus" OR "Mystacornis" OR "Newtonia" OR "Oriolia" OR "Philentoma" OR "Prionops" OR "Pseudobias" OR "Schetba" OR "Tephrodornis" OR "Tylas" OR "Vanga" OR "Xenopirostris" OR "Anomalospiza" OR "Vidua" OR "Cyclarhis" OR "Erpornis" OR "Hylophilus" OR "Pteruthius" OR "Vireo" OR "Vireolanius" OR "Zeledonia" OR "Apalopteron" OR "Dasycrotapha" OR "Heleia" OR "Lophozosterops" OR "Sterrhoptilus" OR "Yuhina" OR "Zosterops" OR "Zosterornis" OR "Agamia" OR "Ardea" OR "Ardeola" OR "Botaurus" OR "Bubulcus" OR "Butorides" OR "Cochlearius" OR "Dupetor" OR "Egretta" OR "Gorsachius" OR "Ixobrychus" OR "Nyctanassa" OR "Nycticorax" OR "Pilherodius" OR "Syrigma" OR "Tigriornis" OR "Tigrisoma" OR "Zebrilus" OR "Balaeniceps" OR "Pelecanus" OR "Scopus" OR "Bostrychia" OR "Eudocimus" OR "Geronticus" OR "Lophotibis" OR "Mesembrinibis" OR "Nipponia" OR "Phimosus" OR "Platalea" OR "Plegadis" OR "Pseudibis" OR "Theristicus" OR "Threskiornis" OR "Phaethon" OR "Phoeniconaias" OR "Phoenicoparrus" OR "Phoenicopterus" OR "Bucco" OR "Chelidoptera" OR "Hapaloptila" OR "Hypnelus" OR "Malacoptila" OR "Micromonacha" OR "Monasa" OR "Nonnula" OR "Notharchus" OR "Nystalus" OR "Capito" OR "Eubucco" OR "Brachygalba" OR "Galbalcyrhynchus" OR "Galbula" OR "Jacamaralcyon" OR "Jacamerops" OR "Indicator" OR "Melichneutes" OR "Melignomon" OR "Prodotiscus" OR "Buccanodon" OR "Gymnobucco" OR "Lybius" OR "Pogoniulus" OR "Stactolaema" OR "Trachyphonus" OR "Psilopogon" OR "Blythipicus" OR "Campephilus" OR "Campethera" OR "Celeus" OR "Chloropicus" OR "Chrysocolaptes" OR "Chrysophlegma" OR "Colaptes" OR "Dendrocopos" OR "Dendrocoptes" OR "Dendropicos" OR "Dinopium" OR "Dryobates" OR "Dryocopus" OR "Gecinulus" OR "Geocolaptes" OR "Jynx" OR "Leiopicus" OR "Leuconotopicus" OR "Meiglyptes" OR "Melanerpes" OR "Micropternus" OR "Mulleripicus" OR "Nesoctites" OR "Picoides" OR "Piculus" OR "Picumnus" OR "Picus" OR "Reinwardtipicus" OR "Sasia" OR "Sphyrapicus" OR "Veniliornis" OR "Yungipicus" OR "Andigena" OR "Aulacorhynchus" OR "Pteroglossus" OR "Ramphastos" OR "Selenidera" OR "Semnornis" OR "Aechmophorus" OR "Podiceps" OR "Podilymbus" OR "Poliocephalus" OR "Rollandia" OR "Tachybaptus" OR "Diomedea" OR "Phoebastria" OR "Phoebetria" OR "Thalassarche" OR "Hydrobates" OR "Oceanodroma" OR "Fregetta" OR "Garrodia" OR "Nesofregetta" OR "Oceanites" OR "Pelagodroma" OR "Aphrodroma" OR "Ardenna" OR "Bulweria" OR "Calonectris" OR "Daption" OR "Fulmarus" OR "Halobaena" OR "Macronectes" OR "Pachyptila" OR "Pagodroma" OR "Pelecanoides" OR "Procellaria" OR "Pseudobulweria" OR "Pterodroma" OR "Puffinus" OR "Thalassoica" OR "Cacatua" OR "Callocephalon" OR "Calyptorhynchus" OR "Eolophus" OR "Lophochroa" OR "Nymphicus" OR "Probosciger" OR "Alipiopsitta" OR "Amazona" OR "Anodorhynchus" OR "Ara" OR "Aratinga" OR "Bolborhynchus" OR "Brotogeris" OR "Conuropsis" OR "Cyanoliseus" OR "Cyanopsitta" OR "Deroptyus" OR "Diopsittaca" OR "Enicognathus" OR "Eupsittula" OR "Forpus" OR "Graydidascalus" OR "Guarouba" OR "Guaruba" OR "Hapalopsittaca" OR "Leptosittaca" OR "Myiopsitta" OR "Nannopsittaca" OR "Orthopsittaca" OR "Pionites" OR "Pionopsitta" OR "Pionus" OR "Poicephalus" OR "Primolius" OR "Psilopsiagon" OR "Psittacara" OR "Psittacus" OR "Pyrilia" OR "Pyrrhura" OR "Rhynchopsitta" OR "Thectocercus" OR "Touit" OR "Triclaria" OR "Agapornis" OR "Alisterus" OR "Aprosmictus" OR "Barnardius" OR "Bolbopsittacus" OR "Chalcopsitta" OR "Charmosyna" OR "Coracopsis" OR "Cyanoramphus" OR "Cyclopsitta" OR "Eclectus" OR "Eos" OR "Eunymphicus" OR "Geoffroyus" OR "Glossopsitta" OR "Lathamus" OR "Loriculus" OR "Lorius" OR "Melopsittacus" OR "Micropsitta" OR "Neophema" OR "Neopsephotus" OR "Neopsittacus" OR "Northiella" OR "Oreopsittacus" OR "Parvipsitta" OR "Pezoporus" OR "Phigys" OR "Platycercus" OR "Polytelis" OR "Prioniturus" OR "Prosopeia" OR "Psephotellus" OR "Psephotus" OR "Pseudeos" OR "Psittacella" OR "Psittacula" OR "Psittaculirostris" OR "Psitteuteles" OR "Psittinus" OR "Psittrichas" OR "Purpureicephalus" OR "Tanygnathus" OR "Trichoglossus" OR "Vini" OR "Nestor" OR "Strigops" OR "Pterocles" OR "Syrrhaptes" OR "Rhea" OR "Aptenodytes" OR "Eudyptes" OR "Eudyptula" OR "Megadyptes" OR "Pygoscelis" OR "Spheniscus" OR "Aegolius" OR "Asio" OR "Athene" OR "Bubo" OR "Glaucidium" OR "Ketupa" OR "Lophostrix" OR "Megascops" OR "Micrathene" OR "Ninox" OR "Otus" OR "Pseudoscops" OR "Psiloscops" OR "Pulsatrix" OR "Sceloglaux" OR "Scotopelia" OR "Strix" OR "Surnia" OR "Xenoglaux" OR "Phodilus" OR "Tyto" OR "Aepyornis" OR "Mullerornis" OR "Struthio" OR "Anhinga" OR "Fregata" OR "Leucocarbo" OR "Microcarbo" OR "Nannopterum" OR "Phalacrocorax" OR "Morus" OR "Sula" OR "Crypturellus" OR "Eudromia" OR "Nothocercus" OR "Nothoprocta" OR "Nothura" OR "Rhynchotus" OR "Tinamotis" OR "Tinamus" OR "Apalharpactes" OR "Apaloderma" OR "Harpactes" OR "Pharomachrus" OR "Trogon" OR "Tetrastes" OR "Hesperiphona") AND ("experiment\*" OR "manipulat\*") ))\>
+
+Complete search string for the systematic search
+:::
+
+### Decision Tree
+
+::: {#figsupp-decision-tree}
+![Decision Tree for both Title and Abstract as well as Full-text Screening](figures/Decision_Tree_updated.png)
+:::
+
+::: {#figsupp-prisma-flowchart}
+This is the prisma flowchart
+:::
+
+::: {#figsupp-correlation}
+Table for different values of correlation
+:::
+
+::: {#figsupp-MLMA-excluded}
+Model output and plot including proxies that were excluded
+:::
+
+![](figures/Figure_parasite_birds_trait.png)

### 2025-07-05 code/00_search_stratergy_litsearchr_code.R

@@ -3,16 +3,14 @@
 # Since it is only available through Github and not CRAN
 # Skip this part if you have already installed litsearchr 
 
-
-install.packages("remotes")
-library(remotes)
+pacman::p_load(remotes, tidyverse)
 #to install litsearchr from Github
 install_github("elizagrames/litsearchr", ref="main")
 
 #-----------------------------------------------------------------------------------------------
 
 #Loading required packaged if they are already installed
-pacman::p_load(litsearchr,igraph,ggplot2,tidyverse)
+pacman::p_load(litsearchr,igraph,ggplot2)
 
 #---------------------------------- Naive search file import and deduplication---------------------------------------------
  
@@ -64,22 +62,22 @@ rakedkeywords<-
 #--------------------counting the occurance of searched keywords across studies in our database----------------------------
 
 #create_dfm counts the occurrence of the searched keywords across the studies and produces a matrix
-naive_dfm<-litsearchr::create_dfm(elements = paste(deduplicated_naiveimport$title,
-                                                   deduplicated_naiveimport$abstract,
-                                                   deduplicated_naiveimport$keywords),
+naive_dfm<-litsearchr::create_dfm(elements = paste(deduplicated_naiveimport$keywords,
+                                                   deduplicated_naiveimport$title,
+                                                   deduplicated_naiveimport$abstracts),
                                  features = rakedkeywords)
 
 
 
 #creating the network graph showing co-occurrence between the words (note that one can change
 #the numbers of studies and minimal occurence)
-naivegraph<-litsearchr::create_network(search_dfm = naive_dfm, min_studies = 3, 
-                                        min_occ = 2)
+  naivegraph<-litsearchr:: create_network(search_dfm = naive_dfm, min_studies = 3, 
+                                         min_occ = 2)
 
 #------------------------------------plots to visualise the searched keywords----------------------------------------------
 
-#it shows the grap with the co-occurence of words
-plot(naivegraph)
+#it shows the graph with the co-occurence of words
+# plot(naivegraph)
 
 #The ‘strength’ of each term in the network is the number of other terms that it appears together with
 strengths <- strength(naivegraph)
[…]

### 2025-07-05 code/01_systematic_search_deduplication.R

@@ -1,0 +1,112 @@
+##############################################################
+# Description of script and Instructions
+##############################################################
+
+# This script is to:
+# 1. import the .bib files from Web of Science (WOS) and Scopus
+# 2. combine the 2 .bib files to produce a full reference list (encoding errors may occur depending 
+# on the system and "UTF-16LE" was used in this case for writing and reading the full_reference_before_deduplication)
+# 3. deduplicate the full reference list and produce a unique list of 
+# papers
+
+# INPUT files: 
+# GNM_wos.bib
+# GNM_scopus.bib
+# full_reference_before_deduplication.csv should be read to see the exact data we 
+# used before de-duplication.Error in loading with revtools::read_bibliography
+# function when re-checked the code now added lines of code to read bib files with synthesisr
+
+# OUTPUT files:
+# full_reference_before_deduplication.csv
+# unique_reference_list.csv
+
+# Packages used: dplyr , revtools , synthesisr
+
+
+# created on 12.09.22 for green nest material project and updated on 02.06.2025
+# Code written by: SD and revised by: NA
+
+##############################################################
+# Packages needed
+##############################################################
+
+# load pacakges
+# If pacman is not installed already use
+# install.packages("pacman")
+pacman::p_load(dplyr, revtools)
+
+# cleaning up
+rm(list=ls())
+
+
+################################
+
+# importing the .bib files from WEB OF SCIENCE and SCOPUS
+
+## Initially this code used revtools::read_bibliography to read the .bib files from
+## WOS and Scopus. On re-running the code during check, this gives loading error. 
+## A good fix is to use synthesisr package so I am switching to that now even though 
+## in the project I used revtools (and report the same)..
+
+pacman::p_load(synthesisr)
+
+# reference_data_wos <- read_bibliography("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
+# reference_data_scopus <- read_bibliography("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
+
+
+reference_data_wos <- synthesisr::read_ref("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
+reference_data_scopus <- synthesisr::read_ref("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
+
+# reducing fields to the minimum number of fields
+# so that all databases have the same columns. Also, these fields
+# are the important ones for the screening.
+# reducing_fields <- c("label","title","author","journal",
[…]

### 2025-07-05 code/02_abstract_screening.R

@@ -1,0 +1,206 @@
+##############################################################
+# Description of script and Instructions
+##############################################################
+
+# This script is to:
+# 1. import the unique reference list after de-duplication
+# 2. Adding a unique identified (Paper_ID) for each article
+# 3. Creating subsets for title and abstract screening for the 
+# three screeners (SD, JS and TR) for preliminary and final phase of screening
+
+# Second part of this script was created to import the files after 
+# title and abstract screening to..
+
+# 4. import the files after title and abstract screening (after resolving any differences)
+# 5. Creating a final dataset_after_abstract_screening with only final decisions
+# 6. Creating a file with selected_abstract_screening for further steps
+
+# INPUT files required
+# 
+# differences_prelim_set1_2022_10_07
+# differences_prelim_set2_2022_10_14
+# differences_abstract_screening_set1
+# differences_abstract_screening_set2
+# differences_abstract_screening_set3
+
+# Title and abstract screening was conducted using revtools package- screen_abstracts()
+
+# Packages used: dplyr , revtools , readr, tidyverse, stringr
+
+
+# first created on 04.10.22 for green nest material project
+# Code written by: SD and revised by: NA
+
+##############################################################
+##############################################################
+# Before title and abstract screening was performed
+##############################################################
+##############################################################
+
+##############################################################
+# Packages needed
+##############################################################
+
+# load pacakges
+pacman::p_load(dplyr, revtools, readr, 
+               tidyverse, stringr)
+
+# cleaning up
+rm(list=ls())
+
+# set seed for reproducibility (for consistent random number generation)
+set.seed(1)
+
+############################################################
+# Importing data after de-duplication
+############################################################
+
+unique_reference_list <- read.table("data/01_systematic_search/02_reference_data/unique_reference_list.csv",
+                                    header=T,sep=",")
+
+# Giving individual paper ID for screening
+
+Paper_ID=sprintf("GNM_%03d", 1:nrow(unique_reference_list))
+unique_reference_list=cbind(Paper_ID,unique_reference_list)
+
+
+##################################################################
+# Abstract screening subsets for multiple screenings 
[…]

### 2025-07-05 code/03_fulltext_and_data_extraction.R

@@ -1,0 +1,136 @@
+##############################################################
+# Description of script and Instructions
+##############################################################
+# This script is to:
+# 1. import the selected_abstract_screening
+# 2. Creating subsets for data-extraction for the 
+# three screeners (SD, JS and TR) for preliminary and final phase of extraction
+
+
+
+# Packages used: readr
+
+# created on 09.08.23 for green nest material project
+# Code written by: SD and revised by: NA
+
+##############################################################
+##############################################################
+# For creating the dataset for full-text screening 
+# and data-extraction. Full-text screening and data-extraction
+# were performed together in Microsoft Excel
+##############################################################
+##############################################################
+
+##############################################################
+# Packages needed
+##############################################################
+
+# Load required packages
+# install.packages("pacman")
+pacman::p_load(readr, readxls)
+
+# environment clean up
+rm(list=ls())
+
+# set seed for reproducibility (essential for consistency of random number generation)
+set.seed(1)
+
+##############################################################
+# To load selected papers dataset after the abstract screening
+##############################################################
+
+selected_abstract_screening <- read_csv("data/01_systematic_search/03_title_and_abstract_screening/selected_abstract_screening.csv")
+
+##################################################################
+# Data-extraction subsets for multiple screenings 
+##################################################################
+
+##############################################################
+# Data-extraction (performed by SD, JS and TR) 
+# To randomly select 5 papers (~12.5%) for pilot data-extraction
+# Data-extraction performed on excel
+##############################################################
+
+random_ID1<-sample(1:nrow(selected_abstract_screening),5)
+prelim_extraction=selected_abstract_screening[random_ID1,]
+
+# write.csv(prelim_extraction,"data/02_data_extraction/prelim_extraction.csv",row.names=FALSE)
+
+##############################################################
+# Rest of the data-extraction performed by SD, JS and TR 
+# Each data-extraction is performed twice by two data-extractors 
+##############################################################
+
+# To create three sets with all the records for which the data 
+# extraction should be performed
+
+##############################################################
+
[…]

### 2025-07-05 data/02_data_extraction/extracted_raw_data/analysis_GNM_001_rep_table3.R

@@ -1,0 +1,44 @@
+pacman::p_load(here,tidyverse, readr)
+data_GNM_001_rep_table3 <- read_csv("data/02_data_extraction/extracted_raw_data/data_GNM_001_rep_table3.csv")
+
+# The dataset was provided in the paper as a table. It is not available in the 
+# published dataset so I am using it from the paper as a saved .csv file
+
+# Info from Table 3: abundance of nest-dwelling ectoparasitic arthropods between 
+# the 2 experimental groups of collected nests (treatment: control—0 and test—1)
+
+# Common names of all the taxonomic groups...
+common_names <- tibble(
+  TaxonomicGroup = c("Siphonaptera", "Diptera", "Protocalliphora", "Acari", "Ixodida",
+                     "Coleoptera", "Dermestidae", "Histeridae", "Staphylinidae", "Hymenoptera",
+                     "Lepidoptera", "Collembola", "Psocodea", "Hemiptera"),
+  CommonName = c("Fleas", "Flies", "Blowfly Parasites", "Mites", "Ticks",
+                 "Beetles", "Skin Beetles", "Clown Beetles", "Rove Beetles", "Wasps, Bees, and Ants",
+                 "Butterflies and Moths", "Springtails", "Booklice and Barklice", "True Bugs")
+)
+
+# Convert multiple columns into long format
+summary_data <- data_GNM_001_rep_table3 %>%
+  pivot_longer(cols = c(Siphonaptera, Diptera, Protocalliphora, Acari, Ixodida,
+                        Coleoptera, Dermestidae, Histeridae, Staphylinidae, Hymenoptera,
+                        Lepidoptera, Collembola, Psocodea, Hemiptera),
+               names_to = "TaxonomicGroup",
+               values_to = "Count") %>%
+# To calculate mean, SD and sample size by treatment for all measured taxonomic groups
+  group_by(Treatment, TaxonomicGroup) %>%
+  summarise(mean = mean(Count, na.rm = TRUE),
+            sd = sd(Count, na.rm = TRUE),
+            samplesize = n(),
+            .groups = "drop") %>%
+  left_join(common_names, by = "TaxonomicGroup") # Add common names
+
+# Print the final dataframe
+print(summary_data)
+
+
+ # Replace 0 with "Control" and 1 with "Treatment" in the Treatment column as given in table 3 summary
+summary_data <- summary_data %>%
[…]

### 2025-07-05 data/02_data_extraction/extracted_raw_data/analysis_GNM_069.R

@@ -1,0 +1,170 @@
+
+## Setting up workspace
+
+pacman::p_load(dplyr, readr) #Packages needed
+rm(list=ls()) ## cleaning up
+set.seed(1) #set seed for reproducibility (for random number generation)
+
+data_GNM_069 <- read_csv("data/02_data_extraction/extracted_raw_data/data_GNM_069.csv")
+
+head(data_GNM_069)
+summary(data_GNM_069)
+names(data_GNM_069)
+
+
+names(data_GNM_069) <- make.names(names(data_GNM_069), unique=TRUE)
+
+
+# Variables to extract: 
+# Tarsus length  3 days old  /	 Tarsus.length..14.days.old./ Body mas  3 days old. /	
+# log10.mesophilic.bacteria..3.days.old./
+# log10.Enterococcus..3.days.old. /# log.Carnus..day.8. / 
+#log10.mesophilic.bacteria..8days.old. / 
+# /Body.mas..14.days.old. /
+#/ Rank.Telomere.length..day.14. / 
+#Residuals.Rank.Telomere.length..day.14. / Dif.rank..14.3.days. / 
+# Residuals.Dif.rank..14.3.days.
+
+#Extracting data (SD;MEAN;sample size) Tarsus.length..3.days.old.
+
+data_GNM_069 %>%
+  group_by(Feather.treatments, Plant.treatments, Location, Nest) %>%
+  summarise(Tarsus.length..3.days.old.=mean(Tarsus.length..3.days.old.),
+            samplesize=(n())) %>%
+  group_by(Feather.treatments, Plant.treatments, Location) %>%
+     summarise(mean=mean(Tarsus.length..3.days.old.),
+                  sd=sd(Tarsus.length..3.days.old.),
+                  samplesize=(n()))
+
+
+
+#Extracting data (SD;MEAN;sample size) Tarsus.length..14.days.old.
+data_GNM_069 %>%
+  group_by(Feather.treatments, Plant.treatments, Location, Nest) %>%
+  summarise(Tarsus.length..14.days.old.=mean(Tarsus.length..14.days.old.),
+            samplesize=(n()))%>%
+  group_by(Feather.treatments, Plant.treatments, Location) %>%
+  summarise(mean=mean(Tarsus.length..14.days.old.),
+            sd=sd(Tarsus.length..14.days.old.),
+            samplesize=(n()))
+
+#Extracting data (SD;MEAN;sample size) Body.mas..3.days.old.
+data_GNM_069 %>%
[…]

### 2025-07-06 code/06_data_preparation.Rmd
Results comments addressed (initial stage).. continue results and discussion

---
title: "Data Preparation"
author: "Shreya D."
date: '`r Sys.Date()`'
output: html_document
license: CC-BY-4.0
email: shreya.dimri@uni-bielefeld.de
---

We have merged the data from different sources after data extraction, cleaned the typos and made it more usable. We have excluded the articles that did not pass full-text screening and the fitness proxies that we could not find a direction for the effect. These are steps done in the script **05_data_cleaning.Rmd** that generates the file **dataset_after_cleaning.csv**

In this script we will continue to prepare our dataset for use in meta-analysis, calculates variables for effect size estimation (SMDH, lnRR).

#### Input files needed

data/03_data_cleaning/dataset_after_cleaning.csv

#### Output files generated

### Setting up the workspace

```{r setup, warning=FALSE, message=FALSE, echo=F}

# Setting up workspace

pacman::p_load(here, tidyverse, dplyr, stringr, metafor, orchaRd,ggpubr,ggrepel) #Packages needed

rm(list=ls()) ## cleaning up

set.seed(8341) #set seed for reproducibility (for random number generation)

# Loading cleaned dataset

dataset_after_cleaning <- read_csv(here::here("data/03_data_cleaning/dataset_after_cleaning.csv"))

## Now all the changes we make to the file.. we will store them in data_analysis

dataset_analysis<-dataset_after_cleaning
```

#### Loading functions

Some functions we will need in this manuscript.. sourced mainly from Nakagawa 2022 : Online tutorial <https://alistairmcnairsenior.github.io/Miss_SD_Sim/>

```{r}

# Function to calculate Geary's "number"
  geary <- function(mean, sd, n){
    (1 / (sd / mean)) * ((4*n^(3/2)) / (1 + 4*n))
  }

# Shinichi Nakagawa, Daniel W. A. Noble, Malgorzata Lagisz, Rebecca Spake, Wolfgang Viechtbauer and Alistair M. Senior. 2022. A robust and readily implementable method for the meta-analysis of response ratios with and without missing standard deviations. Ecology Letters, DOI: 10.1111/ele.14144

  # Functions provided in the workalong
cv_avg <- function(x, sd, n, group, data, label = NULL, sub_b = TRUE, cv2=FALSE){

  # Check if the name is specified or not. If not, then assign it the name of the mean, x, variable input in the function. https://stackoverflow.com/questions/60644445/converting-tidyeval-arguments-to-string
  if(is.null(label)){
    label <- purrr::map_chr(enquos(x), rlang::as_label)
  }

  # Calculate between study CV. Take weighted mean CV within study, and then take a weighted mean across studies of the within study CV. Weighted based on sample size and pooled sample size.
  b_grp_cv_data <- data                                             %>%
    dplyr::group_by({{group}})                            %>%
    dplyr::mutate(   w_CV2 = weighted_CV({{sd}}, {{x}}, {{n}}, cv2=cv2),
                     n_mean = mean({{n}}, na.rm = TRUE))   %>%
    dplyr::ungroup(.)                                     %>%
    dplyr::mutate(b_CV2 = weighted.mean(w_CV2, n_mean, na.rm = TRUE), .keep = "used")

  # Make sure that label of the calculated columns is distinct from any other columns
  names(b_grp_cv_data) <- paste0(names(b_grp_cv_data), "_", label)

  # Append these calculated columns back to the original data and return the full dataset.
  if(sub_b){
    b_grp_cv_data <- b_grp_cv_data %>% dplyr::select(grep("b_", names(b_grp_cv_data)))
    dat_new <- cbind(data, b_grp_cv_data)
  } else {
    dat_new <- cbind(data, b_grp_cv_data)
  }

  return(data.frame(dat_new))
}

# You also need the helper function

weighted_CV <- function(sd, x, n, cv2=FALSE){
  if(cv2){
    weighted.mean(na_if((sd / x)^2, Inf), n, na.rm = TRUE)
  }else{
    weighted.mean(na_if((sd / x), Inf), n, na.rm = TRUE)^2
  }
}

#' @title lnrr_laj
#' @description Calculates log response ratio based on Taylor expansion from Jajeunesse 2011
#' @param m1 Mean of treatment group 1
#' @param m2 Mean of treatment group 2
#' @param cv1_2 Coefficient of variation squared (CV^2) for treatment group 1
#' @param cv2_2 Coefficient of variation squared (CV^2) for treatment group 2
#' @param n1 Sample size for treatment group 1
#' @param n2 Sample size for treatment group 2
#' @param taylor A logical indicating whether to calculate point estimate with Taylor expansion.
#'
lnrr_laj <- function(m1, m2, cv1_2, cv2_2, n1, n2, taylor=TRUE){
  if(taylor){
    log(m1 / m2) + 0.5*((cv1_2 / n1) - (cv2_2 / n2))
  } else {
    log(m1 / m2)
  }
}

#' @title v_lnrr_laj
#' @description Calculates the sampling variance for log response ratio based on second order Taylor expansion proposed by Lajeunesse 2011
#' @param cv1_2 Coefficient of variation squared (CV^2) for treatment group 1
#' @param cv2_2 Coefficient of variation squared (CV^2) for treatment group 2
#' @param n1 Sample size for treatment group 1
#' @param n2 Sample size for treatment group 2
#' @param taylor A logical indicating whether to calculate point estimate with Taylor expansion.
v_lnrr_laj <- function(cv1_2, cv2_2, n1, n2,  taylor=TRUE){
  if(taylor){
  ((cv1_2) / n1) + ((cv2_2) / n2) +
    ((cv1_2)^2 / (2*n1^2)) + ((cv2_2)^2 / (2*n2^2))
  } else {
    ((cv1_2) / n1) + ((cv2_2) / n2)
  }
}

```

# Preparing Random Effects

In our pre-registration, we considered the following levels of non-independence for our analysis:

"(1) paper_ID, which encompasses estimates extracted from the same primary study,

(2) experiment_ID,

(3) group_ID

(4) repeated_traits_ID, and

(5) observation_ID which corresponds to a unit-level observation identity and models within-study variance

As mentioned above, if we obtain additional effect sizes for other bird species after we update our search and/or contact authors, our models may need to account for phylogenetic nonindependence via the inclusion of two additional random effects: "species" and "phylogeny" following Cinar et al. (2022)."

-   We also need to add `observation ID` which is the unit-level identity (unique for each row) for within-study variance.

-   In the way we extracted this information, each paper_ID needs to be added to the random effect level of `experiment_ID`, `group_ID` and `repeated_trait_ID` to make sure they are unique values.

```{r Prepare Random Effects as Unique ID}

dataset_analysis<-dataset_analysis%>%

  mutate(Observation_ID = as.factor(row_number()))%>%

  mutate(experiment_ID_coded = as.factor(paste(paper_ID, experiment_ID, sep="_")),.after=experiment_ID)%>%
  mutate(group_ID_coded = as.factor(paste(paper_ID, group_ID, sep="_")),.after=group_ID)%>%
  mutate(repeated_trait_ID_coded = as.factor(paste(paper_ID,repeated_trait_ID, sep="_")),.after=repeated_trait_ID)

# random_effects_check<-dataset_analysis%>%select(paper_ID,experiment_ID,group_ID,repeated_trait_ID, experiment_ID_coded,group_ID_coded, repeated_trait_ID_coded)

```

-   We also decided to add `population ID` since we noticed several studies were performed in the same geographical location.

```{r}
dataset_analysis<-dataset_analysis%>%
  mutate(population_ID = as.factor(population_location))

# Let's look at the nammes of the locations
# unique(dataset_analysis$population_ID)

# There are clearly many repeated names, let's clean this up a bit

dataset_analysis <- dataset_analysis %>%
  mutate(
    population_ID = str_squish(as.character(population_location)),  # Clean whitespace
    population_ID = case_when(
      # Lodz
      str_detect(population_ID, regex("lodz|łódź|central poland", ignore_case = TRUE)) ~ "Lodz, Poland",

      # Montijo / Tagus Estuary
      str_detect(population_ID, regex("montijo|tagus estuary|air force base", ignore_case = TRUE)) ~ "Montijo, Portugal",

      # Madrid Region
      str_detect(population_ID, regex("madrid|manzanares|villalba|soto del real|central spain", ignore_case = TRUE)) ~ "Madrid Province, Spain",

      # Nova Scotia / New Brunswick
      str_detect(population_ID, regex("nova scotia|new brunswick", ignore_case = TRUE)) ~ "Nova Scotia and New Brunswick, Canada",

      # Vosbergen
      str_detect(population_ID, regex("vosbergen|groningen", ignore_case = TRUE)) ~ "Vosbergen, Netherlands",

      # Hoya de Guadix
      str_detect(population_ID, regex("hoya de guadix|calahorra|hueneja", ignore_case = TRUE)) ~ "Hoya de Guadix, Spain",

      # Valsaín
      str_detect(population_ID, regex("valsain|segovia", ignore_case = TRUE)) ~ "Valsaín, Spain",

      # Vanderhoof
      str_detect(population_ID, regex("vanderhoof", ignore_case = TRUE)) ~ "Vanderhoof, Canada",

      # Patuxent
      str_detect(population_ID, regex("patuxent|laurel, maryland", ignore_case = TRUE)) ~ "Patuxent Wildlife Research Center, USA",

      # Betty Daw’s Wood
      str_detect(population_ID, regex("betty daw", ignore_case = TRUE)) ~ "Betty Daw’s Wood, UK",

      # Lake Ammersee
      str_detect(population_ID, regex("ammersee|south germany|andechs", ignore_case = TRUE)) ~ "Lake Ammersee, Germany",

      # Corsica
      str_detect(population_ID, regex("corsica|muro valley|quercus", ignore_case = TRUE)) ~ "Corsica, France",

      # SWRC Philadelphia
      str_detect(population_ID, regex("swrc|philadelphia", ignore_case = TRUE)) ~ "SWRC, Philadelphia, USA",

      # Coimbra
      str_detect(population_ID, regex("coimbra|mata nacional do choupal", ignore_case = TRUE)) ~ "Coimbra, Portugal",

      # Kuankuoshui
      str_detect(population_ID, regex("kuankuoshui", ignore_case = TRUE)) ~ "Kuankuoshui Nature Reserve, China",

      # Werther
      str_detect(population_ID, regex("werther|52°06′n|52°06’n", ignore_case = TRUE)) ~ "Werther, Germany",

      # Bergen
      str_detect(population_ID, regex("bergen", ignore_case = TRUE)) ~ "Bergen, Norway",

      # for clean but unmatched names
      TRUE ~ str_to_title(population_ID)
    )
  )

```

# Effective Sample Size Calculation

For comparisons involving the shared control or treatment groups across multiple studies, we adjust the sample sizes by dividing them by the number of times each group is included in comparisons. This adjustment helps to prevent any inflation of the effect sizes due to repeated use of the same groups and account for the shared-group non-independence.

```{r effective sample size}

dataset_analysis<-dataset_analysis%>%
  mutate(effective_n_experiment=(n_experiment/shared_experiment),.after=n_experiment)%>%
  mutate(effective_n_control=(n_control/shared_control),.after=n_control)
```

Checking the range of effective sample size in our dataset

```{r}
dataset_analysis%>%
  summarise(control_min=min(effective_n_control,na.rm=T),
            control_max=max(effective_n_control,na.rm=T),
            na_control = sum(is.na(effective_n_control)),
            experiment_min=min(effective_n_experiment,na.rm=T),
            experiment_max=max(effective_n_experiment,na.rm=T),
             na_experiment = sum(is.na(effective_n_experiment)))
```

We have some NA and some values of effective sample size 1 and below.. lets see where this is

```{r}
low_sample<-dataset_analysis%>%
  filter(effective_n_control<2 | effective_n_experiment<2)
```

Many of these data points come from GNM_355. There are datapoints with sample size of 1 for some groups. We have extracted data by days and months.. I will combine these for this paper because of such low sample size.

After combining or those I could not combine.. some still have a low sample size..

We can only estimate SMHD with dF (n1+n2-2) greater than 1. lnRR could be calculated regardless. So I will not exclude any rows specifically even though the effective sample size could be lower than 2 in a group.

# Converting variance to SD

There were no other measure of dispersion, only SE and SD, so no need to convert anything more.

```{r Calculating SD}
## Calculating sd from difference variance measures (only for se so far)

# For experimental group
dataset_analysis <- dataset_analysis %>%
  mutate(sd_experiment = if_else(type_measure_dispersion_experiment %in% c('se', 'SE'), #condition to check
      measure_dispersion_experiment * sqrt(as.numeric(n_experiment)), # do this if true
      measure_dispersion_experiment), #else do this
      .after=measure_dispersion_experiment)
# For control group
dataset_analysis <- dataset_analysis %>%
  mutate(sd_control = if_else(type_measure_dispersion_control %in% c('se', 'SE'), #condition to check
      measure_dispersion_control* sqrt(as.numeric(n_control)), # do this if true
      measure_dispersion_control), #else do this
      .after=measure_dispersion_control)
```

Some checks for the value of mean and SD

```{r}
# Some rows contain NAs, check why
# contains_NA<-dataset_analysis%>%
# filter(is.na(measure_central_tendency_experiment)|is.na(measure_dispersion_experiment))

# 24 rows contain NA and I checked them manually, everything looks okay. 
# - 4 rows contain only statistical test values and 
# - 4 rows contain values for contingency tables only
# - 16 are missing data that authors did not provide for which we will use 0 as effect size. 
```

# No effect size provided

Authors did not report the means/effect size for some cases but said they found no difference between the group. For these cases, we will assume the effect size to be exactly zero.

We will calculate the mean trait values by trait type (e.g. physiological, reproductive, etc.) We calculate the mean of both treatment and control group. Then I will assign this mean trait value to all the fitness proxies of that trait type. This way, the difference X1-X2 would be 0 (for SMDH) as well as the log(X1/X2) would also be zero (for log response ratio). Using this, we will then impute the SD for the effect size.

We imputed its sampling variance using the missing-case approach described for lnRR. (see *Nakagawa, S., Noble, D.W.A., Lagisz, M., Spake, R., Viechtbauer, W. & Senior, A.M. (2023) A robust and readily implementable method for the meta-analysis of response ratios with and without missing standard deviations. Ecology Letters, 26, 232–244. Available from: <https://doi.org/10.1111/ele.14144>* for more details)

Using the formula (n1+n2)/(n1×n2)(n_1 + n_2)/(n_1 \\times n_2)(n1​+n2​)/(n1​×n2​) for SMDH (see *Lajeunesse, Marc J., 'Recovering Missing or Partial Data from Studies: A Survey of Conversions and Imputations for Meta-analysis', in Julia Koricheva, Jessica Gurevitch, and Kerrie Mengersen (eds), Handbook of Meta-analysis in Ecology and Evolution (Princeton, NJ, 2013; online edn, Princeton Scholarship Online, 19 Oct. 2017), <https://doi.org/10.23943/princeton/9780691137285.003.0013>, accessed 5 July 2025* for more details)\
\
We will also run a sensitivity analysis without these proxies to ensure robustness of our results.

```{r}
# To calculate means by groups
trait_mean<- dataset_analysis%>%
  group_by(trait_type)%>%
  summarise(
    cumulative_mean = mean (
      c(measure_central_tendency_experiment,measure_central_tendency_control),
      na.rm=T
    ),
    count = n()
  )%>%
  arrange(desc(count))

# Now I need to assign the mean values from this to the missing ES proxies
dataset_analysis<-dataset_analysis%>%
  left_join(trait_mean, by= "trait_type")%>%
  mutate(measure_central_tendency_experiment = if_else((
    proxy_comment == "use 0 as ES" & !is.na(proxy_comment)),
    cumulative_mean,
    measure_central_tendency_experiment),
    measure_central_tendency_control = if_else((
    proxy_comment == "use 0 as ES" & !is.na(proxy_comment)),
    cumulative_mean,
    measure_central_tendency_control),)%>%
  select(-cumulative_mean)

```

# Effect Size Estimation

## Calculate lnRR

### Geary's Test

```{r}
# Assumption of normality assumed to be approximately correct when values are >= 3.
dataset_analysis<- dataset_analysis %>% 
         mutate(geary_control = geary(measure_central_tendency_control,
                                      sd_control, 
                                      n_control),
                    geary_trt = geary(measure_central_tendency_experiment,
                                      sd_experiment, 
                                      n_experiment),
                   geary_test = ifelse(geary_control >= 3 & geary_trt >= 3, "pass", "fail"))

# How many fail?
    geary_res <-dataset_analysis %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()

    geary_res
```

**48 observations fail Geary's test.**

However, we do not exclude anything but as suggested by Lajeunesse (2015), I will do a sensitivity analysis with and without these effect sizes for lnRR.

Since lnRR can only be calculated for ratio scale data (i.e., data with a true zero; among other assumptions), we will exclude effect sizes with a negative value when calculating lnRR.

```{r for lnRR}

## ─────────────────────────────────────────────────────────────
## 1.  Keeping rows where lnRR can be calculated. 
## Inferential stats and contingency table can only be used for SMDH.
##    — store the dropped rows to inspect and join back later
## ─────────────────────────────────────────────────────────────

only_SMDH <-dataset_analysis%>%
  filter(proxy_decision == "contingency table"
         |proxy_decision == "SMDH only")

dataset_analysis <- dataset_analysis %>%
  anti_join(only_SMDH, by = names(dataset_analysis))

## -------------------------------------------------------------------------
## 2. Rows whose means are > 0 (lnRR needs ratio scale data)
##  - store the dropped rows to inspect and join back later to the dataset
## -------------------------------------------------------------------------

neg_means<- dataset_analysis%>%
 filter(measure_central_tendency_experiment <= 0 |
         measure_central_tendency_control <= 0)

dataset_analysis <- dataset_analysis %>%
  anti_join(neg_means, by = names(dataset_analysis))

## -------------------------------------------------------------------------
## 3. Estimating lnRR using metafor::escalc for cases where SD is available
## -------------------------------------------------------------------------

# Using function 'escalc()' (with measure=ROM and 'vtype=LS')

dataset_analysis<- escalc(measure = "ROM", 
              vtype= "LS",
                        n1i = effective_n_experiment, 
                        n2i = effective_n_control,
                        m1i = measure_central_tendency_experiment, 
                        m2i = measure_central_tendency_control,
                        sd1i = sd_experiment, 
                        sd2i = sd_control,
                        data = dataset_analysis, 
                        var.names = c('lnRR',
                                      'lnRR_variance'),
                        add.measure = FALSE,
                        append = TRUE)

## How many lnRR were not calculates?

not_calculated<-dataset_analysis%>%filter(is.na(lnRR)|is.na(lnRR_variance))

## 16 rows have missing values of ES.. we have to impute the values here..

## -------------------------------------------------------------------------
## 4. Estimating lnRR using Missing Case approach from Nakagawa 2022
##    see https://alistairmcnairsenior.github.io/Miss_SD_Sim/
## -------------------------------------------------------------------------

# A: Calculate the average between study CV, which will replace missing values.
   # Study-level pooled CV² (square of weighted-average CV)
   # – one call per group, using your cv_avg() helper

dataset_analysis <- cv_avg(x = measure_central_tendency_experiment, 
                           sd = sd_experiment,
                           n = effective_n_experiment, 
                           group = paper_ID, 
                           label = "exp",
                           data = dataset_analysis)
dataset_analysis <- cv_avg(measure_central_tendency_control, 
                           sd = sd_control,
                           n = effective_n_control, 
                           group = paper_ID, 
                           label = "con",
                           data = dataset_analysis)
# B: Keep study-specific CV² when SD present and pooled CV² when SD is missing

dataset_analysis <- dataset_analysis %>%
  mutate(cv_Control= sd_control/measure_central_tendency_control,
         cv_Experimental= sd_experiment/measure_central_tendency_experiment,
         cv2_con_new = if_else(is.na(sd_control),
                               b_CV2_con,          # pooled CV²
                               cv_Control^2),      # study-specific CV²
         cv2_exp_new = if_else(is.na(sd_experiment),
                               b_CV2_exp,
                               cv_Experimental^2))

# C: Lajeunesse Eqs. 6 & 7 for EVERY row using lnrr_laj and v_lnrr_laj functions
## As would be recommended for ALL CASE method from Nakagawa 2022.

dataset_analysis <- dataset_analysis %>%
  mutate(lnrr_laj = lnrr_laj(m1 = measure_central_tendency_experiment,
                             m2 = measure_central_tendency_control,
                             cv1_2 = cv2_exp_new,
                             cv2_2 = cv2_con_new,
                             n1 = effective_n_experiment,
                             n2 = effective_n_control),
         v_lnrr_laj = v_lnrr_laj(cv1_2 = cv2_exp_new,
                                 cv2_2 = cv2_con_new,
                                 n1 = effective_n_experiment,
                                 n2 = effective_n_control))

## -------------------------------------------------------------------------
## 4. Replace NA ("use 0 as ES") cases in lnRR/lnRR_variance with imputed values
## -------------------------------------------------------------------------

dataset_analysis<-dataset_analysis%>%
  mutate(lnRR = if_else((
    proxy_comment == "use 0 as ES" & !is.na(proxy_comment)),
    lnrr_laj,
    lnRR),
   lnRR_variance = if_else((
    proxy_comment == "use 0 as ES" & !is.na(proxy_comment)),
    v_lnrr_laj,
    lnRR_variance),)%>%
select(-b_CV2_exp,-b_CV2_con,-cv_Control,-cv_Experimental,-cv2_con_new,-cv2_exp_new,-lnrr_laj,-v_lnrr_laj)

## How many lnRR were not calculated now?

not_calculated<-dataset_analysis%>%filter(is.na(lnRR)|is.na(lnRR_variance))

## All rows have a value, good.. this is what would be expected.

## -------------------------------------------------------------------------
## 5. Adding back the removed rows with NA values for the new columns
## We still have to use these for calculating SMDH values in the dataset
## -------------------------------------------------------------------------

dataset_analysis<-bind_rows(dataset_analysis,only_SMDH,neg_means)
```

### Sign for Effect Size

We have to ensure throughout the dataset that positive values mean higher estimates of fitness in the experimental group compared to their control counterparts by multiplying all the effect sizes by their corresponding sign **(stored in variable proxies_sign)**, i.e., by -1 or +1.

```{r correct sign for ES}

dataset_analysis<-dataset_analysis%>%
  mutate(lnRR_sign=lnRR*proxies_sign)
```

### Outliers Check

We do not plan to exclude any outliers as long as the extracted data is seemingly correct.

Now let's plot means and SD to see everything looks okay

```{r}

# ## We have to exclude the datapoints where we do not have dispersion value. We have added 0 ES in some cases and this is not allowing the lm line to be plotted
# #
# temp_data<-dataset_analysis%>%
#   filter(!is.na(measure_dispersion_experiment) & !is.na(measure_dispersion_control) & !is.na(measure_central_tendency_experiment) & !is.na(measure_central_tendency_control) & !is.na(lnRR))
# dataset_lnRR_plot<-temp_data
# 
# outliers_experiment<- dataset_lnRR %>%
#   filter(measure_dispersion_experiment>100)
# outliers_control<- dataset_lnRR %>%
#   filter(measure_dispersion_control >100)
# 
# 
# # For experimental group
# 
# # Fit a linear model to extract the intercept
# lm_fit_experiment <- lm(log(measure_dispersion_experiment) ~
#                           log(measure_central_tendency_experiment),
#                         data = dataset_lnRR_plot)
# intercept_value_experiment <- coef(lm_fit_experiment)[1] # Extract the intercept
# 
# lm_fit_control <- lm(log(measure_dispersion_control) ~
#                        log(measure_central_tendency_control),
#                      data = dataset_lnRR_plot)
# intercept_value_control <- coef(lm_fit_control)[1]
# 
# # Scatter plot of means vs SDs for experimental group
# dataset_lnRR_plot %>%
#   ggplot(aes(x = log(measure_central_tendency_experiment),
#              y = log(measure_dispersion_experiment),
#              size = effective_n_experiment,
#              colour = trait_type)) +
#   geom_point(alpha = 0.6) +
#   geom_text_repel(
#     data = outliers_experiment,
#     aes(
#       x = log(measure_central_tendency_experiment),
#       y = log(measure_dispersion_experiment),
#       label = fitness_proxy_cleaned
#     ),
#     size = 3, color = "black", max.overlaps = 15
#   ) +
#   geom_smooth(
#     method = "lm",  # Adds a regression line
#     se = TRUE,      # Adds confidence intervals
#     color = "blue", # Color of the line
#     linetype = "solid",# Style of the line
#     size = 0.4
#   ) +
#   # Add a line representing correlation of 1
#   geom_abline(
#     slope = 1,       # Slope of the line
#     intercept = intercept_value_experiment,   # Intercept of the line
#     color = "black", # Color of the line
#     linetype = "dashed", # Style of the line
#     size = 0.4       # Thickness of the line
#   )+
#   labs(
#     x = "Log Mean Value",
#     y = "Log Standard Deviation (SD)",
#     title = "Log-transformed Experimental Groups"
#   ) +
#   theme_minimal() +
#   theme(
#     plot.title = element_text(size = 12, face = "bold"),
#     axis.title = element_text(size = 10),
#     axis.text = element_text(size = 10)
#   )
# 
# # For Control group
# 
# # Scatter plot of means vs SDs for experimental group
# dataset_lnRR_plot %>%
#   ggplot(aes(x = log(measure_central_tendency_control),
#              y = log(measure_dispersion_control),
#              size = effective_n_control)) +
#   geom_point(color = "brown", alpha = 0.6) +
#   geom_text_repel(
#     data = outliers_control,
#     aes(
#       x = log(measure_central_tendency_control),
#       y = log(measure_dispersion_control),
#       label = fitness_proxy_cleaned
#     ),
#     size = 3, color = "black", max.overlaps = 15
#   ) +
#   geom_smooth(
#     method = "lm",  # Adds a regression line
#     se = TRUE,      # Adds confidence intervals
#     color = "blue", # Color of the line
#     linetype = "dashed", # Style of the line
#     size= 0.4
#   ) +
#   # Add a line representing correlation of 1
#   geom_abline(
#     slope = 1,       # Slope of the line
#     intercept = intercept_value_control,   # Intercept of the line
#     color = "black", # Color of the line
#     linetype = "dashed", # Style of the line
#     size = 0.4       # Thickness of the line
#   )+
#   labs(
#     x = "Log Mean Value",
#     y = "Log Standard Deviation (SD)",
#     title = "Log-transformed Control Groups"
#   ) +
#   theme_minimal() +
#   theme(
#     plot.title = element_text(size = 12, face = "bold"),
#     axis.title = element_text(size = 10),
#     axis.text = element_text(size = 10),
#     legend.position = "none"
#   )
# 
# 
# # ggarrange(sd_experiment_plot,sd_control_plot,
#                                      ncol = 2,  nrow = 1,
#                                      labels = c("A.", "B.",
#                                                 common.legend = TRUE))

```

```{r Funnel Plot}

funnel_lnRR <- dataset_analysis %>%
  ggplot(aes(x = lnRR_sign, y = 1 / lnRR_variance)) +
  geom_point(color= "#7DCE82", alpha = 0.4, size = 3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "#8B4513", linewidth=0.65) +  # Add vertical dashed line at x = 0
  ggtitle("Funnel Plot for lnRR") +
  xlab("lnRR") +
  ylab("Precision (1/Variance)")

print(funnel_lnRR)

rows_with_missing <- dataset_analysis %>%
  filter(is.na(lnRR_sign) | is.na(lnRR_variance))

```

```{r}
log_values <- dataset_analysis %>%
  filter(str_detect(variable_note, regex("log", ignore_case = TRUE)))
```

## Calculate SMDH

-   For results only reported as inferential statistics (e.g., t-test, chi-square), we will use the equations provided by (Lajeunesse 2013; Nakagawa and Cuthill 2007; and other sources if needed) to calculate their corresponding SMD estimates for the analyses.

-   Note that lnRR cannot be calculated from inferential statistics and that only SMD without heteroskedasticity correction can be calculated from inferential statistics.

```{r}
#-------------------------------------------------------------------------
# 1. SMDH for most cases where mean, variance and sample size was reported
#-------------------------------------------------------------------------

## using function 'escalc()' with measure=SMDH and 'vtype=LS'

dataset_analysis<- escalc(measure = "SMD", 
              vtype= "LS",
                        n1i = effective_n_experiment, 
                        n2i = effective_n_control,
                        m1i = measure_central_tendency_experiment, 
                        m2i = measure_central_tendency_control,
                        sd1i = sd_experiment, 
                        sd2i = sd_control,
                        data = dataset_analysis, 
                        var.names = c('SMDH',
                                      'SMDH_variance'),
                        add.measure = FALSE,
                        append = TRUE)

# Cases where it was not calculated using mean, variance and sample size
noSMDH<-dataset_analysis%>%filter(is.na(SMDH))

#-------------------------------------------------------------------------
# 2. No effect of the treatment is present but 
# estimates (means, test statistics or effect size) were not reported
#-------------------------------------------------------------------------

# Since authors report no significant effect of the treatment, 
# we assume that the means are not different in the treatment and control group. 
# Under this assumption SMD = M(treatment)-M(control)/SD(pooled) which would be zero
# and the associated variance = n(treatment)+n(control)/n(treatment)+n(control)

dataset_analysis <- dataset_analysis %>%
  mutate(SMDH = if_else(proxy_comment == "use 0 as ES" & !is.na(proxy_comment), (measure_central_tendency_experiment-measure_central_tendency_control), SMDH))%>%
  mutate(SMDH_variance = if_else(proxy_comment == "use 0 as ES" & !is.na(proxy_comment), ((effective_n_experiment+effective_n_control)/(effective_n_experiment*effective_n_control)), SMDH_variance))

# Cases where it was not calculated using mean, variance and sample size
noSMDH<-dataset_analysis%>%filter(is.na(SMDH))

```

#### Data as contingency table

**IMPORTANT NOTE**: For calculation from contingency tables, the measure of central tendency is used to store value of percentage of success reported. It is not a measure of central tendency.

For cases when the data is reported as a contingency table. In these cases we will calculate the Odds ratio and convert it to SMD.. (and not SMDH)

General Calculation Formulas

1.  **Number of Successes and Failures**

    -   Success in Group A: $S_A = \left(\frac{p_A}{100}\right) \times N_A$

    -   Failure in Group A: $F_A = N_A - S_A$

    -   Success in Group B: $S_B = \left(\frac{p_B}{100}\right) \times N_B$

    -   Failure in Group B: $F_B = N_B - S_B$

        where N is Total Sample Size and P is the number of successful nests

2.  **Odds Ratio (OR)**\
    $$OR = \frac{S_A \times F_B}{S_B \times F_A}$$

3.  **Log Odds Ratio (lnOR)**\
    $$\ln(OR) = \log \left( \frac{S_A \times F_B}{S_B \times F_A} \right)$$

4.  **Variance of Log Odds Ratio (lnOR)**

    $$ V_{\ln OR} = \frac{1}{2} \left( \frac{1}{S_A} + \frac{1}{F_A} + \frac{1}{S_B} + \frac{1}{F_B} \right)$$

5.  **Standardized Mean Difference (SMD)**

    $$SMD = \frac{\ln(OR) \times \sqrt{3}}{\pi}$$

6.  **Variance of Standardized Mean Difference (SMD)**

    $$V_{SMD} = \frac{3 \times V_{\ln OR}}{\pi^2}$$

```{r}
contingency_table<-dataset_analysis%>%filter(proxy_decision=="contingency table")

unique(contingency_table$fitness_proxy)
# We have nests with complete reproductive success (%)..

# Calculate Odds Ratio (OR) and Log Odds Ratio (lnOR)

contingency_table <- contingency_table %>%
  mutate(
    # Calculate the number of successes and failures for experiment and control groups
    success_experiment = round((measure_central_tendency_experiment / 100) * n_experiment),
    failure_experiment = n_experiment - success_experiment,
    success_control = round((measure_central_tendency_control / 100) * n_control),
    failure_control = n_control - success_control)
    # Calculate Log Odds Ratio (lnOR)
contingency_table<- escalc(measure="OR", ai=success_experiment, bi=failure_experiment, ci=success_control, di=failure_control, data=contingency_table, var.names = c('lnOR',
                                      'lnOR_variance'))
# Calculate SMDH
contingency_table <- contingency_table %>%
  mutate(SMDH=(lnOR*sqrt(3))/pi,
         SMDH_variance=(3*lnOR_variance)/pi^2)

# Update SMDH and SMDH_variance based on Observation_ID
dataset_analysis <- rows_update(
  x = dataset_analysis,           # Target dataset to update
  y = contingency_table %>% 
        select(Observation_ID, SMDH, SMDH_variance), # Updates from contingency_table
  by = "Observation_ID"       # Match on Observation_ID
)
```

#### For SMDH from ANCOVA and t-test

Note that, since we did not have access to the corresponding $R^2$ values, using Equation 1 for transforming F-values from an ANCOVA into Cohen's d, we will use Equation 2 instead.

Equation 1: Estimating Cohen's d from independent groups using ANCOVA

![From Cooper2019 Table 11.3](/images/ancova-d.png)

Equation 2: Estimating Cohen's d from independent groups using ANOVA

![From Cooper2019 Table 11.3](/images/anova-d.png)

We will slightly overestimate $d$ and underestimate $V_d$ the larger that unknown $R^2$ value is (see simulation on sensitivity analysis tab); however, we decided to use it to avoid excluding those three effect sizes.

```{r}

ancova_SMDH<-dataset_analysis%>%filter(statistics_type=="ANCOVA")
# 3 effect size where SMDH needs to be estimated from ANCOVA

# Function to compute Cohen's d (from ANOVA)
d_anova <- function(F, n1, n2) {
  sqrt((F * (n1 + n2)) / (n1 * n2))
}

# Function to compute variance (from ANOVA)
var_d_anova <- function(d_anova, n1, n2) {
  ((n1 + n2) / (n1 * n2)) + (d_anova^2 / (2 * (n1 + n2)))
}

ancova_SMDH<-ancova_SMDH%>%
  mutate(SMDH = sign_relationship*(d_anova(statistics_value,n_experiment,n_control)))%>%
    mutate(SMDH_variance = var_d_anova(SMDH, n_experiment,n_control))

# Update SMDH and SMDH_variance based on Observation_ID
dataset_analysis <- rows_update(
  x = dataset_analysis,           # Target dataset to update
  y = ancova_SMDH %>% 
        select(Observation_ID, SMDH, SMDH_variance), # Updates from ancova_SMDH
  by = "Observation_ID"       # Match on Observation_ID
)
```

![from Table 11.1 Cooper2019](/images/t-d.png)

```{r}
# 1 effect size where SMDH needs to be estimated from t-test statistics
t_test_SMDH<-dataset_analysis%>%filter(statistics_type=="t-test")

# Function to compute Cohen's d (from t)
d_t_test <- function(t, n1, n2) {
  t * sqrt((n1 + n2) / (n1 * n2))
}

# Function to compute variance (from t)
var_d_t_test <- function(d_t_test, n1, n2) {
  ((n1 + n2) / (n1 * n2)) + (d_t_test^2 / (2 * (n1 + n2)))
}

t_test_SMDH<-t_test_SMDH%>%
  mutate(SMDH = sign_relationship*(d_t_test(statistics_value,n_experiment,n_control)))%>%
    mutate(SMDH_variance = var_d_t_test(SMDH, n_experiment,n_control))

# Update SMDH and SMDH_variance based on Observation_ID
dataset_analysis <- rows_update(
  x = dataset_analysis,           # Target dataset to update
  y = t_test_SMDH %>% 
        select(Observation_ID, SMDH, SMDH_variance), # Updates from t_test_SMDH
  by = "Observation_ID"       # Match on Observation_ID
)
```

### Sign for Effect Size

```{r correct sign for ES SMDH}

dataset_analysis<-dataset_analysis%>%
  mutate(SMDH_sign=SMDH*proxies_sign)
```

### Low sample size

```{r}
# 9 from GNM_355 where repeated estimates over days for haemoglobin are present and I cannot combine them as I did for chick mass over months.. since the sample is the same and these are the repeated measures of the same sample.
noSMDH=dataset_analysis%>%filter(is.na(SMDH))
```

## Saving all output files

```{r}
# # Complete dataset that can be used for analysis
# write.csv(dataset_analysis,file=here::here("data/04_data_analysis/dataset_analysis.csv"),row.names = FALSE)
# 
# 
# # Dataset that can be used to estimate lnRR
# 
# dataset_lnRR<-dataset_analysis%>%
#   filter(!is.na(lnRR_sign) & !is.na(lnRR_variance))
# 
# write.csv(dataset_lnRR,file=here::here("data/04_data_analysis/dataset_lnRR.csv"),row.names = FALSE)
# 
# # Dataset that can be used to estimate SMD(H)
# 
# dataset_SMDH<-dataset_analysis%>%
#   filter(!is.na(SMDH_sign) & !is.na(SMDH_variance))
# 
# write.csv(dataset_SMDH,file=here::here("data/04_data_analysis/dataset_SMDH.csv"),row.names = FALSE)
```

### 2025-07-06 docs/code/07_data_analysis.Rmd
Results comments addressed (initial stage).. continue results and discussion

--- 2025-06-17 docs/notebook/data_analysis.qmd
@@
 ---
-title: "Green Nest Material Meta-Analysis"
-subtitle: "The adaptive value of green nest material across birds: A systematic review and meta-analysis"
-author: "Shreya Dimri"
-date: last-modified
-
-format:
-  html:
-   toc: true 
-   toc-title: "Table of Contents" 
-   toc-depth: 2 
-   toc-expand: 3 
-   toc-location: left 
-   mainfont: Verdana 
-   monofont: Jetbrains Mono 
-   fontsize: 12pt 
-   code-fold: show
-   df-print: paged 
-   highlight-style: github 
-   pdf: default
-editor: visual
+title: "Data Analysis"
+author: "Shreya D."
+date: "`r Sys.Date()`"
+output: html_document
 ---
 
-## Loading Data for analysis
-
-```{r setup, warning=FALSE, message=FALSE, echo=F}
+# Loading Data for analysis
+
+```{r load_packages-data, warning=FALSE, message=FALSE}
 
@@
 # For plotting trees, and although not strictly necessary, we may need the `ggtree` R package, which you should be able to install by running:
-# if (!require("BiocManager", quietly = TRUE))
-# install.packages("BiocManager")
-# BiocManager::install("ggtree")
-
-#devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
-pacman::p_load(here, tidyverse, metafor,ggpubr,orchaRd,ggpubfigs) #Packages needed
+ if (!require("BiocManager", quietly = TRUE))
+ install.packages("BiocManager")
+ BiocManager::install("ggtree")
+
+if (!require("orchaRd", quietly = TRUE))
+devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
+
+pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs)
+
+#Packages needed
+
 rm(list=ls()) ## cleaning up
+
 set.seed(430) #set seed for reproducibility (for random number generation)
-# Loading cleaned dataset
-dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
 
@@
 }
+
+# ------------------------------------------------------------
+# Loading cleaned dataset
+# ------------------------------------------------------------
+
+dataset_analysis<-read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))
+
+dataset_lnRR<-read_csv(here::here("data/04_data_analysis/dataset_lnRR.csv"))
+
+dataset_SMDH<-read_csv(here::here("data/04_data_analysis/dataset_SMDH.csv"))
+
 ```
@@
 # load packages
+
 pacman::p_load(rotl,
@@
                ggtree)
-# Doesn't matter if I take dataset_lnRR or dataset_SMDH
+
+# We have 7 bird species in the dataset
 bird_species <- unique(dataset_analysis$bird_species)
@@
 taxa
+
 # check approximate matches
 taxa[taxa$approximate_match==TRUE & !(is.na(taxa$approximate_match)),]
+
 # phylogenetic information for our species from the Open Tree of Life
+
 tree <- rotl::tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")
 ape::is.binary(tree)
+
 # here are the species included in the tree
@@
   select(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded)%>%
-  mutate(across(c(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded), as.character)) %>%
+  mutate(across(c(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded), as.factor)) %>%
   make_long(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded)
@@
   select(paper_ID, bird_species, population_ID)%>%
-  mutate(across(c(paper_ID, bird_species, population_ID), as.character)) %>%
+  mutate(across(c(paper_ID, bird_species, population_ID), as.factor)) %>%
   make_long(paper_ID, bird_species, population_ID)
@@
 
+```{r}
+# Let's just quickly ensure all the important variables are 
+# in the correct data type
+
+dataset_analysis<- dataset_analysis%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID,bird_species), as.factor))
+
+dataset_lnRR<- dataset_lnRR%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID, bird_species), as.factor))
+
+dataset_SMDH<- dataset_SMDH%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID,bird_species), as.factor))
+
+```
+
 ```{r seperating datasets for analysis}
 
-## For lnRR
+## For lnRR (or simply load dataset as provided)
+# dataset_lnRR<-dataset_analysis%>%
+# filter(lnRR_sign != "NA" | lnRR_variance != "NA")
+
 # selecting dataset which are not flagged
-dataset_lnRR<-dataset_analysis%>%
-   filter(lnRR_sign != "NA" | lnRR_variance != "NA")%>%
+dataset_lnRR<-dataset_lnRR%>%
   filter(proxy_decision == "include")
@@
 
+# selecting only dataset that passes geary's test
+lnRR_geary_passed<-dataset_lnRR%>%filter(geary_test=="pass")
+
 ## For SMDH
@@
 
-```
-
-Exploring heterogeneity in intercept only model
-
-This is the function from Yefeng's Github for interpretting heterogeneity.
-I have to download the data used for this function to be able to use it.
-For now I am using the values from the table directly so I should just delete it later before finishing the code.
+# saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
+```
+
+#### Exploring heterogeneity in intercept only model
+
+This is the function from Yefeng's Github for interpreting heterogeneity. I have to download the data used for this function to be able to use it.
+
+I am using the values from the table directly..
 
@@
 
-## lnRR-heterogeneity
-
 Let us look at the heterogeneity in lnRR intercept-only model
@@
 sigma2_main_model_vector <- sum(intercept_lnRR$sigma2)
+
 # 0.11, 0.27, and 0.57 for lnRR
+
 I2_main_model_vector <- orchaRd::i2_ml(intercept_lnRR)
+
 # 0.88, 0.95, and 0.99 for lnRR
-CV_main_model_vector <- orchaRd::cvh1_ml(intercept_lnRR)
+
+CV2_main_model_vector <- orchaRd::cvh2_ml(intercept_lnRR)
+CV1_main_model_vector <- orchaRd::cvh1_ml(intercept_lnRR)
+
 # CVH2 (CVH1) - 1.36 (1.16), 3.76 (1.94), and 12.1 (3.48) for lnRR
-M_main_model_vector <- orchaRd::m1_ml(intercept_lnRR)
+
+M2_main_model_vector <- orchaRd::m2_ml(intercept_lnRR)
+M1_main_model_vector <- orchaRd::m1_ml(intercept_lnRR)
+
 # M2(M1) - 0.58 (0.54), 0.79 (0.66), and 0.78 for lnRR;
@@
 
-their sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
+The sampling variances will be fitted as variance--covariance matrices assuming a 0.5 correlation (ρs) between sampling variances from the same paper_ID (Noble et al. 2017).
 
@@
 # saving the model
-# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
 ```
@@
 # 0.88, 0.95, and 0.99 for lnRR
-CV_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
+CV2_main_model_vector <- orchaRd::cvh2_ml(intercept_SMDH)
+CV1_main_model_vector <- orchaRd::cvh1_ml(intercept_SMDH)
 # CVH2 (CVH1) - 1.36 (1.16), 3.76 (1.94), and 12.1 (3.48) for lnRR
-M_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)
+M2_main_model_vector <- orchaRd::m2_ml(intercept_SMDH)
+M1_main_model_vector <- orchaRd::m1_ml(intercept_SMDH)
 # M2 (M1) - 0.58 (0.54), 0.79 (0.66), and 0.78 for lnRR
@@
 
-saveRDS(Bivariate_model, file = here::here("sensitivity_analysis/bivariate_model.rds"))
+# Saving the model
+saveRDS(Bivariate_model, file = here::here("model/sensitivity_analysis/bivariate_model.rds"))
+# saving the dataset for this model
+write.csv(dataset_bivariate,here::here("data/05_data_sensitivity_analysis/dataset_bivariate.csv"))
 
@@
 
-### Sensitivity Analysis with published data only
-
-```{r}
+### With published data only
+
+```{r}
+
+#----------------------------------------------------------------------------
+# for lnRR as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_lnRR_published, file = here::here("sensitivity_analysis/SA_lnRR_published.rds"))
+# Saving the model
+saveRDS(SA_lnRR_published, file = here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
+# saving the dataset for this model
+write.csv(dataset_lnRR_published,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_published.csv"))
 
@@
 predict(SA_lnRR_published)
+
+#----------------------------------------------------------------------------
+# for SMDH as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_SMDH_published, file = here::here("sensitivity_analysis/SA_SMDH_published.rds"))
+# Saving the model
+saveRDS(SA_SMDH_published, file = here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))
+# saving the dataset for this model
+write.csv(dataset_SMDH_published,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_published.csv"))
 
@@
 
-### Sensitivity Analysis with flagged proxies
-
-```{r}
+### With flagged proxies
+
+Some traits for which the relationship with fitness is unclear or highly debated in the literature
+
+```{r}
+
+#----------------------------------------------------------------------------
+# for lnRR as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_lnRR_flagged, file = here::here("sensitivity_analysis/SA_lnRR_flagged.rds"))
+# Saving the model
+saveRDS(SA_lnRR_flagged, file = here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
+# saving the dataset for this model
+write.csv(lnRR_con_flagged,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_con_flagged.csv"))
 
@@
 
-## Now for SMDH
+#----------------------------------------------------------------------------
+# for SMDH as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_SMDH_flagged, file = here::here("sensitivity_analysis/SA_SMDH_flagged.rds"))
+# Saving the model
+saveRDS(SA_SMDH_flagged, file = here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))
+# saving the dataset for this model
+write.csv(SMDH_con_flagged,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_con_flagged.csv"))
 
@@
 
-### Sensitivity Analysis without 0 ES
-
-```{r}
+### Without 0 ES
+
+```{r}
+
+#----------------------------------------------------------------------------
+# for lnRR as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_lnRR_no_missingES, file = here::here("sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+# Saving the model
+saveRDS(SA_lnRR_no_missingES, file = here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+# saving the dataset for this model
+write.csv(lnRR_sin_missingES,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_sin_missingES.csv"))
 
@@
 
-## Now we do this for SMDH
+#----------------------------------------------------------------------------
+# for SMDH as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_SMDH_no_missingES, file = here::here("sensitivity_analysis/SA_SMDH_no_missingES.rds"))
+# Saving the model
+saveRDS(SA_SMDH_no_missingES, file = here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))
+# saving the dataset for this model
+write.csv(SMDH_sin_missingES,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_sin_missingES.csv"))
 
@@
 
-### Sensitivity Analysis with flagged proxies and no missing ES
-
-```{r}
+### With flagged proxies and no missing ES
+
+```{r}
+
+#----------------------------------------------------------------------------
+# for lnRR as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_lnRR_flagged_no_missingES, file = here::here("sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
+# Saving the model
+saveRDS(SA_lnRR_flagged_no_missingES, file = here::here("model/sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
+
+# saving the dataset for this model
+write.csv(lnRR_flagged_no_missingES,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_flagged_no_missingES.csv"))
 
@@
 
-## with SMDH
+#----------------------------------------------------------------------------
+# for SMDH as Effect Size
+#----------------------------------------------------------------------------
 
@@
 
-# saving the model
-saveRDS(SA_SMDH_flagged_no_missingES, file = here::here("sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
+# Saving the model
+saveRDS(SA_SMDH_flagged_no_missingES, file = here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
+
+# saving the dataset for this model
+write.csv(SMDH_flagged_no_missingES,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_flagged_no_missingES.csv"))
 
@@
 
-### Sensitivity analysis only using effect sizes calculated from means, SDs, and ns
+### No inferential stats for SMDH: effect sizes calculated from means, SDs, and sample size
 
@@
 ```{r}
+
+#----------------------------------------------------------------------------
+# for SMDH as Effect Size
+#----------------------------------------------------------------------------
+
 # Preparing new variance-covariance matrix
@@
 
-# saving the model
-saveRDS(SA_SMDH_no_inferential, file = here::here("sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+# Saving the model
+saveRDS(SA_SMDH_no_inferential, file = here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+
+# saving the dataset for this model
+write.csv(SMDH_no_inferential,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_inferential.csv"))
 
@@
 
-### Different values of sampling variance correlation
+### Exluding failed geary's test for lnRR
+
+```{r}
+#----------------------------------------------------------------------------
+# for  lnRR  as Effect Size
+#----------------------------------------------------------------------------
+
+VCV_lnRR_geary_passed <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = lnRR_geary_passed,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_geary_passed<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_geary_passed, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = lnRR_geary_passed)
+
+# Saving the model
+saveRDS(SA_lnRR_geary_passed, file = here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))
+
+# saving the dataset for this model
+write.csv(lnRR_geary_passed,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_geary_passed.csv"))
+
+```
+
+### Excluding the parasite and pathogen load fitness proxies
+
+It excludes all the fitness proxies relating to parasite and pathogen loads/ abundance etc.
+
+```{r}
+#----------------------------------------------------------------------------
+# for  lnRR  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_lnRR_no_para<-dataset_lnRR%>%filter(is.na(parasite_type))
+
+## The dataset is reduced to almost half
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_para)
+
+VCV_lnRR_no_para <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_para,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_para<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_para, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_para)
+
+# Saving the model
+saveRDS(SA_lnRR_no_para, file = here::here("model/sensitivity_analysis/SA_lnRR_no_para.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_no_para,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_para.csv"))
+
+#----------------------------------------------------------------------------
+# for  SMDH  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_SMDH_no_para<-dataset_SMDH%>%filter(is.na(parasite_type))
+
+## The dataset is reduced to almost half
+nrow(dataset_SMDH)-nrow(dataset_SMDH_no_para)
+
+VCV_SMDH_no_para <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_no_para,
+                  rho = 0.5) # assuming that the effect sizes within the same study are correlated with rho = 0.5
+
+SA_SMDH_no_para<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_para, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_no_para)
+
+# Saving the model
+saveRDS(SA_SMDH_no_para, file = here::here("model/sensitivity_analysis/SA_SMDH_no_para.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_no_para,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_para.csv"))
+
+```
+
+## Different values of sampling variance correlation
 
@@
 
-```{r}
+```{r hypothesis-model}
 lnRR_hypothesis <-
@@
                   data = dataset_lnRR)
-
+# Save model
 saveRDS(lnRR_hypothesis, file = here::here("model/lnRR_hypothesis.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/hypothesis_lnRR.csv"))
 
@@
 
+# Save model
 saveRDS(SMDH_hypothesis, file = here::here("model/SMDH_hypothesis.rds"))
-```
-
-# Exploratory Analysis
-
-For our exploratory analyses (see section Exploratory Analyses), we will run unimoderator multilevel meta-regressions using the following moderators:
-
-#### Type of parasites
+
+# saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/hypothesis_SMDH.csv"))
+```
+
+# Meta-regressions
+
+For understanding the heterogeneity in our intercept-only model, we will run unimoderator multilevel meta-regressions (see section Exploratory Analyses in pre-registration or manuscript) using the following moderators:
+
+## Type of experimental design
+
+(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).
+
+```{r}
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_lnRR_design <- dataset_lnRR %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design )
+
+# Saving the model
+saveRDS(lnRR_design, file = here::here("model/lnRR_design.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_design,here::here("data/04_data_analysis/design_lnRR.csv"))
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design <- dataset_SMDH %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design )
+
+# Saving the model
+saveRDS(SMDH_design, file = here::here("model/SMDH_design.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_design,here::here("data/04_data_analysis/design_SMDH.csv"))
+```
+
+Let me try to do a sensitivity analysis to see what happens when I remove the control condition of 3 in the overall model since that is expected to not have an effect according to the authors as well..
+i.e.
+it is a double control..
+
+### Excluding non-aromatic and blank comparison (i.e. the two control group comparison)
+
+```{r}
+
+## For the lnRR effect size...
+dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3)
+## Only some rows are removed... 
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp3)
+
+VCV_lnRR_no_comp3 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_comp3,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_comp3<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_comp3, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_comp3)
+
+# Saving the model
+saveRDS(SA_lnRR_no_comp3, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_no_comp3,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp3.csv"))
+
+#----------------------------------------------------------------------------
+# for  SMDH  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3)
+## Only some rows are removed... 
+nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp3)
+
+VCV_SMDH_no_comp3 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_no_comp3,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_SMDH_no_comp3<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_comp3, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_no_comp3)
+
+# Saving the model
+saveRDS(SA_SMDH_no_comp3, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_no_comp3,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp3.csv"))
+```
+
+Results remain practically the same irrespective..
+
+## Time of addition of green nest material
+
+(levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).
+
+```{r}
+## We use the complete dataset in this case
+lnRR_time_gnm_addition <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ - 1 + time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+## Saving the model
+saveRDS(lnRR_time_gnm_addition, file = here::here("model/lnRR_time_gnm_addition.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/time_gnm_lnRR.csv"))
+
+## Now similarly for the SMDH effect size using the complete dataset
+SMDH_time_gnm_addition <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ - 1 + time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+## Saving the model
+saveRDS(SMDH_time_gnm_addition, file = here::here("model/SMDH_time_gnm_addition.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/time_gnm_SMDH.csv"))
+```
+
+## Type of parasites
 
@@
 
-saveRDS( lnRR_parasite, file = here::here("model/lnRR_parasite.rds"))
+# Saving the model
+saveRDS(lnRR_parasite, file = here::here("model/lnRR_parasite.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_parasite,here::here("data/04_data_analysis/parasite_lnRR.csv"))
 
@@
 
+# Save the model
 saveRDS(SMDH_parasite, file = here::here("model/SMDH_parasite.rds"))
-```
-
-#### Time of addition of green nest material
-
-(levels: before egg hatching, after egg hatching, continuously throughout the nesting phase).
-
-```{r}
-## We use the complete dataset in this case
-lnRR_time_gnm_addition <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
-                    mods = ~ - 1 + time_of_gnm_addition,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_lnRR)
-
-saveRDS(lnRR_time_gnm_addition, file = here::here("model/lnRR_time_gnm_addition.rds"))
-
-## Now similarly for the SMDH effect size using the complete dataset
-SMDH_time_gnm_addition <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
-                    mods = ~ - 1 + time_of_gnm_addition,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_SMDH)
-
-saveRDS(SMDH_time_gnm_addition, file = here::here("model/SMDH_time_gnm_addition.rds"))
-```
-
-#### Type of experimental design
-
-(levels: 1 = non-aromatic vs. aromatic, 2 = no added material vs. aromatic, 3 = no added material vs. non-aromatic).
-
-```{r}
-# This analysis only includes dataset that has a proxy relating to comaparision type
-dataset_lnRR_design <- dataset_lnRR %>%
-  filter(!is.na(comparision_type))%>%
-  mutate(comparision_type= as.factor(comparision_type))
-
-VCV_lnRR_design <- vcalc(vi = lnRR_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_lnRR_design,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-lnRR_design <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR_design ,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + comparision_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_lnRR_design )
-
-saveRDS(lnRR_design, file = here::here("model/lnRR_design.rds"))
-
-# This analysis only includes dataset that has a proxy relating to comaparision type
-dataset_SMDH_design <- dataset_SMDH %>%
-  filter(!is.na(comparision_type))%>%
-  mutate(comparision_type= as.factor(comparision_type))
-
-VCV_SMDH_design <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH_design,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-SMDH_design <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_design ,# specify lnRR's sampling variance;
-                    mods = ~ - 1 + comparision_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_SMDH_design )
-
-saveRDS(SMDH_design, file = here::here("model/SMDH_design.rds"))
-```
-
-Let me try to do a sensitivity analysis to see what happens when I remove the control condition of 3 in the overall model since that is expected to not have an effect according to the authors as well..
-i.e.
-it is a double control..
-
-```{r}
-dataset_lnRR_remove3<-dataset_lnRR%>%filter(is.na(comparision_type) | comparision_type!="3")
-
-VCV_lnRR_remove3 <- vcalc(vi = lnRR_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_lnRR_remove3,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-lnRR_remove3 <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR_remove3 ,# specify lnRR's sampling variance;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_lnRR_remove3 )
-
-## Now for SMDH
-
-dataset_SMDH_remove3<-dataset_SMDH%>%filter(is.na(comparision_type) | comparision_type!="3")
-
-VCV_SMDH_remove3 <- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH_remove3,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-SMDH_remove3 <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_remove3 ,# specify lnRR's sampling variance;
-                    mods = ~ 1,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                  test = "t",
-                  control = list(optimizer="optim"),
-                  data = dataset_SMDH_remove3 )
-
-summary(SMDH_remove3)
-```
-
-Results remain practically the same irrespective..
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_parasite,here::here("data/04_data_analysis/parasite_SMDH.csv"))
+```
 
@@
 
+# Saving the model
 saveRDS(lnRR_birds, file = here::here("model/lnRR_birds.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/birds_lnRR.csv"))
 
@@
 
+# Saving the model
 saveRDS(SMDH_birds, file = here::here("model/SMDH_birds.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/birds_SMDH.csv"))
 ```
@@
 ```{r}
+
 lnRR_trait <-
@@
 
+# Saving the model
 saveRDS(lnRR_trait, file = here::here("model/lnRR_trait.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/trait_lnRR.csv"))
 
@@
 
+# Saving the model
 saveRDS(SMDH_trait, file = here::here("model/SMDH_trait.rds"))
-```
-
-# **Sensitivity analyses / robustness checks**
-
-We will run several sensitivity analyses using the same random effect structure as described above aimed at ensuring the robustness of our results.
-
-3.
-We will re-run our intercept-only multivariate meta-analysis (with both lnRR and SMDH as effect sizes) using 0.3 and 0.7 correlation (ρs) between sampling variances from the same paper_ID.
-If we find large differences in conclusions depending on ρs, we will run the corresponding sensitivity analyses for all our meta-regressions as well.
-
-4.
-If during our analyses we notice the need to run additional sensitivity analyses to ensure the robustness of our results, we will label those analyses as non-pre-registered and report them in the supplementary materials of the eventual manuscript.
-
-### Risk of Bias
+
+# Saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_lnRR.csv"))
+```
+
+# Risk of Bias
 
@@
 
-## Publication Bias
+# Publication Bias
 
@@
 ```{r}
-## For lnRR complete dataset
-VCV_lnRR_published<- vcalc(vi = lnRR_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_lnRR_published,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-all_in_lnRR <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ - 1 + time_of_gnm_addition + 
-                      year_MeanCenter + 
-                      sqrt_effective_n_inv + 
-                      comparision_type + 
-                      bird_species + 
-                      trait_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = dataset_lnRR_published)
-
-## For SMDH complete published dataset
-VCV_SMDH_published<- vcalc(vi = SMDH_variance,
-                  cluster = paper_ID,
-                  obs = Observation_ID,
-                  data = dataset_SMDH_published,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-all_in_SMDH<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-                    V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
-                    mods = ~ - 1 + time_of_gnm_addition + 
-                      year_MeanCenter + 
-                      sqrt_effective_n_inv + 
-                      comparision_type + 
-                      bird_species + 
-                      trait_type,
-                    random = list(~ 1 | paper_ID,
-                                  ~ 1 | Observation_ID,
-                                  ~ 1 | group_ID_coded,
-                                  ~ 1 | population_ID,
-                                  ~ 1 | bird_species),
-                    method = "REML",
-                    control = list(optimizer="optim"),
-                    test = "t",
-                    data = dataset_SMDH_published)
-```
+# ## For lnRR complete dataset
+# 
+# ## I am changing the year of unpublished studies to 2025 which is to now, assuming that if they were to be published now, what would be the effect.
+I will keep in mind that in this model if I do find an evidence of publication bias over years, I should keep in mind it is non-independent of the unpublished studies
+# 
+# dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+# 
+# VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
+#                   cluster = paper_ID,
+#                   obs = Observation_ID,
+#                   data = dataset_lnRR_all_in,
+#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+#                   )
+# 
+# lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+#                     V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
+#                     mods = ~ time_of_gnm_addition + 
+#                       year_MeanCenter + 
+#                       sqrt_effective_n_inv + 
+#                       as.factor(comparision_type) + 
+#                       bird_species + 
+#                       trait_type,
+#                     random = list(~ 1 | paper_ID,
+#                                   ~ 1 | Observation_ID,
+#                                   ~ 1 | group_ID_coded,
+#                                   ~ 1 | population_ID,
+#                                   ~ 1 | bird_species),
+#                     method = "REML",
+#                     control = list(optimizer="optim"),
+#                     test = "t",
+#                     data = dataset_lnRR_all_in)
+# 
+# 
+# 
+# ## For SMDH complete published dataset
+# 
+# dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
+# 
+# VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
+#                   cluster = paper_ID,
+#                   obs = Observation_ID,
+#                   data = dataset_SMDH_all_in,
+#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+#                   )
+# 
+# SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+#                     V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
+#                     mods = ~ time_of_gnm_addition + 
+#                       year_MeanCenter + 
+#                       sqrt_effective_n_inv + 
+#                       as.factor(comparision_type) + 
+#                       bird_species + 
+#                       trait_type,
+#                     random = list(~ 1 | paper_ID,
+#                                   ~ 1 | Observation_ID,
+#                                   ~ 1 | group_ID_coded,
+#                                   ~ 1 | population_ID,
+#                                   ~ 1 | bird_species),
+#                     method = "REML",
+#                     control = list(optimizer="optim"),
+#                     test = "t",
+#                     data = dataset_SMDH_all_in)
+```
+
+# Pair-wise comparison for meta-regression
+
+including including post-hoc Wald tests
+
+For this I have to run all the meta-regressions again without removing the intercepts, good luck to me!
+
+```{r}
+#----------------------------------------------------------------------------------
+# For Different hypothesis
+#----------------------------------------------------------------------------------
+
+# lnRR_hypothesis_pc <-
+#   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+#                     V = VCV_lnRR,# specify lnRR's sampling variance;
+#                     mods = ~ Hypothesis,
+#                     random = list(~ 1 | paper_ID,
+#                                   ~ 1 | Observation_ID,
+#                                   ~ 1 | group_ID_coded,
+#                                   ~ 1 | population_ID,
+#                                   ~ 1 | bird_species),
+#                     method = "REML",
+#                   test = "t",
+#                   control = list(optimizer="optim"),
+#                   data = dataset_lnRR)
+# 
+# # I now want to test for statistical differences between groups. Male and fem
+# # information for androgens can be obtained from the outcome of the table. For thyroid
+# # hormones I need to do Post-hoc Wald tests: 
+# car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
+```

### 2025-07-06 docs/code/08_figures-tables.Rmd
Results comments addressed (initial stage).. continue results and discussion

---
title: "Figures"
author: "Shreya D."
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ---- FIGURES ————–

# Visualising location and bird species

I am using the figure code from here and adapting it for my needs..

Mentesana, L., Hau, M., D'Amelio, P.B., Adreani, N.M. and Sánchez-Tójar, A. (2025), Do Egg Hormones Have Fitness Consequences in Wild Birds? A Systematic Review and Meta-Analysis. Ecology Letters, 28: e70100. <https://doi.org/10.1111/ele.70100>

Code here: `https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R`

```{r message=FALSE, warning=FALSE}
## Let's get the needed packages
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")

if (!requireNamespace("orchaRd", quietly = TRUE))
    devtools::install_github("daniel1noble/orchaRd", ref = "main")

pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot,maps)

## Let's first get the data in for this plot

# Loading cleaned dataset
dataset_analysis<- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))

```

```{r location-map}

# To split population_ID into location and country
dataset_analysis[c('Location','Country')] <- str_split_fixed(dataset_analysis$population_ID, ',', 2)

### For the purpose of this map, I am adding the the longitude and latitude of the study area manually. They exist in the dataset_analysis$population_location as they were extracted from the paper. I have also added some by just searching the general location since the coordinates were not provided for these..

data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
                             Lat_Location=c(51.50,38.41,40.45,
                                            45.40,52.39, 37.18,
                                            54,39.05,
                                            51.57,48,42.54,39.95,
                                            40.13,28.10,52.06,60.39),
                             Long_Location=c(19.29,-9.02,-3.50,
                                             -64.10,6.05,-3.11,
                                             -124,-76.81,
                                             -2.26,11,8.91,-75.16,
                                             -8.27,107.10,8.25,5.32))

## Let's now merge the datasets by the location names

dataset_analysis <- dataset_analysis %>%
  left_join(data_coordinates, by = "Location")

## Count how many times each Location appears in the full dataset
location_counts <- dataset_analysis %>%
  group_by(Location) %>%
  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')

# I will subset the data base so that I get one row per Location AND bird_species.
# Like this, I get one point per location independently of the number of effect sizes 
# we have per place.
dataset_analysis_unique_rows <- dataset_analysis %>%
  distinct(Location, bird_species, .keep_all = TRUE)

# Merge the counts into the unique rows dataset
dataset_analysis_unique_rows <- dataset_analysis_unique_rows %>%
  left_join(location_counts, by = "Location")

# create data for world coordinates using  
# map_data() function 
world_coordinates <- map_data("world")

# create world map using ggplot() function 
# geom_map() function takes world coordinates as input to plot world map 
fig_map <- ggplot(world_coordinates, aes(x = long, y = lat)) + 
  geom_map(map = world_coordinates, 
    aes(map_id = region), 
    color = "white", fill= "#D9EAF7") + 
  geom_point(data = dataset_analysis_unique_rows, 
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour=bird_species), alpha = 0.6) +
scale_size(range = c(3, 5)) +
  scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +

  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  guides(size = "none", alpha = "none") +
  labs(x = "Longitude",
       y = "Latitude",
       col = "Bird Species")+
  theme_classic() +
  theme(legend.position = c(0.99, 0.15),
        legend.justification = c("right", "bottom"),
        legend.background = element_rect(fill = "white", color = "black"),
        legend.text = element_text(size=6),
        axis.title = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank())

# To add the zoomed in map.. to show the points more clearly
zoom_map <- ggplot() + 
  geom_map(data = world_coordinates, map = world_coordinates,
           aes(map_id = region),
           color = "white", fill = "#D4D4D4") +
  geom_point(data = dataset_analysis_unique_rows,
             aes(x = Long_Location, y = Lat_Location,
                 size = size.freq, colour = bird_species),
             alpha = 0.6) +
  scale_size(range = c(1, 2)) +
  scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(color = "white", fill="white"),
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

geographic_distribution <- ggdraw() +
  draw_plot(fig_map) +
  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.52, height = 0.22) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))

ggsave(here::here("figures/Figure_Distribution.png"), plot = geographic_distribution, height = 100, width = 170, units= 'mm', dpi = 600)
```

# Visualizing author network

```{r}
# # Loading cleaned dataset
# dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
# 
# library(tidyverse)
# library(tidyr)
# library(igraph)
# installed.packages("ggraph")
# library(ggraph)
# 
# clean_author <- function(name) {
#   name %>%
#     str_replace_all(",", "") %>%   # remove commas
#     str_squish() %>%              # remove excess whitespace
#     str_to_title()                # standardize case (optional, if needed)
# }
# 
# # Apply cleaning to first and last author fields
# author_roles <- dataset_analysis %>%
#   distinct(paper_ID, .keep_all = TRUE) %>%
#   select(paper_ID, authors, bird_species) %>%
#   mutate(
#     author_list = str_split(authors, ";\\s*"),
#     first_author = map_chr(author_list, 1),
#     last_author = map_chr(author_list, ~ tail(.x, 1))
#   )%>%
#   mutate(
#     first_author=case_when(
#       first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
#       first_author == "Soler J J" ~ "Soler J. J.",
#       first_author == "Glądalski, M" ~ "Gladalski M.",
#       first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
#       TRUE ~ as.character(first_author)
#     ))%>%
#   mutate(
#     last_author=case_when(
#       last_author == "Veiga J P" ~ "Veiga J. P.",
#       TRUE ~ as.character(last_author)
#     )
#   )
# 
# # 2. Create Core Author Pairs (First → Last)
# author_pairs_core <- author_roles %>%
#   select(paper_ID, first_author, last_author) %>%
#   rename(from = first_author, to = last_author) %>%
#   filter(from != to) %>%
#   count(from, to, name = "weight")
# 
# # 3. Build Author Graph
# author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)
# 
# # 4. Assign Dominant Bird Species to PIs (last authors)
# author_species <- author_roles %>%
#   select(last_author, bird_species) %>%
#   group_by(last_author, bird_species) %>%
#   count() %>%
#   slice_max(n, n = 1) %>%
#   distinct(last_author, .keep_all = TRUE)
# 
# # Add species as vertex attribute
# V(author_graph)$bird_species <- author_species$bird_species[
#   match(V(author_graph)$name, author_species$last_author)
# ]
# 
# # 5. Optional: Scale node size by number of papers per author
# author_paper_counts <- author_roles %>%
#   pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
#   count(author, name = "paper_count")
# 
# # Add paper count attribute
# V(author_graph)$paper_count <- author_paper_counts$paper_count[
#   match(V(author_graph)$name, author_paper_counts$author)
# ]
# 
# # Replace NAs with small size for isolated authors
# V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1
# 
# # 6. Plot with ggraph
# ggraph(author_graph, layout = "fr") +
#   geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
#   geom_node_point(aes(color = bird_species, size = paper_count)) +
#   geom_node_text(aes(label = name), repel = TRUE, size = 3) +
#   scale_edge_width(range = c(0.3, 2)) +
#   scale_size(range = c(3, 10)) +
#   theme_void() +
#   labs(title = "Author Collaboration Network by Bird Species",
#        size = "Paper Count") +
#   theme(legend.position = "right")
#

```

# Intercept only model

Orchard plot for overall effect of green nest material on fitness using lnRR and SMDH

```{r orchard plot for intercept only models}
pacman::p_load(here,tidyverse,metafor,orchaRd,patchwork,cowplot)

# Loading models for SMDH and lnRR

intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))

# Plot for lnRR
intercept_lnRR_plot <- orchaRd::orchard_plot(intercept_lnRR,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Log Response Ratio- lnRR)",
                                    fill = T) +
   scale_fill_manual(values = "#98C127") +
   scale_colour_manual(values = "#98C127" ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Plot for SMDH
intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
                                    mod = "1",
                                    group = "paper_ID",
                                    trunk.size = 0.25,
                                    branch.size = 2,
                                    twig.size = 0.5,
                                    alpha = 0.2,
                                    xlab = "Effect size (Standardized Mean Difference- SMD(H))",
                                    fill = TRUE) +
  scale_fill_manual(values = "#F47A00") +
  scale_colour_manual(values = "#F47A00") +
  theme_minimal(base_size = 14) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
    legend.position = c(0.98, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_blank()
  ) +
  labs(x = "Intercept")

# Combine using patchwork
Figure_intercept <- intercept_lnRR_plot / intercept_SMDH_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
```

# Hypothesis meta-regression

```{r orchard plot hypothesis meta-regression}

# Loading models for SMDH and lnRR

lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))

# Plot lnRR meta-regression on hypothesis

lnRR_hypothesis_plot <-
  orchard_plot(mod_results(lnRR_hypothesis,
                           mod = "Hypothesis",
                           group = "paper_ID"),
               trunk.size = 0.25,
               branch.size = 1,
               twig.size = 0.5,
               alpha = 0.4,
               xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
  theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.01, hjust = 0.5)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

# Plot SMDH meta-regression on hypothesis

SMDH_hypothesis_plot <-
  orchard_plot(
    mod_results(
      SMDH_hypothesis,
      mod = "Hypothesis",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.4,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.05),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 90, vjust = 0.8, hjust = 1)
  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))

SMDH_hypothesis_plot <- SMDH_hypothesis_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_hypothesis <- lnRR_hypothesis_plot + SMDH_hypothesis_plot +
  plot_annotation(tag_level = c("A","B"))

ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
```

# Other meta-regressions

# A. Combined Plot

## Time of green nest material addition

```{r orchard plot time of gnm addition meta-regression}

# Loading models for SMDH and lnRR

lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))

lnRR_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      lnRR_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("After egg laying", "Before egg laying", "Continous addition"))

SMDH_time_gnm_addition_plot <-
  orchard_plot(mod_results(
      SMDH_time_gnm_addition,
      mod = "time_of_gnm_addition",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "bottom",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

## Experimental Design

```{r orchard plot experimental design meta-regression}

# Loading models for SMDH and lnRR

lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

```

### Now we combine these plots

```{r combining meta-regression plots, effect}

## I am going to remove the y ticks from the SMDH plots to make it smaller..
SMDH_design_plot <- SMDH_design_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 240, width = 250, units = "mm", dpi = 600)

```

# B. Combined Plot

## Parasite Type

```{r orchard plot parasite type meta-regression}

# Loading models for SMDH and lnRR

lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

lnRR_parasite_plot <-
  orchard_plot(mod_results(
      lnRR_parasite,
      mod = "parasite_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_parasite_plot <-
  orchard_plot(mod_results(
      SMDH_parasite,
      mod = "parasite_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
  )

```

## Bird Species

```{r orchard plot bird species meta-regression}

# Loading models for SMDH and lnRR

lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))

lnRR_birds_plot <-
  orchard_plot(mod_results(
      lnRR_birds,
      mod = "bird_species",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_birds_plot <-
  orchard_plot(mod_results(
      SMDH_birds,
      mod = "bird_species",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
  )
```

## Trait studied

```{r orchard plot trait-studied meta-regression}

# Loading models for SMDH and lnRR

lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))

lnRR_trait_plot <-
  orchard_plot(mod_results(
      lnRR_trait,
      mod = "trait_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
  )

SMDH_trait_plot <-
  orchard_plot(mod_results(
      SMDH_trait,
      mod = "trait_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0), 
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size =6, angle = 0, vjust = 0.5, hjust = 1)
  )
```

### Now we combine these plot

```{r combining meta-regression plots, no effect}

## I am going to remove the y ticks from the SMDH plots to make it smaller..
SMDH_parasite_plot <- SMDH_parasite_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_birds_plot <- SMDH_birds_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_trait_plot <- SMDH_trait_plot +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_parasite_birds_trait <- ((lnRR_parasite_plot + SMDH_parasite_plot) / 
                                  (lnRR_birds_plot + SMDH_birds_plot) / 
                                  (lnRR_trait_plot + SMDH_trait_plot)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_parasite_birds_trait.png"), plot = Figure_parasite_birds_trait, height = 250, width = 400, units = "mm", dpi = 600)

```

# Publication Bias Tests

```{r}

###---Small study Effects ----###

lnRR_small_study<-readRDS(here::here("model/lnRR_small_study.rds"))
SMDH_small_study<-readRDS(here::here("model/SMDH_small_study.rds"))

lnRR_small_study_bubble<-orchaRd::bubble_plot(mod_results(lnRR_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  labs(y = "Effect size (lnRR)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_small_study_bubble<-orchaRd::bubble_plot(mod_results(SMDH_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  labs(y = "Effect size (SMDH)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

###---Decline Effects ----###

lnRR_decline_eff<-readRDS(here::here("model/lnRR_decline_eff.rds"))
SMDH_decline_eff<-readRDS(here::here("model/SMDH_decline_eff.rds"))

lnRR_decline_eff_bubble<-orchaRd::bubble_plot(mod_results(lnRR_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  labs(y = "Effect size (lnRR)",
       x = "Publication Year (Mean Cenetered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_decline_effect_bubble<-orchaRd::bubble_plot(mod_results(SMDH_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  labs(y = "Effect size (SMDH)",
       x = "Publication Year (Mean Cenetered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

# Combine using patchwork
Figure_publication_bias <- ((lnRR_small_study_bubble + SMDH_small_study_bubble) /
                               (lnRR_decline_eff_bubble + SMDH_decline_effect_bubble)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_publication_bias.png"), plot = Figure_publication_bias, height = 300, width = 400, units = "mm", dpi = 600)
```

# -------- TABLES ———-

## Table: Sensitivity analysis for intercept only model

```{r}
#| label: SA_intercept_only_table

pacman::p_load(gt,dplyr,metafor)

# Loading the models including flagged proxies
SA_lnRR_flagged<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
SA_SMDH_flagged<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))

# Loading the models without data for those using 0 as ES because authors reported no effect
SA_lnRR_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
SA_SMDH_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))

# Loading the models without data for those using 0 as ES because authors reported no effect and including flagged proxies
SA_lnRR_flagged_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
SA_SMDH_flagged_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))

# Loading the model for SMDH without inferential statistics. There is none for lnRR because we can only uses means and deviation to estimate lnRR
SA_SMDH_no_inferential<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))

# Now let's build the table

SA_intercept_only <- tibble::tibble(
  effect_size = c("lnRR","lnRR","lnRR","SMDH","SMDH","SMDH","SMDH"),
  data_used = c("Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),

  Estimate = c(SA_lnRR_flagged$b[1],
               SA_lnRR_no_missingES$b[1],
               SA_lnRR_flagged_no_missingES$b[1],
               SA_SMDH_flagged$b[1],
               SA_SMDH_no_missingES$b[1],
               SA_SMDH_flagged_no_missingES$b[1],
               SA_SMDH_no_inferential$b[1]),

  CI_Lower = c(SA_lnRR_flagged$ci.lb,
               SA_lnRR_no_missingES$ci.lb,
               SA_lnRR_flagged_no_missingES$ci.lb,
               SA_SMDH_flagged$ci.lb,
               SA_SMDH_no_missingES$ci.lb,
               SA_SMDH_flagged_no_missingES$ci.lb,
               SA_SMDH_no_inferential$ci.lb),

  CI_Upper = c(SA_lnRR_flagged$ci.ub,
               SA_lnRR_no_missingES$ci.ub,
               SA_lnRR_flagged_no_missingES$ci.ub,
               SA_SMDH_flagged$ci.ub,
               SA_SMDH_no_missingES$ci.ub,
               SA_SMDH_flagged_no_missingES$ci.ub,
               SA_SMDH_no_inferential$ci.ub),

  PI_Lower = c(predict(SA_lnRR_flagged)$pi.lb,
               predict(SA_lnRR_no_missingES)$pi.lb,
               predict(SA_lnRR_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged)$pi.lb,
               predict(SA_SMDH_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_no_inferential)$pi.lb),

  PI_Upper = c(predict(SA_lnRR_flagged)$pi.ub,
               predict(SA_lnRR_no_missingES)$pi.ub,
               predict(SA_lnRR_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged)$pi.ub,
               predict(SA_SMDH_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_no_inferential)$pi.ub),

  P_value = c(SA_lnRR_flagged$pval,
              SA_lnRR_no_missingES$pval,
              SA_lnRR_flagged_no_missingES$pval,
              SA_SMDH_flagged$pval,
              SA_SMDH_no_missingES$pval,
              SA_SMDH_flagged_no_missingES$pval,
              SA_SMDH_no_inferential$pval),

  Q_value = c(SA_lnRR_flagged$QE,
              SA_lnRR_no_missingES$QE,
              SA_lnRR_flagged_no_missingES$QE,
              SA_SMDH_flagged$QE,
              SA_SMDH_no_missingES$QE,
              SA_SMDH_flagged_no_missingES$QE,
              SA_SMDH_no_inferential$QE),

  k_effect_sizes = c(SA_lnRR_flagged$k,
        SA_lnRR_no_missingES$k,
        SA_lnRR_flagged_no_missingES$k,
        SA_SMDH_flagged$k,
        SA_SMDH_no_missingES$k,
        SA_SMDH_flagged_no_missingES$k,
        SA_SMDH_no_inferential$k),

  n_studies = c(length(SA_lnRR_flagged$s.levels.f[[1]]),
                      length(SA_lnRR_no_missingES$s.levels.f[[1]]),
                      length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged$s.levels.f[[1]]),
                      length(SA_SMDH_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_no_inferential$s.levels.f[[1]])
))

# Combine CI and PI into a single column each for compactness
SA_intercept_only <- SA_intercept_only %>%
  mutate(
    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
    P_value = scales::pvalue(P_value),
    Q_value = sprintf("%.2f", Q_value)
  ) %>%
  select(
    effect_size,
    data_used,
    Estimate,
    CI,
    PI,
    P_value,
    Q_value,
    k_effect_sizes,
    n_studies
  )

# Let's make this table pretty
SA_intercept_only<-SA_intercept_only%>%
  gt()%>%
  tab_options(
    table.font.size = px(12),
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    heading.title.font.size = px(14),
    heading.subtitle.font.size = px(12),
    column_labels.font.weight = "bold"
  ) %>%
  tab_header(
    title = md("**Summary of Sensitivity Analyses for lnRR and SMDH Intercept-only models**")
  ) %>%
  cols_label(
    effect_size = "Effect Size",
    data_used = "Data used in model",
    Estimate = "Estimate",
    CI = "95% CI",
    PI = "95% PI",
    P_value = "P-value",
    Q_value = "Q value",
    k_effect_sizes = "k (No. of Effect Sizes)",
    n_studies = "n (No. of Studies)"
  ) %>%
  fmt_number(
    columns = c(Estimate),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 14,
    table.border.top.width = px(2),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  opt_table_outline()

#saving as a docx file
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
```

## Table: Output from meta-regressions

```{r}

pacman::p_load(gt, tidyverse, metafor, purrr, stringr)

# Loading models for experimental design
lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

# Loading models for parasite type
lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

# Loading models for time of green nest material addition
lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))

# Loading models for the type of trait studied
lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))

# Loading models for the bird species studied
lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
```

```{r}

# Let's source our custom function to extract values from the meta-regressions
source(here::here("functions/extractor_metareg.R"))

## For lnRR Values
lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type")%>%
  bind_rows(extractor_metareg(lnRR_birds,"bird_species"))%>%
  bind_rows(extractor_metareg(lnRR_trait,"trait_type"))%>%
  bind_rows(extractor_metareg(lnRR_design,"comparision_type"))%>%
  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition"))%>%
  mutate(effect_size = "lnRR")

## For SMDH Values
SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type")%>%
  bind_rows(extractor_metareg(SMDH_birds,"bird_species"))%>%
  bind_rows(extractor_metareg(SMDH_trait,"trait_type"))%>%
  bind_rows(extractor_metareg(SMDH_design,"comparision_type"))%>%
  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition"))%>%
  mutate(effect_size = "SMDH")

## Now let's write the table for publication:
# Combine both results
combined_results <- bind_rows(lnRR_results, SMDH_results)%>%
  pivot_wider(
    id_cols = c(moderator, level),
    names_from = effect_size,
    values_from = c(estimate, p_value, CI, PI, k, n),
    names_glue = "{.value}_{effect_size}"
  )%>% # Prepare row labels to mimic grouping
  arrange(moderator, level)%>%
  mutate(row_type = "level")

# Create moderator header rows for heterogeneity metrics
  moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
  select(moderator, effect_size, Q, Q_pval, R2_marginal) %>%
    distinct()%>%
    pivot_wider(
      names_from = effect_size,
      values_from = c(Q, Q_pval, R2_marginal),
      names_glue = "{.value}_{effect_size}"
    )%>%
  mutate(level = "Heterogeneity ",
         row_type = "moderator")

# Final combined table with headers and levels
combined_results <- bind_rows(moderator_header, combined_results) %>%
  arrange(moderator, row_type)%>% select(-row_type)%>%
  relocate(level, .after = moderator)%>%
  mutate(moderator=case_when(moderator=="parasite_type"~"Parasite Type",
                             moderator=="bird_species"~"Bird Species",
                             moderator=="trait_type"~"Trait Type Category",
                             moderator=="comparision_type"~"Experimental Design",
                             moderator=="time_of_gnm_addition"~"Time of Green Nest Material Addition"))%>%
  mutate(level = case_when(level==1 ~ "Non-aromatic vs. Aromatic",
                           level==2 ~ "No added material vs. Aromatic",
                           level==3 ~ "No added material vs. Non-aromatic",
                           level=="a" ~ "After egg hatching",
                           level=="b" ~ "Before egg hatching",
                           level=="c" ~ "Continously through nesting phase",
                           level=="Parasitic_and_pathogenic"~"Parasitic and Pathogen Related", .default=level))

# Optional: clean up or reorder columns for display
# Select and order columns for clarity
MLMR_table <- combined_results %>%
  gt(groupname_col = "moderator") %>%
  tab_header(title = md("**Multilevel Meta-analytic Models for Exploratory Analyses**")) %>%
  cols_label(
    Q_lnRR = "Q",
    Q_pval_lnRR = "Q p-val",
    R2_marginal_lnRR = "R²_mar",
    Q_SMDH = "Q",
    Q_pval_SMDH = "Q p-val",
    R2_marginal_SMDH = "R²_mar",
    level = "Level",
    estimate_lnRR = "Estimate",
    CI_lnRR = "95% CI",
    PI_lnRR = "95% PI",
    p_value_lnRR = "P-val",
    k_lnRR = "k",
    n_lnRR = "n",
    estimate_SMDH = "Estimate",
    CI_SMDH = "95% CI",
    PI_SMDH = "95% PI",
    p_value_SMDH = "P-val",
    k_SMDH = "k",
    n_SMDH = "n"
  ) %>%
   sub_missing(
    columns = everything(),
    missing_text = ""
  ) %>%
  opt_table_outline() %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 12,
    table.border.top.width = px(2),
    column_labels.font.weight = "medium",
    row_group.font.weight = "bold"
  )   %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      rows = level == "Heterogeneity"
    ))%>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_lnRR),
      rows = p_value_lnRR < 0.05
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_SMDH),
      rows = p_value_SMDH < 0.05
    )
  )%>%
  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
  tab_spanner(label = "SMDH", columns = contains("_SMDH"))

#saving as a docx file
gtsave(MLMR_table,here::here("tables/EA_MLMR_table.docx"))
gtsave(MLMR_table,here::here("tables/EA_MLMR_table.html"))
```

### 2025-07-06 docs/manuscript_GNM.qmd
Results comments addressed (initial stage).. continue results and discussion

--- 2025-05-11 docs/manuscript_GNM.qmd
@@
 
+# Abstract
+
+According to PRISMA Checklist.. I must:
+
+-   Summarise the aims and scope of the review
+
+-   Describe the data set
+
+-   State the results of the primary outcome
+
+-   State conclusions
+
+-   State limitations
+
+# Introduction
+
+Nest and nest-building are fundamental across a diverse range of animals, including insects (e.g., termites, spiders), mammals (e.g., platypus, rodents), and perhaps more famously, birds.
+Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@mainwaring2014; @deeming2023; @hansell2000].
+While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@suárez-rodríguez2013; @sergio2011; @sheard2024].
+These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in many bird species [@moreno1994; @hoi1996], even across species [@soler1995].
+Nest-building behaviour is increasingly recognized as an expression of the extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
+Yet, despite hundreds of scientific articles studying nests and nesting behaviour in birds being published each year, much remains unknown.
+
+An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
+This green nest material (GNM) ---leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species keep adding it even after the nest is finished.
+Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+Collecting and constantly replenishing GNM requires extra foraging flights, sometimes even outside the territory [@mennerat2009].
+The costs associated with nest building [@mainwaring2013], and these additional efforts suggest that GNM is unlikely to be gathered opportunistically and suggests a possible adaptive significance.
+
+Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
+First, the courtship hypothesis suggests that mostly males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
+This hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
+Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
+The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+
+Second, and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence [@wimberger1984].
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
+Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
+The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
+Thus, while both hypotheses suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
+
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic properties have been proposed.
+These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], or simply fulfilling a structural function [@lyons1987].
+However, these alternative functional roles have received little support or attention.
+In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
+Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and potentially far-reaching in its implications.
+
+To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e.
+combining both the nest protection and drug hypotheses due to their non-exclusivity).
+In addition, we explore the observed context-dependency (i.e., high heterogeneity among effect sizes) via meta-regressions.
+Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
+microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design (aromatic vs.
+non-aromatic vs.
+no added material), the focal species, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
+Our meta-analysis of experimental studies is the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
+
 ```{r Setup, include=FALSE, echo=FALSE}
 devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
-pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
+pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork,english)
 source(here::here("functions/extractor_metareg.R"))
 ```
+
+# Methods
+
+## Registration and Reporting
+
+We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+The pre-registration details our objectives, a priori hypotheses and predictions, methods and planned data analyses.
+Unless stated otherwise, we adhered to the registered protocol.
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist and @figsupp-prisma-flow).
+All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
+
+## Information source and search
 
@@
 # Systematic search and abstract screening
-unique_reference_list <- read_csv("data/unique_reference_list.csv")
-full_reference_before_deduplication<-read_csv("data/full_reference_before_deduplication.csv")
-selected_abstract_screening<-read_csv("data/selected_abstract_screening.csv")
+unique_reference_list <- read_csv("data/01_systematic_search/02_reference_data/unique_reference_list.csv")
+full_reference_before_deduplication<-read_csv("data/01_systematic_search/02_reference_data/full_reference_before_deduplication.csv")
+selected_abstract_screening<-read_csv("data/01_systematic_search/03_title_and_abstract_screening/selected_abstract_screening.csv")
 
 # For updated search
-unique_reference_list_repeat <- read_csv("data/unique_reference_repeat_12082024.csv")
-full_reference_before_deduplication_repeat<-read_csv("data/full_reference_repeat_12082024.csv")
-selected_abstract_screening_repeat<-read_csv("data/selected_abstract_screening_repeat.csv")
+unique_reference_list_repeat <- read_csv("data/01_systematic_search/04_search_repeat_12082024/unique_reference_repeat_12082024.csv")
+full_reference_before_deduplication_repeat<-read_csv("data/01_systematic_search/04_search_repeat_12082024/full_reference_repeat_12082024.csv")
+selected_abstract_screening_repeat<-read_csv("data/01_systematic_search/04_search_repeat_12082024/selected_abstract_screening_repeat.csv")
 
 # For fulltext screening
-excluded_fulltext <- read_csv("data/excluded_fulltext.csv")
+excluded_fulltext <- read_csv("data/01_systematic_search/03_title_and_abstract_screening/excluded_fulltext.csv")
 ```
 
-# Methods
-
-## Registration and Reporting
-
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
-The pre-registration details the study's objectives, a priori hypotheses and predictions, methods and planned data analyses.
-Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist).
-All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
-
-## Information source and search
-
-We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022.
-The keyword search query was designed as a three-block query to included terms related to the predictor/treatment (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), our population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit it to only experimental studies only ("experiment\*" OR "manipulat\*").
+We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022 (see update below).
+The keyword search query was designed as a three-block query to include terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
@@
 
-All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree (@figsupp-decision-tree).
-We included all studies on birds that experimentally manipulated the green nest material (both aromatics or herbs).
-`{r} nrow(selected_abstract_screening)` articles passed the title-and-abstract screening and were further evaluated during the full-text screening.
-Each article was screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
-We used the same criteria as above (see @figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
-`{r} nrow(excluded_fulltext)` articles were excluded.
+All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
+We included all studies on birds that experimentally manipulated the GNM (both aromatics or herbs).
+`{r} tools::toTitleCase(as.character(english::english(nrow(selected_abstract_screening))))` articles passed the title-and-abstract screening and were further evaluated during the full-text screening, where each article was independently screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
+We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
+`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` passed the full-text screening and were, thus, eligible for our meta-analysis.
 All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
 
-To update our systematic lietrature search, we repeated our search on 12.08.2024.
-This updated search found `{r} nrow(unique_reference_list_repeat)` unique articles after removing ``` {r} nrow(full_reference_before_deduplication_repeat)-``nrow(unique_reference_list_repeat) ``` duplicates.
-Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article.
-Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles.
-In all, X <!--# Fill the no.
-of articles that are included --> articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
+We updated our systematic literature search by repeating our search on 12.08.2024.
+We found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
+Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before (@figsupp-decision-tree), and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article for our meta-analysis.
+Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles through other sources (i.e., identified through a poster by a collaborator and through an independent recommendation by a colleague).
+In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
 
@@
 The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
-We extracted the primary data (i.e., measures of central tendency, variance and sample size) from text whenever possible.
-In cases where primary data was only available in figures (e.g., boxplots), we used `metaDigitise` v.1.0.1 (@pick2018).
-If primary data was not available, we extracted any inferential statistics (t value, F value) that could be transformed into an effect size.
-In cases where the values could not be extracted from the article but datasets were provided, we calculated the means, SD and sample sizes from the provided raw data.
-When data was presented in different sources (e.g.
-in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).
-
-To obtain missing data (e.g., non-reported results, missing sample sizes, etc.) and to locate grey literature (i.e.
-unpublished data), we wrote to the corresponding author of the articles that passed full-text screening using a standardized email template (\@figsupp-email).
-We contacted four authors for missing data, while all corresponding authors were asked for any potential unpublished data that could be included in our meta-analysis.
-All four authors responded to our email but only two could provide the data as requested; one did not have the data any more and one did not give a conclusive response.
-In addition, one author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO) provided data for an unpublished study.
-In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
+We prioritised extracting the primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package `metaDigitise` v.1.0.1 (@pick2018).
+If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), that could be transformed into an effect size.
+Last, if the previous steps failed but the article has openly shared datasets (n = `{r} length(raw_data)`), we calculated the means, SD and sample sizes from them.
+**When data was presented in different sources (e.g.
+in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).**
 
@@
 Treatments consisted of aromatic materials added by authors, birds, or both.
-In cases comparing non-aromatic material to a blank nest, the non-aromatic material was considered the treatment.
+For cases that compared non-aromatic material to where authors did not add any additional nest material and any material added by the birds was removed, the non-aromatic material was considered the treatment.
 We recorded the type of comparison being made as a moderator.
+For each study, we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, or supplementary materials).
+We categorised the fitness proxies measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
+For studies testing whether GNM affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
+For a complete list of variables extracted see @figsupp-variables .
+We did not include some traits in all our analyses because it was unclear how they related to fitness (k = `{r} nrow(excluded_proxies)` , n = `{r} length(unique(excluded_proxies$paper_ID))`; see @figsupp-excluded-proxies for the list and reasons of exclusion).
 
-For each study we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and information about the extracted data (location or source of the data recorded).
-We categorized the fitness proxy measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load and phenology.
-For parasites or pathogens, we categorised them into arthropods or micro-organisms.
-For a complete list of variables extracted see @figsupp-variables .
-We did not include some traits in all our analyses becaause it was unclear how they related to fitness (k=`{r} nrow(excluded_proxies)` , n=`{r} length(unique(excluded_proxies$paper_ID))`;see @figsupp-excluded-proxies for the list and reason of exclusion).
-We also had to exclude some effect sizes (n=?, k=?) because of the low sample size per group (less than x).
+To obtain missing data (e.g., non-reported results, missing sample sizes, etc.), we contacted four authors.
+All four authors responded to our email, but only two provided the data as requested; one did not have the data any more, and one did not give a conclusive response.
+Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))`) to ask for any potential unpublished data that could be included in our meta-analysis.
+One corresponding author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO), provided data for another unpublished study.
+In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
+Author correspondance was performed using a standardised email template (@figsupp-email).
+In all, we extracted data for `{r} length(unique(published_studies$paper_ID))` published articles (k = `{r} nrow(published_studies)`) and `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`).
 
@@
 
-To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMDH.
+To estimate the effect of GNM addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
 Thus, throughout, we fitted two separate sets of model for each effect size.
@@
 We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k=`{r} nrow(SAonly_proxies)` , n=`{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly_proxies).
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g.
+sex ratio, testosterone levels, etc.), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
 For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
-
-<!--# You have to correct the numbers for contingency table. It does not include the one data point from unpublished results -->
 
@@
 
-To test the relative importance of the two main hypotheses suggested for green nest material: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
-For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators (@nakagawa2012).
+To test the relative importance of the two main hypotheses suggested for GNM: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
 
@@
 
+```{r}
+parasite_pathogen<-dataset_after_cleaning%>%filter(trait_type=="Parasitic_and_pathogenic")
+```
+
 We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
-To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (n=?, k=?).
+To understand the effect of GNM on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`).
 We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
-We also ran a meta-regression with with the entire dataset set using bird species as a moderator (levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris, Parus major, Passer cinnamomeus, Buteo buteo) to understand if the effect of green nest material on fitness depended on the system being studied.
-To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.
-We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
-We explored the impact of methodological differences on the relationship between green nest material and fitness.
+We also ran a meta-regression with the entire dataset set using bird species as a moderator (levels: *Buteo buteo*, *Cyanistes caeruleus*, *Passer cinnamomeus*, *Parus major*, *Sturnus unicolor*, *Sturnus vulgaris*, *Tachycineta bicolor*) to understand if the effect of GNM on fitness depended on the system being studied.
+To test the effect of time of addition of GNM on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with Time of addition of GNM as the moderator.
+We explored the effect of GNM on fitness depending on the type of trait studies (levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We explored the impact of methodological differences on the relationship between GNM and fitness.
 To understand the effect of type of experimental design (i.e.
@@
 We tested for evidence of publication bias, both small-study and decline effects following @nakagawa2021.
-Publication bias tests were performed for both lnRR and SMDH separately, and using the same random effect structure as reported above.
+Publication bias tests were performed for both lnRR and SMD(H) separately, and using the same random effect structure as reported above.
 To test for small-study effects, we ran a multilevel meta-regression, using the inverse of the effective sample size as a moderator.
@@
 
-We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations.
+We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@fig-distribution).
 About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
-Our dataset included two unpublished studies (k=XX effect sizes), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean (±SD) number of effect sizes per study was `{r} as.numeric(format(mean(ES_per_study$n), digit=3))` ± `{r} as.numeric(format(sd(ES_per_study$n), digit=2))`(range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean sample size per effect size were `{r} median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))` and `{r} as.numeric(format(mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)), digit=3))` respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
+Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
+The mean (±SD) number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean effective sample size (i.e.
+after accounting for shared-group non-independence) were `{r} sprintf("%.1f", median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))` and `{r} sprintf("%.1f",mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))`, respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
+
+![**Geographical distribution of the 16 study population in this meta-analysis:** Point size reflects the number of effect sizes coming from the location and colour denotes species (see legend), with an inset zooming on the cluster of distribution.](figures/Figure_Distribution.png){#fig-distribution}
 
@@
 intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
-bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
+bivariate_model<-readRDS(here::here("model/sensitivity_analysis/bivariate_model.rds"))
 ```
 
-Both lnRR and SMDH intercept-only multilevel meta-analyses showed an increase in fitness in the nests with an increase in green nest material compared to control nests; however, the overall effect was only statistically significant for SMDH.
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness in the nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
-The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH2~total~ = `{r} round(as.double(orchaRd::cvh2_ml(intercept_lnRR)[1]),2)` and M2~total =~ `{r} round(as.double(orchaRd::m2_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
-The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high.
-Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2024a; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
+First, the model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM \[@fig-mean-effect (A); lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high variability across effect sizes.
+Second, the model using SMD(H) showed a small positive and statistically significant effect of an experimental increase of GNM on fitness \[@fig-mean-effect (B); SMDH = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
+Total raw heterogeneity (𝜎^2^) was ``` {r}``sprintf("%.3f",sum(intercept_SMDH$sigma2)) ``` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+For lnRR, these heterogeneity metrics exceeded the 75th percentile benchmark (see @supp-tab-heterogeneity for detailed estimates of heterogeneity).
 
-While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
-These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
-The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
 As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
-While neither intercept was statistically significant, the results strengthens the interpretation that any effect of green nest material on fitness outcomes in likely to be very small at best \[lnRR = `{r} as.double(formatC(coef(bivariate_model)[1], digit = 3, format="f"))`, p-value = `{r} as.double(formatC(bivariate_model$pval[1], digits = 3, format = "f"))` and SMDH = `{r} as.double(formatC(coef(bivariate_model)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(bivariate_model$pval[2], digits = 3, format = "f"))`\].
+While neither intercept was statistically significant, the results strengthen the interpretation that any effect of GNM on fitness outcomes is likely small at best \[lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`\].
 
-![Overall effect of green nest material on fitness: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
-Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardized mean difference as effect sizes.
-k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect width="1059"}
+![**Overall effect of green nest material on all fitness proxies combined:** Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect}
 
-## **Hypotheses explaining the effect of green nest material**
+## **Mechanistic Hypotheses: explaining the effect of Green Nest Material**
 
@@
 
-Using the multilevel meta-regressions, we found no clear support for the proposed hypotheses in the literature ([@fig-hypothesis]).
-There is a small positive but non-significant effect of green nest material on fitness related to reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMDH~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
-We found even smaller, non-significant effect of green nest material on fitness related to protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ =`{r} summary_lnRR_hypothesis$estimate[3]`, CI: `{r} summary_lnRR_hypothesis$CI[3]`, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMDH~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
-In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either hypotheses, we found a small positive effect which was significant only in the case of SMDH \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMDH~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
-The moderator explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@fig-hypothesis]).
+There was a small positive but statistically non-significant average effect of GNM on fitness related to courtship efforts and investment (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
+The estimates were even smaller for the protective effect or health benefits for nestlings as proposed by the nest protection and drug hypothesis \[lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, CI: ``` {r}``summary_lnRR_hypothesis$CI[3] ```, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
+Our meta-regression contained a third category that included effect sizes that could not be clearly assigned to either hypothesis.
+We found a small positive effect which was statistically significant only in the case of SMD(H) \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
+The moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
 
@@
 log response ratio (lnRR) and B.
-Standardized mean difference (SMDH).
+Standardized mean difference (SMD(H)).
 Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
@@
 
-## Pre-registered exploratory analyses
+## What other factors explain heterogeneity among effect sizes?
 
@@
 
-The effect of green nest material on fitness varied largely by the experimental design.
-The experimental design comparison between no added material and aromatic material showed a positive and statistically significant effect on fitness \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\].
-The experimental design comparison between no added material and non-aromatic material showed a negative effect on fitness, which was significant in lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value = `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
-Contrary to our expectation, the non-aromatic and aromatic green nest material comparison showed small negative non-significant effect on fitness \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMDH~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
-Experimental design comparison type also explained a large proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
+Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several multilevel meta-regressions.
+First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design.
+The overall effect size for the comparison between no added material and aromatic material was positive and statistically significant \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, it was negative for the comparison between no added material and non-aromatic material statistically significantly so lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
+Last, the comparison between non-aromatic and aromatic material showed a small negative statistically non-significant effect \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMD(H)~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
+The moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
 
-When green nest material was added continuously throughout the nesting phase, the effect of it on fitness was positive and statistically significant in the case of SMDH \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMDH~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
-Addition after egg hatching showed a positive but non-significant effect on fitness and before egg hatching had a near zero non-significant effect [\@fig-MR](C-D); Table X\].
-Timing of addition of green nest material explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
+Second, when GNM was added continuously throughout the nesting phase, its overall effect was positive and statistically significant, at least for SMD(H) \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
+compared to its addition before or after egg hatching \[[\@fig-MR](C-D); Table X\].
+Timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
 
-![](figures/Figure_design_time_gnm_addition.png){#fig-MR}
+![Orchard plot showing overall effect of green nest material depending on the multilevel meta-regression for experimental design for - A.
+log response ratio (lnRR) and B.
+Standardized mean difference (SMD(H)) and time of GNM addition for - C.
+log response ratio (lnRR) and D.
+Standardized mean difference (SMD(H)).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_design_time_gnm_addition.png){#fig-MR}
 
-There is positive non-significant effect of increased green nest material on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
+Third, there is a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
 \[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
@@
 
-Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
-All confidence and prediction intervals overlapped zero.
+Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
 However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
 
-Among different types of fitness trait, only morphological trait showed positive effect of green nest material on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
+Among different types of fitness trait, only morphological trait showed positive effect of GNM on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
 Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
@@
 
-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\-\--
+# Discussion
 
-## Supplementary Appendix
+Summary of the results.. wrap up with a few points
+
+Second paragraph
+
+-   Discussing your results.. effect sizes
+
+-   Difference between the hypothesis, whether you can do it or not
+
+-   Experimental design difference.. importance of aromatic vs. Non-aromatic (are the same that aroma per say) and time of addition
+
+    Third paragraph :
+
+How much heterogeneity is explained..
+
+Limitations and issues about the data.. mechanism, publication bias.. species are few tested, few labs..
+
+Proxies that are closer..
+
+If study ID is
+
+Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased GNM, though the strength of these effects depended on the effect size metric used.
+SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of GNM---whether through sexual signalling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+
+The While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of GNM on fitness.
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+
+------------------------------------------------------------------------
+
+# Supplementary Appendix
 

### 2025-07-06 functions/extractor_metareg.R

@@ -11,7 +11,7 @@ extractor_metareg <- function(model, moderator_name) {
   mod.data <- model$data
   
   summ.k_n <-  mod.data %>%
-    group_by(level= as.character(mod.data[[moderator_name]])) %>%
+    group_by(level= as.character(.data[[moderator_name]])) %>%
     summarise(
       k = n(),  # effect sizes
       n = n_distinct(paper_ID),  # unique papers
@@ -113,12 +113,13 @@ extractor_metareg <- function(model, moderator_name) {
     mutate(
       pi_lower = format(round(pi.lb,3),nsmall=3),
       pi_upper = format(round(pi.ub,3),nsmall=3),
-      CI = paste0("[", ci_lower, ",",ci_upper, "]"),
-      PI = paste0("[", pi_lower, ",",pi_upper, "]"),
+      CI = paste0("[", ci_lower, ", ",ci_upper, "]"),
+      PI = paste0("[", pi_lower, ", ",pi_upper, "]"),
     )%>%
     select(moderator,level,estimate,p_value,CI,PI,k,n,Q,Q_pval,R2_marginal)%>%
     mutate(
-      Q_pval = if_else(Q_pval<0.001, "<0.001",as.character(Q_pval))
+      Q_pval = if_else(as.numeric(Q_pval) <0.001, "<0.001",as.character(Q_pval)),
+      p_value = if_else(as.numeric(p_value) <0.001, "<0.001",as.character(p_value))
     )
   
   

### 2025-07-08 docs/manuscript_GNM.qmd
Nothing much changed.. just pushing from desktop to now continue working from my laptop

@@
 Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high variability across effect sizes.
-Second, the model using SMD(H) showed a small positive and statistically significant effect of an experimental increase of GNM on fitness \[@fig-mean-effect (B); SMDH = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
-Total raw heterogeneity (𝜎^2^) was ``` {r}``sprintf("%.3f",sum(intercept_SMDH$sigma2)) ``` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+Second, the model using SMD(H) showed a small positive and statistically significant effect of an experimental increase of GNM on fitness \[@fig-mean-effect (B); SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
 For lnRR, these heterogeneity metrics exceeded the 75th percentile benchmark (see @supp-tab-heterogeneity for detailed estimates of heterogeneity).
@@
 
-Third, there is a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
+Third, there was a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
 \[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
@@
 
-Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
+Fourth, the bird species had a small positive statistically non-significant increase with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
 However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
 
-Among different types of fitness trait, only morphological trait showed positive effect of GNM on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
+Lastly, among different types of fitness trait, only morphological trait had a positive effect of GNM on fitness, which was statistically significant for SMD(H) \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
 Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
 All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
-Trait type accounted for a small amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Trait type accounted for some of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
 
@@
 
-Summary of the results.. wrap up with a few points
+Our pre-registered systematic review and meta-analysis provides the first quantitative synthesis of experimental studies on green nest material (GNM) across birds and reveals that, on average, supplementing nests with GNM yields only small benefits.
+The strength of the overall effects of GNM differed between the effect size metric used.
+Using the lnRR we found a non-significant 1.6% increase in overall fitness proxies, whereas the SMD(H) indicated a small but statistically significant positive effect (SMD(H)= 0.179).
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+There was moderate to high heterogeneity among the effect sizes, which we tried to understand using several biological and methodological moderators.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution [@yang2024].
+
+Contrary to long-standing verbal models, neither the courtship hypothesis (visual/olfactory signalling) nor the parental-care hypothesis (parasite repellency or pharmacological “drug” effects) emerged as a consistent driver of these small gains.
+Effect estimates associated with courtship traits were positive but non-significant, and those associated with nestling protection were essentially zero.
+In other words, current evidence does not allow us to attribute the weak average benefit of GNM to a single prevailing mechanism.
+This result mirrors the idiosyncratic outcomes scattered through the primary literature and indicates that future tests will need to measure multiple pathways simultaneously—ideally pairing behavioural observations with direct assays of ectoparasites, microbial load, and nest-air volatiles.
+
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of GNM --whether through sexual signalling, parasite reduction, or direct nestling benefits-- lack consistent empirical support across studies.
 
 Second paragraph
-
--   Discussing your results.. effect sizes
 
@@
 
-Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased GNM, though the strength of these effects depended on the effect size metric used.
-SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
-Importantly, our results reveal that the commonly studied mechanistic hypotheses of GNM---whether through sexual signalling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+Temp Discussion:
 
-The While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of GNM on fitness.
-These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
-The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+**Discussion**
+
+[manuscript_GNM]{.underline}.
+The discrepancy between metrics underscores how the inferred magnitude of benefit depends on the underlying scale: lnRR captures proportional shifts, whereas SMDᴴ reflects absolute shifts that are sensitive to among-study variance.
+Nonetheless, both converge on the same biological interpretation—if GNM is adaptive, the advantage appears subtle rather than dramatic, and it is expressed against a backdrop of substantial heterogeneity (I² ≈ 66–99 %).
+
+Methodological context explained far more of the variance than biological hypothesis.
+Designs that compared nests with **no added material** versus **aromatic material** produced the largest positive effects (lnRR ≈ 0.15; SMDᴴ ≈ 0.84), whereas contrasts between **no material** and **non-aromatic plant matter** were negative, and the canonical **aromatic vs.
+non-aromatic** comparison was indistinguishable from zero.
+These patterns emphasise that simply adding any material can alter micro-climate, and that the perceived “aromatic benefit” may in part reflect removing a structural disadvantage in controls rather than an odour-specific mechanism.
+In addition, time of addition mattered: experiments that replenished GNM continuously throughout nesting detected stronger benefits (significant under SMDᴴ) than those adding it only before or after hatching, hinting that persistence of volatile release or parental display may be important [manuscript_GNM]{.underline}.
+
+Despite these insights, most of the heterogeneity remains unexplained.
+Experimental design alone accounted for roughly a third of total variance, whereas parasite type, trait category, timing, and species identity each explained ≤ 8 % [manuscript_GNM]{.underline}.
+The residual scatter likely stems from taxonomic and geographic bias—82 % of effect sizes come from just three passerines (blue tit, spotless starling, European starling) studied at 16 sites, many of them by the same research groups.
+Publication-bias diagnostics were equivocal, yet small-study effects cannot be excluded given the prevalence of datasets with ≤ 5 nests per group and the tendency to publish novel positive outcomes.
+Together these limitations caution against broad generalisation and point to the need for coordinated multi-lab efforts on under-represented taxa (e.g., open-cup builders, raptors).
+
+Several practical recommendations follow.
+First, future experiments should adopt fully factorial designs that separate **structure** (any plant vs.
+none) from **chemistry** (aromatic vs.
+non-aromatic) and track volatilome dynamics across the nesting cycle.
+Second, fitness proxies should move beyond morphology—currently the only trait category with a significant positive response—to harder endpoints such as fledging success, juvenile recruitment, and parental survival.
+Third, sharing raw data and negative results will be essential to reduce residual heterogeneity and clarify whether the modest average benefit we detect is biologically meaningful or a statistical artefact of design choices.
+
+In summary, our review shows that adding green plant material to bird nests can increase fitness‐related measures, but the effect is small, context-dependent, and not yet pinned to a single mechanism.
+By refining experimental designs, broadening taxonomic coverage, and integrating chemical ecology with behavioural ecology, the next generation of studies can resolve whether GNM is truly an adaptive extended phenotype or merely a conspicuous but weak contributor to avian reproductive success.
+
+Nicely looking colours!!!!
+Alright, alright.
+In short, ask me more if it is not clear.
+When you ran these 2 meta-regressions specifically, you normally would run them twice, once without the intercept from which you obtain the values you are presenting (i.e., the real lnRR and SMD(H) estimates specific for each off the three levels: Parental Care, Courtship, and Both), and then you would run them with the intercept.
+In the latter, the intercept, unless you changed the order of the levels in the moderator (which is a factor), would represent "Both", and the output would not tell you the difference between the estimate of level "Courtship" and "Both", and "Parental Care" and "Both" (i.e., the estimate is a difference, e.g. lnRRboth = 0.025 - lnRRcourtship = 0.038 = -0.13) and whether that difference is statistically significant.
+We want to show whether any differences between the levels are statistically significant, so we should present these p-values to say whether each of the pair-wise comparisons differs statistically or not.
+For you to know if "Courtship" and "Parental Care", you need to run an extra line of code, because from the model you only get the information about the difference between all levels of the factor (in this case, "Courtship" and "Parental Care") and the reference level AKA intercept (in this case "Both"). \
+\
+You can use:\
+car::linearHypothesis(model, rbind(c(0,1,-1)))\
+\
+For more: [https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms](https://www.google.com/url?q=https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms&sa=D&source=docs&ust=1751963317237496&usg=AOvVaw3NHnLsaKPtM6xq0VTTbXZO)
+
+Importantly, if the moderator would be a continuous moderator, e.g.
+publication year, you do not need to do any extra test, but should present the estimates for the intercept in the model as well as the estimates for the slope.
+When the moderator is continuous, you do not remove the intercept (i.e., no -1).
+Let me know if something is unclear.
+Good job, looking forward to reading the manuscript.
 

### 2025-07-09 code/07_data_analysis.Rmd
No build, pushing to switch machines :D

--- 2025-07-06 docs/code/07_data_analysis.Rmd
@@
 # saving the model
-saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))
-
-# saving the dataset for this model
-write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
+# saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))
+
+# saving the dataset for this model
+# write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
 ```
@@
 # saving the model
-saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
-
-# saving the dataset for this model
-write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
+# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+
+# saving the dataset for this model
+# write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
 ```
@@
 ## For the lnRR effect size...
-dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3)
+dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3 | is.na(comparision_type))
 ## Only some rows are removed... 
@@
 
-dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3)
+dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3 | is.na(comparision_type))
 ## Only some rows are removed... 
@@
 
-Results remain practically the same irrespective..
+Overall conclusions remain practically the same irrespective.. now what about the meta-regression using Type of Experiment Design
+
+```{r}
+
+dataset_lnRR_design_SA <- dataset_lnRR %>% filter(comparision_type!=3)
+
+VCV_lnRR_design_SA <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_SA,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_SA <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_SA ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_SA )
+
+## Now for SMDH
+
+dataset_SMDH_design_SA <- dataset_SMDH %>% filter(comparision_type!=3)
+
+VCV_SMDH_design_SA <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design_SA,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design_SA <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design_SA ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design_SA)
+```
 
@@
 #----------------------------------------------------------------------------------
-
-# lnRR_hypothesis_pc <-
-#   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_lnRR,# specify lnRR's sampling variance;
-#                     mods = ~ Hypothesis,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                   test = "t",
-#                   control = list(optimizer="optim"),
-#                   data = dataset_lnRR)
-# 
-# # I now want to test for statistical differences between groups. Male and fem
-# # information for androgens can be obtained from the outcome of the table. For thyroid
-# # hormones I need to do Post-hoc Wald tests: 
-# car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
-```
+## For lnRR
+VCV_lnRR<- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_hypothesis_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance;
+                    mods = ~ Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+# I now want to test for statistical differences between groups. Male and fem
+# information for androgens can be obtained from the outcome of the table. For thyroid
+# hormones I need to do Post-hoc Wald tests:
+car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
+
+# saving the model
+saveRDS(lnRR_hypothesis_pc, file = here::here("model/lnRR_hypothesis_pc.rds"))
+
+# For SMDH
+
+VCV_SMDH <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_hypothesis_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance;
+                    mods = ~ Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+# I now want to test for statistical differences between groups. Male and fem
+# information for androgens can be obtained from the outcome of the table. For thyroid
+# hormones I need to do Post-hoc Wald tests:
+car::linearHypothesis(SMDH_hypothesis_pc, rbind(c(0,1,-1)))
+# saving the model
+saveRDS(SMDH_hypothesis_pc, file = here::here("model/SMDH_hypothesis_pc.rds"))
+
+#----------------------------------------------------------------------------------
+# For Type of experimental design
+#----------------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_lnRR_design <- dataset_lnRR %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design ,# specify lnRR's sampling variance;
+                    mods = ~ comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design )
+
+# Saving the model
+saveRDS(lnRR_design_pc, file = here::here("model/lnRR_design_pc.rds"))
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design <- dataset_SMDH %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design ,# specify lnRR's sampling variance;
+                    mods = ~ comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design )
+
+# Saving the model
+saveRDS(SMDH_design_pc, file = here::here("model/SMDH_design_pc.rds"))
+
+#----------------------------------------------------------------------------------
+# For Time of addition of GNM
+#----------------------------------------------------------------------------------
+
+## We use the complete dataset in this case
+lnRR_time_gnm_addition_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+## Saving the model
+saveRDS(lnRR_time_gnm_addition_pc, file = here::here("model/lnRR_time_gnm_addition_pc.rds"))
+
+## Now similarly for the SMDH effect size using the complete dataset
+SMDH_time_gnm_addition_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+                    mods = ~ time_of_gnm_addition,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+## Saving the model
+saveRDS(SMDH_time_gnm_addition_pc, file = here::here("model/SMDH_time_gnm_addition_pc.rds"))
+
+#----------------------------------------------------------------------------------
+# Parasite Type
+#----------------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to parasite or pathogen
+dataset_lnRR_parasite <- dataset_lnRR%>%
+  filter(!is.na(parasite_type))%>%
+  mutate(parasite_type=as.factor(parasite_type),
+         paper_ID=as.factor(paper_ID),
+         Observation_ID=as.factor(Observation_ID),
+         group_ID_coded=as.factor(group_ID_coded),
+         bird_species=as.factor(bird_species))
+
+VCV_lnRR_parasite <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_parasite,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_parasite_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_parasite,# specify lnRR's sampling variance;
+                    mods = ~ parasite_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                   test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_parasite)
+
+# Saving the model
+saveRDS(lnRR_parasite_pc, file = here::here("model/lnRR_parasite_pc.rds"))
+
+### Similiarly for SMDH as well selecting the dataset with parasite type
+# This analysis only includes dataset that has a proxy relating to parasite or pathogen
+dataset_SMDH_parasite <- dataset_SMDH%>%
+  filter(!is.na(parasite_type))
+VCV_SMDH_parasite <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_parasite,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_parasite_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
+                    mods =  parasite_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                   test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_parasite)
+
+# Save the model
+saveRDS(SMDH_parasite_pc, file = here::here("model/SMDH_parasite_pc.rds"))
+
+#----------------------------------------------------------------------------------
+# Bird Species
+#----------------------------------------------------------------------------------
+
+lnRR_birds_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance;
+                    mods = ~ bird_species,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+# Saving the model
+saveRDS(lnRR_birds_pc, file = here::here("model/lnRR_birds_pc.rds"))
+
+## Now doing this for SMDH
+
+SMDH_birds_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance;
+                    mods = ~  bird_species,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+# Saving the model
+saveRDS(SMDH_birds_pc, file = here::here("model/SMDH_birds_pc.rds"))
+
+#----------------------------------------------------------------------------------
+# Type of trait studied
+#----------------------------------------------------------------------------------
+
+lnRR_trait_pc <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR,# specify lnRR's sampling variance;
+                    mods = ~ trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR)
+
+# Saving the model
+saveRDS(lnRR_trait_pc, file = here::here("model/lnRR_trait_pc.rds"))
+
+## Now similarly for SMDH
+
+SMDH_trait_pc <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH,# specify lnRR's sampling variance;
+                    mods = ~ trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH)
+
+# Saving the model
+saveRDS(SMDH_trait_pc, file = here::here("model/SMDH_trait_pc.rds"))
+
+```
+
+\

### 2025-07-09 code/08_figures-tables.Rmd
No build, pushing to switch machines :D

--- 2025-07-06 docs/code/08_figures-tables.Rmd
@@
 
-# ---- FIGURES ————–
+# ---- FIGURES --------------
 
@@
                  size = size.freq, colour = bird_species),
-             alpha = 0.6) +
-  scale_size(range = c(1, 2)) +
+             alpha = 0.9) +
+  scale_size(range = c(2, 4)) +
   scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
+  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
   theme_void() +
@@
   draw_plot(fig_map) +
-  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.52, height = 0.22) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))
+  draw_plot(zoom_map, x = 0.05, y = 0.15, width = 0.28, height = 0.38) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))
 
@@
 # Plot for lnRR
-intercept_lnRR_plot <- orchaRd::orchard_plot(intercept_lnRR,
+
+intercept_lnRR_plot<- orchaRd::orchard_plot(intercept_lnRR,
                                              mod = "1",
                                              group = "paper_ID",
-                                    trunk.size = 0.25,
+                                             trunk.size = 0.3,
                                              branch.size = 2,
@@
                                              alpha = 0.2,
-                                    xlab = "Effect size (Log Response Ratio- lnRR)",
+                                             xlab = "Effect size (lnRR)", 
                                              fill =  T) +
@@
                                     group = "paper_ID",
-                                    trunk.size = 0.25,
+                                    trunk.size = 0.3,
                                     branch.size = 2,
@@
                                     alpha = 0.2,
-                                    xlab = "Effect size (Standardized Mean Difference- SMD(H))",
+                                    xlab = "Effect size (SMDH)",
                                     fill = TRUE) +
@@
 ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
+
+###----------------------------------------------------------------------------------
+
+## Now the cropped versions presented in the main manuscript..
+
+###----------------------------------------------------------------------------------
+
+intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
+                                             mod = "1",
+                                             group = "paper_ID",
+                                             trunk.size = 0.5,
+                                             branch.size = 2,
+                                             twig.size = 0.5,
+                                             alpha = 0.2,
+                                             xlab = "Effect size (lnRR)", 
+                                             fill =  T) +
+  scale_fill_manual(values = "#98C127") +
+  scale_colour_manual(values = "#98C127" ) +
+    scale_y_continuous(limits = c(-0.7, 0.7)) +
+theme_minimal(base_size = 14) +
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
+    legend.position = c(0.98, 0.05),
+    legend.justification = c(1, 0),
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 7),
+    legend.text = element_text(size = 7),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_blank()
+  ) +
+  labs(x = "Intercept")
+
+# Plot for SMDH
+intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
+                                    mod = "1",
+                                    group = "paper_ID",
+                                    trunk.size = 0.5,
+                                    branch.size = 2,
+                                    twig.size = 0.5,
+                                    alpha = 0.2,
+                                    xlab = "Effect size (SMDH)",
+                                    fill = TRUE) +
+  scale_fill_manual(values = "#F47A00") +
+  scale_colour_manual(values = "#F47A00") +
+  scale_y_continuous(limits = c(-2.7, 2.7)) +
+  theme_minimal(base_size = 14) +
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
+    legend.position = c(0.98, 0.05),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 7),
+    legend.text = element_text(size = 7),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_blank()
+  ) +
+  labs(x = "Intercept")
+
+# Combine using patchwork
+Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
+  plot_annotation(tag_level = c("A","B"))
+
+ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
 ```
@@
   labs(x = "",
-       y = "lnRR")+
+       y = "Effect size (lnRR)")+
   theme(
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 90, vjust = 0.01, hjust = 0.5)
-  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))
 
@@
   labs(x = "",
-       y = "SMD(H)")+
+       y = "Effect size (SMDH)")+
     theme(
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 90, vjust = 0.8, hjust = 1)
-  )+ scale_x_discrete(labels = c("Both","Courtship","Parental Care"))
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental Care"))
 
@@
 ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+# Plot lnRR meta-regression on hypothesis
+
+lnRR_hypothesis_plot_crop <-
+  orchard_plot(mod_results(lnRR_hypothesis,
+                           mod = "Hypothesis",
+                           group = "paper_ID"),
+               trunk.size = 0.5,
+               branch.size = 1.3,
+               twig.size = 0.5,
+               alpha = 0.4,
+               fill = T,
+               xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+    scale_y_continuous(limits = c(-0.7, 0.7)) +
+  labs(x = "",
+       y = "Effect size (lnRR)")+
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.05),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
+
+# Plot SMDH meta-regression on hypothesis
+
+SMDH_hypothesis_plot_crop <-
+  orchard_plot(
+    mod_results(
+      SMDH_hypothesis,
+      mod = "Hypothesis",
+      group = "paper_ID"
+    ),
+    trunk.size = 0.5,
+    branch.size = 1.3,
+    twig.size = 0.5,
+    alpha = 0.4,
+    fill = T,
+    xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.7, 2.7)) +
+  labs(x = "",
+       y = "Effect size (SMDH)")+
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.05),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
+
+SMDH_hypothesis_plot_crop <- SMDH_hypothesis_plot_crop +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Combine using patchwork
+Figure_hypothesis_crop <- lnRR_hypothesis_plot_crop + SMDH_hypothesis_plot_crop +
+  plot_annotation(tag_level = c("A","B"))
+
+ggsave(here::here("figures/Figure_hypothesis_crop.png"), plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
 ```
@@
 
-# -------- TABLES ———-
+# -------- TABLES ----------
 

### 2025-07-09 manuscript_GNM.qmd
No build, pushing to switch machines :D

@@
 
-Nest and nest-building are fundamental across a diverse range of animals, including insects (e.g., termites, spiders), mammals (e.g., platypus, rodents), and perhaps more famously, birds.
-Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@mainwaring2014; @deeming2023; @hansell2000].
-While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@suárez-rodríguez2013; @sergio2011; @sheard2024].
-These non-structural additions suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
-Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in many bird species [@moreno1994; @hoi1996], even across species [@soler1995].
+Nest and nest-building are fundamental across a diverse range of animals, including arthropods (e.g., termites, spiders), mammals (e.g., platypus, rodents), and perhaps more famously, birds.
+Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@hansell2000; @mainwaring2014; @deeming2023].
+While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including mud, stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@sergio2011; @suárez-rodríguez2013; @sheard2024].
+These are considered non-structural additions and suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in several bird species [@moreno1994; @hoi1996], even interspecifically [@soler1995].
 Nest-building behaviour is increasingly recognized as an expression of the extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
@@
 An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
-This green nest material (GNM) ---leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species keep adding it even after the nest is finished.
-Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-Collecting and constantly replenishing GNM requires extra foraging flights, sometimes even outside the territory [@mennerat2009].
-The costs associated with nest building [@mainwaring2013], and these additional efforts suggest that GNM is unlikely to be gathered opportunistically and suggests a possible adaptive significance.
+This green nest material (hereafter GNM) --- which often corresponds to leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species like blue tit *(Cyanistes cyanus)*, keep adding it even after the nest is finished.
+Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some time weeks, requires extra time, and some cases flying outside one's territory [@mennerat2009].
+Thus, the general costs associated with nest building [@mainwaring2013], and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
 
 Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
-First, the courtship hypothesis suggests that mostly males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
-This hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
-The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy to other males [@eens1993; @gwinner1997; @brouwer2004], particularly in cavity-nesting species where visual cues inside the nest are limited.
+The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
+Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993].
+The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
-Second, and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
-This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence [@wimberger1984].
+Second, the most widely tested hypothesis is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that provided indirect evidence for it by comparing nest reuse, diet composition and GNM presence [@wimberger1984].
 Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
-Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
-The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
-Thus, while both hypotheses suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
-Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
+Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@lafuma2001; @dawson2004; @mennerat2009b; @quiroga2012] have shown mixed results in some cases, GNM was been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
+This alternative hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
+Thus, while both the nest protection and drug hypothesis suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load, something difficult to achieve.
 
-Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic properties have been proposed.
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic (i.e., volatiles and secondary metabolites) properties have been also proposed.
 These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], or simply fulfilling a structural function [@lyons1987].
@@
 In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
-Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and potentially far-reaching in its implications.
+Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
 
@@
 Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e.
-combining both the nest protection and drug hypotheses due to their non-exclusivity).
-In addition, we explore the observed context-dependency (i.e., high heterogeneity among effect sizes) via meta-regressions.
+combination of both the nest protection and drug hypotheses).
+In addition, we tested several potential moderators that might explain the observed context-dependency (i.e., high heterogeneity among effect sizes).
 Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
-microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design (aromatic vs.
+microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design used (aromatic vs.
 non-aromatic vs.
-no added material), the focal species, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
+no added material), the focal species studied, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
 Our meta-analysis of experimental studies is the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
@@
 
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+We pre-registered our study protocol on the Open Science Framework [@dimri2024] prior to data exploration and analysis.
 The pre-registration details our objectives, a priori hypotheses and predictions, methods and planned data analyses.
@@
 We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022 (see update below).
-The keyword search query was designed as a three-block query to include terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
+The keyword search query was designed as a three-block query including terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
-We searched through titles, abstracts and keywords in English-language only with no restrictions on publication date or study type.
+Although our search string only included keywords in English, we planned to screen any study in English, Spanish, Portuguese and Hindi, but found none.
+We searched through titles, abstracts and keywords with no restrictions on publication date or study type.
 We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, to confirm our keyword selection.
-After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 [@westgate2019], we found `{r} nrow(unique_reference_list)` unique records.
+Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
 
@@
 
-All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
-We included all studies on birds that experimentally manipulated the green nest material (both aromatics or herbs).
+All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package 'revtools' following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
+We included all studies on birds that experimentally manipulated the GNM (both aromatics or herbs).
 `{r} tools::toTitleCase(as.character(english::english(nrow(selected_abstract_screening))))` articles passed the title-and-abstract screening and were further evaluated during the full-text screening, where each article was independently screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
-We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
+We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (@figsupp-fitness-proxies).
 `{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` passed the full-text screening and were, thus, eligible for our meta-analysis.
@@
 
-We updated our systematic literature search by repeating our search on 12.08.2024.
-We found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
-Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before (@figsupp-decision-tree), and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article for our meta-analysis.
-Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles through other sources (i.e., identified through a poster by a collaborator and through an independent recommendation by a colleague).
-In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
+We updated our systematic literature search by repeating our search on the 12th of August, 2024 and found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
+Only one observer (SD) performed both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
+Lastly, we identified `{r} as.character(english::english(nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)), 1, 1))` additional eligible articles recommended by two colleagues.
+In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` published articles were eligible for our meta-analysis, but we also obtained two additional unpublished studies (more details below and in @figsupp-prisma-flowchart).
 
@@
 
-The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
+The data of each article ware extracted evenly by one of three authors (SD, TR, JMGS), with another screener verifying the procedure, and four authors (SD, TR, JMGS, AST) collectively discussing and revising unclear cases.
 We prioritised extracting the primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package `metaDigitise` v.1.0.1 (@pick2018).
-If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), that could be transformed into an effect size.
-Last, if the previous steps failed but the article has openly shared datasets (n = `{r} length(raw_data)`), we calculated the means, SD and sample sizes from them.
-**When data was presented in different sources (e.g.
-in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).**
+If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`effect sizes, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))` studies), that could be transformed into an effect size.
+Last, if the previous steps failed but the article had openly archieved data, we calculated the means, SD and sample sizes from them (n = `{r} length(raw_data)`).
 
-We extracted the means, variances and sample size for each control-treatment pairwise comparison.
-Controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material, or no material at all.
-Treatments consisted of aromatic materials added by authors, birds, or both.
-For cases that compared non-aromatic material to where authors did not add any additional nest material and any material added by the birds was removed, the non-aromatic material was considered the treatment.
-We recorded the type of comparison being made as a moderator.
+We extracted the means, variances and sample sizes for each control-treatment pairwise comparison.
+Depending on the experimental design of each study, controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material than the treatments, no additional material added, or removal of material added by birds; whereas treatments consisted of aromatic materials added by authors, birds, or both.
+Those comparisons were coded either as non-aromatic GNM vs.
+aromatic GNM, or no added GNM vs.
+aromatic GNM, in our moderator "experimental design".
+However, there was a third type of comparison used in some studies comparing nests with experimentally added non-aromatic GNM to nests without any added GNM or in which GNM added by the birds was removed by the authors.
+In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these effect sizes as non-aromatic GNM vs.
+no added GNM in our moderator "experimental design".
+The moderator "experimental design" was used for subsequent meta-regressions.
 For each study, we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, or supplementary materials).
 We categorised the fitness proxies measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
-For studies testing whether green nest material affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
+For studies testing whether GNM affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
 For a complete list of variables extracted see @figsupp-variables .
-We did not include some traits in all our analyses because it was unclear how they related to fitness (k = `{r} nrow(excluded_proxies)` , n = `{r} length(unique(excluded_proxies$paper_ID))`; see @figsupp-excluded-proxies for the list and reasons of exclusion).
+We did not include some traits reported in the original studies in all our analyses because it was unclear from the study and our own judgement how they related to fitness (k = `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))`; studies see @figsupp-excluded-proxies for the list and reasons of exclusion).
 
-To obtain missing data (e.g., non-reported results, missing sample sizes, etc.), we contacted four authors.
+To obtain missing data (e.g., non-reported results, missing sample sizes), we contacted four authors.
 All four authors responded to our email, but only two provided the data as requested; one did not have the data any more, and one did not give a conclusive response.
-Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))`) to ask for any potential unpublished data that could be included in our meta-analysis.
-One corresponding author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO), provided data for another unpublished study.
+Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))` studies) to ask for any potential unpublished data that could be included in our meta-analysis.
+One author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of us (MO), provided data for another unpublished study.
 In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
 Author correspondance was performed using a standardised email template (@figsupp-email).
-In all, we extracted data for `{r} length(unique(published_studies$paper_ID))` published articles (k = `{r} nrow(published_studies)`) and `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`).
 
@@
 In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
-SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance— specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1 (excluded k = `{r} nrow(low_sample)`, n = `{r} length(unique(low_sample$paper_ID))`)
+SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance--- specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1 (excluded k = `{r} nrow(low_sample)`, n = `{r} length(unique(low_sample$paper_ID))`)
 
@@
 
-To estimate the effect of green nest material addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
+To estimate the effect of GNM addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
 Thus, throughout, we fitted two separate sets of model for each effect size.
@@
 We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness was unclear, to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g.
+sex ratio, testosterone levels, etc.), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
 For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
@@
 
-To test the relative importance of the two main hypotheses suggested for green nest material: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
+To test the relative importance of the two main hypotheses suggested for GNM: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
 For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
@@
 We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
-To understand the effect of green nest material on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`).
+To understand the effect of GNM on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`).
 We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
-We also ran a meta-regression with the entire dataset set using bird species as a moderator (levels: *Buteo buteo*, *Cyanistes caeruleus*, *Passer cinnamomeus*, *Parus major*, *Sturnus unicolor*, *Sturnus vulgaris*, *Tachycineta bicolor*) to understand if the effect of green nest material on fitness depended on the system being studied.
-To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with Time of addition of green nest material as the moderator.
-We explored the effect of green nest material on fitness depending on the type of trait studies (levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
-We explored the impact of methodological differences on the relationship between green nest material and fitness.
+We also ran a meta-regression with the entire dataset set using bird species as a moderator (levels: *Buteo buteo*, *Cyanistes caeruleus*, *Passer cinnamomeus*, *Parus major*, *Sturnus unicolor*, *Sturnus vulgaris*, *Tachycineta bicolor*) to understand if the effect of GNM on fitness depended on the system being studied.
+To test the effect of time of addition of GNM on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with Time of addition of GNM as the moderator.
+We explored the effect of GNM on fitness depending on the type of trait studies (levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
+We explored the impact of methodological differences on the relationship between GNM and fitness.
 To understand the effect of type of experimental design (i.e.
@@
 
-We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations.
+We obtained `{r} nrow(dataset_analysis)` effect sizes from a total of `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@fig-distribution).
 About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
 Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean (±SD) number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean effective sample size (i.e.
-after accounting for shared-group non-independence) were `{r} sprintf("%.1f", median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))` and `{r} sprintf("%.1f",mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))`, respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%select(paper_ID,effective_n_control,effective_n_experiment, lnRR, SMDH)%>%filter(effective_n_experiment<2|effective_n_control<2))` effect sizes had a sample size of less than 2 in each group).
+The mean ±SD number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` and , respectively (range: `{r} min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`--`{r} max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
+
+![**Geographical distribution of the 16 study populations included in a meta-analysis testing the adaptive value of green nest materials in birds:** Point size reflects the number of effect sizes coming from the location, and colour denotes species (see legend), with an inset zooming on the cluster of distribution.](figures/Figure_Distribution.png){#fig-distribution}
 
@@
 intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
-bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
+bivariate_model<-readRDS(here::here("model/sensitivity_analysis/bivariate_model.rds"))
 ```
 
-Both lnRR and SMDH intercept-only multilevel meta-analyses showed an increase in fitness in the nests with an increase in green nest material compared to control nests; however, the overall effect was only statistically significant for SMDH.
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness in the nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
-The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH2~total~ = `{r} round(as.double(orchaRd::cvh2_ml(intercept_lnRR)[1]),2)` and M2~total =~ `{r} round(as.double(orchaRd::m2_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes.
-The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high.
-Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2024a; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)
+First, lnRR showed an average statistically non-significant increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM \[@fig-mean-effect (A); lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
 
-As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
-While neither intercept was statistically significant, the results strengthens the interpretation that any effect of green nest material on fitness outcomes in likely to be very small at best \[lnRR = `{r} as.double(formatC(coef(bivariate_model)[1], digit = 3, format="f"))`, p-value = `{r} as.double(formatC(bivariate_model$pval[1], digits = 3, format = "f"))` and SMDH = `{r} as.double(formatC(coef(bivariate_model)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(bivariate_model$pval[2], digits = 3, format = "f"))`\].
+Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM \[@fig-mean-effect (B); SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see @supp-tab-heterogeneity for detailed estimates of heterogeneity).
 
-![Overall effect of green nest material on fitness: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
-Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardized mean difference as effect sizes.
-k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect width="1059"}
+These overall results, and their conclusions were robust to several sensitivity analysis.
+First, we fitted a pre-registered bivariate multilevel meta-analytic model including both effect sizes as response variables \[lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`\].
+In addition, we ran several non-pre-registered sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was unclear, (ii) the removal effect sizes that were originally reported as simply statistically non-significant, (iii) both (i) and (ii), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
+The number of effect sizes included in those sensitivity analyses ranged from 227 to 279 effect sizes, and the conclusions remained largely the same (\@supp-tab-SA).
 
-## **Hypotheses explaining the effect of green nest material**
+![Overall effect of green nest material on all fitness proxies combined: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (transparent coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section \[\@supp-full-fig\] for complete figures).](figures/Figure_overall_effect_crop.png){#fig-mean-effect}
+
+## **Mechanistic Hypotheses: explaining the effect of Green Nest Material**
 
@@
 summary_SMDH_hypothesis<-extractor_metareg(SMDH_hypothesis,"Hypothesis")
+
+lnRR_hypothesis_pc<-readRDS(here::here("model/lnRR_hypothesis_pc.rds"))
+SMDH_hypothesis_pc<-readRDS(here::here("model/SMDH_hypothesis_pc.rds"))
+
+summary_lnRR_hypothesis_pc<-extractor_metareg(lnRR_hypothesis_pc,"Hypothesis")
+summary_SMDH_hypothesis_pc<-extractor_metareg(SMDH_hypothesis_pc,"Hypothesis")
+
+summary(lnRR_hypothesis_pc)
+car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
+summary(SMDH_hypothesis_pc)
+car::linearHypothesis(SMDH_hypothesis_pc, rbind(c(0,1,-1)))
 ```
 
-Using the multilevel meta-regressions, we found no clear support for the proposed hypotheses in the literature ([@fig-hypothesis]).
-There is a small positive but non-significant effect of green nest material on fitness related to reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMDH~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
-We found even smaller, non-significant effect of green nest material on fitness related to protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ =`{r} summary_lnRR_hypothesis$estimate[3]`, CI: `{r} summary_lnRR_hypothesis$CI[3]`, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMDH~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
-In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either hypotheses, we found a small positive effect which was significant only in the case of SMDH \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMDH~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
-The moderator explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@fig-hypothesis]).
+The estimates for the courtship hypothesis \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]`; SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\] and the nest protection and drug hypothesis (i.e.
+"parental care hypothesis") \[lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, CI: ``` {r}``summary_lnRR_hypothesis$CI[3] ```, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]`; SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\] were small and statistically significant.
+However, notice that about half of all effect sizes could not be unequivocally assigned to only one hypothesis, so our meta-regression contained a third category that combined both.
+This category showed an average positive increase in fitness outcomes in nests with an experimental increase of GNM, but the effect was only significant for SMD(H) \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]`; SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
+None of the three categories differed statistically significantly from each other (p-value~lnRR~ \> 0.262 and p-value~lnRR~ \> 0.178 in all cases), and the moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
 
-![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests.
+![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as potential drivers of fitness benefits from green nest material in nests.
 Orchard plot of the multilevel meta-regression for A.
 log response ratio (lnRR) and B.
-Standardized mean difference (SMDH).
+Standardized mean difference (SMD(H)).
 Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
-k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section \[\@fig-supp-hypothesis\] for complete figures).](figures/Figure_hypothesis_crop.png){#fig-hypothesis}
 
-## Pre-registered exploratory analyses
+## What other factors explain heterogeneity among effect sizes?
 
@@
 summary_SMDH_design<- extractor_metareg(SMDH_design,"comparision_type")
+
+## Now pair-wise comparison
+lnRR_design_pc<-readRDS(here::here("model/lnRR_design_pc.rds"))
+SMDH_design_pc<-readRDS(here::here("model/SMDH_design_pc.rds"))
+
+summary(lnRR_design_pc)
+car::linearHypothesis(lnRR_design_pc, rbind(c(0,1,-1)))
+summary(SMDH_design_pc)
+car::linearHypothesis(SMDH_design_pc, rbind(c(0,1,-1)))
+
 ```
 
-The effect of green nest material on fitness varied largely by the experimental design.
-The experimental design comparison between no added material and aromatic material showed a positive and statistically significant effect on fitness \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\].
-The experimental design comparison between no added material and non-aromatic material showed a negative effect on fitness, which was significant in lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value = `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
-Contrary to our expectation, the non-aromatic and aromatic green nest material comparison showed small negative non-significant effect on fitness \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMDH~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
-Experimental design comparison type also explained a large proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
+Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several multilevel meta-regressions.
+First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design.
+The overall effect size for the comparison between no added material and aromatic material was positive and statistically significant \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, it was negative for the comparison between no added material and non-aromatic material statistically significantly so lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
+Last, the comparison between non-aromatic and aromatic material showed a small negative statistically non-significant effect \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMD(H)~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
+The moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
 
-When green nest material was added continuously throughout the nesting phase, the effect of it on fitness was positive and statistically significant in the case of SMDH \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMDH~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
-Addition after egg hatching showed a positive but non-significant effect on fitness and before egg hatching had a near zero non-significant effect [\@fig-MR](C-D); Table X\].
-Timing of addition of green nest material explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
+Second, when GNM was added continuously throughout the nesting phase, its overall effect was positive and statistically significant, at least for SMD(H) \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
+compared to its addition before or after egg hatching \[[\@fig-MR](C-D); Table X\].
+Timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
 
-![](figures/Figure_design_time_gnm_addition.png){#fig-MR}
+![Orchard plot showing overall effect of green nest material depending on the multilevel meta-regression for experimental design for - A.
+log response ratio (lnRR) and B.
+Standardized mean difference (SMD(H)) and time of GNM addition for - C.
+log response ratio (lnRR) and D.
+Standardized mean difference (SMD(H)).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_design_time_gnm_addition.png){#fig-MR}
 
-There is positive non-significant effect of increased green nest material on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
+Third, there was a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
 \[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
@@
 
-Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
+Fourth, the bird species had a small positive statistically non-significant increase with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
 However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
 
-Among different types of fitness trait, only morphological trait showed positive effect of green nest material on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
+Lastly, among different types of fitness trait, only morphological trait had a positive effect of GNM on fitness, which was statistically significant for SMD(H) \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
 Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
 All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
-Trait type accounted for a small amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Trait type accounted for some of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
 
@@
 
-Summary of the results.. wrap up with a few points
+Our pre-registered systematic review and meta-analysis provides the first quantitative synthesis of experimental studies on green nest material (GNM) across birds and reveals that, on average, supplementing nests with GNM yields only small benefits.
+The strength of the overall effects of GNM differed between the effect size metric used.
+Using the lnRR we found a non-significant 1.6% increase in overall fitness proxies, whereas the SMD(H) indicated a small but statistically significant positive effect (SMD(H)= 0.179).
+These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
+There was moderate to high heterogeneity among the effect sizes, which we tried to understand using several biological and methodological moderators.
+The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution [@yang2024].
+
+Contrary to long-standing verbal models, neither the courtship hypothesis (visual/olfactory signalling) nor the parental-care hypothesis (parasite repellency or pharmacological "drug" effects) emerged as a consistent driver of these small gains.
+Effect estimates associated with courtship traits were positive but non-significant, and those associated with nestling protection were essentially zero.
+In other words, current evidence does not allow us to attribute the weak average benefit of GNM to a single prevailing mechanism.
+This result mirrors the idiosyncratic outcomes scattered through the primary literature and indicates that future tests will need to measure multiple pathways simultaneously---ideally pairing behavioural observations with direct assays of ectoparasites, microbial load, and nest-air volatiles.
+
+Importantly, our results reveal that the commonly studied mechanistic hypotheses of GNM --whether through sexual signalling, parasite reduction, or direct nestling benefits-- lack consistent empirical support across studies.
 
 Second paragraph
-
--   Discussing your results.. effect sizes
 
@@
 
-Our systematic review and meta-analysis found a small positive increase in fitness benefits in the bird nests with increased green nest material, though the strength of these effects depended on the effect size metric used.
-SMDH showed a larger effect with the There is high heterogeneity among the effect sizes, emphasizing the context-dependence of this benefit.
-Importantly, our results reveal that the commonly studied mechanistic hypotheses of green nest material---whether through sexual signalling, parasite reduction, or direct nestling benefits---lack consistent empirical support across studies.
+Temp Discussion:
 
-The While lnRR and SMDH differ in their measurement scale, both effect sizes suggest a small positive but non-conclusive effect of green nest material on fitness.
-These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
-The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution (@yang2024).
+**Discussion**
+
+[manuscript_GNM]{.underline}.
+The discrepancy between metrics underscores how the inferred magnitude of benefit depends on the underlying scale: lnRR captures proportional shifts, whereas SMDᴴ reflects absolute shifts that are sensitive to among-study variance.
+Nonetheless, both converge on the same biological interpretation---if GNM is adaptive, the advantage appears subtle rather than dramatic, and it is expressed against a backdrop of substantial heterogeneity (I² ≈ 66--99 %).
+
+Methodological context explained far more of the variance than biological hypothesis.
+Designs that compared nests with **no added material** versus **aromatic material** produced the largest positive effects (lnRR ≈ 0.15; SMDᴴ ≈ 0.84), whereas contrasts between **no material** and **non-aromatic plant matter** were negative, and the canonical **aromatic vs.
+non-aromatic** comparison was indistinguishable from zero.
+These patterns emphasise that simply adding any material can alter micro-climate, and that the perceived "aromatic benefit" may in part reflect removing a structural disadvantage in controls rather than an odour-specific mechanism.
+In addition, time of addition mattered: experiments that replenished GNM continuously throughout nesting detected stronger benefits (significant under SMDᴴ) than those adding it only before or after hatching, hinting that persistence of volatile release or parental display may be important [manuscript_GNM]{.underline}.
+
+Despite these insights, most of the heterogeneity remains unexplained.
+Experimental design alone accounted for roughly a third of total variance, whereas parasite type, trait category, timing, and species identity each explained ≤ 8 % [manuscript_GNM]{.underline}.
+The residual scatter likely stems from taxonomic and geographic bias---82 % of effect sizes come from just three passerines (blue tit, spotless starling, European starling) studied at 16 sites, many of them by the same research groups.
+Publication-bias diagnostics were equivocal, yet small-study effects cannot be excluded given the prevalence of datasets with ≤ 5 nests per group and the tendency to publish novel positive outcomes.
+Together these limitations caution against broad generalisation and point to the need for coordinated multi-lab efforts on under-represented taxa (e.g., open-cup builders, raptors).
+
+Several practical recommendations follow.
+First, future experiments should adopt fully factorial designs that separate **structure** (any plant vs.
+none) from **chemistry** (aromatic vs.
+non-aromatic) and track volatilome dynamics across the nesting cycle.
+Second, fitness proxies should move beyond morphology---currently the only trait category with a significant positive response---to harder endpoints such as fledging success, juvenile recruitment, and parental survival.
+Third, sharing raw data and negative results will be essential to reduce residual heterogeneity and clarify whether the modest average benefit we detect is biologically meaningful or a statistical artefact of design choices.
+
+In summary, our review shows that adding green plant material to bird nests can increase fitness‐related measures, but the effect is small, context-dependent, and not yet pinned to a single mechanism.
+By refining experimental designs, broadening taxonomic coverage, and integrating chemical ecology with behavioural ecology, the next generation of studies can resolve whether GNM is truly an adaptive extended phenotype or merely a conspicuous but weak contributor to avian reproductive success.
+
+Nicely looking colours!!!!
+Alright, alright.
+In short, ask me more if it is not clear.
+When you ran these 2 meta-regressions specifically, you normally would run them twice, once without the intercept from which you obtain the values you are presenting (i.e., the real lnRR and SMD(H) estimates specific for each off the three levels: Parental Care, Courtship, and Both), and then you would run them with the intercept.
+In the latter, the intercept, unless you changed the order of the levels in the moderator (which is a factor), would represent "Both", and the output would not tell you the difference between the estimate of level "Courtship" and "Both", and "Parental Care" and "Both" (i.e., the estimate is a difference, e.g. lnRRboth = 0.025 - lnRRcourtship = 0.038 = -0.13) and whether that difference is statistically significant.
+We want to show whether any differences between the levels are statistically significant, so we should present these p-values to say whether each of the pair-wise comparisons differs statistically or not.
+For you to know if "Courtship" and "Parental Care", you need to run an extra line of code, because from the model you only get the information about the difference between all levels of the factor (in this case, "Courtship" and "Parental Care") and the reference level AKA intercept (in this case "Both"). \
+\
+You can use:\
+car::linearHypothesis(model, rbind(c(0,1,-1)))\
+\
+For more: [https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms](https://www.google.com/url?q=https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms&sa=D&source=docs&ust=1751963317237496&usg=AOvVaw3NHnLsaKPtM6xq0VTTbXZO)
+
+Importantly, if the moderator would be a continuous moderator, e.g.
+publication year, you do not need to do any extra test, but should present the estimates for the intercept in the model as well as the estimates for the slope.
+When the moderator is continuous, you do not remove the intercept (i.e., no -1).
+Let me know if something is unclear.
+Good job, looking forward to reading the manuscript.
 
@@
 study design, taxa, data availability)                                                                              | No                       |                                                                                                                          |
-|  |  | 4.2 | Justify criteria, if necessary (i.e. not obvious from aims and scope. | No |  |
-| **Finding studies** | **0%** | 5.1 | Define the type of search (e.g. comprehensive search, representative sample) | No |  |
-|  |  | 5.2 | State what sources of information were sought (e.g. published and unpublished studies, personal communications) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 4.2                                                                                                          | Justify criteria, if necessary (i.e.
+not obvious from aims and scope.
+| No                       |                                                                                                                          |
+| **Finding studies**                                                                                                                                                                     | **0%**                                                                                                                                                                                                                                                      | 5.1                                                                                                          | Define the type of search (e.g.
+comprehensive search, representative sample)                                                                                                                                                                                                                          | No                       |                                                                                                                          |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 5.2                                                                                                          | State what sources of information were sought (e.g.
+published and unpublished studies, personal communications)                                                                                                                                                                                       | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 5.3                                                                                                          | Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators                                                                                                                                                                                   | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 5.4                                                                                                          | Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates)                                                                                                                                                                        | No                       |                                                                                                                          |
-| **Study selection** | **0%** | 6.1 | Describe how studies were selected for inclusion at each stage of the screening process (e.g. use of decision trees, screening software) | No |  |
-|  |  | 6.2 | Report the number of people involved and how they contributed (e.g. independent parallel screening) | No |  |
-| **Data collection process** | **0%** | 7.1 | Describe where in the reports data were collected from (e.g. text or figures) | No |  |
-|  |  | 7.2 | Describe how data were collected (e.g. software used to digitize figures, external data sources) | No |  |
-| 7.3 | Describe moderator variables that were constructed from collected data (e.g. number of generations calculated from years and average generation time) | No |  |  |  |
+| **Study selection**                                                                                                                                                                     | **0%**                                                                                                                                                                                                                                                      | 6.1                                                                                                          | Describe how studies were selected for inclusion at each stage of the screening process (e.g.
+use of decision trees, screening software)                                                                                                                                                              | No                       |                                                                                                                          |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 6.2                                                                                                          | Report the number of people involved and how they contributed (e.g.
+independent parallel screening)                                                                                                                                                                                                   | No                       |                                                                                                                          |
+| **Data collection process**                                                                                                                                                             | **0%**                                                                                                                                                                                                                                                      | 7.1                                                                                                          | Describe where in the reports data were collected from (e.g.
+text or figures)                                                                                                                                                                                                                         | No                       |                                                                                                                          |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 7.2                                                                                                          | Describe how data were collected (e.g.
+software used to digitize figures, external data sources)                                                                                                                                                                                                      | No                       |                                                                                                                          |
+| 7.3                                                                                                                                                                                     | Describe moderator variables that were constructed from collected data (e.g.
+number of generations calculated from years and average generation time)                                                                                                       | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 | 7.4                                                                                                                                                                                     | Report how missing or ambiguous information was dealt with during data collection (e.g.
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 8.2                                                                                                          | Describe items that do not appear in the main results, or which could not be extracted due to insufficient information                                                                                                                                                                                | No                       |                                                                                                                          |
-| 8.3 | Describe main assumptions or simplifications that were made (e.g. categorising both 'length' and 'mass' as 'morphology') | No |  |  |  |
-|  |  | 8.4 | Describe the type of replication unit (e.g. individuals, broods, study sites) | No |  |
+| 8.3                                                                                                                                                                                     | Describe main assumptions or simplifications that were made (e.g.
+categorising both 'length' and 'mass' as 'morphology')                                                                                                                                    | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 8.4                                                                                                          | Describe the type of replication unit (e.g.
+individuals, broods, study sites)                                                                                                                                                                                                                         | No                       |                                                                                                                          |
 | **Assessment of individual study quality**                                                                                                                                              | **0%**                                                                                                                                                                                                                                                      | 9.1                                                                                                          | Describe whether the quality of studies included in the systematic review or meta-analysis was assessed (e.g.
 blinded data collection, reporting quality, experimental versus observational)                                                                                                          | No                       |                                                                                                                          |
-|  |  | 9.2 | Describe how information about study quality was incorporated into analyses (e.g. meta-regression and/or sensitivity analysis) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 9.2                                                                                                          | Describe how information about study quality was incorporated into analyses (e.g.
+meta-regression and/or sensitivity analysis)                                                                                                                                                                        | No                       |                                                                                                                          |
 | **Effect size measures**                                                                                                                                                                | **0%**                                                                                                                                                                                                                                                      | 10.1                                                                                                         | Describe effect size(s) used                                                                                                                                                                                                                                                                          | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-|  |  | 10.2 | Provide a reference to the equation of each calculated effect size (e.g. standardised mean difference, log response ratio) and (if applicable) its sampling variance | No |  |
-| **Missing data** | **0%** | 11.1 | Describe any steps taken to deal with missing data during analysis (e.g. imputation, complete case, subset analysis) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 10.2                                                                                                         | Provide a reference to the equation of each calculated effect size (e.g.
+standardised mean difference, log response ratio) and (if applicable) its sampling variance                                                                                                                                  | No                       |                                                                                                                          |
+| **Missing data**                                                                                                                                                                        | **0%**                                                                                                                                                                                                                                                      | 11.1                                                                                                         | Describe any steps taken to deal with missing data during analysis (e.g.
+imputation, complete case, subset analysis)                                                                                                                                                                                  | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 11.2                                                                                                         | Justify the decisions made to deal with missing data                                                                                                                                                                                                                                                  | No                       |                                                                                                                          |
@@
 common/fixed effects model, unweighted model), provide justification for this choice                                      | No                       |                                                                                                                          |
-| **Software** | **0%** | 13.1 | Describe the statistical platform used for inference (e.g. R) | No |  |
+| **Software**                                                                                                                                                                            | **0%**                                                                                                                                                                                                                                                      | 13.1                                                                                                         | Describe the statistical platform used for inference (e.g.
+R)                                                                                                                                                                                                                                         | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 13.2                                                                                                         | Describe the packages used to run models                                                                                                                                                                                                                                                              | No                       |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 13.5                                                                                                         | Describe the version numbers of all software used                                                                                                                                                                                                                                                     | No                       |                                                                                                                          |
-| **Non-independence** | **0%** | 14.1 | Describe the types of non-independence encountered (e.g. phylogenetic, spatial, multiple measurements over time) | No |  |
+| **Non-independence**                                                                                                                                                                    | **0%**                                                                                                                                                                                                                                                      | 14.1                                                                                                         | Describe the types of non-independence encountered (e.g.
+phylogenetic, spatial, multiple measurements over time)                                                                                                                                                                                      | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| **Publication bias and sensitivity analysis** | **0%** | 16.1 | Describe assessments of the risk of bias due to missing results (e.g. publication, time-lag, and taxonomic biases) | No |  |
+| **Publication bias and sensitivity analysis**                                                                                                                                           | **0%**                                                                                                                                                                                                                                                      | 16.1                                                                                                         | Describe assessments of the risk of bias due to missing results (e.g.
+publication, time-lag, and taxonomic biases)                                                                                                                                                                                    | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| **Clarification of post hoc analyses** | **0%** | 17.1 | When hypotheses were formulated after data analysis, this should be acknowledged. | No |  |
+| **Clarification of post hoc analyses**                                                                                                                                                  | **0%**                                                                                                                                                                                                                                                      | 17.1                                                                                                         | When hypotheses were formulated after data analysis, this should be acknowledged.
+| No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| **Metadata, data, and code** | 18.1 | Share metadata (i.e. data descriptions) | No |  |  |
+| **Metadata, data, and code**                                                                                                                                                            | 18.1                                                                                                                                                                                                                                                        | Share metadata (i.e.
+data descriptions)                                                                      | No                                                                                                                                                                                                                                                                                                    |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| 19.4 | Present a Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)-like flowchart (www.prisma-statement.org). | No |  |  |  |
+| 19.4                                                                                                                                                                                    | Present a Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)-like flowchart (www.prisma-statement.org).
+| No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| Provide a summary of key characteristics for reported outcomes (either in text or figures; e.g. one quarter of effect sizes reported for vertebrates and the rest invertebrates) | No |  |  |  |  |
+| Provide a summary of key characteristics for reported outcomes (either in text or figures; e.g.
+one quarter of effect sizes reported for vertebrates and the rest invertebrates)        | No                                                                                                                                                                                                                                                          |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| 20.4 | Provide a summary of limitations of included moderators (e.g. collinearity and overlap between moderators) | No |  |  |  |
+| 20.4                                                                                                                                                                                    | Provide a summary of limitations of included moderators (e.g.
+collinearity and overlap between moderators)                                                                                                                                                  | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| **Meta-regression** | 23.1 | Provide estimates of meta-regression slopes (i.e. regression coefficients) and confidence/credible intervals | No |  |  |
+| **Meta-regression**                                                                                                                                                                     | 23.1                                                                                                                                                                                                                                                        | Provide estimates of meta-regression slopes (i.e.
+regression coefficients) and confidence/credible intervals | No                                                                                                                                                                                                                                                                                                    |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-|  |  | 23.2 | Include estimates and confidence/credible intervals for all moderator variables that were assessed (i.e. complete reporting) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 23.2                                                                                                         | Include estimates and confidence/credible intervals for all moderator variables that were assessed (i.e.
+complete reporting)                                                                                                                                                                          | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| 23.4 | Describe outcomes from model selection, if done (e.g. R2 and AIC) | No |  |  |  |
+| 23.4                                                                                                                                                                                    | Describe outcomes from model selection, if done (e.g.
+R2 and AIC)                                                                                                                                                                                           | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| **Outcomes of publication bias and sensitivity analysis** | **0%** | 24.1 | Provide results for the assessments of the risks of bias (e.g. Egger's regression, funnel plots) | No |  |
+| **Outcomes of publication bias and sensitivity analysis**                                                                                                                               | **0%**                                                                                                                                                                                                                                                      | 24.1                                                                                                         | Provide results for the assessments of the risks of bias (e.g.
+Egger's regression, funnel plots)                                                                                                                                                                                                      | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-|  |  | 25.2 | Summarise the main findings in terms of the precision of effects (e.g. size of confidence intervals, statistical significance) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 25.2                                                                                                         | Summarise the main findings in terms of the precision of effects (e.g.
+size of confidence intervals, statistical significance)                                                                                                                                                                        | No                       |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-| 25.6 | Consider limitations and their influence on the generality of conclusions, such as gaps in the available evidence (e.g. taxonomic and geographical research biases) | No |  |  |  |
+| 25.6                                                                                                                                                                                    | Consider limitations and their influence on the generality of conclusions, such as gaps in the available evidence (e.g.
+taxonomic and geographical research biases)                                                                                         | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
@@
 |                                                                                                                                                                                         |                                                                                                                                                                                                                                                             |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-|  |  | 27.2 | List included studies as referenced sources (e.g. rather than listing them in a table or supplement) | No |  |
+|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 27.2                                                                                                         | List included studies as referenced sources (e.g.
+rather than listing them in a table or supplement)                                                                                                                                                                                                  | No                       |                                                                                                                          |
 
@@
 ![](figures/Figure_parasite_birds_trait.png)
+
+![Overall effect of green nest material on all fitness proxies combined: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (transparent coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png)
+
+![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as potential drivers of fitness benefits from green nest material in nests.
+Orchard plot of the multilevel meta-regression for A.
+log response ratio (lnRR) and B.
+Standardized mean difference (SMD(H)).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-supp-hypothesis width="1035"}

### 2025-07-12 code/08_figures-tables.Rmd
push to continue on laptop

--- 2025-07-06 docs/code/08_figures-tables.Rmd
@@
                              Lat_Location=c(51.50,38.41,40.45,
-                                            45.40,52.39, 37.18,
+                                            45.40,52.39, 37.18,40.53,
                                             54,39.05,
@@
                              Long_Location=c(19.29,-9.02,-3.50,
-                                             -64.10,6.05,-3.11,
+                                             -64.10,6.05,-3.11,-4.01,
                                              -124,-76.81,
@@
 location_counts <- dataset_analysis %>%
-  group_by(Location) %>%
-  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')
+  group_by(Location, bird_species) %>%
+  summarise(
+    size.freq = n(),
+  )
 
@@
 dataset_analysis_unique_rows <- dataset_analysis_unique_rows %>%
-  left_join(location_counts, by = "Location")
+  left_join(location_counts, by = c("Location", "bird_species"))
 
@@
              aes(x = Long_Location, y = Lat_Location,
-                 size = size.freq, colour=bird_species), alpha = 0.6) +
-scale_size(range = c(3, 5)) +
+                 size = size.freq, colour=bird_species),
+             alpha = 0.6) +
+ scale_size(range = c(1, 2.5)) +
   scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
@@
                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  guides(size = "none", alpha = "none") +
+  guides(size = "none", alpha = "none",
+         colour = guide_legend(override.aes = list(size = 1.5), keywidth = 0.4,
+                               keyheight = 0.4))+
   labs(x = "Longitude",
@@
   theme_classic() +
-  theme(legend.position = c(0.99, 0.15),
+  theme(plot.margin = margin(t =15, r = 15, b = 5, l = 5),  
+        legend.position = c(1.02, 0.42),
         legend.justification = c("right", "bottom"),
@@
         legend.text = element_text(size=6),
-        axis.title = element_text(size = 10),
-        axis.text.x = element_text(size = 10),
-        axis.text.y = element_blank())
+        legend.title = element_text(size=7),
+        axis.title = element_text(size = 8),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10))
 
@@
                  size = size.freq, colour = bird_species),
-             alpha = 0.6) +
+             position = position_jitter(width = 0.2, height = 0.2),
+             alpha = 0.7) +
   scale_size(range = c(1, 2)) +
@@
                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  coord_cartesian(xlim = c(-120, 120), ylim = c(25, 65)) +  # Northern Hemisphere
+  coord_cartesian(xlim = c(-10, 20), ylim = c(25, 65)) +  # Northern Hemisphere
   theme_void() +
@@
   draw_plot(fig_map) +
-  draw_plot(zoom_map, x = 0.10, y = 0.12, width = 0.52, height = 0.22) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))
+  draw_plot(zoom_map, x = 0.11, y = 0.21, width = 0.20, height = 0.28) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.2))
 
@@
                                              alpha = 0.2,
-                                    xlab = "Effect size (Log Response Ratio- lnRR)",
-                                    fill = T) +
+                                             xlab = "Effect size (lnRR)", 
+                                             fill =  T,
+                                             k.pos = c(0.53,0.6,0.6)) +
   scale_fill_manual(values = "#98C127") +
@@
     legend.direction = "horizontal",
-    legend.title = element_text(size = 7),
+    legend.title = element_text(size = 6),
     legend.text = element_text(size = 7),
@@
                                     alpha = 0.2,
-                                    xlab = "Effect size (Standardized Mean Difference- SMD(H))",
-                                    fill = TRUE) +
+                                    xlab = "Effect size (SMDH)",
+                                    fill = TRUE,
+                                    k.pos = c(2,0.6,0.6)) +
   scale_fill_manual(values = "#F47A00") +
@@
 ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
+
+###----------------------------------------------------------------------------------
+
+## Now the cropped versions presented in the main manuscript..
+
+###----------------------------------------------------------------------------------
+
+intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
+                                             mod = "1",
+                                             group = "paper_ID",
+                                             trunk.size = 0.5,
+                                             branch.size = 2,
+                                             twig.size = 0.5,
+                                             alpha = 0.2,
+                                             xlab = "Effect size (lnRR)", 
+                                             fill =  T,
+                                             k.pos = c(0.53,0.6,0.6)) +
+  scale_fill_manual(values = "#98C127") +
+  scale_colour_manual(values = "#98C127" ) +
+    scale_y_continuous(limits = c(-0.6, 0.6)) +
+theme_minimal(base_size = 14) +
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
+    legend.position = c(0.98, 0.05),
+    legend.justification = c(1, 0),
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 7),
+    legend.text = element_text(size = 7),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_blank()
+  ) +
+  labs(x = "Intercept")
+
+# Plot for SMDH
+intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
+                                    mod = "1",
+                                    group = "paper_ID",
+                                    trunk.size = 0.5,
+                                    branch.size = 2,
+                                    twig.size = 0.5,
+                                    alpha = 0.2,
+                                    xlab = "Effect size (SMDH)",
+                                    fill = TRUE,
+                                    k.pos = c(2,0.6,0.6)) +
+  scale_fill_manual(values = "#F47A00") +
+  scale_colour_manual(values = "#F47A00") +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+  theme_minimal(base_size = 14) +
+  theme(
+    panel.border = element_rect(colour = "black", fill = NA, size = 0.8),
+    legend.position = c(0.98, 0.05),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.title = element_text(size = 7),
+    legend.text = element_text(size = 7),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_blank()
+  ) +
+  labs(x = "Intercept")
+
+# Combine using patchwork
+Figure_intercept_crop <- intercept_lnRR_plot_crop / intercept_SMDH_plot_crop +
+  plot_annotation(tag_level = c("A","B"))
+
+ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
 ```
@@
   labs(x = "",
-       y = "lnRR")+
+       y = "Effect size (lnRR)")+
   theme(
     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+    legend.position.inside = c(0.99, 0.01),
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.justification = c(1, 0), 
@@
   labs(x = "",
-       y = "SMD(H)")+
+       y = "Effect size (SMDH)")+
     theme(
     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+    legend.position.inside = c(0.99, 0.01),
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.justification = c(1, 0), 
@@
 ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+# Plot lnRR meta-regression on hypothesis
+
+lnRR_hypothesis_plot_crop <-
+  orchard_plot(mod_results(lnRR_hypothesis,
+                           mod = "Hypothesis",
+                           group = "paper_ID"),
+               trunk.size = 0.5,
+               branch.size = 1.3,
+               twig.size = 0.5,
+               alpha = 0.4,
+               fill = T,
+               k.pos = c(0.4,0.6,0.6),
+               xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+    scale_y_continuous(limits = c(-0.6, 0.6)) +
+  labs(x = "",
+       y = "Effect size (lnRR)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 5),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
+
+# Plot SMDH meta-regression on hypothesis
+
+SMDH_hypothesis_plot_crop <-
+  orchard_plot(
+    mod_results(
+      SMDH_hypothesis,
+      mod = "Hypothesis",
+      group = "paper_ID"
+    ),
+    trunk.size = 0.5,
+    branch.size = 1.3,
+    twig.size = 0.5,
+    alpha = 0.4,
+    fill = T,
+    k.pos = c(1.9,0.6,0.6),
+    xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+  labs(x = "",
+       y = "Effect size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 5),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
+
+SMDH_hypothesis_plot_crop <- SMDH_hypothesis_plot_crop +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Combine using patchwork
+Figure_hypothesis_crop <- lnRR_hypothesis_plot_crop + SMDH_hypothesis_plot_crop +
+  plot_annotation(tag_level = c("A","B"))
+
+ggsave(here::here("figures/Figure_hypothesis_crop.png"), plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
 ```
@@
   ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
   xlab ="") +
@@
   labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "bottom",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
+       y = "Effect Size (lnRR)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
         legend.title = element_text(size = 6),
@@
         axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("After egg laying", "Before egg laying", "Continous addition"))
+  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
 
@@
   ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
+  labs(x = "",
+       y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
+  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+lnRR_time_gnm_addition_plot_cropped <-
+  orchard_plot(mod_results(
+    lnRR_time_gnm_addition,
+    mod = "time_of_gnm_addition",
+    group = "paper_ID"
+  ),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
   xlab ="") +
@@
   scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
   labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "bottom",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
+       y = "Effect Size (lnRR)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
         legend.title = element_text(size = 6),
@@
         axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  )
+  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+
+SMDH_time_gnm_addition_plot_cropped <-
+  orchard_plot(mod_results(
+      SMDH_time_gnm_addition,
+      mod = "time_of_gnm_addition",
+      group = "paper_ID"
+    ),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+    k.pos = c(1.9,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+labs(x = "",
+     y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
+  ) + scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
 
@@
     ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1,0.6,0.6),
   xlab ="") +
@@
 labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0),
-    # legend.direction = "horizontal",
+     y = "Effect Size (lnRR)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.title = element_text(size = 6),
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
 
@@
     ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1.5,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
+labs(x = "",
+     y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+lnRR_design_plot_cropped <-
+  orchard_plot(mod_results(
+      lnRR_design,
+      mod = "comparision_type",
+      group = "paper_ID"
+    ),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
   xlab ="") +
@@
   scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
 labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0),
-    # legend.direction = "horizontal",
+     y = "Effect Size (lnRR)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.title = element_text(size = 6),
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  )
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
+
+SMDH_design_plot_cropped <-
+  orchard_plot(mod_results(
+      SMDH_design,
+      mod = "comparision_type",
+      group = "paper_ID"
+    ),
+   trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+    k.pos = c(1.9,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+labs(x = "",
+     y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
 
@@
 # Combine using patchwork
-Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
+Figure_design_time_gnm_addition<- ((lnRR_design_plot + SMDH_design_plot) /
                                (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
@@
 ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 240, width = 250, units = "mm", dpi = 600)
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+## I am going to remove the y ticks from the SMDH plots to make it smaller..
+SMDH_design_plot_cropped <- SMDH_design_plot_cropped +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+SMDH_time_gnm_addition_plot_cropped <- SMDH_time_gnm_addition_plot_cropped +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Combine using patchwork
+Figure_design_time_gnm_addition_cropped <- ((lnRR_design_plot_cropped + SMDH_design_plot_cropped) /
+                               (lnRR_time_gnm_addition_plot_cropped + SMDH_time_gnm_addition_plot_cropped)) +
+  plot_annotation(tag_levels = "A")
+
+ggsave(here::here("figures/Figure_design_time_gnm_addition_cropped.png"), plot = Figure_design_time_gnm_addition_cropped, height = 240, width = 250, units = "mm", dpi = 600)
 
@@
 
-# -------- TABLES ———-
+# -------- Supplementary Material Table ----------
+
+```{r}
+
+# Loading packages
+
+pacman::p_load(gt,dplyr,metafor)
+```
+
+```{r}
+#| label: excluded_proxy_table
+
+merged_data_extraction <- read_csv(here::here("data/03_data_cleaning/merged_data_extraction.csv"), show_col_types = F)
+
+dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"), show_col_types = F)
+
+excluded_proxies<- merged_data_extraction %>%
+  filter(fulltext_screening == "included") %>%
+  filter(proxy_decision== "exclude")%>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+SA_only_proxies <- dataset_analysis %>%
+  filter(proxy_decision == "sensitivity-analysis")%>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+# Now binding them together
+combined_summary <- bind_rows(
+  excluded_proxies %>% mutate(Category = "Completely excluded"),
+  SA_only_proxies   %>% mutate(Category = "Sensitivity-analysis only")
+) %>%
+  arrange(Category, paper_ID)
+
+# Group by category
+excluded_proxies <-combined_summary %>%
+  gt() %>%
+  tab_header(
+    title = md("**Excluded Fitness Proxies**")
+  ) %>%
+  # define row-groups
+  tab_row_group(
+    group    = "Completely excluded",
+    rows     = Category == "Completely excluded"
+  ) %>%
+  tab_row_group(
+    group    = "Sensitivity-analysis only",
+    rows     = Category == "Sensitivity-analysis only"
+  ) %>%
+  # hide the helper column
+  cols_hide("Category") %>%
+  # relabel columns
+  cols_label(
+         `paper_ID`             = "Paper ID",
+         `Number of proxies`    = "Noumber\nof Proxies",
+         `Excluded Proxies`     = "Excluded\nProxies",
+         `Reason for Exclusion` = "Reason for Exclusion"
+  ) %>%
+  fmt_markdown(columns = c(`Excluded Proxies`, `Reason for Exclusion`)) %>%
+  opt_align_table_header(align = "left") %>%
+  cols_align(
+    align   = "left",
+    columns = everything()
+  ) %>%
+  tab_options(
+    table.width               = pct(90),
+    row.striping.background_color = "#F7F7F7"
+  )
+
+# gtsave(
+#   data = excluded_proxies,
+#   filename = here::here("/tables/excluded_proxies_table.pdf"),
+#   expand = 10   # adds a little padding around the table
+# )
+```
 
@@
 
-pacman::p_load(gt,dplyr,metafor)
+# Loading the models including only published data
+SA_lnRR_published<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
+SA_SMDH_published<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))
+
+# Loading the models without Comparison Type 3
+SA_lnRR_no_comp3<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
+SA_SMDH_no_comp3<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))
 
@@
 
+# Loading the model for Geary's Test Passed. There is none for SMDH because we do not know the guideline for SMDH and Geary's Test
+SA_lnRR_geary_passed<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))
+
 # Now let's build the table
@@
 SA_intercept_only <- tibble::tibble(
-  effect_size = c("lnRR","lnRR","lnRR","SMDH","SMDH","SMDH","SMDH"),
-  data_used = c("Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),
-
-  Estimate = c(SA_lnRR_flagged$b[1],
+  effect_size = c("lnRR","lnRR","lnRR","lnRR","lnRR","lnRR",
+                  "SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMDH"),
+  data_used = c("Including published data only","Excluding Experimental Design Non-Aromatic Vs.
+No added material","Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Excluding effect sizes where lnRR failed Geary's Test","Including published data only","Excluding Experimental Design Non-Aromatic Vs.
+No added material", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),
+
+  Estimate = c(SA_lnRR_published$b[1],
+               SA_lnRR_no_comp3$b[1],
+               SA_lnRR_flagged$b[1],
                SA_lnRR_no_missingES$b[1],
                SA_lnRR_flagged_no_missingES$b[1],
+               SA_lnRR_geary_passed$b[1],
+               SA_SMDH_published$b[1],
+               SA_SMDH_no_comp3$b[1],
                SA_SMDH_flagged$b[1],
@@
 
-  CI_Lower = c(SA_lnRR_flagged$ci.lb,
+  CI_Lower = c(SA_lnRR_published$ci.lb,
+               SA_lnRR_no_comp3$ci.lb,
+               SA_lnRR_flagged$ci.lb,
                SA_lnRR_no_missingES$ci.lb,
                SA_lnRR_flagged_no_missingES$ci.lb,
+               SA_lnRR_geary_passed$ci.lb,
+               SA_SMDH_published$ci.lb,
+               SA_SMDH_no_comp3$ci.lb,
                SA_SMDH_flagged$ci.lb,
@@
 
-  CI_Upper = c(SA_lnRR_flagged$ci.ub,
+  CI_Upper = c(SA_lnRR_published$ci.ub,
+               SA_lnRR_no_comp3$ci.ub,
+               SA_lnRR_flagged$ci.ub,
                SA_lnRR_no_missingES$ci.ub,
                SA_lnRR_flagged_no_missingES$ci.ub,
+               SA_lnRR_geary_passed$ci.ub,
+               SA_SMDH_published$ci.ub,
+               SA_SMDH_no_comp3$ci.ub,
                SA_SMDH_flagged$ci.ub,
@@
 
-  PI_Lower = c(predict(SA_lnRR_flagged)$pi.lb,
+  PI_Lower = c(predict(SA_lnRR_published)$pi.lb,
+               predict(SA_lnRR_no_comp3)$pi.lb,
+               predict(SA_lnRR_flagged)$pi.lb,
                predict(SA_lnRR_no_missingES)$pi.lb,
                predict(SA_lnRR_flagged_no_missingES)$pi.lb,
+               predict(SA_lnRR_geary_passed)$pi.lb,
+               predict(SA_SMDH_published)$pi.lb,
+               predict(SA_SMDH_no_comp3)$pi.lb,
                predict(SA_SMDH_flagged)$pi.lb,
@@
 
-  PI_Upper = c(predict(SA_lnRR_flagged)$pi.ub,
+  PI_Upper = c(predict(SA_lnRR_published)$pi.ub,
+               predict(SA_lnRR_no_comp3)$pi.ub,
+               predict(SA_lnRR_flagged)$pi.ub,
                predict(SA_lnRR_no_missingES)$pi.ub,
                predict(SA_lnRR_flagged_no_missingES)$pi.ub,
+               predict(SA_lnRR_geary_passed)$pi.ub,
+               predict(SA_SMDH_published)$pi.ub,
+               predict(SA_SMDH_no_comp3)$pi.ub,
                predict(SA_SMDH_flagged)$pi.ub,
@@
 
-  P_value = c(SA_lnRR_flagged$pval,
+  P_value =  c(SA_lnRR_published$pval,
+               SA_lnRR_no_comp3$pval,
+               SA_lnRR_flagged$pval,
                SA_lnRR_no_missingES$pval,
                SA_lnRR_flagged_no_missingES$pval,
+               SA_lnRR_geary_passed$pval,
+               SA_SMDH_published$pval,
+               SA_SMDH_no_comp3$pval,
                SA_SMDH_flagged$pval,
@@
 
-  Q_value = c(SA_lnRR_flagged$QE,
+  Q_value = c(SA_lnRR_published$QE,
+               SA_lnRR_no_comp3$QE,
+               SA_lnRR_flagged$QE,
                SA_lnRR_no_missingES$QE,
                SA_lnRR_flagged_no_missingES$QE,
+               SA_lnRR_geary_passed$QE,
+               SA_SMDH_published$QE,
+               SA_SMDH_no_comp3$QE,
                SA_SMDH_flagged$QE,
@@
 
-  k_effect_sizes = c(SA_lnRR_flagged$k,
+  k_effect_sizes = c(SA_lnRR_published$k,
+               SA_lnRR_no_comp3$k,
+               SA_lnRR_flagged$k,
                SA_lnRR_no_missingES$k,
                SA_lnRR_flagged_no_missingES$k,
+               SA_lnRR_geary_passed$k,
+               SA_SMDH_published$k,
+               SA_SMDH_no_comp3$k,
                SA_SMDH_flagged$k,
@@
 
-  n_studies = c(length(SA_lnRR_flagged$s.levels.f[[1]]),
+  n_studies = c(length(SA_lnRR_published$s.levels.f[[1]]),
+               length(SA_lnRR_no_comp3$s.levels.f[[1]]),
+               length(SA_lnRR_flagged$s.levels.f[[1]]),
                length(SA_lnRR_no_missingES$s.levels.f[[1]]),
                length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
+               length(SA_lnRR_geary_passed$s.levels.f[[1]]),
+               length(SA_SMDH_published$s.levels.f[[1]]),
+               length(SA_SMDH_no_comp3$s.levels.f[[1]]),
                length(SA_SMDH_flagged$s.levels.f[[1]]),
@@
     P_value,
-    Q_value,
     k_effect_sizes,
@@
   tab_header(
-    title = md("**Summary of Sensitivity Analyses for lnRR and SMDH Intercept-only models**")
+    title = md("**Summary of Sensitivity Analyses for lnRR and SMD(H) Intercept-only models**")
   ) %>%
@@
     P_value = "P-value",
-    Q_value = "Q value",
     k_effect_sizes = "k (No. of Effect Sizes)",
@@
 
-#saving as a docx file
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
-```
+# Saving as an image
+gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.png"))
+
+# For saving as a docx file
+# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
+# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
+```
+
+\
+
+```{r Table for lnRR rho sensitivity analysis}
+
+# t4 <- data.frame(rho  = rho_range,
+#                  "overall effect"  = sapply(lnRR_VCV_range, function(x) coef(x)),
+#                  "standard error" = sapply(lnRR_VCV_range, function(x) x$se),
+#                  "p-value" = sapply(lnRR_VCV_range, function(x) x$pval),
+#                  "Lower CI" = sapply(lnRR_VCV_range, function(x) x$ci.lb),
+#                  "Upper CI" = sapply(lnRR_VCV_range, function(x) x$ci.ub),
+#                  "Log-likehood" = sapply(lnRR_VCV_range, function(x) fitstats(x)[1,1]),
+#                  "AIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[3,1]),
+#                  "BIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[4,1]),
+#                  "AICc" = sapply(lnRR_VCV_range, function(x) fitstats(x)[5,1]))
+# 
+# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
+# 
+# t4 %>% dfround(4) %>% DT::datatable()
+```
+
+# -------- TABLES ----------
 
@@
 
-# Create moderator header rows for heterogeneity metrics
-  moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
-  select(moderator, effect_size, Q, Q_pval, R2_marginal) %>%
-    distinct()%>%
-    pivot_wider(
-      names_from = effect_size,
-      values_from = c(Q, Q_pval, R2_marginal),
-      names_glue = "{.value}_{effect_size}"
-    )%>%
-  mutate(level = "Heterogeneity ",
-         row_type = "moderator")
+# # Create moderator header rows for heterogeneity metrics
+#   moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
+#   select(moderator, effect_size, R2_marginal) %>%
+#     distinct()%>%
+#     pivot_wider(
+#       names_from = effect_size,
+#       values_from = c( R2_marginal),
+#       names_glue = "{.value}_{effect_size}"
+#     )%>%
+#   mutate(level = "Heterogeneity ",
+#          row_type = "moderator")
 
 # Final combined table with headers and levels
-combined_results <- bind_rows(moderator_header, combined_results) %>%
+ combined_results <- combined_results %>%
+   # bind_rows(moderator_header ,combined_results) %>%
   arrange(moderator, row_type)%>% select(-row_type)%>%
   relocate(level, .after = moderator)%>%
-  mutate(moderator=case_when(moderator=="parasite_type"~"Parasite Type",
-                             moderator=="bird_species"~"Bird Species",
-                             moderator=="trait_type"~"Trait Type Category",
-                             moderator=="comparision_type"~"Experimental Design",
-                             moderator=="time_of_gnm_addition"~"Time of Green Nest Material Addition"))%>%
-  mutate(level = case_when(level==1 ~ "Non-aromatic vs. Aromatic",
-                           level==2 ~ "No added material vs. Aromatic",
-                           level==3 ~ "No added material vs. Non-aromatic",
-                           level=="a" ~ "After egg hatching",
-                           level=="b" ~ "Before egg hatching",
-                           level=="c" ~ "Continously through nesting phase",
-                           level=="Parasitic_and_pathogenic"~"Parasitic and Pathogen Related", .default=level))
+  mutate(moderator = case_when(
+    moderator == "parasite_type" ~ "5. Parasite\nType",
+    moderator == "bird_species" ~ "3. Bird\nSpecies",
+    moderator == "trait_type" ~ "4. Trait\nCategory",
+    moderator == "comparision_type" ~ "1. Experimental\nDesign",
+    moderator == "time_of_gnm_addition" ~ "2. Time of\nGNM Addition"
+  ))%>%mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Experimental\nDesign",
+      "2. Time of\nGNM Addition",
+      "3. Bird\nSpecies",
+      "4. Trait\nCategory",
+      "5. Parasite\nType"
+    )
+  ))%>%
+  arrange(moderator)%>%
+  mutate(level = case_when(level==1 ~ "Non-aromatic\nvs. Aromatic",
+                           level==2 ~ "No added material\nvs. Aromatic",
+                           level==3 ~ "No added material\nvs. Non-aromatic",
+                           level=="a" ~ "After egg\nhatching",
+                           level=="b" ~ "Before egg\nhatching",
+                           level=="c" ~ "Continously through\nnesting phase",
+                           level=="Parasitic_and_pathogenic"~"Parasitic and\nPathogen Related", .default=level))
 
@@
   gt(groupname_col = "moderator") %>%
-  tab_header(title = md("**Multilevel Meta-analytic Models for Exploratory Analyses**")) %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Exploratory Analyses**")) %>%
   cols_label(
-    Q_lnRR = "Q",
-    Q_pval_lnRR = "Q p-val",
-    R2_marginal_lnRR = "R²_mar",
-    Q_SMDH = "Q",
-    Q_pval_SMDH = "Q p-val",
-    R2_marginal_SMDH = "R²_mar",
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
     level = "Level",
@@
   ) %>%
-  tab_style(
-    style = cell_text(weight = "bold"),
-    locations = cells_body(
-      rows = level == "Heterogeneity"
-    ))%>%
+  # tab_style(
+  #   style = cell_text(weight = "bold"),
+  #   locations = cells_body(
+  #     rows = level == "Heterogeneity"
+  #   ))%>%
   tab_style(
@@
   tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
-  tab_spanner(label = "SMDH", columns = contains("_SMDH"))
-
-#saving as a docx file
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.docx"))
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.html"))
-```
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
+  )
+
+# saving the image
+gtsave(MLMR_table,here::here("tables/MLMR_table.png"))
+
+# #saving as a docx file or html
+# gtsave(MLMR_table,here::here("tables/MLMR_table.docx"))
+# gtsave(MLMR_table,here::here("tables/MLMR_table.html"))
+```

### 2025-07-12 docs/code/05_data_cleaning.Rmd
push to continue on laptop

@@
 knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
+
+if (!requireNamespace("pacman", quietly = TRUE)) {
+  install.packages("pacman")
+}
+
+pacman::p_load(here, dplyr, readxl, purrr, stringr, knitr, tidyverse)
+
+rm(list=ls()) ## clearing up any previously present variable
 ```
@@
 -   data_extraction_UnpublishedThesis.xlsx
-
-#### Setting up the space
-
-```{r load_packages, message=FALSE, warning=FALSE}
-
-pacman::p_load(here, dplyr, readxl, purrr, stringr, knitr, tidyverse)
-
-rm(list=ls()) ## clearing up any previously present variable
-```
 
@@
 
-# write.csv(merged_data_extraction,here::here("data/03_data_cleaning/merged_data_extraction.csv"),row.names=FALSE)
+write.csv(merged_data_extraction,here::here("data/03_data_cleaning/merged_data_extraction.csv"),row.names=FALSE)
 ```

### 2025-07-12 docs/code/07_data_analysis.Rmd
push to continue on laptop

@@
 ```{r}
-# install.packages("pacman")
-# load packages
-
-pacman::p_load(rotl,
-               ape,
-               ggtree)
-
-# We have 7 bird species in the dataset
-bird_species <- unique(dataset_analysis$bird_species)
-
-# extracting taxonomic information
-taxa <- rotl::tnrs_match_names(names = bird_species)
-taxa
-
-# check approximate matches
-taxa[taxa$approximate_match==TRUE & !(is.na(taxa$approximate_match)),]
-
-# phylogenetic information for our species from the Open Tree of Life
-
-tree <- rotl::tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")
-ape::is.binary(tree)
-
-# here are the species included in the tree
-sort(tree$tip.label)
-
-# removing the underscore "_" from the tree tip.label
-tree$tip.label <- gsub("_"," ", tree$tip.label)
-sort(tree$tip.label)
-
-# compute branch lengths of tree
-phylo_branch <- compute.brlen(tree, method = "Grafen", power = 1)
-
-# check tree is ultrametric
-is.ultrametric(phylo_branch) # TRUE
-
-# matrix to be included in the models
-bird_phylo <- vcv(phylo_branch, cor = T)
-bird_phylo
-
-plot(tree) #check: https://www.rdocumentation.org/packages/ape/versions/5.3/topics/plot.phylo
+# # install.packages("pacman")
+# # load packages
+# 
+# pacman::p_load(rotl,
+#                ape,
+#                ggtree)
+# 
+# 
+# # We have 7 bird species in the dataset
+# bird_species <- unique(dataset_analysis$bird_species)
+# 
+# # extracting taxonomic information
+# taxa <- rotl::tnrs_match_names(names = bird_species)
+# taxa
+# 
+# # check approximate matches
+# taxa[taxa$approximate_match==TRUE & !(is.na(taxa$approximate_match)),]
+# 
+# # phylogenetic information for our species from the Open Tree of Life
+# 
+# tree <- rotl::tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")
+# ape::is.binary(tree)
+# 
+# # here are the species included in the tree
+# sort(tree$tip.label)
+# 
+# # removing the underscore "_" from the tree tip.label
+# tree$tip.label <- gsub("_"," ", tree$tip.label)
+# sort(tree$tip.label)
+# 
+# # compute branch lengths of tree
+# phylo_branch <- compute.brlen(tree, method = "Grafen", power = 1)
+# 
+# # check tree is ultrametric
+# is.ultrametric(phylo_branch) # TRUE
+# 
+# # matrix to be included in the models
+# bird_phylo <- vcv(phylo_branch, cor = T)
+# bird_phylo
+# 
+# plot(tree) #check: https://www.rdocumentation.org/packages/ape/versions/5.3/topics/plot.phylo
 ```
@@
 ## For lnRR (or simply load dataset as provided)
-# dataset_lnRR<-dataset_analysis%>%
-# filter(lnRR_sign != "NA" | lnRR_variance != "NA")
+dataset_lnRR<-dataset_analysis%>%
+filter(lnRR_sign != "NA" | lnRR_variance != "NA")
 
@@
 dataset_SMDH<-dataset_analysis%>%
-   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
+   filter(proxy_decision != "sensitivity-analysis" | is.na(proxy_decision))
 
@@
 
-[**Robust variance estimation to guard against arbitary value of sampling correlation**]{.underline} - 'robust()' function from R package 'metafor' (Viechtbauer 2010) using 'CR2' (bias reduced linearization correction) from the R package 'clubSandwich' (Pustejovsky 2024) for small-sample size adjustment.
-
-At the moment, this is not working..
-
-```{r}
-#MLMA_lnRR_RVE<- robust(MLMA_lnRR_VCV,
-#                        cluster = paper_ID,
-#                        clubSandwich = TRUE,
-#                        verbose=T)
-
-# # summary(MLMA_lnRR_RVE)
-# I2_CI <- i2_ml(MLMA_lnRR_RVE) # Relative heterogeneity
-# round(I2_CI,2) # absolute heterogeneity is reported in the summary of the model
-```
-
 ::: callout-important
-Sensitivity Analysis
-
-We will also perform a sensitivity analysis using 0.3 and 0.7 correlation between the sampling variances from the same paper_ID and report it in the supplementary materials.
+**Pre-registered**: We will also perform a sensitivity analysis using 0.3 and 0.7 correlation between the sampling variances from the same paper_ID and report it in the supplementary materials.
 If this sensitivity analysis shows large differences in conclusions for the intercept-only model, we will proceed to perform such sensitivity analysis for the meta-regressions.
@@
 ```{r lnRR rho sensitivity analysis}
-# rho_range <- c(0.3, 0.5, 0.7)
-# 
-# MLMAlnRR_VCV_range <- list() # repeatedly run the specified model with varying rho
-# for (i in 1:length(rho_range))
-# {VCV_range <- vcalc(vi = lnRR_variance,
+
+# rho_range <- c(0.2,0.3, 0.5, 0.7,0.8)
+# 
+# SA_lnRR_VCV_range <- list() # repeatedly run the specified model with varying rho
+# for (i in 1:length(rho_range)){
+#   VCV_range <- vcalc(vi = lnRR_variance,
 #                      cluster = paper_ID,
-#                   subgroup = group_ID,
 #                      obs = Observation_ID,
 #                      data = dataset_lnRR,
-#                    rho = rho_range[i],
-#                     ) # impute sampling variance covariance matrix with varying rho
-# 
-# MLMAlnRR_VCV_range[[i]] <- rma.mv(yi = lnRR_sign,
-#                                   V = VCV_range, # sampling variance covariance matrix with varying values of rho.
+#                      rho = rho_range[i])
+# 
+#   lnRR_VCV_range[[i]] <- rma.mv(yi = lnRR_sign,
+#                                 V = VCV_range,
 #                                 random = list(~ 1 | paper_ID,
 #                                               ~ 1 | Observation_ID,
-#                                   ~ 1 | experiment_ID,
-#                                   ~ 1 | group_ID,
-#                                   ~ 1 | repeated_trait_ID),
+#                                               ~ 1 | group_ID_coded,
+#                                               ~ 1 | population_ID,
+#                                               ~ 1 | bird_species),
 #                                 method = "REML",
-#                                   data = dataset_lnRR # run the model with varying rho
-# )
+#                                 data = dataset_lnRR)
 # }
 # 
-# save(VCV_range, file = here::here("GNM/figures/VCV_range.Rdata"))
-# save(MLMAlnRR_VCV_range, file = here::here("GNM/figures/MLMAlnRR_VCV_range.Rdata"))
-
-```
-
-```{r Table for lnRR rho sensitivity analysis}
-
-# t4 <- data.frame(rho  = rho_range,
-#                  "overall effect"  = sapply(MLMAlnRR_VCV_range, function(x) coef(x)),
-#                  "standard error" = sapply(MLMAlnRR_VCV_range, function(x) x$se),
-#                  "p-value" = sapply(MLMAlnRR_VCV_range, function(x) x$pval),
-#                  "Lower CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.lb),
-#                  "Upper CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.ub),
-#                  "Log-likehood" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[1,1]),
-#                  "AIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[3,1]),
-#                  "BIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[4,1]),
-#                  "AICc" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[5,1]))
-# 
-# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
-# 
-# t4 %>% dfround(4) %>% DT::datatable()
+# 
+# save(SA_lnRR_VCV_range, file = here::here("model/sensitivity_analysis/SA_lnRR_VCV_range.rds"))
+# 
+# 
+# #------------------------------------------------------------------
+# #-------------Now for SMDH the same SA with diff Rho---------------
+# #------------------------------------------------------------------
+# 
+# SA_SMDH_VCV_range <- list()
+# 
+# for (i in 1:length(rho_range)){
+#   VCV_range <- vcalc(vi = SMDH_variance,
+#                      cluster = paper_ID,
+#                      obs = Observation_ID,
+#                      data = dataset_SMDH,
+#                      rho = rho_range[i])
+#   SA_SMDH_VCV_range[[i]] <- rma.mv(yi = SMDH_sign,
+#                                 V = VCV_range,
+#                                 random = list(~ 1 | paper_ID,
+#                                               ~ 1 | Observation_ID,
+#                                               ~ 1 | group_ID_coded,
+#                                               ~ 1 | population_ID,
+#                                               ~ 1 | bird_species),
+#                                 method = "REML",
+#                                 data = dataset_SMDH)
+# }
+# 
+# 
+# save(SA_SMDH_VCV_range, file = here::here("model/sensitivity_analysis/SA_SMDH_VCV_range.rds"))
+
 ```

### 2025-07-12 docs/manuscript_GNM.qmd
push to continue on laptop

@@
 An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
-This green nest material (GNM) ---leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species keep adding it even after the nest is finished.
-Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is thought to be selected from a small, non-random subset of local flora [@clark1985; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-Collecting and constantly replenishing GNM requires extra foraging flights, sometimes even outside the territory [@mennerat2009].
-The costs associated with nest building [@mainwaring2013], and these additional efforts suggest that GNM is unlikely to be gathered opportunistically and suggests a possible adaptive significance.
+This green nest material (hereafter GNM), which often corresponds to leaves, sprigs, herbs and branches, is typically added from the start of nest building until egg laying, although some species like the blue tit (Cyanistes cyanus), keep adding it even after the nest is finished.
+Importantly, contrary to the structural nest materials (e.g., twigs, mud), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @mennerat2009b) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some times weeks, requires extra time, and in some cases flying outside one’s territory [@mennerat2009].
+Thus, the general costs associated with nest-building [@mainwaring2013], and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
 
-Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
-First, the courtship hypothesis suggests that mostly males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy, particularly in cavity-nesting species since visual cues inside the nest are limited.
-This hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that (i) unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and seemingly increasing this behaviour in the presence of potential mates [@eens1993], and (ii) females often prefer nests with fresh GNM.
-The courtship hypothesis was later extended to explain GNM addition solely by females in species like Blue Tits (*Cyanistes caeruleus*), therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015) First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004)), particularly in cavity-nesting species where visual cues inside the nest are limited.
+The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (Sturnus vulgaris) carried fresh plant material to their nests while singing and displaying to females.
+Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993] The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
-Second, and the most widely tested one, is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
-This hypothesis traces back to a comparative study in raptors (Falconiformes) that proposed it and provided indirect evidence for it by comparing the nest reuse, diet composition and GNM presence [@wimberger1984].
-Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
-Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@dawson2004; @lafuma2001; @mennerat2009b; @quiroga2012] have shown mixed results, and in some cases, GNM has been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
-The drug hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
-Thus, while both hypotheses suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
-Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load.
+Second, the most widely tested hypothesis is the nest protection hypothesis, which proposes that the volatile compounds in GNM reduce the amount of parasites and pathogens in the nests, enhancing offspring survival.
+This hypothesis traces back to a comparative study in raptors (Falconiformes) that provided indirect evidence for it by comparing nest reuse, diet composition and GNM presence [@wimberger1984].
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; Clark and Mason 1988).
+Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@lafuma2001; @dawson2004; @mennerat2009b; @quiroga2012] have shown mixed results.
+In some cases, GNM was shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
+This alternative hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
+Thus, while both the nest protection and drug hypothesis suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load, something difficult to achieve.
 
-Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic properties have been proposed.
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic (i.e., volatiles and secondary metabolites) properties have been also proposed.
 These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], or simply fulfilling a structural function [@lyons1987].
@@
 In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
-Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and potentially far-reaching in its implications.
+Given that nest building is widespread across taxa —including but not limited to birds— and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
 
 To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
-Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e.
-combining both the nest protection and drug hypotheses due to their non-exclusivity).
-In addition, we explore the observed context-dependency (i.e., high heterogeneity among effect sizes) via meta-regressions.
-Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
-microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design (aromatic vs.
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e., a combination of both the nest protection and drug hypotheses).
+In addition, we tested several potential moderators that might explain the observed context-dependency (i.e., high heterogeneity among effect sizes).
+Specifically, we tested whether the effect of GNM varied depending on the experimental design used (aromatic vs.
 non-aromatic vs.
-no added material), the focal species, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
+no added material), the timing of GNM addition (before hatching, after hatching, or continuously), the focal species studied, the type of fitness proxy investigated (e.g., physiology, morphology, reproduction), and the type of parasite (arthropods vs.
+microorganisms).
 Our meta-analysis of experimental studies is the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
@@
 
-## Registration and Reporting
+## Registration and reporting
 
-We pre-registered our study protocol on Open Science Framework [@dimri2024] prior to data exploration and analysis.
+We pre-registered our study protocol on the Open Science Framework [@dimri2024] prior to data exploration and analysis.
 The pre-registration details our objectives, a priori hypotheses and predictions, methods and planned data analyses.
 Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist and @figsupp-prisma-flow).
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@tabsupp-checklist; @figsupp-prisma-flow).
 All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
@@
 
-We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022 (see update below).
-The keyword search query was designed as a three-block query to include terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
+We conducted a systematic search on Web of Science Core Collection and Scopus on the 7th of September, 2022 (see update below).
+The keyword search query was designed as a three-block query including terms related to our treatment of interest ((“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and to limit the search results to experimental studies only (“experiment\*” OR “manipulat\*”).
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
-We searched through titles, abstracts and keywords in English-language only with no restrictions on publication date or study type.
-We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, to confirm our keyword selection.
-After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 [@westgate2019], we found `{r} nrow(unique_reference_list)` unique records.
+Although our search string only included keywords in English, we planned to screen any study in English, Spanish, Portuguese and Hindi, but found none.
+We searched through titles, abstracts and keywords with no restrictions on publication date or study type.
+We validated our search using an initial library of 15 relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used the R package ‘litsearchr’ v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package ‘revtools’ v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
 
@@
 
-All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package `revtools` following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
+All titles and abstracts were equally allocated and screened independently by at least two screeners (SD, TR, JMGS) using the R package ‘revtools’ following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
 We included all studies on birds that experimentally manipulated the GNM (both aromatics or herbs).
 `{r} tools::toTitleCase(as.character(english::english(nrow(selected_abstract_screening))))` articles passed the title-and-abstract screening and were further evaluated during the full-text screening, where each article was independently screened by a single screener (SD, TR, JMGS), with another screener verifying the procedure.
-We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (see @figsupp-fitness-proxies).
-`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` passed the full-text screening and were, thus, eligible for our meta-analysis.
-All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
+We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (@figsupp-fitness-proxies).
+`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` articles passed the full-text screening, and were, thus, eligible for our meta-analysis.
+All conflicts in screening decisions (1% for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
 
-We updated our systematic literature search by repeating our search on 12.08.2024.
-We found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
-Only one observer (SD) performed the title-and-abstract and full-text screening using the same decision trees as before (@figsupp-decision-tree), and found `{r} sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)` additional eligible article for our meta-analysis.
-Lastly, we identified `{r} nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T))` additional eligible articles through other sources (i.e., identified through a poster by a collaborator and through an independent recommendation by a colleague).
-In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` articles were eligible for our meta-analysis (more details in @figsupp-prisma-flowchart).
+We updated our systematic literature search by repeating our search on the 12th of August, 2024, and found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
+Only one observer (SD) performed the both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
+Lastly, we identified `{r} as.character(english::english(nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)), 1, 1))` additional eligible articles recommended by two colleagues.
+In all, `{r} nrow(selected_abstract_screening)-nrow(excluded_fulltext)+nrow(selected_abstract_screening_repeat)` published articles were eligible for our meta-analysis, but we also obtained two additional unpublished studies (more details below and in @figsupp-prisma-flowchart).
 
-## Data Extraction
+## Data extraction
 
@@
 
+dataset_lnRR <- read_csv("data/04_data_analysis/dataset_lnRR.csv", show_col_types = F)
+
+dataset_SMDH <- read_csv("data/04_data_analysis/dataset_SMDH.csv", show_col_types = F)
+
+lnRR_comp3<-dataset_lnRR%>%filter(comparision_type==3)
+
+SMDH_comp3<-dataset_SMDH%>%filter(comparision_type==3)
+
+multiple_comparision <- dataset_analysis %>%
+group_by(paper_ID) %>%
+  summarise(n_types = n_distinct(comparision_type),             
+    types   = paste(sort(unique(comparision_type)), collapse = ", "),
+    .groups = "drop") %>%
+  filter(n_types > 1)
 ```
 
-The data of each article was extracted evenly by one of the three authors (SD, TR, JMGS), with another screener verifying the procedure.
-We prioritised extracting the primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package `metaDigitise` v.1.0.1 (@pick2018).
-If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), that could be transformed into an effect size.
-Last, if the previous steps failed but the article has openly shared datasets (n = `{r} length(raw_data)`), we calculated the means, SD and sample sizes from them.
-**When data was presented in different sources (e.g.
-in a boxplot and as an inferential statistics), we prioritized the source having the maximum resolution (the boxplot, in this example).**
+The data of each article were extracted evenly by one of three authors (SD, TR,  JMGS), with another screener verifying the procedure, and four authors (SD, TR, JMGS, AST) collectively discussing and revising unclear cases.
+We prioritised extracting primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package ‘metaDigitise’ v1.0.1 [@pick2018].
+If primary data were not available, we extracted inferential statistics such as *t* and *F* values or descriptive statistics such as contingency tables (see below), that could be transformed into an effect size.
+Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from them (n = `{r} length(raw_data)`).
 
-We extracted the means, variances and sample size for each control-treatment pairwise comparison.
-Controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material, or no material at all.
-Treatments consisted of aromatic materials added by authors, birds, or both.
-For cases that compared non-aromatic material to where authors did not add any additional nest material and any material added by the birds was removed, the non-aromatic material was considered the treatment.
-We recorded the type of comparison being made as a moderator.
-For each study, we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, or supplementary materials).
-We categorised the fitness proxies measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
+We extracted the means, variances and sample sizes for each control-treatment pairwise comparison.
+Depending on the experimental design of each study, controls included non-aromatic materials such as grass or moss, lesser amounts of aromatic material than the treatments, no additional material added, or removal of material added by birds; whereas treatments consisted of aromatic materials added by authors, birds, or both.
+Those comparisons were coded either as non-aromatic GNM vs.
+aromatic GNM, or no added GNM vs.
+aromatic GNM, in our moderator “experimental design”.
+However, there was a third type of comparison used in some studies comparing nests with experimentally added non-aromatic GNM to nests without any added GNM or in which GNM added by the birds was removed by the authors.
+In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these `{r} nrow(lnRR_comp3)` and `{r} nrow(SMDH_comp3)` effect sizes, respectively, as non-aromatic GNM vs.
+no added GNM in our moderator “experimental design”.
+Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator “experimental design” was used for subsequent meta-regressions.
+In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons.
+
+For each study, we also extracted information related to the study subjects (species of birds, geographical location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, supplementary materials).
+We categorised the fitness proxies measured into 6 broad categories: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
 For studies testing whether GNM affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
-For a complete list of variables extracted see @figsupp-variables .
-We did not include some traits in all our analyses because it was unclear how they related to fitness (k = `{r} nrow(excluded_proxies)` , n = `{r} length(unique(excluded_proxies$paper_ID))`; see @figsupp-excluded-proxies for the list and reasons of exclusion).
+For a complete list of variables extracted, see @figsupp-variables .
+We did not include some traits reported in the original studies (k = `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))` studies) in our analyses because it was unclear from the study and our own judgement how they related to fitness (see @figsupp-excluded-proxies).
 
-To obtain missing data (e.g., non-reported results, missing sample sizes, etc.), we contacted four authors.
+To obtain missing data (e.g., non-reported results, missing sample sizes), we contacted four corresponding authors.
 All four authors responded to our email, but only two provided the data as requested; one did not have the data any more, and one did not give a conclusive response.
-Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))`) to ask for any potential unpublished data that could be included in our meta-analysis.
-One corresponding author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of the authors of this study (MO), provided data for another unpublished study.
-In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
-Author correspondance was performed using a standardised email template (@figsupp-email).
-In all, we extracted data for `{r} length(unique(published_studies$paper_ID))` published articles (k = `{r} nrow(published_studies)`) and `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`).
+Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))` articles that passed full-text screening to ask for any potential unpublished data that could be included in our meta-analysis using a standardised email template (@figsupp-email).
+One author provided data for an unpublished study on Blue Tits (see description in @figsupp-unpublished-study) and one of us (MO), provided data for an unpublished study on Common Buzzards (Buteo buteo).
 
@@
 
-low_sample<-dataset_analysis%>%filter(is.na(SMDH_sign))
+low_sample<-read_csv("data/03_data_cleaning/low_sample.csv", show_col_types = F)
 
-dataset_lnRR <- read_csv("data/04_data_analysis/dataset_lnRR.csv", show_col_types = F)
-
-dataset_SMDH <- read_csv("data/04_data_analysis/dataset_SMDH.csv", show_col_types = F)
 ```
 
-We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` [@metafor].
-We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that positive values indicate the 'fitness' value increased in the treatment group.
-In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the effect size sign was inverted to ensure comparability across all fitness proxies.
-In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
-SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance— specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1 (excluded k = `{r} nrow(low_sample)`, n = `{r} length(unique(low_sample$paper_ID))`)
+Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package ‘metafor’ v4.8-0 [@metafor].
+We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a ‘fitness’ increase in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted prior to analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
+SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance; specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1.
+There were `{r} as.character(english::english(nrow(low_sample), 1, 1))` effect sizes from `{r} as.character(english::english(length(unique(low_sample$paper_ID)), 1, 1))`) study that did not fulfil that requirement, which we then excluded entirely from the dataset.
 
-For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) using the equations provided by @thehand2019.
-For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`, n = `{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
+For the few cases for which we could not extract means and variances but inferential statistics such as t and F values, we estimated SMD values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) using the equations provided by @thehand2019.
+For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the 'escalc' function (measure=OR) from 'metafor' and subsequently converted it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
 
-When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size, whenever possible to reduce the effect of genetic relatedness non-independence.
-In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
-For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k = `{r} nrow(no_ES)`, n = `{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparison and imputed its sampling variance using the missing-case approach described in @nakagawa2022 for lnRR and using $\frac{n_1+n_2}{n_1×n_2}$ for SMD [@lajeunesse2013].
+When calculating each effect size’s associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
+In cases where the same control or treatment group was used across multiple comparisons, sample sizes were adjusted prior to calculating effect sizes by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
+For cases where the authors of an original article reported a statistically non-significant difference between two groups but without providing numerical values (k = `{r} nrow(no_ES)`, n = `{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparison and imputed its sampling variance using the missing-case approach described in @nakagawa2022 for lnRR and using $\frac{n_1+n_2}{n_1×n_2}$ for SMD [@lajeunesse2013].
 
-## Data Analysis
+## Data analysis
 
 We performed all analyses in R version 4.5.1 [@R-version].
-All multilevel meta-analytical models and meta-regressions were fit using metafor v.4.8-0 [@metafor].
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the vcalc function from metafor.
-(See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
+All multilevel meta-analytical models and meta-regressions were fitted using ‘metafor’ v.4.8-0 [@metafor].
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from ‘metafor’ (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
-We considered the following levels of non-independence for our analyses: multiple effect sizes collected from (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g.
-birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; eg.
-males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g.
-chick mass on day 7, 14 and 21).
+We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
 
 Unless stated otherwise, we fitted the following random effects in all our models to account for non-independence: Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
-Our random effect structure deviated from our pre-registration since, initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
-However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution i.e.
+Our random effect structure deviated from our pre-registration since, initially, we had pre-registered the inclusion of Experiment ID and Repeated trait ID but not Population ID.
+However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution, i.e.
 Experiment ID.
-Additionally, few effect sizes were measured repeatedly, making the Repeated trait ID almost identical to the observation-level random effect (Observation ID), so we excluded it (@figsupp-random-effect).
-Last, we decided to add Population ID, since we noticed that several studies were performed in the same geographical locations.
+Additionally, since few effect sizes were measured repeatedly, making Repeated trait ID almost identical to the observation-level random effect Observation ID, we excluded it (@figsupp-random-effect).
+Last, we decided to add Population ID since we noticed after extracting the data but before any analyses that several studies were performed in the same geographical locations.
 
-### Meta-analytic models: biological predictions
+### Meta-analytic mean and hypotheses
 
-To estimate the effect of GNM addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
+To estimate the effect of GNM on fitness across birds, we used two effect sizes: lnRR and SMD(H).
 Thus, throughout, we fitted two separate sets of model for each effect size.
 First, we fitted multilevel intercept-only meta-analytical model to test the overall effect, its uncertainty and heterogeneity.
-We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g.
-sex ratio, testosterone levels, etc.), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
-For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
+We used the `rma.mv` function from the 'metafor' package using the 'REML' method and a *t* distribution for calculating the test statistics and confidence intervals for the moderators.
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
+For all intercept-only models, we estimated the total amount of absolute heterogeneity ($σ^2$; the total variation not explained by sampling error), its sources or relative heterogeneity ($I^2$), mean-standardised metric (CVH2) and variance-mean-standardised metric of heterogeneity (M2) following the pluralistic approach suggested by @yang2024a .
 
-<!--# Check what is MLMA-excluded and figsupp-SAonly-proxies for figures and decide which one makes more sense to include/exclude?? -->
+To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator ‘hypothesis’ (levels: courtship, parental care, both).
+For this and all meta-regressions, we estimated $R_{marginal}^2$,which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
+Unless stated otherwise, all meta-regressions correspond to unimoderator meta-regressions.
 
-To test the relative importance of the two main hypotheses suggested for GNM: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
-For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
-
-### Meta-analytic models: exploratory analyses
+### Exploratory meta-regressions
 
@@
 
-We performed additional pre-registered multi-level meta-regressions for which we did not have clear or strong directional predictions on specific subsets of data.
-To understand the effect of GNM on the parasite load depending on the type of parasites, we used effect sizes on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`).
-We ran a meta-regression with a type of parasite as a moderator (levels: arthropod, micro-organism).
-We also ran a meta-regression with the entire dataset set using bird species as a moderator (levels: *Buteo buteo*, *Cyanistes caeruleus*, *Passer cinnamomeus*, *Parus major*, *Sturnus unicolor*, *Sturnus vulgaris*, *Tachycineta bicolor*) to understand if the effect of GNM on fitness depended on the system being studied.
-To test the effect of time of addition of GNM on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with Time of addition of GNM as the moderator.
-We explored the effect of GNM on fitness depending on the type of trait studies (levels: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.
-We explored the impact of methodological differences on the relationship between GNM and fitness.
-To understand the effect of type of experimental design (i.e.
-whether the authors compared - non-aromatic vs.
+We performed additional pre-registered multilevel meta-regressions for which we did not have clear or strong directional predictions.
+To understand the effect of type of experimental design (i.e., whether the authors compared non-aromatic vs.
 aromatic, no added material vs.
 aromatic, no added material vs.
-non-aromatic), we ran a meta-regression with the type of experimental design as a moderator.
+non-aromatic), we ran a meta-regression with the type of experimental design as the moderator.
+To test the effect of time of addition of GNM on fitness (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase), we ran a meta-regression with time of addition of GNM as the moderator.
+We also ran a meta-regression using bird species as the moderator (levels: Buteo buteo, Cyanistes caeruleus, Passer cinnamomeus, Parus major, Sturnus unicolor, Sturnus vulgaris, Tachycineta bicolor) to understand if and how the effect of GNM on fitness might differ among species.
+Furthermore, we explored the effect of GNM on fitness depending on the type of trait (i.e., fitness proxy) studied (levels: behaviour, morphology, parasite and pathogenic load, phenology, physiology, reproduction) using a meta-regression with the trait type as the moderator.
+Last, for the subset focusing on parasites and pathogens (k = `{r} nrow(parasite_pathogen)`, n = `{r} length(unique(parasite_pathogen$paper_ID))`)), we ran a meta-regression with the type of parasite as the moderator (levels: arthropod, micro-organism).
+
+In addition, we performed X additional multilevel meta-regressions intended to explore the potential threats to the internal validity of each study on our conclusions (i.e., Risk of Bias or RoB) following recommendations in Culina et al.
+(2025).
+…
 
@@
 
-Publication bias occurs when a subset of research findings, most often statistically non-significant ones, are less likely to be published or being published as compared to the rest.
-We tested for evidence of publication bias, both small-study and decline effects following @nakagawa2021.
-Publication bias tests were performed for both lnRR and SMD(H) separately, and using the same random effect structure as reported above.
-To test for small-study effects, we ran a multilevel meta-regression, using the inverse of the effective sample size as a moderator.
-To test for decline effects (also known as time-lag bias; @sanchez-tojar2018), we ran multilevel meta-regression year of publication (mean-centered) as a moderator.
+Publication bias occurs when a subset of research findings, most often statistically non-significant ones, are less likely to be published or published later [@Jennisons2013].
+ There are two types of publication biases found to be commonplace in ecology and evolutionary biology: small-study and decline effects [@yang2023].
+We tested them for both lnRR and SMD(H) separately, following @nakagawa2022a.
+To test for small-study effects, we ran a multilevel meta-regression using the inverse of the effective sample size as the moderator.
+To test for decline effects (also known as time-lag bias; @sanchez-tojar2018), we ran a multilevel meta-regression using year of publication (mean-centered) as the moderator.
 
@@
 
-```{r review-results}
+```{r review-results, include=FALSE, echo=FALSE}
 
@@
 
-We obtained `{r} nrow(dataset_analysis)` effect sizes from `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@fig-distribution).
+We obtained `{r} nrow(dataset_analysis)` effect sizes from a total of `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@figmain-distribution).
 About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
 Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean (±SD) number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the median and mean effective sample size (i.e.
-after accounting for shared-group non-independence) were `{r} sprintf("%.1f", median(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))` and `{r} sprintf("%.1f",mean(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment)))`, respectively (range: `{r} min(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`--`{r} max(c(dataset_analysis$effective_n_control,dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
+The mean ±standard deviation number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`, range: `{r} min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`--`{r} max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
 
-![**Geographical distribution of the 16 study population in this meta-analysis:** Point size reflects the number of effect sizes coming from the location and colour denotes species (see legend), with an inset zooming on the cluster of distribution.](figures/Figure_Distribution.png){#fig-distribution}
+![**Geographical distribution of the 17 study populations included in a meta-analysis testing the adaptive value of green nest material in birds**.Point size reflects the number of effect sizes coming from the location (range: 3 - 34 effect sizes), and colour denotes species (see legend), with an inset zooming on a dense cluster of data points.](figures/Figure_Distribution.png){#figmain-distribution}
 
-## **Overall effect of green nest material on fitness proxies**
+## **Meta-analytic mean**
 
-```{r overall-results}
+```{r overall-results, include=FALSE, echo=FALSE}
 intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
@@
 
-Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness in the nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness outcomes in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
-First, the model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM \[@fig-mean-effect (A); lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high variability across effect sizes.
-Second, the model using SMD(H) showed a small positive and statistically significant effect of an experimental increase of GNM on fitness \[@fig-mean-effect (B); SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
-For lnRR, these heterogeneity metrics exceeded the 75th percentile benchmark (see @supp-tab-heterogeneity for detailed estimates of heterogeneity).
+First, lnRR showed an average statistically non-significant increase in fitness outcomes of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM (@figmain-mean-effect A; lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`) but heterogeneity among effect sizes was high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
 
-As a pre-registered sensitivity analysis, we fitted a bivariate multilevel meta-analytic model including both the effect sizes.
-While neither intercept was statistically significant, the results strengthen the interpretation that any effect of GNM on fitness outcomes is likely small at best \[lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`\].
+Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM (@figmain-mean-effect B; SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`), but heterogeneity among effect sizes was moderate to high.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see [@supp-tab-heterogeneity] for detailed estimates of heterogeneity).
 
-![**Overall effect of green nest material on all fitness proxies combined:** Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
-Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
-k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png){#fig-mean-effect}
+These overall results, and their conclusions were robust to several sensitivity analyses.
+First, we fitted a pre-registered bivariate multilevel meta-analytic model including both effect sizes as response variables (lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`).
+In addition, we ran several sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was unclear (non-pre-registered), (ii) the removal effect sizes that were originally reported as simply statistically non-significant (non-pre-registered), (iii) both (i) and (ii) (non-pre-registered), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
+The number of effect sizes included in those sensitivity analyses ranged from 182 to 274 effect sizes, and the conclusions remained largely the same [@tabsupp-SA-intercept].
 
-## **Mechanistic Hypotheses: explaining the effect of Green Nest Material**
+![**Overall effect of green nest material on all fitness proxies combined.** The meta-analytic mean (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio (lnRR), and (B) standardised mean difference (SMD(H)).
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section \[\@figsupp-overall\] for complete figures).](figures/Figure_overall_effect_crop.png){#figmain-mean-effect}
 
-```{r hypotheses-results}
+## **Mechanistic Hypotheses**
+
+```{r hypotheses-results, include=FALSE, echo=FALSE}
 lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
@@
 summary_SMDH_hypothesis<-extractor_metareg(SMDH_hypothesis,"Hypothesis")
+
+lnRR_hypothesis_pc<-readRDS(here::here("model/lnRR_hypothesis_pc.rds"))
+SMDH_hypothesis_pc<-readRDS(here::here("model/SMDH_hypothesis_pc.rds"))
+
+summary_lnRR_hypothesis_pc<-extractor_metareg(lnRR_hypothesis_pc,"Hypothesis")
+summary_SMDH_hypothesis_pc<-extractor_metareg(SMDH_hypothesis_pc,"Hypothesis")
+
+summary(lnRR_hypothesis_pc)
+car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
+summary(SMDH_hypothesis_pc)
+car::linearHypothesis(SMDH_hypothesis_pc, rbind(c(0,1,-1)))
 ```
 
-Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@fig-hypothesis]).
-There was a small positive but statistically non-significant average effect of GNM on fitness related to courtship efforts and investment (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\].
-The estimates were even smaller for the protective effect or health benefits for nestlings as proposed by the nest protection and drug hypothesis \[lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, CI: ``` {r}``summary_lnRR_hypothesis$CI[3] ```, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\].
-Our meta-regression contained a third category that included effect sizes that could not be clearly assigned to either hypothesis.
-We found a small positive effect which was statistically significant only in the case of SMD(H) \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
-The moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@figmain-hypothesis]).
+The estimates for the courtship hypothesis (lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[2]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]`; SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[2]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`), and the nest protection and drug hypothesis (i.e., "parental care hypothesis") (lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[3]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]`; SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[3]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`) were statistically non-significant.
+However, notice that about half of all effect sizes could not be unequivocally assigned to only one hypothesis, so our meta-regression contained a third category that combined both.
+This category showed an average positive increase in fitness outcomes in nests with an experimental increase of GNM, but the effect was only statistically significant for SMD(H) (lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[1]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]`; SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[1]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`).
+None of the three categories differed statistically significantly from each other (${p-value}_{lnRR)}$ \> 0.211 and ${p-value}_{SMD(H)}$ \> 0.178 in all cases), and the moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
 
-![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests.
-Orchard plot of the multilevel meta-regression for A.
-log response ratio (lnRR) and B.
-Standardized mean difference (SMD(H)).
-Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
-k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}
+![**There is no clear evidence to favour either the courtship or the parental care hypothesis as drivers of potential fitness benefits of green nest material.** Orchard plot of the multilevel meta-regression for (A) log response ratio (lnRR) and (B) standardised mean difference (SMD(H)).
+Mean estimates (large circles), 95% confidence intervals (thicker bars), and prediction intervals (thinner bars) are shown along with the individual data points (transparently coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section [@figsupp-hypothesis] for complete figures).](figures/Figure_hypothesis_crop.png){#figmain-hypothesis}
 
-## What other factors explain heterogeneity among effect sizes?
+## Exploratory meta-regressions
 
-```{r}
+```{r include=FALSE, echo=FALSE}
 # Loading models for parasite type
@@
 
+# Now pair-wise comparison model for time of green nest material addition
+lnRR_time_gnm_addition_pc<-readRDS(here::here("model/lnRR_time_gnm_addition_pc.rds"))
+SMDH_time_gnm_addition_pc<-readRDS(here::here("model/SMDH_time_gnm_addition_pc.rds"))
+
+summary(lnRR_time_gnm_addition_pc)
+car::linearHypothesis(lnRR_time_gnm_addition_pc, rbind(c(0,1,-1)))
+summary(SMDH_time_gnm_addition_pc)
+car::linearHypothesis(SMDH_time_gnm_addition_pc, rbind(c(0,1,-1)))
+
+#---------------------------------------------------------------------------
+#---------------------------------------------------------------------------
+#---------------------------------------------------------------------------
+
 # Loading models for experimental design
@@
 summary_SMDH_design<- extractor_metareg(SMDH_design,"comparision_type")
+
+## Now pair-wise comparison
+lnRR_design_pc<-readRDS(here::here("model/lnRR_design_pc.rds"))
+SMDH_design_pc<-readRDS(here::here("model/SMDH_design_pc.rds"))
+
+summary(lnRR_design_pc)
+car::linearHypothesis(lnRR_design_pc, rbind(c(0,1,-1)))
+summary(SMDH_design_pc)
+car::linearHypothesis(SMDH_design_pc, rbind(c(0,1,-1)))
 ```
 
-Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several multilevel meta-regressions.
-First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design.
-The overall effect size for the comparison between no added material and aromatic material was positive and statistically significant \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, it was negative for the comparison between no added material and non-aromatic material statistically significantly so lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
-Last, the comparison between non-aromatic and aromatic material showed a small negative statistically non-significant effect \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMD(H)~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
-The moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
+Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several additional multilevel meta-regressions.
 
-Second, when GNM was added continuously throughout the nesting phase, its overall effect was positive and statistically significant, at least for SMD(H) \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
-compared to its addition before or after egg hatching \[[\@fig-MR](C-D); Table X\].
-Timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
+![**Experimental designs comparing nests with aromatic green nest material against nests without any green material, and those adding the material continuously, lead to the larger fitness effects.** Orchard plots of the multilevel meta-regressions showing the overall effect of green nest material depending on experimental design for (A: log response ratio (lnRR); B: standardized mean difference (SMD(H)), and time of green nest material addition (C: log response ratio (lnRR); D: standardized mean difference (SMD(H)).
+Mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars), are shown along the individual data points (transparently coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section [@figsupp-design-time] for complete figures).](figures/Figure_design_time_gnm_addition_cropped.png){#figmain-design-time}
 
-![Orchard plot showing overall effect of green nest material depending on the multilevel meta-regression for experimental design for - A.
-log response ratio (lnRR) and B.
-Standardized mean difference (SMD(H)) and time of GNM addition for - C.
-log response ratio (lnRR) and D.
-Standardized mean difference (SMD(H)).
-Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
-k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_design_time_gnm_addition.png){#fig-MR}
+First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design used ([@figmain-design-time]A,B).
+The overall effect size for the comparison between no added material and aromatic GNM was positive and statistically significant (lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, 95% CI: `{r} summary_lnRR_design$CI[2]`, 95% PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, 95% CI: `{r} summary_SMDH_design$CI[2]`, 95% PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, the comparison between non-aromatic GNM and aromatic GNM was small and statistically non-significant ([@tabmain-MLMR]).
+The latter suggests that, despite not being considered in the hypotheses, non-aromatic GNM could also play some role; however, the comparison between no added material and non-aromatic GNM, was negative and, although based on only 3 studies, statistically significantly so for lnRR (lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, 95% CI: `{r} summary_lnRR_design$CI[3]`, 95% PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]`;[@tabmain-MLMR]).
+ All levels but one differed statistically significantly (${p-value}_{lnRR}$ \< 0.004 and ${p-value}_{SMD(H)}$ \< 0.001 in all cases, except  ${SMD(H)}_{no-material-vs-aromatic}$ vs.
+${SMD(H)}_{no-material-vs-non-aromatic}$ p-value = 0.140), and the moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
 
-Third, there was a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
-\[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
-The type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+Second, the overall positive effect of GNM on fitness outcomes tended to be larger when GNM was added continuously throughout the nesting phase ([@figmain-design-time]C,D).
+The overall effect was positive and statistically significant so for SMD(H) when material was continuously and experimentally added to the nest (lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`), whereas the effect was small and statistically non-significant when added before egg hatching [@tabmain-MLMR].
+Last, the overall effect also tended to be positive for SMD(H) when GNM was added after egg hatching only, although only marginally so (SMD(H)~after_egg_hatching~ = `{r} summary_SMDH_time_gnm_addition$estimate[1]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[1]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[1]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[1]`, k = `{r} summary_SMDH_time_gnm_addition$k[1]`, n = `{r} summary_SMDH_time_gnm_addition$n[1]`; [@tabmain-MLMR]).
+The three categories did not differ statistically significantly from each other (p-value~lnRR~ \> 0.307 and p-value~SMD(H)~ \> 0.243 in all cases).
+The timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
 
-Fourth, the bird species had a small positive statistically non-significant increase with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
-However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+![](tables/MLMR_table.png){#tabmain-MLMR}
 
-Lastly, among different types of fitness trait, only morphological trait had a positive effect of GNM on fitness, which was statistically significant for SMD(H) \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
-Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
-All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
-Trait type accounted for some of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Third, Third, although none of the species-specific mean estimates were statistically significant, most were positive [[\@figsupp-MR](C-D); @tabmain-MLMR], and bird species identity explained a non-negligible amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant and reproduction marginally so, both only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; SMDH~reproduction~ = `{r} summary_SMDH_trait$estimate[6]`, 95% CI: `{r} summary_SMDH_trait$CI[6]`, 95% PI: `{r} summary_SMDH_trait$PI[6]`, p-value = `{r} summary_SMDH_trait$p_value[6]`, k = `{r} summary_SMDH_trait$k[6]`, n = `{r} summary_SMDH_trait$n[6]`) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Last, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically signficantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
 
@@
 
-Contrary to long-standing verbal models, neither the courtship hypothesis (visual/olfactory signalling) nor the parental-care hypothesis (parasite repellency or pharmacological “drug” effects) emerged as a consistent driver of these small gains.
+Contrary to long-standing verbal models, neither the courtship hypothesis (visual/olfactory signalling) nor the parental-care hypothesis (parasite repellency or pharmacological "drug" effects) emerged as a consistent driver of these small gains.
 Effect estimates associated with courtship traits were positive but non-significant, and those associated with nestling protection were essentially zero.
 In other words, current evidence does not allow us to attribute the weak average benefit of GNM to a single prevailing mechanism.
-This result mirrors the idiosyncratic outcomes scattered through the primary literature and indicates that future tests will need to measure multiple pathways simultaneously—ideally pairing behavioural observations with direct assays of ectoparasites, microbial load, and nest-air volatiles.
+This result mirrors the idiosyncratic outcomes scattered through the primary literature and indicates that future tests will need to measure multiple pathways simultaneously---ideally pairing behavioural observations with direct assays of ectoparasites, microbial load, and nest-air volatiles.
 
@@
 The discrepancy between metrics underscores how the inferred magnitude of benefit depends on the underlying scale: lnRR captures proportional shifts, whereas SMDᴴ reflects absolute shifts that are sensitive to among-study variance.
-Nonetheless, both converge on the same biological interpretation—if GNM is adaptive, the advantage appears subtle rather than dramatic, and it is expressed against a backdrop of substantial heterogeneity (I² ≈ 66–99 %).
+Nonetheless, both converge on the same biological interpretation---if GNM is adaptive, the advantage appears subtle rather than dramatic, and it is expressed against a backdrop of substantial heterogeneity (I² ≈ 66--99 %).
 
@@
 non-aromatic** comparison was indistinguishable from zero.
-These patterns emphasise that simply adding any material can alter micro-climate, and that the perceived “aromatic benefit” may in part reflect removing a structural disadvantage in controls rather than an odour-specific mechanism.
+These patterns emphasise that simply adding any material can alter micro-climate, and that the perceived "aromatic benefit" may in part reflect removing a structural disadvantage in controls rather than an odour-specific mechanism.
 In addition, time of addition mattered: experiments that replenished GNM continuously throughout nesting detected stronger benefits (significant under SMDᴴ) than those adding it only before or after hatching, hinting that persistence of volatile release or parental display may be important [manuscript_GNM]{.underline}.
@@
 Experimental design alone accounted for roughly a third of total variance, whereas parasite type, trait category, timing, and species identity each explained ≤ 8 % [manuscript_GNM]{.underline}.
-The residual scatter likely stems from taxonomic and geographic bias—82 % of effect sizes come from just three passerines (blue tit, spotless starling, European starling) studied at 16 sites, many of them by the same research groups.
+The residual scatter likely stems from taxonomic and geographic bias---82 % of effect sizes come from just three passerines (blue tit, spotless starling, European starling) studied at 16 sites, many of them by the same research groups.
 Publication-bias diagnostics were equivocal, yet small-study effects cannot be excluded given the prevalence of datasets with ≤ 5 nests per group and the tendency to publish novel positive outcomes.
@@
 non-aromatic) and track volatilome dynamics across the nesting cycle.
-Second, fitness proxies should move beyond morphology—currently the only trait category with a significant positive response—to harder endpoints such as fledging success, juvenile recruitment, and parental survival.
+Second, fitness proxies should move beyond morphology---currently the only trait category with a significant positive response---to harder endpoints such as fledging success, juvenile recruitment, and parental survival.
 Third, sharing raw data and negative results will be essential to reduce residual heterogeneity and clarify whether the modest average benefit we detect is biologically meaningful or a statistical artefact of design choices.
@@
 
-```{r results='asis'}
-cat(readLines("tables/SA_intercept_only.html"), sep ="\n")
-```
-
-```{r results='asis'}
-cat(readLines("tables/EA_MLMR_table.html"), sep ="\n")
-```
-
-![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
-
-### PRISMA Checklist
+# PRISMA Checklist
 
@@
 
-::: {#figsupp-checklist .table}
+::: {#tabsupp-checklist .table}
 |  |  |  |  |  |  |
@@
 
+### Plots with complete dataset (without cropping the plots)
+
 ![](figures/Figure_parasite_birds_trait.png)
+
+![Overall effect of green nest material on all fitness proxies combined: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (transparent coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
+k: number of effect sizes (number of studies is shown in the brackets)](figures/Figure_overall_effect.png)
+
+![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as potential drivers of fitness benefits from green nest material in nests.
+Orchard plot of the multilevel meta-regression for A.
+log response ratio (lnRR) and B.
+Standardized mean difference (SMD(H)).
+Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#figsupp-hypothesis width="1035"}
+
+# All sensitivity-analysis/robustness check
+
+![](tables/SA_intercept_only.png){#tabsupp-SA-intercept}
+
+# Maybe-maybe stuff
+
+![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
+
+###

### 2025-07-12 manuscript_GNM.qmd
push to continue on laptop

@@
 An intriguing nesting behaviour observed in some bird species is the addition of fresh, often aromatic, plant material to the nest.
-This green nest material (hereafter GNM) --- which often corresponds to leaves, sprigs, herbs and branches--- is typically added from the start of nest building until egg laying, although some species like blue tit *(Cyanistes cyanus)*, keep adding it even after the nest is finished.
-Importantly, contrary to the structural nest materials (e.g., twigs, branches), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @clark1985) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some time weeks, requires extra time, and some cases flying outside one's territory [@mennerat2009].
-Thus, the general costs associated with nest building [@mainwaring2013], and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
+This green nest material (hereafter GNM), which often corresponds to leaves, sprigs, herbs and branches, is typically added from the start of nest building until egg laying, although some species like the blue tit (Cyanistes cyanus), keep adding it even after the nest is finished.
+Importantly, contrary to the structural nest materials (e.g., twigs, mud), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @mennerat2009b) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
+GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some times weeks, requires extra time, and in some cases flying outside one’s territory [@mennerat2009].
+Thus, the general costs associated with nest-building [@mainwaring2013], and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
 
-Several hypotheses have been proposed to explain the adaptive function of GNM [@dubiec2013; @scott-baumann2015].
-First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females or advertise nest site occupancy to other males [@eens1993; @gwinner1997; @brouwer2004], particularly in cavity-nesting species where visual cues inside the nest are limited.
-The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (*Sturnus vulgaris*) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in both European and Spotless Starlings (*Sturnus unicolor*) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993].
-The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015) First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004)), particularly in cavity-nesting species where visual cues inside the nest are limited.
+The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (Sturnus vulgaris) carried fresh plant material to their nests while singing and displaying to females.
+Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993] The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
@@
 This hypothesis traces back to a comparative study in raptors (Falconiformes) that provided indirect evidence for it by comparing nest reuse, diet composition and GNM presence [@wimberger1984].
-Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1988).
-Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@lafuma2001; @dawson2004; @mennerat2009b; @quiroga2012] have shown mixed results in some cases, GNM was been shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; Clark and Mason 1988).
+Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@lafuma2001; @dawson2004; @mennerat2009b; @quiroga2012] have shown mixed results.
+In some cases, GNM was shown to improve offspring condition without reducing the amount of parasites in the nests [@gwinner2000], which led to the development of the drug hypothesis.
 This alternative hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
@@
 In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
-Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
+Given that nest building is widespread across taxa —including but not limited to birds— and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
 
 To address this gap, we conducted a pre-registered systematic review and meta-analysis of experiments testing the effect of GNM on various fitness proxies across birds.
-Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e.
-combination of both the nest protection and drug hypotheses).
+Our meta-analysis explicitly evaluates the overall evidence for the adaptive significance of GNM, as well as assesses the relative importance of the main suggested hypotheses: the courtship hypothesis and parental care hypothesis (i.e., a combination of both the nest protection and drug hypotheses).
 In addition, we tested several potential moderators that might explain the observed context-dependency (i.e., high heterogeneity among effect sizes).
-Specifically, we tested whether the effect of GNM varied depending on the type of parasite (arthropods vs.
-microorganisms), the timing of GNM addition (before hatching, after hatching, or continuously), the experimental design used (aromatic vs.
+Specifically, we tested whether the effect of GNM varied depending on the experimental design used (aromatic vs.
 non-aromatic vs.
-no added material), the focal species studied, and the type of fitness proxy investigated (e.g., physiology, morphology, reproduction).
+no added material), the timing of GNM addition (before hatching, after hatching, or continuously), the focal species studied, the type of fitness proxy investigated (e.g., physiology, morphology, reproduction), and the type of parasite (arthropods vs.
+microorganisms).
 Our meta-analysis of experimental studies is the first quantitative synthesis testing the causal relationship between GNM and fitness across birds.
@@
 
-## Registration and Reporting
+## Registration and reporting
 
@@
 Unless stated otherwise, we adhered to the registered protocol.
-We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@figsupp-checklist and @figsupp-prisma-flow).
+We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (@tabsupp-checklist; @figsupp-prisma-flow).
 All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).
@@
 
-We conducted a systematic search on Web of Science Core Collection and Scopus on 07.09.2022 (see update below).
-The keyword search query was designed as a three-block query including terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
+We conducted a systematic search on Web of Science Core Collection and Scopus on the 7th of September, 2022 (see update below).
+The keyword search query was designed as a three-block query including terms related to our treatment of interest ((“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and to limit the search results to experimental studies only (“experiment\*” OR “manipulat\*”).
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
@@
 We searched through titles, abstracts and keywords with no restrictions on publication date or study type.
-We validated our search using an initial library of `{r} nrow(own_library)` relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
-After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using R package 'revtools' v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
+We validated our search using an initial library of 15 relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
+Additionally, we used the R package ‘litsearchr’ v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package ‘revtools’ v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
 
@@
 
-All titles and abstracts were equally allocated and screened independently by atleast two screeners (SD, TR, JMGS) using the R package 'revtools' following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
+All titles and abstracts were equally allocated and screened independently by at least two screeners (SD, TR, JMGS) using the R package ‘revtools’ following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
 We included all studies on birds that experimentally manipulated the GNM (both aromatics or herbs).
@@
 We used the same criteria as above (@figsupp-decision-tree) with an additional evaluation of whether the variable of interest in the article was in our list of fitness proxies of interest (@figsupp-fitness-proxies).
-`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` passed the full-text screening and were, thus, eligible for our meta-analysis.
-All conflicts in screening decisions (\~1% disagreement for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
+`{r} paste0(toupper(substring(x <- as.character(english::english(nrow(selected_abstract_screening) - nrow(excluded_fulltext))), 1, 1)), substring(x, 2))` articles passed the full-text screening, and were, thus, eligible for our meta-analysis.
+All conflicts in screening decisions (1% for title-and-abstract screening, and none for full-text screening) were resolved through discussion.
 
-We updated our systematic literature search by repeating our search on the 12th of August, 2024 and found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
-Only one observer (SD) performed both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
+We updated our systematic literature search by repeating our search on the 12th of August, 2024, and found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
+Only one observer (SD) performed the both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
 Lastly, we identified `{r} as.character(english::english(nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)), 1, 1))` additional eligible articles recommended by two colleagues.
@@
 
-## Data Extraction
+## Data extraction
 
@@
 
+dataset_lnRR <- read_csv("data/04_data_analysis/dataset_lnRR.csv", show_col_types = F)
+
+dataset_SMDH <- read_csv("data/04_data_analysis/dataset_SMDH.csv", show_col_types = F)
+
+lnRR_comp3<-dataset_lnRR%>%filter(comparision_type==3)
+
+SMDH_comp3<-dataset_SMDH%>%filter(comparision_type==3)
+
+multiple_comparision <- dataset_analysis %>%
+group_by(paper_ID) %>%
+  summarise(n_types = n_distinct(comparision_type),             
+    types   = paste(sort(unique(comparision_type)), collapse = ", "),
+    .groups = "drop") %>%
+  filter(n_types > 1)
 ```
 
-The data of each article ware extracted evenly by one of three authors (SD, TR, JMGS), with another screener verifying the procedure, and four authors (SD, TR, JMGS, AST) collectively discussing and revising unclear cases.
-We prioritised extracting the primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package `metaDigitise` v.1.0.1 (@pick2018).
-If primary data were not available, we extracted inferential statistics such as *t* and *F* values (k = `{r} nrow(inferential_only)`effect sizes, n = `{r} length(unique(inferential_only$paper_ID))`) or descriptive statistics such as contingency tables (k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))` studies), that could be transformed into an effect size.
-Last, if the previous steps failed but the article had openly archieved data, we calculated the means, SD and sample sizes from them (n = `{r} length(raw_data)`).
+The data of each article were extracted evenly by one of three authors (SD, TR,  JMGS), with another screener verifying the procedure, and four authors (SD, TR, JMGS, AST) collectively discussing and revising unclear cases.
+We prioritised extracting primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package ‘metaDigitise’ v1.0.1 [@pick2018].
+If primary data were not available, we extracted inferential statistics such as *t* and *F* values or descriptive statistics such as contingency tables (see below), that could be transformed into an effect size.
+Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from them (n = `{r} length(raw_data)`).
 
@@
 aromatic GNM, or no added GNM vs.
-aromatic GNM, in our moderator "experimental design".
+aromatic GNM, in our moderator “experimental design”.
 However, there was a third type of comparison used in some studies comparing nests with experimentally added non-aromatic GNM to nests without any added GNM or in which GNM added by the birds was removed by the authors.
-In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these effect sizes as non-aromatic GNM vs.
-no added GNM in our moderator "experimental design".
-The moderator "experimental design" was used for subsequent meta-regressions.
-For each study, we also extracted information related to the study subjects (species of birds, location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, or supplementary materials).
-We categorised the fitness proxies measured into 6 broad categories - physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
+In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these `{r} nrow(lnRR_comp3)` and `{r} nrow(SMDH_comp3)` effect sizes, respectively, as non-aromatic GNM vs.
+no added GNM in our moderator “experimental design”.
+Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator “experimental design” was used for subsequent meta-regressions.
+In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons.
+
+For each study, we also extracted information related to the study subjects (species of birds, geographical location of the study population), the methodology of the study (plant species used as treatment and control, fitness proxy measured) and the source from which we extracted data (e.g., figures, tables, raw data files, supplementary materials).
+We categorised the fitness proxies measured into 6 broad categories: physiology, morphology, reproduction, behaviour, parasite and pathogenic load, and phenology.
 For studies testing whether GNM affects the number of parasites or pathogens found in offspring and/or nests, we categorised them into arthropods or microorganisms.
-For a complete list of variables extracted see @figsupp-variables .
-We did not include some traits reported in the original studies in all our analyses because it was unclear from the study and our own judgement how they related to fitness (k = `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))`; studies see @figsupp-excluded-proxies for the list and reasons of exclusion).
+For a complete list of variables extracted, see @figsupp-variables .
+We did not include some traits reported in the original studies (k = `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))` studies) in our analyses because it was unclear from the study and our own judgement how they related to fitness (see @figsupp-excluded-proxies).
 
-To obtain missing data (e.g., non-reported results, missing sample sizes), we contacted four authors.
+To obtain missing data (e.g., non-reported results, missing sample sizes), we contacted four corresponding authors.
 All four authors responded to our email, but only two provided the data as requested; one did not have the data any more, and one did not give a conclusive response.
-Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the articles that passed full-text screening (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))` studies) to ask for any potential unpublished data that could be included in our meta-analysis.
-One author provided data for an unpublished study (see description in @figsupp-unpublished-study) and one of us (MO), provided data for another unpublished study.
-In all, we extracted data for `{r} included_papers_no - 2` published articles and 2 unpublished studies.
-Author correspondance was performed using a standardised email template (@figsupp-email).
+Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))` articles that passed full-text screening to ask for any potential unpublished data that could be included in our meta-analysis using a standardised email template (@figsupp-email).
+One author provided data for an unpublished study on Blue Tits (see description in @figsupp-unpublished-study) and one of us (MO), provided data for an unpublished study on Common Buzzards (Buteo buteo).
 
@@
 
-low_sample<-dataset_analysis%>%filter(is.na(SMDH_sign))
+low_sample<-read_csv("data/03_data_cleaning/low_sample.csv", show_col_types = F)
 
-dataset_lnRR <- read_csv("data/04_data_analysis/dataset_lnRR.csv", show_col_types = F)
-
-dataset_SMDH <- read_csv("data/04_data_analysis/dataset_SMDH.csv", show_col_types = F)
 ```
 
-We calculated two effect sizes for each pairwise comparison: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the `escalc` function (`measure= ROM` and `SMDH` respectively, `vtype= "LS"`) in the R package `metafor` [@metafor].
-We specified the treatment group as the numerator and the control group as the denominator for lnRR and treatment minus control for SMDH, such that positive values indicate the 'fitness' value increased in the treatment group.
-In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, scab score etc., the effect size sign was inverted to ensure comparability across all fitness proxies.
-In all cases, the effect sizes were coded such that the fitness proxies were positively correlated with the overall fitness.
-SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance--- specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1 (excluded k = `{r} nrow(low_sample)`, n = `{r} length(unique(low_sample$paper_ID))`)
+Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package ‘metafor’ v4.8-0 [@metafor].
+We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a ‘fitness’ increase in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted prior to analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
+SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance; specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1.
+There were `{r} as.character(english::english(nrow(low_sample), 1, 1))` effect sizes from `{r} as.character(english::english(length(unique(low_sample$paper_ID)), 1, 1))`) study that did not fulfil that requirement, which we then excluded entirely from the dataset.
 
-For inferential statistics (e.g., *t* value, *F* value), we estimated SMD values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) using the equations provided by @thehand2019.
-For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the `escalc` function (`measure=OR`) from `metafor` and subsequently converted it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`, n = `{r} length(unique(negative_lnRR$paper_ID))`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
+For the few cases for which we could not extract means and variances but inferential statistics such as t and F values, we estimated SMD values (k = `{r} nrow(inferential_only)`, n = `{r} length(unique(inferential_only$paper_ID))`) using the equations provided by @thehand2019.
+For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the 'escalc' function (measure=OR) from 'metafor' and subsequently converted it to SMD using equations from @thehand2019.
+Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
 
-When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size, whenever possible to reduce the effect of genetic relatedness non-independence.
-In cases where the control or treatment group was used repeatedly across multiple comparisons, sample sizes were adjusted by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
-For the cases where the authors of an original article reported no statistically significant difference between two groups but did not provide numerical values (k = `{r} nrow(no_ES)`, n = `{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparison and imputed its sampling variance using the missing-case approach described in @nakagawa2022 for lnRR and using $\frac{n_1+n_2}{n_1×n_2}$ for SMD [@lajeunesse2013].
+When calculating each effect size’s associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
+In cases where the same control or treatment group was used across multiple comparisons, sample sizes were adjusted prior to calculating effect sizes by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
+For cases where the authors of an original article reported a statistically non-significant difference between two groups but without providing numerical values (k = `{r} nrow(no_ES)`, n = `{r} length(unique(no_ES$paper_ID))`), we assigned zero as the effect size for that comparison and imputed its sampling variance using the missing-case approach described in @nakagawa2022 for lnRR and using $\frac{n_1+n_2}{n_1×n_2}$ for SMD [@lajeunesse2013].
 
-## Data Analysis
+## Data analysis
 
 We performed all analyses in R version 4.5.1 [@R-version].
-All multilevel meta-analytical models and meta-regressions were fit using metafor v.4.8-0 [@metafor].
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (*ρ*) between sampling variances from the same study [@noble2017] using the vcalc function from metafor.
-(See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
+All multilevel meta-analytical models and meta-regressions were fitted using ‘metafor’ v.4.8-0 [@metafor].
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from ‘metafor’ (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
-We considered the following levels of non-independence for our analyses: multiple effect sizes collected from (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g.
-birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; eg.
-males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g.
-chick mass on day 7, 14 and 21).
+We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
 
 Unless stated otherwise, we fitted the following random effects in all our models to account for non-independence: Paper ID, Group ID, Species ID, Population ID and an observation-level random effect (Observation ID).
-Our random effect structure deviated from our pre-registration since, initially we had pre-registered the inclusion of Experiment ID and repeated trait ID and not population ID.
-However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution i.e.
+Our random effect structure deviated from our pre-registration since, initially, we had pre-registered the inclusion of Experiment ID and Repeated trait ID but not Population ID.
+However, Experiment ID and Group ID were almost indistinguishable, so we decided to leave out the one with lesser resolution, i.e.
 Experiment ID.
-Additionally, few effect sizes were measured repeatedly, making the Repeated trait ID almost identical to the observation-level random effect (Observation ID), so we excluded it (@figsupp-random-effect).
-Last, we decided to add Population ID, since we noticed that several studies were performed in the same geographical locations.
+Additionally, since few effect sizes were measured repeatedly, making Repeated trait ID almost identical to the observation-level random effect Observation ID, we excluded it (@figsupp-random-effect).
+Last, we decided to add Population ID since we noticed after extracting the data but before any analyses that several studies were performed in the same geographical locations.
 
-### Meta-analytic models: biological predictions
+### Meta-analytic mean and hypotheses
 
-To estimate the effect of GNM addition on fitness across birds, we used two effect sizes: lnRR and SMD(H).
+To estimate the effect of GNM on fitness across birds, we used two effect sizes: lnRR and SMD(H).
 Thus, throughout, we fitted two separate sets of model for each effect size.
 First, we fitted multilevel intercept-only meta-analytical model to test the overall effect, its uncertainty and heterogeneity.
-We used the `rma.mv` function from the `metafor` package using the 'REML' method and a *t* distribution for calculating test statistics and confidence intervals for the fixed effects.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g.
-sex ratio, testosterone levels, etc.), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`; see @figsupp-SAonly-proxies).
-For all intercept-only models, we estimated the total amount of absolute heterogeneity ($𝜎^2$; the variation not explained by the sampling error), its sources (or relative heterogeneity; $I^2$), mean-standardised metric ($CVH2$) and variance-mean-standardised metric of heterogeneity ($M2$) following the pluralistic approach suggested by @yang2025.
+We used the `rma.mv` function from the 'metafor' package using the 'REML' method and a *t* distribution for calculating the test statistics and confidence intervals for the moderators.
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
+For all intercept-only models, we estimated the total amount of absolute heterogeneity ($σ^2$; the total variation not explained by sampling error), its sources or relative heterogeneity ($I^2$), mean-standardised metric (CVH2) and variance-mean-standardised metric of heterogeneity (M2) following the pluralistic approach suggested by @yang2024a .
 
-<!--# Check what is MLMA-excluded and figsupp-SAonly-proxies for figures and decide which one makes more sense to include/exclude?? -->
+To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator ‘hypothesis’ (levels: courtship, parental care, both).
+For this and all meta-regressions, we estimated $R_{marginal}^2$,which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
+Unless stated otherwise, all meta-regressions correspond to unimoderator meta-regressions.
 
-To test the relative importance of the two main hypotheses suggested for GNM: Courtship hypothesis and Parental care hypothesis (combining nest protection and drug hypothesis), we ran a multilevel meta-regression with 'hypothesis' (Courtship hypothesis, Parental care hypothesis, Both) as a moderator.
-For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
-
-### Meta-analytic models: exploratory analyses
+### Exploratory meta-regressions
 
@@
 
-We obtained `{r} nrow(dataset_analysis)` effect sizes from a total of `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@fig-distribution).
+We obtained `{r} nrow(dataset_analysis)` effect sizes from a total of `{r} length(unique(dataset_analysis$paper_ID))` studies conducted on `{r} length(unique(dataset_analysis$bird_species))` species across `{r} length(unique(dataset_analysis$population_ID))` geographical locations (@figmain-distribution).
 About `{r} round(sum(birds_info$perc[birds_info$perc>15]))`% of the effect sizes came from three bird species (`{r} birds_info$bird_species[birds_info$perc > 15][1]`, k = `{r} birds_info$n[birds_info$perc > 15][1]`; `{r} birds_info$bird_species[birds_info$perc > 15][2]`, k = `{r} birds_info$n[birds_info$perc > 15][2]`; `{r} birds_info$bird_species[birds_info$perc > 15][3]`, k = `{r} birds_info$n[birds_info$perc > 15][3]`).
 Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean ±SD number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` and , respectively (range: `{r} min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`--`{r} max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
+The mean ±standard deviation number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`, range: `{r} min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`--`{r} max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
 
-![**Geographical distribution of the 16 study populations included in a meta-analysis testing the adaptive value of green nest materials in birds:** Point size reflects the number of effect sizes coming from the location, and colour denotes species (see legend), with an inset zooming on the cluster of distribution.](figures/Figure_Distribution.png){#fig-distribution}
+![**Geographical distribution of the 17 study populations included in a meta-analysis testing the adaptive value of green nest material in birds**.Point size reflects the number of effect sizes coming from the location (range: 3 - 34 effect sizes), and colour denotes species (see legend), with an inset zooming on a dense cluster of data points.](figures/Figure_Distribution.png){#figmain-distribution}
 
-## **Overall effect of green nest material on fitness proxies**
+## **Meta-analytic mean**
 
-```{r overall-results}
+```{r overall-results, include=FALSE, echo=FALSE}
 intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
@@
 
-Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness in the nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness outcomes in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
-First, lnRR showed an average statistically non-significant increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM \[@fig-mean-effect (A); lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high.
+First, lnRR showed an average statistically non-significant increase in fitness outcomes of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM (@figmain-mean-effect A; lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`) but heterogeneity among effect sizes was high.
 Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
 
-Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM \[@fig-mean-effect (B); SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], but heterogeneity among effect sizes was moderate to high.
+Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM (@figmain-mean-effect B; SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`), but heterogeneity among effect sizes was moderate to high.
 Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
-For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see @supp-tab-heterogeneity for detailed estimates of heterogeneity).
+For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see [@supp-tab-heterogeneity] for detailed estimates of heterogeneity).
 
-These overall results, and their conclusions were robust to several sensitivity analysis.
-First, we fitted a pre-registered bivariate multilevel meta-analytic model including both effect sizes as response variables \[lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`\].
-In addition, we ran several non-pre-registered sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was unclear, (ii) the removal effect sizes that were originally reported as simply statistically non-significant, (iii) both (i) and (ii), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
-The number of effect sizes included in those sensitivity analyses ranged from 227 to 279 effect sizes, and the conclusions remained largely the same (\@supp-tab-SA).
+These overall results, and their conclusions were robust to several sensitivity analyses.
+First, we fitted a pre-registered bivariate multilevel meta-analytic model including both effect sizes as response variables (lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`).
+In addition, we ran several sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was unclear (non-pre-registered), (ii) the removal effect sizes that were originally reported as simply statistically non-significant (non-pre-registered), (iii) both (i) and (ii) (non-pre-registered), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
+The number of effect sizes included in those sensitivity analyses ranged from 182 to 274 effect sizes, and the conclusions remained largely the same [@tabsupp-SA-intercept].
 
-![Overall effect of green nest material on all fitness proxies combined: Mean meta-analytic estimate (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (transparent coloured circles) scaled by precision (inverse of standard error).
-Results are shown as an orchard plot for the intercept-only model (A) using log response ratio and (B) standardised mean difference as effect sizes.
+![**Overall effect of green nest material on all fitness proxies combined.** The meta-analytic mean (large circle) with 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) are shown along with the data points (coloured circles) scaled by precision (inverse of standard error).
+Results are shown as an orchard plot for the intercept-only model (A) using log response ratio (lnRR), and (B) standardised mean difference (SMD(H)).
 k: number of effect sizes (number of studies is shown in the brackets).
-The x-axes are cropped to aid visualization (See Section \[\@supp-full-fig\] for complete figures).](figures/Figure_overall_effect_crop.png){#fig-mean-effect}
+The x-axes are cropped to aid visualization (See Section \[\@figsupp-overall\] for complete figures).](figures/Figure_overall_effect_crop.png){#figmain-mean-effect}
 
-## **Mechanistic Hypotheses: explaining the effect of Green Nest Material**
+## **Mechanistic Hypotheses**
 
-```{r hypotheses-results}
+```{r hypotheses-results, include=FALSE, echo=FALSE}
 lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
@@
 
-Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@fig-hypothesis]).
-The estimates for the courtship hypothesis \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]`; SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\] and the nest protection and drug hypothesis (i.e.
-"parental care hypothesis") \[lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, CI: ``` {r}``summary_lnRR_hypothesis$CI[3] ```, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]`; SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\] were small and statistically significant.
+Our multilevel meta-regressions found no clear support for the two main hypotheses proposed in the literature ([@figmain-hypothesis]).
+The estimates for the courtship hypothesis (lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[2]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]`; SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[2]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`), and the nest protection and drug hypothesis (i.e., "parental care hypothesis") (lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[3]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]`; SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[3]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`) were statistically non-significant.
 However, notice that about half of all effect sizes could not be unequivocally assigned to only one hypothesis, so our meta-regression contained a third category that combined both.
-This category showed an average positive increase in fitness outcomes in nests with an experimental increase of GNM, but the effect was only significant for SMD(H) \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]`; SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\].
-None of the three categories differed statistically significantly from each other (p-value~lnRR~ \> 0.262 and p-value~lnRR~ \> 0.178 in all cases), and the moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
+This category showed an average positive increase in fitness outcomes in nests with an experimental increase of GNM, but the effect was only statistically significant for SMD(H) (lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[1]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]`; SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[1]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`).
+None of the three categories differed statistically significantly from each other (${p-value}_{lnRR)}$ \> 0.211 and ${p-value}_{SMD(H)}$ \> 0.178 in all cases), and the moderator explained very heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).
 
-![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as potential drivers of fitness benefits from green nest material in nests.
-Orchard plot of the multilevel meta-regression for A.
-log response ratio (lnRR) and B.
-Standardized mean difference (SMD(H)).
-Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
+![**There is no clear evidence to favour either the courtship or the parental care hypothesis as drivers of potential fitness benefits of green nest material.** Orchard plot of the multilevel meta-regression for (A) log response ratio (lnRR) and (B) standardised mean difference (SMD(H)).
+Mean estimates (large circles), 95% confidence intervals (thicker bars), and prediction intervals (thinner bars) are shown along with the individual data points (transparently coloured circles) scaled by precision (inverse of standard error).
 k: number of effect sizes (number of studies is shown in the brackets).
-The x-axes are cropped to aid visualization (See Section \[\@fig-supp-hypothesis\] for complete figures).](figures/Figure_hypothesis_crop.png){#fig-hypothesis}
+The x-axes are cropped to aid visualization (See Section [@figsupp-hypothesis] for complete figures).](figures/Figure_hypothesis_crop.png){#figmain-hypothesis}
 
-## What other factors explain heterogeneity among effect sizes?
+## Exploratory meta-regressions
 
-```{r}
+```{r include=FALSE, echo=FALSE}
 # Loading models for parasite type
@@
 car::linearHypothesis(SMDH_design_pc, rbind(c(0,1,-1)))
-
 ```
 
-Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several multilevel meta-regressions.
-First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design.
-The overall effect size for the comparison between no added material and aromatic material was positive and statistically significant \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, it was negative for the comparison between no added material and non-aromatic material statistically significantly so lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\].
-Last, the comparison between non-aromatic and aromatic material showed a small negative statistically non-significant effect \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMD(H)~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\].
-The moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
+Our intercept-only models above showed moderate to high levels of heterogeneity among effect sizes, which we tried to explain by performing several additional multilevel meta-regressions.
 
-Second, when GNM was added continuously throughout the nesting phase, its overall effect was positive and statistically significant, at least for SMD(H) \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\].
-compared to its addition before or after egg hatching \[[\@fig-MR](C-D); Table X\].
-Timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
+![**Experimental designs comparing nests with aromatic green nest material against nests without any green material, and those adding the material continuously, lead to the larger fitness effects.** Orchard plots of the multilevel meta-regressions showing the overall effect of green nest material depending on experimental design for (A: log response ratio (lnRR); B: standardized mean difference (SMD(H)), and time of green nest material addition (C: log response ratio (lnRR); D: standardized mean difference (SMD(H)).
+Mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars), are shown along the individual data points (transparently coloured circles) scaled by precision (inverse of standard error).
+k: number of effect sizes (number of studies is shown in the brackets).
+The x-axes are cropped to aid visualization (See Section [@figsupp-design-time] for complete figures).](figures/Figure_design_time_gnm_addition_cropped.png){#figmain-design-time}
 
-![Orchard plot showing overall effect of green nest material depending on the multilevel meta-regression for experimental design for - A.
-log response ratio (lnRR) and B.
-Standardized mean difference (SMD(H)) and time of GNM addition for - C.
-log response ratio (lnRR) and D.
-Standardized mean difference (SMD(H)).
-Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
-k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_design_time_gnm_addition.png){#fig-MR}
+First, the overall effect of GNM on fitness outcome differed largely depending on the experimental design used ([@figmain-design-time]A,B).
+The overall effect size for the comparison between no added material and aromatic GNM was positive and statistically significant (lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, 95% CI: `{r} summary_lnRR_design$CI[2]`, 95% PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMD(H)~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, 95% CI: `{r} summary_SMDH_design$CI[2]`, 95% PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\], whereas, the comparison between non-aromatic GNM and aromatic GNM was small and statistically non-significant ([@tabmain-MLMR]).
+The latter suggests that, despite not being considered in the hypotheses, non-aromatic GNM could also play some role; however, the comparison between no added material and non-aromatic GNM, was negative and, although based on only 3 studies, statistically significantly so for lnRR (lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, 95% CI: `{r} summary_lnRR_design$CI[3]`, 95% PI: `{r} summary_lnRR_design$PI[3]`, p-value `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]`;[@tabmain-MLMR]).
+ All levels but one differed statistically significantly (${p-value}_{lnRR}$ \< 0.004 and ${p-value}_{SMD(H)}$ \< 0.001 in all cases, except  ${SMD(H)}_{no-material-vs-aromatic}$ vs.
+${SMD(H)}_{no-material-vs-non-aromatic}$ p-value = 0.140), and the moderator experimental design explained a large proportion of heterogeneity, indicating its great importance ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).
 
-Third, there was a positive statistically non-significant effect of increased GNM on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms.
-\[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\].
-The type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+Second, the overall positive effect of GNM on fitness outcomes tended to be larger when GNM was added continuously throughout the nesting phase ([@figmain-design-time]C,D).
+The overall effect was positive and statistically significant so for SMD(H) when material was continuously and experimentally added to the nest (lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`), whereas the effect was small and statistically non-significant when added before egg hatching [@tabmain-MLMR].
+Last, the overall effect also tended to be positive for SMD(H) when GNM was added after egg hatching only, although only marginally so (SMD(H)~after_egg_hatching~ = `{r} summary_SMDH_time_gnm_addition$estimate[1]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[1]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[1]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[1]`, k = `{r} summary_SMDH_time_gnm_addition$k[1]`, n = `{r} summary_SMDH_time_gnm_addition$n[1]`; [@tabmain-MLMR]).
+The three categories did not differ statistically significantly from each other (p-value~lnRR~ \> 0.307 and p-value~SMD(H)~ \> 0.243 in all cases).
+The timing of addition of GNM explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).
 
-Fourth, the bird species had a small positive statistically non-significant increase with an experimental increase in GNM, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\].
-However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+![](tables/MLMR_table.png){#tabmain-MLMR}
 
-Lastly, among different types of fitness trait, only morphological trait had a positive effect of GNM on fitness, which was statistically significant for SMD(H) \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\].
-Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\].
-All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\].
-Trait type accounted for some of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Third, although none of the species-specific mean estimates were statistically significant, most were positive [[\@figsupp-MR](C-D); @tabmain-MLMR], and bird species identity explained a non-negligible amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant and reproduction marginally so, both only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; SMDH~reproduction~ = `{r} summary_SMDH_trait$estimate[6]`, 95% CI: `{r} summary_SMDH_trait$CI[6]`, 95% PI: `{r} summary_SMDH_trait$PI[6]`, p-value = `{r} summary_SMDH_trait$p_value[6]`, k = `{r} summary_SMDH_trait$k[6]`, n = `{r} summary_SMDH_trait$n[6]`; @figsupp-MR; @tabmain-MLMR) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Last, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically signficantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
 
@@
 study design, taxa, data availability) | No |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 4.2                                                                                                          | Justify criteria, if necessary (i.e.
-not obvious from aims and scope.
-| No                       |                                                                                                                          |
-| **Finding studies**                                                                                                                                                                     | **0%**                                                                                                                                                                                                                                                      | 5.1                                                                                                          | Define the type of search (e.g.
-comprehensive search, representative sample)                                                                                                                                                                                                                          | No                       |                                                                                                                          |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 5.2                                                                                                          | State what sources of information were sought (e.g.
-published and unpublished studies, personal communications)                                                                                                                                                                                       | No                       |                                                                                                                          |
+|  |  | 4.2 | Justify criteria, if necessary (i.e. not obvious from aims and scope. | No |  |
+| **Finding studies** | **0%** | 5.1 | Define the type of search (e.g. comprehensive search, representative sample) | No |  |
+|  |  | 5.2 | State what sources of information were sought (e.g. published and unpublished studies, personal communications) | No |  |
 |  |  | 5.3 | Include, for each database searched, the exact search strings used, with keyword combinations and Boolean operators | No |  |
 |  |  | 5.4 | Provide enough information to repeat the equivalent search (if possible), including the timespan covered (start and end dates) | No |  |
-| **Study selection**                                                                                                                                                                     | **0%**                                                                                                                                                                                                                                                      | 6.1                                                                                                          | Describe how studies were selected for inclusion at each stage of the screening process (e.g.
-use of decision trees, screening software)                                                                                                                                                              | No                       |                                                                                                                          |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 6.2                                                                                                          | Report the number of people involved and how they contributed (e.g.
-independent parallel screening)                                                                                                                                                                                                   | No                       |                                                                                                                          |
-| **Data collection process**                                                                                                                                                             | **0%**                                                                                                                                                                                                                                                      | 7.1                                                                                                          | Describe where in the reports data were collected from (e.g.
-text or figures)                                                                                                                                                                                                                         | No                       |                                                                                                                          |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 7.2                                                                                                          | Describe how data were collected (e.g.
-software used to digitize figures, external data sources)                                                                                                                                                                                                      | No                       |                                                                                                                          |
-| 7.3                                                                                                                                                                                     | Describe moderator variables that were constructed from collected data (e.g.
-number of generations calculated from years and average generation time)                                                                                                       | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| **Study selection** | **0%** | 6.1 | Describe how studies were selected for inclusion at each stage of the screening process (e.g. use of decision trees, screening software) | No |  |
+|  |  | 6.2 | Report the number of people involved and how they contributed (e.g. independent parallel screening) | No |  |
+| **Data collection process** | **0%** | 7.1 | Describe where in the reports data were collected from (e.g. text or figures) | No |  |
+|  |  | 7.2 | Describe how data were collected (e.g. software used to digitize figures, external data sources) | No |  |
+| 7.3 | Describe moderator variables that were constructed from collected data (e.g. number of generations calculated from years and average generation time) | No |  |  |  |
 | 7.4 | Report how missing or ambiguous information was dealt with during data collection (e.g.
@@
 |  |  | 8.2 | Describe items that do not appear in the main results, or which could not be extracted due to insufficient information | No |  |
-| 8.3                                                                                                                                                                                     | Describe main assumptions or simplifications that were made (e.g.
-categorising both 'length' and 'mass' as 'morphology')                                                                                                                                    | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 8.4                                                                                                          | Describe the type of replication unit (e.g.
-individuals, broods, study sites)                                                                                                                                                                                                                         | No                       |                                                                                                                          |
+| 8.3 | Describe main assumptions or simplifications that were made (e.g. categorising both 'length' and 'mass' as 'morphology') | No |  |  |  |
+|  |  | 8.4 | Describe the type of replication unit (e.g. individuals, broods, study sites) | No |  |
 | **Assessment of individual study quality** | **0%** | 9.1 | Describe whether the quality of studies included in the systematic review or meta-analysis was assessed (e.g.
 blinded data collection, reporting quality, experimental versus observational) | No |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 9.2                                                                                                          | Describe how information about study quality was incorporated into analyses (e.g.
-meta-regression and/or sensitivity analysis)                                                                                                                                                                        | No                       |                                                                                                                          |
+|  |  | 9.2 | Describe how information about study quality was incorporated into analyses (e.g. meta-regression and/or sensitivity analysis) | No |  |
 | **Effect size measures** | **0%** | 10.1 | Describe effect size(s) used | No |  |
 |  |  |  |  |  |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 10.2                                                                                                         | Provide a reference to the equation of each calculated effect size (e.g.
-standardised mean difference, log response ratio) and (if applicable) its sampling variance                                                                                                                                  | No                       |                                                                                                                          |
-| **Missing data**                                                                                                                                                                        | **0%**                                                                                                                                                                                                                                                      | 11.1                                                                                                         | Describe any steps taken to deal with missing data during analysis (e.g.
-imputation, complete case, subset analysis)                                                                                                                                                                                  | No                       |                                                                                                                          |
+|  |  | 10.2 | Provide a reference to the equation of each calculated effect size (e.g. standardised mean difference, log response ratio) and (if applicable) its sampling variance | No |  |
+| **Missing data** | **0%** | 11.1 | Describe any steps taken to deal with missing data during analysis (e.g. imputation, complete case, subset analysis) | No |  |
 |  |  | 11.2 | Justify the decisions made to deal with missing data | No |  |
@@
 common/fixed effects model, unweighted model), provide justification for this choice | No |  |
-| **Software**                                                                                                                                                                            | **0%**                                                                                                                                                                                                                                                      | 13.1                                                                                                         | Describe the statistical platform used for inference (e.g.
-R)                                                                                                                                                                                                                                         | No                       |                                                                                                                          |
+| **Software** | **0%** | 13.1 | Describe the statistical platform used for inference (e.g. R) | No |  |
 |  |  | 13.2 | Describe the packages used to run models | No |  |
@@
 |  |  | 13.5 | Describe the version numbers of all software used | No |  |
-| **Non-independence**                                                                                                                                                                    | **0%**                                                                                                                                                                                                                                                      | 14.1                                                                                                         | Describe the types of non-independence encountered (e.g.
-phylogenetic, spatial, multiple measurements over time)                                                                                                                                                                                      | No                       |                                                                                                                          |
+| **Non-independence** | **0%** | 14.1 | Describe the types of non-independence encountered (e.g. phylogenetic, spatial, multiple measurements over time) | No |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| **Publication bias and sensitivity analysis**                                                                                                                                           | **0%**                                                                                                                                                                                                                                                      | 16.1                                                                                                         | Describe assessments of the risk of bias due to missing results (e.g.
-publication, time-lag, and taxonomic biases)                                                                                                                                                                                    | No                       |                                                                                                                          |
+| **Publication bias and sensitivity analysis** | **0%** | 16.1 | Describe assessments of the risk of bias due to missing results (e.g. publication, time-lag, and taxonomic biases) | No |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| **Clarification of post hoc analyses**                                                                                                                                                  | **0%**                                                                                                                                                                                                                                                      | 17.1                                                                                                         | When hypotheses were formulated after data analysis, this should be acknowledged.
-| No                       |                                                                                                                          |
+| **Clarification of post hoc analyses** | **0%** | 17.1 | When hypotheses were formulated after data analysis, this should be acknowledged. | No |  |
 |  |  |  |  |  |  |
-| **Metadata, data, and code**                                                                                                                                                            | 18.1                                                                                                                                                                                                                                                        | Share metadata (i.e.
-data descriptions)                                                                      | No                                                                                                                                                                                                                                                                                                    |                          |                                                                                                                          |
+| **Metadata, data, and code** | 18.1 | Share metadata (i.e. data descriptions) | No |  |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| 19.4                                                                                                                                                                                    | Present a Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)-like flowchart (www.prisma-statement.org).
-| No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| 19.4 | Present a Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)-like flowchart (www.prisma-statement.org). | No |  |  |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| Provide a summary of key characteristics for reported outcomes (either in text or figures; e.g.
-one quarter of effect sizes reported for vertebrates and the rest invertebrates)        | No                                                                                                                                                                                                                                                          |                                                                                                              |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| Provide a summary of key characteristics for reported outcomes (either in text or figures; e.g. one quarter of effect sizes reported for vertebrates and the rest invertebrates) | No |  |  |  |  |
 |  |  |  |  |  |  |
-| 20.4                                                                                                                                                                                    | Provide a summary of limitations of included moderators (e.g.
-collinearity and overlap between moderators)                                                                                                                                                  | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| 20.4 | Provide a summary of limitations of included moderators (e.g. collinearity and overlap between moderators) | No |  |  |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| **Meta-regression**                                                                                                                                                                     | 23.1                                                                                                                                                                                                                                                        | Provide estimates of meta-regression slopes (i.e.
-regression coefficients) and confidence/credible intervals | No                                                                                                                                                                                                                                                                                                    |                          |                                                                                                                          |
+| **Meta-regression** | 23.1 | Provide estimates of meta-regression slopes (i.e. regression coefficients) and confidence/credible intervals | No |  |  |
 |  |  |  |  |  |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 23.2                                                                                                         | Include estimates and confidence/credible intervals for all moderator variables that were assessed (i.e.
-complete reporting)                                                                                                                                                                          | No                       |                                                                                                                          |
+|  |  | 23.2 | Include estimates and confidence/credible intervals for all moderator variables that were assessed (i.e. complete reporting) | No |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| 23.4                                                                                                                                                                                    | Describe outcomes from model selection, if done (e.g.
-R2 and AIC)                                                                                                                                                                                           | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| 23.4 | Describe outcomes from model selection, if done (e.g. R2 and AIC) | No |  |  |  |
 |  |  |  |  |  |  |
-| **Outcomes of publication bias and sensitivity analysis**                                                                                                                               | **0%**                                                                                                                                                                                                                                                      | 24.1                                                                                                         | Provide results for the assessments of the risks of bias (e.g.
-Egger's regression, funnel plots)                                                                                                                                                                                                      | No                       |                                                                                                                          |
+| **Outcomes of publication bias and sensitivity analysis** | **0%** | 24.1 | Provide results for the assessments of the risks of bias (e.g. Egger's regression, funnel plots) | No |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 25.2                                                                                                         | Summarise the main findings in terms of the precision of effects (e.g.
-size of confidence intervals, statistical significance)                                                                                                                                                                        | No                       |                                                                                                                          |
+|  |  | 25.2 | Summarise the main findings in terms of the precision of effects (e.g. size of confidence intervals, statistical significance) | No |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-| 25.6                                                                                                                                                                                    | Consider limitations and their influence on the generality of conclusions, such as gaps in the available evidence (e.g.
-taxonomic and geographical research biases)                                                                                         | No                                                                                                           |                                                                                                                                                                                                                                                                                                       |                          |                                                                                                                          |
+| 25.6 | Consider limitations and their influence on the generality of conclusions, such as gaps in the available evidence (e.g. taxonomic and geographical research biases) | No |  |  |  |
 |  |  |  |  |  |  |
@@
 |  |  |  |  |  |  |
-|                                                                                                                                                                                         |                                                                                                                                                                                                                                                             | 27.2                                                                                                         | List included studies as referenced sources (e.g.
-rather than listing them in a table or supplement)                                                                                                                                                                                                  | No                       |                                                                                                                          |
+|  |  | 27.2 | List included studies as referenced sources (e.g. rather than listing them in a table or supplement) | No |  |
 
@@
 
+### Plots with complete dataset (without cropping the plots)
+
 ![](figures/Figure_parasite_birds_trait.png)
@@
 Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error).
-k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-supp-hypothesis width="1035"}
+k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#figsupp-hypothesis width="1035"}
+
+# All sensitivity-analysis/robustness check
+
+![](tables/SA_intercept_only.png){#tabsupp-SA-intercept}
+
+# Maybe-maybe stuff
+
+![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
+
+###

### 2025-07-26 manuscript_GNM.qmd
Temp commit back to desktop

@@
 Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@hansell2000; @mainwaring2014; @deeming2023].
-While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including mud, stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@sergio2011; @suárez-rodríguez2013; @sheard2024].
+While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including mud, stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@sergio2011; @suárez-rodríguez2013; @jagiello2023; @sheard2024].
 These are considered non-structural additions and suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
@@
 Importantly, contrary to the structural nest materials (e.g., twigs, mud), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @mennerat2009b) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some times weeks, requires extra time, and in some cases flying outside one’s territory [@mennerat2009].
+GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for sometimes over weeks, requires extra time and, in some cases, flying outside one's territory [@mennerat2009].
 Thus, the general costs associated with nest-building [@mainwaring2013], and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
@@
 This alternative hypothesis suggests that the volatiles present in GNM directly enhance offspring immune function and/or health independent of parasite or pathogen control [@gwinner2000; @mennerat2009a].
-Thus, while both the nest protection and drug hypothesis suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
+Thus, while both the nest protection and drug hypotheses suggest an adaptive benefit of GNM by enhancing offspring survival, the drug hypothesis emphasizes a pharmacological mechanism, whereas the nest protection hypothesis emphasizes parasite and pathogen repellency.
 Importantly, these two hypotheses are not mutually exclusive unless the improvement in offspring health can be proved to be unrelated to a reduction in parasite or pathogen load, something difficult to achieve.
 
-Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic (i.e., volatiles and secondary metabolites) properties have been also proposed.
+Last, several additional adaptive hypotheses or functions of GNM that do not refer to its aromatic (i.e., volatiles and secondary metabolites) properties have also been proposed.
 These include benefits such as enhancing the crypticity of the nest [@skutch1957], providing insulation or sun protection for eggs and offspring [@mertens1977], or simply fulfilling a structural function [@lyons1987].
@@
 In all, despite decades of research, abundant observational and experimental studies, and two crucial narrative reviews [@dubiec2013; @scott-baumann2015], we still do not know the overall adaptive significance of GNM, its generality across bird species, and the relative importance of each of the suggested mechanisms.
-Given that nest building is widespread across taxa —including but not limited to birds— and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
+Given that nest building is widespread across taxa ---including but not limited to birds--- and is increasingly recognized as an expression of the extended phenotype, a quantitative synthesis of this field is both timely and has potentially far-reaching implications.
 
@@
 We conducted a systematic search on Web of Science Core Collection and Scopus on the 7th of September, 2022 (see update below).
-The keyword search query was designed as a three-block query including terms related to our treatment of interest ((“green\*” OR “herb\*” OR “aromatic\*”) AND “nest\*”), population of interest (“bird\*” OR “aves” OR “avian” OR “ornithol\*” OR “passerine\*” OR “passeriform\*” OR “songbird\*” OR list of all bird genera) and to limit the search results to experimental studies only (“experiment\*” OR “manipulat\*”).
+The keyword search query was designed as a three-block query including terms related to our treatment of interest (("green\*" OR "herb\*" OR "aromatic\*") AND "nest\*"), population of interest ("bird\*" OR "aves" OR "avian" OR "ornithol\*" OR "passerine\*" OR "passeriform\*" OR "songbird\*" OR list of all bird genera) and to limit the search results to experimental studies only ("experiment\*" OR "manipulat\*").
 The complete search strings tailored to each specific platform are provided in @figsupp-string.
@@
 We validated our search using an initial library of 15 relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package ‘litsearchr’ v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
-After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package ‘revtools’ v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
+Additionally, we used the R package 'litsearchr' v1.0.0 [@grames2019], which did not yield any new relevant terms, confirming our queries.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package 'revtools' v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
 
@@
 
-All titles and abstracts were equally allocated and screened independently by at least two screeners (SD, TR, JMGS) using the R package ‘revtools’ following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
+All titles and abstracts were equally allocated and screened independently by at least two screeners (SD, TR, JMGS) using the R package 'revtools' following a pre-designed decision tree with all inclusion/exclusion criteria (@figsupp-decision-tree).
 We included all studies on birds that experimentally manipulated the GNM (both aromatics or herbs).
@@
 We updated our systematic literature search by repeating our search on the 12th of August, 2024, and found `{r} nrow(unique_reference_list_repeat)` unique articles after removing `{r} nrow(full_reference_before_deduplication_repeat)-nrow(unique_reference_list_repeat)` duplicates.
-Only one observer (SD) performed the both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
+Only one observer (SD) performed both screenings using the same decision trees as before (@figsupp-decision-tree), and found `{r} as.character(english::english(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T), 1, 1))` additional eligible article for our meta-analysis.
 Lastly, we identified `{r} as.character(english::english(nrow(selected_abstract_screening_repeat)-(sum(selected_abstract_screening_repeat$screened_abstracts=="selected", na.rm=T)), 1, 1))` additional eligible articles recommended by two colleagues.
@@
 The data of each article were extracted evenly by one of three authors (SD, TR,  JMGS), with another screener verifying the procedure, and four authors (SD, TR, JMGS, AST) collectively discussing and revising unclear cases.
-We prioritised extracting primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package ‘metaDigitise’ v1.0.1 [@pick2018].
-If primary data were not available, we extracted inferential statistics such as *t* and *F* values or descriptive statistics such as contingency tables (see below), that could be transformed into an effect size.
-Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from them (n = `{r} length(raw_data)`).
+We prioritised extracting primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package 'metaDigitise' v1.0.1 [@pick2018].
+If primary data were not available, we extracted inferential statistics such as t and F values or contingency tables to transform them into effect sizes (see below).
+Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from each group ourselves (n = `{r} length(raw_data)`).
 
@@
 aromatic GNM, or no added GNM vs.
-aromatic GNM, in our moderator “experimental design”.
+aromatic GNM, in our moderator "experimental design".
 However, there was a third type of comparison used in some studies comparing nests with experimentally added non-aromatic GNM to nests without any added GNM or in which GNM added by the birds was removed by the authors.
 In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these `{r} nrow(lnRR_comp3)` and `{r} nrow(SMDH_comp3)` effect sizes, respectively, as non-aromatic GNM vs.
-no added GNM in our moderator “experimental design”.
-Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator “experimental design” was used for subsequent meta-regressions.
+no added GNM in our moderator "experimental design".
+Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator "experimental design" was used for subsequent meta-regressions.
 In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons.
@@
 
-Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package ‘metafor’ v4.8-0 [@metafor].
-We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a ‘fitness’ increase in the treatment group.
+Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package 'metafor' v4.8-0 [@metafor].
+We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a 'fitness' increase in the treatment group.
 In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted prior to analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
@@
 
-When calculating each effect size’s associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
+When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
 In cases where the same control or treatment group was used across multiple comparisons, sample sizes were adjusted prior to calculating effect sizes by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
@@
 We performed all analyses in R version 4.5.1 [@R-version].
-All multilevel meta-analytical models and meta-regressions were fitted using ‘metafor’ v.4.8-0 [@metafor].
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from ‘metafor’ (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
+All multilevel meta-analytical models and meta-regressions were fitted using 'metafor' v.4.8-0 [@metafor].
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from 'metafor' (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
@@
 
-To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator ‘hypothesis’ (levels: courtship, parental care, both).
+To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator 'hypothesis' (levels: courtship, parental care, both).
 For this and all meta-regressions, we estimated $R_{marginal}^2$,which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
@@
 (2025).
-…
+...
 
@@
 Our dataset included `{r} length(unique(unpublished_studies$paper_ID))` unpublished studies (k = `{r} nrow(unpublished_studies)`), with the remaining studies being published between `{r} min((dataset_analysis$year_publication),na.rm = T)` and `{r} max((dataset_analysis$year_publication),na.rm = T)`.
-The mean ±standard deviation number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`, range: `{r} min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`--`{r} max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment)`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
+The mean ±standard deviation number of effect sizes per study was `{r} sprintf("%.1f", mean(ES_per_study$n))` ± `{r} sprintf("%.1f",sd(ES_per_study$n))` (median: `{r} sprintf("%.1f", median(ES_per_study$n))` range: `{r} min(ES_per_study$n)`--`{r} max(ES_per_study$n)`) and the mean effective sample size (i.e., the number of nests/individuals per effect size after accounting for shared-group non-independence) was `{r} sprintf("%.1f",mean(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` ±`{r} sprintf("%.1f", sd(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))` (median: `{r} sprintf("%.1f",median(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`, range: `{r} floor(min(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`--`{r} round(max(dataset_analysis$effective_n_control+dataset_analysis$effective_n_experiment))`; `{r} nrow(dataset_analysis%>%filter(n_experiment<5|n_control<5))` data points had a sample size of less than 5 nests in each group).
 
@@
 First, lnRR showed an average statistically non-significant increase in fitness outcomes of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM (@figmain-mean-effect A; lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`) but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (*Q* = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (*I^2^~total~* = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
 
 Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM (@figmain-mean-effect B; SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`), but heterogeneity among effect sizes was moderate to high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (*Q* = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (*I^2^~total~* = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
 For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see [@supp-tab-heterogeneity] for detailed estimates of heterogeneity).
@@
 First, we fitted a pre-registered bivariate multilevel meta-analytic model including both effect sizes as response variables (lnRR = `{r} sprintf("%.3f",(coef(bivariate_model)[1]))`, p-value = `{r} sprintf("%.3f",(bivariate_model$pval[1]))` and SMD(H) = `{r} sprintf("%.3f",(coef(bivariate_model)[2]))` , p-value = `{r} sprintf("%.3f",(bivariate_model$pval[2]))`).
-In addition, we ran several sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was unclear (non-pre-registered), (ii) the removal effect sizes that were originally reported as simply statistically non-significant (non-pre-registered), (iii) both (i) and (ii) (non-pre-registered), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
+In addition, we ran several sensitivity analyses to test the robustness of the overall results to: (i) the inclusion of traits for which their relationship with fitness was debated in the literature (non-pre-registered), (ii) the removal effect sizes that were originally reported as simply statistically non-significant (non-pre-registered), (iii) both (i) and (ii) (non-pre-registered), and, (iv) the removal of effect sizes that were calculated by transforming inferential statistics.
 The number of effect sizes included in those sensitivity analyses ranged from 182 to 274 effect sizes, and the conclusions remained largely the same [@tabsupp-SA-intercept].
@@
 The estimates for the courtship hypothesis (lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[2]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]`; SMD(H)~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[2]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`), and the nest protection and drug hypothesis (i.e., "parental care hypothesis") (lnRR~parental_care~ = `{r} summary_lnRR_hypothesis$estimate[3]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[3]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]`; SMD(H)~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[3]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`) were statistically non-significant.
-However, notice that about half of all effect sizes could not be unequivocally assigned to only one hypothesis, so our meta-regression contained a third category that combined both.
+However, about half of all effect sizes could not be unequivocally assigned to only one hypothesis, so our meta-regression contained a third category that combined both.
 This category showed an average positive increase in fitness outcomes in nests with an experimental increase of GNM, but the effect was only statistically significant for SMD(H) (lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, 95% CI: `{r} summary_lnRR_hypothesis$CI[1]`, 95% PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]`; SMD(H)~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, 95% CI: `{r} summary_SMDH_hypothesis$CI[1]`, 95% PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`).
@@
 Second, the overall positive effect of GNM on fitness outcomes tended to be larger when GNM was added continuously throughout the nesting phase ([@figmain-design-time]C,D).
-The overall effect was positive and statistically significant so for SMD(H) when material was continuously and experimentally added to the nest (lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`), whereas the effect was small and statistically non-significant when added before egg hatching [@tabmain-MLMR].
+The overall effect was positive and statistically significant so for SMD(H) when material was continuously and experimentally added to the nest (lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]`; SMD(H)~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`), whereas the effect was small and statistically non-significant when added before egg hatching [@tabmain-MLMR].
 Last, the overall effect also tended to be positive for SMD(H) when GNM was added after egg hatching only, although only marginally so (SMD(H)~after_egg_hatching~ = `{r} summary_SMDH_time_gnm_addition$estimate[1]`, 95% CI: `{r} summary_SMDH_time_gnm_addition$CI[1]`, 95% PI: `{r} summary_SMDH_time_gnm_addition$PI[1]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[1]`, k = `{r} summary_SMDH_time_gnm_addition$k[1]`, n = `{r} summary_SMDH_time_gnm_addition$n[1]`; [@tabmain-MLMR]).

### 2025-08-07 docs/code/07_data_analysis.Rmd
First mansucript draft

@@
 predict(SA_SMDH_flagged_no_missingES)
+```
+
+Are the meta-regression robust to this analysis
+
+```{r}
+
+dataset_lnRR_design_flagged_no_missingES <- lnRR_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design_flagged_no_missingES <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_flagged_no_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_flagged_no_missingE <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_flagged_no_missingES)
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design_flagged_no_missingES <-SMDH_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design_flagged_no_missingES <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design_flagged_no_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design_flagged_no_missingE <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design_flagged_no_missingES)
+
 ```
@@
 
+# Sensitivity Analysis: Excluding Non-aromatic Vs. Aromatic
+
+We are aware that removing over 50% of the dataset will cause some moderator levels to drop out.
+But if our goal is to critically examine the role of aromaticity and potentially argue that its importance has been overstated, this could be a very informative step.
+
+```{r}
+
+## For the lnRR effect size...
+dataset_lnRR_no_comp1<-dataset_lnRR%>%filter(comparision_type!=1 | is.na(comparision_type))
+## Only some rows are removed... 
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp1)
+
+VCV_lnRR_no_comp1 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_comp1<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_comp1)
+
+# Saving the model
+saveRDS(SA_lnRR_no_comp1, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp1.csv"))
+
+#----------------------------------------------------------------------------
+# for  SMDH  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_SMDH_no_comp1<-dataset_SMDH%>%filter(comparision_type!=1 | is.na(comparision_type))
+## Only some rows are removed... 
+nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp1)
+
+VCV_SMDH_no_comp1 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_SMDH_no_comp1<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_no_comp1)
+
+# Saving the model
+saveRDS(SA_SMDH_no_comp1, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp1.csv"))
+
+#----------------------------------------------------------------------------
+# Rerunning the two mechanistic hypothesis meta-regressions with those effect sizes excluded
+#----------------------------------------------------------------------------
+
+lnRR_hypothesis_no_comp1 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_comp1,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_no_comp1)
+# Save model
+saveRDS(lnRR_hypothesis_no_comp1, file = here::here("model/lnRR_hypothesis_no_comp1.rds"))
+
+SMDH_hypothesis_no_comp1 <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_comp1,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_no_comp1)
+
+# Save model
+saveRDS(SMDH_hypothesis_no_comp1, file = here::here("model/SMDH_hypothesis_no_comp1.rds"))
+
+#----------------------------------------------------------------------------
+## Now re-running all the 5 meta-regressions once again
+#----------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_lnRR_design_no_comp1 <- dataset_lnRR_no_comp1 %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design_no_comp1 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_no_comp1 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_no_comp1 )
+
+# Saving the model
+saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design_no_comp1 <- dataset_SMDH_no_comp1 %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design_no_comp1 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_no_comp1 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_no_comp1 )
+
+# Saving the model
+saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))
+```
+
+\
+
 # Risk of Bias
 
-6\. Blinding: (Levels: yes, no(
-
-7\. Random Assignment: (Levels: yes, no)
-
-8\. Missing Data: (Levels: yes, no)
-
-Note that the specific subset of data for each meta-regression may differ based on the data availability (e.g., information about the type of parasites is only available for effect sizes based on parasite/pathogen related fitness proxy).
-We will conduct meta-regression on suitable subsets of data for each analysis, provided we have sufficient effect sizes per moderator level (i.e., at least 5 effect sizes per moderator level).
-
-::: callout-important
-## Phylogenetic Effects
-
-Note also that if we obtain additional effect sizes for other bird species after we update our search and/or contact authors, our models may need to account for phylogenetic nonindependence via the inclusion of two additional random effects: "species" and "phylogeny" following Cinar et al.
-(2022).
-:::
-
-## Other Analysis
-
-### Risk of Bias Assessment
-
--   RoB - The outcome will be presented in the form of a [**summary table**]{.underline}. We will conduct uni-moderator meta-regressions using these variables.
+We have pre-registered the Risk Of Bias analysis, the three we will explore:
+
+1.  **Blinding**
+
+    ```{r}
+    unique(dataset_lnRR$blinding)
+
+    lnRR_blinding <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + blinding,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_blinding, file = here::here("model/lnRR_blinding.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_blinding.csv"))
+
+    SMDH_blinding <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + blinding,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_blinding, file = here::here("model/SMDH_blinding.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_blinding.csv"))
+    ```
+
+2.  Random Assignment
+
+    ```{r}
+
+    unique(dataset_lnRR$random_assignment)
+
+    lnRR_random_assignment <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + random_assignment,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_random_assignment, file = here::here("model/lnRR_random_assignment.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_random_assignment.csv"))
+
+    SMDH_random_assignment <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + random_assignment,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_random_assignment, file = here::here("model/SMDH_random_assignment.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_random_assignment.csv"))
+    ```
+
+3.  Missing Vs. Not Missing
+
+    ```{r}
+
+    unique(dataset_lnRR$missing_data)
+
+    lnRR_missing_data <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + missing_data,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_missing_data, file = here::here("model/lnRR_missing_data.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_missing_data.csv"))
+
+    SMDH_missing_data <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + missing_data,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_missing_data, file = here::here("model/SMDH_missing_data.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_missing_data.csv"))
+    ```
 
@@
 ## --- Now for SMDH -----
+
 dataset_SMDH_published<-dataset_SMDH_published%>%
@@
 # 
-# dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
-#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
-#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
-#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
-#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
-# 
-# VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
-#                   cluster = paper_ID,
-#                   obs = Observation_ID,
-#                   data = dataset_lnRR_all_in,
-#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-#                   )
-# 
-# lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
-#                     mods = ~ time_of_gnm_addition + 
-#                       year_MeanCenter + 
-#                       sqrt_effective_n_inv + 
-#                       as.factor(comparision_type) + 
-#                       bird_species + 
-#                       trait_type,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                     control = list(optimizer="optim"),
-#                     test = "t",
-#                     data = dataset_lnRR_all_in)
-# 
-# 
-# 
-# ## For SMDH complete published dataset
-# 
-# dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
-#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
-#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
-#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
-#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
-# 
-# VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
-#                   cluster = paper_ID,
-#                   obs = Observation_ID,
-#                   data = dataset_SMDH_all_in,
-#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-#                   )
-# 
-# SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
-#                     mods = ~ time_of_gnm_addition + 
-#                       year_MeanCenter + 
-#                       sqrt_effective_n_inv + 
-#                       as.factor(comparision_type) + 
-#                       bird_species + 
-#                       trait_type,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                     control = list(optimizer="optim"),
-#                     test = "t",
-#                     data = dataset_SMDH_all_in)
+dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ as.factor(4), TRUE ~ comparision_type))
+
+VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition +
+                      year_MeanCenter +
+                      sqrt_effective_n_inv +
+                      comparision_type +
+                      bird_species +
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_all_in)
+
+# saving the model
+saveRDS(lnRR_all_in, file = here::here("model/lnRR_all_in.rds"))
+
+## For SMDH complete published dataset
+
+dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
+  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
+  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+  mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
+  mutate(comparision_type= case_when(is.na(comparision_type) ~ as.factor(4), TRUE ~ comparision_type))
+
+VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_all_in,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ time_of_gnm_addition +
+                      year_MeanCenter +
+                      sqrt_effective_n_inv +
+                      as.factor(comparision_type) +
+                      bird_species +
+                      trait_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_all_in)
+
+# saving the model
+saveRDS(SMDH_all_in, file = here::here("model/SMDH_all_in.rds"))
 ```
@@
 
-including including post-hoc Wald tests
-
-For this I have to run all the meta-regressions again without removing the intercepts, good luck to me!
+Including post-hoc Wald tests
+
+For this I have to run all the meta-regressions again without removing the intercepts
 

### 2025-08-07 docs/code/08_figures-tables.Rmd
First mansucript draft

@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))
 
@@
     ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1.5,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
+labs(x = "",
+     y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))
+
+##-----------------------------------------------------------------------------
+
+# Now the cropped figures for the main manuscript
+
+##-----------------------------------------------------------------------------
+
+lnRR_design_plot_cropped <-
+  orchard_plot(mod_results(
+      lnRR_design,
+      mod = "comparision_type",
+      group = "paper_ID"
+    ),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
   xlab ="") +
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  )
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))
+
+SMDH_design_plot_cropped <-
+  orchard_plot(mod_results(
+      SMDH_design,
+      mod = "comparision_type",
+      group = "paper_ID"
+    ),
+   trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+    k.pos = c(1.9,0.6,0.6),
+  xlab ="") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+labs(x = "",
+     y = "Effect Size (SMDH)")+
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+    legend.position.inside = c(0.99, 0.01),
+    legend.justification = c(1, 0), 
+    legend.direction = "horizontal",
+    legend.background = element_blank(),
+    legend.key = element_blank(),
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6),
+    axis.title = element_text(size = 10),
+    axis.text.x = element_text(size = 10),
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))
 
@@
   scale_fill_manual(values = "mediumpurple4") +
+  coord_cartesian(ylim = c(-2.5, 2.5)) +
   labs(y = "Effect size (lnRR)",
@@
   scale_fill_manual(values = "mediumpurple4") +
+  coord_cartesian(ylim = c(-10, 7)) +
   labs(y = "Effect size (SMDH)",
@@
   scale_fill_manual(values = "#218833") +
+  coord_cartesian(ylim = c(-2.5, 2.5)) +
   labs(y = "Effect size (lnRR)",
-       x = "Publication Year (Mean Cenetered)")+
+       x = "Publication Year (Mean Centered)")+
     theme(
@@
   scale_fill_manual(values = "#218833") +
+  coord_cartesian(ylim = c(-10, 7)) +
   labs(y = "Effect size (SMDH)",
-       x = "Publication Year (Mean Cenetered)")+
+       x = "Publication Year (Mean Centered)")+
     theme(
@@
 
-# -------- TABLES ———-
+# ----- Supplementary Material Table -------
+
+```{r}
+
+# Loading packages
+
+pacman::p_load(gt,dplyr,metafor)
+```
+
+```{r}
+#| label: excluded_proxy_table
+
+merged_data_extraction <- read_csv(here::here("data/03_data_cleaning/merged_data_extraction.csv"), show_col_types = F)
+
+dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"), show_col_types = F)
+
+excluded_proxies<- merged_data_extraction %>%
+  filter(fulltext_screening == "included") %>%
+  filter(proxy_decision== "exclude")%>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+SA_only_proxies <- dataset_analysis %>%
+  filter(proxy_decision == "sensitivity-analysis")%>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+# Now binding them together
+combined_summary <- bind_rows(
+  excluded_proxies %>% mutate(Category = "Completely excluded"),
+  SA_only_proxies   %>% mutate(Category = "Sensitivity-analysis only")
+) %>%
+  arrange(Category, paper_ID)
+
+# Group by category
+excluded_proxies <-combined_summary %>%
+  gt() %>%
+  tab_header(
+    title = md("**Excluded Fitness Proxies**")
+  ) %>%
+  # define row-groups
+  tab_row_group(
+    group    = "Completely excluded",
+    rows     = Category == "Completely excluded"
+  ) %>%
+  tab_row_group(
+    group    = "Sensitivity-analysis only",
+    rows     = Category == "Sensitivity-analysis only"
+  ) %>%
+  # hide the helper column
+  cols_hide("Category") %>%
+  # relabel columns
+  cols_label(
+         `paper_ID`             = "Paper ID",
+         `Number of proxies`    = "Noumber\nof Proxies",
+         `Excluded Proxies`     = "Excluded\nProxies",
+         `Reason for Exclusion` = "Reason for Exclusion"
+  ) %>%
+  fmt_markdown(columns = c(`Excluded Proxies`, `Reason for Exclusion`)) %>%
+  opt_align_table_header(align = "left") %>%
+  cols_align(
+    align   = "left",
+    columns = everything()
+  ) %>%
+  tab_options(
+    table.width               = pct(90),
+    row.striping.background_color = "#F7F7F7"
+  )
+
+# gtsave(
+#   data = excluded_proxies,
+#   filename = here::here("/tables/excluded_proxies_table.pdf"),
+#   expand = 10   # adds a little padding around the table
+# )
+```
 
@@
 
-#saving as a docx file
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
-```
-
-## Table: Output from meta-regressions
+# Saving as an image
+gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.png"))
+
+# For saving as a docx file
+# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
+# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
+```
+
+```{r Table for lnRR rho sensitivity analysis}
+
+# t4 <- data.frame(rho  = rho_range,
+#                  "overall effect"  = sapply(lnRR_VCV_range, function(x) coef(x)),
+#                  "standard error" = sapply(lnRR_VCV_range, function(x) x$se),
+#                  "p-value" = sapply(lnRR_VCV_range, function(x) x$pval),
+#                  "Lower CI" = sapply(lnRR_VCV_range, function(x) x$ci.lb),
+#                  "Upper CI" = sapply(lnRR_VCV_range, function(x) x$ci.ub),
+#                  "Log-likehood" = sapply(lnRR_VCV_range, function(x) fitstats(x)[1,1]),
+#                  "AIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[3,1]),
+#                  "BIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[4,1]),
+#                  "AICc" = sapply(lnRR_VCV_range, function(x) fitstats(x)[5,1]))
+# 
+# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
+# 
+# t4 %>% dfround(4) %>% DT::datatable()
+```
+
+## Table: RoB Meta-regressions
 
@@
 
+# Loading models for blinding performed or not
+lnRR_blinding<-readRDS(here::here("model/lnRR_blinding.rds"))
+SMDH_blinding<-readRDS(here::here("model/SMDH_blinding.rds"))
+
+# Loading models for random sampling assignment performed or not
+lnRR_random_assignment<-readRDS(here::here("model/lnRR_random_assignment.rds"))
+SMDH_random_assignment<-readRDS(here::here("model/SMDH_random_assignment.rds"))
+
+# Loading models for missing data present or not
+lnRR_missing_data<-readRDS(here::here("model/lnRR_missing_data.rds"))
+SMDH_missing_data<-readRDS(here::here("model/SMDH_missing_data.rds"))
+
+```
+
+```{r}
 pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
-
-# Loading models for experimental design
-lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
-SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
-
-# Loading models for parasite type
-lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
-SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
-
-# Loading models for time of green nest material addition
-lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
-SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
-
-# Loading models for the type of trait studied
-lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
-SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
-
-# Loading models for the bird species studied
-lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
-SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
-```
-
-```{r}
 
@@
 ## For lnRR Values
-lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type")%>%
-  bind_rows(extractor_metareg(lnRR_birds,"bird_species"))%>%
-  bind_rows(extractor_metareg(lnRR_trait,"trait_type"))%>%
-  bind_rows(extractor_metareg(lnRR_design,"comparision_type"))%>%
-  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition"))%>%
+lnRR_results_RoB <- extractor_metareg(lnRR_blinding,"blinding")%>%
+  bind_rows(extractor_metareg(lnRR_random_assignment,"random_assignment"))%>%
+  bind_rows(extractor_metareg(lnRR_missing_data,"missing_data"))%>%
   mutate(effect_size = "lnRR")
@@
 ## For SMDH Values
-SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type")%>%
-  bind_rows(extractor_metareg(SMDH_birds,"bird_species"))%>%
-  bind_rows(extractor_metareg(SMDH_trait,"trait_type"))%>%
-  bind_rows(extractor_metareg(SMDH_design,"comparision_type"))%>%
-  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition"))%>%
+SMDH_results_RoB <- extractor_metareg(SMDH_blinding,"blinding")%>%
+  bind_rows(extractor_metareg(SMDH_random_assignment,"random_assignment"))%>%
+  bind_rows(extractor_metareg(SMDH_missing_data,"missing_data"))%>%
   mutate(effect_size = "SMDH")
@@
 # Combine both results
-combined_results <- bind_rows(lnRR_results, SMDH_results)%>%
+combined_results_RoB <- bind_rows(lnRR_results_RoB, SMDH_results_RoB)%>%
   pivot_wider(
@@
 
-# Create moderator header rows for heterogeneity metrics
-  moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
-  select(moderator, effect_size, Q, Q_pval, R2_marginal) %>%
-    distinct()%>%
-    pivot_wider(
-      names_from = effect_size,
-      values_from = c(Q, Q_pval, R2_marginal),
-      names_glue = "{.value}_{effect_size}"
-    )%>%
-  mutate(level = "Heterogeneity ",
-         row_type = "moderator")
-
 # Final combined table with headers and levels
-combined_results <- bind_rows(moderator_header, combined_results) %>%
+ combined_results_RoB <- combined_results_RoB %>%
+   # bind_rows(moderator_header ,combined_results) %>%
   arrange(moderator, row_type)%>% select(-row_type)%>%
   relocate(level, .after = moderator)%>%
-  mutate(moderator=case_when(moderator=="parasite_type"~"Parasite Type",
-                             moderator=="bird_species"~"Bird Species",
-                             moderator=="trait_type"~"Trait Type Category",
-                             moderator=="comparision_type"~"Experimental Design",
-                             moderator=="time_of_gnm_addition"~"Time of Green Nest Material Addition"))%>%
-  mutate(level = case_when(level==1 ~ "Non-aromatic vs. Aromatic",
-                           level==2 ~ "No added material vs. Aromatic",
-                           level==3 ~ "No added material vs. Non-aromatic",
-                           level=="a" ~ "After egg hatching",
-                           level=="b" ~ "Before egg hatching",
-                           level=="c" ~ "Continously through nesting phase",
-                           level=="Parasitic_and_pathogenic"~"Parasitic and Pathogen Related", .default=level))
-
-# Optional: clean up or reorder columns for display
+  mutate(moderator = case_when(
+    moderator == "blinding" ~ "1. Blinding",
+    moderator == "random_assignment" ~ "2. Random assignment to treatment",
+    moderator == "missing_data" ~ "3. Partial Reporting"
+  ))%>%mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Blinding",
+      "2. Random assignment to treatment",
+      "3. Partial Reporting"
+    )
+  ))%>%
+  arrange(moderator)%>%
+  mutate(level = case_when(level=="y" ~ "Yes",
+                           level=="n" ~ "No", .default=level))
+
+# Clean up or reorder columns for display
 # Select and order columns for clarity
-MLMR_table <- combined_results %>%
+RoB_table <- combined_results_RoB %>%
   gt(groupname_col = "moderator") %>%
-  tab_header(title = md("**Multilevel Meta-analytic Models for Exploratory Analyses**")) %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Risk of Bias**")) %>%
   cols_label(
-    Q_lnRR = "Q",
-    Q_pval_lnRR = "Q p-val",
-    R2_marginal_lnRR = "R²_mar",
-    Q_SMDH = "Q",
-    Q_pval_SMDH = "Q p-val",
-    R2_marginal_SMDH = "R²_mar",
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
     level = "Level",
@@
     locations = cells_body(
-      rows = level == "Heterogeneity"
-    ))%>%
-  tab_style(
-    style = cell_text(weight = "bold"),
-    locations = cells_body(
       columns = c(p_value_lnRR),
@@
   tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
-  tab_spanner(label = "SMDH", columns = contains("_SMDH"))
-
-#saving as a docx file
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.docx"))
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.html"))
-```
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
+  )
+
+# saving the image
+gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))
+
+# #saving as a docx file or html
+# gtsave(RoB_table,here::here("tables/SA_RoB_table.docx"))
+# gtsave(RoB_table,here::here("tables/SA_RoB_table.html"))
+```
+
+# -------- TABLES ----------
+
+## Table: Output from meta-regressions
+
+```{r}
+pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
+
+# Loading models for experimental design
+lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
+
+# Loading models for parasite type
+lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
+SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
+
+# Loading models for time of green nest material addition
+lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
+SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
+
+# Loading models for the type of trait studied
+lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
+
+# Loading models for the bird species studied
+lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+```
+
+```{r}
+
+# Let's source our custom function to extract values from the meta-regressions
+source(here::here("functions/extractor_metareg.R"))
+
+## For lnRR Values
+lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type")%>%
+  bind_rows(extractor_metareg(lnRR_birds,"bird_species"))%>%
+  bind_rows(extractor_metareg(lnRR_trait,"trait_type"))%>%
+  bind_rows(extractor_metareg(lnRR_design,"comparision_type"))%>%
+  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition"))%>%
+  mutate(effect_size = "lnRR")
+
+## For SMDH Values
+SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type")%>%
+  bind_rows(extractor_metareg(SMDH_birds,"bird_species"))%>%
+  bind_rows(extractor_metareg(SMDH_trait,"trait_type"))%>%
+  bind_rows(extractor_metareg(SMDH_design,"comparision_type"))%>%
+  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition"))%>%
+  mutate(effect_size = "SMDH")
+
+## Now let's write the table for publication:
+# Combine both results
+combined_results <- bind_rows(lnRR_results, SMDH_results)%>%
+  pivot_wider(
+    id_cols = c(moderator, level),
+    names_from = effect_size,
+    values_from = c(estimate, p_value, CI, PI, k, n),
+    names_glue = "{.value}_{effect_size}"
+  )%>% # Prepare row labels to mimic grouping
+  arrange(moderator, level)%>%
+  mutate(row_type = "level")
+
+# # Create moderator header rows for heterogeneity metrics
+#   moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
+#   select(moderator, effect_size, R2_marginal) %>%
+#     distinct()%>%
+#     pivot_wider(
+#       names_from = effect_size,
+#       values_from = c( R2_marginal),
+#       names_glue = "{.value}_{effect_size}"
+#     )%>%
+#   mutate(level = "Heterogeneity ",
+#          row_type = "moderator")
+
+# Final combined table with headers and levels
+ combined_results <- combined_results %>%
+   # bind_rows(moderator_header ,combined_results) %>%
+  arrange(moderator, row_type)%>% select(-row_type)%>%
+  relocate(level, .after = moderator)%>%
+  mutate(moderator = case_when(
+    moderator == "parasite_type" ~ "5. Parasite\nType",
+    moderator == "bird_species" ~ "3. Bird\nSpecies",
+    moderator == "trait_type" ~ "4. Trait\nCategory",
+    moderator == "comparision_type" ~ "1. Experimental\nDesign",
+    moderator == "time_of_gnm_addition" ~ "2. Time of\nGNM Addition"
+  ))%>%mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Experimental\nDesign",
+      "2. Time of\nGNM Addition",
+      "3. Bird\nSpecies",
+      "4. Trait\nCategory",
+      "5. Parasite\nType"
+    )
+  ))%>%
+  arrange(moderator)%>%
+  mutate(level = case_when(level==1 ~ "Non-aromatic\nvs. Aromatic",
+                           level==2 ~ "No added material\nvs. Aromatic",
+                           level==3 ~ "No added material\nvs. Non-aromatic",
+                           level=="a" ~ "After egg\nhatching",
+                           level=="b" ~ "Before egg\nhatching",
+                           level=="c" ~ "Continously through\nnesting phase",
+                           level=="Parasitic_and_pathogenic"~"Parasitic and\nPathogen Related", .default=level))
+
+# Optional: clean up or reorder columns for display
+# Select and order columns for clarity
+MLMR_table <- combined_results %>%
+  gt(groupname_col = "moderator") %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Exploratory Analyses**")) %>%
+  cols_label(
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
+    level = "Level",
+    estimate_lnRR = "Estimate",
+    CI_lnRR = "95% CI",
+    PI_lnRR = "95% PI",
+    p_value_lnRR = "P-val",
+    k_lnRR = "k",
+    n_lnRR = "n",
+    estimate_SMDH = "Estimate",
+    CI_SMDH = "95% CI",
+    PI_SMDH = "95% PI",
+    p_value_SMDH = "P-val",
+    k_SMDH = "k",
+    n_SMDH = "n"
+  ) %>%
+   sub_missing(
+    columns = everything(),
+    missing_text = ""
+  ) %>%
+  opt_table_outline() %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 12,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "medium",
+    row_group.font.weight = "bold"
+  )   %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)
+    ),
+    locations = cells_body()
+  ) %>%
+  # tab_style(
+  #   style = cell_text(weight = "bold"),
+  #   locations = cells_body(
+  #     rows = level == "Heterogeneity"
+  #   ))%>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_lnRR),
+      rows = p_value_lnRR < 0.05
+    )
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_SMDH),
+      rows = p_value_SMDH < 0.05
+    )
+  )%>%
+  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
+  )
+
+# saving the image
+gtsave(MLMR_table,here::here("tables/MLMR_table.png"))
+
+# #saving as a docx file or html
+# gtsave(MLMR_table,here::here("tables/MLMR_table.docx"))
+# gtsave(MLMR_table,here::here("tables/MLMR_table.html"))
+```

### 2025-08-07 docs/manuscript_GNM.qmd
First mansucript draft

@@
 Importantly, contrary to the structural nest materials (e.g., twigs, mud), GNM is selected from a small, non-random subset of local flora [@clark1985; @petit2002; @garrido-bautista2023], and often characterized by high levels of aromatic volatile compounds (commonly used by songbirds: @mennerat2009b) or secondary metabolites such as oils and resins (commonly used by raptors: @ontiveros2007).
-GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for some times weeks, requires extra time, and in some cases flying outside one’s territory [@mennerat2009].
+GNM is unlikely to be gathered opportunistically, and collecting these uncommon GNM, and replenishing it for sometimes over weeks, requires extra time and, in some cases, flying outside one’s territory [@mennerat2009].
 Thus, the general costs associated with nest-building [@mainwaring2013],  and the additional effort, time and energy devoted to add these non-structural materials suggest an important adaptive function of GNM.
 
-Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015) First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004)), particularly in cavity-nesting species where visual cues inside the nest are limited.
+Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015).
+First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004), particularly in cavity-nesting species where visual cues inside the nest are limited.
 The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (Sturnus vulgaris) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993] The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993].
+The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
@@
 We validated our search using an initial library of 15 relevant articles that we had previously identified (@figsupp-own-library), ensuring all were retrieved.
-Additionally, we used the R package ‘litsearchr’ v1.0.0 [@grames2019], which did not yield any new relevant terms, confirm our queries.
-After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package ‘revtools’ v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
+Additionally, we used the R package ‘litsearchr’ v1.0.0 [@grames2019], which did not yield any new relevant terms, confirming our queries.
+After removing `{r} nrow(full_reference_before_deduplication)-nrow(unique_reference_list)` duplicates using the R package 'revtools' v0.4.1 [@westgate2019], we identified `{r} nrow(unique_reference_list)` unique records.
 
@@
 We prioritised extracting primary data (i.e., measures of central tendency, variance and sample size) from text and tables, or, if that was not possible, from figures (e.g., boxplots) using the R package ‘metaDigitise’ v1.0.1 [@pick2018].
-If primary data were not available, we extracted inferential statistics such as *t* and *F* values or descriptive statistics such as contingency tables (see below), that could be transformed into an effect size.
-Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from them (n = `{r} length(raw_data)`).
+If primary data were not available, we extracted inferential statistics such as t and F values or contingency tables to transform them into effect sizes (see below).
+Last, if the previous steps failed but the article had openly archived data, we calculated the means, standard deviation and sample sizes from each group ourselves (n = `{r} length(raw_data)`).
 
@@
 In this type of comparison, the non-aromatic GNM was considered the treatment, and we coded these `{r} nrow(lnRR_comp3)` and `{r} nrow(SMDH_comp3)` effect sizes, respectively, as non-aromatic GNM vs.
-no added GNM in our moderator “experimental design”.
-Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator “experimental design” was used for subsequent meta-regressions.
-In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons.
+no added GNM in our moderator "experimental design".
+Importantly, our conclusions were robust to the exclusion of these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator "experimental design" was used for subsequent meta-regressions.
+In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons, and accounted for (shared-group) non-independence in our analyses (more below).
 
@@
 For a complete list of variables extracted, see @figsupp-variables .
-We did not include some traits reported in the original studies (k = `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))` studies) in our analyses because it was unclear from the study and our own judgement how they related to fitness (see @figsupp-excluded-proxies).
+During data extraction, we encountered some traits (e.g., white-blood-cell ratio, parent mass; `{r} nrow(excluded_proxies)` effect sizes, n = `{r} length(unique(excluded_proxies$paper_ID))` studies) that we did not include in any of our analyses because it was unclear from the study and our own judgement how these traits related to fitness (see @figsupp-excluded-proxies for the list and reasons of exclusion).
 
@@
 Additionally, to locate grey literature (i.e., unpublished data), we wrote to the corresponding author(s) of all the (n = `{r} (nrow(selected_abstract_screening) - nrow(excluded_fulltext))` articles that passed full-text screening to ask for any potential unpublished data that could be included in our meta-analysis using a standardised email template (@figsupp-email).
-One author provided data for an unpublished study on Blue Tits (see description in @figsupp-unpublished-study) and one of us (MO), provided data for an unpublished study on Common Buzzards (Buteo buteo).
+One author provided data for an unpublished study on Blue Tits (see description in @figsupp-unpublished-study) and one of us (MO) provided data for an unpublished study on Common Buzzards (*Buteo buteo*).
 
@@
 
-Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package ‘metafor’ v4.8-0 [@metafor].
-We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a ‘fitness’ increase in the treatment group.
-In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted prior to analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
+Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package 'metafor' v4.8-0 [@metafor].
+We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a 'fitness' increase in the treatment group.
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted before analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
 SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance; specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1.
@@
 For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the 'escalc' function (measure=OR) from 'metafor' and subsequently converted it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
+Since lnRR cannot be calculated from inferential statistics, dichotomous variables, or traits including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
 
-When calculating each effect size’s associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
+When calculating each effect size's associated sampling variance, we prioritised the number of nests in each group over the number of individuals as the sample size whenever possible to reduce the effect of genetic relatedness non-independence.
 In cases where the same control or treatment group was used across multiple comparisons, sample sizes were adjusted prior to calculating effect sizes by dividing them by the number of times each group was used in a comparison to account for shared group non-independence.
@@
 
-We performed all analyses in R version 4.5.1 [@R-version].
-All multilevel meta-analytical models and meta-regressions were fitted using ‘metafor’ v.4.8-0 [@metafor].
-Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from ‘metafor’ (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
+We performed all analyses in R v4.5.1 [@R-version].
+All multilevel meta-analytical models and meta-regressions were fitted using 'metafor' v.4.8-0 [@metafor].
+Sampling variances were modelled as variance-covariance matrices assuming a 0.5 correlation (ρ) between sampling variances from the same study [@noble2017] using the vcalc function from 'metafor' (See Supplementary Appendix @figsupp-correlation for sensitivity analyses using different values of *ρ*).
 
-We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
+We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
 
@@
 Experiment ID.
-Additionally, since few effect sizes were measured repeatedly, making Repeated trait ID almost identical to the observation-level random effect Observation ID, we excluded it (@figsupp-random-effect).
-Last, we decided to add Population ID since we noticed after extracting the data but before any analyses that several studies were performed in the same geographical locations.
+Additionally, few effect sizes were measured repeatedly, making Repeated trait ID almost identical to Observation ID (@figsupp-random-effect), so we excluded Repeated trait ID.
+Last, we decided to add Population ID since we noticed after extracting the data, but before any analyses, that several studies were performed in the same geographical locations.
 
@@
 We used the `rma.mv` function from the 'metafor' package using the 'REML' method and a *t* distribution for calculating the test statistics and confidence intervals for the moderators.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
 For all intercept-only models, we estimated the total amount of absolute heterogeneity ($σ^2$; the total variation not explained by sampling error), its sources or relative heterogeneity ($I^2$), mean-standardised metric (CVH2) and variance-mean-standardised metric of heterogeneity (M2) following the pluralistic approach suggested by @yang2024a .
 
-To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator ‘hypothesis’ (levels: courtship, parental care, both).
-For this and all meta-regressions, we estimated $R_{marginal}^2$,which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
+To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator 'hypothesis' (levels: courtship, parental care, both).
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
 Unless stated otherwise, all meta-regressions correspond to unimoderator meta-regressions.
@@
 
-In addition, we performed X additional multilevel meta-regressions intended to explore the potential threats to the internal validity of each study on our conclusions (i.e., Risk of Bias or RoB) following recommendations in Culina et al.
-(2025).
-…
+In addition, we performed three additional pre-registered multilevel meta-regressions intended to explore the potential threats to the internal validity of each study on our conclusions (i.e., Risk of Bias or RoB) following recommendations in @culina2025 .
+We evaluated the effects of (1) blinding (whether outcome assessors were blinded to the experimental group), (2) random assignment to treatment, and (3) partial reporting (whether all measured outcomes were completely reported or only a subset).
+For each RoB category, we coded studies (levels: yes, no) and included each category as a moderator in a meta-regression separately for both lnRR and SMD(H).
 
@@
 
-Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness outcomes in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness estimates in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
 First, lnRR showed an average statistically non-significant increase in fitness outcomes of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in GNM (@figmain-mean-effect A; lnRR = `{r} sprintf("%.3f", coef(intercept_lnRR))`, 95% CI: \[`{r} sprintf("%.3f", intercept_lnRR$ci.lb)` to `{r} sprintf("%.3f", intercept_lnRR$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_lnRR)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_lnRR)$pi.ub)`\], p-value = `{r} sprintf("%.3f", intercept_lnRR$pval)`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`) but heterogeneity among effect sizes was high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_lnRR$sigma2))` (*Q* = `{r} sprintf("%.1f",sum(intercept_lnRR$QE))`, p \< 0.001), the measures of relative (*I^2^~total~* = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_lnRR)[1])`%) and standardised heterogeneity (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_lnRR)[1])` and M2~total =~ `{r} sprintf("%.2f", orchaRd::m2_ml(intercept_lnRR)[1])`) suggested high heterogeneity across effect sizes.
 
 Second, SMD(H) showed an average statistically significant increase in fitness outcomes in nests with an experimental increase of GNM (@figmain-mean-effect B; SMD(H) = `{r} sprintf("%.3f", coef(intercept_SMDH))`, 95% CI: \[`{r} sprintf("%.3f",(intercept_SMDH)$ci.lb)` to `{r} sprintf("%.3f",(intercept_SMDH)$ci.ub)`\], 95% PI: \[`{r} sprintf("%.3f", predict(intercept_SMDH)$pi.lb)` to `{r} sprintf("%.3f", predict(intercept_SMDH)$pi.ub)`\], p-value = `{r} sprintf("%.3f",intercept_SMDH$pval)`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`), but heterogeneity among effect sizes was moderate to high.
-Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (Q = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (I^2^~total~ = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
+Total raw heterogeneity (𝜎^2^) was `{r} sprintf("%.3f",sum(intercept_SMDH$sigma2))` (*Q* = `{r} sprintf("%.1f",sum(intercept_SMDH$QE))`, p \< 0.001), relative heterogeneity was smaller compared to that of lnRR (*I^2^~total~* = `{r} sprintf("%.1f",orchaRd::i2_ml(intercept_SMDH)[1])`%) and the standardised heterogeneity metrics (CVH2~total~ = `{r} sprintf("%.2f", orchaRd::cvh2_ml(intercept_SMDH)[1])` and M2~total =~ `{r} sprintf("%.2f",orchaRd::m2_ml(intercept_SMDH)[1])`) lied between the 50th and 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution [@yang2024a].
 For lnRR, all three heterogeneity metrics exceeded the 75th percentile benchmark (see [@supp-tab-heterogeneity] for detailed estimates of heterogeneity).
@@
 car::linearHypothesis(SMDH_design_pc, rbind(c(0,1,-1)))
+
+#---------------------------------------------------------------------------
+#---------------------------------------------------------------------------
+#---------------------------------------------------------------------------
+
+# Now loading the models for RoB Meta-regressions
+
+# Loading models for blinding performed or not
+lnRR_blinding<-readRDS(here::here("model/lnRR_blinding.rds"))
+SMDH_blinding<-readRDS(here::here("model/SMDH_blinding.rds"))
+
+summary_lnRR_blinding<-extractor_metareg(lnRR_blinding,"blinding")
+summary_SMDH_blinding<-extractor_metareg(SMDH_blinding,"blinding")
+
+# Loading models for random sampling assignment performed or not
+lnRR_random_assignment<-readRDS(here::here("model/lnRR_random_assignment.rds"))
+SMDH_random_assignment<-readRDS(here::here("model/SMDH_random_assignment.rds"))
+
+summary_lnRR_random_assignment<-extractor_metareg(lnRR_random_assignment,"random_assignment")
+summary_SMDH_random_assignment<-extractor_metareg(SMDH_random_assignment,"random_assignment")
+
+# Loading models for missing data present or not
+lnRR_missing_data<-readRDS(here::here("model/lnRR_missing_data.rds"))
+SMDH_missing_data<-readRDS(here::here("model/SMDH_missing_data.rds"))
+
+summary_lnRR_missing_data<-extractor_metareg(lnRR_missing_data,"missing_data")
+summary_SMDH_missing_data<-extractor_metareg(SMDH_missing_data,"missing_data")
+
 ```
@@
 
-Third, Third, although none of the species-specific mean estimates were statistically significant, most were positive [[\@figsupp-MR](C-D); @tabmain-MLMR], and bird species identity explained a non-negligible amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
-Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant and reproduction marginally so, both only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; SMDH~reproduction~ = `{r} summary_SMDH_trait$estimate[6]`, 95% CI: `{r} summary_SMDH_trait$CI[6]`, 95% PI: `{r} summary_SMDH_trait$PI[6]`, p-value = `{r} summary_SMDH_trait$p_value[6]`, k = `{r} summary_SMDH_trait$k[6]`, n = `{r} summary_SMDH_trait$n[6]`) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
-Last, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically signficantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+Third, although none of the species-specific mean estimates were statistically significant, most were positive [[\@figsupp-MR](C-D); @tabmain-MLMR], and bird species identity explained a non-negligible amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
+Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; @figsupp-MR; @tabmain-MLMR) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Fifth, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically significantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+
+Lastly, the risk of bias categories we evaluated (i.e., blinding, random assignment to each treatment and partial reporting) were not statistically significant for lnRR ([@tabsupp-SA-RoB]).
+SMD(H) was positive and statistically significant for studies without blinding (SMD(H)~No Blinding~ = `{r} summary_SMDH_blinding$estimate[1]`, 95% CI: `{r} summary_SMDH_blinding$CI[1]`, 95% PI: `{r} summary_SMDH_blinding$PI[1]`, p-value = `{r} summary_SMDH_blinding$p_value[1]`, k = `{r} summary_SMDH_blinding$k[1]`, n = `{r} summary_SMDH_blinding$n[1]`; @tabsupp-SA-RoB), with random assignment to treatment (SMD(H)~Random Assignment~ = `{r} summary_SMDH_random_assignment$estimate[2]`, 95% CI: `{r} summary_SMDH_random_assignment$CI[2]`, 95% PI: `{r} summary_SMDH_random_assignment$PI[2]`, p-value = `{r} summary_SMDH_random_assignment$p_value[2]`, k = `{r} summary_SMDH_random_assignment$k[2]`, n = `{r} summary_SMDH_random_assignment$n[2]`; @tabsupp-SA-RoB) and where no data was missing (SMD(H)~No Partial Reporting~ = `{r} summary_SMDH_missing_data$estimate[1]`, 95% CI: `{r} summary_SMDH_missing_data$CI[1]`, 95% PI: `{r} summary_SMDH_missing_data$PI[1]`, p-value = `{r} summary_SMDH_missing_data$p_value[1]`, k = `{r} summary_SMDH_missing_data$k[1]`, n = `{r} summary_SMDH_missing_data$n[1]`; @tabsupp-SA-RoB).
+Notably, other levels of each category included fewer than four studies, indicating that the observed significance likely reflects the higher statistical power in the larger sample level rather than any systematic bias.
+All the three categories for risk of bias explained very little heterogeneity ($R^2_{marginal(lnRR)}$\> `{r} as.double(round(orchaRd::r2_ml(lnRR_blinding)*100,1))[1]`%; $R^2_{marginal(SMD(H))}$\> `{r} as.double(round(orchaRd::r2_ml(SMDH_random_assignment)*100,1))[1]`%).
 
@@
 
+```{r}
+lnRR_small_study<-readRDS(here::here("model/lnRR_small_study.rds"))
+SMDH_small_study<-readRDS(here::here("model/SMDH_small_study.rds"))
+
+lnRR_decline_eff<-readRDS(here::here("model/lnRR_decline_eff.rds"))
+SMDH_decline_eff<-readRDS(here::here("model/SMDH_decline_eff.rds"))
+```
+
+We found no clear evidence for publication bias in the published literature [@figsupp-pub-bias].
+There was no evidence for small-study effect for lnRR i.e.
+studies with smaller sample sizes did not have larger effect size estimates (lnRR~intercept~= `{r} sprintf("%.3f", coef(lnRR_small_study)[1])`, 95% CI: \[`{r} sprintf("%.3f", lnRR_small_study$ci.lb[1])`, `{r} sprintf("%.3f", lnRR_small_study$ci.ub[1])`\], p-value = `{r} sprintf("%.3f", lnRR_small_study$pval[1])`, lnRR~slope~ = `{r} sprintf("%.3f", coef(lnRR_small_study)[2])`, 95% CI: \[`{r} sprintf("%.3f", lnRR_small_study$ci.lb[2])`; `{r} sprintf("%.3f", lnRR_small_study$ci.ub[2])`\], p-value = `{r} sprintf("%.3f", lnRR_small_study$pval[2])`, k = `{r} lnRR_small_study$k`, n = `{r} length(lnRR_small_study$s.levels.f[[1]])`, $R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_small_study)*100,1))[1]`%).
+There was a tendency for effect sizes to be larger when sample size was smaller but this relationship was not statistically significant (SMDH~slope~ = `{r} sprintf("%.3f", coef(SMDH_small_study)[2])`, 95% CI: \[`{r} sprintf("%.3f", SMDH_small_study$ci.lb[2])`, `{r} sprintf("%.3f", SMDH_small_study$ci.ub[2])`\], p-value = `{r} sprintf("%.3f", SMDH_small_study$pval[2])`, k = `{r} SMDH_small_study$k`, n = `{r} length(SMDH_small_study$s.levels.f[[1]])`, $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_small_study)*100,1))[1]`%).
+After adjusting for the funnelplot asymmetry (i.e., small study effect), the overall effect of GNM on fitness outcomes disappeared (SMDH~intercept~ = `{r} sprintf("%.3f", coef(SMDH_small_study)[1])`, 95% CI: \[`{r} sprintf("%.3f", SMDH_small_study$ci.lb[1])`, `{r} sprintf("%.3f", SMDH_small_study$ci.ub[1])`\], p-value = `{r} sprintf("%.3f", SMDH_small_study$pval[1])`).
+
+Since published effect sizes did not seem to change considerably over time, our analyses suggest no clear evidence of decline effects (i.e., time-lag bias) in published effect sizes (lnRR~intercept~ = `{r} sprintf("%.3f", coef(lnRR_decline_eff)[1])`, 95% CI: \[`{r} sprintf("%.3f", lnRR_decline_eff$ci.lb[1])`; `{r} sprintf("%.3f", lnRR_decline_eff$ci.ub[1])`\], p-value = `{r} sprintf("%.3f", lnRR_decline_eff$pval[1])`, lnRR~slope~ = `{r} sprintf("%.3f", coef(lnRR_decline_eff)[2])`, 95% CI: \[`{r} sprintf("%.3f", lnRR_decline_eff$ci.lb[2])` to `{r} sprintf("%.3f", lnRR_decline_eff$ci.ub[2])`\], p-value = `{r} sprintf("%.3f", lnRR_decline_eff$pval[2])`, k = `{r} lnRR_small_study$k`, n = `{r} length(lnRR_decline_eff$s.levels.f[[1]])`, $R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_decline_eff)*100,1))[1]`%; SMDH~intercept~ = `{r} sprintf("%.3f", coef(SMDH_decline_eff)[1])`, 95% CI: \[`{r} sprintf("%.3f", SMDH_decline_eff$ci.lb[1])` to `{r} sprintf("%.3f", SMDH_decline_eff$ci.ub[1])`\], p-value = `{r} sprintf("%.3f", SMDH_decline_eff$pval[1])`, SMDH~slope~ = `{r} sprintf("%.3f", coef(SMDH_decline_eff)[2])`, 95% CI: \[`{r} sprintf("%.3f", SMDH_decline_eff$ci.lb[2])` to `{r} sprintf("%.3f", SMDH_decline_eff$ci.ub[2])`\], p-value = `{r} sprintf("%.3f", SMDH_decline_eff$pval[2])`, k = `{r} SMDH_decline_eff$k`, n = `{r} length(SMDH_decline_eff$s.levels.f[[1]])`, $R^2_{marginal(SMD(H))}$ = `{r} as.double(round(orchaRd::r2_ml(SMDH_decline_eff)*100,1))[1]`%).
+
 # Discussion
 
-Our pre-registered systematic review and meta-analysis provides the first quantitative synthesis of experimental studies on green nest material (GNM) across birds and reveals that, on average, supplementing nests with GNM yields only small benefits.
+Our pre-registered systematic review and meta-analysis provides the quantitative synthesis of adaptive function of green nest material (GNM) across birds through experimental evidence testing this relationship.
+We found that, on average, supplementing nests with GNM has a small positive effect on fitness proxies.
+Using two different effect size metrics, lnRR and SMD(H), and various sensitivity analyses, we found the direction of the effect to be consistent, which was statistically significant in the case of SMD(H).
+Sensitivity analyses, showed that the effect for both lnRR and SMD(H) slightly increased while the p-values decreased.
+There was moderate to high heterogeneity among effect sizes.
+We explored this heterogeneity through several biological and methodological moderators that we predicted could explain the differences in the fitness proxies, which accounted for some variation.
+However, a substantial portion of heterogeneity remains unexplained, highlighting the context-dependency of this effect as also suggested in the previous reviews on the topic [@dubiec2013; @scott-baumann2015].
+
 The strength of the overall effects of GNM differed between the effect size metric used.
-Using the lnRR we found a non-significant 1.6% increase in overall fitness proxies, whereas the SMD(H) indicated a small but statistically significant positive effect (SMD(H)= 0.179).
-These differences in overall effect size magnitude likely reflect the underlying biological and statistical assumptions - lnRR incorporates the mean difference at a multiplicative scale whereas SMDH expresses the difference on an additive scale.
-There was moderate to high heterogeneity among the effect sizes, which we tried to understand using several biological and methodological moderators.
-The difference in relative heterogeneity (I^2^) between the two effect sizes aligns with broader trends observed in meta-analysis in ecology and evolution [@yang2024].
+The difference between the two effect size metrics (lnRR and SMD(H)) is likely due to the distinct assumptions regarding the underlying biological processes and the statistical properties.
+While lnRR reflects the multiplicative effect of the treatment, SMD(H) expresses the effect on an additive scale.
+These divergent results highlight the importance of choosing appropriate effect size metrics that align with the biological data at hand or in cases where several different types of measures are present, using both [@yang2024].
+The difference in relative heterogeneity (I^2^) between the two effect sizes also aligns with broader trends observed in meta-analysis in ecology and evolution [@yang2024a].
 
-Contrary to long-standing verbal models, neither the courtship hypothesis (visual/olfactory signalling) nor the parental-care hypothesis (parasite repellency or pharmacological "drug" effects) emerged as a consistent driver of these small gains.
-Effect estimates associated with courtship traits were positive but non-significant, and those associated with nestling protection were essentially zero.
-In other words, current evidence does not allow us to attribute the weak average benefit of GNM to a single prevailing mechanism.
-This result mirrors the idiosyncratic outcomes scattered through the primary literature and indicates that future tests will need to measure multiple pathways simultaneously---ideally pairing behavioural observations with direct assays of ectoparasites, microbial load, and nest-air volatiles.
+We found no clear evidence supporting the long-standing mechanistic hypotheses explaining the adaptive function of GNM.
+The current evidence does not allow us to attribute the fitness benefit of GNM to a single mechanism.
+In the reviewed literature, only a few fitness proxies could be directly linked to courtship traits despite several studies looking into this mechanism.
+Traits such as courtship time, male provisioning, which are more closely linked to courtship hypothesis, showed no statistically significant effects.
+Contrary to our expectations, proxies associated with the parental-care hypothesis (i.e., nest protection and drug hypotheses combined), such as parasite loads, nestling health, had no adaptive benefits.
+Only proxies that could not be clearly assigned to either of the mechanistic hypotheses, such as survival rate, nestling morphological estimates, which we categorized as being associated with "both" the mechanisms, showed a positive effect of GNM addition.
+This ambiguity reflects the challenge of interpreting many fitness proxies in relation to underlying mechanisms, as they may be influenced by multiple overlapping processes.
 
-Importantly, our results reveal that the commonly studied mechanistic hypotheses of GNM --whether through sexual signalling, parasite reduction, or direct nestling benefits-- lack consistent empirical support across studies.
+Among the various predictors that we tested in our meta-regressions, methodological moderators accounted for substantially large part of the heterogeneity in effect sizes as compared to biological moderators.
+Our results highlight that the experimental design strongly influences the observed effect of GNM on fitness proxies.
+Experiments comparing nests with no added material and aromatic material showed larger positive effects.
+There was a `{r} round((exp(as.double(summary_lnRR_design$estimate[2]))-1)*100)`% increase in the fitness proxies in nests with GNM for experiments in this experimental design.
+The comparison between non-aromatic and aromatic GNM had a near zero effect.
+This suggests that simply adding non-aromatic materials, though often overlooked, can also contribute to fitness-related benefits through other alternative mechanisms.
+These benefits could include increasing the crypticity of a nest [@skutch1957], providing insulation to the eggs [@mertens1977], providing protection from sun or simply helping maintain the temperature and micro-climate of the nest.
+In other words, the aromatic property of GNM may not be the driving factor of the adaptive benefit.
+Experiments comparing no added material with non-aromatic GNM were negative.
+It is important to note that this particular comparison was highly underpowered to make meaningful conclusions.
 
-Second paragraph
+Additionally, the continuous addition of GNM throughout the nesting period showed greater positive effects compared to addition limited to either before or after egg hatching.
+Previous work on Blue Tits has shown that the head-space concentration of active compounds in the aromatic plants can reduce within 24 hours [@petit2002], and females often replace removed herbs [@mennerat2008; @banbura1995].
+This repeated addition has been suggested as a mechanism to maintain an aromatic environment to repel parasites or reduce their abundance.
+However, this larger adaptive benefit from continuous addition of GNM through the nesting phase can also be explained by the structural or micro-climate benefits of the GNM.
+Fresh GNM can act as a renewable lining that improves nest insulation and humidity buffering as the nesting material gradually desiccates [@mertens1977; @taverner1933].
+Such micro-climate stability can accelerate nestling development while reducing thermoregulatory costs for the parents [@mainwaring2013].
+Regular replenishment could also help replace the wilted material in the nest thus maintaining the structure of the nest and may have hygiene function by diluting faecal matter or food debris in the nest [@peralta-sanchez2010].
 
--   Difference between the hypothesis, whether you can do it or not
+Among the various types of fitness proxies, morphological outcomes showed the largest positive effect in nests with GNM.
+Morphological traits such as nestling body mass, tarsus length, or wing length are often used as indicators of offspring body condition.
+All other trait types, including physiology, reproduction, phenology, and behaviour, showed small to moderate positive effects that were not statistically significant, whereas the proxies related to parasite or pathogen load showed weak inconsistent effects.
+Our results suggest that GNM may have more pronounced effects on development or growth-related traits but not on parasite defense.
+This result further emphasizes that there is no clear evidence supporting the nest protection hypothesis, despite its prominence in the literature.
+While the drug hypothesis has been proposed as an alternative explanation for enhanced offspring condition, several other mechanisms could also be at play.
+For example, improved morphological condition of the offspring could result from enhanced micro-climate of the nest, better incubation of the eggs or indirectly through sexually selected male traits, as suggested by courtship hypothesis.
+The diversity of fitness proxies and their varied biological interpretations makes it difficult to disentangle the precise pathways through which GNM impacts fitness.
 
--   Experimental design difference.. importance of aromatic vs. Non-aromatic (are the same that aroma per say) and time of addition
+We found that the overall effect of GNM on fitness proxies was highly heterogeneous and was mainly associated with within-study variation rather than among-study variation.
+This suggests that, once methodological and biological factors within studies are accounted for, the overall effect of GNM in our meta-analysis is consistent across studies as potentially generalisable.
+Among the biological moderators that we explored, species identity explained some of the observed heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`%; $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%), indicating some species-specific effects.
+Trait-type also accounted for a small proportion of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+The intrinsic differences in life-history traits, nest construction or habitat condition across bird species may influence how GNM affects fitness-related measures.
+All other biological moderators explained a negligible amount of heterogeneity.
+About one-fourth of the observed heterogeneity in effect sizes was explained by experimental design.
+This methodological moderator is an important factor in the study design in detecting the adaptive benefit of GNM.
 
-    Third paragraph :
+We found high reporting quality in the primary study included in our meta-analysis, with only 0.06% partial reporting.
+There was no evidence for time-lag bias, suggesting that the results have not systematically declined over time.
+However, there was evidence of potential small-study effects suggesting slightly larger effects in smaller studies, but this relationship was only present in case of SMD(H) and lacked statistical support.
+However, after adjusting for this, the overall effect of GNM on fitness outcomes in SMD(H) was no longer significant, indicating that the observed benefit may be sensitive to publication bias assumptions and should be interpreted with caution.
+We found that a considerable number of primary studies had very low sample sizes.`{r} as.double(round((nrow(dataset_analysis%>%filter(n_experiment<10|n_control<10))/nrow(dataset_analysis))*100))[1]`% of the effect sizes were based on fewer than 10 nests per group.
 
-How much heterogeneity is explained..
-
-Limitations and issues about the data.. mechanism, publication bias.. species are few tested, few labs..
-
-Proxies that are closer..
-
-If study ID is
-
-Temp Discussion:
-
-**Discussion**
-
-[manuscript_GNM]{.underline}.
-The discrepancy between metrics underscores how the inferred magnitude of benefit depends on the underlying scale: lnRR captures proportional shifts, whereas SMDᴴ reflects absolute shifts that are sensitive to among-study variance.
-Nonetheless, both converge on the same biological interpretation---if GNM is adaptive, the advantage appears subtle rather than dramatic, and it is expressed against a backdrop of substantial heterogeneity (I² ≈ 66--99 %).
-
-Methodological context explained far more of the variance than biological hypothesis.
-Designs that compared nests with **no added material** versus **aromatic material** produced the largest positive effects (lnRR ≈ 0.15; SMDᴴ ≈ 0.84), whereas contrasts between **no material** and **non-aromatic plant matter** were negative, and the canonical **aromatic vs.
-non-aromatic** comparison was indistinguishable from zero.
-These patterns emphasise that simply adding any material can alter micro-climate, and that the perceived "aromatic benefit" may in part reflect removing a structural disadvantage in controls rather than an odour-specific mechanism.
-In addition, time of addition mattered: experiments that replenished GNM continuously throughout nesting detected stronger benefits (significant under SMDᴴ) than those adding it only before or after hatching, hinting that persistence of volatile release or parental display may be important [manuscript_GNM]{.underline}.
-
-Despite these insights, most of the heterogeneity remains unexplained.
-Experimental design alone accounted for roughly a third of total variance, whereas parasite type, trait category, timing, and species identity each explained ≤ 8 % [manuscript_GNM]{.underline}.
-The residual scatter likely stems from taxonomic and geographic bias---82 % of effect sizes come from just three passerines (blue tit, spotless starling, European starling) studied at 16 sites, many of them by the same research groups.
-Publication-bias diagnostics were equivocal, yet small-study effects cannot be excluded given the prevalence of datasets with ≤ 5 nests per group and the tendency to publish novel positive outcomes.
-Together these limitations caution against broad generalisation and point to the need for coordinated multi-lab efforts on under-represented taxa (e.g., open-cup builders, raptors).
-
-Several practical recommendations follow.
-First, future experiments should adopt fully factorial designs that separate **structure** (any plant vs.
-none) from **chemistry** (aromatic vs.
-non-aromatic) and track volatilome dynamics across the nesting cycle.
-Second, fitness proxies should move beyond morphology---currently the only trait category with a significant positive response---to harder endpoints such as fledging success, juvenile recruitment, and parental survival.
-Third, sharing raw data and negative results will be essential to reduce residual heterogeneity and clarify whether the modest average benefit we detect is biologically meaningful or a statistical artefact of design choices.
-
-In summary, our review shows that adding green plant material to bird nests can increase fitness‐related measures, but the effect is small, context-dependent, and not yet pinned to a single mechanism.
-By refining experimental designs, broadening taxonomic coverage, and integrating chemical ecology with behavioural ecology, the next generation of studies can resolve whether GNM is truly an adaptive extended phenotype or merely a conspicuous but weak contributor to avian reproductive success.
-
-Nicely looking colours!!!!
-Alright, alright.
-In short, ask me more if it is not clear.
-When you ran these 2 meta-regressions specifically, you normally would run them twice, once without the intercept from which you obtain the values you are presenting (i.e., the real lnRR and SMD(H) estimates specific for each off the three levels: Parental Care, Courtship, and Both), and then you would run them with the intercept.
-In the latter, the intercept, unless you changed the order of the levels in the moderator (which is a factor), would represent "Both", and the output would not tell you the difference between the estimate of level "Courtship" and "Both", and "Parental Care" and "Both" (i.e., the estimate is a difference, e.g. lnRRboth = 0.025 - lnRRcourtship = 0.038 = -0.13) and whether that difference is statistically significant.
-We want to show whether any differences between the levels are statistically significant, so we should present these p-values to say whether each of the pair-wise comparisons differs statistically or not.
-For you to know if "Courtship" and "Parental Care", you need to run an extra line of code, because from the model you only get the information about the difference between all levels of the factor (in this case, "Courtship" and "Parental Care") and the reference level AKA intercept (in this case "Both"). \
-\
-You can use:\
-car::linearHypothesis(model, rbind(c(0,1,-1)))\
-\
-For more: [https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms](https://www.google.com/url?q=https://www.metafor-project.org/doku.php/tips:testing_factors_lincoms&sa=D&source=docs&ust=1751963317237496&usg=AOvVaw3NHnLsaKPtM6xq0VTTbXZO)
-
-Importantly, if the moderator would be a continuous moderator, e.g.
-publication year, you do not need to do any extra test, but should present the estimates for the intercept in the model as well as the estimates for the slope.
-When the moderator is continuous, you do not remove the intercept (i.e., no -1).
-Let me know if something is unclear.
-Good job, looking forward to reading the manuscript.
+Overall, our meta-analysis found a small positive effect of green nest material (GNM) on fitness estimates, the mechanisms and magnitude of these effects remain largely unclear and context-dependent.
+Future primary studies should focus on increasing sample sizes to improve statistical power.
+A substantial portion of effect sizes in this literature are derived from small, underpowered studies, which not only inflate heterogeneity but also contribute to uncertainty in effect estimates.
+Additionally, the selection of fitness proxies should be guided by their biological relevance and prioritizing proxies that clearly demonstrate survival or reproductive success, such as fledging rates, recruitment, etc., would provide a more robust foundation for future mechanistic investigations.
+Furthermore, studies remain heavily biased towards just three bird species, limiting our ability to infer broad patterns of this behaviour.
+Expanding the scope to other bird species with diverse nesting ecologies and habitat conditions can be useful in understanding the adaptive benefits of this behaviour.
 
@@
 |  |  |  |  |  |  |
-|------------|------------|------------|------------|------------|------------|
+|----|----|----|----|----|----|
 | **Checklist item** | I**tem score** | **Sub-item number** | **Sub-item** | **Reported by authors?** | **Notes** |
@@
 
+### Risk of Bias
+
+![](tables/SA_RoB_table.png){#tabsupp-SA-RoB}
+
+### Publication Bias
+
+![](figures/Figure_publication_bias.png){#figsupp-pub-bias}
+
 # Maybe-maybe stuff
@@
 ![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
-
-###

### 2025-08-16 code/07_data_analysis.Rmd
Added another sensitivity analysis without non-aromatic and aromatic comparison

@@
 
-pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs)
+pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs,readr)
 
@@
 # saving the model
-# saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))
-
-# saving the dataset for this model
-# write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
+ saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))
+
+# saving the dataset for this model
+ write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
 ```
@@
 # saving the model
-# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
-
-# saving the dataset for this model
-# write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
+ saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
+
+# saving the dataset for this model
+ write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
 ```
@@
 
+Are the meta-regression robust to this analysis
+
+```{r}
+
+dataset_lnRR_design_flagged_no_missingES <- lnRR_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design_flagged_no_missingES <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_flagged_no_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_flagged_no_missingE <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_flagged_no_missingES)
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design_flagged_no_missingES <-SMDH_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design_flagged_no_missingES <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design_flagged_no_missingES,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design_flagged_no_missingE <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design_flagged_no_missingES)
+
+```
+
 ### No inferential stats for SMDH: effect sizes calculated from means, SDs, and sample size
@@
 
+# Sensitivity Analysis: Excluding Non-aromatic Vs. Aromatic
+
+We are aware that removing over 50% of the dataset will cause some moderator levels to drop out.
+But if our goal is to critically examine the role of aromaticity and potentially argue that its importance has been overstated, this could be a very informative step.
+
+```{r}
+
+## For the lnRR effect size...
+dataset_lnRR_no_comp1<-dataset_lnRR%>%filter(comparision_type!=1 | is.na(comparision_type))
+## Only some rows are removed... 
+nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp1)
+
+VCV_lnRR_no_comp1 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_lnRR_no_comp1<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_lnRR_no_comp1)
+
+# Saving the model
+saveRDS(SA_lnRR_no_comp1, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp1.csv"))
+
+#----------------------------------------------------------------------------
+# for  SMDH  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_SMDH_no_comp1<-dataset_SMDH%>%filter(comparision_type!=1 | is.na(comparision_type))
+## Only some rows are removed... 
+nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp1)
+
+VCV_SMDH_no_comp1 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+
+SA_SMDH_no_comp1<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+                    mods = ~ 1,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                    control = list(optimizer="optim"),
+                    test = "t",
+                    data = dataset_SMDH_no_comp1)
+
+# Saving the model
+saveRDS(SA_SMDH_no_comp1, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp1.csv"))
+
+#----------------------------------------------------------------------------
+# Rerunning the two mechanistic hypothesis meta-regressions with those effect sizes excluded
+#----------------------------------------------------------------------------
+
+lnRR_hypothesis_no_comp1 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_no_comp1,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_no_comp1)
+# Save model
+saveRDS(lnRR_hypothesis_no_comp1, file = here::here("model/lnRR_hypothesis_no_comp1.rds"))
+
+SMDH_hypothesis_no_comp1 <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_no_comp1,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + Hypothesis,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_no_comp1)
+
+# Save model
+saveRDS(SMDH_hypothesis_no_comp1, file = here::here("model/SMDH_hypothesis_no_comp1.rds"))
+
+#----------------------------------------------------------------------------
+## Now re-running all the 5 meta-regressions once again
+#----------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_lnRR_design_no_comp1 <- dataset_lnRR_no_comp1 %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design_no_comp1 <- vcalc(vi = lnRR_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_lnRR_design_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+lnRR_design_no_comp1 <-
+  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+                    V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_lnRR_design_no_comp1 )
+
+# Saving the model
+saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))
+
+# This analysis only includes dataset that has a proxy relating to comaparision type
+dataset_SMDH_design_no_comp1 <- dataset_SMDH_no_comp1 %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design_no_comp1 <- vcalc(vi = SMDH_variance,
+                  cluster = paper_ID,
+                  obs = Observation_ID,
+                  data = dataset_SMDH_design_no_comp1,
+                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+                  )
+SMDH_design_no_comp1 <-
+  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+                    V = VCV_SMDH_design_no_comp1 ,# specify lnRR's sampling variance;
+                    mods = ~ - 1 + comparision_type,
+                    random = list(~ 1 | paper_ID,
+                                  ~ 1 | Observation_ID,
+                                  ~ 1 | group_ID_coded,
+                                  ~ 1 | population_ID,
+                                  ~ 1 | bird_species),
+                    method = "REML",
+                  test = "t",
+                  control = list(optimizer="optim"),
+                  data = dataset_SMDH_design_no_comp1 )
+
+# Saving the model
+saveRDS(SMDH_design_no_comp1, file = here::here("model/SMDH_design_no_comp1.rds"))
+```
+
+\
+
 # Risk of Bias
 
-6\. Blinding: (Levels: yes, no(
-
-7\. Random Assignment: (Levels: yes, no)
-
-8\. Missing Data: (Levels: yes, no)
-
-Note that the specific subset of data for each meta-regression may differ based on the data availability (e.g., information about the type of parasites is only available for effect sizes based on parasite/pathogen related fitness proxy).
-We will conduct meta-regression on suitable subsets of data for each analysis, provided we have sufficient effect sizes per moderator level (i.e., at least 5 effect sizes per moderator level).
-
-::: callout-important
-## Phylogenetic Effects
-
-Note also that if we obtain additional effect sizes for other bird species after we update our search and/or contact authors, our models may need to account for phylogenetic nonindependence via the inclusion of two additional random effects: "species" and "phylogeny" following Cinar et al.
-(2022).
-:::
-
-## Other Analysis
-
-### Risk of Bias Assessment
-
--   RoB - The outcome will be presented in the form of a [**summary table**]{.underline}. We will conduct uni-moderator meta-regressions using these variables.
+We have pre-registered the Risk Of Bias analysis, the three we will explore:
+
+1.  **Blinding**
+
+    ```{r}
+    unique(dataset_lnRR$blinding)
+
+    lnRR_blinding <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + blinding,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_blinding, file = here::here("model/lnRR_blinding.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_blinding.csv"))
+
+    SMDH_blinding <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + blinding,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_blinding, file = here::here("model/SMDH_blinding.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_blinding.csv"))
+    ```
+
+2.  Random Assignment
+
+    ```{r}
+
+    unique(dataset_lnRR$random_assignment)
+
+    lnRR_random_assignment <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + random_assignment,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_random_assignment, file = here::here("model/lnRR_random_assignment.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_random_assignment.csv"))
+
+    SMDH_random_assignment <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + random_assignment,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_random_assignment, file = here::here("model/SMDH_random_assignment.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_random_assignment.csv"))
+    ```
+
+3.  Missing Vs. Not Missing
+
+    ```{r}
+
+    unique(dataset_lnRR$missing_data)
+
+    lnRR_missing_data <-
+      metafor::rma.mv(yi = lnRR_sign,
+                        V = VCV_lnRR,
+                        mods = ~ - 1 + missing_data,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_lnRR)
+
+    # Saving the model
+    saveRDS(lnRR_missing_data, file = here::here("model/lnRR_missing_data.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_missing_data.csv"))
+
+    SMDH_missing_data <-metafor::rma.mv(yi = SMDH_sign, 
+                        V = VCV_SMDH,
+                        mods = ~ - 1 + missing_data,
+                        random = list(~ 1 | paper_ID,
+                                      ~ 1 | Observation_ID,
+                                      ~ 1 | group_ID_coded,
+                                      ~ 1 | population_ID,
+                                      ~ 1 | bird_species),
+                        method = "REML",
+                      test = "t",
+                      control = list(optimizer="optim"),
+                      data = dataset_SMDH)
+
+    # Saving the model
+    saveRDS(SMDH_missing_data, file = here::here("model/SMDH_missing_data.rds"))
+
+    # Saving the dataset for this model
+    write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_missing_data.csv"))
+    ```
 

### 2025-08-16 code/08_figures-tables.Rmd
Temp commit back to desktop
Added another sensitivity analysis without non-aromatic and aromatic comparison

@@
     axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
-  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))
 
@@
     axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
-  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))
 
@@
 
-# -------- Supplementary Material Table ----------
+# ----- Supplementary Material Table -------
 
@@
 ```
-
-\
 
@@
 
+## Table: RoB Meta-regressions
+
+```{r}
+
+# Loading models for blinding performed or not
+lnRR_blinding<-readRDS(here::here("model/lnRR_blinding.rds"))
+SMDH_blinding<-readRDS(here::here("model/SMDH_blinding.rds"))
+
+# Loading models for random sampling assignment performed or not
+lnRR_random_assignment<-readRDS(here::here("model/lnRR_random_assignment.rds"))
+SMDH_random_assignment<-readRDS(here::here("model/SMDH_random_assignment.rds"))
+
+# Loading models for missing data present or not
+lnRR_missing_data<-readRDS(here::here("model/lnRR_missing_data.rds"))
+SMDH_missing_data<-readRDS(here::here("model/SMDH_missing_data.rds"))
+
+```
+
+```{r}
+pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
+
+# Let's source our custom function to extract values from the meta-regressions
+source(here::here("functions/extractor_metareg.R"))
+
+## For lnRR Values
+lnRR_results_RoB <- extractor_metareg(lnRR_blinding,"blinding")%>%
+  bind_rows(extractor_metareg(lnRR_random_assignment,"random_assignment"))%>%
+  bind_rows(extractor_metareg(lnRR_missing_data,"missing_data"))%>%
+  mutate(effect_size = "lnRR")
+
+## For SMDH Values
+SMDH_results_RoB <- extractor_metareg(SMDH_blinding,"blinding")%>%
+  bind_rows(extractor_metareg(SMDH_random_assignment,"random_assignment"))%>%
+  bind_rows(extractor_metareg(SMDH_missing_data,"missing_data"))%>%
+  mutate(effect_size = "SMDH")
+
+## Now let's write the table for publication:
+# Combine both results
+combined_results_RoB <- bind_rows(lnRR_results_RoB, SMDH_results_RoB)%>%
+  pivot_wider(
+    id_cols = c(moderator, level),
+    names_from = effect_size,
+    values_from = c(estimate, p_value, CI, PI, k, n),
+    names_glue = "{.value}_{effect_size}"
+  )%>% # Prepare row labels to mimic grouping
+  arrange(moderator, level)%>%
+  mutate(row_type = "level")
+
+# Final combined table with headers and levels
+ combined_results_RoB <- combined_results_RoB %>%
+   # bind_rows(moderator_header ,combined_results) %>%
+  arrange(moderator, row_type)%>% select(-row_type)%>%
+  relocate(level, .after = moderator)%>%
+  mutate(moderator = case_when(
+    moderator == "blinding" ~ "1. Blinding",
+    moderator == "random_assignment" ~ "2. Random assignment to treatment",
+    moderator == "missing_data" ~ "3. Partial Reporting"
+  ))%>%mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Blinding",
+      "2. Random assignment to treatment",
+      "3. Partial Reporting"
+    )
+  ))%>%
+  arrange(moderator)%>%
+  mutate(level = case_when(level=="y" ~ "Yes",
+                           level=="n" ~ "No", .default=level))
+
+# Clean up or reorder columns for display
+# Select and order columns for clarity
+RoB_table <- combined_results_RoB %>%
+  gt(groupname_col = "moderator") %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Risk of Bias**")) %>%
+  cols_label(
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
+    level = "Level",
+    estimate_lnRR = "Estimate",
+    CI_lnRR = "95% CI",
+    PI_lnRR = "95% PI",
+    p_value_lnRR = "P-val",
+    k_lnRR = "k",
+    n_lnRR = "n",
+    estimate_SMDH = "Estimate",
+    CI_SMDH = "95% CI",
+    PI_SMDH = "95% PI",
+    p_value_SMDH = "P-val",
+    k_SMDH = "k",
+    n_SMDH = "n"
+  ) %>%
+   sub_missing(
+    columns = everything(),
+    missing_text = ""
+  ) %>%
+  opt_table_outline() %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 12,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "medium",
+    row_group.font.weight = "bold"
+  )   %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)
+    ),
+    locations = cells_body()
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_lnRR),
+      rows = p_value_lnRR < 0.05
+    )
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_SMDH),
+      rows = p_value_SMDH < 0.05
+    )
+  )%>%
+  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
+  )
+
+# saving the image
+gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))
+
+# #saving as a docx file or html
+# gtsave(RoB_table,here::here("tables/SA_RoB_table.docx"))
+# gtsave(RoB_table,here::here("tables/SA_RoB_table.html"))
+```
+
+## Table: Sensitivity Analysis: Without Non-aromatic Vs. Aromatic
+
+```{r}
+# Loading intercept-only model without Non-aromatic Vs. Aromatic
+SA_lnRR_no_comp1<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))
+SA_SMDH_no_comp1<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))
+
+# Loading models for hypothesis without Non-aromatic Vs. Aromatic
+lnRR_hypothesis_no_comp1<-readRDS(here::here("model/lnRR_hypothesis_no_comp1.rds"))
+SMDH_hypothesis_no_comp1<-readRDS(here::here("model/lnRR_hypothesis_no_comp1.rds"))
+
+# Loading models for design without Non-aromatic Vs. Aromatic
+lnRR_design_no_comp1<-readRDS(here::here("model/lnRR_design_no_comp1.rds"))
+SMDH_design_no_comp1<-readRDS(here::here("model/lnRR_design_no_comp1.rds"))
+
+```
+
+**For intercept-only model**
+
+```{r}
+SA_intercept_no_comp1 <- tibble::tibble(
+  effect_size = c("lnRR",
+                  "SMD(H)"),
+  data_used = c("Without Non-Aromatic Vs. Aromatic material","Without Non-Aromatic Vs. Aromatic material"),
+
+  Estimate = c(SA_lnRR_no_comp1$b[1],SA_SMDH_no_comp1$b[1]),
+  CI_Lower = c(SA_lnRR_no_comp1$ci.lb,
+               SA_SMDH_no_comp1$ci.lb),
+  CI_Upper = c(SA_lnRR_no_comp1$ci.ub,
+               SA_SMDH_no_comp1$ci.ub),
+  PI_Lower = c(predict(SA_lnRR_no_comp1)$pi.lb,
+               predict(SA_SMDH_no_comp1)$pi.lb),
+  PI_Upper = c(predict(SA_lnRR_no_comp1)$pi.ub,
+               predict(SA_SMDH_no_comp1)$pi.ub),
+  P_value =  c(SA_lnRR_no_comp1$pval,
+               SA_SMDH_no_comp1$pval),
+  Q_value = c(SA_lnRR_no_comp1$QE,
+               SA_SMDH_no_comp1$QE),
+  k_effect_sizes = c(SA_lnRR_no_comp1$k,
+               SA_SMDH_no_comp1$k),
+  n_studies = c(length(SA_lnRR_no_comp1$s.levels.f[[1]]),
+               length(SA_SMDH_no_comp1$s.levels.f[[1]])))
+
+# Combine CI and PI into a single column each for compactness
+SA_intercept_no_comp1 <- SA_intercept_no_comp1 %>%
+  mutate(
+    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
+    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
+    P_value = scales::pvalue(P_value),
+    Q_value = sprintf("%.2f", Q_value)
+  ) %>%
+  select(
+    effect_size,
+    data_used,
+    Estimate,
+    CI,
+    PI,
+    P_value,
+    k_effect_sizes,
+    n_studies
+  )
+
+# Let's make this table pretty
+SA_intercept_no_comp1<-SA_intercept_no_comp1%>%
+  gt()%>%
+  tab_options(
+    table.font.size = px(12),
+    table.border.top.color = "black",
+    table.border.bottom.color = "black",
+    heading.title.font.size = px(14),
+    heading.subtitle.font.size = px(12),
+    column_labels.font.weight = "bold"
+  ) %>%
+  tab_header(
+    title = md("**Summary of Sensitivity Analyses without Non-aromatic Vs. Aromatic experimental design for lnRR and SMD(H) Intercept-only models**")
+  ) %>%
+  cols_label(
+    effect_size = "Effect Size",
+    data_used = "Data used in model",
+    Estimate = "Estimate",
+    CI = "95% CI",
+    PI = "95% PI",
+    P_value = "P-value",
+    k_effect_sizes = "k (No. of Effect Sizes)",
+    n_studies = "n (No. of Studies)"
+  ) %>%
+  fmt_number(
+    columns = c(Estimate),
+    decimals = 3
+  ) %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)
+    ),
+    locations = cells_body()
+  ) %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 14,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "bold",
+    row_group.font.weight = "bold"
+  ) %>%
+  opt_table_outline()
+
+# Saving as an image
+gtsave(SA_intercept_no_comp1, here::here("tables/SA_intercept_no_comp1.png"))
+```
+
+**For meta-regressions**
+
+```{r}
+pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
+
+# Let's source our custom function to extract values from the meta-regressions
+source(here::here("functions/extractor_metareg.R"))
+
+## For lnRR Values
+lnRR_no_comp1 <- extractor_metareg(lnRR_hypothesis_no_comp1,"Hypothesis")%>%
+  bind_rows(extractor_metareg(lnRR_design_no_comp1,"comparision_type"))%>%
+  mutate(effect_size = "lnRR")
+
+## For SMDH Values
+SMDH_no_comp1 <- extractor_metareg(SMDH_hypothesis_no_comp1,"Hypothesis")%>%
+  bind_rows(extractor_metareg(SMDH_design_no_comp1,"comparision_type"))%>%
+  mutate(effect_size = "SMDH")
+
+combined_results_no_comp1 <- bind_rows(lnRR_no_comp1, SMDH_no_comp1)%>%
+  pivot_wider(
+    id_cols = c(moderator, level),
+    names_from = effect_size,
+    values_from = c(estimate, p_value, CI, PI, k, n),
+    names_glue = "{.value}_{effect_size}"
+  )%>% # Prepare row labels to mimic grouping
+  arrange(moderator, level)%>%
+  mutate(row_type = "level")
+
+# Final combined table with headers and levels
+ combined_results_no_comp1 <- combined_results_no_comp1 %>%
+   # bind_rows(moderator_header ,combined_results) %>%
+  arrange(moderator, row_type)%>% select(-row_type)%>%
+  relocate(level, .after = moderator)%>%
+  mutate(moderator = case_when(
+    moderator == "Hypothesis" ~ "1. Hypothesis",
+    moderator == "comparision_type" ~ "2. Experimental Design"
+  ))%>%mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Hypothesis",
+      "2. Experimental Design"
+    )
+  ))%>%
+  arrange(moderator)%>%
+   mutate(level = case_when(level==2 ~ "No added material\nvs. Aromatic",
+                           level==3 ~ "No added material\nvs. Non-aromatic", .default=level))
+
+# Clean up or reorder columns for display
+# Select and order columns for clarity
+combined_results_no_comp1 <- combined_results_no_comp1 %>%
+  gt(groupname_col = "moderator") %>%
+  tab_header(title = md("**Sensitivity Analysis: Multilevel Meta Regressions without Non-aromatic Vs. Aromatic experimental design**")) %>%
+  cols_label(
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
+    level = "Level",
+    estimate_lnRR = "Estimate",
+    CI_lnRR = "95% CI",
+    PI_lnRR = "95% PI",
+    p_value_lnRR = "P-val",
+    k_lnRR = "k",
+    n_lnRR = "n",
+    estimate_SMDH = "Estimate",
+    CI_SMDH = "95% CI",
+    PI_SMDH = "95% PI",
+    p_value_SMDH = "P-val",
+    k_SMDH = "k",
+    n_SMDH = "n"
+  ) %>%
+   sub_missing(
+    columns = everything(),
+    missing_text = ""
+  ) %>%
+  opt_table_outline() %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 12,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "medium",
+    row_group.font.weight = "bold"
+  )   %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)
+    ),
+    locations = cells_body()
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_lnRR),
+      rows = p_value_lnRR < 0.05
+    )
+  ) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_SMDH),
+      rows = p_value_SMDH < 0.05
+    )
+  )%>%
+  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
+  )
+
+# saving the image
+gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))
+
+```
+
 # -------- TABLES ----------
@@
 ```{r}
-
 pacman::p_load(gt, tidyverse, metafor, purrr, stringr)

### 2025-08-16 manuscript_GNM.qmd
Added another sensitivity analysis without non-aromatic and aromatic comparison

@@
 Nests provide structural support for eggs, parents, and offspring, and protect them against predators and environmental pressures, and are thus key to reproductive success and survival [@hansell2000; @mainwaring2014; @deeming2023].
-While most birds use organic plant materials such as twigs, branches, grass, and moss, some incorporate inorganic items, including mud, stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@sergio2011; @suárez-rodríguez2013; @jagiello2023; @sheard2024].
-These are considered non-structural additions and suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
-Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in several bird species [@moreno1994; @hoi1996], even interspecifically [@soler1995].
+While most birds use organic plant materials such as twigs, branches, grass, and moss to build their nests, some incorporate inorganic items, including mud, stones, feathers, snake skins and even anthropogenic materials like plastic and cigarette butts [@sergio2011; @suárez-rodríguez2013; @jagiello2023; @sheard2024].
+The latter are considered non-structural additions and suggest that nests are more than just physical shelters; they can be complex tools shaped by both natural and sexual selection for multiple functions.
+Indeed, nests can play a key role in sexual display, and features such as size have been shown to act as sexually selected signals of parental quality in several bird species [e.g., @moreno1994; @hoi1996], even interspecifically by brood parasites [@soler1995].
 Nest-building behaviour is increasingly recognized as an expression of the extended phenotype (reviewed by @moreno2012), and phylogeny has been shown to be an important factor explaining both mean and within-species variation in nest morphology [@perez2023].
@@
 
-Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015) First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004)), particularly in cavity-nesting species where visual cues inside the nest are limited.
+Several hypotheses have been proposed to explain the adaptive function of GNM (reviewed in @dubiec2013; @scott-baumann2015).
+First, the courtship hypothesis suggests that (mostly) males use GNM as visual or olfactory signals to attract females and/or advertise nest site occupancy to other males (e.g., @eens1993; @gwinner1997; @brouwer2004), particularly in cavity-nesting species where visual cues inside the nest are limited.
 The courtship hypothesis traces back to the early natural history observations by @kessel1957, who noted that male European Starlings (Sturnus vulgaris) carried fresh plant material to their nests while singing and displaying to females.
-Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993] The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
+Subsequent studies in both European and Spotless Starlings (Sturnus unicolor) supported this view that GNM may serve as a sexually selected signal of male quality by showing that females often prefer nests with fresh GNM, and that unpaired males conspicuously deliver GNM during courtship, stopping right after the onset of egg laying [@brouwer2004; @veiga2006], and increasing this behaviour in the presence of potential mates [@eens1993].
+The courtship hypothesis was later extended to explain GNM addition solely by females in Blue Tits, therefore suggesting that GNM might serve as a sexually selected signal of female quality [@tomás2013].
 
@@
 This hypothesis traces back to a comparative study in raptors (Falconiformes) that provided indirect evidence for it by comparing nest reuse, diet composition and GNM presence [@wimberger1984].
-Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings, therefore confirming two of the three key criteria for evaluating the nest protection hypothesis (i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; Clark and Mason 1988).
+Soon after, a preference for GNM containing insect-repellent and antimicrobial volatiles was experimentally confirmed in European Starlings and suggested three key criteria for evaluating the nest protection hypothesis [i.e., selective plant use, bioactive chemical properties and demonstrable adaptive benefits; @clark1985].
 Observational and experimental studies on raptors [@ontiveros2007; @dykstra2009] and passerines [@lafuma2001; @dawson2004; @mennerat2009b; @quiroga2012] have shown mixed results.
@@
 no added GNM in our moderator "experimental design".
-Importantly, our conclusions were robust to these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator "experimental design" was used for subsequent meta-regressions.
-In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons.
+Importantly, our conclusions were robust to the exclusion of these effect sizes (\@Table SX), so we kept them in our dataset, and the moderator "experimental design" was used for subsequent meta-regressions.
+In studies where three groups were compared (n = `{r} nrow(multiple_comparision)`), we extracted all possible pairwise comparisons, and accounted for (shared-group) non-independence in our analyses (more below).
 
@@
 
-Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the escalc function (measure = ROM and SMDH respectively, vtype = "LS") in the R package 'metafor' v4.8-0 [@metafor].
+Using the means, standard deviations and sample sizes for each control-treatment pairwise comparison, we calculated two effect sizes: a log response ratio (lnRR) and a standardised mean difference with heteroskedasticity correction (SMDH), using the 'escalc' function (measure = ROM and SMDH, respectively, vtype = "LS") in the R package 'metafor' v4.8-0 [@metafor].
 We specified the treatment group as the numerator and the control group as the denominator for lnRR, and treatment minus control for SMDH, such that positive values indicate a 'fitness' increase in the treatment group.
-In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted prior to analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
+In cases such as measures of parasite load or prevalence, laying or hatching dates, courtship time, or scab score, the effect size sign was inverted before analysis to ensure that a positive value consistently meant an increase in fitness regardless of fitness proxy (i.e., to ensure comparability across effect sizes).
 SMDH could only be calculated when there were enough data points in both treatment and control groups to estimate the pooled variance; specifically, when the degrees of freedom (i.e., n1+n2−2) was greater than 1.
@@
 For dichotomous variables (e.g., number of successful nests, k = `{r} nrow(contingency_table)`, n = `{r} length(unique(contingency_table$paper_ID))`), we calculated the log odds ratio (lnOR) using the 'escalc' function (measure=OR) from 'metafor' and subsequently converted it to SMD using equations from @thehand2019.
-Since lnRR cannot be calculated from inferential statistics, or dichotomous variables, or for comparisons including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
+Since lnRR cannot be calculated from inferential statistics, dichotomous variables, or traits including zero or negative values (k = `{r} nrow(negative_lnRR)`), the number of effect sizes included in the lnRR (k = `{r} nrow(dataset_lnRR)`, n = `{r} length(unique(dataset_lnRR$paper_ID))`) subset is smaller than that of SMDH (k = `{r} nrow(dataset_SMDH)`, n = `{r} length(unique(dataset_SMDH$paper_ID))`).
 
@@
 
-We performed all analyses in R version 4.5.1 [@R-version].
+We performed all analyses in R v4.5.1 [@R-version].
 All multilevel meta-analytical models and meta-regressions were fitted using 'metafor' v.4.8-0 [@metafor].
@@
 
-We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years or birds studied at the same location separated by distance), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
+We originally considered the following levels of non-independence for our analyses: multiple effect sizes collected from  (a) same study (Paper ID), (b) bird species (Species ID) and (c) geographical locations (population ID), (d) sub-populations within the same location (Experiment ID; e.g., birds studied at the same location for multiple years), (e) groups of individuals within a population (Group ID; e.g., males and females in a population, first clutch and second clutch) were represented in our data several times, and (f) repeated measurement of the same trait within the same individuals (Repeated trait ID; e.g., chick mass on day 7, 14 and 21).
 
@@
 We used the `rma.mv` function from the 'metafor' package using the 'REML' method and a *t* distribution for calculating the test statistics and confidence intervals for the moderators.
-We also conducted a sensitivity analysis including some traits for which the relationship with fitness is unclear or debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
+We also conducted a sensitivity analysis including some traits for which the relationship with fitness is debated in the literature (e.g., sex ratio, testosterone levels), to test the robustness of our results (@figsupp-MLMA-excluded; k = `{r} nrow(SAonly_proxies)` , n = `{r} length(unique(SAonly_proxies$paper_ID))`).
 For all intercept-only models, we estimated the total amount of absolute heterogeneity ($σ^2$; the total variation not explained by sampling error), its sources or relative heterogeneity ($I^2$), mean-standardised metric (CVH2) and variance-mean-standardised metric of heterogeneity (M2) following the pluralistic approach suggested by @yang2024a .
@@
 To test the relative importance of the two main adaptive hypotheses suggested for GNM, that is, the courtship and the parental care hypothesis, which combines the nest protection and drug hypotheses, we ran a multilevel meta-regression including the moderator 'hypothesis' (levels: courtship, parental care, both).
-For this and all meta-regressions, we estimated $R_{marginal}^2$,which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
+For this and all meta-regressions, we estimated $R_{marginal}^2$, which corresponds to the percentage of heterogeneity explained by the moderators [@nakagawa2012].
 Unless stated otherwise, all meta-regressions correspond to unimoderator meta-regressions.
@@
 
-In addition, we performed X additional multilevel meta-regressions intended to explore the potential threats to the internal validity of each study on our conclusions (i.e., Risk of Bias or RoB) following recommendations in Culina et al.
-(2025).
-...
+In addition, we performed three additional pre-registered multilevel meta-regressions intended to explore the potential threats to the internal validity of each study on our conclusions (i.e., Risk of Bias or RoB) following recommendations in @culina2025 .
+We evaluated the effects of (1) blinding (whether outcome assessors were blinded to the experimental group), (2) random assignment to treatment, and (3) partial reporting (whether all measured outcomes were completely reported or only a subset).
+For each RoB category, we coded studies (levels: yes, no) and included each category as a moderator in a meta-regression separately for both lnRR and SMD(H).
 
@@
 
-Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness outcomes in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
+Both lnRR and SMD(H) intercept-only multilevel meta-analyses showed an average increase in fitness estimates in nests with an experimental increase in GNM compared to control nests; however, the overall effect was only statistically significant for SMD(H).
 
@@
 Third, although none of the species-specific mean estimates were statistically significant, most were positive [[\@figsupp-MR](C-D); @tabmain-MLMR], and bird species identity explained a non-negligible amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).
-Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant and reproduction marginally so, both only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; SMDH~reproduction~ = `{r} summary_SMDH_trait$estimate[6]`, 95% CI: `{r} summary_SMDH_trait$CI[6]`, 95% PI: `{r} summary_SMDH_trait$PI[6]`, p-value = `{r} summary_SMDH_trait$p_value[6]`, k = `{r} summary_SMDH_trait$k[6]`, n = `{r} summary_SMDH_trait$n[6]`; @figsupp-MR; @tabmain-MLMR) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
-Last, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically signficantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+Fourth, most fitness trait-specific mean estimates were positive, but only morphology was statistically significant only for SMD(H) (SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, 95% CI: `{r} summary_SMDH_trait$CI[2]`, 95% PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`; @figsupp-MR; @tabmain-MLMR) and trait type accounted for small amount of the heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).
+Fifth, for the subset of outcomes relating to pathogen and parasitic load, estimates for arthropods and micro-organisms did not differed statistically significantly (\@figsupp-MR; @tabmain-MLMR) and the type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMD(H))}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).
+
+Lastly, the risk of bias categories we evaluated (i.e., blinding, random assignment to each treatment and partial reporting) were not statistically significant for lnRR ([@tabsupp-SA-RoB]).
+SMD(H) was positive and statistically significant for studies without blinding (SMD(H)~No Blinding~ = `{r} summary_SMDH_blinding$estimate[1]`, 95% CI: `{r} summary_SMDH_blinding$CI[1]`, 95% PI: `{r} summary_SMDH_blinding$PI[1]`, p-value = `{r} summary_SMDH_blinding$p_value[1]`, k = `{r} summary_SMDH_blinding$k[1]`, n = `{r} summary_SMDH_blinding$n[1]`; @tabsupp-SA-RoB), with random assignment to treatment (SMD(H)~Random Assignment~ = `{r} summary_SMDH_random_assignment$estimate[2]`, 95% CI: `{r} summary_SMDH_random_assignment$CI[2]`, 95% PI: `{r} summary_SMDH_random_assignment$PI[2]`, p-value = `{r} summary_SMDH_random_assignment$p_value[2]`, k = `{r} summary_SMDH_random_assignment$k[2]`, n = `{r} summary_SMDH_random_assignment$n[2]`; @tabsupp-SA-RoB) and where no data was missing (SMD(H)~No Partial Reporting~ = `{r} summary_SMDH_missing_data$estimate[1]`, 95% CI: `{r} summary_SMDH_missing_data$CI[1]`, 95% PI: `{r} summary_SMDH_missing_data$PI[1]`, p-value = `{r} summary_SMDH_missing_data$p_value[1]`, k = `{r} summary_SMDH_missing_data$k[1]`, n = `{r} summary_SMDH_missing_data$n[1]`; @tabsupp-SA-RoB).
+Notably, other levels of each category included fewer than four studies, indicating that the observed significance likely reflects the higher statistical power in the larger sample level rather than any systematic bias.
+All the three categories for risk of bias explained very little heterogeneity ($R^2_{marginal(lnRR)}$\> `{r} as.double(round(orchaRd::r2_ml(lnRR_blinding)*100,1))[1]`%; $R^2_{marginal(SMD(H))}$\> `{r} as.double(round(orchaRd::r2_ml(SMDH_random_assignment)*100,1))[1]`%).
 

### 2025-08-16 code/05_data_cleaning.Rmd
Results comments addressed (initial stage).. continue results and discussion
Added data, code, model and figures

--- 2025-07-05 docs/code/05_data_cleaning.Rmd
@@
 
-Whichever between Cyanistes caeruleus and Parus major is higher.. assign that..
-
 ## Some quick checks to make sure all names are clean
@@
 unique(dataset_after_cleaning$proxy_decision)
+
+## Ensuring all names for risk of bias meta-regression are clean
+
+unique(dataset_after_cleaning$blinding)
+
+dataset_after_cleaning <- dataset_after_cleaning %>%
+  mutate(blinding = case_when(
+    blinding == "no" ~ "n",
+    TRUE ~ blinding
+  ))
+
+## And now
+unique(dataset_after_cleaning$blinding)
+## all good, works!
+
+## And now for missing data
+unique(dataset_after_cleaning$missing_data)
+
+dataset_after_cleaning <- dataset_after_cleaning %>%
+  mutate(missing_data = case_when(
+    missing_data == "no" ~ "n",
+    missing_data == "yes" ~ "y",
+    TRUE ~ missing_data
+  ))
+
+## And now
+unique(dataset_after_cleaning$missing_data)
+# Gooood!
+
+## Last one is 
+unique(dataset_after_cleaning$random_assignment)
+
+dataset_after_cleaning <- dataset_after_cleaning %>%
+  mutate(random_assignment = case_when(
+    random_assignment == "no" ~ "n",
+    random_assignment == "yes" ~ "y",
+    TRUE ~ random_assignment
+  ))
+
+# And now?
+unique(dataset_after_cleaning$random_assignment)
+
+## Good good, all looks well now!
 ```

### 2025-08-16 code/06_data_preparation.Rmd
Added data, code, model and figures

@@
 # Setting up workspace
-
+if (!requireNamespace("pacman", quietly = TRUE)) {
+  install.packages("pacman")
+}
 pacman::p_load(here, tidyverse, dplyr, stringr, metafor, orchaRd,ggpubr,ggrepel) #Packages needed
@@
       # Madrid Region
-      str_detect(population_ID, regex("madrid|manzanares|villalba|soto del real|central spain", ignore_case = TRUE)) ~ "Madrid Province, Spain",
+      str_detect(population_ID, regex("madrid|manzanares|villalba|soto del real", ignore_case = TRUE)) ~ "Madrid Province, Spain",
 
@@
 since the sample is the same and these are the repeated measures of the same sample.
-noSMDH=dataset_analysis%>%filter(is.na(SMDH))
+low_sample=dataset_analysis%>%filter(is.na(SMDH))
+write.csv(low_sample,file=here::here("data/03_data_cleaning/low_sample.csv"),row.names = FALSE)
+```
+
+This is very very low sample size, it makes no sense to keep them. I will exclude them from all the further analysis.
+
+```{r}
+dataset_analysis<-dataset_analysis%>%anti_join(low_sample,by="Observation_ID")
 ```

### 2025-08-16 code/00_search_stratergy_litsearchr_code.R

@@ -3,9 +3,7 @@
 # Since it is only available through Github and not CRAN
 # Skip this part if you have already installed litsearchr 
 
-
-install.packages("remotes")
-library(remotes)
+pacman::p_load(remotes, tidyverse)
 #to install litsearchr from Github
 install_github("elizagrames/litsearchr", ref="main")
 
@@ -64,20 +62,22 @@ rakedkeywords<-
 #--------------------counting the occurance of searched keywords across studies in our database----------------------------
 
 #create_dfm counts the occurrence of the searched keywords across the studies and produces a matrix
-naive_dfm<-litsearchr::create_dfm(elements = paste(dedup$keywords,dedup$title,dedup$abstracts),
+naive_dfm<-litsearchr::create_dfm(elements = paste(deduplicated_naiveimport$keywords,
+                                                   deduplicated_naiveimport$title,
+                                                   deduplicated_naiveimport$abstracts),
                                  features = rakedkeywords)
 
 
 
 #creating the network graph showing co-occurrence between the words (note that one can change
 #the numbers of studies and minimal occurence)
-naivegraph<-litsearchr:: create_network(search_dfm = naive_dfm, min_studies = 3, 
-                                        min_occ = 2)
+  naivegraph<-litsearchr:: create_network(search_dfm = naive_dfm, min_studies = 3, 
+                                         min_occ = 2)
 
 #------------------------------------plots to visualise the searched keywords----------------------------------------------
 
-#it shows the grap with the co-occurence of words
-plot(naivegraph)
+#it shows the graph with the co-occurence of words
+# plot(naivegraph)
 
 #The ‘strength’ of each term in the network is the number of other terms that it appears together with
 strengths <- strength(naivegraph)
@@ -87,7 +87,7 @@ data.frame(term=names(strengths), strength=strengths, row.names=NULL) %>%
   arrange(strength) ->
   term_strengths
 
-#term_strengths
+# term_strengths
 
 # plot to show the strength of each term to set a cutoff and include the important terms that occur multiple times
 cutoff_fig <- ggplot(term_strengths, aes(x=rank, y=strength, label=term)) +
@@ -101,17 +101,17 @@ cutoff_fig
 #... keywords (the highter the percentage the more keywords)
[…]

### 2025-08-16 code/01_systematic_search_deduplication.R

@@ -12,14 +12,18 @@
 # INPUT files: 
 # GNM_wos.bib
 # GNM_scopus.bib
+# full_reference_before_deduplication.csv should be read to see the exact data we 
+# used before de-duplication.Error in loading with revtools::read_bibliography
+# function when re-checked the code now added lines of code to read bib files with synthesisr
 
 # OUTPUT files:
 # full_reference_before_deduplication.csv
 # unique_reference_list.csv
-# Packages used: dplyr , revtools
+
+# Packages used: dplyr , revtools , synthesisr
 
 
-# created on 12.09.22 for green nest material project 
+# created on 12.09.22 for green nest material project and updated on 02.06.2025
 # Code written by: SD and revised by: NA
 
 ##############################################################
@@ -39,16 +43,32 @@ rm(list=ls())
 
 # importing the .bib files from WEB OF SCIENCE and SCOPUS
 
-reference_data_wos <- read_bibliography("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
-reference_data_scopus <- read_bibliography("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
+## Initially this code used revtools::read_bibliography to read the .bib files from
+## WOS and Scopus. On re-running the code during check, this gives loading error. 
+## A good fix is to use synthesisr package so I am switching to that now even though 
+## in the project I used revtools (and report the same)..
+
+pacman::p_load(synthesisr)
+
+# reference_data_wos <- read_bibliography("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
+# reference_data_scopus <- read_bibliography("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
+
+
+reference_data_wos <- synthesisr::read_ref("data/01_systematic_search/02_reference_data/web_of_science/GNM_wos.bib")
+reference_data_scopus <- synthesisr::read_ref("data/01_systematic_search/02_reference_data/scopus/GNM_scopus.bib")
 
 # reducing fields to the minimum number of fields
 # so that all databases have the same columns. Also, these fields
 # are the important ones for the screening.
-reducing_fields <- c("label","title","author","journal",
-                         "volume","number","pages","year",
-                         "doi","abstract") 
+# reducing_fields <- c("label","title","author","journal",
+#                          "volume","number","pages","year",
+#                          "doi","abstract") 
 
+# I have to exclude the label field which I had selected earlier when 
+# I used revtools for this merge. In synthesisr, I do not get the label column.
[…]

### 2025-08-16 code/02_abstract_screening.R

@@ -8,19 +8,42 @@
 # 3. Creating subsets for title and abstract screening for the 
 # three screeners (SD, JS and TR) for preliminary and final phase of screening
 
+# Second part of this script was created to import the files after 
+# title and abstract screening to..
+
+# 4. import the files after title and abstract screening (after resolving any differences)
+# 5. Creating a final dataset_after_abstract_screening with only final decisions
+# 6. Creating a file with selected_abstract_screening for further steps
+
+# INPUT files required
+# 
+# differences_prelim_set1_2022_10_07
+# differences_prelim_set2_2022_10_14
+# differences_abstract_screening_set1
+# differences_abstract_screening_set2
+# differences_abstract_screening_set3
+
 # Title and abstract screening was conducted using revtools package- screen_abstracts()
 
-# Packages used: dplyr , revtools , readr
+# Packages used: dplyr , revtools , readr, tidyverse, stringr
 
-# created on 04.10.22 for green nest material project
-# Code written by: SD and revised by: 
+
+# first created on 04.10.22 for green nest material project
+# Code written by: SD and revised by: NA
+
+##############################################################
+##############################################################
+# Before title and abstract screening was performed
+##############################################################
+##############################################################
 
 ##############################################################
 # Packages needed
 ##############################################################
 
 # load pacakges
-pacman::p_load(dplyr, revtools, readr)
+pacman::p_load(dplyr, revtools, readr, 
+               tidyverse, stringr)
 
 # cleaning up
 rm(list=ls())
@@ -53,9 +76,15 @@ unique_reference_list=cbind(Paper_ID,unique_reference_list)
 
 random_ID1<-sample(1:nrow(unique_reference_list),40)
 prelim_screen_set1=unique_reference_list[random_ID1[1:20],]
-screen_abstracts(prelim_screen_set1)
+# screen_abstracts(prelim_screen_set1)
 prelim_screen_set2=unique_reference_list[random_ID1[21:40],]
-screen_abstracts(prelim_screen_set2)
+# screen_abstracts(prelim_screen_set2)
+
+# Please uncomment the line with screen_abstracts() if you want to 
+# open the GUI to do the screening yourself..
+# To see the results of the abstract screening conducted for this project,
+# see below..
+
 
 ##############################################################
[…]

### 2025-08-16 code/04_data_extraction.R

@@ -1,82 +1,0 @@
-##############################################################
-# Description of script and Instructions
-##############################################################
-# This script is to:
-# 1. import the selected_abstract_screening
-# 2. Creating subsets for data-extraction for the 
-# three screeners (SD, JS and TR) for preliminary and final phase of extraction
-
-# data-extraction was performed in Microsoft Excel
-
-# Packages used: readr
-
-# created on 09.08.23 for green nest material project
-# Code written by: SD and revised by: NA
-
-
-##############################################################
-# Packages needed
-##############################################################
-
-# Load required packages
-# install.packages("pacman")
-pacman::p_load(readr)
-
-# environment clean up
-rm(list=ls())
-
-# set seed for reproducibility (essential for consistency of random number generation)
-set.seed(1)
-
-##############################################################
-# To load selected papers dataset after the abstract screening
-##############################################################
-
-selected_abstract_screening <- read_csv("data/01_systematic_search/03_title_and_abstract_screening/selected_abstract_screening.csv")
-
-##################################################################
-# Data-extraction subsets for multiple screenings 
-##################################################################
-
-##############################################################
-# Data-extraction (performed by SD, JS and TR) 
-# To randomly select 5 papers (~12.5%) for pilot data-extraction
-# Data-extraction performed on excel
-##############################################################
-
-random_ID1<-sample(1:nrow(selected_abstract_screening),5)
-prelim_extraction=selected_abstract_screening[random_ID1,]
-
-# write.csv(prelim_extraction,"data/02_data_extraction/prelim_extraction.csv",row.names=FALSE)
-
-##############################################################
-# Rest of the data-extraction performed by SD, JS and TR 
-# Each data-extraction is performed twice by two data-extractors 
-##############################################################
-
-# To create three sets with all the records for which the data 
-# extraction should be performed
-
-##############################################################
-
-#screened by SD and checked by TR
-random_ID2=sample(setdiff(1:nrow(selected_abstract_screening), random_ID1), 12)
-data_extraction_setSD=selected_abstract_screening[random_ID2,]
-
-# write.csv(data_extraction_setSD,"data/02_data_extraction/data_extraction_setSD.csv",row.names=FALSE)
-##############################################################
-
-#screened by TR and checked by JS
[…]

### 2025-08-16 code/04_search_repeat_12082024.R

@@ -1,0 +1,166 @@
+##############################################################
+# Description of script and Instructions
+##############################################################
+
+# This script is to:
+# 1. import the .bib files from Web of Science (WOS) and Scopus for the repeated search on 12th August 2024
+# 2. combine the 2 .bib files (I have used one .csv for scopus since .bib was giving encoding errors while loading) 
+# to produce a full reference list (encoding errors may occur depending 
+# on the system and "UTF-16LE" was used in this case for writing and reading the full_reference_before_deduplication)
+# 3. deduplicate the full reference list and produce a unique list of 
+# papers (unique_reference_repeat_120824)
+# 4. Adding a unique identified (Paper_ID) for each article for this section
+# 5. 
+
+# INPUT files: 
+# GNM_wos.bib
+# GNM_scopus.bib
+
+# OUTPUT files:
+# full_reference_before_deduplication.csv
+# unique_reference_list.csv
+# Packages used: dplyr , revtools
+
+
+# created on 12.08.24 for green nest material project 
+# Code written by: SD and revised by: NA
+
+##############################################################
+# Packages needed
+##############################################################
+
+# load pacakges
+# If pacman is not installed already use
+# install.packages("pacman")
+pacman::p_load(dplyr, revtools, readr)
+
+# cleaning up
+rm(list=ls())
+
+
+# set seed for reproducibility (for consistent random number generation)
+set.seed(7)
+
+################################
+
+# importing the .bib files from WEB OF SCIENCE and SCOPUS
+
+reference_data_wos <- read_bibliography("data/01_systematic_search/04_search_repeat_12082024/GNM_repeat_wos.bib")
+reference_data_scopus <- read_bibliography("data/01_systematic_search/04_search_repeat_12082024/GNM_repeat_scopus.csv")
+
+# reducing fields to the minimum number of fields
+# so that all databases have the same columns. Also, these fields
+# are the important ones for the screening.
+reducing_fields <- c("label","title","author","journal",
+                     "volume","number","pages","year",
+                     "doi","abstract") 
+
+## Since I decided to use .csv for scopus, the column names are different and 
+# I will have to edit it.
+
+reference_data_scopus <- reference_data_scopus%>%rename(journal=source_title,
+                                                        number=issue,
+                                                        doi=DOI)%>%
+  mutate(pages=paste(reference_data_scopus$page_start,reference_data_scopus$page_end,sep = "-"))
+  
+
+
[…]

### 2025-08-16 data/02_data_extraction/extracted_raw_data/analysis_GNM_010.R

@@ -1,0 +1,57 @@
+pacman::p_load(here,tidyverse, readr)
+data_GNM_010 <- read_csv("data/02_data_extraction/extracted_raw_data/data_GNM_010_clutch_overview.csv")
+
+head(data_GNM_010)
+summary(data_GNM_010)
+names(data_GNM_010)
+
+# Variables to extract: eggslaid;	chickshatchday;	maxchicks;	hatchsuccess;	massday7;	meandevoscore
+
+#Extracting data (SD;MEAN;sample size) eggslaid
+
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(eggslaid)),
+            sd=(sd(na.omit(eggslaid))),
+            samplesize=(n()))
+
+#Extracting data (SD;MEAN;sample size) chickshatchday
+
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(chickshatchday)),
+            sd=(sd(na.omit(chickshatchday))),
+            samplesize=(n()))
+
+#Extracting data (SD;MEAN;sample size) maxchicks 
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(maxchicks)),
+            sd=(sd(na.omit(maxchicks))),
+            samplesize=(n()))
+
+
+
+#Extracting data (SD;MEAN;sample size) hatchsuccess  
+
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(hatchsuccess)),
+            sd=(sd(na.omit(hatchsuccess))),
+            samplesize=(n()))
+
+#Extracting data (SD;MEAN;sample size) massday7 
+
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(massday7)),
+            sd=(sd(na.omit(massday7))),
+            samplesize=(n()))
+
+#Extracting data (SD;MEAN;sample size) meandevoscore 
+data_GNM_010 %>%
+  group_by(nesttype, year) %>%
+  summarise(mean=mean(na.omit(meandevoscore)),
+            sd=(sd(na.omit(meandevoscore))),
+            samplesize=(n()))
+

### 2025-08-16 data/02_data_extraction/extracted_raw_data/analysis_GNM_018.R

@@ -1,0 +1,48 @@
+## Setting up workspace
+
+pacman::p_load(dplyr, readxl) #Packages needed
+rm(list=ls()) ## cleaning up
+set.seed(251) #set seed for reproducibility (for random number generation)
+
+data_GNM_018 <- read_excel("data/02_data_extraction/extracted_raw_data/GNM_018_data-by-authors.xlsx")
+head(data_GNM_018)
+summary(data_GNM_018)
+names(data_GNM_018)
+
+
+laying_date<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(LDATE),
+            sd=sd(LDATE),
+            samplesize=(n()))
+
+clutch_size<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(CS),
+            sd=sd(CS),
+            samplesize=(n()))
+
+hatching_date<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(HDATE),
+            sd=sd(HDATE),
+            samplesize=(n()))
+
+brood_size_day6<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(BS6),
+            sd=sd(BS6),
+            samplesize=(n()))
+
+hatching_success<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(HS),
+            sd=sd(HS),
+            samplesize=(n()))
+
+reproductive_success<-data_GNM_018 %>%
+  group_by(expPlants) %>%
+  summarise(mean=mean(na.omit(RS)),
+            sd=sd(na.omit(RS)),
+            samplesize=(na.omit(n())))
+

### 2025-08-16 data/02_data_extraction/extracted_raw_data/analysis_GNM_237.R

@@ -1,0 +1,222 @@
+
+# The dataset provided by the authors was split in 3 files 
+#(to be handled by R)# namely:  
+#natural_nests; 
+#artificial_nests_2012;
+# and artificial_nests_2013
+
+
+library(readr)
+# Extracting data from the file "natural_nests_GNM_237";
+data<-read_csv("data/02_data_extraction/extracted_raw_data/natural_nests_GNM_237.csv")
+
+head(data)
+tail(data)
+summary(data)
+names(data)
+
+library(dplyr)
+
+#Extracting data (SD;MEAN;sample size) llog.mesophilic.bacterial.density..1st.
+data %>%
+  group_by(Feather.treatment, Plant.treatment,Contamination, Year) %>%
+  summarise(mean=mean(na.omit(log.mesophilic.bacterial.density..1st.)),
+            sd=(sd(na.omit(log.mesophilic.bacterial.density..1st.))),
+            samplesize=(n()))
+
+# creating csv file to help the data extraction
+natlogmes1st<-data %>%
+  group_by(Feather.treatment, Plant.treatment,Contamination, Year) %>%
+  summarise(mean=mean(na.omit(log.mesophilic.bacterial.density..1st.)),
+            sd=(sd(na.omit(log.mesophilic.bacterial.density..1st.))),
+            samplesize=(n()))
+
+write.csv(natlogmes1st, "natlogmes1st.csv")
+
+getwd()
+#Extracting data (SD;MEAN;sample size) log.mesophilic.bacterial.density..2nd.
+
+data %>%
+  group_by(Feather.treatment, Plant.treatment,Contamination, Year) %>%
+  summarise(mean=mean(na.omit(log.mesophilic.bacterial.density..2nd.)),
+            sd=(sd(na.omit(log.mesophilic.bacterial.density..2nd.))),
+            samplesize=(n()))
+
+# creating csv file to help the data extraction 
+natlogmes2nd<-data %>%
+  group_by(Feather.treatment, Plant.treatment,Contamination, Year) %>%
+  summarise(mean=mean(na.omit(log.mesophilic.bacterial.density..2nd.)),
+            sd=(sd(na.omit(log.mesophilic.bacterial.density..2nd.))),
+            samplesize=(n()))
+
+write.csv(natlogmes2nd, "natlogmes2nd.csv")
+
+
+
+
+# Extracting data from the file "artificial_nests_2012_GNM_237"
+
[…]

### 2025-08-16 functions/extractor_metareg.R

@@ -1,0 +1,126 @@
+# Let's write a function for extracting values from a meta-regression
+
+extractor_metareg <- function(model, moderator_name) {
+  
+  mod.summ <- summary(model)
+  # Extract levels of moderator (from rownames)
+  mod.levels <- rownames(mod.summ$beta)
+  mod.levels <- gsub(paste0(moderator_name),"", mod.levels)
+  
+  # Need to pass the complete data from the model to be able to calculate k and n for each level of moderator
+  mod.data <- model$data
+  
+  summ.k_n <-  mod.data %>%
+    group_by(level= as.character(.data[[moderator_name]])) %>%
+    summarise(
+      k = n(),  # effect sizes
+      n = n_distinct(paper_ID),  # unique papers
+      .groups = "drop"
+    )
+  
+  # Now we need a small function to extract the prediction interval per level of the moderator
+  # Get prediction intervals for each level
+  get_predicted<-function(model,mod.levels)
+  {
+    # Identity matrix for dummy-coded levels - categorical variables need dummy coding in metafor
+    newmods_mat <- diag(length(mod.levels))
+    predict.data<- data.frame(predict(model,newmods = newmods_mat))
+    predict.data<- predict.data%>%bind_cols(level=mod.levels)%>%select(pi.lb,pi.ub,level)
+    return(predict.data)
+  }
+  
+  prediction_interval<-get_predicted(model,mod.levels)
+  
+  ## Let's get all the heterogeneity metrics too
+  ## I am copying the r2_ml and R2_calc function code from orchaRd package
+  r2_ml <- function(model, data, boot = NULL) {
+    
+    if(all(class(model) %in% c("robust.rma", "rma.mv", "rma", "rma.uni")) == FALSE) {stop("Sorry, you need to fit a metafor model of class robust.rma, rma.mv, rma, rma.uni")}
+    
+    if(any(model$tau2 > 0)) { stop("Sorry. At the moment r2_ml cannot take models with heterogeneous variance.")}
+    
+    R2 <- R2_calc(model)
+    
+    if(!is.null(boot)){
+      
+      if(any(class(model) %in% c("robust.rma")) == TRUE){stop("Sorry, bootstrapping currently doesn't work for robust.rma objects. Please use rma.mv instead.")}
+      # Simulate the vector of effect sizes
[…]

### 2025-08-18 code/01_systematic_search_deduplication.R
*Code reviewed [MO] *ensuring all required packages are automatically installed if missing *adding tidyvderse, here and readxl *adding session.info()

@@ -1,6 +1,4 @@
-##############################################################
-# Description of script and Instructions
-##############################################################
+# Description of script and Instructions ---------------------
 
 # This script is to:
 # 1. import the .bib files from Web of Science (WOS) and Scopus
@@ -20,81 +18,95 @@
 # full_reference_before_deduplication.csv
 # unique_reference_list.csv
 
-# Packages used: dplyr , revtools , synthesisr
-
+# Packages used: 
+# dplyr (v1.1.4)
+# revtools (v0.4.1)
 
 # created on 12.09.22 for green nest material project and updated on 02.06.2025
-# Code written by: SD and revised by: NA
+# Code written by: SD and revised by: MO [2025/08/18]
 
-##############################################################
-# Packages needed
-##############################################################
+# Required packages ------------------------------------------
 
-# load pacakges
-# If pacman is not installed already use
-# install.packages("pacman")
-pacman::p_load(dplyr, revtools)
+# Required packages are load and managed through pacman
+# Install package pacman if not installed already
+if (!"pacman" %in% rownames(installed.packages())) {
+  install.packages("pacman")
+}
+pacman::p_load(dplyr, revtools, readr)
 
-# cleaning up
-rm(list=ls())
+# importing the .bib files from WEB OF SCIENCE and SCOPUS ----
 
+# Initially this code used revtools::read_bibliography to read the .bib files from
+# WOS and Scopus. On re-running the code during check, this gives loading error. 
+# A good fix is to use the synthesisr package so I am switching to that now even though 
+# in the project I used revtools (and report the same)..
 
-################################
+# Mon Aug 18 17:32:54 2025 ------------------------------
+# I tested this script by running all code with a clean (empty) R library to ensure 
+# all packages are installed based on current releases on CRAN:
+# revtools::read_bibliography seems to work just fine, only prompting a warning message. 
+# The content is equal to synthesisr::read_ref, except for minor 
+# encoding differences in certain identifiers, i.e. strings denoting researcher names etc. 
+# 
+# Therefore, changing back to revtools::read_bibliography [MO]
 
-# importing the .bib files from WEB OF SCIENCE and SCOPUS
+# Mon Aug 18 16:27:39 2025 ------------------------------
+# pacman::p_load(synthesisr)
 
[…]

### 2025-08-18 code/02_abstract_screening.R

@@ -1,5 +1,5 @@
 ##############################################################
-# Description of script and Instructions
+# Description of script and Instructions ---------------------
 ##############################################################
 
 # This script is to:
@@ -25,11 +25,16 @@
 
 # Title and abstract screening was conducted using revtools package- screen_abstracts()
 
-# Packages used: dplyr , revtools , readr, tidyverse, stringr
+# Packages used: 
+# dplyr , 
+# revtools , 
+# readr, 
+# tidyverse, 
+# stringr
 
 
 # first created on 04.10.22 for green nest material project
-# Code written by: SD and revised by: NA
+# Code written by: SD and revised by: MO [2025/08/24]
 
 ##############################################################
 ##############################################################
@@ -37,47 +42,55 @@
 ##############################################################
 ##############################################################
 
-##############################################################
-# Packages needed
-##############################################################
+# Required packages ------------------------------------------
 
-# load pacakges
-pacman::p_load(dplyr, revtools, readr, 
-               tidyverse, stringr)
+# Required packages are load and managed through pacman
+# Install package pacman if not installed already
+if (!"pacman" %in% rownames(installed.packages())) {
+  install.packages("pacman")
+}
 
-# cleaning up
-rm(list=ls())
-
-# set seed for reproducibility (for consistent random number generation)
+# load packages or install if not found
+pacman::p_load(dplyr, #v1.1.4
+               revtools, #v0.4.1
+               readr, #v2.1.5
+               tidyverse, #v2.0.0
+               stringr #v1.5.1
+               )
+# set seed for reproducibility -------------------------------
+# (ensures consistent random number generation)
 set.seed(1)
 
-############################################################
-# Importing data after de-duplication
-############################################################
-
-unique_reference_list <- read.table("data/01_systematic_search/02_reference_data/unique_reference_list.csv",
-                                    header=T,sep=",")
+# Importing data after de-duplication -------------------------
+# table containing 383 papers
+unique_reference_list <- read.table(
[…]

### 2025-08-18 code/03_fulltext_and_data_extraction.R

@@ -1,17 +1,14 @@
-##############################################################
-# Description of script and Instructions
+# Description of script and Instructions ---------------------
 ##############################################################
 # This script is to:
 # 1. import the selected_abstract_screening
 # 2. Creating subsets for data-extraction for the 
 # three screeners (SD, JS and TR) for preliminary and final phase of extraction
 
-
-
 # Packages used: readr
 
 # created on 09.08.23 for green nest material project
-# Code written by: SD and revised by: NA
+# Code written by: SD and revised by: MO [2025/08/24]
 
 ##############################################################
 ##############################################################
@@ -21,18 +18,24 @@
 ##############################################################
 ##############################################################
 
-##############################################################
-# Packages needed
-##############################################################
+# Required packages ------------------------------------------
+
+# Required packages are load and managed through pacman
+# Install package pacman if not installed already
+if (!"pacman" %in% rownames(installed.packages())) {
+  install.packages("pacman")
+}
 
 # Load required packages
-# install.packages("pacman")
-pacman::p_load(readr, readxls)
+pacman::p_load(
+  here, #v1.0.1
+  readr, #v2.1.5
+  readxl, #v1.4.5
+  tidyverse #v2.0.0
+)
 
-# environment clean up
-rm(list=ls())
-
-# set seed for reproducibility (essential for consistency of random number generation)
+# set seed for reproducibility -------------------------------
+# (ensures consistent random number generation)
 set.seed(1)
 
 ##############################################################
@@ -51,9 +54,10 @@ selected_abstract_screening <- read_csv("data/01_systematic_search/03_title_and_
 # Data-extraction performed on excel
 ##############################################################
 
-random_ID1<-sample(1:nrow(selected_abstract_screening),5)
-prelim_extraction=selected_abstract_screening[random_ID1,]
+random_ID1 <- sample(1:nrow(selected_abstract_screening),5)
+prelim_extraction <- selected_abstract_screening[random_ID1,]
 
+## export to csv file (already saved as part of this repository)
[…]

### 2025-08-25 code/05_data_cleaning.Rmd
small tweaks & rendering html

@@
 knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
-
+```
+
+## Preface
+
+In order to replicate the data cleaning steps shown in this document the following packages are required:
+
+```{r}
+## Install/load package pacman
 if (!requireNamespace("pacman", quietly = TRUE)) {
@@
 }
-
-pacman::p_load(here, dplyr, readxl, purrr, stringr, knitr, tidyverse)
-
-rm(list=ls()) ## clearing up any previously present variable
-```
-
-# Data Cleaning
-
-This is the step conducted once all the data from different sources was extracted.
+## Install/load required packages
+pacman::p_load(here, 
+               dplyr, 
+               readxl,
+               purrr,
+               stringr, 
+               knitr, 
+               tidyverse)
+```
+
+## Overview
+
+Data cleaning was conducted once all the data from different sources were extracted.
 
@@
 
--   We found **1** **paper** from from repeating the search on 12th August 2024
+-   We found **1** **paper** from repeating the search on 12th August 2024
 
@@
 
-#### What do we do here?
+## Summary: Steps shown in this document
 
@@
 
-#### **Importing files after data extraction**
-
-You can find all the data that is needed for this analysis.. in folder **data/02_data_extraction**. In short, we need the following files to run the data cleaning:
-
--   data_extraction_setJMGS_checkedSD.xlsx
-
--   data_extraction_setSD_checkedTR.xlsx
-
--   data_extraction_setTR_checkedJS_checkedSD.xlsx
-
--   data_extraction_repeat_search_JMGS.xlsx
-
--   data_extraction_repeat_search_SD.xlsx
-
--   data_extraction_repeat_search_TR.xlsx
-
--   data_extraction_MO_checkedSD.xlsx
-
--   data_extraction_UnpublishedThesis.xlsx
+## Importing files after data extraction
+
+All the data that is required for this analysis are found in [data/02_data_extraction](https://github.com/shreyadimri/Green_Nest_Material/tree/main/data/02_data_extraction).
+In short, we need the following files to run the data cleaning:
+
+* [data_extraction_setJMGS_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx)
+
+* [data_extraction_setSD_checkedTR.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx)
+
+* [data_extraction_setTR_checkedJS_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx)
+
+* [data_extraction_repeat_search_JMGS.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx)
+
+* [data_extraction_repeat_search_SD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_SD.xlsx)
+
+* [data_extraction_repeat_search_TR.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_TR.xlsx)
+
+* [data_extraction_MO_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_MO_checkedSD.xlsx)
+
+*[data_extraction_UnpublishedThesis.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx)
 
 ```{r import, warning=FALSE, message=FALSE}
-
-## We use column_types to make the loading variable datatype of all the datafiles same.
-
+## Specifying column_types to control data types of each column
 column_types = c(
@@
 
-# Data extracted from the selected papers after abstract screening
-
-set_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx"),col_types =column_types)
-set_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx"),col_types =column_types)
-set_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx"),col_types =column_types)
-
-# Data extracted from repeated search on 12.Aug.2024
-
-set2_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx"),col_types =column_types)
-set2_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_SD.xlsx"),col_types =column_types)
-set2_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_TR.xlsx"),col_types =column_types)
-
-# Unpublished dataset
-set_unpublished1 <- read_excel(here::here("data/02_data_extraction/data_extraction_MO_checkedSD.xlsx"),col_types =column_types)
-set_unpublished2 <-read_excel(here::here("data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx"),col_types =column_types)
-
-# Merge all datasets
-merged_data_extraction<-full_join(set_JMGS,set_SD)%>%full_join(set_TR)%>%full_join(set2_JMGS)%>%full_join(set2_SD)%>%full_join(set2_TR)%>%full_join(set_unpublished1)%>%full_join(set_unpublished2)
-
-write.csv(merged_data_extraction,here::here("data/03_data_cleaning/merged_data_extraction.csv"),row.names=FALSE)
-```
-
-### Full-text Screening
-
-#### **Excluded articles**
-
-These were the articles extracted during full-text screening according to the decision tree, for the following reasons given below..
+## read data extracted from the selected papers after abstract screening
+set_JMGS <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx"),
+                       col_types = column_types)
+set_SD <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx"),
+                     col_types =column_types)
+set_TR <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx"),
+                     col_types =column_types)
+
+## read data extracted from repeated search on 12.Aug.2024
+set2_JMGS <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx"),
+                        col_types =column_types)
+set2_SD <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_SD.xlsx"),
+                      col_types =column_types)
+set2_TR <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_TR.xlsx"),
+                      col_types =column_types)
+
+## read data of unpublished dataset
+set_unpublished1 <- read_excel(path = here::here("data/02_data_extraction/data_extraction_MO_checkedSD.xlsx"),
+                               col_types =column_types)
+set_unpublished2 <-read_excel(path = here::here("data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx"),
+                              col_types =column_types)
+
+## Merge all datasets
+merged_data_extraction <- 
+  full_join(set_JMGS,set_SD) %>% 
+  full_join(set_TR) %>% 
+  full_join(set2_JMGS) %>%
+  full_join(set2_SD) %>% 
+  full_join(set2_TR) %>%
+  full_join(set_unpublished1) %>%
+  full_join(set_unpublished2)
+
+## export merged datasets to csv file
+# write.csv(merged_data_extraction, here::here("data/03_data_cleaning/merged_data_extraction.csv"), row.names=FALSE)
+```
+
+## Full-text Screening
+
+### **Excluded articles**
+
+These were the articles excluded during full-text screening according to the decision tree, for the reasons given below ...
 
@@
 excluded_fulltext <- merged_data_extraction %>% filter(fulltext_screening=="excluded")
-excluded_papers_no<-length(unique(excluded_fulltext$paper_ID))
-
+excluded_papers_no <- length(unique(excluded_fulltext$paper_ID))
+
+## export excluded_fulltext to csv file
 # write.csv(excluded_fulltext,here::here("data/03_data_cleaning/excluded_fulltext.csv"),row.names=FALSE)
@@
 #| echo: false
-
 kable(as.data.frame(summary(as.factor(excluded_fulltext$fulltext_notes))),
@@
 
-#### **Included articles**
+### **Included articles**
 
@@
 included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
-
 ```
@@
 We extracted the names of the variables that the authors measured as it is, often along with the location/year when they were measured.
-We will now clean them a bit, making sure they are all named correctly.
+We will now clean them a bit, making sure they are all named consistently.
 We are cleaning some of the names of the fitness proxy and storing them in the new variable called *fitness_proxy_cleaned*
@@
 
-**1. Male and female proportion of visit:**
+#### 1. **Male and female proportion of visit:**
 
@@
 ```{r}
-
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**2. Male and female provisioning**
-
-```{r}
-
+```
+
+#### 2. **Male and female provisioning**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**3.** **Male food provisioning**
-
-```{r}
+```
+
+#### 3. **Male food provisioning**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**4.** **Male incubation attendance**
-
-```{r}
+#### 4. **Male incubation attendance**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**5.** **Male Risk Taking**
-
-```{r}
+```
+
+#### 5.**Male Risk Taking**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**6.** **Sex Ratio**
+#### 6. **Sex Ratio**
 
@@
 ```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**7.** **Female Testosterone**
-
-```{r}
-
+#### 7. **Female Testosterone**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**8.** **Yolk Hormones**
-
-```{r}
+#### 8. **Yolk Hormones**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**9.** **Courtship Time**
-
-```{r}
+#### 9. **Courtship Time**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-### Both Hypothesis :
-
-**1.** **Laying Date**
-
-```{r}
+### Both Hypotheses :
+
+#### 1. **Laying Date**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**2.** **Hatching Date**
-
-```{r}
+```
+
+#### 2. **Hatching Date**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**3.** **Clutch size**
-
-```{r}
+```
+
+#### 3. **Clutch size**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**4. Number of nestlings (different age)**
-
-```{r}
-
+#### 4. **Number of nestlings (different age)**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**5. Number of fledglings**
-
-```{r}
+```
+
+#### 5. **Number of fledglings**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**6. Nestling survival rate**
-
-```{r}
-
+#### 6. **Nestling survival rate**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**7. Recruitment probability**
-
-```{r}
-
+```
+
+#### 7. **Recruitment probability**
+
+```{r}
+## code new variable fitness_proxy_cleaned
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-8\. **Hatching success**
+```
+
+#### 8. **Hatching success**
 
@@
 
-**9.** **Fledgling success**
+#### 9. **Fledgling success**
 
@@
 
-**10.** **Reproductive success**
+#### 10. **Reproductive success**
 
@@
 
-11\. **Nest mortality**
+#### 11. **Nest mortality**
 
@@
   ))
-
-```
-
-**12. Mouth colouration**
-
-```{r}
-
+```
+
+#### 12. **Mouth colouration**
+
+```{r}
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
   ))
-
-```
-
-**13. Male and female dispersal distance**
+```
+
+#### 13. **Male and female dispersal distance**
 
@@
 
-**14. Egg Size**
+#### 14. **Egg Size**
 
@@
 
-**15. Chick mass, nestling mass and fledgling mass**
-
-```{r}
-# Checked paper GNM_069 and GNM_349 and the word body mass is used to describe nestlings of 14 days and 17 days respectlively
+#### 15. **Chick mass, nestling mass and fledgling mass**
+
+```{r}
+# Checked paper GNM_069 and GNM_349 and the word body mass is used to describe nestlings of 14 days and 17 days respectively
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**16. Nestling Size**
+#### 16. **Nestling Size**
 
@@
 
-**17. Nestling Tarsus Length**
-
-```{r}
-
-#checked paper GNM_069 word tarsus length is used to describe nestlings of 14 days
-
+#### 17. **Nestling Tarsus Length**
+
+```{r}
+##checked paper GNM_069 word tarsus length is used to describe nestlings of 14 days
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-**18. Nestling Wing Length**
+#### 18. **Nestling Wing Length**
 
@@
 
-**19. Male and female body size**
+#### 19. **Male and female body size**
 
@@
 
-**20.** **Male and female mass**
+#### 20. **Male and female mass**
 
@@
 
-**21.** **Male and female wing length**
+#### 21. **Male and female wing length**
 
@@
 
-**21.** **Male and female tarsus length**
+#### 22. **Male and female tarsus length**
 
@@
 
-**22. Female body condition (Tarsus/wing)**
+#### 23. **Female body condition (Tarsus/wing)**
 
@@
 
-### For variables that fit Parental care hypothesis:
-
-1\. **Number of mites**
+### Parental care hypothesis:
+
+#### 1. **Number of mites**
 
@@
 
-**3.** **Number of fleas**
+#### 2. **Number of fleas**
 
@@
 
-**4.** **Ticks Load**
+#### 4. **Ticks Load**
 
@@
 
-#### 1. **Haemoglobin Measure**
+#### 14. **Haemoglobin Measure**
 
@@
 
-#### **2. Glucose Measure**
+#### 15. **Glucose Measure**
 
@@
 
-#### **5. Nestling Immunity**
+#### 16. **Nestling Immunity**
 
@@
 
-#### **7. Nestling Leukocytes**
+#### 17. **Nestling Leukocytes**
 
@@
 
-#### **8. Chick Feather Development**
+#### 18. **Chick Feather Development**
 
@@
 
-#### **9. Development Score**
+#### 19. **Development Score**
 
@@
 
-#### **11. Telomere measure**
+#### 20. **Telomere measure**
 
@@
 
-#### **12. Fat Score**
+#### 21. **Fat Score**
 
@@
 
+### Summary fitness proxies
+
 ```{r}
@@
 
-# # kable(as.data.frame(summary(as.factor
-#                             (na.omit(
-#                               dataset_after_cleaning$fitness_proxy_cleaned)))),
-#       col.names=("Number of effect sizes"),
-#       caption = "Proxies of fitness")
+kable(as.data.frame(summary(as.factor
+                            (na.omit(
+                              dataset_after_cleaning$fitness_proxy_cleaned)))),
+      col.names=("Number of effect sizes"),
+      caption = "Proxies of fitness")
 
@@
 
-## We excluded some proxies from our dataset
+## Proxies exluced from our dataset
+
+Some proxies were excluded from the analyes after data cleaning:
 
 ```{r excluded proxies, echo=F}
-
-unique(dataset_after_cleaning$proxy_decision)
-
-excluded_proxies <- dataset_after_cleaning %>% filter(proxy_decision=="exclude" | proxy_decision=="exclude_NA" | proxy_decision=="excluded_NA" )
+## list all proxy_decision values
+#unique(dataset_after_cleaning$proxy_decision)
+excluded_proxies <- dataset_after_cleaning %>% 
+  filter(proxy_decision=="exclude" | proxy_decision=="exclude_NA" | proxy_decision=="excluded_NA" )
 
 excluded_proxies%>%
-  select(c(paper_ID,fitness_proxy,proxy_comment))%>%
-  kable(col.names=(c("Paper ID","Fitness Trait","Reason for exclusion" )),caption = "Excluded proxies")
-
+  select(c(paper_ID,fitness_proxy,proxy_comment)) %>%
+  kable(col.names=(c("Paper ID","Fitness Trait","Reason for exclusion" )), caption = "Excluded proxies")
+
+## remove from the data set
 dataset_after_cleaning <- dataset_after_cleaning %>% 
@@
 
- unique(dataset_after_cleaning$proxy_decision) 
-```
-
-### Adding Observation ID column
-
-```{r}
-dataset_after_cleaning <- dataset_after_cleaning %>%
-  mutate(Observation_ID=row_number(), .before = experiment_ID)
-
-```
-
-### Adding Hypothesis column
+## list all proxy_decision values after cleaning
+#unique(dataset_after_cleaning$proxy_decision) 
+```
+
+## Adding Observation ID column
+
+```{r}
+dataset_after_cleaning <- dataset_after_cleaning %>%
+  mutate(Observation_ID = row_number(), .before = experiment_ID)
+```
+
+## Adding Hypothesis column
 
@@
     ,.after = PCH)
-
 #checked, has no NAs
@@
 
-#### Cleaning Type of trait studied
+### Cleaning Type of trait studied
 
@@
 ```{r}
-
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-### Adding Type of parasites
+## Adding Type of parasites
 
@@
 
-### Time of addition of green nest material
+## Time of addition of green nest material
 
@@
 
-### Type of experimental design
+## Type of experimental design
 
@@
 
-(levels: Cyanistes caeruleus, Sturnus unicolor, Tachycineta bicolor, Sturnus vulgaris; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)
+(levels: *Cyanistes caeruleus*, *Sturnus unicolor*, *Tachycineta bicolor*, *Sturnus vulgaris*; note that these levels reflect the list of species studied in our current database, which may increase after updating our search and/or receiving unpublished data from authors)
 
@@
 
-## Some quick checks to make sure all names are clean
+### Cleaning coding of factors
+
+Checking coding of several factors to ensure all are named consistently
 
@@
 unique(dataset_after_cleaning$proxy_decision)
-
 ## found a typo, let's fix:
-
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 ## Ensuring all names for risk of bias meta-regression are clean
-
 unique(dataset_after_cleaning$blinding)
 
+## make blinding decision 'n' -> 'no'
 dataset_after_cleaning <- dataset_after_cleaning %>%
@@
 
-```{r}
-write.csv(dataset_after_cleaning,file=here::here("data/03_data_cleaning/dataset_after_cleaning.csv"),row.names = FALSE)
-```
+```{r, eval=FALSE}
+## save cleaned dataset to csv file
+write.csv(x = dataset_after_cleaning,
+          file = here::here("data/03_data_cleaning/dataset_after_cleaning.csv"), 
+          row.names = FALSE)
+```
+
+#### Session info
+
+```{r, echo=FALSE}
+sessionInfo()
+```

### 2025-08-31 code/07_data_analysis.Rmd
Code checked & formatted; html rendered

--- 2025-07-06 docs/code/07_data_analysis.Rmd
@@
 
-# Loading Data for analysis
-
-```{r load_packages-data, warning=FALSE, message=FALSE}
-
-# Setting up workspace
-
-# For plotting trees, and although not strictly necessary, we may need the `ggtree` R package, which you should be able to install by running:
- if (!require("BiocManager", quietly = TRUE))
+## Preface
+### Setting up the workspace
+
+* Install and load required packages
+
+```{r setup, warning=FALSE, message=FALSE}
+## Setting up workspace using pacman
+if (!requireNamespace("pacman", quietly = TRUE)) {
+  install.packages("pacman")
+}
+
+# For plotting trees, and although not strictly necessary, 
+# we may need the `ggtree` R package, which you should be able to install by running:
+if (!requireNamespace("ggtree", quietly = TRUE)) {
+  ## Install using BiocManager
+  if (!requireNamespace("BiocManager", quietly = TRUE)) {
     install.packages("BiocManager")
+  }
   BiocManager::install("ggtree")  
-
-if (!require("orchaRd", quietly = TRUE))
-devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
-
-pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs)
-
-#Packages needed
-
-rm(list=ls()) ## cleaning up
-
-set.seed(430) #set seed for reproducibility (for random number generation)
-
-# Functions needed
-
-# function to estimate typical sampling error variance obtained from 
-# https://github.com/Yefeng0920/heterogeneity_ecoevo/tree/main/function
+}
+
+## installing orchaRd from GitHub
+if (!requireNamespace("orchaRd", quietly = TRUE)) {
+  ## installing orchaRd from GitHub
+  pacman::p_install_gh("daniel1noble/orchaRd", ref = 'main')
+}
+
+## installing ggsankey from GitHub
+if (!requireNamespace("ggsankey", quietly = TRUE)) {
+  ## installing orchaRd from GitHub
+  pacman::p_install_gh("davidsjoberg/ggsankey", ref = 'main')
+}
+
+## Install/load required packages
+pacman::p_load(
+  car,
+  ellipse,
+  here,
+  ggpubfigs,
+  ggpubr,
+  ggsankey,
+  metafor,
+  orchaRd,
+  tidyverse
+)
+```
+
+### Custom functions
+
+For the presented analyses, we need to define the function [sigma2_v](https://github.com/Yefeng0920/heterogeneity_ecoevo/blob/main/function/function.R) to estimate typical sampling error variance
+
+```{r custom functions, warning=FALSE, message=FALSE}
 sigma2_v <- function(mod){
@@
 }
+```
+
+### Loading Data for analysis
+
+```{r load_packages-data, warning=FALSE, message=FALSE}
+## set seed for reproducibility 
+## (for random number generation)
+set.seed(430)
 
@@
 
-dataset_analysis<-read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))
-
-dataset_lnRR<-read_csv(here::here("data/04_data_analysis/dataset_lnRR.csv"))
-
-dataset_SMDH<-read_csv(here::here("data/04_data_analysis/dataset_SMDH.csv"))
-
-```
-
-### Creating Phylogeny for the plot
-
-```{r}
-# install.packages("pacman")
-# load packages
-
-pacman::p_load(rotl,
-               ape,
-               ggtree)
-
-# We have 7 bird species in the dataset
+dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))
+
+dataset_lnRR <- read_csv(here::here("data/04_data_analysis/dataset_lnRR.csv"))
+
+dataset_SMDH <- read_csv(here::here("data/04_data_analysis/dataset_SMDH.csv"))
+```
+
+## Creating Phylogeny for the plot
+
+```{r phylogeny, eval=FALSE}
+## NOT run
+## -----------------------------------------------------------
+
+## required packages
+pacman::p_load(rotl, ape, ggtree)
+
+## We have 7 bird species in the dataset
 bird_species <- unique(dataset_analysis$bird_species)
 
-# extracting taxonomic information
-taxa <- rotl::tnrs_match_names(names = bird_species)
-taxa
-
-# check approximate matches
+## extracting taxonomic information
+(taxa <- rotl::tnrs_match_names(names = bird_species))
+
+## check approximate matches
 taxa[taxa$approximate_match==TRUE & !(is.na(taxa$approximate_match)),]
 
-# phylogenetic information for our species from the Open Tree of Life
+## phylogenetic information for our species from the Open Tree of Life
 
 tree <- rotl::tol_induced_subtree(ott_ids = taxa[["ott_id"]], label_format = "name")
+## check
 ape::is.binary(tree)
 
-# here are the species included in the tree
+## here are the species included in the tree
 sort(tree$tip.label)
 
-# removing the underscore "_" from the tree tip.label
+## removing the underscore "_" from the tree tip.label
 tree$tip.label <- gsub("_"," ", tree$tip.label)
@@
 
-# compute branch lengths of tree
+## compute branch lengths of tree
 phylo_branch <- compute.brlen(tree, method = "Grafen", power = 1)
 
-# check tree is ultrametric
-is.ultrametric(phylo_branch) # TRUE
-
-# matrix to be included in the models
+## check tree is ultrametric
+is.ultrametric(phylo_branch)
+
+## matrix to be included in the models
 bird_phylo <- vcv(phylo_branch, cor = T)
@@
 
-plot(tree) #check: https://www.rdocumentation.org/packages/ape/versions/5.3/topics/plot.phylo
-```
-
-### Visualizing random effects structure
-
-```{r}
-# install.packages("devtools")
-devtools::install_github("davidsjoberg/ggsankey")
-library(ggsankey)
-
+## plot(tree) #check: https://www.rdocumentation.org/packages/ape/versions/5.3/topics/plot.phylo
+plot(tree)
+```
+
+## Visualizing random effects structure
+
+```{r random-effects}
 sankey_data <- dataset_analysis %>%
-  select(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded)%>%
+  ## select variables
+  select(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded) %>%
   mutate(across(c(Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded), as.factor)) %>%
@@
 sankey_data <- dataset_analysis %>%
-  select(paper_ID, bird_species, population_ID)%>%
+  select(paper_ID, bird_species, population_ID) %>%
   mutate(across(c(paper_ID, bird_species, population_ID), as.factor)) %>%
@@
 
-ggplot(sankey_data, aes(x = x, 
-               next_x = next_x, 
-               node = node, 
-               next_node = next_node,
-               fill = factor(node))) +
-  geom_sankey() +
-  scale_fill_discrete(drop=FALSE) +
-  theme(legend.position = "none")
-
-ggplot(sankey_data, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
+## visualise sankey_data
+ggplot(sankey_data,
+       aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node))) +
   geom_alluvial(flow.alpha = .6) +
@@
         plot.title = element_text(hjust = .5))
-
-```
-
-# Preparing datasets
+```
+
+## Preparing datasets
 
@@
 # in the correct data type
-
-dataset_analysis<- dataset_analysis%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID,bird_species), as.factor))
-
-dataset_lnRR<- dataset_lnRR%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID, bird_species), as.factor))
-
-dataset_SMDH<- dataset_SMDH%>%mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded, paper_ID, experiment_ID_coded, group_ID_coded, comparision_type,Hypothesis,trait_type,parasite_type,time_of_gnm_addition, blinding, random_assignment, missing_data, population_ID,bird_species), as.factor))
-
+dataset_analysis<- dataset_analysis %>%
+  mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded,
+                  paper_ID, experiment_ID_coded, group_ID_coded,
+                  comparision_type, Hypothesis, trait_type,
+                  parasite_type, time_of_gnm_addition, blinding,
+                  random_assignment, missing_data, population_ID,
+                  bird_species),
+                as.factor))
+
+dataset_lnRR <- dataset_lnRR %>%
+  mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded,
+                  paper_ID, experiment_ID_coded, group_ID_coded,
+                  comparision_type, Hypothesis, trait_type,
+                  parasite_type, time_of_gnm_addition, blinding,
+                  random_assignment, missing_data, population_ID, 
+                  bird_species),
+                as.factor))
+
+dataset_SMDH <- dataset_SMDH %>% mutate(across(c(paper_ID, Observation_ID, repeated_trait_ID_coded,
+                                                 paper_ID, experiment_ID_coded, group_ID_coded,
+                                                 comparision_type, Hypothesis, trait_type,
+                                                 parasite_type, time_of_gnm_addition, blinding,
+                                                 random_assignment, missing_data, population_ID,
+                                                 bird_species),
+                                               as.factor))
 ```
@@
 ```{r seperating datasets for analysis}
-
 ## For lnRR (or simply load dataset as provided)
-# dataset_lnRR<-dataset_analysis%>%
-# filter(lnRR_sign != "NA" | lnRR_variance != "NA")
-
-# selecting dataset which are not flagged
-dataset_lnRR<-dataset_lnRR%>%
+dataset_lnRR <- dataset_analysis %>%
+  filter(lnRR_sign != "NA" | lnRR_variance != "NA")
+
+## selecting dataset which are not flagged
+dataset_lnRR <- dataset_lnRR %>%
   filter(proxy_decision == "include")
 
-# selecting only published dataset
-dataset_lnRR_published<-dataset_lnRR%>%
+## selecting only published dataset
+dataset_lnRR_published <- dataset_lnRR %>%
   filter(!is.na(year_publication))
 
-# selecting dataset which are flagged
-lnRR_con_flagged<-dataset_analysis%>%
+## selecting dataset which are flagged
+lnRR_con_flagged <- dataset_analysis %>%
   filter(lnRR_sign != "NA" | lnRR_variance != "NA")%>%
@@
 
-# selecting dataset without those using 0 as ES because authors reported no effect
+## selecting dataset without those using 0 as ES because authors reported no effect
 lnRR_sin_missingES <- dataset_lnRR %>% 
@@
 
-lnRR_flagged_no_missingES<- lnRR_con_flagged %>% 
+lnRR_flagged_no_missingES <- lnRR_con_flagged %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))
 
-# selecting only dataset that passes geary's test
-lnRR_geary_passed<-dataset_lnRR%>%filter(geary_test=="pass")
+## selecting only dataset that passes geary's test
+lnRR_geary_passed <- dataset_lnRR %>%
+  filter(geary_test == "pass")
 
 ## For SMDH
-# selecting dataset which are not flagged
-dataset_SMDH<-dataset_analysis%>%
-   filter(proxy_decision == "include"| proxy_decision == "SMDH only"|proxy_decision =="contingency table") %>% filter(SMDH_sign != "NA")
-
-# selecting only published dataset
-dataset_SMDH_published<-dataset_SMDH%>%
+## --------------------------------------------------------------
+## selecting dataset which are not flagged
+dataset_SMDH <- dataset_analysis %>%
+  filter(proxy_decision != "sensitivity-analysis" | is.na(proxy_decision))
+
+## selecting only published datasets
+dataset_SMDH_published <- dataset_SMDH %>%
   filter(!is.na(year_publication))
 
-# selecting dataset which are flagged
-SMDH_con_flagged<-dataset_analysis%>%
+## selecting dataset which are flagged
+SMDH_con_flagged <- dataset_analysis %>%
   filter(SMDH_sign != "NA")
 
-# selecting dataset without those using 0 as ES because authors reported no effect
+## selecting dataset without those using 0 as ES 
+## because authors reported no effect
 
@@
 
-SMDH_flagged_no_missingES<- SMDH_con_flagged %>% 
+SMDH_flagged_no_missingES <- SMDH_con_flagged %>% 
   filter(!proxy_comment %in% c("use 0 as ES"))
 
-# selecting dataset which are not flagged but without the SMDH calculated from inferential statistics
-
-SMDH_no_inferential<-dataset_analysis%>%
-  filter(proxy_decision == "include")%>% filter(SMDH_sign != "NA")
-```
-
-# Overall effect : Intercept-only meta-analytic model
+## selecting dataset which are not flagged 
+## but without the SMDH calculated from inferential statistics
+
+SMDH_no_inferential <- dataset_analysis %>%
+  filter(proxy_decision == "include") %>%
+  filter(SMDH_sign != "NA")
+```
+
+## Overall effect : Intercept-only meta-analytic model
 
@@
 
-## using lnRR
+### using lnRR
 
 ```{r intercept-only-model-lnRR}
-VCV_lnRR<- vcalc(vi = lnRR_variance,
+VCV_lnRR <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
   data = dataset_lnRR,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
+  # assuming that the effect sizes within the same study 
+  # are correlated with rho = 0.5
+  rho = 0.5)
+
+intercept_lnRR <- rma.mv(
+  # specify lnRR as the effect size measure;
+  yi = lnRR_sign,
+  # specify lnRR's sampling variance-covariance matrix;
+  V = VCV_lnRR, 
   mods = ~ 1,
+  # set random effects structure
   random = list(~ 1 | paper_ID,
@@
   data = dataset_lnRR)
-# saving the model
-saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))
-
-# saving the dataset for this model
-write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
+```
+
+```{r, eval = FALSE}
+## NOT RUN
+
+## saving the model
+saveRDS(intercept_lnRR, 
+        file = here::here("model/intercept_lnRR.rds"))
+
+## saving the dataset for this model
+write.csv(dataset_lnRR,
+          here::here("data/04_data_analysis/intercept_lnRR.csv"))
 ```
@@
 
-```{r function-interpret-heterogeneity}
-# ## Function is from the Pluralistic approach to heterogeneity from Yefeng's Pre-print repository from GitHub
-# 
-# #-----------------------heterogeneity interpretation-----------------------#
-# het_interpret <- function(observed_value, het_type, es_type, data) {
-#   
-#   if (!het_type %in% c("I2", "CVH", "M", "sigma2", "V_bar")) {
-#     stop("Invalid heterogeneity type. Choose from 'I2', 'CVH', 'M', 'sigma2', or 'V_bar'.")
-#   }
-#   
-#   if (!es_type %in% unique(data$es.type)) {
-#     stop("Invalid effect size type. Check the levels of 'es.type'.")
-#   }
-#   
-#   filtered_data <- data %>% filter(es.type == es_type)
-#   
-#   if (nrow(filtered_data) == 0) {
-#     stop("No data available for the selected effect size type.")
-#   }
-#   
-#   het_values <- filtered_data[[het_type]]
-#   
-#   percentiles <- quantile(het_values, probs = seq(0, 1, by = 0.05), na.rm = TRUE)
-#   
-#   lower_bound <- max(percentiles[percentiles <= observed_value], na.rm = TRUE)
-#   upper_bound <- min(percentiles[percentiles >= observed_value], na.rm = TRUE)
-#   lower_percentile <- names(percentiles)[percentiles == lower_bound]
-#   upper_percentile <- names(percentiles)[percentiles == upper_bound]
-#   
-#   percentile_range <- paste0(lower_percentile, "-", upper_percentile, "th percentile")
-#   
-#   # return the results
-#   return(tibble::tibble(
-#     observed_value = observed_value,
-#     het_type = het_type,
-#     es_type = es_type,
-#     percentile_range = percentile_range
-#   ))
-# }
-# x<-het_interpret(observed_value= I2_main_model_vector[1], 
-#                  het_type = "I2", 
-#                  es_type = "lnRR_sign", 
-#                  data= intercept_lnRR)
-
+```{r function-interpret-heterogeneity, eval=FALSE}
+# Sun Aug 31 12:01:40 2025 ------------------------------
+# Uncommented this code chunk but set eval = F
+
+## Function is from the Pluralistic approach to heterogeneity 
+## from Yefeng's Pre-print repository from GitHub
+
+## -----------------------heterogeneity interpretation-----------------------#
+het_interpret <- function(observed_value, het_type, es_type, data) {
+
+  if (!het_type %in% c("I2", "CVH", "M", "sigma2", "V_bar")) {
+    stop("Invalid heterogeneity type. Choose from 'I2', 'CVH', 'M', 'sigma2', or 'V_bar'.")
+  }
+
+  if (!es_type %in% unique(data$es.type)) {
+    stop("Invalid effect size type. Check the levels of 'es.type'.")
+  }
+
+  filtered_data <- data %>% filter(es.type == es_type)
+
+  if (nrow(filtered_data) == 0) {
+    stop("No data available for the selected effect size type.")
+  }
+
+  het_values <- filtered_data[[het_type]]
+
+  percentiles <- quantile(het_values, probs = seq(0, 1, by = 0.05), na.rm = TRUE)
+
+  lower_bound <- max(percentiles[percentiles <= observed_value], na.rm = TRUE)
+  upper_bound <- min(percentiles[percentiles >= observed_value], na.rm = TRUE)
+  lower_percentile <- names(percentiles)[percentiles == lower_bound]
+  upper_percentile <- names(percentiles)[percentiles == upper_bound]
+
+  percentile_range <- paste0(lower_percentile, "-", upper_percentile, "th percentile")
+
+  # return the results
+  return(tibble::tibble(
+    observed_value = observed_value,
+    het_type = het_type,
+    es_type = es_type,
+    percentile_range = percentile_range
+  ))
+}
+x <- het_interpret(observed_value = I2_main_model_vector[1],
+                   het_type = "I2",
+                   es_type = "lnRR_sign",
+                   data = intercept_lnRR)
+# Sun Aug 31 12:04:36 2025 ------------------------------
+# Error in het_interpret(observed_value = I2_main_model_vector[1], het_type = "I2", :
+# Invalid effect size type. Check the levels of 'es.type'.
 ```
@@
 
-```{r}
-
+```{r sigma2_v intercept_lnRR}
 # Then also:
@@
 round(sum(intercept_lnRR$sigma2), 3)
-
 ```
@@
 ```{r intercept-only-model-SMDH}
-
-VCV_SMDH <- vcalc(vi = SMDH_variance,
+VCV_SMDH <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
   data = dataset_SMDH,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-                  )
-
-intercept_SMDH<- rma.mv(yi = SMDH_sign, # specify SMDH as the effect size measure;
-                    V = VCV_SMDH, # specify SMDH's sampling variance-covariance matrix;
+  # assuming that the effect sizes 
+  # within the same study are correlated with rho = 0.5
+  rho = 0.5 
+)
+
+intercept_SMDH <- rma.mv(
+  # specify SMDH as the effect size measure;
+  yi = SMDH_sign,
+  # specify SMDH's sampling variance-covariance matrix;
+  V = VCV_SMDH, 
   mods = ~ 1,
@@
   data = dataset_SMDH)
-
-# saving the model
+```
+
+```{r saving SMDH data, eval = FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+## saving the model
 saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))
 
-# saving the dataset for this model
+## saving the dataset for this model
 write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
@@
 
-## SMDH-heterogeneity
+### SMDH-heterogeneity
 
@@
 round(sum(intercept_SMDH$sigma2), 3)
-
 ```
@@
 
-```{r}
-dataset_bivariate <- data.frame(paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
+```{r Bivariate Meta-analytical model}
+dataset_bivariate <- data.frame(
+  paper_ID = c(dataset_lnRR$paper_ID, dataset_SMDH$paper_ID),
   Observation_ID = c(dataset_lnRR$Observation_ID, dataset_SMDH$Observation_ID),
@@
   V_ES = c(dataset_lnRR$lnRR_variance, dataset_SMDH$SMDH_variance),
-                      ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMDH", nrow(dataset_SMDH)))
-                      )
-
-VCV_bivariate <- vcalc(vi = V_ES, # sampling variances of lnRR and SMD that are correlated within the same study;
-             cluster = paper_ID, # study identity;
-             type = ES_measure, # different types of effect size measures underlying the observed effect sizes;
-             data = dataset_bivariate, # the long format data frame;
-             rho = 0.2, # assuming that the effect sizes within the same study are correlated with rho = 0.5.
-             nearpd = TRUE # specify whether impose the non positive definite VCV matrix (not invertible) to the nearest positive semi-definite matrix 
-             )
-
-Bivariate_model <- rma.mv(yi = ES, # specify the effect size estimate (the variable ES in our case);
-                V = VCV_bivariate, # specify the imputed variance-covariance matrix;
-                mods = ~ ES_measure - 1, # specify the variable "ES_measure" indicating the types of effect size measures;
+  ES_measure = c(rep("lnRR", nrow(dataset_lnRR)), rep("SMDH", nrow(dataset_SMDH))))
+
+VCV_bivariate <- vcalc(
+  # sampling variances of lnRR and SMD that are correlated within the same study;
+  vi = V_ES, 
+  # study identity;
+  cluster = paper_ID,
+  # different types of effect size measures underlying the observed effect sizes;
+  type = ES_measure, 
+  # the long format data frame;
+  data = dataset_bivariate, 
+  # assuming that the effect sizes within the same study are correlated with rho = 0.5.
+  rho = 0.2, 
+  # specify whether impose the non positive definite VCV matrix 
+  # (not invertible) to the nearest positive semi-definite matrix
+  nearpd = TRUE)
+
+Bivariate_model <- rma.mv(
+  # specify the effect size estimate (the variable ES in our case);
+  yi = ES, 
+  # specify the imputed variance-covariance matrix;
+  V = VCV_bivariate, 
+  # specify the variable "ES_measure" indicating the types of effect size measures;
+  mods = ~ ES_measure - 1, 
+  # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
   random = list(~ ES_measure | paper_ID, 
@@
                 ~ 1 | bird_species
-                              ), # add correlated random effects corresponding to the lnRR and SMD parameters in the same study;
-                struct = "UN", # impose an unstructured variance-covariance of the study-specific random effects;
-                test = "t", # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
-                method = "REML", # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
-                data = dataset_bivariate, # the long format dataset
-                sparse = T
-               )
-
-# Saving the model
-saveRDS(Bivariate_model, file = here::here("model/sensitivity_analysis/bivariate_model.rds"))
+  ), 
+  # impose an unstructured variance-covariance of the study-specific random effects;
+  struct = "UN",
+  # t distribution is specified to test the overall effect against the null hypothesis and construct confidence intervals;
+  test = "t", 
+  # restricted likelihood maximum is assigned as the estimator for variance components as suggested;
+  method = "REML", 
+  # the long format dataset
+  data = dataset_bivariate, 
+  sparse = T)
+
+summary(Bivariate_model)
+```
+
+```{r, eval = FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(Bivariate_model, 
+        file = here::here("model/sensitivity_analysis/bivariate_model.rds"))
+
 # saving the dataset for this model
-write.csv(dataset_bivariate,here::here("data/05_data_sensitivity_analysis/dataset_bivariate.csv"))
-
-summary(Bivariate_model)
+write.csv(dataset_bivariate,
+          here::here("data/05_data_sensitivity_analysis/dataset_bivariate.csv"))
 ```
@@
 ```{r WARNING = F}
-pacman::p_load(ellipse)
-ab.l <- matreg(y=2, x=1, R=Bivariate_model$G, cov=TRUE, means=coef(Bivariate_model), n=Bivariate_model$g.levels.comb.k) # fit regression model
-
-xy <- ellipse(Bivariate_model$G, centre=coef(Bivariate_model), level=0.95) # get 95% coverage region
-ellipse_df <- data.frame(x = xy[, 1], y = xy[, 2]) # convert it int dataframe so that we can use ggplot to make a figure
+# fit regression model
+ab.l <- matreg(
+  y = 2, 
+  x = 1,
+  R = Bivariate_model$G, 
+  cov = TRUE, 
+  means = coef(Bivariate_model), 
+  n = Bivariate_model$g.levels.comb.k)
+
+xy <- ellipse(Bivariate_model$G, 
+              centre = coef(Bivariate_model),
+              # get 95% coverage region
+              level = 0.95)
+
+## convert it into data frame 
+## so that we can use ggplot to make a figure
+ellipse_df <- data.frame(x = xy[, 1],
+                         y = xy[, 2])
 
@@
 There is a very high negative correlation between the two effect sizes.
-This probably is an artifact of the data and not a true correlation.
+This probably is an artefact of the data and not a true correlation.
 If you look at the model summary, the $tau^2$ for lnRR, it is extremely small 0.0008, i.e., there is very little variance.
@@
 For SMDH on the other hand, the $tau^2$ is 0.1681 that is much larger.
-This difference in the variance estimate itself could be causing this artifact of the model.
-I will only go ahead to present this model as a senstivity analysis because I am not completely convinced by it's robustness.
-
-# Sensitivity Analysis
+This difference in the variance estimate itself could be causing this artefact of the model.
+I will only go ahead to present this model as a sensitivity analysis because I am not completely convinced by it's robustness.
+
+## Sensitivity Analysis
 
@@
 ```{r}
-
 #----------------------------------------------------------------------------
@@
 # Preparing new variance-covariance matrix
-
-VCV_lnRR_published <- vcalc(vi = lnRR_variance,
+VCV_lnRR_published <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
   data = dataset_lnRR_published,
-                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+  # assuming that the effect sizes within the same study
+  #  are correlated with rho = 0.5
+  rho = 0.5 
 )
@@
 ## Running intercept only model
-
-SA_lnRR_published<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-                    V = VCV_lnRR_published, # specify lnRR's sampling variance-covariance matrix;
+SA_lnRR_published <- rma.mv(
+  # specify lnRR as the effect size measure;
+  yi = lnRR_sign, 
+  # specify lnRR's sampling variance-covariance matrix;
+  V = VCV_lnRR_published, 
   mods = ~ 1,
@@
   data = dataset_lnRR_published)
-
-# Saving the model
-saveRDS(SA_lnRR_published, file = here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
+```
+
+```{r, eval = F}
+## NOT RUN
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_lnRR_published, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
+
 # saving the dataset for this model
-write.csv(dataset_lnRR_published,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_published.csv"))
-
+write.csv(dataset_lnRR_published,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_published.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_lnRR_published)
@@
 # Preparing new variance-covariance matrix
-
-VCV_SMDH_published <- vcalc(vi = SMDH_variance,
+VCV_SMDH_published <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_SMDH_published<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_published<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_published, # specify lnRR's sampling variance-covariance matrix;
@@
   data = dataset_SMDH_published)
-
-# Saving the model
-saveRDS(SA_SMDH_published, file = here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))
-# saving the dataset for this model
-write.csv(dataset_SMDH_published,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_published.csv"))
-
+```
+
+```{r, eval =FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+## Saving the model
+saveRDS(SA_SMDH_published, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))
+
+## saving the dataset for this model
+write.csv(dataset_SMDH_published,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_published.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_SMDH_published)
 predict(SA_SMDH_published)
-
 ```
@@
 # Preparing new variance-covariance matrix
-
-VCV_lnRR_flagged <- vcalc(vi = lnRR_variance,
+VCV_lnRR_flagged <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_lnRR_flagged<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_flagged<- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_flagged, # specify lnRR's sampling variance-covariance matrix;
@@
   data = lnRR_con_flagged)
-
-# Saving the model
-saveRDS(SA_lnRR_flagged, file = here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
-# saving the dataset for this model
-write.csv(lnRR_con_flagged,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_con_flagged.csv"))
-
+```
+
+```{r, eval=FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+## Saving the model
+saveRDS(SA_lnRR_flagged, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
+
+## saving the dataset for this model
+write.csv(lnRR_con_flagged,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_con_flagged.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_lnRR_flagged)
@@
 
-VCV_SMDH_flagged <- vcalc(vi = SMDH_variance,
+VCV_SMDH_flagged <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 
-SA_SMDH_flagged<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_flagged<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_flagged, # specify lnRR's sampling variance-covariance matrix;
@@
   data = SMDH_con_flagged)
-
-# Saving the model
-saveRDS(SA_SMDH_flagged, file = here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))
-# saving the dataset for this model
-write.csv(SMDH_con_flagged,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_con_flagged.csv"))
-
+```
+
+```{r, eval=FALSE}
+## Saving the model
+saveRDS(SA_SMDH_flagged, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))
+
+## saving the dataset for this model
+write.csv(SMDH_con_flagged,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_con_flagged.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_SMDH_flagged)
 predict(SA_SMDH_flagged)
-
 ```
@@
 # Preparing new variance-covariance matrix
-
-VCV_lnRR_no_missingES <- vcalc(vi = lnRR_variance,
+VCV_lnRR_no_missingES <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_lnRR_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_no_missingES <- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
   data = lnRR_sin_missingES)
-
-# Saving the model
-saveRDS(SA_lnRR_no_missingES, file = here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+```
+
+```{r, eval=FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_lnRR_no_missingES, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+
 # saving the dataset for this model
-write.csv(lnRR_sin_missingES,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_sin_missingES.csv"))
-
+write.csv(lnRR_sin_missingES,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_sin_missingES.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_lnRR_no_missingES)
@@
 # Preparing new variance-covariance matrix
-
-VCV_SMDH_no_missingES <- vcalc(vi = SMDH_variance,
+VCV_SMDH_no_missingES <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_SMDH_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_no_missingES <- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
   data = SMDH_sin_missingES)
-
-# Saving the model
-saveRDS(SA_SMDH_no_missingES, file = here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SA_SMDH_no_missingES, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))
 # saving the dataset for this model
-write.csv(SMDH_sin_missingES,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_sin_missingES.csv"))
-
+write.csv(SMDH_sin_missingES,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_sin_missingES.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_SMDH_no_missingES)
 predict(SA_SMDH_no_missingES)
-
 ```
@@
 # Preparing new variance-covariance matrix
-
-VCV_flagged_no_missingES <- vcalc(vi = lnRR_variance,
+VCV_flagged_no_missingES <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_lnRR_flagged_no_missingES<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_flagged_no_missingES<- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
   data = lnRR_flagged_no_missingES)
-
+```
+
+```{r, eval=FALSE}
 # Saving the model
@@
 # saving the dataset for this model
-write.csv(lnRR_flagged_no_missingES,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_flagged_no_missingES.csv"))
-
+write.csv(lnRR_flagged_no_missingES,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_flagged_no_missingES.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_lnRR_flagged_no_missingES)
@@
 # Preparing new variance-covariance matrix
-
-VCV_SMDH_flagged_no_missingES <- vcalc(vi = SMDH_variance,
+VCV_SMDH_flagged_no_missingES <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_SMDH_flagged_no_missingES<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_flagged_no_missingES <- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_flagged_no_missingES, # specify lnRR's sampling variance-covariance matrix;
@@
   data = SMDH_flagged_no_missingES)
-
-# Saving the model
-saveRDS(SA_SMDH_flagged_no_missingES, file = here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SA_SMDH_flagged_no_missingES, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
 
 # saving the dataset for this model
-write.csv(SMDH_flagged_no_missingES,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_flagged_no_missingES.csv"))
-
+write.csv(SMDH_flagged_no_missingES,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_flagged_no_missingES.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_SMDH_flagged_no_missingES)
@@
 
+Are the meta-regression robust to this analysis
+
+```{r}
+dataset_lnRR_design_flagged_no_missingES <- lnRR_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_lnRR_design_flagged_no_missingES <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_design_flagged_no_missingES,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_design_flagged_no_missingE <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+  mods = ~ - 1 + comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_design_flagged_no_missingES)
+
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_SMDH_design_flagged_no_missingES <- SMDH_flagged_no_missingES %>% filter(!is.na(comparision_type))
+
+VCV_SMDH_design_flagged_no_missingES <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_design_flagged_no_missingES,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_design_flagged_no_missingE <-
+  metafor::rma.mv(
+    yi = SMDH_sign, # specify lnRR as the effect size measure;
+    V = VCV_SMDH_design_flagged_no_missingES ,# specify lnRR's sampling variance;
+    mods = ~ - 1 + comparision_type,
+    random = list(~ 1 | paper_ID,
+                  ~ 1 | Observation_ID,
+                  ~ 1 | group_ID_coded,
+                  ~ 1 | population_ID,
+                  ~ 1 | bird_species),
+    method = "REML",
+    test = "t",
+    control = list(optimizer="optim"),
+    data = dataset_SMDH_design_flagged_no_missingES)
+```
+
 ### No inferential stats for SMDH: effect sizes calculated from means, SDs, and sample size
@@
 # Preparing new variance-covariance matrix
-
-VCV_SMDH_no_inferential <- vcalc(vi = SMDH_variance,
+VCV_SMDH_no_inferential <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 ## Running intercept only model
-
-SA_SMDH_no_inferential<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_no_inferential<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_no_inferential, # specify lnRR's sampling variance-covariance matrix;
@@
   data = SMDH_no_inferential)
-
-# Saving the model
-saveRDS(SA_SMDH_no_inferential, file = here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_SMDH_no_inferential, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))
 
 # saving the dataset for this model
-write.csv(SMDH_no_inferential,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_inferential.csv"))
-
+write.csv(SMDH_no_inferential,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_inferential.csv"))
+```
+
+```{r}
 # What is the effect now?
-
 summary(SA_SMDH_no_inferential)
@@
 
-VCV_lnRR_geary_passed <- vcalc(vi = lnRR_variance,
+VCV_lnRR_geary_passed <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 
-SA_lnRR_geary_passed<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_geary_passed <- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_geary_passed, # specify lnRR's sampling variance-covariance matrix;
@@
   data = lnRR_geary_passed)
-
-# Saving the model
-saveRDS(SA_lnRR_geary_passed, file = here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SA_lnRR_geary_passed, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))
 
 # saving the dataset for this model
-write.csv(lnRR_geary_passed,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_geary_passed.csv"))
-
+write.csv(lnRR_geary_passed,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_geary_passed.csv"))
 ```
@@
 #----------------------------------------------------------------------------
-
-dataset_lnRR_no_para<-dataset_lnRR%>%filter(is.na(parasite_type))
+dataset_lnRR_no_para <- dataset_lnRR %>% 
+  filter(is.na(parasite_type))
 
 ## The dataset is reduced to almost half
-nrow(dataset_lnRR)-nrow(dataset_lnRR_no_para)
-
-VCV_lnRR_no_para <- vcalc(vi = lnRR_variance,
+nrow(dataset_lnRR) - nrow(dataset_lnRR_no_para)
+
+VCV_lnRR_no_para <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 
-SA_lnRR_no_para<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_no_para <- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_no_para, # specify lnRR's sampling variance-covariance matrix;
@@
   data = dataset_lnRR_no_para)
-
-# Saving the model
-saveRDS(SA_lnRR_no_para, file = here::here("model/sensitivity_analysis/SA_lnRR_no_para.rds"))
+```
+
+```{r, eval=FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_lnRR_no_para, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_no_para.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR_no_para,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_para.csv"))
-
+write.csv(dataset_lnRR_no_para,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_para.csv"))
+```
+
+```{r}
 #----------------------------------------------------------------------------
@@
 #----------------------------------------------------------------------------
-
-dataset_SMDH_no_para<-dataset_SMDH%>%filter(is.na(parasite_type))
+dataset_SMDH_no_para <- dataset_SMDH %>%
+  filter(is.na(parasite_type))
 
 ## The dataset is reduced to almost half
-nrow(dataset_SMDH)-nrow(dataset_SMDH_no_para)
-
-VCV_SMDH_no_para <- vcalc(vi = SMDH_variance,
+nrow(dataset_SMDH) - nrow(dataset_SMDH_no_para)
+
+VCV_SMDH_no_para <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 
-SA_SMDH_no_para<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_no_para<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_no_para, # specify lnRR's sampling variance-covariance matrix;
@@
   data = dataset_SMDH_no_para)
-
-# Saving the model
-saveRDS(SA_SMDH_no_para, file = here::here("model/sensitivity_analysis/SA_SMDH_no_para.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SA_SMDH_no_para, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_no_para.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_SMDH_no_para,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_para.csv"))
-
+write.csv(dataset_SMDH_no_para,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_para.csv"))
 ```
@@
 
-```{r lnRR rho sensitivity analysis}
-# rho_range <- c(0.3, 0.5, 0.7)
-# 
-# MLMAlnRR_VCV_range <- list() # repeatedly run the specified model with varying rho
-# for (i in 1:length(rho_range))
-# {VCV_range <- vcalc(vi = lnRR_variance,
-#                   cluster = paper_ID,
-#                   subgroup = group_ID,
-#                   obs = Observation_ID,
-#                   data = dataset_lnRR,
-#                    rho = rho_range[i],
-#                     ) # impute sampling variance covariance matrix with varying rho
-# 
-# MLMAlnRR_VCV_range[[i]] <- rma.mv(yi = lnRR_sign,
-#                                   V = VCV_range, # sampling variance covariance matrix with varying values of rho.
-#                                  random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | experiment_ID,
-#                                   ~ 1 | group_ID,
-#                                   ~ 1 | repeated_trait_ID),
-#                                   method = "REML",
-#                                   data = dataset_lnRR # run the model with varying rho
-# )
-# }
-# 
-# save(VCV_range, file = here::here("GNM/figures/VCV_range.Rdata"))
-# save(MLMAlnRR_VCV_range, file = here::here("GNM/figures/MLMAlnRR_VCV_range.Rdata"))
-
-```
-
-```{r Table for lnRR rho sensitivity analysis}
-
-# t4 <- data.frame(rho  = rho_range,
-#                  "overall effect"  = sapply(MLMAlnRR_VCV_range, function(x) coef(x)),
-#                  "standard error" = sapply(MLMAlnRR_VCV_range, function(x) x$se),
-#                  "p-value" = sapply(MLMAlnRR_VCV_range, function(x) x$pval),
-#                  "Lower CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.lb),
-#                  "Upper CI" = sapply(MLMAlnRR_VCV_range, function(x) x$ci.ub),
-#                  "Log-likehood" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[1,1]),
-#                  "AIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[3,1]),
-#                  "BIC" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[4,1]),
-#                  "AICc" = sapply(MLMAlnRR_VCV_range, function(x) fitstats(x)[5,1]))
-# 
-# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
-# 
-# t4 %>% dfround(4) %>% DT::datatable()
+```{r lnRR rho sensitivity analysis, eval=FALSE}
+# Sun Aug 31 13:13:02 2025 ------------------------------
+# Make Code chunk executable ...
+rho_range <- c(0.2,0.3, 0.5, 0.7,0.8)
+
+# repeatedly run the specified model with varying rho
+SA_lnRR_VCV_range <- list() 
+for (i in 1:length(rho_range)) {
+  VCV_range <- vcalc(
+    vi = lnRR_variance,
+    cluster = paper_ID,
+    obs = Observation_ID,
+    data = dataset_lnRR,
+    rho = rho_range[i])
+
+  # Sun Aug 31 13:13:25 2025 ------------------------------
+  #set lnRR_VCV_range[[i]] to SA_lnRR_VCV_range[[i]]
+
+  SA_lnRR_VCV_range[[i]] <- rma.mv(
+    yi = lnRR_sign,
+    V = VCV_range,
+    random = list(~ 1 | paper_ID,
+                  ~ 1 | Observation_ID,
+                  ~ 1 | group_ID_coded,
+                  ~ 1 | population_ID,
+                  ~ 1 | bird_species),
+    method = "REML",
+    data = dataset_lnRR)
+}
+```
+
+```{r, eval=FALSE}
+## NOT run
+## save to RDS file
+save(SA_lnRR_VCV_range, file = here::here("model/sensitivity_analysis/SA_lnRR_VCV_range.rds"))
+```
+
+```{r, eval=FALSE}
+# Sun Aug 31 13:14:00 2025 ------------------------------
+# Make Code chunk executable ...
+
+#------------------------------------------------------------------
+#-------------Now for SMDH the same SA with diff Rho---------------
+#------------------------------------------------------------------
+
+SA_SMDH_VCV_range <- list()
+for (i in 1:length(rho_range)){
+  VCV_range <- vcalc(
+    vi = SMDH_variance,
+    cluster = paper_ID,
+    obs = Observation_ID,
+    data = dataset_SMDH,
+    rho = rho_range[i])
+
+  SA_SMDH_VCV_range[[i]] <- rma.mv(
+    yi = SMDH_sign,
+    V = VCV_range,
+    random = list(~ 1 | paper_ID,
+                  ~ 1 | Observation_ID,
+                  ~ 1 | group_ID_coded,
+                  ~ 1 | population_ID,
+                  ~ 1 | bird_species),
+    method = "REML",
+    data = dataset_SMDH)
+}
+```
+
+```{r, eval=FALSE}
+## NOT RUN
+## -----------------------------------------------------------
+
+save(SA_SMDH_VCV_range, 
+     file = here::here("model/sensitivity_analysis/SA_SMDH_VCV_range.rds"))
 ```
@@
 lnRR_hypothesis <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+  metafor::rma.mv(
+    yi = lnRR_sign, # specify lnRR as the effect size measure;
     V = VCV_lnRR,# specify lnRR's sampling variance;
@@
     data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN
+## -----------------------------------------------------------
 # Save model
-saveRDS(lnRR_hypothesis, file = here::here("model/lnRR_hypothesis.rds"))
+saveRDS(lnRR_hypothesis, 
+        file = here::here("model/lnRR_hypothesis.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR,here::here("data/04_data_analysis/hypothesis_lnRR.csv"))
-
+write.csv(dataset_lnRR,
+          here::here("data/04_data_analysis/hypothesis_lnRR.csv"))
+```
+
+```{r}
 lnRR_hypothesis_R2 <- r2_ml(lnRR_hypothesis)
@@
 
-SMDH_hypothesis <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_hypothesis <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH)
-
+```
+
+```{r, eval=FALSE}
 # Save model
-saveRDS(SMDH_hypothesis, file = here::here("model/SMDH_hypothesis.rds"))
+saveRDS(SMDH_hypothesis,
+        file = here::here("model/SMDH_hypothesis.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_SMDH,here::here("data/04_data_analysis/hypothesis_SMDH.csv"))
+write.csv(dataset_SMDH,
+          here::here("data/04_data_analysis/hypothesis_SMDH.csv"))
 ```
@@
 ```{r}
-# This analysis only includes dataset that has a proxy relating to comaparision type
-dataset_lnRR_design <- dataset_lnRR %>% filter(!is.na(comparision_type))
-
-VCV_lnRR_design <- vcalc(vi = lnRR_variance,
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_lnRR_design <- dataset_lnRR %>% 
+  filter(!is.na(comparision_type))
+
+VCV_lnRR_design <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 )
+
 lnRR_design <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+  metafor::rma.mv(
+    yi = lnRR_sign, # specify lnRR as the effect size measure;
     V = VCV_lnRR_design ,# specify lnRR's sampling variance;
@@
     data = dataset_lnRR_design )
-
-# Saving the model
-saveRDS(lnRR_design, file = here::here("model/lnRR_design.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(lnRR_design,
+        file = here::here("model/lnRR_design.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR_design,here::here("data/04_data_analysis/design_lnRR.csv"))
-
-# This analysis only includes dataset that has a proxy relating to comaparision type
-dataset_SMDH_design <- dataset_SMDH %>% filter(!is.na(comparision_type))
-
-VCV_SMDH_design <- vcalc(vi = SMDH_variance,
+write.csv(dataset_lnRR_design,
+          here::here("data/04_data_analysis/design_lnRR.csv"))
+```
+
+```{r}
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_SMDH_design <- dataset_SMDH %>%
+  filter(!is.na(comparision_type))
+
+VCV_SMDH_design <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 )
-SMDH_design <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+
+SMDH_design <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_design ,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH_design )
-
-# Saving the model
-saveRDS(SMDH_design, file = here::here("model/SMDH_design.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SMDH_design, 
+        file = here::here("model/SMDH_design.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_SMDH_design,here::here("data/04_data_analysis/design_SMDH.csv"))
+write.csv(dataset_SMDH_design,
+          here::here("data/04_data_analysis/design_SMDH.csv"))
 ```
@@
 ```{r}
-
 ## For the lnRR effect size...
-dataset_lnRR_no_comp3<-dataset_lnRR%>%filter(comparision_type!=3)
+dataset_lnRR_no_comp3 <- dataset_lnRR %>% 
+  filter(comparision_type!=3 | is.na(comparision_type))
+
 ## Only some rows are removed... 
-nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp3)
-
-VCV_lnRR_no_comp3 <- vcalc(vi = lnRR_variance,
+nrow(dataset_lnRR) - nrow(dataset_lnRR_no_comp3)
+
+VCV_lnRR_no_comp3 <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 
-SA_lnRR_no_comp3<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+SA_lnRR_no_comp3<- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_no_comp3, # specify lnRR's sampling variance-covariance matrix;
@@
   data = dataset_lnRR_no_comp3)
-
-# Saving the model
-saveRDS(SA_lnRR_no_comp3, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
+```
+
+```{r, eval=FALSE}
+# Saving the model
+saveRDS(SA_lnRR_no_comp3, 
+        file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR_no_comp3,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp3.csv"))
-
+write.csv(dataset_lnRR_no_comp3,
+          here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp3.csv"))
+```
+
+```{r}
 #----------------------------------------------------------------------------
@@
 
-dataset_SMDH_no_comp3<-dataset_SMDH%>%filter(comparision_type!=3)
+dataset_SMDH_no_comp3 <- dataset_SMDH %>%
+  filter(comparision_type!=3 | is.na(comparision_type))
+
 ## Only some rows are removed... 
-nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp3)
-
-VCV_SMDH_no_comp3 <- vcalc(vi = SMDH_variance,
+nrow(dataset_SMDH) - nrow(dataset_SMDH_no_comp3)
+
+VCV_SMDH_no_comp3 <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 
-SA_SMDH_no_comp3<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SA_SMDH_no_comp3<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_no_comp3, # specify lnRR's sampling variance-covariance matrix;
@@
   data = dataset_SMDH_no_comp3)
-
-# Saving the model
-saveRDS(SA_SMDH_no_comp3, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_SMDH_no_comp3, 
+        file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_SMDH_no_comp3,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp3.csv"))
-```
-
-Results remain practically the same irrespective..
+write.csv(dataset_SMDH_no_comp3,
+          here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp3.csv"))
+```
+
+Overall conclusions remain practically the same irrespective.. now what about the meta-regression using Type of Experiment Design
+
+```{r}
+dataset_lnRR_design_SA <- dataset_lnRR %>%
+  filter(comparision_type!=3)
+
+VCV_lnRR_design_SA <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_design_SA,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_design_SA <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_design_SA ,# specify lnRR's sampling variance;
+  mods = ~ - 1 + comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_design_SA )
+
+## Now for SMDH
+
+dataset_SMDH_design_SA <- dataset_SMDH %>%
+  filter(comparision_type!=3)
+
+VCV_SMDH_design_SA <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_design_SA,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_design_SA <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_design_SA ,# specify lnRR's sampling variance;
+  mods = ~ - 1 + comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH_design_SA)
+```
 
@@
 ## We use the complete dataset in this case
-lnRR_time_gnm_addition <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+lnRR_time_gnm_addition <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
@@
   data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
 ## Saving the model
-saveRDS(lnRR_time_gnm_addition, file = here::here("model/lnRR_time_gnm_addition.rds"))
+saveRDS(lnRR_time_gnm_addition, 
+        file = here::here("model/lnRR_time_gnm_addition.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR,here::here("data/04_data_analysis/time_gnm_lnRR.csv"))
-
+write.csv(dataset_lnRR,
+          here::here("data/04_data_analysis/time_gnm_lnRR.csv"))
+```
+
+```{r}
 ## Now similarly for the SMDH effect size using the complete dataset
-SMDH_time_gnm_addition <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_time_gnm_addition <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
@@
   data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
 ## Saving the model
-saveRDS(SMDH_time_gnm_addition, file = here::here("model/SMDH_time_gnm_addition.rds"))
+saveRDS(SMDH_time_gnm_addition, 
+        file = here::here("model/SMDH_time_gnm_addition.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_SMDH,here::here("data/04_data_analysis/time_gnm_SMDH.csv"))
+write.csv(dataset_SMDH,
+          here::here("data/04_data_analysis/time_gnm_SMDH.csv"))
 ```
@@
 # This analysis only includes dataset that has a proxy relating to parasite or pathogen
-dataset_lnRR_parasite <- dataset_lnRR%>%
-  filter(!is.na(parasite_type))%>%
+dataset_lnRR_parasite <- dataset_lnRR %>%
+  filter(!is.na(parasite_type)) %>%
   mutate(parasite_type=as.factor(parasite_type),
@@
 
-VCV_lnRR_parasite <- vcalc(vi = lnRR_variance,
+VCV_lnRR_parasite <- vcalc(
+  vi = lnRR_variance,
   cluster = paper_ID,
@@
 
-lnRR_parasite <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+lnRR_parasite <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_parasite,# specify lnRR's sampling variance;
@@
   data = dataset_lnRR_parasite)
-
-# Saving the model
-saveRDS(lnRR_parasite, file = here::here("model/lnRR_parasite.rds"))
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_parasite, 
+        file = here::here("model/lnRR_parasite.rds"))
 
 # saving the dataset for this model
-write.csv(dataset_lnRR_parasite,here::here("data/04_data_analysis/parasite_lnRR.csv"))
-
-### Similiarly for SMDH as well selecting the dataset with parasite type
+write.csv(dataset_lnRR_parasite,
+          here::here("data/04_data_analysis/parasite_lnRR.csv"))
+```
+
+```{r}
+### Similarly for SMDH as well selecting the dataset with parasite type
 # This analysis only includes dataset that has a proxy relating to parasite or pathogen
-dataset_SMDH_parasite <- dataset_SMDH%>%
+dataset_SMDH_parasite <- dataset_SMDH %>%
   filter(!is.na(parasite_type))
-VCV_SMDH_parasite <- vcalc(vi = SMDH_variance,
+
+VCV_SMDH_parasite <- vcalc(
+  vi = SMDH_variance,
   cluster = paper_ID,
@@
 
-SMDH_parasite <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_parasite <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH_parasite)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
@@
 ```{r}
-lnRR_birds <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+lnRR_birds <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR,# specify lnRR's sampling variance;
@@
   data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
@@
 write.csv(dataset_lnRR,here::here("data/04_data_analysis/birds_lnRR.csv"))
-
+```
+
+```{r}
 ## Now doing this for SMDH
 
-SMDH_birds <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_birds <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
@@
 ```{r}
-
-lnRR_trait <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+lnRR_trait <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR,# specify lnRR's sampling variance;
@@
 write.csv(dataset_lnRR,here::here("data/04_data_analysis/trait_lnRR.csv"))
-
+```
+
+```{r}
 ## Now similarly for SMDH
 
-SMDH_trait <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_trait <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH,# specify lnRR's sampling variance;
@@
 
+# Sensitivity Analysis: Excluding Non-aromatic Vs. Aromatic
+
+We are aware that removing over 50% of the dataset will cause some moderator levels to drop out.
+But if our goal is to critically examine the role of aromaticity and potentially argue that its importance has been overstated, this could be a very informative step.
+
+```{r}
+## For the lnRR effect size...
+dataset_lnRR_no_comp1<-dataset_lnRR %>%
+  filter(comparision_type!=1 | is.na(comparision_type))
+
+## Only some rows are removed... 
+nrow(dataset_lnRR) - nrow(dataset_lnRR_no_comp1)
+
+VCV_lnRR_no_comp1 <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_no_comp1,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SA_lnRR_no_comp1<- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+  mods = ~ 1,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  control = list(optimizer="optim"),
+  test = "t",
+  data = dataset_lnRR_no_comp1)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_lnRR_no_comp1, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_lnRR_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp1.csv"))
+```
+
+```{r}
+#----------------------------------------------------------------------------
+# for  SMDH  as Effect Size
+#----------------------------------------------------------------------------
+
+dataset_SMDH_no_comp1 <- dataset_SMDH %>%
+  filter(comparision_type!=1 | is.na(comparision_type))
+
+## Only some rows are removed... 
+nrow(dataset_SMDH) - nrow(dataset_SMDH_no_comp1)
+
+VCV_SMDH_no_comp1 <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_no_comp1,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SA_SMDH_no_comp1<- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_no_comp1, # specify lnRR's sampling variance-covariance matrix;
+  mods = ~ 1,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  control = list(optimizer="optim"),
+  test = "t",
+  data = dataset_SMDH_no_comp1)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SA_SMDH_no_comp1, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))
+
+# saving the dataset for this model
+write.csv(dataset_SMDH_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp1.csv"))
+```
+
+```{r}
+#----------------------------------------------------------------------------
+# Rerunning the two mechanistic hypothesis meta-regressions with those effect sizes excluded
+#----------------------------------------------------------------------------
+
+lnRR_hypothesis_no_comp1 <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_no_comp1,# specify lnRR's sampling variance;
+  mods = ~ - 1 + Hypothesis,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_no_comp1)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Save model
+saveRDS(lnRR_hypothesis_no_comp1, file = here::here("model/lnRR_hypothesis_no_comp1.rds"))
+```
+
+```{r}
+SMDH_hypothesis_no_comp1 <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_no_comp1,# specify lnRR's sampling variance;
+  mods = ~ - 1 + Hypothesis,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH_no_comp1)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Save model
+saveRDS(SMDH_hypothesis_no_comp1, file = here::here("model/SMDH_hypothesis_no_comp1.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------
+## Now re-running all the 5 meta-regressions once again
+#----------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_lnRR_design_no_comp1 <- dataset_lnRR_no_comp1 %>%
+  filter(!is.na(comparision_type))
+
+VCV_lnRR_design_no_comp1 <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_design_no_comp1,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+lnRR_design_no_comp1 <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
+  mods = ~ - 1 + comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_design_no_comp1 )
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))
+```
+
+```{r}
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_SMDH_design_no_comp1 <- dataset_SMDH_no_comp1 %>%
+  filter(!is.na(comparision_type))
+
+VCV_SMDH_design_no_comp1 <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_design_no_comp1,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_design_no_comp1 <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
+  mods = ~ - 1 + comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_design_no_comp1 )
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))
+```
+
 # Risk of Bias
 
-6\. Blinding: (Levels: yes, no(
-
-7\. Random Assignment: (Levels: yes, no)
-
-8\. Missing Data: (Levels: yes, no)
-
-Note that the specific subset of data for each meta-regression may differ based on the data availability (e.g., information about the type of parasites is only available for effect sizes based on parasite/pathogen related fitness proxy).
-We will conduct meta-regression on suitable subsets of data for each analysis, provided we have sufficient effect sizes per moderator level (i.e., at least 5 effect sizes per moderator level).
-
-::: callout-important
-## Phylogenetic Effects
-
-Note also that if we obtain additional effect sizes for other bird species after we update our search and/or contact authors, our models may need to account for phylogenetic nonindependence via the inclusion of two additional random effects: "species" and "phylogeny" following Cinar et al.
-(2022).
-:::
-
-## Other Analysis
-
-### Risk of Bias Assessment
-
--   RoB - The outcome will be presented in the form of a [**summary table**]{.underline}. We will conduct uni-moderator meta-regressions using these variables.
+We have pre-registered the Risk Of Bias analysis, the three we will explore:
+
+1.  **Blinding**
+
+```{r}
+unique(dataset_lnRR$blinding)
+
+lnRR_blinding <- metafor::rma.mv(
+  yi = lnRR_sign,
+  V = VCV_lnRR,
+  mods = ~ - 1 + blinding,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_blinding, file = here::here("model/lnRR_blinding.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_blinding.csv"))
+```
+
+```{r}
+SMDH_blinding <- metafor::rma.mv(
+  yi = SMDH_sign, 
+  V = VCV_SMDH,
+  mods = ~ - 1 + blinding,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_blinding, file = here::here("model/SMDH_blinding.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_blinding.csv"))
+```
+
+2.  Random Assignment
+
+```{r}
+unique(dataset_lnRR$random_assignment)
+
+lnRR_random_assignment <- metafor::rma.mv(
+  yi = lnRR_sign,
+  V = VCV_lnRR,
+  mods = ~ - 1 + random_assignment,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_random_assignment, file = here::here("model/lnRR_random_assignment.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_random_assignment.csv"))
+```
+
+```{r}
+SMDH_random_assignment <- metafor::rma.mv(
+  yi = SMDH_sign, 
+  V = VCV_SMDH,
+  mods = ~ - 1 + random_assignment,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_random_assignment, file = here::here("model/SMDH_random_assignment.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_random_assignment.csv"))
+```
+
+3.  Missing Vs. Not Missing
+
+```{r}
+unique(dataset_lnRR$missing_data)
+
+lnRR_missing_data <- metafor::rma.mv(
+  yi = lnRR_sign,
+  V = VCV_lnRR,
+  mods = ~ - 1 + missing_data,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_missing_data, file = here::here("model/lnRR_missing_data.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_lnRR,here::here("data/04_data_analysis/lnRR_missing_data.csv"))
+```
+
+```{r}
+SMDH_missing_data <- metafor::rma.mv(
+  yi = SMDH_sign, 
+  V = VCV_SMDH,
+  mods = ~ - 1 + missing_data,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_missing_data, file = here::here("model/SMDH_missing_data.rds"))
+
+# Saving the dataset for this model
+write.csv(dataset_SMDH,here::here("data/04_data_analysis/SMDH_missing_data.csv"))
+```
 
@@
 ```{r}
-
-dataset_lnRR_published<-dataset_lnRR_published%>%
-  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+dataset_lnRR_published <- dataset_lnRR_published %>%
+  mutate(effective_n_inv = 
+           1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control))) %>%
   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))
 
-lnRR_small_study <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+lnRR_small_study <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_published,# specify lnRR's sampling variance;
@@
   data = dataset_lnRR_published)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
@@
 saveRDS(lnRR_small_study, file = here::here("model/lnRR_small_study.rds"))
-
+```
+
+```{r}
 summary(lnRR_small_study)
-
 round(r2_ml(lnRR_small_study)*100,2)
@@
 
-dataset_SMDH_published<-dataset_SMDH_published%>%
-  mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
+dataset_SMDH_published <- dataset_SMDH_published %>%
+  mutate(effective_n_inv = 
+           1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control))) %>%
   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))
 
-SMDH_small_study <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+SMDH_small_study <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_published,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH_published)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
 
@@
 saveRDS(SMDH_small_study, file = here::here("model/SMDH_small_study.rds"))
-
+```
+
+```{r}
 summary(SMDH_small_study)
-
 round(r2_ml(SMDH_small_study)*100,2)
-
 ```
@@
 ```{r}
-dataset_lnRR_published<-dataset_lnRR_published%>%
-  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])
-
-lnRR_decline_eff <-
-  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
+dataset_lnRR_published <- dataset_lnRR_published %>%
+  mutate(year_MeanCenter = scale(as.numeric(year_publication), scale = F)[,1])
+
+lnRR_decline_eff <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
   V = VCV_lnRR_published,# specify lnRR's sampling variance;
@@
 saveRDS(lnRR_decline_eff, file = here::here("model/lnRR_decline_eff.rds"))
-
+```
+
+```{r}
 summary(lnRR_decline_eff)
-
 round(r2_ml(lnRR_decline_eff)*100,2)
@@
 ## --- Now for SMDH -----
-dataset_SMDH_published<-dataset_SMDH_published%>%
-  mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])
-
-SMDH_decline_eff <-
-  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
+
+dataset_SMDH_published<-dataset_SMDH_published %>%
+  mutate(year_MeanCenter = scale(as.numeric(year_publication), scale = F)[,1])
+
+SMDH_decline_eff <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
   V = VCV_SMDH_published,# specify lnRR's sampling variance;
@@
   data = dataset_SMDH_published)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
 # saving the model
 saveRDS(SMDH_decline_eff, file = here::here("model/SMDH_decline_eff.rds"))
-
+```
+
+```{r}
 summary(SMDH_decline_eff)
-
 round(r2_ml(SMDH_decline_eff)*100,2)
-
 ```
@@
 # 
-# dataset_lnRR_all_in<-dataset_lnRR%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
-#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
-#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
-#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
-#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
-# 
-# VCV_lnRR_all_in<- vcalc(vi = lnRR_variance,
-#                   cluster = paper_ID,
-#                   obs = Observation_ID,
-#                   data = dataset_lnRR_all_in,
-#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-#                   )
-# 
-# lnRR_all_in <- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
-#                     mods = ~ time_of_gnm_addition + 
-#                       year_MeanCenter + 
-#                       sqrt_effective_n_inv + 
-#                       as.factor(comparision_type) + 
-#                       bird_species + 
-#                       trait_type,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                     control = list(optimizer="optim"),
-#                     test = "t",
-#                     data = dataset_lnRR_all_in)
-# 
-# 
-# 
-# ## For SMDH complete published dataset
-# 
-# dataset_SMDH_all_in<-dataset_SMDH%>%mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication))%>%
-#   mutate(year_MeanCenter=scale(as.numeric(year_publication),scale=F)[,1])%>%
-#   mutate(effective_n_inv=1/((4*effective_n_experiment*effective_n_control)/(effective_n_experiment+effective_n_control)))%>%
-#   mutate(sqrt_effective_n_inv=sqrt(effective_n_inv))%>%
-#   mutate(comparision_type= case_when(is.na(comparision_type) ~ 4, TRUE ~ comparision_type))
-# 
-# VCV_SMDH_all_in<- vcalc(vi = SMDH_variance,
-#                   cluster = paper_ID,
-#                   obs = Observation_ID,
-#                   data = dataset_SMDH_all_in,
-#                   rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
-#                   )
-# 
-# SMDH_all_in<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
-#                     mods = ~ time_of_gnm_addition + 
-#                       year_MeanCenter + 
-#                       sqrt_effective_n_inv + 
-#                       as.factor(comparision_type) + 
-#                       bird_species + 
-#                       trait_type,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                     control = list(optimizer="optim"),
-#                     test = "t",
-#                     data = dataset_SMDH_all_in)
+dataset_lnRR_all_in <- dataset_lnRR %>%
+  mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication)) %>%
+  mutate(year_MeanCenter = scale(as.numeric(year_publication), scale = F)[,1]) %>%
+  mutate(effective_n_inv = 
+           1/((4*effective_n_experiment * effective_n_control)/(effective_n_experiment + effective_n_control))) %>%
+  mutate(sqrt_effective_n_inv = sqrt(effective_n_inv)) %>%
+  mutate(comparision_type = case_when(is.na(comparision_type) ~ as.factor(4), TRUE ~ comparision_type))
+
+VCV_lnRR_all_in <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_all_in,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_all_in <- rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_all_in, # specify lnRR's sampling variance-covariance matrix;
+  mods = ~ time_of_gnm_addition +
+    year_MeanCenter +
+    sqrt_effective_n_inv +
+    comparision_type +
+    bird_species +
+    trait_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  control = list(optimizer="optim"),
+  test = "t",
+  data = dataset_lnRR_all_in)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# saving the model
+saveRDS(lnRR_all_in, file = here::here("model/lnRR_all_in.rds"))
+```
+
+```{r}
+## For SMDH complete published dataset
+
+dataset_SMDH_all_in <- dataset_SMDH %>%
+  mutate(year_publication = case_when(is.na(year_publication) ~ 2025, TRUE ~ year_publication)) %>%
+  mutate(year_MeanCenter = scale(as.numeric(year_publication), scale = F)[,1]) %>%
+  mutate(effective_n_inv = 
+           1/((4 * effective_n_experiment * effective_n_control)/(effective_n_experiment + effective_n_control))) %>%
+  mutate(sqrt_effective_n_inv = sqrt(effective_n_inv)) %>%
+  mutate(comparision_type = case_when(is.na(comparision_type) ~ as.factor(4), TRUE ~ comparision_type))
+
+VCV_SMDH_all_in <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_all_in,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_all_in <- rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_all_in, # specify lnRR's sampling variance-covariance matrix;
+  mods = ~ time_of_gnm_addition +
+    year_MeanCenter +
+    sqrt_effective_n_inv +
+    as.factor(comparision_type) +
+    bird_species +
+    trait_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  control = list(optimizer="optim"),
+  test = "t",
+  data = dataset_SMDH_all_in)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# saving the model
+saveRDS(SMDH_all_in, file = here::here("model/SMDH_all_in.rds"))
 ```
@@
 #----------------------------------------------------------------------------------
-
-# lnRR_hypothesis_pc <-
-#   metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
-#                     V = VCV_lnRR,# specify lnRR's sampling variance;
-#                     mods = ~ Hypothesis,
-#                     random = list(~ 1 | paper_ID,
-#                                   ~ 1 | Observation_ID,
-#                                   ~ 1 | group_ID_coded,
-#                                   ~ 1 | population_ID,
-#                                   ~ 1 | bird_species),
-#                     method = "REML",
-#                   test = "t",
-#                   control = list(optimizer="optim"),
-#                   data = dataset_lnRR)
-# 
-# # I now want to test for statistical differences between groups. Male and fem
-# # information for androgens can be obtained from the outcome of the table. For thyroid
-# # hormones I need to do Post-hoc Wald tests: 
-# car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
-```
+## For lnRR
+VCV_lnRR<- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_hypothesis_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR,# specify lnRR's sampling variance;
+  mods = ~ Hypothesis,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+
+# I now want to test for statistical differences between groups. Male and fem
+# information for androgens can be obtained from the outcome of the table. For thyroid
+# hormones I need to do Post-hoc Wald tests:
+car::linearHypothesis(lnRR_hypothesis_pc, rbind(c(0,1,-1)))
+
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# saving the model
+saveRDS(lnRR_hypothesis_pc, file = here::here("model/lnRR_hypothesis_pc.rds"))
+```
+
+```{r}
+# For SMDH
+
+VCV_SMDH <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_hypothesis_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH,# specify lnRR's sampling variance;
+  mods = ~ Hypothesis,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+
+# I now want to test for statistical differences between groups. Male and fem
+# information for androgens can be obtained from the outcome of the table. For thyroid
+# hormones I need to do Post-hoc Wald tests:
+car::linearHypothesis(SMDH_hypothesis_pc, rbind(c(0,1,-1)))
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# saving the model
+saveRDS(SMDH_hypothesis_pc, file = here::here("model/SMDH_hypothesis_pc.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------------
+# For Type of experimental design
+#----------------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_lnRR_design <- dataset_lnRR %>%
+  filter(!is.na(comparision_type))
+
+VCV_lnRR_design <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_design,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_design_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_design ,# specify lnRR's sampling variance;
+  mods = ~ comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_design )
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_design_pc, file = here::here("model/lnRR_design_pc.rds"))
+```
+
+```{r}
+# This analysis only includes dataset that has a proxy relating to comparison type
+dataset_SMDH_design <- dataset_SMDH %>%
+  filter(!is.na(comparision_type))
+
+VCV_SMDH_design <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_design,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_design_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_design ,# specify lnRR's sampling variance;
+  mods = ~ comparision_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH_design )
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_design_pc, file = here::here("model/SMDH_design_pc.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------------
+# For Time of addition of GNM
+#----------------------------------------------------------------------------------
+
+## We use the complete dataset in this case
+lnRR_time_gnm_addition_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+  mods = ~ time_of_gnm_addition,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+## Saving the model
+saveRDS(lnRR_time_gnm_addition_pc, file = here::here("model/lnRR_time_gnm_addition_pc.rds"))
+```
+
+```{r}
+## Now similarly for the SMDH effect size using the complete dataset
+SMDH_time_gnm_addition_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH,# specify lnRR's sampling variance using the variance-covariance matrix we created for the intercept-only model since the whole dataset is being used in this case as well
+  mods = ~ time_of_gnm_addition,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+## Saving the model
+saveRDS(SMDH_time_gnm_addition_pc, file = here::here("model/SMDH_time_gnm_addition_pc.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------------
+# Parasite Type
+#----------------------------------------------------------------------------------
+
+# This analysis only includes dataset that has a proxy relating to parasite or pathogen
+dataset_lnRR_parasite <- dataset_lnRR %>%
+  filter(!is.na(parasite_type)) %>%
+  mutate(parasite_type = as.factor(parasite_type),
+         paper_ID = as.factor(paper_ID),
+         Observation_ID = as.factor(Observation_ID),
+         group_ID_coded = as.factor(group_ID_coded),
+         bird_species = as.factor(bird_species))
+
+VCV_lnRR_parasite <- vcalc(
+  vi = lnRR_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_lnRR_parasite,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+lnRR_parasite_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR_parasite,# specify lnRR's sampling variance;
+  mods = ~ parasite_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR_parasite)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_parasite_pc, file = here::here("model/lnRR_parasite_pc.rds"))
+```
+
+```{r}
+### Similarly for SMDH as well selecting the dataset with parasite type
+# This analysis only includes dataset that has a proxy relating to parasite or pathogen
+dataset_SMDH_parasite <- dataset_SMDH %>%
+  filter(!is.na(parasite_type))
+
+VCV_SMDH_parasite <- vcalc(
+  vi = SMDH_variance,
+  cluster = paper_ID,
+  obs = Observation_ID,
+  data = dataset_SMDH_parasite,
+  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
+)
+
+SMDH_parasite_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH_parasite,# specify lnRR's sampling variance;
+  mods =  parasite_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH_parasite)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Save the model
+saveRDS(SMDH_parasite_pc, file = here::here("model/SMDH_parasite_pc.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------------
+# Bird Species
+#----------------------------------------------------------------------------------
+
+lnRR_birds_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR,# specify lnRR's sampling variance;
+  mods = ~ bird_species,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_birds_pc, file = here::here("model/lnRR_birds_pc.rds"))
+```
+
+```{r}
+## Now doing this for SMDH
+
+SMDH_birds_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH,# specify lnRR's sampling variance;
+  mods = ~  bird_species,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_birds_pc, file = here::here("model/SMDH_birds_pc.rds"))
+```
+
+```{r}
+#----------------------------------------------------------------------------------
+# Type of trait studied
+#----------------------------------------------------------------------------------
+
+lnRR_trait_pc <- metafor::rma.mv(
+  yi = lnRR_sign, # specify lnRR as the effect size measure;
+  V = VCV_lnRR,# specify lnRR's sampling variance;
+  mods = ~ trait_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_lnRR)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(lnRR_trait_pc, file = here::here("model/lnRR_trait_pc.rds"))
+```
+
+```{r}
+## Now similarly for SMDH
+SMDH_trait_pc <- metafor::rma.mv(
+  yi = SMDH_sign, # specify lnRR as the effect size measure;
+  V = VCV_SMDH,# specify lnRR's sampling variance;
+  mods = ~ trait_type,
+  random = list(~ 1 | paper_ID,
+                ~ 1 | Observation_ID,
+                ~ 1 | group_ID_coded,
+                ~ 1 | population_ID,
+                ~ 1 | bird_species),
+  method = "REML",
+  test = "t",
+  control = list(optimizer="optim"),
+  data = dataset_SMDH)
+```
+
+```{r, eval=FALSE}
+## NOT RUN 
+## -----------------------------------------------------------
+
+# Saving the model
+saveRDS(SMDH_trait_pc, file = here::here("model/SMDH_trait_pc.rds"))
+```
+
+## Session info
+```{r}
+sessionInfo()
+```

### 2025-08-31 code/08_figures-tables.Rmd
Code checked & formatted; html rendered

--- 2025-07-09 code/08_figures-tables.Rmd
@@
 
-# Visualising location and bird species
-
-I am using the figure code from here and adapting it for my needs..
-
-Mentesana, L., Hau, M., D'Amelio, P.B., Adreani, N.M.
-and Sánchez-Tójar, A.
-(2025), Do Egg Hormones Have Fitness Consequences in Wild Birds?
-A Systematic Review and Meta-Analysis.
-Ecology Letters, 28: e70100.
-<https://doi.org/10.1111/ele.70100>
-
-Code here: `https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R`
-
-```{r message=FALSE, warning=FALSE}
-## Let's get the needed packages
-if (!requireNamespace("devtools", quietly = TRUE))
-    install.packages("devtools")
-
-if (!requireNamespace("orchaRd", quietly = TRUE))
-    devtools::install_github("daniel1noble/orchaRd", ref = "main")
-
-pacman::p_load(ggplot2,dplyr,stringr,readr,cowplot,maps)
-
-## Let's first get the data in for this plot
+## Visualising location and bird species
+
+For visualising purposes we use adapt code by [Mentesana, Hau, D'Amelio, Adreani, & Sánchez-Tójar, (2025)](https://doi.org/10.1111/ele.70100), available on the accompanying [GitHub repository](https://github.com/ASanchez-Tojar/meta-analysis_egg_hormones_and_fitness/blob/main/code/003_figures.R).
+
+The following code chunk is used to set up the workspace and load (or install) all required packages to replicate the generatation of figures and tables presented in our manuscript.
+
+```{r load packages, message=FALSE, warning=FALSE}
+## Setting up workspace using pacman
+if (!requireNamespace("pacman", quietly = TRUE)) {
+  install.packages("pacman")
+}
+
+## installing orchaRd from GitHub
+if (!requireNamespace("orchaRd", quietly = TRUE)) {
+  ## installing orchaRd from GitHub
+  pacman::p_install_gh("daniel1noble/orchaRd", ref = 'main')
+}
+
+## Install/load required packages
+pacman::p_load(
+  cowplot,
+  ggraph, # visualising author network
+  gt, # suppl 
+  here,
+  igraph, # visualising author network
+  maps,
+  metafor,
+  orchaRd,
+  patchwork,
+  purrr,
+  tidyverse)
+```
+
+For the purpose of this map, longitude and latitude of the study area manually added to the dataset.
+They are saved to `dataset_analysis$population_location` as they were extracted from the respective papers.
+If not provided by the authors, a general location was manually selected.
+Note, coordinates are used for visualising only.
+
+* Load datasets
+
+```{r location-map}
+## Load data for plotting a location map
+## -----------------------------------------------------------
 
 # Loading cleaned dataset
-dataset_analysis<- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))
-
-```
-
-```{r location-map}
-
-# To split population_ID into location and country
+dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"))
+
+## Split population_ID into location and country
 dataset_analysis[c('Location','Country')] <- str_split_fixed(dataset_analysis$population_ID, ',', 2)
 
-### For the purpose of this map, I am adding the the longitude and latitude of the study area manually.
-They exist in the dataset_analysis$population_location as they were extracted from the paper.
-I have also added some by just searching the general location since the coordinates were not provided for these..
-
-data_coordinates<-data.frame(Location = unique(dataset_analysis$Location),
-                             Lat_Location=c(51.50,38.41,40.45,
-                                            45.40,52.39, 37.18,
-                                            54,39.05,
-                                            51.57,48,42.54,39.95,
+## set coordinates for sampling locations
+data_coordinates <- data.frame(
+  Location = unique(dataset_analysis$Location),
+  Lat_Location = c(51.50, 38.41, 40.45, 45.40, 52.39, 37.18,
+                   40.53, 54, 39.05, 51.57, 48, 42.54, 39.95,
                    40.13,28.10,52.06,60.39),
-                             Long_Location=c(19.29,-9.02,-3.50,
-                                             -64.10,6.05,-3.11,
-                                             -124,-76.81,
-                                             -2.26,11,8.91,-75.16,
-                                             -8.27,107.10,8.25,5.32))
+  Long_Location = c(19.29,-9.02,-3.50, -64.10, 6.05, -3.11,
+                    -4.01, -124, -76.81, -2.26, 11, 8.91,
+                    -75.16, -8.27, 107.10, 8.25, 5.32))
 
 ## Let's now merge the datasets by the location names
-
 dataset_analysis <- dataset_analysis %>%
@@
 location_counts <- dataset_analysis %>%
-  group_by(Location) %>%
-  summarise(size.freq = n_distinct(paper_ID), .groups = 'drop')
+  group_by(Location, bird_species) %>%
+  summarise(size.freq = n())
 
@@
            aes(map_id = region), 
-    color = "white", fill= "#D9EAF7") + 
+           color = "white", fill = "#D9EAF7") + 
   geom_point(data = dataset_analysis_unique_rows, 
              aes(x = Long_Location, y = Lat_Location,
-                 size = size.freq, colour=bird_species), alpha = 0.6) +
-scale_size(range = c(3, 5)) +
+                 size = size.freq, colour = bird_species),
+             alpha = 0.6) +
+  scale_size(range = c(1, 2.5)) +
   scale_fill_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
@@
                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  guides(size = "none", alpha = "none") +
+  guides(size = "none", alpha = "none",
+         colour = guide_legend(override.aes = list(size = 1.5), keywidth = 0.4,
+                               keyheight = 0.4)) +
   labs(x = "Longitude",
        y = "Latitude",
-       col = "Bird Species")+
+       col = "Bird Species") +
   theme_classic() +
-  theme(legend.position = c(0.99, 0.15),
+  theme(plot.margin = margin(t = 15, r = 15, b = 5, l = 5),  
+        legend.position = c(1.02, 0.42),
         legend.justification = c("right", "bottom"),
         legend.background = element_rect(fill = "white", color = "black"),
-        legend.text = element_text(size=6),
-        axis.title = element_text(size = 10),
-        axis.text.x = element_text(size = 10),
-        axis.text.y = element_blank())
+        legend.text = element_text(size = 6),
+        legend.title = element_text(size = 7),
+        axis.title = element_text(size = 8),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10))
 
@@
                  size = size.freq, colour = bird_species),
-             alpha = 0.9) +
-  scale_size(range = c(2, 4)) +
+             position = position_jitter(width = 0.2, height = 0.2),
+             alpha = 0.7) +
+  scale_size(range = c(1, 2)) +
   scale_colour_manual(values = c("#00B0BE","#FFB255",  "#FF8CAE", 
@@
   theme_void() +
-  theme(
-    legend.position = "none",
-    plot.background = element_rect(color = "white", fill="white"),
-    panel.border = element_rect(colour = "black", fill = NA, size = 1)
-  )
+  theme(legend.position = "none",
+        plot.background = element_rect(color = "white", fill = "white"),
+        panel.border = element_rect(colour = "black", fill = NA, size = 1))
 
@@
   draw_plot(fig_map) +
-  draw_plot(zoom_map, x = 0.05, y = 0.15, width = 0.28, height = 0.38) + theme(panel.border = element_rect(colour = "black", fill=NA, size=1.5))
-
-ggsave(here::here("figures/Figure_Distribution.png"), plot = geographic_distribution, height = 100, width = 170, units= 'mm', dpi = 600)
-```
-
-# Visualizing author network
-
-```{r}
-# # Loading cleaned dataset
+  draw_plot(zoom_map, x = 0.11, y = 0.21, width = 0.20, height = 0.28) +
+  theme(panel.border = element_rect(colour = "black", fill = NA, size = 1.2))
+
+print(geographic_distribution)
+```
+
+```{r, eval=FALSE}
+## Save image file
+ggsave(here::here("figures/Figure_Distribution.png"),
+       plot = geographic_distribution, height = 100, width = 170, units= 'mm', dpi = 600)
+```
+
+## Visualizing author network
+
+```{r author-network, eval=FALSE}
+# Sun Aug 31 19:25:52 2025 ------------------------------
+# Show code, but eval = FALSE
+
+## Loading cleaned dataset
+# Sun Aug 31 19:26:35 2025 ------------------------------
+# The folliwing file is not found, assume same as above?!
 # dataset_analysis<- read_csv(here::here("data/03_data_cleaning/dataset_analysis.csv"))
-# 
-# library(tidyverse)
-# library(tidyr)
-# library(igraph)
-# installed.packages("ggraph")
-# library(ggraph)
-# 
-# clean_author <- function(name) {
-#   name %>%
-#     str_replace_all(",", "") %>%   # remove commas
-#     str_squish() %>%              # remove excess whitespace
-#     str_to_title()                # standardize case (optional, if needed)
-# }
-# 
-# # Apply cleaning to first and last author fields
-# author_roles <- dataset_analysis %>%
-#   distinct(paper_ID, .keep_all = TRUE) %>%
-#   select(paper_ID, authors, bird_species) %>%
-#   mutate(
-#     author_list = str_split(authors, ";\\s*"),
-#     first_author = map_chr(author_list, 1),
-#     last_author = map_chr(author_list, ~ tail(.x, 1))
-#   )%>%
-#   mutate(
-#     first_author=case_when(
-#       first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
-#       first_author == "Soler J J" ~ "Soler J. J.",
-#       first_author == "Glądalski, M" ~ "Gladalski M.",
-#       first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
-#       TRUE ~ as.character(first_author)
-#     ))%>%
-#   mutate(
-#     last_author=case_when(
-#       last_author == "Veiga J P" ~ "Veiga J. P.",
-#       TRUE ~ as.character(last_author)
-#     )
-#   )
-# 
-# # 2. Create Core Author Pairs (First → Last)
-# author_pairs_core <- author_roles %>%
-#   select(paper_ID, first_author, last_author) %>%
-#   rename(from = first_author, to = last_author) %>%
-#   filter(from != to) %>%
-#   count(from, to, name = "weight")
-# 
-# # 3. Build Author Graph
-# author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)
-# 
-# # 4. Assign Dominant Bird Species to PIs (last authors)
-# author_species <- author_roles %>%
-#   select(last_author, bird_species) %>%
-#   group_by(last_author, bird_species) %>%
-#   count() %>%
-#   slice_max(n, n = 1) %>%
-#   distinct(last_author, .keep_all = TRUE)
-# 
-# # Add species as vertex attribute
-# V(author_graph)$bird_species <- author_species$bird_species[
-#   match(V(author_graph)$name, author_species$last_author)
-# ]
-# 
-# # 5. Optional: Scale node size by number of papers per author
-# author_paper_counts <- author_roles %>%
-#   pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
-#   count(author, name = "paper_count")
-# 
-# # Add paper count attribute
-# V(author_graph)$paper_count <- author_paper_counts$paper_count[
-#   match(V(author_graph)$name, author_paper_counts$author)
-# ]
-# 
-# # Replace NAs with small size for isolated authors
-# V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1
-# 
-# # 6. Plot with ggraph
-# ggraph(author_graph, layout = "fr") +
-#   geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
-#   geom_node_point(aes(color = bird_species, size = paper_count)) +
-#   geom_node_text(aes(label = name), repel = TRUE, size = 3) +
-#   scale_edge_width(range = c(0.3, 2)) +
-#   scale_size(range = c(3, 10)) +
-#   theme_void() +
-#   labs(title = "Author Collaboration Network by Bird Species",
-#        size = "Paper Count") +
-#   theme(legend.position = "right")
-#
-
-```
-
-# Intercept only model
+
+clean_author <- function(name) {
+  name %>%
+    str_replace_all(",", "") %>%   # remove commas
+    str_squish() %>%              # remove excess whitespace
+    str_to_title()                # standardize case (optional, if needed)
+}
+
+# Apply cleaning to first and last author fields
+author_roles <- dataset_analysis %>%
+  distinct(paper_ID, .keep_all = TRUE) %>%
+  select(paper_ID, authors, bird_species) %>%
+  mutate(
+    author_list = str_split(authors, ";\\s*"),
+    first_author = map_chr(author_list, 1),
+    last_author = map_chr(author_list, ~ tail(.x, 1))
+  ) %>%
+  mutate(
+    first_author=case_when(
+      first_author == "Polo, V" | first_author == "Polo V" ~ "Polo V.",
+      first_author == "Soler J J" ~ "Soler J. J.",
+      first_author == "Glądalski, M" ~ "Gladalski M.",
+      first_author == "Gwinner, H" | first_author == "Gwinner H" ~ "Gwinner H.",
+      TRUE ~ as.character(first_author)
+    )) %>%
+  mutate(
+    last_author=case_when(
+      last_author == "Veiga J P" ~ "Veiga J. P.",
+      TRUE ~ as.character(last_author)
+    )
+  )
+
+# 2. Create Core Author Pairs (First → Last)
+author_pairs_core <- author_roles %>%
+  select(paper_ID, first_author, last_author) %>%
+  rename(from = first_author, to = last_author) %>%
+  filter(from != to) %>%
+  count(from, to, name = "weight")
+
+# 3. Build Author Graph
+author_graph <- graph_from_data_frame(author_pairs_core, directed = TRUE)
+
+# 4. Assign Dominant Bird Species to PIs (last authors)
+author_species <- author_roles %>%
+  select(last_author, bird_species) %>%
+  group_by(last_author, bird_species) %>%
+  count() %>%
+  slice_max(n, n = 1) %>%
+  distinct(last_author, .keep_all = TRUE)
+
+# Add species as vertex attribute
+V(author_graph)$bird_species <- author_species$bird_species[
+  match(V(author_graph)$name, author_species$last_author)
+]
+
+# 5. Optional: Scale node size by number of papers per author
+author_paper_counts <- author_roles %>%
+  pivot_longer(cols = c(first_author, last_author), names_to = "role", values_to = "author") %>%
+  count(author, name = "paper_count")
+
+# Add paper count attribute
+V(author_graph)$paper_count <- author_paper_counts$paper_count[
+  match(V(author_graph)$name, author_paper_counts$author)
+]
+
+# Replace NAs with small size for isolated authors
+V(author_graph)$paper_count[is.na(V(author_graph)$paper_count)] <- 1
+
+# 6. Plot with ggraph
+ggraph(author_graph, layout = "fr") +
+  geom_edge_link(aes(width = weight), alpha = 0.4, color = "grey50") +
+  geom_node_point(aes(color = bird_species, size = paper_count)) +
+  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
+  scale_edge_width(range = c(0.3, 2)) +
+  scale_size(range = c(3, 10)) +
+  theme_void() +
+  labs(title = "Author Collaboration Network by Bird Species",
+       size = "Paper Count") +
+  theme(legend.position = "right")
+```
+
+## Intercept only model
 
@@
 ```{r orchard plot for intercept only models}
-pacman::p_load(here,tidyverse,metafor,orchaRd,patchwork,cowplot)
-
 # Loading models for SMDH and lnRR
-
-intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
-intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
+intercept_lnRR <- readRDS(here::here("model/intercept_lnRR.rds"))
+intercept_SMDH <- readRDS(here::here("model/intercept_SMDH.rds"))
 
 # Plot for lnRR
-
-intercept_lnRR_plot<- orchaRd::orchard_plot(intercept_lnRR,
+intercept_lnRR_plot <- orchaRd::orchard_plot(
+  intercept_lnRR,
   mod = "1",
@@
   xlab = "Effect size (lnRR)", 
-                                             fill =  T) +
+  fill =  T,
+  k.pos = c(0.53,0.6,0.6)) +
   scale_fill_manual(values = "#98C127") +
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_blank()
-  ) +
+    axis.text.y = element_blank()) +
   labs(x = "Intercept")
@@
 # Plot for SMDH
-intercept_SMDH_plot <- orchaRd::orchard_plot(intercept_SMDH,
+intercept_SMDH_plot <- orchaRd::orchard_plot(
+  intercept_SMDH,
   mod = "1",
@@
   xlab = "Effect size (SMDH)",
-                                    fill = TRUE) +
+  fill = TRUE,
+  k.pos = c(2,0.6,0.6)) +
   scale_fill_manual(values = "#F47A00") +
@@
   plot_annotation(tag_level = c("A","B"))
-
-ggsave(here::here("figures/Figure_overall_effect.png"), plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
-
-###----------------------------------------------------------------------------------
-
-## Now the cropped versions presented in the main manuscript..
-
-###----------------------------------------------------------------------------------
-
-intercept_lnRR_plot_crop <- orchaRd::orchard_plot(intercept_lnRR,
+print(Figure_intercept)
+```
+
+```{r figures/Figure_overall_effect.png, eval=FALSE}
+## save image file
+ggsave(here::here("figures/Figure_overall_effect.png"), 
+       plot = Figure_intercept, height = 150, width = 170, units = "mm", dpi = 600)
+```
+
+Now the crop the figure as presented in the main manuscript
+
+```{r orchard plot for intercept only models; manuscript file}
+intercept_lnRR_plot_crop <- orchaRd::orchard_plot(
+  intercept_lnRR,
   mod = "1",
@@
   xlab = "Effect size (lnRR)", 
-                                             fill =  T) +
+  fill =  T,
+  k.pos = c(0.53,0.6,0.6)) +
   scale_fill_manual(values = "#98C127") +
   scale_colour_manual(values = "#98C127" ) +
-    scale_y_continuous(limits = c(-0.7, 0.7)) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
   theme_minimal(base_size = 14) +
@@
 # Plot for SMDH
-intercept_SMDH_plot_crop <- orchaRd::orchard_plot(intercept_SMDH,
+intercept_SMDH_plot_crop <- orchaRd::orchard_plot(
+  intercept_SMDH,
   mod = "1",
@@
   xlab = "Effect size (SMDH)",
-                                    fill = TRUE) +
+  fill = TRUE,
+  k.pos = c(2,0.6,0.6)) +
   scale_fill_manual(values = "#F47A00") +
   scale_colour_manual(values = "#F47A00") +
-  scale_y_continuous(limits = c(-2.7, 2.7)) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
   theme_minimal(base_size = 14) +
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_blank()
-  ) +
-  labs(x = "Intercept")
+    axis.text.y = element_blank()) + labs(x = "Intercept")
 
@@
   plot_annotation(tag_level = c("A","B"))
-
-ggsave(here::here("figures/Figure_overall_effect_crop.png"), plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
-```
-
-# Hypothesis meta-regression
+print(Figure_intercept_crop)
+```
+
+```{r figures/Figure_overall_effect_crop.png, eval=FALSE}
+## save image file 
+ggsave(here::here("figures/Figure_overall_effect_crop.png"), 
+       plot = Figure_intercept_crop, height = 150, width = 170, units = "mm", dpi = 600)
+```
+
+## Hypothesis meta-regression
 
 ```{r orchard plot hypothesis meta-regression}
-
 # Loading models for SMDH and lnRR
-
-lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
-SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))
+lnRR_hypothesis <- readRDS(here::here("model/lnRR_hypothesis.rds"))
+SMDH_hypothesis <- readRDS(here::here("model/SMDH_hypothesis.rds"))
 
 # Plot lnRR meta-regression on hypothesis
-
-lnRR_hypothesis_plot <-
-  orchard_plot(mod_results(lnRR_hypothesis,
+lnRR_hypothesis_plot <- orchard_plot(mod_results(
+  lnRR_hypothesis,
   mod = "Hypothesis",
@@
   alpha = 0.4,
-               xlab ="") +
+  xlab = "") +
   scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
@@
   labs(x = "",
-       y = "Effect size (lnRR)")+
+       y = "Effect size (lnRR)") +
   theme(
     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+    legend.position.inside = c(0.99, 0.01),
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.justification = c(1, 0), 
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
   scale_x_discrete(labels = c("Both","Courtship","Parental Care"))
@@
 # Plot SMDH meta-regression on hypothesis
-
-SMDH_hypothesis_plot <-
-  orchard_plot(
-    mod_results(
+SMDH_hypothesis_plot <- orchard_plot(mod_results(
   SMDH_hypothesis,
   mod = "Hypothesis",
-      group = "paper_ID"
-    ),
+  group = "paper_ID"),
   trunk.size = 0.25,
@@
   alpha = 0.4,
-    xlab ="") +
+  xlab = "") +
   scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
   scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  labs(x = "",
-       y = "Effect size (SMDH)")+
+  labs(x = "", y = "Effect size (SMDH)") +
   theme(
     panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+    legend.position.inside = c(0.99, 0.01),
+    legend.background = element_blank(),
+    legend.key = element_blank(),
     legend.justification = c(1, 0), 
@@
   plot_annotation(tag_level = c("A","B"))
-
-ggsave(here::here("figures/Figure_hypothesis.png"), plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
-
-##-----------------------------------------------------------------------------
-
-# Now the cropped figures for the main manuscript
-
-##-----------------------------------------------------------------------------
-
+print(Figure_hypothesis)
+```
+
+```{r figures/Figure_hypothesis.png, eval=FALSE}
+## save image file 
+ggsave(here::here("figures/Figure_hypothesis.png"),
+       plot = Figure_hypothesis, height = 120, width = 250, units = "mm", dpi = 600)
+```
+
+Now the cropped figures for the main manuscript
+
+```{r orchard plot hypothesis meta-regression; MS fig}
 # Plot lnRR meta-regression on hypothesis
-
-lnRR_hypothesis_plot_crop <-
-  orchard_plot(mod_results(lnRR_hypothesis,
+lnRR_hypothesis_plot_crop <- orchard_plot(mod_results(
+  lnRR_hypothesis,
   mod = "Hypothesis",
@@
   fill = T,
-               xlab ="") +
+  k.pos = c(0.4,0.6,0.6),
+  xlab = "") +
   scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
   scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-    scale_y_continuous(limits = c(-0.7, 0.7)) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
   labs(x = "",
-       y = "Effect size (lnRR)")+
-  theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+       y = "Effect size (lnRR)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
         legend.justification = c(1, 0), 
         legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
         legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+        legend.text = element_text(size = 5),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
   scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
@@
 # Plot SMDH meta-regression on hypothesis
-
-SMDH_hypothesis_plot_crop <-
-  orchard_plot(
-    mod_results(
+SMDH_hypothesis_plot_crop <- orchard_plot(mod_results(
   SMDH_hypothesis,
   mod = "Hypothesis",
-      group = "paper_ID"
-    ),
+  group = "paper_ID"),
   trunk.size = 0.5,
@@
   fill = T,
-    xlab ="") +
+  k.pos = c(1.9,0.6,0.6),
+  xlab = "") +
   scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
   scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  scale_y_continuous(limits = c(-2.7, 2.7)) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
   labs(x = "",
-       y = "Effect size (SMDH)")+
-  theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position.inside = c(0.99, 0.05),
+       y = "Effect size (SMDH)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
         legend.justification = c(1, 0), 
         legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
         legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
+        legend.text = element_text(size = 5),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
   scale_x_discrete(labels = c("Both","Courtship","Parental\nCare"))
@@
   plot_annotation(tag_level = c("A","B"))
-
-ggsave(here::here("figures/Figure_hypothesis_crop.png"), plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
-```
-
-# Other meta-regressions
-
-# A. Combined Plot
-
-## Time of green nest material addition
+print(Figure_hypothesis_crop)
+```
+
+```{r figures/Figure_hypothesis_crop.png, eval=FALSE}
+ggsave(here::here("figures/Figure_hypothesis_crop.png"),
+       plot = Figure_hypothesis_crop, height = 120, width = 250, units = "mm", dpi = 600)
+```
+
+## Other meta-regressions
+
+### A. Combined Plot
+
+#### Time of green nest material addition
 
 ```{r orchard plot time of gnm addition meta-regression}
-
 # Loading models for SMDH and lnRR
 
-lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
-SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
-
-lnRR_time_gnm_addition_plot <-
-  orchard_plot(mod_results(
+lnRR_time_gnm_addition <- readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
+SMDH_time_gnm_addition <- readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
+
+lnRR_time_gnm_addition_plot <- orchard_plot(mod_results(
   lnRR_time_gnm_addition,
   mod = "time_of_gnm_addition",
-      group = "paper_ID"
-    ),
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  labs(x = "", y = "Effect Size (lnRR)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
+  scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+
+SMDH_time_gnm_addition_plot <- orchard_plot(mod_results(
+  SMDH_time_gnm_addition,
+  mod = "time_of_gnm_addition",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  labs(x = "", y = "Effect Size (SMDH)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
+  scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+```
+
+Now the cropped figures for the main manuscript
+
+```{r lnRR_time_gnm_addition_plot_cropped}
+lnRR_time_gnm_addition_plot_cropped <- orchard_plot(mod_results(
+  lnRR_time_gnm_addition,
+  mod = "time_of_gnm_addition",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
+  labs(x = "", y = "Effect Size (lnRR)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
+  scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+
+SMDH_time_gnm_addition_plot_cropped <- orchard_plot(mod_results(
+  SMDH_time_gnm_addition,
+  mod = "time_of_gnm_addition",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1.9,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+  labs(x = "", y = "Effect Size (SMDH)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
+  scale_x_discrete(labels = c("After egg\nlaying", "Before egg\nlaying", "Continous\naddition"))
+```
+
+```{r Sun Aug 31 19:49:27 2025, eval=FALSE}
+# Sun Aug 31 19:49:27 2025 ------------------------------
+# Figure save is missing!
+```
+
+## Experimental Design
+
+```{r orchard plot experimental design meta-regression}
+# Loading models for SMDH and lnRR
+lnRR_design <- readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design <- readRDS(here::here("model/SMDH_design.rds"))
+
+lnRR_design_plot <- orchard_plot(mod_results(
+  lnRR_design,
+  mod = "comparision_type",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  labs(x = "", y = "Effect Size (lnRR)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic",
+                              "No material\nVs. aromatic",
+                              "No material\nVs. non-Aromatic"))
+
+SMDH_design_plot <- orchard_plot(mod_results(
+  SMDH_design,
+  mod = "comparision_type",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1.5,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  labs(x = "", y = "Effect Size (SMDH)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic",
+                              "No material\nVs. aromatic",
+                              "No material\nVs. Non-aromatic"))
+```
+
+Now the cropped figures for the main manuscript
+
+```{r orchard plot experimental design meta-regression; manuscript figure}
+lnRR_design_plot_cropped <- orchard_plot(mod_results(
+  lnRR_design,
+  mod = "comparision_type",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(0.4,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-0.6, 0.6)) +
+  labs(x = "", y = "Effect Size (lnRR)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic",
+                              "No material\nVs. aromatic",
+                              "No material\nVs. Non-aromatic"))
+
+SMDH_design_plot_cropped <- orchard_plot(mod_results(
+  SMDH_design,
+  mod = "comparision_type",
+  group = "paper_ID"),
+  trunk.size = 0.5,
+  branch.size = 1.3,
+  twig.size = 0.5,
+  alpha = 0.4,
+  fill = T,
+  k.pos = c(1.9,0.6,0.6),
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  scale_y_continuous(limits = c(-2.3, 2.3)) +
+  labs(x = "", y = "Effect Size (SMDH)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position.inside = c(0.99, 0.01),
+        legend.justification = c(1, 0), 
+        legend.direction = "horizontal",
+        legend.background = element_blank(),
+        legend.key = element_blank(),
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)) + 
+  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic",
+                              "No material\nVs. aromatic", 
+                              "No material\nVs. non-Aromatic"))
+```
+
+```{r Sun Aug 31 19:54:26 2025, eval=FALSE}
+# Sun Aug 31 19:54:26 2025 ------------------------------
+# Save image file here
+```
+
+### Now we combine these plots
+
+```{r combining meta-regression plots, effect}
+## I am going to remove the y ticks from the SMDH plots to make it smaller..
+SMDH_design_plot <- SMDH_design_plot +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Combine using patchwork
+Figure_design_time_gnm_addition <- 
+  ((lnRR_design_plot + SMDH_design_plot) /
+     (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
+  plot_annotation(tag_levels = "A")
+print(Figure_design_time_gnm_addition)
+```
+
+```{r Figure_design_time_gnm_addition.png, eval=FALSE}
+## save image file
+ggsave(here::here("figures/Figure_design_time_gnm_addition.png"),
+       plot = Figure_design_time_gnm_addition, height = 240, width = 250, units = "mm", dpi = 600)
+```
+
+* Now the cropped figures for the main manuscript
+
+```{r SMDH_design_plot_cropped}
+## I am going to remove the y ticks from the SMDH plots to make it smaller..
+SMDH_design_plot_cropped <- SMDH_design_plot_cropped +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+SMDH_time_gnm_addition_plot_cropped <- SMDH_time_gnm_addition_plot_cropped +
+  theme(axis.text.y  = element_blank(),
+        axis.title.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+# Combine using patchwork
+Figure_design_time_gnm_addition_cropped <- 
+  ((lnRR_design_plot_cropped + SMDH_design_plot_cropped) /
+     (lnRR_time_gnm_addition_plot_cropped + SMDH_time_gnm_addition_plot_cropped)) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r Figure_design_time_gnm_addition_cropped.png, eval=FALSE}
+## save image file
+ggsave(here::here("figures/Figure_design_time_gnm_addition_cropped.png"), 
+       plot = Figure_design_time_gnm_addition_cropped, height = 240, width = 250, units = "mm",
+       dpi = 600)
+```
+
+## B. Combined Plot
+
+### Parasite Type
+
+```{r orchard plot parasite type meta-regression}
+# Loading models for SMDH and lnRR
+lnRR_parasite <- readRDS(here::here("model/lnRR_parasite.rds"))
+SMDH_parasite <- readRDS(here::here("model/SMDH_parasite.rds"))
+
+lnRR_parasite_plot <- orchard_plot(mod_results(
+  lnRR_parasite,
+  mod = "parasite_type",
+  group = "paper_ID"),
   trunk.size = 0.25,
@@
   alpha = 0.2,
-    xlab ="") +
- scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
   labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "bottom",
+       y = "lnRR") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position = "none",
         # legend.position.inside = c(0.98, 0.05),
@@
         axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("After egg laying", "Before egg laying", "Continous addition"))
-
-SMDH_time_gnm_addition_plot <-
-  orchard_plot(mod_results(
-      SMDH_time_gnm_addition,
-      mod = "time_of_gnm_addition",
-      group = "paper_ID"
-    ),
+        axis.text.y = element_text(size = 6,angle = 0, vjust = 0.5, hjust = 1))
+
+SMDH_parasite_plot <- orchard_plot(mod_results(
+  SMDH_parasite,
+  mod = "parasite_type",
+  group = "paper_ID"),
   trunk.size = 0.25,
@@
   alpha = 0.2,
-    xlab ="") +
- scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  xlab = "") +
+  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
+  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
   labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "bottom",
+       y = "SMD(H)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position = "none",
         # legend.position.inside = c(0.98, 0.05),
@@
         axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  )
-
-```
-
-## Experimental Design
-
-```{r orchard plot experimental design meta-regression}
-
+        axis.text.y = element_text(size = 6,angle = 0, vjust = 0.5, hjust = 1))
+```
+
+### Bird Species
+
+```{r orchard plot bird species meta-regression}
 # Loading models for SMDH and lnRR
-
-lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
-SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
-
-lnRR_design_plot <-
-  orchard_plot(mod_results(
-      lnRR_design,
-      mod = "comparision_type",
-      group = "paper_ID"
-    ),
+lnRR_birds <- readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds <- readRDS(here::here("model/SMDH_birds.rds"))
+
+lnRR_birds_plot <- orchard_plot(mod_results(
+  lnRR_birds,
+  mod = "bird_species",
+  group = "paper_ID"),
   trunk.size = 0.25,
@@
   alpha = 0.2,
-    xlab ="") +
- scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  xlab = "") +
+  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
+  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                "#F47A00", "#98C127","#003A7D","#7E4794")) +
   labs(x = "",
-       y = "lnRR")+
+       y = "lnRR") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+        legend.position = "none",
+        # legend.position.inside = c(0.98, 0.05),
+        # legend.justification = c(1, 0), 
+        # legend.direction = "horizontal",
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6),
+        axis.title = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 6,angle = 0, vjust = 0.5, hjust = 1))
+
+SMDH_birds_plot <- orchard_plot(mod_results(
+  SMDH_birds,
+  mod = "bird_species",
+  group = "paper_ID"),
+  trunk.size = 0.25,
+  branch.size = 1,
+  twig.size = 0.5,
+  alpha = 0.2,
+  xlab = "") +
+  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
+  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                "#F47A00", "#98C127","#003A7D","#7E4794")) +
+  labs(x = "",
+       y = "SMD(H)") +
   theme(
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
-  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))
-
-SMDH_design_plot <-
-  orchard_plot(mod_results(
-      SMDH_design,
-      mod = "comparision_type",
-      group = "paper_ID"
-    ),
+    axis.text.y = element_text(size = 6,angle = 0, vjust = 0.5, hjust = 1))
+```
+
+### Trait studied
+
+```{r orchard plot trait-studied meta-regression}
+# Loading models for SMDH and lnRR
+lnRR_trait <- readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait <- readRDS(here::here("model/SMDH_trait.rds"))
+
+lnRR_trait_plot <- orchard_plot(mod_results(
+  lnRR_trait,
+  mod = "trait_type",
+  group = "paper_ID"),
   trunk.size = 0.25,
@@
   alpha = 0.2,
-    xlab ="") +
- scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
+  xlab = "") +
+  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
+  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                "#F47A00", "#98C127","#003A7D","#7E4794")) +
   labs(x = "",
-       y = "SMD(H)")+
+       y = "lnRR") +
   theme(
@@
     axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
+    axis.text.y = element_text(size = 6,angle = 0, vjust = 0.5, hjust = 1)
   )
 
-```
-
-### Now we combine these plots
-
-```{r combining meta-regression plots, effect}
-
-## I am going to remove the y ticks from the SMDH plots to make it smaller..
-SMDH_design_plot <- SMDH_design_plot +
-  theme(axis.text.y  = element_blank(),
-        axis.title.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-SMDH_time_gnm_addition_plot <- SMDH_time_gnm_addition_plot +
-  theme(axis.text.y  = element_blank(),
-        axis.title.y = element_blank(),
-        axis.ticks.y = element_blank())
-
-# Combine using patchwork
-Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
-                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
-  plot_annotation(tag_levels = "A")
-
-ggsave(here::here("figures/Figure_design_time_gnm_addition.png"), plot = Figure_design_time_gnm_addition, height = 240, width = 250, units = "mm", dpi = 600)
-
-```
-
-# B. Combined Plot
-
-## Parasite Type
-
-```{r orchard plot parasite type meta-regression}
-
-# Loading models for SMDH and lnRR
-
-lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
-SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
-
-lnRR_parasite_plot <-
+SMDH_trait_plot <-
   orchard_plot(mod_results(
-      lnRR_parasite,
-      mod = "parasite_type",
-      group = "paper_ID"
-    ),
+    SMDH_trait,
+    mod = "trait_type",
+    group = "paper_ID"),
     trunk.size = 0.25,
@@
     alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
+    xlab = "") +
+  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                  "#F47A00", "#98C127","#003A7D","#7E4794")) +
+  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
+                                "#F47A00", "#98C127","#003A7D","#7E4794")) +
   labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+       y = "SMD(H)") +
+  theme(  panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
           legend.position = "none",
@@
           axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
-  )
-
-SMDH_parasite_plot <-
-  orchard_plot(mod_results(
-      SMDH_parasite,
-      mod = "parasite_type",
-      group = "paper_ID"
-    ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values = c("#FF8CAE", "#003A7D")) +
-  scale_fill_manual(values = c("#FF8CAE", "#003A7D")) +
-  labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
-  )
-
-```
-
-## Bird Species
-
-```{r orchard plot bird species meta-regression}
-
-# Loading models for SMDH and lnRR
-
-lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
-SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
-
-lnRR_birds_plot <-
-  orchard_plot(mod_results(
-      lnRR_birds,
-      mod = "bird_species",
-      group = "paper_ID"
-    ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
-  )
-
-SMDH_birds_plot <-
-  orchard_plot(mod_results(
-      SMDH_birds,
-      mod = "bird_species",
-      group = "paper_ID"
-    ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
-  )
-```
-
-## Trait studied
-
-```{r orchard plot trait-studied meta-regression}
-
-# Loading models for SMDH and lnRR
-
-lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
-SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
-
-lnRR_trait_plot <-
-  orchard_plot(mod_results(
-      lnRR_trait,
-      mod = "trait_type",
-      group = "paper_ID"
-    ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  labs(x = "",
-       y = "lnRR")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6,angle = 0, vjust = 0.5, hjust = 1)
-  )
-
-SMDH_trait_plot <-
-  orchard_plot(mod_results(
-      SMDH_trait,
-      mod = "trait_type",
-      group = "paper_ID"
-    ),
-    trunk.size = 0.25,
-    branch.size = 1,
-    twig.size = 0.5,
-    alpha = 0.2,
-    xlab ="") +
-  scale_colour_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  scale_fill_manual(values =  c("#00B0BE","#FFB255",  "#FF8CAE", 
-                                 "#F47A00", "#98C127","#003A7D","#7E4794")) +
-  labs(x = "",
-       y = "SMD(H)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
-    legend.position = "none",
-    # legend.position.inside = c(0.98, 0.05),
-    # legend.justification = c(1, 0), 
-    # legend.direction = "horizontal",
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6),
-    axis.title = element_text(size = 10),
-    axis.text.x = element_text(size = 10),
-    axis.text.y = element_text(size =6, angle = 0, vjust = 0.5, hjust = 1)
-  )
+          axis.text.y = element_text(size = 6, angle = 0, vjust = 0.5, hjust = 1))
 ```
@@
 ```{r combining meta-regression plots, no effect}
-
 ## I am going to remove the y ticks from the SMDH plots to make it smaller..
@@
 # Combine using patchwork
-Figure_parasite_birds_trait <- ((lnRR_parasite_plot + SMDH_parasite_plot) / 
+Figure_parasite_birds_trait <-
+  ((lnRR_parasite_plot + SMDH_parasite_plot) / 
      (lnRR_birds_plot + SMDH_birds_plot) / 
@@
   plot_annotation(tag_levels = "A")
-
-ggsave(here::here("figures/Figure_parasite_birds_trait.png"), plot = Figure_parasite_birds_trait, height = 250, width = 400, units = "mm", dpi = 600)
-
-```
-
-# Publication Bias Tests
+print(Figure_parasite_birds_trait)
+```
+
+```{r Figure_parasite_birds_trait.png, eval=FALSE}
+## save image file
+ggsave(here::here("figures/Figure_parasite_birds_trait.png"), 
+       plot = Figure_parasite_birds_trait, height = 250, width = 400, units = "mm", dpi = 600)
+
+```
+
+## Publication Bias Tests
 
 ```{r}
-
 ###---Small study Effects ----###
-
-lnRR_small_study<-readRDS(here::here("model/lnRR_small_study.rds"))
-SMDH_small_study<-readRDS(here::here("model/SMDH_small_study.rds"))
-
-lnRR_small_study_bubble<-orchaRd::bubble_plot(mod_results(lnRR_small_study,
-                     mod="sqrt_effective_n_inv",
-                     group="paper_ID",
-                     weights="prop"),
-                     group="paper_ID") +
-  scale_colour_manual(values ="mediumpurple4") +
+lnRR_small_study <- readRDS(here::here("model/lnRR_small_study.rds"))
+SMDH_small_study <- readRDS(here::here("model/SMDH_small_study.rds"))
+
+lnRR_small_study_bubble <- orchaRd::bubble_plot(mod_results(
+  lnRR_small_study,
+  mod = "sqrt_effective_n_inv",
+  group = "paper_ID",
+  weights = "prop"),
+  group = "paper_ID") +
+  scale_colour_manual(values = "mediumpurple4") +
   scale_fill_manual(values = "mediumpurple4") +
+  coord_cartesian(ylim = c(-2.5, 2.5)) +
   labs(y = "Effect size (lnRR)",
-       x = expression(sqrt(1 / N[effective])))+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+       x = expression(sqrt(1 / N[effective]))) +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
         legend.title = element_text(size = 10),
@@
 
-SMDH_small_study_bubble<-orchaRd::bubble_plot(mod_results(SMDH_small_study,
-                     mod="sqrt_effective_n_inv",
-                     group="paper_ID",
-                     weights="prop"),
-                     group="paper_ID") +
-  scale_colour_manual(values ="mediumpurple4") +
+SMDH_small_study_bubble <- orchaRd::bubble_plot(mod_results(
+  SMDH_small_study,
+  mod = "sqrt_effective_n_inv",
+  group = "paper_ID",
+  weights = "prop"),
+  group = "paper_ID") +
+  scale_colour_manual(values = "mediumpurple4") +
   scale_fill_manual(values = "mediumpurple4") +
+  coord_cartesian(ylim = c(-10, 7)) +
   labs(y = "Effect size (SMDH)",
-       x = expression(sqrt(1 / N[effective])))+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+       x = expression(sqrt(1 / N[effective]))) +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
         legend.title = element_text(size = 10),
@@
 
-lnRR_decline_eff<-readRDS(here::here("model/lnRR_decline_eff.rds"))
-SMDH_decline_eff<-readRDS(here::here("model/SMDH_decline_eff.rds"))
-
-lnRR_decline_eff_bubble<-orchaRd::bubble_plot(mod_results(lnRR_decline_eff,
-                     mod="year_MeanCenter",
-                     group="paper_ID",
-                     weights="prop"),
-                     group="paper_ID")+
-  scale_colour_manual(values ="#218833") +
+lnRR_decline_eff <- readRDS(here::here("model/lnRR_decline_eff.rds"))
+SMDH_decline_eff <- readRDS(here::here("model/SMDH_decline_eff.rds"))
+
+lnRR_decline_eff_bubble <- orchaRd::bubble_plot(mod_results(
+  lnRR_decline_eff,
+  mod = "year_MeanCenter",
+  group = "paper_ID",
+  weights = "prop"),
+  group = "paper_ID") +
+  scale_colour_manual(values = "#218833") +
   scale_fill_manual(values = "#218833") +
+  coord_cartesian(ylim = c(-2.5, 2.5)) +
   labs(y = "Effect size (lnRR)",
-       x = "Publication Year (Mean Cenetered)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+       x = "Publication Year (Mean Centered)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
         legend.title = element_text(size = 10),
@@
 
-SMDH_decline_effect_bubble<-orchaRd::bubble_plot(mod_results(SMDH_decline_eff,
-                     mod="year_MeanCenter",
-                     group="paper_ID",
-                     weights="prop"),
-                     group="paper_ID")+
-  scale_colour_manual(values ="#218833") +
+SMDH_decline_effect_bubble <- orchaRd::bubble_plot(mod_results(
+  SMDH_decline_eff,
+  mod = "year_MeanCenter",
+  group = "paper_ID",
+  weights = "prop"),
+  group = "paper_ID") +
+  scale_colour_manual(values = "#218833") +
   scale_fill_manual(values = "#218833") +
+  coord_cartesian(ylim = c(-10, 7)) +
   labs(y = "Effect size (SMDH)",
-       x = "Publication Year (Mean Cenetered)")+
-    theme(
-    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
+       x = "Publication Year (Mean Centered)") +
+  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
         legend.title = element_text(size = 10),
@@
 # Combine using patchwork
-Figure_publication_bias <- ((lnRR_small_study_bubble + SMDH_small_study_bubble) /
+Figure_publication_bias <-
+  ((lnRR_small_study_bubble + SMDH_small_study_bubble) /
      (lnRR_decline_eff_bubble + SMDH_decline_effect_bubble)) +
   plot_annotation(tag_levels = "A")
-
-ggsave(here::here("figures/Figure_publication_bias.png"), plot = Figure_publication_bias, height = 300, width = 400, units = "mm", dpi = 600)
-```
-
-# -------- TABLES ----------
+print(Figure_publication_bias)
+```
+
+```{r Figure_publication_bias.png, eval=FALSE}
+## save image file
+ggsave(here::here("figures/Figure_publication_bias.png"), 
+       plot = Figure_publication_bias, height = 300, width = 400, units = "mm", dpi = 600)
+```
+
+# ----- Supplementary Material Table -------
+
+```{r}
+#| label: excluded_proxy_table
+
+merged_data_extraction <- read_csv(here::here("data/03_data_cleaning/merged_data_extraction.csv"),
+                                   show_col_types = F)
+
+dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"),
+                             show_col_types = F)
+
+excluded_proxies <- merged_data_extraction %>%
+  filter(fulltext_screening == "included") %>%
+  filter(proxy_decision == "exclude") %>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion` = paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+SA_only_proxies <- dataset_analysis %>%
+  filter(proxy_decision == "sensitivity-analysis") %>%
+  select(paper_ID, fitness_proxy, proxy_comment) %>%
+  distinct() %>%
+  group_by(paper_ID) %>%
+  summarise(
+    `Number of proxies` = n(),
+    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
+    `Reason for Exclusion` = paste(proxy_comment,  collapse = "; "),
+    .groups = "drop")
+
+# Now binding them together
+combined_summary <- bind_rows(
+  excluded_proxies %>% mutate(Category = "Completely excluded"),
+  SA_only_proxies   %>% mutate(Category = "Sensitivity-analysis only")) %>%
+  arrange(Category, paper_ID)
+
+# Group by category
+excluded_proxies <- combined_summary %>%
+  gt() %>%
+  tab_header(
+    title = md("**Excluded Fitness Proxies**")) %>%
+  # define row-groups
+  tab_row_group(
+    group    = "Completely excluded",
+    rows     = Category == "Completely excluded") %>%
+  tab_row_group(
+    group    = "Sensitivity-analysis only",
+    rows     = Category == "Sensitivity-analysis only") %>%
+  # hide the helper column
+  cols_hide("Category") %>%
+  # relabel columns
+  cols_label(
+    `paper_ID`             = "Paper ID",
+    `Number of proxies`    = "Noumber\nof Proxies",
+    `Excluded Proxies`     = "Excluded\nProxies",
+    `Reason for Exclusion` = "Reason for Exclusion") %>%
+  fmt_markdown(columns = c(`Excluded Proxies`, `Reason for Exclusion`)) %>%
+  opt_align_table_header(align = "left") %>%
+  cols_align(align   = "left",
+             columns = everything()) %>%
+  tab_options(
+    table.width               = pct(90),
+    row.striping.background_color = "#F7F7F7")
+print(excluded_proxies)
+```
+
+```{r excluded_proxies_table.pdf, eval=FALSE}
+## save image file
+gtsave(data = excluded_proxies,
+       filename = here::here("/tables/excluded_proxies_table.pdf"),
+       expand = 10)   # adds a little padding around the table
+```
 
@@
 
-pacman::p_load(gt,dplyr,metafor)
+# Loading the models including only published data
+SA_lnRR_published <- readRDS(here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
+SA_SMDH_published <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))
+
+# Loading the models without Comparison Type 3
+SA_lnRR_no_comp3 <- readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
+SA_SMDH_no_comp3 <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))
 
 # Loading the models including flagged proxies
-SA_lnRR_flagged<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
-SA_SMDH_flagged<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))
+SA_lnRR_flagged <- readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged.rds"))
+SA_SMDH_flagged <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged.rds"))
 
 # Loading the models without data for those using 0 as ES because authors reported no effect
-SA_lnRR_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
-SA_SMDH_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))
+SA_lnRR_no_missingES <- readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_missingES.rds"))
+SA_SMDH_no_missingES <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_missingES.rds"))
 
 # Loading the models without data for those using 0 as ES because authors reported no effect and including flagged proxies
-SA_lnRR_flagged_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
-SA_SMDH_flagged_no_missingES<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
+SA_lnRR_flagged_no_missingES <-
+  readRDS(here::here("model/sensitivity_analysis/SA_lnRR_flagged_no_missingES.rds"))
+SA_SMDH_flagged_no_missingES <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_flagged_no_missingES.rds"))
 
 # Loading the model for SMDH without inferential statistics. There is none for lnRR because we can only uses means and deviation to estimate lnRR
-SA_SMDH_no_inferential<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+SA_SMDH_no_inferential <- readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_inferential.rds"))
+
+# Loading the model for Geary's Test Passed. There is none for SMDH because we do not know the guideline for SMDH and Geary's Test
+SA_lnRR_geary_passed <- readRDS(here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))
 
 # Now let's build the table
-
 SA_intercept_only <- tibble::tibble(
-  effect_size = c("lnRR","lnRR","lnRR","SMDH","SMDH","SMDH","SMDH"),
-  data_used = c("Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),
-
-  Estimate = c(SA_lnRR_flagged$b[1],
+  effect_size = c("lnRR","lnRR","lnRR","lnRR","lnRR","lnRR",
+                  "SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMDH"),
+  data_used = c(
+    "Including published data only",
+    "Excluding Experimental Design Non-Aromatic Vs. No added material",
+    "Including flagged proxies", 
+    "Without those cases where author reported no effect of the treatment",
+    "Including flagged proxies and without the cases with no effect of the treatment", 
+    "Excluding effect sizes where lnRR failed Geary's Test",
+    "Including published data only",
+    "Excluding Experimental Design Non-Aromatic Vs. No added material",
+    "Including flagged proxies",
+    "Without those cases where author reported no effect of the treatment",
+    "Including flagged proxies and without the cases with no effect of the treatment",
+    "Without the cases where SMDH was calculated from inferential statistics"),
+
+  Estimate = c(SA_lnRR_published$b[1],
+               SA_lnRR_no_comp3$b[1],
+               SA_lnRR_flagged$b[1],
                SA_lnRR_no_missingES$b[1],
                SA_lnRR_flagged_no_missingES$b[1],
+               SA_lnRR_geary_passed$b[1],
+               SA_SMDH_published$b[1],
+               SA_SMDH_no_comp3$b[1],
                SA_SMDH_flagged$b[1],
@@
 
-  Q_value = c(SA_lnRR_flagged$QE,
+  Q_value = c(SA_lnRR_published$QE,
+              SA_lnRR_no_comp3$QE,
+              SA_lnRR_flagged$QE,
               SA_lnRR_no_missingES$QE,
               SA_lnRR_flagged_no_missingES$QE,
+              SA_lnRR_geary_passed$QE,
+              SA_SMDH_published$QE,
+              SA_SMDH_no_comp3$QE,
               SA_SMDH_flagged$QE,
@@
 
-  k_effect_sizes = c(SA_lnRR_flagged$k,
+  k_effect_sizes = c(SA_lnRR_published$k,
+                     SA_lnRR_no_comp3$k,
+                     SA_lnRR_flagged$k,
                      SA_lnRR_no_missingES$k,
                      SA_lnRR_flagged_no_missingES$k,
+                     SA_lnRR_geary_passed$k,
+                     SA_SMDH_published$k,
+                     SA_SMDH_no_comp3$k,
                      SA_SMDH_flagged$k,
@@
 
-  n_studies = c(length(SA_lnRR_flagged$s.levels.f[[1]]),
+  n_studies = c(length(SA_lnRR_published$s.levels.f[[1]]),
+                length(SA_lnRR_no_comp3$s.levels.f[[1]]),
+                length(SA_lnRR_flagged$s.levels.f[[1]]),
                 length(SA_lnRR_no_missingES$s.levels.f[[1]]),
                 length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
+                length(SA_lnRR_geary_passed$s.levels.f[[1]]),
+                length(SA_SMDH_published$s.levels.f[[1]]),
+                length(SA_SMDH_no_comp3$s.levels.f[[1]]),
                 length(SA_SMDH_flagged$s.levels.f[[1]]),
@@
                 length(SA_SMDH_flagged_no_missingES$s.levels.f[[1]]),
-                      length(SA_SMDH_no_inferential$s.levels.f[[1]])
-))
+                length(SA_SMDH_no_inferential$s.levels.f[[1]])))
 
@@
     P_value,
-    Q_value,
     k_effect_sizes,
-    n_studies
-  )
+    n_studies)
 
 # Let's make this table pretty
-SA_intercept_only<-SA_intercept_only%>%
-  gt()%>%
+SA_intercept_only <- SA_intercept_only %>%
+  gt() %>%
   tab_options(
@@
   tab_header(
-    title = md("**Summary of Sensitivity Analyses for lnRR and SMDH Intercept-only models**")
-  ) %>%
+    title = md("**Summary of Sensitivity Analyses for lnRR and SMD(H) Intercept-only models**")) %>%
   cols_label(
@@
   opt_table_outline()
-
-#saving as a docx file
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
-gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
-```
-
-## Table: Output from meta-regressions
+```
+
+```{r SA_intercept_only, eval=FALSE}
+## Saving as an image
+gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.png"))
+
+## For saving as a docx file
+gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.docx"))
+gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.html"))
+```
+
+```{r Table for lnRR rho sensitivity analysis, eval=FALSE}
+# Sun Aug 31 20:11:12 2025 ------------------------------
+# Make code execuatable, but eval = FALSE
+t4 <- data.frame(
+  rho  = rho_range,
+  "overall effect"  = sapply(lnRR_VCV_range, function(x) coef(x)),
+  "standard error" = sapply(lnRR_VCV_range, function(x) x$se),
+  "p-value" = sapply(lnRR_VCV_range, function(x) x$pval),
+  "Lower CI" = sapply(lnRR_VCV_range, function(x) x$ci.lb),
+  "Upper CI" = sapply(lnRR_VCV_range, function(x) x$ci.ub),
+  "Log-likehood" = sapply(lnRR_VCV_range, function(x) fitstats(x)[1,1]),
+  "AIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[3,1]),
+  "BIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[4,1]),
+  "AICc" = sapply(lnRR_VCV_range, function(x) fitstats(x)[5,1]))
+
+colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)",
+                  "Standard error", "p-value", "Lower CI", 
+                  "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
+
+t4 %>% dfround(4) %>% 
+  DT::datatable()
+```
+
+## Table: RoB Meta-regressions
 
 ```{r}
-
-pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
-
-# Loading models for experimental design
-lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
-SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))
-
-# Loading models for parasite type
-lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
-SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))
-
-# Loading models for time of green nest material addition
-lnRR_time_gnm_addition<-readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
-SMDH_time_gnm_addition<-readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
-
-# Loading models for the type of trait studied
-lnRR_trait<-readRDS(here::here("model/lnRR_trait.rds"))
-SMDH_trait<-readRDS(here::here("model/SMDH_trait.rds"))
-
-# Loading models for the bird species studied
-lnRR_birds<-readRDS(here::here("model/lnRR_birds.rds"))
-SMDH_birds<-readRDS(here::here("model/SMDH_birds.rds"))
+# Loading models for blinding performed or not
+lnRR_blinding <- readRDS(here::here("model/lnRR_blinding.rds"))
+SMDH_blinding <- readRDS(here::here("model/SMDH_blinding.rds"))
+
+# Loading models for random sampling assignment performed or not
+lnRR_random_assignment <- readRDS(here::here("model/lnRR_random_assignment.rds"))
+SMDH_random_assignment <- readRDS(here::here("model/SMDH_random_assignment.rds"))
+
+# Loading models for missing data present or not
+lnRR_missing_data <- readRDS(here::here("model/lnRR_missing_data.rds"))
+SMDH_missing_data <- readRDS(here::here("model/SMDH_missing_data.rds"))
 ```
@@
 ```{r}
-
 # Let's source our custom function to extract values from the meta-regressions
@@
 ## For lnRR Values
-lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type")%>%
-  bind_rows(extractor_metareg(lnRR_birds,"bird_species"))%>%
-  bind_rows(extractor_metareg(lnRR_trait,"trait_type"))%>%
-  bind_rows(extractor_metareg(lnRR_design,"comparision_type"))%>%
-  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition"))%>%
+lnRR_results_RoB <- extractor_metareg(lnRR_blinding,"blinding") %>%
+  bind_rows(extractor_metareg(lnRR_random_assignment,"random_assignment")) %>%
+  bind_rows(extractor_metareg(lnRR_missing_data,"missing_data")) %>%
   mutate(effect_size = "lnRR")
@@
 ## For SMDH Values
-SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type")%>%
-  bind_rows(extractor_metareg(SMDH_birds,"bird_species"))%>%
-  bind_rows(extractor_metareg(SMDH_trait,"trait_type"))%>%
-  bind_rows(extractor_metareg(SMDH_design,"comparision_type"))%>%
-  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition"))%>%
+SMDH_results_RoB <- extractor_metareg(SMDH_blinding,"blinding") %>%
+  bind_rows(extractor_metareg(SMDH_random_assignment,"random_assignment")) %>%
+  bind_rows(extractor_metareg(SMDH_missing_data,"missing_data")) %>%
   mutate(effect_size = "SMDH")
@@
 # Combine both results
-combined_results <- bind_rows(lnRR_results, SMDH_results)%>%
+combined_results_RoB <- bind_rows(lnRR_results_RoB, SMDH_results_RoB) %>%
   pivot_wider(
@@
     names_glue = "{.value}_{effect_size}"
-  )%>% # Prepare row labels to mimic grouping
-  arrange(moderator, level)%>%
+  ) %>% # Prepare row labels to mimic grouping
+  arrange(moderator, level) %>%
   mutate(row_type = "level")
 
-# Create moderator header rows for heterogeneity metrics
-  moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
-  select(moderator, effect_size, Q, Q_pval, R2_marginal) %>%
-    distinct()%>%
-    pivot_wider(
-      names_from = effect_size,
-      values_from = c(Q, Q_pval, R2_marginal),
-      names_glue = "{.value}_{effect_size}"
-    )%>%
-  mutate(level = "Heterogeneity ",
-         row_type = "moderator")
-
 # Final combined table with headers and levels
-combined_results <- bind_rows(moderator_header, combined_results) %>%
-  arrange(moderator, row_type)%>% select(-row_type)%>%
-  relocate(level, .after = moderator)%>%
-  mutate(moderator=case_when(moderator=="parasite_type"~"Parasite Type",
-                             moderator=="bird_species"~"Bird Species",
-                             moderator=="trait_type"~"Trait Type Category",
-                             moderator=="comparision_type"~"Experimental Design",
-                             moderator=="time_of_gnm_addition"~"Time of Green Nest Material Addition"))%>%
-  mutate(level = case_when(level==1 ~ "Non-aromatic vs. Aromatic",
-                           level==2 ~ "No added material vs. Aromatic",
-                           level==3 ~ "No added material vs. Non-aromatic",
-                           level=="a" ~ "After egg hatching",
-                           level=="b" ~ "Before egg hatching",
-                           level=="c" ~ "Continously through nesting phase",
-                           level=="Parasitic_and_pathogenic"~"Parasitic and Pathogen Related", .default=level))
-
-# Optional: clean up or reorder columns for display
+combined_results_RoB <- combined_results_RoB %>%
+  # bind_rows(moderator_header ,combined_results) %>%
+  arrange(moderator, row_type) %>% select(-row_type) %>%
+  relocate(level, .after = moderator) %>%
+  mutate(moderator = case_when(
+    moderator == "blinding" ~ "1. Blinding",
+    moderator == "random_assignment" ~ "2. Random assignment to treatment",
+    moderator == "missing_data" ~ "3. Partial Reporting"
+  )) %>%
+  mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Blinding",
+      "2. Random assignment to treatment",
+      "3. Partial Reporting"
+    ))) %>%
+  arrange(moderator) %>%
+  mutate(level = case_when(
+    level == "y" ~ "Yes",
+    level == "n" ~ "No",
+    .default = level))
+
+# Clean up or reorder columns for display
 # Select and order columns for clarity
-MLMR_table <- combined_results %>%
+RoB_table <- combined_results_RoB %>%
   gt(groupname_col = "moderator") %>%
-  tab_header(title = md("**Multilevel Meta-analytic Models for Exploratory Analyses**")) %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Risk of Bias**")) %>%
   cols_label(
-    Q_lnRR = "Q",
-    Q_pval_lnRR = "Q p-val",
-    R2_marginal_lnRR = "R²_mar",
-    Q_SMDH = "Q",
-    Q_pval_SMDH = "Q p-val",
-    R2_marginal_SMDH = "R²_mar",
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
     level = "Level",
@@
     k_SMDH = "k",
-    n_SMDH = "n"
-  ) %>%
+    n_SMDH = "n") %>%
   sub_missing(
     columns = everything(),
-    missing_text = ""
-  ) %>%
+    missing_text = "") %>%
+  opt_table_outline() %>%
+  tab_options(
+    table.font.size = "small",
+    heading.title.font.size = 12,
+    table.border.top.width = px(2),
+    column_labels.font.weight = "medium",
+    row_group.font.weight = "bold") %>%
+  tab_style(
+    style = cell_borders(
+      sides = "bottom",
+      color = "black",
+      weight = px(1)),
+    locations = cells_body()) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_lnRR),
+      rows = p_value_lnRR < 0.05)) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = cells_body(
+      columns = c(p_value_SMDH),
+      rows = p_value_SMDH < 0.05)) %>%
+  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH)))
+```
+
+```{r, eval=FALSE}
+# saving the image
+gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))
+
+# saving as a docx file or html
+gtsave(RoB_table,here::here("tables/SA_RoB_table.docx"))
+gtsave(RoB_table,here::here("tables/SA_RoB_table.html"))
+```
+
+# -------- TABLES ----------
+
+## Table: Output from meta-regressions
+
+```{r}
+# Loading models for experimental design
+lnRR_design <- readRDS(here::here("model/lnRR_design.rds"))
+SMDH_design <- readRDS(here::here("model/SMDH_design.rds"))
+
+# Loading models for parasite type
+lnRR_parasite <- readRDS(here::here("model/lnRR_parasite.rds"))
+SMDH_parasite <- readRDS(here::here("model/SMDH_parasite.rds"))
+
+# Loading models for time of green nest material addition
+lnRR_time_gnm_addition <- readRDS(here::here("model/lnRR_time_gnm_addition.rds"))
+SMDH_time_gnm_addition <- readRDS(here::here("model/SMDH_time_gnm_addition.rds"))
+
+# Loading models for the type of trait studied
+lnRR_trait <- readRDS(here::here("model/lnRR_trait.rds"))
+SMDH_trait <- readRDS(here::here("model/SMDH_trait.rds"))
+
+# Loading models for the bird species studied
+lnRR_birds <- readRDS(here::here("model/lnRR_birds.rds"))
+SMDH_birds <- readRDS(here::here("model/SMDH_birds.rds"))
+```
+
+```{r}
+# Let's source our custom function to extract values from the meta-regressions
+source(here::here("functions/extractor_metareg.R"))
+
+## For lnRR Values
+lnRR_results <- extractor_metareg(lnRR_parasite,"parasite_type") %>%
+  bind_rows(extractor_metareg(lnRR_birds,"bird_species")) %>%
+  bind_rows(extractor_metareg(lnRR_trait,"trait_type")) %>%
+  bind_rows(extractor_metareg(lnRR_design,"comparision_type")) %>%
+  bind_rows(extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition")) %>%
+  mutate(effect_size = "lnRR")
+
+## For SMDH Values
+SMDH_results <- extractor_metareg(SMDH_parasite,"parasite_type") %>%
+  bind_rows(extractor_metareg(SMDH_birds,"bird_species")) %>%
+  bind_rows(extractor_metareg(SMDH_trait,"trait_type")) %>%
+  bind_rows(extractor_metareg(SMDH_design,"comparision_type")) %>%
+  bind_rows(extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition")) %>%
+  mutate(effect_size = "SMDH")
+
+## Now let's write the table for publication:
+# Combine both results
+combined_results <- bind_rows(lnRR_results, SMDH_results) %>%
+  pivot_wider(
+    id_cols = c(moderator, level),
+    names_from = effect_size,
+    values_from = c(estimate, p_value, CI, PI, k, n),
+    names_glue = "{.value}_{effect_size}"
+  ) %>% # Prepare row labels to mimic grouping
+  arrange(moderator, level) %>%
+  mutate(row_type = "level")
+
+# # Create moderator header rows for heterogeneity metrics
+#   moderator_header<-bind_rows(lnRR_results, SMDH_results) %>%
+#   select(moderator, effect_size, R2_marginal) %>%
+#     distinct() %>%
+#     pivot_wider(
+#       names_from = effect_size,
+#       values_from = c( R2_marginal),
+#       names_glue = "{.value}_{effect_size}"
+#     ) %>%
+#   mutate(level = "Heterogeneity ",
+#          row_type = "moderator")
+
+# Final combined table with headers and levels
+combined_results <- combined_results %>%
+  # bind_rows(moderator_header ,combined_results) %>%
+  arrange(moderator, row_type) %>% select(-row_type) %>%
+  relocate(level, .after = moderator) %>%
+  mutate(moderator = case_when(
+    moderator == "parasite_type" ~ "5. Parasite\nType",
+    moderator == "bird_species" ~ "3. Bird\nSpecies",
+    moderator == "trait_type" ~ "4. Trait\nCategory",
+    moderator == "comparision_type" ~ "1. Experimental\nDesign",
+    moderator == "time_of_gnm_addition" ~ "2. Time of\nGNM Addition"
+  )) %>%
+  mutate(moderator = factor(
+    moderator,
+    levels = c(
+      "1. Experimental\nDesign",
+      "2. Time of\nGNM Addition",
+      "3. Bird\nSpecies",
+      "4. Trait\nCategory",
+      "5. Parasite\nType"
+    ))) %>%
+  arrange(moderator) %>%
+  mutate(level = case_when(
+    level==1 ~ "Non-aromatic\nvs. Aromatic",
+    level==2 ~ "No added material\nvs. Aromatic",
+    level==3 ~ "No added material\nvs. Non-aromatic",
+    level=="a" ~ "After egg\nhatching",
+    level=="b" ~ "Before egg\nhatching",
+    level=="c" ~ "Continously through\nnesting phase",
+    level=="Parasitic_and_pathogenic"~"Parasitic and\nPathogen Related", 
+    .default = level))
+
+# Optional: clean up or reorder columns for display
+# Select and order columns for clarity
+MLMR_table <- combined_results %>%
+  gt(groupname_col = "moderator") %>%
+  tab_header(title = md("**Multilevel Meta Regressions for Exploratory Analyses**")) %>%
+  cols_label(
+    # R2_marginal_lnRR = "R²_mar",
+    # R2_marginal_SMDH = "R²_mar",
+    level = "Level",
+    estimate_lnRR = "Estimate",
+    CI_lnRR = "95% CI",
+    PI_lnRR = "95% PI",
+    p_value_lnRR = "P-val",
+    k_lnRR = "k",
+    n_lnRR = "n",
+    estimate_SMDH = "Estimate",
+    CI_SMDH = "95% CI",
+    PI_SMDH = "95% PI",
+    p_value_SMDH = "P-val",
+    k_SMDH = "k",
+    n_SMDH = "n") %>%
+  sub_missing(
+    columns = everything(),
+    missing_text = "") %>%
   opt_table_outline() %>%
@@
       color = "black",
-      weight = px(1)
-    ),
-    locations = cells_body()
-  ) %>%
-  tab_style(
-    style = cell_text(weight = "bold"),
-    locations = cells_body(
-      rows = level == "Heterogeneity"
-    ))%>%
+      weight = px(1)),
+    locations = cells_body()) %>%
+  # tab_style(
+  #   style = cell_text(weight = "bold"),
+  #   locations = cells_body(
+  #     rows = level == "Heterogeneity"
+  #   )) %>%
   tab_style(
@@
       columns = c(p_value_lnRR),
-      rows = p_value_lnRR < 0.05
-    )
-  ) %>%
+      rows = p_value_lnRR < 0.05)) %>%
   tab_style(
@@
       columns = c(p_value_SMDH),
-      rows = p_value_SMDH < 0.05
-    )
-  )%>%
+      rows = p_value_SMDH < 0.05)) %>%
   tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
-  tab_spanner(label = "SMDH", columns = contains("_SMDH"))
-
-#saving as a docx file
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.docx"))
-gtsave(MLMR_table,here::here("tables/EA_MLMR_table.html"))
-```
+  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
+  tab_style(
+    style = cell_text(whitespace = "nowrap"),
+    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH)))
+```
+
+```{r, eval=FALSE}
+## saving the image
+gtsave(MLMR_table, here::here("tables/MLMR_table.png"))
+## saving as a docx file or html
+gtsave(MLMR_table,here::here("tables/MLMR_table.docx"))
+gtsave(MLMR_table,here::here("tables/MLMR_table.html"))
+```
+
+## Session info
+
+```{r}
+sessionInfo()
+```

### 2025-10-26 code/06_data_preparation.Rmd
Prisma checklist and diagram added, changes to figure code added more tables for supplementary material , updated reviewed code from MO and added proceedings csl file for bibliography.

@@
 ---
+## Preface
 
-We have merged the data from different sources after data extraction, cleaned the typos and made it more usable.
+In this script we will continue to prepare our dataset for use in meta-analysis and calculate variables for effect size estimation (SMDH, lnRR). 
+In the previous script [05_data_cleaning.Rmd](https://github.com/shreyadimri/Green_Nest_Material/blob/main/code/05_data_cleaning.Rmd) we merged the data from different sources after data extraction, and performed several data cleaning procedures, including the standardization of terms.
 We have excluded the articles that did not pass full-text screening and the fitness proxies that we could not find a direction for the effect.
-These are steps done in the script **05_data_cleaning.Rmd** that generates the file **dataset_after_cleaning.csv**
-
-In this script we will continue to prepare our dataset for use in meta-analysis, calculates variables for effect size estimation (SMDH, lnRR).
+The resulting data were saved as [dataset_after_cleaning.csv](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/03_data_cleaning/dataset_after_cleaning.csv)
 
@@
 
-data/03_data_cleaning/dataset_after_cleaning.csv
+[data/03_data_cleaning/dataset_after_cleaning.csv](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/03_data_cleaning/dataset_after_cleaning.csv)
 
@@
 
-```{r setup, warning=FALSE, message=FALSE, echo=F}
+* Install and load required packages
 
-# Setting up workspace
+```{r setup, warning=FALSE, message=FALSE}
+## Setting up workspace using pacman
 if (!requireNamespace("pacman", quietly = TRUE)) {
@@
 }
-pacman::p_load(here, tidyverse, dplyr, stringr, metafor, orchaRd,ggpubr,ggrepel) #Packages needed
 
-rm(list=ls()) ## cleaning up
+## installing orchaRd from GitHub
+if (!requireNamespace("orchaRd", quietly = TRUE)) {
+## installing orchaRd from GitHub
+pacman::p_install_gh("daniel1noble/orchaRd", ref = 'main')
+}
 
-set.seed(8341) #set seed for reproducibility (for random number generation)
+## Install/load required packages
+pacman::p_load(
+  here,
+  tidyverse,
+  metafor,
+  orchaRd,
+  ggpubr)
+```
+
+* Load cleaned dataset [dataset_after_cleaning.csv](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/03_data_cleaning/dataset_after_cleaning.csv)
+
+```{r load cleaned data}
+# set seed for reproducibility (for random number generation)
+set.seed(8341)
 
 # Loading cleaned dataset
-
 dataset_after_cleaning <- read_csv(here::here("data/03_data_cleaning/dataset_after_cleaning.csv"))
 
-## Now all the changes we make to the file.. we will store them in data_analysis
-
-dataset_analysis<-dataset_after_cleaning
+## create working copy to store changes
+dataset_analysis <- dataset_after_cleaning
 ```
 
-#### Loading functions
+#### Custom functions
 
-Some functions we will need in this manuscript.. sourced mainly from Nakagawa 2022 : Online tutorial <https://alistairmcnairsenior.github.io/Miss_SD_Sim/>
+For the presented analyses, several functions are defined, most of them defined in [Nakagawa, Noble, Lagisz, Spake, Viechtbauer, & Senior (2023)](https://doi.org/10.1111/ele.14144) and the accompanying online supplement <https://alistairmcnairsenior.github.io/Miss_SD_Sim/>
 
-```{r}
-
-# Function to calculate Geary's "number"
+```{r define custom functions}
+## Function to calculate Geary's "number"
 geary <- function(mean, sd, n){
@@
 
-# Shinichi Nakagawa, Daniel W.
-A.
-Noble, Malgorzata Lagisz, Rebecca Spake, Wolfgang Viechtbauer and Alistair M.
-Senior.
-2022.
-A robust and readily implementable method for the meta-analysis of response ratios with and without missing standard deviations.
-Ecology Letters, DOI: 10.1111/ele.14144
+## Functions provided in the workalong
+cv_avg <- function(x, sd, n, group, data, label = NULL, sub_b = TRUE, cv2 = FALSE) {
 
-  # Functions provided in the workalong
-cv_avg <- function(x, sd, n, group, data, label = NULL, sub_b = TRUE, cv2=FALSE){
-
-  # Check if the name is specified or not.
-If not, then assign it the name of the mean, x, variable input in the function.
-https://stackoverflow.com/questions/60644445/converting-tidyeval-arguments-to-string
-  if(is.null(label)){
+## Check if the name is specified or not. If not, then assign it the name of the mean, x,
+## variable input in the function.
+##  https://stackoverflow.com/questions/60644445/converting-tidyeval-arguments-to-string
+  if (is.null(label)) {
     label <- purrr::map_chr(enquos(x), rlang::as_label)
@@
 
-  # Calculate between study CV. Take weighted mean CV within study, and then take a weighted mean across studies of the within study CV. Weighted based on sample size and pooled sample size.
+  ## Calculate between study CV. 
+  ## Take weighted mean CV within study, and then take a weighted mean across studies 
+  ## of the within study CV. Weighted based on sample size and pooled sample size.
   b_grp_cv_data <- data %>%
     dplyr::group_by({{group}}) %>%
-    dplyr::mutate(   w_CV2 = weighted_CV({{sd}}, {{x}}, {{n}}, cv2=cv2),
+    dplyr::mutate(   w_CV2 = weighted_CV({{sd}}, {{x}}, {{n}}, cv2 = cv2),
                      n_mean = mean({{n}}, na.rm = TRUE)) %>%
@@
 
-  # Make sure that label of the calculated columns is distinct from any other columns
+  ## Make sure that label of the calculated columns is distinct from any other columns
   names(b_grp_cv_data) <- paste0(names(b_grp_cv_data), "_", label)
 
-  # Append these calculated columns back to the original data and return the full dataset.
+  ## Append these calculated columns back to the original data and return the full dataset.
   if(sub_b){
-    b_grp_cv_data <- b_grp_cv_data %>% dplyr::select(grep("b_", names(b_grp_cv_data)))
+    b_grp_cv_data <- b_grp_cv_data %>%
+      dplyr::select(grep("b_", names(b_grp_cv_data)))
     dat_new <- cbind(data, b_grp_cv_data)
@@
 
-# You also need the helper function
-
-weighted_CV <- function(sd, x, n, cv2=FALSE){
-  if(cv2){
+## You also need the helper function
+weighted_CV <- function(sd, x, n, cv2 = FALSE) {
+  if(cv2) {
     weighted.mean(na_if((sd / x)^2, Inf), n, na.rm = TRUE)
-  }else{
+  } else {
     weighted.mean(na_if((sd / x), Inf), n, na.rm = TRUE)^2
@@
 #'
-lnrr_laj <- function(m1, m2, cv1_2, cv2_2, n1, n2, taylor=TRUE){
-  if(taylor){
+lnrr_laj <- function(m1, m2, cv1_2, cv2_2, n1, n2, taylor = TRUE) {
+  if(taylor) {
     log(m1 / m2) + 0.5*((cv1_2 / n1) - (cv2_2 / n2))
@@
 #' @param taylor A logical indicating whether to calculate point estimate with Taylor expansion.
-v_lnrr_laj <- function(cv1_2, cv2_2, n1, n2,  taylor=TRUE){
+v_lnrr_laj <- function(cv1_2, cv2_2, n1, n2,  taylor = TRUE) {
   if(taylor){
@@
 }
-
 ```
 
-# Preparing Random Effects
+## Preparing Random Effects
 
@@
 
-"(1) paper_ID, which encompasses estimates extracted from the same primary study,
+* (1) paper_ID, which encompasses estimates extracted from the same primary study,
 
-(2) experiment_ID,
+* (2) experiment_ID,
 
-(3) group_ID
+* (3) group_ID
 
-(4) repeated_traits_ID, and
+* (4) repeated_traits_ID, and
 
-(5) observation_ID which corresponds to a unit-level observation identity and models within-study variance
+* (5) observation_ID which corresponds to a unit-level observation identity and models within-study variance
 
@@
 
--   We also need to add `observation ID` which is the unit-level identity (unique for each row) for within-study variance.
+* We also need to add `observation ID` which is the unit-level identity (unique for each row) for within-study variance.
 
--   In the way we extracted this information, each paper_ID needs to be added to the random effect level of `experiment_ID`, `group_ID` and `repeated_trait_ID` to make sure they are unique values.
+* In the way we extracted this information, each paper_ID needs to be added to the random effect level of `experiment_ID`, `group_ID` and `repeated_trait_ID` to make sure they are unique values.
 
 ```{r Prepare Random Effects as Unique ID}
-
-dataset_analysis<-dataset_analysis%>%
-
-  mutate(Observation_ID = as.factor(row_number()))%>%
-
-  mutate(experiment_ID_coded = as.factor(paste(paper_ID, experiment_ID, sep="_")),.after=experiment_ID)%>%
-  mutate(group_ID_coded = as.factor(paste(paper_ID, group_ID, sep="_")),.after=group_ID)%>%
-  mutate(repeated_trait_ID_coded = as.factor(paste(paper_ID,repeated_trait_ID, sep="_")),.after=repeated_trait_ID)
+dataset_analysis <- dataset_analysis %>%
+  mutate(Observation_ID = as.factor(row_number())) %>%
+  mutate(experiment_ID_coded = as.factor(paste(paper_ID, experiment_ID, sep="_")),
+         .after = experiment_ID) %>%
+  mutate(group_ID_coded = as.factor(paste(paper_ID, group_ID, sep="_")),
+         .after = group_ID) %>%
+  mutate(repeated_trait_ID_coded = as.factor(paste(paper_ID,repeated_trait_ID, sep="_")),
+         .after = repeated_trait_ID)
 
 # random_effects_check<-dataset_analysis%>%select(paper_ID,experiment_ID,group_ID,repeated_trait_ID, experiment_ID_coded,group_ID_coded, repeated_trait_ID_coded)
-
 ```
 
--   We also decided to add `population ID` since we noticed several studies were performed in the same geographical location.
+* We also decided to add `population ID` since we noticed several studies were performed in the same geographical location.
 
-```{r}
-dataset_analysis<-dataset_analysis%>%
+```{r cleaning location names}
+dataset_analysis <- dataset_analysis %>%
   mutate(population_ID = as.factor(population_location))
 
-# Let's look at the nammes of the locations
+# Let's look at the names of the locations
 # unique(dataset_analysis$population_ID)
-
 # There are clearly many repeated names, let's clean this up a bit
-
 dataset_analysis <- dataset_analysis %>%
@@
   )
-
 ```
 
-# Effective Sample Size Calculation
+## Effective Sample Size Calculation
 
@@
 ```{r effective sample size}
-
-dataset_analysis<-dataset_analysis%>%
-  mutate(effective_n_experiment=(n_experiment/shared_experiment),.after=n_experiment)%>%
-  mutate(effective_n_control=(n_control/shared_control),.after=n_control)
+dataset_analysis <- dataset_analysis %>%
+  mutate(effective_n_experiment = (n_experiment/shared_experiment), .after = n_experiment) %>%
+  mutate(effective_n_control = (n_control/shared_control),.after = n_control)
 ```
@@
 ```{r}
-dataset_analysis%>%
-  summarise(control_min=min(effective_n_control,na.rm=T),
-            control_max=max(effective_n_control,na.rm=T),
+dataset_analysis %>%
+  summarise(control_min = min(effective_n_control, na.rm = T),
+            control_max = max(effective_n_control, na.rm = T),
             na_control = sum(is.na(effective_n_control)),
-            experiment_min=min(effective_n_experiment,na.rm=T),
-            experiment_max=max(effective_n_experiment,na.rm=T),
+            experiment_min = min(effective_n_experiment, na.rm = T),
+            experiment_max = max(effective_n_experiment, na.rm = T),
             na_experiment = sum(is.na(effective_n_experiment)))
@@
 
-We have some NA and some values of effective sample size 1 and below.. lets see where this is
+We have some NA and some values of effective sample size 1 and below lets see where this is
 
-```{r}
-low_sample<-dataset_analysis%>%
-  filter(effective_n_control<2 | effective_n_experiment<2)
+```{r filter out low sample size}
+low_sample <- dataset_analysis %>%
+  filter(effective_n_control < 2 | effective_n_experiment < 2)
 ```
@@
 
-# Converting variance to SD
+## Converting variance to SD
 
@@
 dataset_analysis <- dataset_analysis %>%
-  mutate(sd_experiment = if_else(type_measure_dispersion_experiment %in% c('se', 'SE'), #condition to check
-      measure_dispersion_experiment * sqrt(as.numeric(n_experiment)), # do this if true
-      measure_dispersion_experiment), #else do this
-      .after=measure_dispersion_experiment)
+  mutate(sd_experiment = if_else(
+    condition = type_measure_dispersion_experiment %in% c('se', 'SE'), 
+    true = measure_dispersion_experiment * sqrt(as.numeric(n_experiment)), 
+    false = measure_dispersion_experiment), 
+    .after = measure_dispersion_experiment)
+
 # For control group
 dataset_analysis <- dataset_analysis %>%
-  mutate(sd_control = if_else(type_measure_dispersion_control %in% c('se', 'SE'), #condition to check
-      measure_dispersion_control* sqrt(as.numeric(n_control)), # do this if true
-      measure_dispersion_control), #else do this
+  mutate(sd_control = if_else(#
+    condition = type_measure_dispersion_control %in% c('se', 'SE'), 
+    true = measure_dispersion_control* sqrt(as.numeric(n_control)), 
+    false = measure_dispersion_control),
     .after=measure_dispersion_control)
@@
 
-# No effect size provided
+## No effect size provided
 
@@
 # To calculate means by groups
-trait_mean<- dataset_analysis%>%
-  group_by(trait_type)%>%
-  summarise(
-    cumulative_mean = mean (
+trait_mean<- dataset_analysis %>%
+  group_by(trait_type) %>%
+  summarise(cumulative_mean = mean (
     c(measure_central_tendency_experiment,measure_central_tendency_control),
-      na.rm=T
+    na.rm = T
     ),
     count = n()
-  )%>%
+  ) %>%
   arrange(desc(count))
@@
 # Now I need to assign the mean values from this to the missing ES proxies
-dataset_analysis<-dataset_analysis%>%
-  left_join(trait_mean, by= "trait_type")%>%
+dataset_analysis <- dataset_analysis %>%
+  left_join(trait_mean, by = "trait_type") %>%
   mutate(measure_central_tendency_experiment = if_else((
@@
       cumulative_mean,
-    measure_central_tendency_control),)%>%
+      measure_central_tendency_control),) %>%
   select(-cumulative_mean)
-
 ```
 
-# Effect Size Estimation
+## Effect Size Estimation
 
-## Calculate lnRR
+### Calculate lnRR
 
-### Geary's Test
+#### Geary's Test
 
@@
 # Assumption of normality assumed to be approximately correct when values are >= 3.
-dataset_analysis<- dataset_analysis %>% 
+dataset_analysis <- dataset_analysis %>% 
   mutate(geary_control = geary(measure_central_tendency_control,
@@
 # How many fail?
-    geary_res <-dataset_analysis %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()
+geary_res <- dataset_analysis %>%
+  group_by(geary_test) %>% 
+  summarise(n = n()) %>%  
+  data.frame()
 
@@
 ```{r for lnRR}
-
-## ─────────────────────────────────────────────────────────────
 ## 1.  Keeping rows where lnRR can be calculated. 
@@
 ##    — store the dropped rows to inspect and join back later
-## ─────────────────────────────────────────────────────────────
 
-only_SMDH <-dataset_analysis%>%
+only_SMDH <-dataset_analysis %>%
   filter(proxy_decision == "contingency table"
@@
 
-## -------------------------------------------------------------------------
 ## 2. Rows whose means are > 0 (lnRR needs ratio scale data)
 ##  - store the dropped rows to inspect and join back later to the dataset
-## -------------------------------------------------------------------------
 
-neg_means<- dataset_analysis%>%
+neg_means <- dataset_analysis %>%
   filter(measure_central_tendency_experiment <= 0 |
@@
 
-## -------------------------------------------------------------------------
 ## 3. Estimating lnRR using metafor::escalc for cases where SD is available
-## -------------------------------------------------------------------------
-
 # Using function 'escalc()' (with measure=ROM and 'vtype=LS')
 
-dataset_analysis<- escalc(measure = "ROM", 
-              vtype= "LS",
+dataset_analysis <- escalc(
+  measure = "ROM", 
+  vtype = "LS",
   n1i = effective_n_experiment, 
@@
 
-not_calculated<-dataset_analysis%>%filter(is.na(lnRR)|is.na(lnRR_variance))
+not_calculated <- dataset_analysis %>% 
+  filter(is.na(lnRR)|is.na(lnRR_variance))
 
@@
 
-## -------------------------------------------------------------------------
 ## 4. Estimating lnRR using Missing Case approach from Nakagawa 2022
 ##    see https://alistairmcnairsenior.github.io/Miss_SD_Sim/
-## -------------------------------------------------------------------------
 
@@
 
-dataset_analysis<-dataset_analysis%>%
+dataset_analysis <- dataset_analysis %>%
   mutate(lnRR = if_else((
@@
       lnRR_variance),)%>%
-select(-b_CV2_exp,-b_CV2_con,-cv_Control,-cv_Experimental,-cv2_con_new,-cv2_exp_new,-lnrr_laj,-v_lnrr_laj)
+  select(-b_CV2_exp, -b_CV2_con, -cv_Control, -cv_Experimental,
+         -cv2_con_new, -cv2_exp_new, -lnrr_laj, -v_lnrr_laj)
 
 ## How many lnRR were not calculated now?
-
-not_calculated<-dataset_analysis%>%filter(is.na(lnRR)|is.na(lnRR_variance))
+not_calculated <- dataset_analysis %>% 
+  filter(is.na(lnRR)|is.na(lnRR_variance))
 
@@
 
-dataset_analysis<-bind_rows(dataset_analysis,only_SMDH,neg_means)
+dataset_analysis <- bind_rows(dataset_analysis, only_SMDH, neg_means)
 ```
 
-### Sign for Effect Size
+#### Sign for Effect Size
 
@@
 ```{r correct sign for ES}
-
-dataset_analysis<-dataset_analysis%>%
-  mutate(lnRR_sign=lnRR*proxies_sign)
+dataset_analysis <- dataset_analysis %>%
+  mutate(lnRR_sign = lnRR*proxies_sign)
 ```
 
-### Outliers Check
+#### Outliers Check
 
@@
 ```{r}
-
 # ## We have to exclude the datapoints where we do not have dispersion value. We have added 0 ES in some cases and this is not allowing the lm line to be plotted
@@
 ```{r Funnel Plot}
-
 funnel_lnRR <- dataset_analysis %>%
@@
   geom_point(color= "#7DCE82", alpha = 0.4, size = 3) +
-  geom_vline(xintercept = 0, linetype = "dashed", color = "#8B4513", linewidth=0.65) +  # Add vertical dashed line at x = 0
+  # Add vertical dashed line at x = 0
+  geom_vline(xintercept = 0, linetype = "dashed", color = "#8B4513", linewidth=0.65) +  
   ggtitle("Funnel Plot for lnRR") +
@@
   filter(is.na(lnRR_sign) | is.na(lnRR_variance))
-
 ```
@@
 
-## Calculate SMDH
+### Calculate SMDH
 
--   For results only reported as inferential statistics (e.g., t-test, chi-square), we will use the equations provided by (Lajeunesse 2013; Nakagawa and Cuthill 2007; and other sources if needed) to calculate their corresponding SMD estimates for the analyses.
+* For results only reported as inferential statistics (e.g., t-test, chi-square), we will use the equations provided by (Lajeunesse 2013; Nakagawa and Cuthill 2007; and other sources if needed) to calculate their corresponding SMD estimates for the analyses.
 
--   Note that lnRR cannot be calculated from inferential statistics and that only SMD without heteroskedasticity correction can be calculated from inferential statistics.
+* Note that lnRR cannot be calculated from inferential statistics and that only SMD without heteroskedasticity correction can be calculated from inferential statistics.
 
 ```{r}
-#-------------------------------------------------------------------------
 # 1. SMDH for most cases where mean, variance and sample size was reported
@@
 
-dataset_analysis<- escalc(measure = "SMD", 
+dataset_analysis <- escalc(
+  measure = "SMD", 
   vtype= "LS",
@@
 # Cases where it was not calculated using mean, variance and sample size
-noSMDH<-dataset_analysis%>%filter(is.na(SMDH))
+noSMDH <- dataset_analysis %>% 
+  filter(is.na(SMDH))
 
-#-------------------------------------------------------------------------
 # 2. No effect of the treatment is present but 
@@
 dataset_analysis <- dataset_analysis %>%
-  mutate(SMDH = if_else(proxy_comment == "use 0 as ES" & !is.na(proxy_comment), (measure_central_tendency_experiment-measure_central_tendency_control), SMDH))%>%
+  mutate(SMDH = if_else(proxy_comment == "use 0 as ES" & !is.na(proxy_comment), (measure_central_tendency_experiment-measure_central_tendency_control), SMDH)) %>%
   mutate(SMDH_variance = if_else(proxy_comment == "use 0 as ES" & !is.na(proxy_comment), ((effective_n_experiment+effective_n_control)/(effective_n_experiment*effective_n_control)), SMDH_variance))
@@
 # Cases where it was not calculated using mean, variance and sample size
-noSMDH<-dataset_analysis%>%filter(is.na(SMDH))
-
+noSMDH <- dataset_analysis %>% filter(is.na(SMDH))
 ```
@@
 
-```{r}
-contingency_table<-dataset_analysis%>%filter(proxy_decision=="contingency table")
+```{r contingency_table}
+contingency_table <- dataset_analysis %>%
+  filter(proxy_decision == "contingency table")
 
@@
     failure_control = n_control - success_control)
+
 # Calculate Log Odds Ratio (lnOR)
-contingency_table<- escalc(measure="OR", ai=success_experiment, bi=failure_experiment, ci=success_control, di=failure_control, data=contingency_table, var.names = c('lnOR',
-                                      'lnOR_variance'))
+contingency_table <- escalc(
+  measure = "OR",
+  ai = success_experiment, 
+  bi = failure_experiment, 
+  ci = success_control, 
+  di = failure_control, 
+  data = contingency_table,
+  var.names = c('lnOR', 'lnOR_variance'))
 # Calculate SMDH
 contingency_table <- contingency_table %>%
-  mutate(SMDH=(lnOR*sqrt(3))/pi,
-         SMDH_variance=(3*lnOR_variance)/pi^2)
+  mutate(SMDH = (lnOR*sqrt(3))/pi,
+         SMDH_variance = (3*lnOR_variance)/pi^2)
 
@@
 dataset_analysis <- rows_update(
-  x = dataset_analysis,           # Target dataset to update
+  # Target dataset to update
+  x = dataset_analysis,           
   y = contingency_table %>% 
@@
 
-![From Cooper2019 Table 11.3](/images/ancova-d.png)
+![From Cooper2019 Table 11.3](../images/ancova-d.png)
 
@@
 
-![From Cooper2019 Table 11.3](/images/anova-d.png)
+![From Cooper2019 Table 11.3](../images/anova-d.png)
 
@@
 ```{r}
-
-ancova_SMDH<-dataset_analysis%>%filter(statistics_type=="ANCOVA")
+ancova_SMDH <- dataset_analysis %>% 
+  filter(statistics_type=="ANCOVA")
 # 3 effect size where SMDH needs to be estimated from ANCOVA
@@
 
-ancova_SMDH<-ancova_SMDH%>%
-  mutate(SMDH = sign_relationship*(d_anova(statistics_value,n_experiment,n_control)))%>%
+ancova_SMDH <- ancova_SMDH %>%
+  mutate(SMDH = sign_relationship*(d_anova(statistics_value, n_experiment, n_control))) %>%
   mutate(SMDH_variance = var_d_anova(SMDH, n_experiment,n_control))
@@
 dataset_analysis <- rows_update(
-  x = dataset_analysis,           # Target dataset to update
+  # Target dataset to update
+  x = dataset_analysis,           
   y = ancova_SMDH %>% 
-        select(Observation_ID, SMDH, SMDH_variance), # Updates from ancova_SMDH
-  by = "Observation_ID"       # Match on Observation_ID
-)
+    # Updates from ancova_SMDH
+    select(Observation_ID, SMDH, SMDH_variance),
+  # Match on Observation_ID
+  by = "Observation_ID")
 ```
@@
 # 1 effect size where SMDH needs to be estimated from t-test statistics
-t_test_SMDH<-dataset_analysis%>%filter(statistics_type=="t-test")
+t_test_SMDH <- dataset_analysis %>% 
+  filter(statistics_type ==" t-test")
 
@@
 
-t_test_SMDH<-t_test_SMDH%>%
-  mutate(SMDH = sign_relationship*(d_t_test(statistics_value,n_experiment,n_control)))%>%
-    mutate(SMDH_variance = var_d_t_test(SMDH, n_experiment,n_control))
+t_test_SMDH <- t_test_SMDH %>%
+  mutate(SMDH = sign_relationship*(d_t_test(statistics_value, n_experiment, n_control))) %>%
+  mutate(SMDH_variance = var_d_t_test(SMDH, n_experiment, n_control))
 
@@
 ```{r correct sign for ES SMDH}
-
-dataset_analysis<-dataset_analysis%>%
-  mutate(SMDH_sign=SMDH*proxies_sign)
+dataset_analysis <- dataset_analysis %>%
+  mutate(SMDH_sign = SMDH*proxies_sign)
 ```
@@
 since the sample is the same and these are the repeated measures of the same sample.
-low_sample=dataset_analysis%>%filter(is.na(SMDH))
-write.csv(low_sample,file=here::here("data/03_data_cleaning/low_sample.csv"),row.names = FALSE)
+low_sample = dataset_analysis %>%
+  filter(is.na(SMDH))
+```
+
+```{r, eval = F}
+## export to csv file
+write.csv(low_sample,
+          file = here::here("data/03_data_cleaning/low_sample.csv"), row.names = FALSE)
 ```
@@
 ```{r}
-dataset_analysis<-dataset_analysis%>%anti_join(low_sample,by="Observation_ID")
+dataset_analysis <- dataset_analysis %>%
+  anti_join(low_sample, by = "Observation_ID")
 ```
@@
 
-```{r}
-# # Complete dataset that can be used for analysis
-# write.csv(dataset_analysis,file=here::here("data/04_data_analysis/dataset_analysis.csv"),row.names = FALSE)
-# 
-# 
-# # Dataset that can be used to estimate lnRR
-# 
-# dataset_lnRR<-dataset_analysis%>%
-#   filter(!is.na(lnRR_sign) & !is.na(lnRR_variance))
-# 
-# write.csv(dataset_lnRR,file=here::here("data/04_data_analysis/dataset_lnRR.csv"),row.names = FALSE)
-# 
-# # Dataset that can be used to estimate SMD(H)
-# 
-# dataset_SMDH<-dataset_analysis%>%
-#   filter(!is.na(SMDH_sign) & !is.na(SMDH_variance))
-# 
-# write.csv(dataset_SMDH,file=here::here("data/04_data_analysis/dataset_SMDH.csv"),row.names = FALSE)
+```{r, eval = F}
+## Complete dataset that can be used for analysis
+write.csv(dataset_analysis, 
+          file = here::here("data/04_data_analysis/dataset_analysis.csv"),
+          row.names = FALSE)
+## Dataset that can be used to estimate lnRR
+dataset_lnRR <- dataset_analysis %>%
+  filter(!is.na(lnRR_sign) & !is.na(lnRR_variance))
+
+write.csv(dataset_lnRR,
+          file = here::here("data/04_data_analysis/dataset_lnRR.csv"),
+          row.names = FALSE)
+## Dataset that can be used to estimate SMD(H)
+dataset_SMDH <- dataset_analysis %>%
+filter(!is.na(SMDH_sign) & !is.na(SMDH_variance))
+write.csv(dataset_SMDH,file=here::here("data/04_data_analysis/dataset_SMDH.csv"),row.names = FALSE)
 ```
